### 2021-11-02 multi-channel-urg.tex
started deriving mck urg

\documentclass[12pt]{article}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref}
\usepackage[margin=0.5in]{geometry}
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\section{Introduction}

\begin{equation}\begin{aligned}
	H = \sum_{k,\sigma,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\sigma} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}
\end{aligned}\end{equation}
\begin{equation}\begin{aligned}
	\Delta H = c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T
\end{aligned}\end{equation}

\section{Leading order renormalization}
Second term.
\begin{equation}\begin{aligned}
	&T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T \\
	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \beta } \frac{1}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}c^\dagger_{q\beta} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{ \beta\alpha}\\
	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} \frac{1}{\omega - \frac{1}{2}D - J S_d^z s_q^z}c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} & \left[\tau = \frac{1}{2}, \epsilon_q = D\right] \\
	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} \frac{\omega - \frac{1}{2}D + J S_d^z s_q^z}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \\
	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\left(\omega - \frac{1}{2}D\right) \left(1 - \hat n_{q\beta}\right) +  J S_d^z c_{q\beta} s_q^z c^\dagger_{q\beta}}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} \\
	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\left(\omega - \frac{1}{2}D\right) \left(1 - \hat n_{q\beta}\right) +  J S_d^z \left(s_q^z + \beta\right) \left(1- \hat n_{q\beta}\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} & \left[\left[c_{q\beta}, s_q^z\right] = \beta c_{q\beta}\right] \\
	&= J^2 |\delta D|\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) + J S_d^z \left(s_q^z + \beta\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b  \\
	&= \frac{J^2\left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}|\delta D| \sum_{\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} & \left[\text{term 1}\right]\\
	&+ \frac{J^3}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} |\delta D|\sum_{\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} S_d^z S_d^b s^b_{\beta \alpha} \left(s_q^z + \beta\right) & \left[\text{term 2}\right] \\
\end{aligned}\end{equation}
First term.
\begin{equation}\begin{aligned}
	&c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c \\
	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime} c^\dagger_{q\beta} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\beta \alpha} \frac{1}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \beta}\\
	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{1}{\omega^\prime - \frac{1}{2}D - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[\tau = -\frac{1}{2},\epsilon_q = -D\right] \\
	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{1}{-\omega + \frac{1}{2}D - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[\omega + \omega^\prime = D\right] \\
							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(-\omega + \frac{1}{2}D\right) + J S_d^z s_q^z}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta}\\
							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) - J S_d^z s_q^z}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) \hat n_{q\beta} - J S_d^z  c^\dagger_{q\beta}s_q^z c_{q\beta}}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} \\
							   &= \frac{J^2\left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha^\prime \beta}\hat n_{q\beta} & \left[\text{term 3}\right] \\
							   &- \frac{J^3}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} S_d^z S_d^b s^b_{\alpha^\prime \beta} c^\dagger_{q\beta}s_q^z c_{q\beta} & \left[\text{term 4}\right] \\
\end{aligned}\end{equation}
Adding the two terms gives
\begin{equation}\begin{aligned}
	\Delta H = \text{term 1} + \text{term 2} + \text{term 3} + \text{term 4}
\end{aligned}\end{equation}
The odd terms together give
\begin{equation}\begin{aligned}
	\text{term 1} + \text{term 3} =
\end{aligned}\end{equation}

\end{document}

### 2021-11-03 multi-channel-urg.tex
computed both terms at second order, now need to relate the omega

@@
 \begin{equation}\begin{aligned}
-	\Delta H = c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T
+	\Delta H = \tau\left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
 \end{aligned}\end{equation}
@@
 \section{Leading order renormalization}
-Second term.
+\subsection{Second term}
 \begin{equation}\begin{aligned}
@@
 	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\left(\omega - \frac{1}{2}D\right) \left(1 - \hat n_{q\beta}\right) +  J S_d^z c_{q\beta} s_q^z c^\dagger_{q\beta}}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} \\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\left(\omega - \frac{1}{2}D\right) \left(1 - \hat n_{q\beta}\right) +  J S_d^z \left(s_q^z + \beta\right) \left(1- \hat n_{q\beta}\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} & \left[\left[c_{q\beta}, s_q^z\right] = \beta c_{q\beta}\right] \\
-	&= J^2 |\delta D|\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) + J S_d^z \left(s_q^z + \beta\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b  \\
-	&= \frac{J^2\left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}|\delta D| \sum_{\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} & \left[\text{term 1}\right]\\
-	&+ \frac{J^3}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} |\delta D|\sum_{\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} S_d^z S_d^b s^b_{\beta \alpha} \left(s_q^z + \beta\right) & \left[\text{term 2}\right] \\
+	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\left(\omega - \frac{1}{2}D\right) \left(1 - \hat n_{q\beta}\right) +  J S_d^z \left(s_q^z + \frac{\beta}{2}\right) \left(1- \hat n_{q\beta}\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} & \left[\left[c_{q\beta}, s_q^z\right] = \frac{\beta}{2} c_{q\beta}\right] \\
+	&= J^2 |\delta D|\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) + J S_d^z \beta}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b & \left[s_q^z = \frac{\beta}{2}\right]  \\
+	&= \frac{J^2\left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} & \left[\text{term 1}\right]\\
+	&+ \frac{J^3}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} |\delta D|\sum_{\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a S_d^z S_d^b s^a_{\alpha^\prime \beta} s^b_{\beta \alpha} \beta & \left[\text{term 2}\right] \\
 \end{aligned}\end{equation}
-First term.
+We will now simplify the terms individually.
+In term 1, only the configurations \(a \neq b\) can lead to a non-trivial impurity spin operator and hence contribute to renormalization.
+For \(a \neq b\), we have \(S_d^a S_d^b = \frac{i}{2} \sum_c \epsilon^{abc}S_d^c \).
+Therefore,
+\begin{equation}\begin{aligned}
+\sum_{a,b}S_d^a S_d^b\left(s^a s^b\right)_{\alpha^\prime \alpha} = - \frac{1}{4}\sum_{c,e} S_d^c \left(s^e\right)_{\alpha^\prime \alpha}\sum_{a,b}\epsilon^{abc}\epsilon^{abe} = - \frac{1}{4}\sum_{c,e} S_d^c \left(s^e\right)_{\alpha^\prime \alpha} 2 \delta_{ce} = -\frac{1}{2}\vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
+\end{aligned}\end{equation}
+Term 1 therefore simplifies to
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\frac{J^2\left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha} && \left[\text{term 1}\right]\\
+\end{aligned}\end{equation}
+In term 2, we use the identity:
+\begin{equation}\begin{aligned}
+S^a S^z S^b = \frac{1}{4}\sum_c \left(\delta_{ac}\delta_{zb} - \delta_{ab}\delta_{zc}\right) S^c
+\end{aligned}\end{equation}
+Substituting this gives
+\begin{equation}\begin{aligned}
+	\sum_{\beta,a,b} S_d^a S_d^z S_d^b s^a_{\alpha^\prime \beta} s^b_{\beta \alpha} \beta &= \frac{1}{4}\sum_{\beta,c}\beta \left(S_d^c s^c_{\alpha^\prime\beta}s^z_{\beta\alpha} - S_d^z s^c_{\alpha^\prime\beta} s^c_{\beta\alpha}\right) \\
+	\implies \text{term 2} &= \frac{J^3|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{\beta k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \beta s^c_{\alpha^\prime\beta}\left(S_d^c s^z_{\beta\alpha} - S_d^z s^c_{\beta\alpha}\right)\\
+			       &= \frac{J^3|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{\beta k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\frac{1}{2}S_d^c s^c_{\alpha^\prime\alpha}\ - \beta S_d^z s^c_{\beta\alpha}s^c_{\alpha^\prime\beta}\right)
+\end{aligned}\end{equation}
+
+\subsection{First term}
 \begin{equation}\begin{aligned}
@@
 	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{1}{\omega^\prime - \frac{1}{2}D - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[\tau = -\frac{1}{2},\epsilon_q = -D\right] \\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{1}{-\omega + \frac{1}{2}D - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[\omega + \omega^\prime = D\right] \\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(-\omega + \frac{1}{2}D\right) + J S_d^z s_q^z}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta}\\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) - J S_d^z s_q^z}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) \hat n_{q\beta} - J S_d^z  c^\dagger_{q\beta}s_q^z c_{q\beta}}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} \\
-							   &= \frac{J^2\left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha^\prime \beta}\hat n_{q\beta} & \left[\text{term 3}\right] \\
-							   &- \frac{J^3}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} S_d^z S_d^b s^b_{\alpha^\prime \beta} c^\dagger_{q\beta}s_q^z c_{q\beta} & \left[\text{term 4}\right] \\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z s_q^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta}\\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) - J S_d^z s_q^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) \hat n_{q\beta} - J S_d^z  c^\dagger_{q\beta}s_q^z c_{q\beta}}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} \\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) \hat n_{q\beta} - J S_d^z \left(s_q^z - \frac{\beta}{2}\right) \hat n_{q\beta}}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} & \left[\left[c^\dagger_{q\beta}, s_q^z\right] = -\frac{\beta}{2} c^\dagger_{q\beta}\right] \\
+							   &= J^2 |\delta D|\sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z \beta}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} & \left[s_q^z = -\frac{1}{2}\beta\right] \\
+							   &= -\frac{J^2\left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^b s^a\right)_{\alpha^\prime \alpha} & \left[\text{term 3}\right] \\
+							   &\quad+ \frac{J^3|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a S_d^z S_d^b s^a_{\beta \alpha} s^b_{\alpha^\prime \beta} \beta & \left[\text{term 4}\right] \\
 \end{aligned}\end{equation}
-Adding the two terms gives
+term 3 can be made identical to term 1 using the relation: \(s^b s^a = -s^b s^a \text{ for } a \neq b\). With this change, term 3 becomes
 \begin{equation}\begin{aligned}
-	\Delta H = \text{term 1} + \text{term 2} + \text{term 3} + \text{term 4}
+	\text{term 3} = \frac{J^2\left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} = \text{term 1}
 \end{aligned}\end{equation}
-The odd terms together give
+For term 4, we get
 \begin{equation}\begin{aligned}
-	\text{term 1} + \text{term 3} =
+	\sum_{\beta,a,b} S_d^a S_d^z S_d^b s^b_{\alpha^\prime \beta} s^a_{\beta \alpha} \beta &= \frac{1}{4}\sum_{\beta,a,b,c}\beta\left(\delta_{ac}\delta_{zb} - \delta_{ab}\delta_{zc}\right) S^cs^b_{\alpha^\prime \beta} s^a_{\beta \alpha} \\
+																&= \frac{1}{4}\sum_{\beta,c}\beta s^c_{\beta\alpha}\left(S^c_d s^z_{\alpha^\prime\beta} - S^z_d s^c_{\alpha^\prime\beta}\right)
+\end{aligned}\end{equation}
+which gives
+\begin{equation}\begin{aligned}
+	\text{term 4} = \frac{J^3|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{\beta k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\frac{1}{2}S_d^c s^c_{\alpha^\prime\alpha}\ - \beta S_d^z s^c_{\beta\alpha}s^c_{\alpha^\prime\beta}\right)
 \end{aligned}\end{equation}

### 2021-11-03 multi-channel-urg.tex
completed second order Kondo URG, everything matches perfectly

@@
 \begin{equation}\begin{aligned}
-	\Delta H = \tau\left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
+	\Delta H = \left[c^\dagger T, \eta \right] = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c - T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\text{term 3} = \frac{J^2\left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} = \text{term 1}
+	\text{term 3} = \frac{J^2\left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} = \frac{1}{2}\frac{J^2\left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
 \end{aligned}\end{equation}
@@
 
+\subsection{Total renormalization}
+From the formula for the renormalization \(\Delta H\), we write
+\begin{equation}\begin{aligned}
+	\Delta H = \frac{1}{2}\left(\text{term 3} + \text{term 4} - \text{term 1} - \text{term 2}\right)
+\end{aligned}\end{equation}
+From the constraints of URG and particle-hole symmetry, we have the constraint \(\omega + \omega^\prime = H_d^0 + H_d^1\).
+\(H_d^0\) is the diagonal part when the current node is unoccupied and \(H_d^1\) is when its occupied.
+For our case, \(H_d^0 + H_d^1 = \sum \epsilon_q \tau_q = D\), because both the hole and particle states have energy of \(\frac{D}{2}\) (\(\epsilon_q\) and \(\tau\) flip sign together).
+We therefore have \((\omega - D/2) = -(\omega^\prime - D/2)\).
+term 2 and term 4 cancel each other and term 3 becomes equal to term 1.
+The total renormalization at second order is therefore (relabelling \(\omega^\prime\) as \(\omega\))
+\begin{equation}\begin{aligned}
+	\Delta H = \text{term 3} = \frac{1}{2}\frac{J^2\left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
+\end{aligned}\end{equation}
+which gives
+\begin{equation}\begin{aligned}
+	\Delta J = \frac{1}{2}\frac{J^2\left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}
+\end{aligned}\end{equation}
+The choice of \(\omega = D\) gives
+\begin{equation}\begin{aligned}
+	\Delta J = \frac{J^2 D |\delta D|}{D^2 - \frac{1}{4}J^2}
+\end{aligned}\end{equation}
+For \(J \ll D\), we get the one-loop PMS form.
+
 \end{document}

### 2021-11-03 multi-channel-urg.tex
added more details on the model, the URG expansion and inserted a missing n_j

--- 2021-11-02 multi-channel-urg.tex
@@
-\documentclass[12pt]{article}
+\documentclass{revtex4-2}
 \usepackage{braket,amsmath,amssymb,graphicx,float,hyperref}
-\usepackage[margin=0.5in]{geometry}
+\allowdisplaybreaks
 \begin{document}
@@
 \section{Introduction}
-
+The multi-channel Kondo model is described by the Hamiltonian
 \begin{equation}\begin{aligned}
-	H = \sum_{k,\sigma,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\sigma} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}
+	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
+\end{aligned}\end{equation}
+It is mostly identical to the single-channel Kondo model: \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels.
+\(\vec S_d, \vec s\) are the impurity and conduction bath spin vectors.
+The renormalization at step \(j\) is given by
+\begin{equation}\begin{aligned}
+	\Delta H_j = \left[c^\dagger T, \eta \right] = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c - T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
 \end{aligned}\end{equation}
 \begin{equation}\begin{aligned}
-	\Delta H = c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T
+	c^\dagger T = J \sum_{k < \Lambda_j, \alpha}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, &&&H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
+\end{aligned}\end{equation}
+Usually we treat the \(\hat \omega\) as number(s) and study the renormalization in the couplings as functions of the quantum fluctuation scales.
+Each value of the fluctuation scale defines an eigendirection of \(\hat \omega\).
+We have then essentially traded off the complexity in the non-commuatativity of the diagonal and off-diagonal terms for all the directions in the manifold of \(\hat \omega\).
+
+Here we will do something different.
+We will redefine the \(\hat \omega\) by pulling out the off-diagonal term from it: \(\hat \omega \to \hat \omega - H_X\), and then study the renormalization at various orders by expanding the denominator in powers of \(H_X\).
+Such a redefinition essentially amounts to a rotation of the eigendirections of \(\hat \omega\).
+This is done in order to extract some information out of \(\hat \omega\), specifically the dependence of the RG equations on the channel number \(K = \sum_\gamma\).
+This dependence is in principle present even if we do not do such a redefinition and expansion, in the various directions and values of \(\omega\), because those values encode the non-perturbative information regarding scattering at all loops.
+However, it is difficult to read off this information directly.
+This step of redefinition followed by expansion is being done with the sole aim of exposing such information.
+
+The expansion we are talking about is
+\begin{equation}\begin{aligned}
+	\eta = \frac{1}{\hat \omega - H_D}T^\dagger c = \frac{1}{\omega^\prime - H_D - H_X}T^\dagger c \simeq \frac{1}{\omega^\prime - H_D}T^\dagger c + \frac{1}{\omega^\prime - H_D}H_X \frac{1}{\omega^\prime - H_D} T^\dagger c
+\end{aligned}\end{equation}
+where \(H_X = J \sum_{k,k^\prime < \Lambda_j, \alpha,\alpha^\prime}\vec{S_d}\cdot\vec{s}_{\alpha \alpha^\prime}c^\dagger_{k\alpha}c_{k^\prime\alpha^\prime}\) is scattering between the entangled electrons.
+With this change, the second and third order renormalizations will take the form
+\begin{equation}\begin{aligned}
+	\Delta H^{(2)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c - T^\dagger c \frac{1}{\omega - H_D}c^\dagger T
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c - T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T
 \end{aligned}\end{equation}
@@
 \section{Leading order renormalization}
-Second term.
 \begin{equation}\begin{aligned}
+	\Delta H^{(2)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c}_\text{first term}~ -~ \underbrace{T^\dagger c \frac{1}{\omega - H_D}c^\dagger T}_\text{second term}
+\end{aligned}\end{equation}
+\subsection{Second term}
+\begin{align}
 	&T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T \\
@@
 	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\left(\omega - \frac{1}{2}D\right) \left(1 - \hat n_{q\beta}\right) +  J S_d^z c_{q\beta} s_q^z c^\dagger_{q\beta}}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} \\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\left(\omega - \frac{1}{2}D\right) \left(1 - \hat n_{q\beta}\right) +  J S_d^z \left(s_q^z + \beta\right) \left(1- \hat n_{q\beta}\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} & \left[\left[c_{q\beta}, s_q^z\right] = \beta c_{q\beta}\right] \\
-	&= J^2 |\delta D|\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) + J S_d^z \left(s_q^z + \beta\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b  \\
-	&= \frac{J^2\left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}|\delta D| \sum_{\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} & \left[\text{term 1}\right]\\
-	&+ \frac{J^3}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} |\delta D|\sum_{\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} S_d^z S_d^b s^b_{\beta \alpha} \left(s_q^z + \beta\right) & \left[\text{term 2}\right] \\
+	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\left(\omega - \frac{1}{2}D\right) \left(1 - \hat n_{q\beta}\right) +  J S_d^z \left(s_q^z + \frac{\beta}{2}\right) \left(1- \hat n_{q\beta}\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} & \left[\left[c_{q\beta}, s_q^z\right] = \frac{\beta}{2} c_{q\beta}\right] \\
+	&= J^2 n_j |\delta D|\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) + J S_d^z \beta}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b & \left[s_q^z = \frac{\beta}{2}\right]  \\
+	&= \frac{J^2 n_j |\delta D|\left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} & \left[\text{term 1}\right]\\
+	&+ \frac{J^3 n_j |\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a S_d^z S_d^b s^a_{\alpha^\prime \beta} s^b_{\beta \alpha} \beta & \left[\text{term 2}\right] \\
+\end{align}
+We will now simplify the terms individually.
+In term 1, only the configurations \(a \neq b\) can lead to a non-trivial impurity spin operator and hence contribute to renormalization.
+For \(a \neq b\), we have \(S_d^a S_d^b = \frac{i}{2} \sum_c \epsilon^{abc}S_d^c \).
+Therefore,
+\begin{equation}\begin{aligned}
+\sum_{a,b}S_d^a S_d^b\left(s^a s^b\right)_{\alpha^\prime \alpha} = - \frac{1}{4}\sum_{c,e} S_d^c \left(s^e\right)_{\alpha^\prime \alpha}\sum_{a,b}\epsilon^{abc}\epsilon^{abe} = - \frac{1}{4}\sum_{c,e} S_d^c \left(s^e\right)_{\alpha^\prime \alpha} 2 \delta_{ce} = -\frac{1}{2}\vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
 \end{aligned}\end{equation}
-First term.
+Term 1 therefore simplifies to
 \begin{equation}\begin{aligned}
+	-\frac{1}{2}\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha} && \left[\text{term 1}\right]\\
+\end{aligned}\end{equation}
+In term 2, we use the identity:
+\begin{equation}\begin{aligned}
+S^a S^z S^b = \frac{1}{4}\sum_c \left(\delta_{ac}\delta_{zb} - \delta_{ab}\delta_{zc}\right) S^c
+\end{aligned}\end{equation}
+Substituting this gives
+\begin{equation}\begin{aligned}
+	\sum_{\beta,a,b} S_d^a S_d^z S_d^b s^a_{\alpha^\prime \beta} s^b_{\beta \alpha} \beta &= \frac{1}{4}\sum_{\beta,c}\beta \left(S_d^c s^c_{\alpha^\prime\beta}s^z_{\beta\alpha} - S_d^z s^c_{\alpha^\prime\beta} s^c_{\beta\alpha}\right) \\
+	\implies \text{term 2} &= \frac{J^3|\delta D| n_j}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{\beta k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \beta s^c_{\alpha^\prime\beta}\left(S_d^c s^z_{\beta\alpha} - S_d^z s^c_{\beta\alpha}\right)\\
+			       &= \frac{J^3|\delta D| n_j}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{\beta k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\frac{1}{2}S_d^c s^c_{\alpha^\prime\alpha}\ - \beta S_d^z s^c_{\beta\alpha}s^c_{\alpha^\prime\beta}\right)
+\end{aligned}\end{equation}
+
+\subsection{First term}
+\begin{align}
 	&c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c \\
@@
 	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{1}{\omega^\prime - \frac{1}{2}D - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[\tau = -\frac{1}{2},\epsilon_q = -D\right] \\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{1}{-\omega + \frac{1}{2}D - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[\omega + \omega^\prime = D\right] \\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(-\omega + \frac{1}{2}D\right) + J S_d^z s_q^z}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta}\\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) - J S_d^z s_q^z}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) \hat n_{q\beta} - J S_d^z  c^\dagger_{q\beta}s_q^z c_{q\beta}}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} \\
-							   &= \frac{J^2\left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha^\prime \beta}\hat n_{q\beta} & \left[\text{term 3}\right] \\
-							   &- \frac{J^3}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} S_d^z S_d^b s^b_{\alpha^\prime \beta} c^\dagger_{q\beta}s_q^z c_{q\beta} & \left[\text{term 4}\right] \\
-\end{aligned}\end{equation}
-Adding the two terms gives
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z s_q^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta}\\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) - J S_d^z s_q^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) \hat n_{q\beta} - J S_d^z  c^\dagger_{q\beta}s_q^z c_{q\beta}}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} \\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) \hat n_{q\beta} - J S_d^z \left(s_q^z - \frac{\beta}{2}\right) \hat n_{q\beta}}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} & \left[\left[c^\dagger_{q\beta}, s_q^z\right] = -\frac{\beta}{2} c^\dagger_{q\beta}\right] \\
+							   &= J^2 n_j |\delta D|\sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z \beta}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} & \left[s_q^z = -\frac{1}{2}\beta\right] \\
+							   &= -\frac{J^2\left(\omega^\prime - \frac{1}{2}D\right) n_j |\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^b s^a\right)_{\alpha^\prime \alpha} & \left[\text{term 3}\right] \\
+							   &\quad+ \frac{J^3 n_j |\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a S_d^z S_d^b s^a_{\beta \alpha} s^b_{\alpha^\prime \beta} \beta & \left[\text{term 4}\right]
+\end{align}
+term 3 can be made identical to term 1 using the relation: \(s^b s^a = -s^b s^a \text{ for } a \neq b\). With this change, term 3 becomes
 \begin{equation}\begin{aligned}
-	\Delta H = \text{term 1} + \text{term 2} + \text{term 3} + \text{term 4}
-\end{aligned}\end{equation}
-The odd terms together give
-\begin{equation}\begin{aligned}
-	\text{term 1} + \text{term 3} =
+	\text{term 3} = \frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} \\
+	= \frac{1}{2}\frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
 \end{aligned}\end{equation}
 
+For term 4, we get
+\begin{equation}\begin{aligned}
+	\sum_{\beta,a,b} S_d^a S_d^z S_d^b s^b_{\alpha^\prime \beta} s^a_{\beta \alpha} \beta = \frac{1}{4}\sum_{\beta,a,b,c}\beta\left(\delta_{ac}\delta_{zb} - \delta_{ab}\delta_{zc}\right) S^cs^b_{\alpha^\prime \beta} s^a_{\beta \alpha} = \frac{1}{4}\sum_{\beta,c}\beta s^c_{\beta\alpha}\left(S^c_d s^z_{\alpha^\prime\beta} - S^z_d s^c_{\alpha^\prime\beta}\right)
+\end{aligned}\end{equation}
+which gives
+\begin{equation}\begin{aligned}
+	\text{term 4} = \frac{J^3 n_j |\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{\beta k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\frac{1}{2}S_d^c s^c_{\alpha^\prime\alpha}\ - \beta S_d^z s^c_{\beta\alpha}s^c_{\alpha^\prime\beta}\right)
+\end{aligned}\end{equation}
+
+\subsection{Total renormalization \(\Delta H^{(2)}\)}
+From the formula for the renormalization \(\Delta H^{(2)}\), we write
+\begin{equation}\begin{aligned}
+	\Delta H^{(2)} = \text{term 3} + \text{term 4} - \text{term 1} - \text{term 2}
+\end{aligned}\end{equation}
+From the constraints of URG and particle-hole symmetry, we have the constraint \(\omega + \omega^\prime = H_d^0 + H_d^1\).
+\(H_d^0\) is the diagonal part when the current node is unoccupied and \(H_d^1\) is when its occupied.
+For our case, \(H_d^0 + H_d^1 = \sum \epsilon_q \tau_q = D\), because both the hole and particle states have energy of \(\frac{D}{2}\) (\(\epsilon_q\) and \(\tau\) flip sign together).
+We therefore have \((\omega - D/2) = -(\omega^\prime - D/2)\).
+term 2 and term 4 cancel each other and term 3 becomes equal to term 1.
+The total renormalization at second order is therefore (relabelling \(\omega^\prime\) as \(\omega\))
+\begin{equation}\begin{aligned}
+	\Delta H^{(2)} = \text{term 3} = \frac{1}{2}\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
+\end{aligned}\end{equation}
+which gives
+\begin{equation}\begin{aligned}
+	\Delta J^{(2)} = \frac{1}{2}\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}
+\end{aligned}\end{equation}
+The choice of \(\omega = D\) gives
+\begin{equation}\begin{aligned}
+	\Delta J^{(2)} = \frac{J^2 D  n_j |\delta D|}{D^2 - \frac{1}{4}J^2}
+\end{aligned}\end{equation}
+For \(J \ll D\), we get the one-loop PMS form.
+
 \end{document}

### 2021-11-05 multi-channel-urg.tex
completed third order URG as well, terms dont look all right, time to troubleshoot

@@
-\documentclass{revtex4-2}
-\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref}
+\documentclass[12pt]{revtex4-2}
+\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
+\numberwithin{equation}{section}
 \allowdisplaybreaks
@@
 Each value of the fluctuation scale defines an eigendirection of \(\hat \omega\).
-We have then essentially traded off the complexity in the non-commuatativity of the diagonal and off-diagonal terms for all the directions in the manifold of \(\hat \omega\).
+We have then essentially traded off the complexity in the non-commutation of the diagonal and off-diagonal terms for all the directions in the manifold of \(\hat \omega\).
 
@@
 \begin{align}
-	&T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T \\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \beta } \frac{1}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}c^\dagger_{q\beta} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{ \beta\alpha}\\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} \frac{1}{\omega - \frac{1}{2}D - J S_d^z s_q^z}c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} & \left[\tau = \frac{1}{2}, \epsilon_q = D\right] \\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} \frac{\omega - \frac{1}{2}D + J S_d^z s_q^z}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\left(\omega - \frac{1}{2}D\right) \left(1 - \hat n_{q\beta}\right) +  J S_d^z c_{q\beta} s_q^z c^\dagger_{q\beta}}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} \\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\left(\omega - \frac{1}{2}D\right) \left(1 - \hat n_{q\beta}\right) +  J S_d^z \left(s_q^z + \frac{\beta}{2}\right) \left(1- \hat n_{q\beta}\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} & \left[\left[c_{q\beta}, s_q^z\right] = \frac{\beta}{2} c_{q\beta}\right] \\
-	&= J^2 n_j |\delta D|\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) + J S_d^z \beta}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b & \left[s_q^z = \frac{\beta}{2}\right]  \\
-	&= \frac{J^2 n_j |\delta D|\left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} & \left[\text{term 1}\right]\\
-	&+ \frac{J^3 n_j |\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a S_d^z S_d^b s^a_{\alpha^\prime \beta} s^b_{\beta \alpha} \beta & \left[\text{term 2}\right] \\
+	T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T = J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \beta } \frac{1}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}c^\dagger_{q\beta} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{ \beta\alpha}
 \end{align}
-We will now simplify the terms individually.
-In term 1, only the configurations \(a \neq b\) can lead to a non-trivial impurity spin operator and hence contribute to renormalization.
-For \(a \neq b\), we have \(S_d^a S_d^b = \frac{i}{2} \sum_c \epsilon^{abc}S_d^c \).
-Therefore,
+In the denominator, the state \(q\beta\) is occupied, so we will substitute \(\tau = + \frac{1}{2}\) and \(s_q^z = \beta\).
+We will also substitute \(\epsilon_q = +D\), because the state was initially unoccupied.
+\begin{align}
+	T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} \frac{1}{\omega - \frac{1}{2}D - J \frac{\beta}{2}S_d^z}c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \\
+	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} \frac{\omega - \frac{1}{2}D + J \frac{\beta}{2}S_d^z }{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \\
+	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\omega - \frac{1}{2}D  +  J S_d^z \frac{\beta}{2}}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} \left(1 - \hat n_{q\beta}\right)
+\end{align}
+We can perform the sum over the states being decoupled: \(\sum_q \hat n_{q\beta} = \sum_{\epsilon_q = D - |\delta D|}^D = n_j \).
+\begin{align}
+	T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T &= J^2 n_j \sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \sum_{\beta,a,b}S_d^a s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) + J S_d^z \frac{\beta}{2}}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b
+\end{align}
+We will now simplify the terms individually. The first term is simpler:
 \begin{equation}\begin{aligned}
-\sum_{a,b}S_d^a S_d^b\left(s^a s^b\right)_{\alpha^\prime \alpha} = - \frac{1}{4}\sum_{c,e} S_d^c \left(s^e\right)_{\alpha^\prime \alpha}\sum_{a,b}\epsilon^{abc}\epsilon^{abe} = - \frac{1}{4}\sum_{c,e} S_d^c \left(s^e\right)_{\alpha^\prime \alpha} 2 \delta_{ce} = -\frac{1}{2}\vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
+	\text{term 3} = \frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \sum_{\beta,a,b}S_d^a S_d^b s^a_{\alpha^\prime \beta}s^b_{\beta \alpha}
 \end{aligned}\end{equation}
-Term 1 therefore simplifies to
+The final sum can be performed using the following trick.
+In order to renormalize the Hamiltonian, the two impurity spin operators \(S_d^a\) and \(S_d^b\) have to multiply to produce another spin operator \(S_d^c\) and that will happen only for \(a\neq b\).
+For \(a \neq b\), we have the relation \(S_d^a S_d^b = \frac{i}{2}\sum_c \epsilon^{abc}S_d^c\).
 \begin{equation}\begin{aligned}
-	-\frac{1}{2}\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha} && \left[\text{term 1}\right]\\
+	\sum_{a,b,\beta}S_d^a S_d^b s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} = \sum_{a,b}S_d^a S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} = -\frac{1}{4}\sum_{a,b,c_1,c_2}\epsilon^{abc_1}\epsilon^{abc_2}S_d^{c_1}\left(s^{c_2}\right)_{\alpha^\prime \alpha}
 \end{aligned}\end{equation}
-In term 2, we use the identity:
-\begin{equation}\begin{aligned}
-S^a S^z S^b = \frac{1}{4}\sum_c \left(\delta_{ac}\delta_{zb} - \delta_{ab}\delta_{zc}\right) S^c
-\end{aligned}\end{equation}
+The double \(\epsilon\) can be evaluated easily: \(\sum_{ab}\epsilon^{abc_1}\epsilon^{abc_2} = \sum_b\left(\delta_{c_1 c_2} - \delta_{b c_2}\delta_{b c_1}\right) = 2 \delta_{c_1 c_2}\).
 Substituting this gives
 \begin{equation}\begin{aligned}
-	\sum_{\beta,a,b} S_d^a S_d^z S_d^b s^a_{\alpha^\prime \beta} s^b_{\beta \alpha} \beta &= \frac{1}{4}\sum_{\beta,c}\beta \left(S_d^c s^c_{\alpha^\prime\beta}s^z_{\beta\alpha} - S_d^z s^c_{\alpha^\prime\beta} s^c_{\beta\alpha}\right) \\
-	\implies \text{term 2} &= \frac{J^3|\delta D| n_j}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{\beta k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \beta s^c_{\alpha^\prime\beta}\left(S_d^c s^z_{\beta\alpha} - S_d^z s^c_{\beta\alpha}\right)\\
-			       &= \frac{J^3|\delta D| n_j}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{\beta k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\frac{1}{2}S_d^c s^c_{\alpha^\prime\alpha}\ - \beta S_d^z s^c_{\beta\alpha}s^c_{\alpha^\prime\beta}\right)
+	\label{term1}
+	\text{term 3} &= \frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \sum_{c} \left(-\frac{1}{2}\right)S_d^c s^c_{\alpha^\prime \alpha} \\
+		      &= \left(-\frac{1}{2}\right)\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha}  \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
+\end{aligned}\end{equation}
+The second term takes a bit more work:
+\begin{equation}\begin{aligned}
+	\text{term 4} = \frac{1}{2}\frac{J^3 n_j }{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \sum_{\beta,a,b}\beta S_d^a S_d^z  S_d^bs^a_{\alpha^\prime \beta}s^b_{\beta \alpha}
+\end{aligned}\end{equation}
+Here we will use the identity:
+\begin{equation}\begin{aligned}
+	\label{identity_SSS}
+	S_d^a S_d^z S_d^b = \left(\frac{1}{4}\delta^{az} + \frac{i}{2}\sum_c \epsilon^{azc}S_d^c\right)S_d^b = \left(\frac{1}{4}\delta^{az}S_d^b + \frac{i}{8} \epsilon^{azb}  - \frac{1}{4}\sum_{c_1,c} \epsilon^{azc_1} \epsilon^{c_1 b c} S_d^c\right)\\
+	= \frac{1}{4}\left(\delta^{az}S_d^b - \delta^{ab}S_d^z + \delta^{bz}S_d^a\right) + \frac{i}{8}\epsilon^{azb}
+\end{aligned}\end{equation}
+We will drop the last numerical term because such a term cannot renormalize the Hamiltonian. Substituting this gives
+\begin{equation}\begin{aligned}
+	\label{term2}
+	\text{term 4} &= \frac{J^3 n_j}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\vec{S_d}\cdot\vec{s}_{\alpha^\prime\alpha} -S_d^z \sum_\beta \beta s^a_{\alpha^\prime\beta} s^a_{\beta\alpha} \right)
 \end{aligned}\end{equation}
@@
 \begin{align}
-	&c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c \\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime} c^\dagger_{q\beta} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\beta \alpha} \frac{1}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \beta}\\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{1}{\omega^\prime - \frac{1}{2}D - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[\tau = -\frac{1}{2},\epsilon_q = -D\right] \\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z s_q^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta}\\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) - J S_d^z s_q^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) \hat n_{q\beta} - J S_d^z  c^\dagger_{q\beta}s_q^z c_{q\beta}}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} \\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) \hat n_{q\beta} - J S_d^z \left(s_q^z - \frac{\beta}{2}\right) \hat n_{q\beta}}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} & \left[\left[c^\dagger_{q\beta}, s_q^z\right] = -\frac{\beta}{2} c^\dagger_{q\beta}\right] \\
-							   &= J^2 n_j |\delta D|\sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z \beta}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} & \left[s_q^z = -\frac{1}{2}\beta\right] \\
-							   &= -\frac{J^2\left(\omega^\prime - \frac{1}{2}D\right) n_j |\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^b s^a\right)_{\alpha^\prime \alpha} & \left[\text{term 3}\right] \\
-							   &\quad+ \frac{J^3 n_j |\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a S_d^z S_d^b s^a_{\beta \alpha} s^b_{\alpha^\prime \beta} \beta & \left[\text{term 4}\right]
+	c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c = J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime} c^\dagger_{q\beta} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\beta \alpha} \frac{1}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \beta}
 \end{align}
-term 3 can be made identical to term 1 using the relation: \(s^b s^a = -s^b s^a \text{ for } a \neq b\). With this change, term 3 becomes
+Here the intermediate state is unoccupied, so we put \(\tau = -\frac{1}{2}, s_q^z = -\frac{\beta}{2}\) and since the initial state was occupied, we put \(\epsilon_q = D\).
+\begin{align}
+	c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c &= \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{J^2}{\omega^\prime - \frac{1}{2}D + J \frac{\beta}{2}S_d^z }c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} \\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega^\prime - \frac{1}{2}D\right) - J \frac{\beta}{2}S_d^z }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta}\\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} \hat n_{q\beta} \\
+							   &= J^2 n_j \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z \frac{1}{2}\beta}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta}
+\end{align}
+We again simplify the terms individually, calling them term 1 and term 2.
+Term 1 can be made identical in form to term 1 using the relation: \(s^b s^a = -s^b s^a \text{ for } a \neq b\).
+With this change, term 3 becomes
 \begin{equation}\begin{aligned}
-	\text{term 3} = \frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} \\
-	= \frac{1}{2}\frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
+	\label{term3}
+	\text{term 1} = \frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} \\
+	= \frac{1}{2}\frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
 \end{aligned}\end{equation}
-
-For term 4, we get
+For term 2, we will use eq.~\ref{identity_SSS} to get
 \begin{equation}\begin{aligned}
-	\sum_{\beta,a,b} S_d^a S_d^z S_d^b s^b_{\alpha^\prime \beta} s^a_{\beta \alpha} \beta = \frac{1}{4}\sum_{\beta,a,b,c}\beta\left(\delta_{ac}\delta_{zb} - \delta_{ab}\delta_{zc}\right) S^cs^b_{\alpha^\prime \beta} s^a_{\beta \alpha} = \frac{1}{4}\sum_{\beta,c}\beta s^c_{\beta\alpha}\left(S^c_d s^z_{\alpha^\prime\beta} - S^z_d s^c_{\alpha^\prime\beta}\right)
-\end{aligned}\end{equation}
-which gives
-\begin{equation}\begin{aligned}
-	\text{term 4} = \frac{J^3 n_j |\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{\beta k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\frac{1}{2}S_d^c s^c_{\alpha^\prime\alpha}\ - \beta S_d^z s^c_{\beta\alpha}s^c_{\alpha^\prime\beta}\right)
+	\label{term4}
+	\text{term 2} = \frac{J^3 n_j }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\vec{S_d}\cdot\vec{s}_{\alpha^\prime\alpha} -S_d^z \sum_\beta \beta s^a_{\alpha^\prime\beta} s^a_{\beta\alpha} \right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta H^{(2)} = \text{term 3} + \text{term 4} - \text{term 1} - \text{term 2}
+	\Delta H^{(2)} = \text{term 1} + \text{term 2} - \text{term 3} - \text{term 4}
 \end{aligned}\end{equation}
+These four terms are given by eqs.~\ref{term1}, \ref{term2}, \ref{term3} and \ref{term4}.
 From the constraints of URG and particle-hole symmetry, we have the constraint \(\omega + \omega^\prime = H_d^0 + H_d^1\).
@@
 We therefore have \((\omega - D/2) = -(\omega^\prime - D/2)\).
-term 2 and term 4 cancel each other and term 3 becomes equal to term 1.
-The total renormalization at second order is therefore (relabelling \(\omega^\prime\) as \(\omega\))
+With this relation, we have \(\text{term 2} = \text{term 4}\) and \( \text{term 3} = -\text{term 1}\).
+The total renormalization at second order is therefore
 \begin{equation}\begin{aligned}
-	\Delta H^{(2)} = \text{term 3} = \frac{1}{2}\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
+	\Delta H^{(2)} = -2 \times \text{term 3} = -\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J^{(2)} = \frac{1}{2}\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}
+	\Delta J^{(2)} = -\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}
 \end{aligned}\end{equation}
-The choice of \(\omega = D\) gives
+For \(\omega < D/2\), we get the flow towards the strong-coupling fixed point.
+That is, there is an attractive stable fixed point at \(J^* = 4|\omega - D/2|\) for all bare \(J > 0\).
+We also get a decay towards the local moment fixed point \(J^* = 0\) for \(J < 0\).
+For \(\omega = -D/2\) and \(J \ll D\), we get the one-loop PMS form.
 \begin{equation}\begin{aligned}
-	\Delta J^{(2)} = \frac{J^2 D  n_j |\delta D|}{D^2 - \frac{1}{4}J^2}
+	\Delta J^{(2)} = \frac{J^2 n_j D}{D^2 - \frac{1}{16}J^2} \simeq \frac{J^2 n_j }{D}
 \end{aligned}\end{equation}
-For \(J \ll D\), we get the one-loop PMS form.
+\section{Next-to-leading order renormalization}
+\begin{equation}\begin{aligned}
+	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term} ~-~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term}
+\end{aligned}\end{equation}
+
+\subsection{First term}
+\begin{equation}\begin{aligned}
+	&c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c\\
+	&= \sum_{q, k, k^\prime, k_1,k_2,\atop{\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} \frac{J^2}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{J}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}\\
+	&\quad\times c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha^\prime \beta}
+\end{aligned}\end{equation}
+\(q\) sums over the momenta being decoupled.
+\(k, k^\prime, k_1,k_2\) sum over the momenta not being decoupled.
+\(\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2\) sum over the spin indices.
+\(l_1,l_2\) sum over the channels.
+We substitute \(s_q^z = -\frac{\beta}{2}\) and \(\epsilon_q \tau_{q\beta} = \frac{D}{2}\).
+The term inside the summation becomes
+\begin{equation}\begin{aligned}
+	&J^3 c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} \frac{1}{\omega^\prime - \frac{D}{2} + J \frac{\beta}{2}S_d^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{1}{\omega^\prime - \frac{D}{2} + J \frac{\beta}{2}S_d^z} c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha^\prime \beta}\\
+	=&\frac{J^3 c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha^\prime \beta}}{\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}
+\end{aligned}\end{equation}
+We will start simplifying this equation by summing over \(q\).
+\(c^\dagger_{q\beta}\) and \(c_{q\beta}\) can be easily combined to form \(\hat n_{q\beta}\), because they anti-commute with the other momenta.
+The sum gives \(\sum_q \hat n_{q\beta l_1} = n_j \).
+This gives (without writing the summations explicitly)
+\begin{equation}\begin{aligned}
+	\frac{J^3 n_j  c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) c^\dagger_{k^\prime\alpha^\prime, l_1} S_d^c s^c_{\alpha^\prime \beta}}{\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}
+\end{aligned}\end{equation}
+The next simplification involves identifying how to contract the operators.
+The contractions have to be done so as to reproduce the original \(\vec{S_d}\cdot\vec{s}c^\dagger c\) form so that we can read off the renormalization.
+Currently, there are four distinct electron labels, \(k,k^\prime,k_1,k_2\).
+There are two ways to contract them.
+The first is by choosing \(k_1\alpha_1 = k_2\alpha_2\).
+However, this term vanishes:
+\begin{equation}\begin{aligned}
+	\sum_{k_1\alpha_1,b}S_d^b s^b_{\alpha_1 \alpha_1} c^\dagger_{k_1\alpha_1,l_2}c_{k_1 \alpha_1,l_2} = \sum_{b,k_1\alpha_1}S_d^b s^b_{\alpha_1 \alpha_1}\hat n_{k_1\alpha_1,l_2} &= \sum_{b}S_d^b \left(\sum_{\alpha_1}s^b_{\alpha_1 \alpha_1}\right) \int_{-D + |\delta D|}^0 d\epsilon \rho(\epsilon)\\
+																						      &= \sum_b S_d^b \text{ Trace }(s^b)\int_{-D + |\delta D|}^0 d\epsilon \rho(\epsilon)= 0
+\end{aligned}\end{equation}
+The other way to contract the indices is by selecting \(k\alpha = k^\prime \alpha^\prime\).
+Those two operators can again be brought together without any change of sign because there will be an even number of flips.
+Summing over \(k=k^\prime\) and the channel index \(l_1\) then gives \(\sum_{l_1}\sum_k \left(1 - \hat n_{k\alpha}\right) = \sum_{l_1}\int_{-D + |\delta D|}^ 0 n_j = K n_j N_j\), where \(n_j = \rho |\delta D|\) and \(N_j = \rho D\).
+\(K = \sum_{l_1}\) is the total number of conduction bath channels.
+The entire expression is now
+\begin{equation}\begin{aligned}
+	\label{first_term}
+	\sum_{k_1,k_2,\beta,\alpha, \atop{\alpha^\prime, \alpha_1,\alpha_2,\atop{l_2,a,b,c}}}\frac{J^3 K N_j n_j  S_d^a s^a_{\beta \alpha} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) S_d^c s^c_{\alpha^\prime \beta}}{\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2} \\
+	= \frac{J^3 K N_j n_j }{\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \sum_{\beta,\alpha, \atop{a,b,c}}S_d^a s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b \\
+	\times \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) S_d^c 
+\end{aligned}\end{equation}
+We now need to simplify the final summation.
+\begin{equation}\begin{aligned}
+	\label{final_sum}
+\sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} S_d^a \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b\left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) S_d^c
+\end{aligned}\end{equation}
+The internal product can be evaluated as follows:
+\begin{equation}\begin{aligned}
+	\label{internal_sum}
+	\left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b\left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) = \left(\omega^\prime - \frac{D}{2}\right)^2 S_d^b - \frac{\beta J}{2}\left(\omega^\prime - \frac{D}{2}\right)\left\{S_d^z, S_d^b\right\} \\
+	+ \frac{J^2}{4}S_d^z S_d^b S_d^z
+\end{aligned}\end{equation}
+The anticommutator is \(\left\{S_d^z, S_d^b\right\} = \frac{\delta^{bz}}{4}\).
+The triple operator product is given by eq.~\ref{identity_SSS}: \(S_d^z S_d^b S_d^z = \frac{1}{4}S_d^b\left(2\delta^{bz} - 1\right)\).
+The right-hand side of eq.~\ref{internal_sum} becomes
+\begin{equation}\begin{aligned}
+	\left[\left(\omega^\prime - \frac{D}{2}\right)^2 + \frac{J^2}{16} \left(2\delta^{bz} - 1\right)\right]S_d^b - \frac{\beta J}{8}\delta^{bz}\left(\omega^\prime - \frac{D}{2}\right) \equiv \mathcal{C}_1^b S_d^b + \mathcal{C}_2^b
+\end{aligned}\end{equation}
+Eq.~\ref{final_sum} takes the form
+\begin{equation}\begin{aligned}
+	\sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\left(\mathcal{C}_1^b S_d^a S_d^b S_d^c+ \mathcal{C}_2^b S_d^a S_d^c\right)  
+\end{aligned}\end{equation}
+These spin products can again be evaluated using standard identities:
+\begin{equation}\begin{aligned}
+	S_d^a S_d^c = \frac{i}{2}\sum_{e}\epsilon^{ace}S_d^e, ~ ~ ~ S_d^a S_d^b S_d^c = \frac{1}{4}\left(\delta^{ab}S_d^c - \delta^{ac}S_d^b + \delta^{bc}S_d^a\right) 
+\end{aligned}\end{equation}
+We have dropped constant terms in both equations because such terms cannot renormalize the Hamiltonian. This gives, for eq.~\ref{final_sum},
+\begin{equation}\begin{aligned}
+	\label{Cb1Cb2}
+	\sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\left[\frac{1}{4}\mathcal{C}_1^b \left(\delta^{ab}S_d^c - \delta^{ac}S_d^b + \delta^{bc}S_d^a\right)+ \mathcal{C}_2^b \frac{i}{2}\sum_{e}\epsilon^{ace}S_d^e\right]
+\end{aligned}\end{equation}
+We take the first term.
+Define \(\mathcal{C}^b_1 = \mathcal{C}_{11} + \mathcal{C}_{12}\delta^{bz}\).
+Also note that the indices \(\alpha,\beta\) can be easily summed over: \(\sum_{\alpha\beta}s^a_{\beta\alpha}c^c_{\alpha\beta} = \text{Trace}\left(s^a s^c\right) = \frac{1}{2}\delta^{ac}\).
+The term in product with \(\mathcal{C}^b_1\) becomes
+\begin{equation}\begin{aligned}
+	\label{Cb1}
+	\frac{1}{2}\sum_{a,b}s^b_{\alpha_1 \alpha_2}\frac{1}{4}\left(\mathcal{C}_{11} + \mathcal{C}_{12}\delta^{bz}\right) \left(2\delta^{ab}S_d^a - S_d^b\right) &= -\frac{1}{8}\sum_{b}s^b_{\alpha_1 \alpha_2}\left(\mathcal{C}_{11} + \mathcal{C}_{12}\delta^{bz}\right)S_d^b\\
+																				  &= -\frac{1}{8}\left(\mathcal{C}_{11} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} + \mathcal{C}_{12}s^z_{\alpha_1\alpha_2}S_d^z\right)
+\end{aligned}\end{equation}
+The term in product with \(\mathcal{C}^b_2\) can be written as
+\begin{equation}\begin{aligned}
+	- \frac{i J\left(\omega^\prime - \frac{D}{2}\right)}{16}\sum_{\beta,\alpha, \atop{a,b,c}} \delta^{bz}\beta s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\sum_{e}\epsilon^{ace}S_d^e &= - \frac{i J\left(\omega^\prime - \frac{D}{2}\right)}{16}\sum_{\beta,\alpha, \atop{a,c}} \beta s^a_{\beta \alpha} s^z_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\sum_{e}\epsilon^{ace}S_d^e\\
+																									   &=\frac{-iJ\left(\omega^\prime - \frac{D}{2}\right)}{32}\sum_{\beta,a,c,e} \beta \left(s^c s^a\right)_{\beta \beta} \alpha_1\delta^{\alpha_1 \alpha_2}\epsilon^{ace}S_d^e\\
+\end{aligned}\end{equation}
+Since \(a \neq c\) (\(a=c\) would make \(\epsilon^{ace} = 0\)), we can use \(\left(s^c s^a\right)_{\beta \beta} = \frac{i}{2}\sum_f \epsilon^{caf}s^f_{\beta\beta} = \frac{i\beta}{4}\epsilon^{caz}\).
+Substituting this gives
+\begin{equation}\begin{aligned}
+	\label{Cb2}
+	\frac{J\left(\omega^\prime - \frac{D}{2}\right)}{64}\sum_{a,c,e} \alpha_1\delta^{\alpha_1 \alpha_2}\epsilon^{ace}\epsilon^{caz}S_d^e = \frac{J\left(\omega^\prime - \frac{D}{2}\right)}{32} \alpha_1\delta^{\alpha_1 \alpha_2}S_d^z
+\end{aligned}\end{equation}
+
+Once we note that \(\mathcal{C}_{11} = \left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\) and \(\omega^\prime - D/2 - 2\mathcal{C}_{12}/J = \omega^\prime - D/2 - J/4\) and when we substitute eqs.~\ref{Cb1} and \ref{Cb2} into eq.~\ref{first_term}, we get
+\begin{equation}\begin{aligned}
+	&-\frac{1}{8}\frac{J^3 K N_j n_j }{\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} \\
+	&+ \frac{J^4 K N_j n_j \left( \omega^\prime - D/2 - J/4 \right) }{16\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
+\end{aligned}\end{equation}
+
+\subsection{Second term}
+\begin{equation}\begin{aligned}
+	&T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T\\
+	&= \sum_{q, k, k^\prime, k_1,k_2,\atop{\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}}c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1}  S_d^c s^c_{\alpha^\prime \beta} \frac{J^2}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{J}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}\\
+	&\quad\times c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha}
+\end{aligned}\end{equation}
+We take similar steps as before:
+\begin{inparaenum}
+	\item \(\epsilon_q \tau_{q\beta} = \frac{D}{2}\)
+	\item \(s^z_q = \frac{\beta}{2}\)
+	\item Sum over \(q\) to get \(n_j\)
+	\item Contract \(k\alpha,k^\prime\alpha^\prime\) to get \(K N_j n_j\)
+	\item Compute the internal product to obtain \(\mathcal{C}_1^b S_d^b - \mathcal{C}_2^b\)
+\end{inparaenum}.
+The expression at this point is
+\begin{equation}\begin{aligned}
+	\label{Cb1Cb2_2}
+	\frac{J^3 K N_j n_j }{\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} S_d^c \left(\mathcal{C}_1^b S_d^b - \mathcal{C}_2^b\right) S_d^a
+\end{aligned}\end{equation}
+\(\mathcal{C}^b_1\) is exactly the same as before, the only difference being \(\omega\) replaces \(\omega^\prime\).
+The sign of \(\mathcal{C}^b_2\) has also flipped, because \(\beta \to -\beta\).
+The other difference is that \(S_d^a\) and \(S_d^c\) have switched places.
+Eq.~\ref{Cb1Cb2} is replaced by
+\begin{equation}\begin{aligned}
+	\label{Cb1Cb2_3}
+	\sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\left[\frac{1}{4}\mathcal{C}_1^b \left(\delta^{ab}S_d^c - \delta^{ac}S_d^b + \delta^{bc}S_d^a\right) + \mathcal{C}_2^b \frac{i}{2}\sum_{e}\epsilon^{ace}S_d^e\right]
+\end{aligned}\end{equation}
+Note that even though \(\mathcal{C}^b_2\) came with a minus sign in eq.~\ref{Cb1Cb2_2}, that minus sign has been canceled by a second minus sign that arises from the exchange of \(a \leftrightarrow c\) in \(\epsilon^{cae}\).
+Since eq.~\ref{Cb1Cb2_3} is identical to eq.~\ref{Cb1Cb2}, we can dirctly write down the renormalization in this case:
+\begin{equation}\begin{aligned}
+	&-\frac{1}{8}\frac{J^3 K N_j n_j }{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} \\
+	&+ \frac{J^4 K N_j n_j \left( \omega - D/2 - J/4 \right) }{16\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
+\end{aligned}\end{equation}
 

### 2021-11-05 multi-channel-urg.tex
corrected typos and some factors, introduced a factor of half to correct the probs, now the only problem is the symmetry-breaking term

@@
-\documentclass[12pt]{revtex4-2}
+\documentclass{revtex4-2}
 \usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
@@
 \begin{equation}\begin{aligned}
-	\Delta H_j = \left[c^\dagger T, \eta \right] = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c - T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
+	\Delta H_j = \left\{c^\dagger T, \eta \right\} = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta H^{(2)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c - T^\dagger c \frac{1}{\omega - H_D}c^\dagger T
+	\Delta H^{(2)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c + T^\dagger c \frac{1}{\omega - H_D}c^\dagger T
 \end{aligned}\end{equation}
 \begin{equation}\begin{aligned}
-	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c - T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T
+	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T
 \end{aligned}\end{equation}
@@
 	\label{term1}
-	\text{term 3} &= \frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \sum_{c} \left(-\frac{1}{2}\right)S_d^c s^c_{\alpha^\prime \alpha} \\
-		      &= \left(-\frac{1}{2}\right)\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha}  \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
+	\text{term 3} &= \frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \sum_{c} \left(-\frac{1}{2}\right)S_d^c s^c_{\alpha^\prime \alpha} = \left(-\frac{1}{2}\right)\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha}  \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
 \end{aligned}\end{equation}
@@
 	\label{identity_SSS}
-	S_d^a S_d^z S_d^b = \left(\frac{1}{4}\delta^{az} + \frac{i}{2}\sum_c \epsilon^{azc}S_d^c\right)S_d^b = \left(\frac{1}{4}\delta^{az}S_d^b + \frac{i}{8} \epsilon^{azb}  - \frac{1}{4}\sum_{c_1,c} \epsilon^{azc_1} \epsilon^{c_1 b c} S_d^c\right)\\
-	= \frac{1}{4}\left(\delta^{az}S_d^b - \delta^{ab}S_d^z + \delta^{bz}S_d^a\right) + \frac{i}{8}\epsilon^{azb}
+	S_d^a S_d^z S_d^b = \left(\frac{1}{4}\delta^{az} + \frac{i}{2}\sum_c \epsilon^{azc}S_d^c\right)S_d^b = \left(\frac{1}{4}\delta^{az}S_d^b + \frac{i}{8} \epsilon^{azb}  - \frac{1}{4}\sum_{c_1,c} \epsilon^{azc_1} \epsilon^{c_1 b c} S_d^c\right) = \frac{1}{4}\left(\delta^{az}S_d^b - \delta^{ab}S_d^z + \delta^{bz}S_d^a\right) + \frac{i}{8}\epsilon^{azb}
 \end{aligned}\end{equation}
@@
 	\label{term3}
-	\text{term 1} = \frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} \\
-	= \frac{1}{2}\frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
+	\text{term 1} = \frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} = \frac{1}{2}\frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta H^{(2)} = \text{term 1} + \text{term 2} - \text{term 3} - \text{term 4}
+	\Delta H^{(2)} = \text{term 1} + \text{term 2} + \text{term 3} + \text{term 4}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term} ~-~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term}
+	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term} ~+~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term}
 \end{aligned}\end{equation}
@@
 	&c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c\\
-	&= \sum_{q, k, k^\prime, k_1,k_2,\atop{\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} \frac{J^2}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{J}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}\\
-	&\quad\times c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha^\prime \beta}
+	&= \sum_{q, k, k^\prime, k_1,k_2,\atop{\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} \frac{J^2}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{J}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha^\prime \beta}
 \end{aligned}\end{equation}
@@
 Those two operators can again be brought together without any change of sign because there will be an even number of flips.
-Summing over \(k=k^\prime\) and the channel index \(l_1\) then gives \(\sum_{l_1}\sum_k \left(1 - \hat n_{k\alpha}\right) = \sum_{l_1}\int_{-D + |\delta D|}^ 0 n_j = K n_j N_j\), where \(n_j = \rho |\delta D|\) and \(N_j = \rho D\).
+Summing over \(k=k^\prime\) and the channel index \(l_1\) then gives \(\sum_{l_1}\sum_k \left(1 - \hat n_{k\alpha}\right) = \sum_{l_1}\int_{-D + |\delta D|}^ 0 n_j = \frac{1}{2}K n_j N_j\), where \(n_j = \rho |\delta D|\) and \(N_j = \rho D\).
 \(K = \sum_{l_1}\) is the total number of conduction bath channels.
+The factor of half is inserted to model the probability of transition appropriately; not all values of \(\epsilon_k\) will contribute equally to the renormalization.
 The entire expression is now
@@
 	\label{first_term}
-	\sum_{k_1,k_2,\beta,\alpha, \atop{\alpha^\prime, \alpha_1,\alpha_2,\atop{l_2,a,b,c}}}\frac{J^3 K N_j n_j  S_d^a s^a_{\beta \alpha} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) S_d^c s^c_{\alpha^\prime \beta}}{\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2} \\
-	= \frac{J^3 K N_j n_j }{\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \sum_{\beta,\alpha, \atop{a,b,c}}S_d^a s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b \\
-	\times \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) S_d^c 
+	&\sum_{k_1,k_2,\beta,\alpha, \atop{\alpha^\prime, \alpha_1,\alpha_2,\atop{l_2,a,b,c}}}\frac{J^3 K N_j n_j  S_d^a s^a_{\beta \alpha} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) S_d^c s^c_{\alpha^\prime \beta}}{2\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2} \\
+	&= \frac{J^3 K N_j n_j }{2\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \sum_{\beta,\alpha, \atop{a,b,c}}S_d^a s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) S_d^c
 \end{aligned}\end{equation}
@@
 	\label{internal_sum}
-	\left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b\left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) = \left(\omega^\prime - \frac{D}{2}\right)^2 S_d^b - \frac{\beta J}{2}\left(\omega^\prime - \frac{D}{2}\right)\left\{S_d^z, S_d^b\right\} \\
-	+ \frac{J^2}{4}S_d^z S_d^b S_d^z
+	\left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b\left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) = \left(\omega^\prime - \frac{D}{2}\right)^2 S_d^b - \frac{\beta J}{2}\left(\omega^\prime - \frac{D}{2}\right)\left\{S_d^z, S_d^b\right\} + \frac{J^2}{4}S_d^z S_d^b S_d^z
 \end{aligned}\end{equation}
-The anticommutator is \(\left\{S_d^z, S_d^b\right\} = \frac{\delta^{bz}}{4}\).
+The anticommutator is \(\left\{S_d^z, S_d^b\right\} = \frac{\delta^{bz}}{2}\).
 The triple operator product is given by eq.~\ref{identity_SSS}: \(S_d^z S_d^b S_d^z = \frac{1}{4}S_d^b\left(2\delta^{bz} - 1\right)\).
@@
 \begin{equation}\begin{aligned}
-	\left[\left(\omega^\prime - \frac{D}{2}\right)^2 + \frac{J^2}{16} \left(2\delta^{bz} - 1\right)\right]S_d^b - \frac{\beta J}{8}\delta^{bz}\left(\omega^\prime - \frac{D}{2}\right) \equiv \mathcal{C}_1^b S_d^b + \mathcal{C}_2^b
+	\left[\left(\omega^\prime - \frac{D}{2}\right)^2 + \frac{J^2}{16} \left(2\delta^{bz} - 1\right)\right]S_d^b - \frac{\beta J}{4}\delta^{bz}\left(\omega^\prime - \frac{D}{2}\right) \equiv \mathcal{C}_1^b S_d^b + \mathcal{C}_2^b
 \end{aligned}\end{equation}
@@
 	\label{Cb1}
-	\frac{1}{2}\sum_{a,b}s^b_{\alpha_1 \alpha_2}\frac{1}{4}\left(\mathcal{C}_{11} + \mathcal{C}_{12}\delta^{bz}\right) \left(2\delta^{ab}S_d^a - S_d^b\right) &= -\frac{1}{8}\sum_{b}s^b_{\alpha_1 \alpha_2}\left(\mathcal{C}_{11} + \mathcal{C}_{12}\delta^{bz}\right)S_d^b\\
-																				  &= -\frac{1}{8}\left(\mathcal{C}_{11} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} + \mathcal{C}_{12}s^z_{\alpha_1\alpha_2}S_d^z\right)
+	\frac{1}{2}\sum_{a,b}s^b_{\alpha_1 \alpha_2}\frac{1}{4}\left(\mathcal{C}_{11} + \mathcal{C}_{12}\delta^{bz}\right) \left(2\delta^{ab}S_d^a - S_d^b\right) &= -\frac{1}{8}\sum_{b}s^b_{\alpha_1 \alpha_2}\left(\mathcal{C}_{11} + \mathcal{C}_{12}\delta^{bz}\right)S_d^b = -\frac{1}{8}\left(\mathcal{C}_{11} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} + \mathcal{C}_{12}s^z_{\alpha_1\alpha_2}S_d^z\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	- \frac{i J\left(\omega^\prime - \frac{D}{2}\right)}{16}\sum_{\beta,\alpha, \atop{a,b,c}} \delta^{bz}\beta s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\sum_{e}\epsilon^{ace}S_d^e &= - \frac{i J\left(\omega^\prime - \frac{D}{2}\right)}{16}\sum_{\beta,\alpha, \atop{a,c}} \beta s^a_{\beta \alpha} s^z_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\sum_{e}\epsilon^{ace}S_d^e\\
-																									   &=\frac{-iJ\left(\omega^\prime - \frac{D}{2}\right)}{32}\sum_{\beta,a,c,e} \beta \left(s^c s^a\right)_{\beta \beta} \alpha_1\delta^{\alpha_1 \alpha_2}\epsilon^{ace}S_d^e\\
+	- \frac{i J\left(\omega^\prime - \frac{D}{2}\right)}{8}\sum_{\beta,\alpha, \atop{a,b,c}} \delta^{bz}\beta s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\sum_{e}\epsilon^{ace}S_d^e &= - \frac{i J\left(\omega^\prime - \frac{D}{2}\right)}{8}\sum_{\beta,\alpha, \atop{a,c}} \beta s^a_{\beta \alpha} s^z_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\sum_{e}\epsilon^{ace}S_d^e\\
+																									   &=\frac{-iJ\left(\omega^\prime - \frac{D}{2}\right)}{8}\sum_{\beta,a,c,e} \beta \left(s^c s^a\right)_{\beta \beta} s^z_{\alpha_1 \alpha_2}\epsilon^{ace}S_d^e\\
 \end{aligned}\end{equation}
@@
 	\label{Cb2}
-	\frac{J\left(\omega^\prime - \frac{D}{2}\right)}{64}\sum_{a,c,e} \alpha_1\delta^{\alpha_1 \alpha_2}\epsilon^{ace}\epsilon^{caz}S_d^e = \frac{J\left(\omega^\prime - \frac{D}{2}\right)}{32} \alpha_1\delta^{\alpha_1 \alpha_2}S_d^z
+	\frac{J\left(\omega^\prime - \frac{D}{2}\right)}{32}\sum_{a,c,e} s^z_{\alpha_1 \alpha_2}\epsilon^{ace}\epsilon^{caz}S_d^e = \frac{J\left(\omega^\prime - \frac{D}{2}\right)}{16} s^z_{\alpha_1 \alpha_2}S_d^z
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	&-\frac{1}{8}\frac{J^3 K N_j n_j }{\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} \\
-	&+ \frac{J^4 K N_j n_j \left( \omega^\prime - D/2 - J/4 \right) }{16\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
+	\label{third_term_1}
+	&-\frac{1}{16}\frac{J^3 K N_j n_j }{\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} + \frac{J^4 K N_j n_j \left( \omega^\prime - D/2 - J/4 \right) }{32\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
 \end{aligned}\end{equation}
@@
 	&T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T\\
-	&= \sum_{q, k, k^\prime, k_1,k_2,\atop{\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}}c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1}  S_d^c s^c_{\alpha^\prime \beta} \frac{J^2}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{J}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}\\
-	&\quad\times c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha}
+	&= \sum_{q, k, k^\prime, k_1,k_2,\atop{\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}}c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1}  S_d^c s^c_{\alpha^\prime \beta} \frac{J^2}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{J}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha}
 \end{aligned}\end{equation}
@@
 	\label{Cb1Cb2_2}
-	\frac{J^3 K N_j n_j }{\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} S_d^c \left(\mathcal{C}_1^b S_d^b - \mathcal{C}_2^b\right) S_d^a
+	\frac{J^3 K N_j n_j }{2\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} S_d^c \left(\mathcal{C}_1^b S_d^b - \mathcal{C}_2^b\right) S_d^a
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	&-\frac{1}{8}\frac{J^3 K N_j n_j }{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} \\
-	&+ \frac{J^4 K N_j n_j \left( \omega - D/2 - J/4 \right) }{16\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
+	\label{third_term_2}
+	-\frac{1}{16}\frac{J^3 K N_j n_j }{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} + \frac{J^4 K N_j n_j \left( \omega - D/2 - J/4 \right) }{32\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
+\end{aligned}\end{equation}
+
+\subsection{Total renormalization \(\Delta H^{(3)}\)}
+We will again use the relation \(\omega - D/2 = -(\omega^\prime - D/2)\). The total renormalization at this order is obtained by adding eqs.~\ref{third_term_1} and \ref{third_term_2}.
+\begin{equation}\begin{aligned}
+	\Delta H^{(3)} = -\frac{J^3 K N_j n_j / 8}{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} - \frac{J^5 K N_j n_j / 64}{\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
 \end{aligned}\end{equation}

### 2021-11-05 multi-channel-urg.tex
wrote down final RG equation in symmetric form by requiring the asymmetric terms to vanish

@@
 \begin{equation}\begin{aligned}
-	\Delta H_j = \left\{c^\dagger T, \eta \right\} = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
+	\Delta H_j = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c - T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta H^{(2)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c}_\text{first term}~ -~ \underbrace{T^\dagger c \frac{1}{\omega - H_D}c^\dagger T}_\text{second term}
+	\Delta H^{(2)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c}_\text{first term}~+~\underbrace{T^\dagger c \frac{1}{\omega - H_D}c^\dagger T}_\text{second term}
 \end{aligned}\end{equation}
@@
 \end{align}
-We will now simplify the terms individually. The first term is simpler:
+We will now simplify the terms individually. The first term, labelled term 3, is simpler:
 \begin{equation}\begin{aligned}
+	\label{term3_def}
 	\text{term 3} = \frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \sum_{\beta,a,b}S_d^a S_d^b s^a_{\alpha^\prime \beta}s^b_{\beta \alpha}
@@
 	\label{identity_SSS}
-	S_d^a S_d^z S_d^b = \left(\frac{1}{4}\delta^{az} + \frac{i}{2}\sum_c \epsilon^{azc}S_d^c\right)S_d^b = \left(\frac{1}{4}\delta^{az}S_d^b + \frac{i}{8} \epsilon^{azb}  - \frac{1}{4}\sum_{c_1,c} \epsilon^{azc_1} \epsilon^{c_1 b c} S_d^c\right) = \frac{1}{4}\left(\delta^{az}S_d^b - \delta^{ab}S_d^z + \delta^{bz}S_d^a\right) + \frac{i}{8}\epsilon^{azb}
+	S_d^a S_d^z S_d^b = \left(\frac{1}{4}\delta^{az} + \frac{i}{2}\sum_c \epsilon^{azc}S_d^c\right)S_d^b = \left(\frac{1}{4}\delta^{az}S_d^b + \frac{i}{8} \epsilon^{azb}  - \frac{1}{4}\sum_{c_1,c} \epsilon^{azc_1} \epsilon^{c_1 b c} S_d^c\right) = \frac{1}{4}\left(\delta^{az}S_d^b - \delta^{ab}S_d^z + \delta^{bz}S_d^a\right)
 \end{aligned}\end{equation}
-We will drop the last numerical term because such a term cannot renormalize the Hamiltonian. Substituting this gives
+We have dropped a numerical term because such a term cannot renormalize the Hamiltonian. Substituting this gives
 \begin{equation}\begin{aligned}
@@
 \begin{align}
-	c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c &= \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{J^2}{\omega^\prime - \frac{1}{2}D + J \frac{\beta}{2}S_d^z }c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} \\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega^\prime - \frac{1}{2}D\right) - J \frac{\beta}{2}S_d^z }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta}\\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} \hat n_{q\beta} \\
-							   &= J^2 n_j \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z \frac{1}{2}\beta}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta}
+	c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c &= \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{J^2}{\omega^\prime - \frac{1}{2}D + J \frac{\beta}{2}S_d^z }c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} \\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{\left(\omega^\prime - \frac{1}{2}D\right) - J \frac{\beta}{2}S_d^z }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta}\\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
+							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^a s^a_{\alpha^\prime \beta} \hat n_{q\beta} \\
+							   &= J^2 n_j \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^b \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z \frac{1}{2}\beta}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^a
 \end{align}
 We again simplify the terms individually, calling them term 1 and term 2. 
-Term 1 can be made identical in form to term 1 using the relation: \(s^b s^a = -s^b s^a \text{ for } a \neq b\).
-With this change, term 3 becomes
+\begin{equation}\begin{aligned}
+	\text{term 1} = \frac{-\left(\omega^\prime - \frac{1}{2}D\right)J^2 n_j} {\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^b S_d^a
+\end{aligned}\end{equation}
+Since this term will renormalize only for \(a \neq b\), we can use \(S_d^b S_d^a = -S_d^a S_d^b\). This gives
+\begin{equation}\begin{aligned}
+	\text{term 1} = \frac{\left(\omega^\prime - \frac{1}{2}D\right)J^2 n_j} {\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^a S_d^b
+\end{aligned}\end{equation}
+This is identical to term 3 (eq.~\ref{term3_def}) except for the change \(\omega^\prime \to \omega\). Copying the result from term 3, we get
 \begin{equation}\begin{aligned}
 	\label{term3}
-	\text{term 1} = \frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} = \frac{1}{2}\frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
+	\text{term 1} = -\frac{1}{2}\frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
 \end{aligned}\end{equation}
-For term 2, we will use eq.~\ref{identity_SSS} to get
+The other term is
+\begin{equation}\begin{aligned}
+	\text{term 2} = \frac{1}{2}\frac{J^3 n_j}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{\beta k k^\prime \alpha \alpha^\prime a b} \beta c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^b S_d^z S_d^a
+\end{aligned}\end{equation}
+From eq.~\ref{identity_SSS}, we know that \(S_d^b S_d^z S_d^a =  S_d^a S_d^z S_d^b\), which means this term is again identical to its counterpart, term 4.
 \begin{equation}\begin{aligned}
 	\label{term4}
-	\text{term 2} = \frac{J^3 n_j }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\vec{S_d}\cdot\vec{s}_{\alpha^\prime\alpha} -S_d^z \sum_\beta \beta s^a_{\alpha^\prime\beta} s^a_{\beta\alpha} \right)
+	\text{term 2} = \frac{J^3 n_j }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\vec{S_d}\cdot\vec{s}_{\alpha^\prime\alpha} -S_d^z \sum_{a \beta} \beta s^a_{\alpha^\prime\beta} s^a_{\beta\alpha} \right)
 \end{aligned}\end{equation}
@@
 These four terms are given by eqs.~\ref{term1}, \ref{term2}, \ref{term3} and \ref{term4}.
-From the constraints of URG and particle-hole symmetry, we have the constraint \(\omega + \omega^\prime = H_d^0 + H_d^1\).
-\(H_d^0\) is the diagonal part when the current node is unoccupied and \(H_d^1\) is when its occupied.
-For our case, \(H_d^0 + H_d^1 = \sum \epsilon_q \tau_q = D\), because both the hole and particle states have energy of \(\frac{D}{2}\) (\(\epsilon_q\) and \(\tau\) flip sign together).
-We therefore have \((\omega - D/2) = -(\omega^\prime - D/2)\).
-With this relation, we have \(\text{term 2} = \text{term 4}\) and \( \text{term 3} = -\text{term 1}\).
+Since the Hamiltonian has particle-hole and \(\mathrm{SU}(2)\) symmetry, we will impose these symmetries by choosing the relation between \(\omega\) and \(\omega^\prime\) such that \(\text{term 2} = \text{term 4}\) and \( \text{term 3} = -\text{term 1}\).
 The total renormalization at second order is therefore
@@
 \begin{equation}\begin{aligned}
-	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term} ~+~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term}
+	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term} ~-~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term}
 \end{aligned}\end{equation}
@@
 	\item Sum over \(q\) to get \(n_j\)
-	\item Contract \(k\alpha,k^\prime\alpha^\prime\) to get \(K N_j n_j\)
+	\item Contract \(k\alpha,k^\prime\alpha^\prime\) to get \(K N_j n_j / 2\)
 	\item Compute the internal product to obtain \(\mathcal{C}_1^b S_d^b - \mathcal{C}_2^b\)
@@
 \subsection{Total renormalization \(\Delta H^{(3)}\)}
-We will again use the relation \(\omega - D/2 = -(\omega^\prime - D/2)\). The total renormalization at this order is obtained by adding eqs.~\ref{third_term_1} and \ref{third_term_2}.
+Similar to the one-loop case, we will choose the require \(\omega\) and \(\omega^\prime\) to be related such that the  RG equations are \(\mathrm{Su}(2)\) symmetric; that is, we will require the terms that renormalize only \(S_d^z s^z\) vanish.
+The total renormalization at this order is obtained by adding eqs.~\ref{third_term_1} and \ref{third_term_2}.
 \begin{equation}\begin{aligned}
-	\Delta H^{(3)} = -\frac{J^3 K N_j n_j / 8}{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} - \frac{J^5 K N_j n_j / 64}{\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
+	\Delta H^{(3)} = -\frac{J^3 K N_j n_j / 8}{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2}
+\end{aligned}\end{equation}
+Combining with \(\Delta H^{(2)}\), we get
+\begin{equation}\begin{aligned}
+	\Delta J = \frac{J^2 n_j \left[2 \left(D - 2\omega\right) - \frac{1}{4}J K N_j\right]}{\left(D - 2\omega\right)^2 - \frac{1}{4}J^2}
 \end{aligned}\end{equation}

### 2021-11-07 multi-channel-urg.tex
pms limit

@@
 \documentclass{revtex4-2}
-\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
+\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist,caption}
 \numberwithin{equation}{section}
@@
 \begin{equation}\begin{aligned}
-	\Delta J = \frac{J^2 n_j \left[2 \left(D - 2\omega\right) - \frac{1}{4}J K N_j\right]}{\left(D - 2\omega\right)^2 - \frac{1}{4}J^2}
+	\Delta J = \frac{J^2 n_j \left[2 \left(D - 2\omega\right) - \frac{1}{2}J K N_j\right]}{\left(D - 2\omega\right)^2 - \frac{1}{4}J^2}
 \end{aligned}\end{equation}
+We choose \(\omega = -D/2\) to get a clearer idea of what the equations say.
+We also set \(N_j = \rho D\) and \(n_j = \rho |\delta D|\).
+Quantities with zero in the subscript will denote their values in the bare Hamiltonian.
+Using \(\delta D = -|\delta D|\), we can write the continuum form of the equation:
+\begin{equation}\begin{aligned}
+	\frac{\:\mathrm{d}J}{\:\mathrm{d}t} = \frac{J^2 \rho D^2 \left(1 - \frac{1}{8}JK\rho\right)}{D^2 - \frac{1}{16}J^2}
+\end{aligned}\end{equation}
+where \(dt = \frac{dD}{D}\).
+\\\\
+\begin{minipage}{0.45\textwidth}
+For \(D \gg J\), we can ignore the \(J\) in the denominator, and the equation reduces to the one-loop poor man's scaling form
+\begin{equation}\begin{aligned}
+	\frac{\:\mathrm{d}J}{\:\mathrm{d}t} \simeq \frac{J^2 \rho D^2 \left(1 - \frac{1}{8}JK\rho\right)}{D^2} = J^2 \rho \left(1 - \frac{1}{8}JK\rho\right)
+\end{aligned}\end{equation}
+This equation has a stable fixed point at \(J^* = \frac{8}{\rho K}\).
+\end{minipage}
+\hfill
+\begin{minipage}{0.45\textwidth}
+	\includegraphics[width=\textwidth]{rg_flow_pms.pdf}
+	\captionof{figure}{Attractive finite \(J\) fixed point of poor man scaling RG equation}
+\end{minipage}
+
+\(J_1^*,J_2^*\) are two critical points of the equation where either the numerator or the denominator changes sign: \(J_1^* = \frac{32 D_0}{K}, J_2^* = 4D\).
+In the thermodynamic limit, \(J_1^* \gg J\), so the numerator is always positive, and the flow of \(J\) is determined by the denominator.
+For \(J_0 < J_2^*\), \(J\) is relevant and flows up towards \(J_2^*\).
+On the other hand, if \(J_0 > J_2^*\), then we have an irrelevant coupling which again flows down towards \(J_2^*\)
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{./rg_flow.pdf}
+	\caption{Attractive RG flows towards the stable intermediate coupling fixed point at \(J_1^*\).}
+\end{figure}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{./K=2,rel_and_irr.pdf}
+	\caption{Attractive RG flows towards the stable intermediate coupling fixed point at \(J_1^*\).}
+\end{figure}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.4\textwidth]{./Jfp_vs_D.pdf}
+	\caption{Variation of the fixed point value \(J^*\) against increasing bandwidth \(D_0\). The single-channel curve (red) keeps rising while the two-channel curve (blue) saturates to a finite value.}
+\end{figure}
 

### 2021-11-08 multi-channel-urg.tex
obtained pms form, determined two phases for the full RG equation, showed that the critical rho vanishes and showed that J1/D vanishes, all this shows that in the neighborhood of J1 and for large D0, equation always reduces to PMS

--- 2021-11-05 multi-channel-urg.tex
@@
 \begin{equation}\begin{aligned}
-	\Delta J = \frac{J^2 n_j \left[2 \left(D - 2\omega\right) - \frac{1}{4}J K N_j\right]}{\left(D - 2\omega\right)^2 - \frac{1}{4}J^2}
+	\Delta J = \frac{J^2 n_j \left[2 \left(D - 2\omega\right) - \frac{1}{2}J K N_j\right]}{\left(D - 2\omega\right)^2 - \frac{1}{4}J^2}
 \end{aligned}\end{equation}
+We choose \(\omega = -D/2\) to get a clearer idea of what the equations say.
+We also set \(N_j = \rho D\) and \(n_j = \rho |\delta D|\).
+Quantities with zero in the subscript will denote their values in the bare Hamiltonian.
+Using \(\delta D = -|\delta D|\), we can write the continuum form of the equation:
+\begin{equation}\begin{aligned}
+	\frac{\:\mathrm{d}J}{\:\mathrm{d}t} = \frac{J^2 \rho D^2 \left(1 - \frac{1}{8}JK\rho\right)}{D^2 - \frac{1}{16}J^2}
+\end{aligned}\end{equation}
+where \(dt = \frac{dD}{D}\).
+
+For \(D \gg J\), we can ignore the \(J\) in the denominator, and the equation reduces to the one-loop poor man's scaling form
+\begin{equation}\begin{aligned}
+	\label{pms_mchannel}
+	\frac{\:\mathrm{d}J}{\:\mathrm{d}t} \simeq \frac{J^2 \rho D^2 \left(1 - \frac{1}{8}JK\rho\right)}{D^2} = J^2 \rho \left(1 - \frac{1}{8}JK\rho\right)
+\end{aligned}\end{equation}
+This equation has a stable fixed point at \(J^* = \frac{8}{\rho K}\).
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.4\textwidth]{rg_flow_pms.pdf}
+	\caption{Attractive finite \(J\) fixed point of poor man scaling RG equation}
+\end{figure}
+For \(D\) not so large, the denominator also comes into play, and we get the possibility of two fixed points, one from the numerator and the other from the numerator.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.7\textwidth]{./rg_flow.pdf}
+	\caption{}
+	\label{rg_flow_general}
+\end{figure}
+
+The numerator fixed point is given by
+\begin{equation}\begin{aligned}
+	J_1^* = \frac{8}{K \rho}
+\end{aligned}\end{equation}
+while the denominator fixed point is defined by the condition
+\begin{equation}\begin{aligned}
+	D^* = \frac{J_2^*}{4}
+\end{aligned}\end{equation}
+For a given \(K\), the position of \(J_1^*\) will be governed by \(\rho\).
+In general, for each bare bandwidth \(D_0\), there exists a minimal \(\rho\), $\rho_\text{min}(D_0)$, above which the the lower fixed point is the one from the numerator.
+That is, for \(\rho > \rho_\text{min}\), if we start scaling from small \(J_0\), it grows until it hits \(J_1^*\) which acts as the attractive fixed point, and \(J_2^*\) lies at a higher value and acts as the repulsive fixed point.
+For \(\rho < \rho_\text{min}\), \(J\) will grow and hit \(J_2^*\) instead, and \(J_1^* > J_2^*\) now becomes the repulsive fixed point.
+\begin{equation}\begin{aligned}
+	\rho_\text{min} = \text{minimum }\left\{\rho, \text{ such that } \frac{8}{K \rho} < 4 D^*(\rho)\right\}
+\end{aligned}\end{equation}
+This behaviour is shown schematically in fig.~\ref{rg_flow_general}. 
+In fig.~\ref{rhomin_vs_D}, we plot \(\rho_\text{min}\) against the bare bandwidth.
+For large \(D_0\), it essentially shrinks to zero, and the numerator becomes the first fixed point for essentially all \(\rho\).
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.7\textwidth]{./rhomin_D.pdf}
+	\caption{Red curve shows variation of \(\rho_\text{min}\) against \(D_0\).
+It vanishes at large \(D_0\).
+Blue curve shows variation of the ratio \(J_1^* / D_0\) with \(D_0\).
+That shrinks as well, showing that the fixed point \(J_1^*\) remains finite in the thermodynamic limit, and the distance between \(J_1^*\) and \(J_2^*\) keeps growing.}
+	\label{rhomin_vs_D}
+\end{figure}
+
+If we assume we are at a sufficiently large \(D_0\) and \(\rho > \rho_\text{min}\), the lower fixed point is \(J_1^*\).
+As shown in fig.~\ref{rhomin_vs_D}, we have \(J_1^* \ll D_0\).
+If we start with \(J_0\) in the neighborhood of \(J_1^*\), we can use \(J_1^* \ll D_0\) to ignore \(J\) in the denominator and the RG equation reduces to the poor man's scaling form eq.~\ref{pms_mchannel}.
+The denominator fixed point has effectively moved off to infinite.
+
+\textbf{\textit{The part of the problem that I have not yet figured out is the following: How do we argue for the same when \(J_0\) is not in the neighborhood of \(J_1^*\)?
+That is, if \(J_0\) is sufficiently large so that we cannot simpify the denominator.
+It is true that in order to compete with a thermodynamically large \(D_0\), the bare \(J_0\) will have to be extremely large, and it's possible that this does not even fall in the class of models we are studying.}}
 

### 2021-11-08 multi-channel-urg.tex
added one more argument for why the large J comparable to D situation is unreasonable

@@
 
-\textbf{\textit{The part of the problem that I have not yet figured out is the following: How do we argue for the same when \(J_0\) is not in the neighborhood of \(J_1^*\)?
+[\textit{The part of the problem that is not yet competely clear is the following: How do we argue for the same when \(J_0\) is not in the neighborhood of \(J_1^*\)?
 That is, if \(J_0\) is sufficiently large so that we cannot simpify the denominator.
-It is true that in order to compete with a thermodynamically large \(D_0\), the bare \(J_0\) will have to be extremely large, and it's possible that this does not even fall in the class of models we are studying.}}
+It is true that in order to compete with a thermodynamically large \(D_0\), the bare \(J_0\) will have to be extremely large, and it's possible that this does not even fall in the class of models we are studying.
+Also, if the Hamiltonian is to be extensive, \(J_0\) must scale as \(1/N\), because the conduction bath spin has two momentum space sums in product and each sum scales as \(N\).
+\(N\) is the number of particles.
+Hence, taking the limit of \(N \to \infty\) would mean \(J\) becoming smaller as compared to larger, so very large \(J_0\) seem unreasonable.}]
 

### 2021-11-15 multi-channel-urg.tex
inserted missing minus sign in continuum equation
typos in forms of URG delta H
obtained k-space effective Hamiltonian

--- 2021-11-08 multi-channel-urg.tex
@@
-\documentclass{revtex4-2}
+\documentclass[10pt]{revtex4-2}
 \usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
@@
 \allowdisplaybreaks
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{ebgaramond}
 \begin{document}
@@
 \maketitle
-\section{Introduction}
+\section{Derivation of URG equations for the multi-channel Kondo model}
+
+\subsection{Introduction}
 The multi-channel Kondo model is described by the Hamiltonian
@@
 \begin{equation}\begin{aligned}
-	\Delta H_j = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c - T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	c^\dagger T = J \sum_{k < \Lambda_j, \alpha}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, &&&H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
+	\Delta H_j = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right), && c^\dagger T = J \sum_{k < \Lambda_j, \alpha}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, &H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-
-\section{Leading order renormalization}
-\begin{equation}\begin{aligned}
-	\Delta H^{(2)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c}_\text{first term}~+~\underbrace{T^\dagger c \frac{1}{\omega - H_D}c^\dagger T}_\text{second term}
-\end{aligned}\end{equation}
-\subsection{Second term}
-\begin{align}
-	T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T = J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \beta } \frac{1}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}c^\dagger_{q\beta} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{ \beta\alpha}
-\end{align}
-In the denominator, the state \(q\beta\) is occupied, so we will substitute \(\tau = + \frac{1}{2}\) and \(s_q^z = \beta\).
-We will also substitute \(\epsilon_q = +D\), because the state was initially unoccupied.
-\begin{align}
-	T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} \frac{1}{\omega - \frac{1}{2}D - J \frac{\beta}{2}S_d^z}c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} \frac{\omega - \frac{1}{2}D + J \frac{\beta}{2}S_d^z }{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \\
-	&= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime,a,b} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} S_d^a s^a_{\alpha^\prime \beta} \frac{\omega - \frac{1}{2}D  +  J S_d^z \frac{\beta}{2}}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\beta \alpha} \left(1 - \hat n_{q\beta}\right)
-\end{align}
-We can perform the sum over the states being decoupled: \(\sum_q \hat n_{q\beta} = \sum_{\epsilon_q = D - |\delta D|}^D = n_j \).
-\begin{align}
-	T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T &= J^2 n_j \sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \sum_{\beta,a,b}S_d^a s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} \frac{\left(\omega - \frac{1}{2}D\right) + J S_d^z \frac{\beta}{2}}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b
-\end{align}
-We will now simplify the terms individually. The first term, labelled term 3, is simpler:
-\begin{equation}\begin{aligned}
-	\label{term3_def}
-	\text{term 3} = \frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \sum_{\beta,a,b}S_d^a S_d^b s^a_{\alpha^\prime \beta}s^b_{\beta \alpha}
-\end{aligned}\end{equation}
-The final sum can be performed using the following trick.
-In order to renormalize the Hamiltonian, the two impurity spin operators \(S_d^a\) and \(S_d^b\) have to multiply to produce another spin operator \(S_d^c\) and that will happen only for \(a\neq b\).
-For \(a \neq b\), we have the relation \(S_d^a S_d^b = \frac{i}{2}\sum_c \epsilon^{abc}S_d^c\).
-\begin{equation}\begin{aligned}
-	\sum_{a,b,\beta}S_d^a S_d^b s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} = \sum_{a,b}S_d^a S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} = -\frac{1}{4}\sum_{a,b,c_1,c_2}\epsilon^{abc_1}\epsilon^{abc_2}S_d^{c_1}\left(s^{c_2}\right)_{\alpha^\prime \alpha}
-\end{aligned}\end{equation}
-The double \(\epsilon\) can be evaluated easily: \(\sum_{ab}\epsilon^{abc_1}\epsilon^{abc_2} = \sum_b\left(\delta_{c_1 c_2} - \delta_{b c_2}\delta_{b c_1}\right) = 2 \delta_{c_1 c_2}\).
-Substituting this gives
-\begin{equation}\begin{aligned}
-	\label{term1}
-	\text{term 3} &= \frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \sum_{c} \left(-\frac{1}{2}\right)S_d^c s^c_{\alpha^\prime \alpha} = \left(-\frac{1}{2}\right)\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha}  \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
-\end{aligned}\end{equation}
-The second term takes a bit more work:
-\begin{equation}\begin{aligned}
-	\text{term 4} = \frac{1}{2}\frac{J^3 n_j }{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \sum_{\beta,a,b}\beta S_d^a S_d^z  S_d^bs^a_{\alpha^\prime \beta}s^b_{\beta \alpha}
-\end{aligned}\end{equation}
-Here we will use the identity:
+We will use the identity
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-We have dropped a numerical term because such a term cannot renormalize the Hamiltonian. Substituting this gives
+
+\subsection{Leading order renormalization}
 \begin{equation}\begin{aligned}
-	\label{term2}
-	\text{term 4} &= \frac{J^3 n_j}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\vec{S_d}\cdot\vec{s}_{\alpha^\prime\alpha} -S_d^z \sum_\beta \beta s^a_{\alpha^\prime\beta} s^a_{\beta\alpha} \right)
+	\Delta H^{(2)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c}_\text{first term}~+~\underbrace{T^\dagger c \frac{1}{\omega - H_D}c^\dagger T}_\text{second term}
+\end{aligned}\end{equation}
+This renormalization is identical to that in the single channel. There is no additional physics due to the presence of multiple channels at this order. It is shown in appendix \ref{1KondoURG}.
+
+\subsection{Next-to-leading order renormalization}
+\begin{equation}\begin{aligned}
+	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term} ~+~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term}
+\end{aligned}\end{equation}
+A general term of this summation has three sets of spin operators coming from \(c^\dagger T, H_X\) and \(T^\dagger c\).
+If we had expressed the spin operators in terms of \(S^z, S^\pm\), most of the terms would have atleast one \(S^+\) or \(S^-\), and by the same argument as in the single-channel case, the denominator will have anti-parallel spins and the Ising term will be negative, leading to the form: \(\omega - D/2 - \epsilon_k/2 + J/4\).
+\(\epsilon_k\) is the energy of the other electron that will be summed over.
+The only term that does not have even one \(S^\pm\) is the one with three \(S^z\).
+We can show that this term will also have the same denominator.
+An instance of this term (in shorthand) is
+\begin{equation}\begin{aligned}
+	S_d^z c^\dagger_{q \uparrow} \frac{1}{\omega - D/2 -\epsilon_k/2 + J/2 S_d^z} S_d^z \frac{1}{\omega - D/2 -\epsilon_k/2 + J/2 S_d^z} S_d^z c_{q \uparrow}\\
+\end{aligned}\end{equation}
+This can be split into up and down configurations of the impurity spin using the decomposition \(S_d^z = \frac{1}{2}\left(\frac{1}{2} + S_d^z\right) - \frac{1}{2}\left(\frac{1}{2} - S_d^z \right) \).
+These configurations will have different quantum fluctuation scales \(\omega, \omega^\prime\):
+\begin{equation}\begin{aligned}
+	\frac{1}{2}S_d^z c^\dagger_{q \uparrow}\left[\frac{\left(\frac{1}{2} + S_d^z\right)}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2} - \frac{\left(\frac{1}{2} - S_d^z\right)}{\left(\omega^\prime - D/2 -\epsilon_k/2 - J/4\right)^2}\right]S_d^z c_{q \uparrow}
+\end{aligned}\end{equation}
+If we now use poor man's scaling values to relate the two \(\omega\)s, we get \(\omega^\prime - \omega = J/2\).
+Substituting this will make both the denominators identical: \(\omega - D/2 -\epsilon_k/2 + J/4\).
+This means that the denominator for all non-zero terms that renormalize the Hamiltonian is \(\omega - D/2 - \epsilon_k/2 + J/4\).
+
+\subsubsection{Calculation of first term}
+\begin{equation}\begin{aligned}
+	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = J^3\sum_{q, k, k_1,k_2,\atop{\beta, \alpha, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} \frac{c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} c^\dagger_{k\alpha, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha \beta}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2}
+\end{aligned}\end{equation}
+\(q\) sums over the momenta being decoupled.
+\(k, k_1,k_2\) sum over the momenta not being decoupled.
+\(\beta, \alpha, \alpha_1,\alpha_2\) sum over the spin indices.
+\(l_1,l_2\) sum over the channels.
+We will start simplifying this equation by summing over \(q\).
+\(c^\dagger_{q\beta}\) and \(c_{q\beta}\) can be easily combined to form \(\hat n_{q\beta}\), because they anti-commute with the other momenta.
+The sum gives \(\sum_q \hat n_{q\beta l_1} = n(D) \).
+This gives
+\begin{equation}\begin{aligned}
+	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = J^3 n(D)\sum_{k, k_1,k_2,\atop{\beta, \alpha, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} \frac{c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} c^\dagger_{k\alpha, l_1} S_d^c s^c_{\alpha \beta}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2}
+\end{aligned}\end{equation}
+The operators \(c^\dagger_{k\alpha}\) and its conjugate can be brought together without any change of sign because there will be an even number of flips. The sum over \(k\) gives
+\begin{equation}\begin{aligned}
+	\sum_k \frac{1 - \hat n_{k\alpha l_1}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2} =  \rho\int \frac{d\epsilon\left[1 - \hat n(\epsilon)_{\alpha l_1}\right] }{\left(\omega - D/2 -\epsilon/2 + J/4\right)^2} = \rho\int_0^{D-2\left( \omega + J/4 \right) } \frac{d\epsilon}{\left(\omega - D/2 -\epsilon/2 + J/4\right)^2}
+\end{aligned}\end{equation}
+The integration goes over positive energies only because of the \(1 - \hat n\) operator; the upper limit of the integration is chosen so as to make the denominator double, because this preserves the symmetry of the denominator and this is what happens in poor man's scaling.
+Performing the integration gives
+\begin{equation}\begin{aligned}
+	\sum_k \frac{1 - \hat n_{k\alpha l_1}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2} = -\frac{1}{2}\frac{\rho}{\omega - D/2 + J/4}
+\end{aligned}\end{equation}
+The sum over the channel index \(l_1\) produces a factor of \(K\). \(K = \sum_{l_1}\) is the total number of conduction bath channels. The entire expression is now
+\begin{equation}\begin{aligned}
+	\label{first_term}
+	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\sum_{\beta, \alpha, \alpha_1,\alpha_2,\atop{a,b,c}} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha_1 \alpha_2} S_d^c s^c_{\alpha \beta} \sum_{k_1,k_2,l_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
+\end{aligned}\end{equation}
+We now need to simplify the spin products.
+The sum over \(\alpha,\beta\) can be carried out immediately: \(\sum_{\alpha,\beta} s^a_{\beta \alpha} s^c_{\alpha \beta} = \text{Trace}\left(s^a s^c\right) = \frac{1}{2}\delta^{ac}\).
+Substituting this gives
+\begin{equation}\begin{aligned}
+	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\frac{1}{2}\sum_{\alpha_1,\alpha_2,a,b} S_d^a S_d^b S_d^a \sum_{k_1,k_2,l_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}s^b_{\alpha_1 \alpha_2}
+\end{aligned}\end{equation}
+The spin product can now be carried out:
+\begin{equation}\begin{aligned}
+	\sum_a S_d^a S_d^b S_d^a = \sum_a S_d^a\left[\frac{1}{4}\delta^{ab} + \frac{i}{2}\sum_c \epsilon^{bac}S_d^c\right] = \frac{1}{4}S_d^b - \frac{1}{4}\sum_{ace}\epsilon^{bac}\epsilon^{ace}S_d^e = \frac{1}{4}S_d^b - \frac{1}{4}S_d^b \sum_{ac}\epsilon^{bac}\epsilon^{acb} \\
+	= -\frac{1}{4}S_d^b
+\end{aligned}\end{equation}
+The renormalization becomes
+\begin{equation}\begin{aligned}
+	\Delta H_1 = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\frac{1}{2}\left( -\frac{1}{4} \right) \sum_{k_1,k_2,\alpha_1,\alpha_2,b} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}\\
+=\frac{1}{16}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4} \sum_{k_1,k_2,\alpha_1,\alpha_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
 \end{aligned}\end{equation}
 
-\subsection{First term}
-\begin{align}
-	c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c = J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime} c^\dagger_{q\beta} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\beta \alpha} \frac{1}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \beta}
-\end{align}
-Here the intermediate state is unoccupied, so we put \(\tau = -\frac{1}{2}, s_q^z = -\frac{\beta}{2}\) and since the initial state was occupied, we put \(\epsilon_q = D\).
-\begin{align}
-	c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c &= \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{J^2}{\omega^\prime - \frac{1}{2}D + J \frac{\beta}{2}S_d^z }c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} \\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{\left(\omega^\prime - \frac{1}{2}D\right) - J \frac{\beta}{2}S_d^z }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta}\\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
-							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^a s^a_{\alpha^\prime \beta} \hat n_{q\beta} \\
-							   &= J^2 n_j \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^b \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z \frac{1}{2}\beta}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^a
-\end{align}
-We again simplify the terms individually, calling them term 1 and term 2. 
-\begin{equation}\begin{aligned}
-	\text{term 1} = \frac{-\left(\omega^\prime - \frac{1}{2}D\right)J^2 n_j} {\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^b S_d^a
-\end{aligned}\end{equation}
-Since this term will renormalize only for \(a \neq b\), we can use \(S_d^b S_d^a = -S_d^a S_d^b\). This gives
-\begin{equation}\begin{aligned}
-	\text{term 1} = \frac{\left(\omega^\prime - \frac{1}{2}D\right)J^2 n_j} {\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^a S_d^b
-\end{aligned}\end{equation}
-This is identical to term 3 (eq.~\ref{term3_def}) except for the change \(\omega^\prime \to \omega\). Copying the result from term 3, we get
-\begin{equation}\begin{aligned}
-	\label{term3}
-	\text{term 1} = -\frac{1}{2}\frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
-\end{aligned}\end{equation}
-The other term is
-\begin{equation}\begin{aligned}
-	\text{term 2} = \frac{1}{2}\frac{J^3 n_j}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{\beta k k^\prime \alpha \alpha^\prime a b} \beta c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^b S_d^z S_d^a
-\end{aligned}\end{equation}
-From eq.~\ref{identity_SSS}, we know that \(S_d^b S_d^z S_d^a =  S_d^a S_d^z S_d^b\), which means this term is again identical to its counterpart, term 4.
-\begin{equation}\begin{aligned}
-	\label{term4}
-	\text{term 2} = \frac{J^3 n_j }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\vec{S_d}\cdot\vec{s}_{\alpha^\prime\alpha} -S_d^z \sum_{a \beta} \beta s^a_{\alpha^\prime\beta} s^a_{\beta\alpha} \right)
-\end{aligned}\end{equation}
-
-\subsection{Total renormalization \(\Delta H^{(2)}\)}
-From the formula for the renormalization \(\Delta H^{(2)}\), we write
-\begin{equation}\begin{aligned}
-	\Delta H^{(2)} = \text{term 1} + \text{term 2} + \text{term 3} + \text{term 4}
-\end{aligned}\end{equation}
-These four terms are given by eqs.~\ref{term1}, \ref{term2}, \ref{term3} and \ref{term4}.
-Since the Hamiltonian has particle-hole and \(\mathrm{SU}(2)\) symmetry, we will impose these symmetries by choosing the relation between \(\omega\) and \(\omega^\prime\) such that \(\text{term 2} = \text{term 4}\) and \( \text{term 3} = -\text{term 1}\).
-The total renormalization at second order is therefore
-\begin{equation}\begin{aligned}
-	\Delta H^{(2)} = -2 \times \text{term 3} = -\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
-\end{aligned}\end{equation}
-which gives
-\begin{equation}\begin{aligned}
-	\Delta J^{(2)} = -\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}
-\end{aligned}\end{equation}
-For \(\omega < D/2\), we get the flow towards the strong-coupling fixed point.
-That is, there is an attractive stable fixed point at \(J^* = 4|\omega - D/2|\) for all bare \(J > 0\).
-We also get a decay towards the local moment fixed point \(J^* = 0\) for \(J < 0\).
-For \(\omega = -D/2\) and \(J \ll D\), we get the one-loop PMS form.
-\begin{equation}\begin{aligned}
-	\Delta J^{(2)} = \frac{J^2 n_j D}{D^2 - \frac{1}{16}J^2} \simeq \frac{J^2 n_j }{D}
-\end{aligned}\end{equation}
-\section{Next-to-leading order renormalization}
-\begin{equation}\begin{aligned}
-	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term} ~-~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term}
-\end{aligned}\end{equation}
-
-\subsection{First term}
-\begin{equation}\begin{aligned}
-	&c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c\\
-	&= \sum_{q, k, k^\prime, k_1,k_2,\atop{\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} \frac{J^2}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{J}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha^\prime \beta}
-\end{aligned}\end{equation}
-\(q\) sums over the momenta being decoupled.
-\(k, k^\prime, k_1,k_2\) sum over the momenta not being decoupled.
-\(\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2\) sum over the spin indices.
-\(l_1,l_2\) sum over the channels.
-We substitute \(s_q^z = -\frac{\beta}{2}\) and \(\epsilon_q \tau_{q\beta} = \frac{D}{2}\).
-The term inside the summation becomes
-\begin{equation}\begin{aligned}
-	&J^3 c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} \frac{1}{\omega^\prime - \frac{D}{2} + J \frac{\beta}{2}S_d^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{1}{\omega^\prime - \frac{D}{2} + J \frac{\beta}{2}S_d^z} c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha^\prime \beta}\\
-	=&\frac{J^3 c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha^\prime \beta}}{\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}
-\end{aligned}\end{equation}
-We will start simplifying this equation by summing over \(q\).
-\(c^\dagger_{q\beta}\) and \(c_{q\beta}\) can be easily combined to form \(\hat n_{q\beta}\), because they anti-commute with the other momenta.
-The sum gives \(\sum_q \hat n_{q\beta l_1} = n_j \).
-This gives (without writing the summations explicitly)
-\begin{equation}\begin{aligned}
-	\frac{J^3 n_j  c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) c^\dagger_{k^\prime\alpha^\prime, l_1} S_d^c s^c_{\alpha^\prime \beta}}{\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}
-\end{aligned}\end{equation}
-The next simplification involves identifying how to contract the operators.
-The contractions have to be done so as to reproduce the original \(\vec{S_d}\cdot\vec{s}c^\dagger c\) form so that we can read off the renormalization.
-Currently, there are four distinct electron labels, \(k,k^\prime,k_1,k_2\).
-There are two ways to contract them.
-The first is by choosing \(k_1\alpha_1 = k_2\alpha_2\).
-However, this term vanishes:
-\begin{equation}\begin{aligned}
-	\sum_{k_1\alpha_1,b}S_d^b s^b_{\alpha_1 \alpha_1} c^\dagger_{k_1\alpha_1,l_2}c_{k_1 \alpha_1,l_2} = \sum_{b,k_1\alpha_1}S_d^b s^b_{\alpha_1 \alpha_1}\hat n_{k_1\alpha_1,l_2} &= \sum_{b}S_d^b \left(\sum_{\alpha_1}s^b_{\alpha_1 \alpha_1}\right) \int_{-D + |\delta D|}^0 d\epsilon \rho(\epsilon)\\
-																						      &= \sum_b S_d^b \text{ Trace }(s^b)\int_{-D + |\delta D|}^0 d\epsilon \rho(\epsilon)= 0
-\end{aligned}\end{equation}
-The other way to contract the indices is by selecting \(k\alpha = k^\prime \alpha^\prime\).
-Those two operators can again be brought together without any change of sign because there will be an even number of flips.
-Summing over \(k=k^\prime\) and the channel index \(l_1\) then gives \(\sum_{l_1}\sum_k \left(1 - \hat n_{k\alpha}\right) = \sum_{l_1}\int_{-D + |\delta D|}^ 0 n_j = \frac{1}{2}K n_j N_j\), where \(n_j = \rho |\delta D|\) and \(N_j = \rho D\).
-\(K = \sum_{l_1}\) is the total number of conduction bath channels.
-The factor of half is inserted to model the probability of transition appropriately; not all values of \(\epsilon_k\) will contribute equally to the renormalization.
-The entire expression is now
-\begin{equation}\begin{aligned}
-	\label{first_term}
-	&\sum_{k_1,k_2,\beta,\alpha, \atop{\alpha^\prime, \alpha_1,\alpha_2,\atop{l_2,a,b,c}}}\frac{J^3 K N_j n_j  S_d^a s^a_{\beta \alpha} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) S_d^c s^c_{\alpha^\prime \beta}}{2\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2} \\
-	&= \frac{J^3 K N_j n_j }{2\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \sum_{\beta,\alpha, \atop{a,b,c}}S_d^a s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) S_d^c
-\end{aligned}\end{equation}
-We now need to simplify the final summation.
-\begin{equation}\begin{aligned}
-	\label{final_sum}
-\sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} S_d^a \left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b\left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) S_d^c
-\end{aligned}\end{equation}
-The internal product can be evaluated as follows:
-\begin{equation}\begin{aligned}
-	\label{internal_sum}
-	\left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right)S_d^b\left(\omega^\prime - \frac{D}{2} - J \frac{\beta}{2}S_d^z\right) = \left(\omega^\prime - \frac{D}{2}\right)^2 S_d^b - \frac{\beta J}{2}\left(\omega^\prime - \frac{D}{2}\right)\left\{S_d^z, S_d^b\right\} + \frac{J^2}{4}S_d^z S_d^b S_d^z
-\end{aligned}\end{equation}
-The anticommutator is \(\left\{S_d^z, S_d^b\right\} = \frac{\delta^{bz}}{2}\).
-The triple operator product is given by eq.~\ref{identity_SSS}: \(S_d^z S_d^b S_d^z = \frac{1}{4}S_d^b\left(2\delta^{bz} - 1\right)\).
-The right-hand side of eq.~\ref{internal_sum} becomes
-\begin{equation}\begin{aligned}
-	\left[\left(\omega^\prime - \frac{D}{2}\right)^2 + \frac{J^2}{16} \left(2\delta^{bz} - 1\right)\right]S_d^b - \frac{\beta J}{4}\delta^{bz}\left(\omega^\prime - \frac{D}{2}\right) \equiv \mathcal{C}_1^b S_d^b + \mathcal{C}_2^b
-\end{aligned}\end{equation}
-Eq.~\ref{final_sum} takes the form
-\begin{equation}\begin{aligned}
-	\sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\left(\mathcal{C}_1^b S_d^a S_d^b S_d^c+ \mathcal{C}_2^b S_d^a S_d^c\right)  
-\end{aligned}\end{equation}
-These spin products can again be evaluated using standard identities:
-\begin{equation}\begin{aligned}
-	S_d^a S_d^c = \frac{i}{2}\sum_{e}\epsilon^{ace}S_d^e, ~ ~ ~ S_d^a S_d^b S_d^c = \frac{1}{4}\left(\delta^{ab}S_d^c - \delta^{ac}S_d^b + \delta^{bc}S_d^a\right) 
-\end{aligned}\end{equation}
-We have dropped constant terms in both equations because such terms cannot renormalize the Hamiltonian. This gives, for eq.~\ref{final_sum},
-\begin{equation}\begin{aligned}
-	\label{Cb1Cb2}
-	\sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\left[\frac{1}{4}\mathcal{C}_1^b \left(\delta^{ab}S_d^c - \delta^{ac}S_d^b + \delta^{bc}S_d^a\right)+ \mathcal{C}_2^b \frac{i}{2}\sum_{e}\epsilon^{ace}S_d^e\right]
-\end{aligned}\end{equation}
-We take the first term.
-Define \(\mathcal{C}^b_1 = \mathcal{C}_{11} + \mathcal{C}_{12}\delta^{bz}\).
-Also note that the indices \(\alpha,\beta\) can be easily summed over: \(\sum_{\alpha\beta}s^a_{\beta\alpha}c^c_{\alpha\beta} = \text{Trace}\left(s^a s^c\right) = \frac{1}{2}\delta^{ac}\).
-The term in product with \(\mathcal{C}^b_1\) becomes
-\begin{equation}\begin{aligned}
-	\label{Cb1}
-	\frac{1}{2}\sum_{a,b}s^b_{\alpha_1 \alpha_2}\frac{1}{4}\left(\mathcal{C}_{11} + \mathcal{C}_{12}\delta^{bz}\right) \left(2\delta^{ab}S_d^a - S_d^b\right) &= -\frac{1}{8}\sum_{b}s^b_{\alpha_1 \alpha_2}\left(\mathcal{C}_{11} + \mathcal{C}_{12}\delta^{bz}\right)S_d^b = -\frac{1}{8}\left(\mathcal{C}_{11} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} + \mathcal{C}_{12}s^z_{\alpha_1\alpha_2}S_d^z\right)
-\end{aligned}\end{equation}
-The term in product with \(\mathcal{C}^b_2\) can be written as
-\begin{equation}\begin{aligned}
-	- \frac{i J\left(\omega^\prime - \frac{D}{2}\right)}{8}\sum_{\beta,\alpha, \atop{a,b,c}} \delta^{bz}\beta s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\sum_{e}\epsilon^{ace}S_d^e &= - \frac{i J\left(\omega^\prime - \frac{D}{2}\right)}{8}\sum_{\beta,\alpha, \atop{a,c}} \beta s^a_{\beta \alpha} s^z_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\sum_{e}\epsilon^{ace}S_d^e\\
-																									   &=\frac{-iJ\left(\omega^\prime - \frac{D}{2}\right)}{8}\sum_{\beta,a,c,e} \beta \left(s^c s^a\right)_{\beta \beta} s^z_{\alpha_1 \alpha_2}\epsilon^{ace}S_d^e\\
-\end{aligned}\end{equation}
-Since \(a \neq c\) (\(a=c\) would make \(\epsilon^{ace} = 0\)), we can use \(\left(s^c s^a\right)_{\beta \beta} = \frac{i}{2}\sum_f \epsilon^{caf}s^f_{\beta\beta} = \frac{i\beta}{4}\epsilon^{caz}\).
-Substituting this gives
-\begin{equation}\begin{aligned}
-	\label{Cb2}
-	\frac{J\left(\omega^\prime - \frac{D}{2}\right)}{32}\sum_{a,c,e} s^z_{\alpha_1 \alpha_2}\epsilon^{ace}\epsilon^{caz}S_d^e = \frac{J\left(\omega^\prime - \frac{D}{2}\right)}{16} s^z_{\alpha_1 \alpha_2}S_d^z
-\end{aligned}\end{equation}
-
-Once we note that \(\mathcal{C}_{11} = \left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\) and \(\omega^\prime - D/2 - 2\mathcal{C}_{12}/J = \omega^\prime - D/2 - J/4\) and when we substitute eqs.~\ref{Cb1} and \ref{Cb2} into eq.~\ref{first_term}, we get
-\begin{equation}\begin{aligned}
-	\label{third_term_1}
-	&-\frac{1}{16}\frac{J^3 K N_j n_j }{\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} + \frac{J^4 K N_j n_j \left( \omega^\prime - D/2 - J/4 \right) }{32\left[\left(\omega^\prime - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
-\end{aligned}\end{equation}
-
-\subsection{Second term}
-\begin{equation}\begin{aligned}
-	&T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T\\
-	&= \sum_{q, k, k^\prime, k_1,k_2,\atop{\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}}c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1}  S_d^c s^c_{\alpha^\prime \beta} \frac{J^2}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{J}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha}
-\end{aligned}\end{equation}
-We take similar steps as before:
-\begin{inparaenum}
-	\item \(\epsilon_q \tau_{q\beta} = \frac{D}{2}\)
-	\item \(s^z_q = \frac{\beta}{2}\)
-	\item Sum over \(q\) to get \(n_j\)
-	\item Contract \(k\alpha,k^\prime\alpha^\prime\) to get \(K N_j n_j / 2\)
-	\item Compute the internal product to obtain \(\mathcal{C}_1^b S_d^b - \mathcal{C}_2^b\)
-\end{inparaenum}.
-The expression at this point is
-\begin{equation}\begin{aligned}
-	\label{Cb1Cb2_2}
-	\frac{J^3 K N_j n_j }{2\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} S_d^c \left(\mathcal{C}_1^b S_d^b - \mathcal{C}_2^b\right) S_d^a
-\end{aligned}\end{equation}
-\(\mathcal{C}^b_1\) is exactly the same as before, the only difference being \(\omega\) replaces \(\omega^\prime\).
-The sign of \(\mathcal{C}^b_2\) has also flipped, because \(\beta \to -\beta\).
-The other difference is that \(S_d^a\) and \(S_d^c\) have switched places.
-Eq.~\ref{Cb1Cb2} is replaced by
-\begin{equation}\begin{aligned}
-	\label{Cb1Cb2_3}
-	\sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\left[\frac{1}{4}\mathcal{C}_1^b \left(\delta^{ab}S_d^c - \delta^{ac}S_d^b + \delta^{bc}S_d^a\right) + \mathcal{C}_2^b \frac{i}{2}\sum_{e}\epsilon^{ace}S_d^e\right]
-\end{aligned}\end{equation}
-Note that even though \(\mathcal{C}^b_2\) came with a minus sign in eq.~\ref{Cb1Cb2_2}, that minus sign has been canceled by a second minus sign that arises from the exchange of \(a \leftrightarrow c\) in \(\epsilon^{cae}\).
-Since eq.~\ref{Cb1Cb2_3} is identical to eq.~\ref{Cb1Cb2}, we can dirctly write down the renormalization in this case:
-\begin{equation}\begin{aligned}
-	\label{third_term_2}
-	-\frac{1}{16}\frac{J^3 K N_j n_j }{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} + \frac{J^4 K N_j n_j \left( \omega - D/2 - J/4 \right) }{32\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
-\end{aligned}\end{equation}
+\subsubsection{Calculation of second term}
+Like the single-channel case, the renormalization coming from the hole excitations is exactly the Hermitian conjugate of that in the particle sector.
+And since the renormalization \(\Delta H_1\) is Hermitian, we have \(\Delta H_0 = \Delta H_1\)
 
 \subsection{Total renormalization \(\Delta H^{(3)}\)}
-Similar to the one-loop case, we will choose the require \(\omega\) and \(\omega^\prime\) to be related such that the  RG equations are \(\mathrm{Su}(2)\) symmetric; that is, we will require the terms that renormalize only \(S_d^z s^z\) vanish.
-The total renormalization at this order is obtained by adding eqs.~\ref{third_term_1} and \ref{third_term_2}.
+The total renormalization is twice that in the particle sector.
 \begin{equation}\begin{aligned}
-	\Delta H^{(3)} = -\frac{J^3 K N_j n_j / 8}{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2}
+	\Delta H^{(3)} = \frac{1}{8}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4} \sum_{k_1,k_2,\alpha_1,\alpha_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
 \end{aligned}\end{equation}
-Combining with \(\Delta H^{(2)}\), we get
+Combining with \(\Delta H^{(2)}\) and replacing \(n(D) = \rho |\delta D|\), we get
 \begin{equation}\begin{aligned}
-	\Delta J = \frac{J^2 n_j \left[2 \left(D - 2\omega\right) - \frac{1}{2}J K N_j\right]}{\left(D - 2\omega\right)^2 - \frac{1}{4}J^2}
+	\frac{\Delta J}{|\Delta D|} = -\frac{J^2 \rho}{\omega - D/2 + J/4} + \frac{1}{8}\frac{J^3 \rho^2 K}{\omega - D/2 + J/4} = -\frac{J^2 \rho}{\omega - D/2 + J/4}\left[1 - \frac{1}{8}J\rho K\right] 
 \end{aligned}\end{equation}
 We choose \(\omega = -D/2\) to get a clearer idea of what the equations say. 
-We also set \(N_j = \rho D\) and \(n_j = \rho |\delta D|\).
-Quantities with zero in the subscript will denote their values in the bare Hamiltonian.
-Using \(\delta D = -|\delta D|\), we can write the continuum form of the equation:
 \begin{equation}\begin{aligned}
-	\frac{\:\mathrm{d}J}{\:\mathrm{d}t} = \frac{J^2 \rho D^2 \left(1 - \frac{1}{8}JK\rho\right)}{D^2 - \frac{1}{16}J^2}
+	\label{mchannel}
+	\frac{\Delta J}{|\Delta D|} = \frac{J^2 \rho}{D - J/4}\left[1 - \frac{1}{8}J\rho K\right] 
 \end{aligned}\end{equation}
-where \(dt = \frac{dD}{D}\).
+Quantities with zero in the subscript will denote their values in the bare Hamiltonian. Using \(\delta D = -|\delta D|\), we can write the continuum form of the equation:
+\begin{equation}\begin{aligned}
+	\frac{\:\mathrm{d}J}{\:\mathrm{d}D} = \frac{J^2 \rho}{D - J/4}\left(\frac{1}{8}J\rho K - 1\right)
+\end{aligned}\end{equation}
 
@@
 	\label{pms_mchannel}
-	\frac{\:\mathrm{d}J}{\:\mathrm{d}t} \simeq \frac{J^2 \rho D^2 \left(1 - \frac{1}{8}JK\rho\right)}{D^2} = J^2 \rho \left(1 - \frac{1}{8}JK\rho\right)
+	\frac{\:\mathrm{d}J}{\:\mathrm{d}D} \simeq  \frac{J^2 \rho}{D}\left(\frac{1}{8}J\rho K - 1\right)
 \end{aligned}\end{equation}
@@
 
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 \end{figure}
-For \(D\) not so large, the denominator also comes into play, and we get the possibility of two fixed points, one from the numerator and the other from the numerator.
-\begin{figure}[htpb]
+For \(D\) not so large, the denominator also comes into play, and eq.\ref{mchannel} holds. We get the possibility of two fixed points - one from the numerator and the other from the numerator.
+\begin{figure}[!htb]
 	\centering
@@
 
-The numerator fixed point is given by
+The numerator and denominator fixed points, \(J_1^*\) and \(J_2^*\) respectively, are given by
 \begin{equation}\begin{aligned}
-	J_1^* = \frac{8}{K \rho}
-\end{aligned}\end{equation}
-while the denominator fixed point is defined by the condition
-\begin{equation}\begin{aligned}
-	D^* = \frac{J_2^*}{4}
+	J_1^* = \frac{8}{K \rho}, && D^* = \frac{J_2^*}{4}
 \end{aligned}\end{equation}
@@
 For large \(D_0\), it essentially shrinks to zero, and the numerator becomes the first fixed point for essentially all \(\rho\).
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 If we start with \(J_0\) in the neighborhood of \(J_1^*\), we can use \(J_1^* \ll D_0\) to ignore \(J\) in the denominator and the RG equation reduces to the poor man's scaling form eq.~\ref{pms_mchannel}.
-The denominator fixed point has effectively moved off to infinite.
+The denominator fixed point has effectively moved off to infinity.
+That this is true can also be argued from the single-channel Kondo model URG results.
+There, we saw that when the bandwidth is scaled to larger values, the strong-coupling fixed point was stable at successively larger values of \(J^*\).
+Since the denominator fixed point is identical in structure in both problems, its reasonable that the same thing will happen here.
 
-\textbf{\textit{The part of the problem that I have not yet figured out is the following: How do we argue for the same when \(J_0\) is not in the neighborhood of \(J_1^*\)?
-That is, if \(J_0\) is sufficiently large so that we cannot simpify the denominator.
-It is true that in order to compete with a thermodynamically large \(D_0\), the bare \(J_0\) will have to be extremely large, and it's possible that this does not even fall in the class of models we are studying.}}
+\section{Derivation of low energy effective Hamiltonian \((k-\text{space})\)}
+Fixed point Hamiltonian is
+\begin{equation}\begin{aligned}
+	H^* = H_0 + J^*\sum_{l} \vec{S_d}\cdot\vec{s_\text{tot}}
+\end{aligned}\end{equation}
+where \(H_0 = \sum_{k,l,\sigma}\epsilon_{k,l}\hat n_{k\sigma,l}\) and \(\vec s_\text{tot} = \sum_l \vec s_l = \sum_{kk^\prime\alpha\alpha^\prime,l} \vec \sigma_{\alpha\alpha^\prime}c^\dagger_{k\alpha,l}c_{k^\prime\alpha^\prime,l}\).
+\(l\) sums over the channels.
+Henceforth we will drop the \(*\).
+Obtaining the effective Hamiltonian involves obtaining the low energy excitations on top of this fixed point Hamiltonian.
+The large-energy excitations are ones that involve spin flips.
+This guides the separation of the Hamiltonian into a diagonal and an off-diagonal piece:
+\begin{equation}\begin{aligned}
+	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_V
+\end{aligned}\end{equation}
+The effective Hamiltonian that has the states \(\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}\) as eigenstates are
+\begin{equation}\begin{aligned}
+	H_\text{eff} = H_d + V \frac{1}{E_\text{gs} - H_d}V = \sum_{k,l,\sigma}\epsilon_{k,l}\hat n_{k\sigma,l} + J S_d^z s_\text{tot}^z + \frac{J}{2}S_d^+ s_\text{tot}^- \frac{1}{E_\text{gs} - J S_d^z s_\text{tot}^z - H_0}\frac{J}{2}S_d^- s_\text{tot}^+\\
+	+\frac{J}{2}S_d^- s_\text{tot}^+ \frac{1}{E_\text{gs} - J S_d^z s_\text{tot}^z - H_0}\frac{J}{2}S_d^+ s_\text{tot}^-
+\end{aligned}\end{equation}
+We can easily simplify the \(S_d^z\) in the denominator, because \(S_d^\pm \frac{1}{A + B S_d^z} = S_d^\pm \frac{1}{A \mp \frac{1}{2}B}\).
+\begin{equation}\begin{aligned}
+	H_\text{eff} = \sum_{k,l,\sigma}\epsilon_{k,l}\hat n_{k\sigma,l} + J S_d^z s_\text{tot}^z + \frac{J^2}{4} s_\text{tot}^- \frac{\frac{1}{2} + S_d^z}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^+ + \frac{J^2}{4} s_\text{tot}^+ \frac{\frac{1}{2} - S_d^z}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^-
+\end{aligned}\end{equation}
+Since \(H_0\) does not commute with the spin operators, we will need to expand the denominator to make sense of this Hamiltonian.
+\begin{equation}\begin{aligned}
+	 s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^+ =  s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0\right] s_\text{tot}^+\\
+	 s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^- =  s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0\right] s_\text{tot}^-
+\end{aligned}\end{equation}
+This is an expansion in \(H_0^n/J^{n+1}, n=0,1,2,\ldots\). The \(n=0\) terms give
+\begin{equation}\begin{aligned}
+	s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}s_\text{tot}^+ = s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)} %= \left[s_\text{tot}\left( s_\text{tot}+1 \right)  - s_\text{tot}^z\left( s_\text{tot}^z + 1 \right) \right] \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\\
+	\\
+	s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}s_\text{tot}^- = s_\text{tot}^+ s_\text{tot}^- \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}% = \left[s_\text{tot}\left( s_\text{tot}+1 \right)  - s_\text{tot}^z\left( s_\text{tot}^z - 1 \right) \right] \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}
+\end{aligned}\end{equation}
 
+One of the \(n=1\) terms gives
+\begin{equation}\begin{aligned}
+	s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^+ =  \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 s_\text{tot}^- H_0 s_\text{tot}^+
+\end{aligned}\end{equation}
+Next we calculate the commutator:
+\begin{equation}\begin{aligned}
+	\left[s_\text{tot}^+, H_0\right] = X^\dagger_{1,\text{tot}} = \sum_l X_{1,l}^\dagger = \sum_{kk^\prime,l}\left(\epsilon_k - \epsilon_{k^\prime}\right) c^\dagger_{k^\prime \uparrow} c_{k \downarrow}
+\end{aligned}\end{equation}
+where \(X_{n,l} \equiv \sum_{k,k^\prime}\left(\epsilon_k - \epsilon_{k^\prime}\right)^n c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \).
+Substituting this commutator gives
+\begin{equation}\begin{aligned}
+	s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^+ =  \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 \left(s_\text{tot}^- s_\text{tot}^+ H_0 - s_\text{tot}^- X^\dagger_{1,\text{tot}}\right)
+\end{aligned}\end{equation}
+The other \(n=1\) term gives
+\begin{equation}\begin{aligned}
+	s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^- =  \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 \left(s_\text{tot}^+ s_\text{tot}^- H_0 + s_\text{tot}^+ X_{1,\text{tot}}\right)
+\end{aligned}\end{equation}
+One of the \(n=2\) terms gives
+\begin{equation}\begin{aligned}
+	&s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^+\\
+	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 s_\text{tot}^- H_0 \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^+ \\
+	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 s_\text{tot}^- H_0 \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\left(s_\text{tot}^+ H_0 - X^\dagger_\text{1,tot}\right) \\
+	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 \left[s_\text{tot}^- H_0 s_\text{tot}^+\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 - s_\text{tot}^- H_0\frac{1}{E_\text{gs} + \frac{J}{2}s_\text{tot}^z}X^\dagger_\text{1,tot}\right] \\
+	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 \left[s_\text{tot}^- \left(s_\text{tot}^+H_0 - X^\dagger_{1,\text{tot}}\right)\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 - s_\text{tot}^- H_0\frac{1}{E_\text{gs} + \frac{J}{2}s_\text{tot}^z}X^\dagger_\text{1,tot}\right] \\
+	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 \left[s_\text{tot}^- s_\text{tot}^+H_0\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 - s_\text{tot}^-\left(X^\dagger_{1,\text{tot}}\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 + H_0\frac{1}{E_\text{gs} + \frac{J}{2}s_\text{tot}^z}X^\dagger_\text{1,tot}\right)\right] \\
+\end{aligned}\end{equation}
+At this point, we need the commutator between \(H_0\) and \(s_\text{tot}^z\):
+\begin{equation}\begin{aligned}
+	\left[H_0, s_\text{tot}^z\right] = Z_{1,\text{tot}} = \sum_l Z_{1, l} = \sum_{k,k^\prime,l}\left( \epsilon_k - \epsilon_{k^\prime} \right) \frac{1}{2}\left(c^\dagger_{k \uparrow,l}c_{k^\prime \uparrow,l} - c^\dagger_{k \downarrow,l}c_{k^\prime \downarrow,l}\right)
+\end{aligned}\end{equation}
+This gives the relation
+\begin{equation}\begin{aligned}
+	H_0 (a + b s_\text{tot}^z) = (a + b s_\text{tot}^z) H_0 + Z_{1,\text{tot}} \implies \frac{1}{a + b s_\text{tot}^z} H_0 = H_0 \frac{1}{a + b s_\text{tot}^z} + \frac{1}{a + b s_\text{tot}^z} Z_{1,\text{tot}} \frac{1}{a + b s_\text{tot}^z}
+\end{aligned}\end{equation}
+Using this, we get
+\begin{align}
+	&s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^+\\
+	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 \left[s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 H_0 - s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} Z_{1,\text{tot}} \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)}H_0\right.\\
+	& \left.- s_\text{tot}^-\left(X^\dagger_{1,\text{tot}}\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 + H_0\frac{1}{E_\text{gs} + \frac{J}{2}s_\text{tot}^z}X^\dagger_\text{1,tot}\right)\right] \\
+	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 \left[s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 H_0 - s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} Z_{1,\text{tot}} H_0\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)}\right]\\
+\end{align}
+At the last step, we dropped the three-particle scattering terms.
+If we look at the effective Hamiltonian for a state \(\ket{S_d^z=\frac{1}{2}, s_\text{tot}, s^z_\text{tot}}\), we can replace the following operators with scalars:
+\begin{gather}
+	\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)} = \gamma_{s_\text{tot}}^{s_\text{tot}^z}\\
+	s_\text{tot}^- s_\text{tot}^+ = s_\text{tot}\left(s_\text{tot} + 1\right) - s^z_\text{tot}\left(s^z_\text{tot} + 1\right) = \chi_{s_\text{tot}}^{s_\text{tot}^z}
+\end{gather}
+The effective Hamiltonian for this state becomes
+\begin{equation}\begin{aligned}
+	H_\text{eff}\ket{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}}\bra{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}} = H_0 + \frac{J}{2}s^z_\text{tot} + \frac{J^2}{4}\gamma_{s_\text{tot}}^{s_\text{tot}^z}\chi_{s_\text{tot}}^{s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}} H_0 - \frac{\gamma_{s_\text{tot}}^{s_\text{tot}^z}}{\chi_{s_\text{tot}}^{s_\text{tot}^z}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right]
+\end{aligned}\end{equation}
+
+\appendix
+
+\section{URG analysis of the single-channel Kondo model}
+\label{1KondoURG}
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{k,l} J^z S_d^z s^z_{kl} + \frac{1}{2}\sum_{k,l} J^t \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right)
+\end{aligned}\end{equation}
+where \(s^z_{kl} = \frac{1}{2}\left(c^\dagger_{k\uparrow}c_{l \uparrow} - c^\dagger_{k\downarrow}c_{l \downarrow}\right)\), \(s^-_{kl} = c^\dagger_{k \downarrow}c_{l \uparrow}\) and \(s^+_{kl} = {s^-_{lk}}^\dagger\).
+Also, \(\tau = \hat n - \frac{1}{2}\).
+\(k,l\) sum over the momentum states.
+\(\vec S_d\) is the impurity spin operator.
+
+The scheme is that we will disentangle an electron \(q\beta\) from the Hamiltonian, \(q\) being the momentum and \(\beta\) the spin. The diagonal part of the Hamiltonian under this scheme is
+\begin{equation}\begin{aligned}
+\label{kondodiag}
+H^D_{q\beta} = \epsilon_q \tau_{q\beta} + J^z S_d^z s_{qq}^z
+\end{aligned}\end{equation}
+The off-diagonal parts at a particular RG step \(H^I_1\) and \(H^I_0\), that start from particle and hole states respectively, are
+\begin{equation}\begin{aligned}
+	H^I_1 = \sum_{|k|<\Lambda,q} J^z S_d^z s^z_{kq} + \frac{1}{2}\sum_{|k|<\Lambda,q} J^t \left(S_d^+ s^-_{kq} + S_d^- s^+_{kq}\right)\\
+	H^I_0 = \sum_{|k|<\Lambda,q} J^z S_d^z s^z_{qk} + \frac{1}{2}\sum_{|k|<\Lambda,q} J^t \left(S_d^+ s^-_{qk}  + S_d^- s^+_{qk}\right)
+\end{aligned}\end{equation}
+\(H^I_1\) is the Hamiltonian term that scatters from the occupied configuration of \(q\), \(H^I_0\) is the same from the unoccupied configuration.
+These are the terms that appear in the numerator.
+\subsection{Particle sector}
+The particle sector involves integrating out those states which are occupied (\(\hat n_{q\beta}=1\)). We will work at an energy  shell \(\epsilon_q = -D\). The renormalization is
+\begin{equation}\begin{aligned}
+	H^I_0 \frac{1}{\omega - H^D_{q\beta}} H^I_1
+\end{aligned}\end{equation}
+
+Both \(H^I_0\) and \(H^I_1\) have all three operators \(S_d^z, S_d^\pm\).
+We call \(S_d^z\) the spin-keep term and the others spin-flip terms.
+The entire product will thus have \(3\times 3 = 9\) terms.
+Not all terms however renormalize the Hamiltonian.
+Those terms that have identical operators on both sides can be ignored because \({S_d^z}^2 = \text{constant}\) and \({S^\pm}^2 = 0\).
+The other six terms will renormalize the Hamiltonian.
+This brings in one more simplification: all the six terms that \textit{will} renormalize the Hamiltonian have a spin flip operator on at least one side of the Greens function.
+This means that in the denominator of the Greens function, \(S_d^z\) and \(s^z_{qq}\) have to be anti-parallel in order to produce a non-zero result for that term.
+This means we can identically replace \(S_d^z s^z_{qq} = -\frac{1}{4}\).
+Also, in the particle sector, the Greens function always has \(c_{q\beta}\) in front of it, so \(\epsilon_q \tau_{q\beta} = D/2\).
+Substituting all this, we get
+\begin{equation}\begin{aligned}
+	\frac{1}{\omega - D/2 + J/4}\sum_{|k,k^\prime|<\Lambda,q}\left[\frac{1}{2}J^z J^t \left(S_d^z S_d^+ s^z_{qk^\prime}s^-_{kq} + S_d^z S_d^- s^z_{qk^\prime}s^+_{kq}\right) + \frac{1}{2}J^t J^z \left(S_d^+ S_d^z s^-_{qk^\prime}s^z_{kq} + S_d^- S_d^z s^+_{qk^\prime}s^z_{kq}\right)\right.\\
++\left.\frac{1}{4}{J^t}^2 \left(S_d^- S_d^+ s^+_{qk^\prime}s^-_{kq} + S_d^+ S_d^- s^-_{qk^\prime}s^+_{kq}\right)\right]
+\end{aligned}\end{equation}
+We now simplify the products and keep only terms diagonal in \(q\).
+For example: \(s^z_{qk^\prime}s^+_{kq} = \frac{1}{2}\hat n_{q \downarrow}s^+_{kk^\prime}\) and \(s^z_{qk^\prime}s^-_{kq} = -\frac{1}{2}\hat n_{q \uparrow}s^-_{kk^\prime}\).
+The renormalization becomes
+\begin{equation}\begin{aligned}
+	\frac{1}{\omega - D/2 + J/4}\sum_{|k,k^\prime|<\Lambda,q}\left[\frac{1}{4}J^z J^t \left(-\frac{1}{2}S_d^+ \hat n_{q}s^-_{kk^\prime} - \frac{1}{4}S_d^- \hat n_{q} s^z_{kk^\prime}\right) - \frac{1}{4}{J^t}^2 S_d^z\left(-\hat n_{q \uparrow}c^\dagger_{k \downarrow}c_{k^\prime \downarrow} + \hat n_{q \downarrow}c^\dagger_{k \uparrow}c_{k^\prime \uparrow}\right)\right]
+\end{aligned}\end{equation}
+We now replace \(\sum_q \hat n_{q\sigma} = n(D)\). The renormalization due to excitations coming from the particle sector is
+\begin{equation}\begin{aligned}
+	\Delta H_1 = -\frac{1}{2}\frac{n(D)}{\omega - D/2 + J/4}\sum_{|k,k^\prime|<\Lambda}\left[J^z J^t \frac{1}{2}\left(S_d^+ s^-_{kk^\prime} + S_d^- s^z_{kk^\prime}\right) + {J^t}^2 S_d^z s^z_{kk^\prime}\right]
+\end{aligned}\end{equation}
+The renormalization in the couplings coming from the particle sector is therefore,
+\begin{equation}\begin{aligned}
+	\label{kondo_part}
+	\Delta J^z = -\frac{1}{2}\frac{{J^t}^2n(D)}{\omega - D/2 + J/4}, && \Delta J^t = -\frac{1}{2}\frac{J^z J^tn(D)}{\omega - D/2 + J/4}
+\end{aligned}\end{equation}
+
+\subsection{Hole sector}
+The hole sector involves integrating out those states which are vacant (\(\hat n_{q\beta}=1\)). We will work at an energy  shell \(\epsilon_q = D\). The renormalization is
+\begin{equation}\begin{aligned}
+	H^I_1 \frac{1}{\omega - H^D_{q\beta}} H^I_0
+\end{aligned}\end{equation}
+The same considerations as those in the particle sector apply here, and the denominator becomes \(\omega - D/2 + J/4\), while the numerator is \(H^I_1 H^I_0\).
+Since this is just the Hermitian conjugate of the particle sector form, we do not need to calculate this separately, because the renormalization here will be \(\Delta H_0 = \Delta H_1^\dagger = \Delta H_1\).
+
+\subsection{Scaling equations}
+Since the renormalization in the hole sector is equal to that in the particle sector, the total renormalization is simply twice that in the particle sector (eqs.~\ref{kondo_part}):
+\begin{equation}\begin{aligned}
+	\Delta J^z = -\frac{{J^t}^2n(D)}{\omega - D/2 + J/4}, && \Delta J^t = -\frac{J^z J^tn(D)}{\omega - D/2 + J/4}
+\end{aligned}\end{equation}
+If we set \(J_z = J_t = J\), we have an SU(2)-symmetric Kondo model \(J \vec{S_d}\cdot\vec{s}\).
+\begin{equation}\begin{aligned}
+	\label{kondosym}
+	\Delta J = - \frac{J^2 n(D)}{\omega - D/2 + \frac{1}{4}J}
+\end{aligned}\end{equation}
+To recover the one-loop form, we can replace \(\omega\) with the bare value \(-D/2\) and ignore the \(J\) in the denominator (small \(J\)).
+\begin{equation}\begin{aligned}
+	\Delta J \approx \frac{J^2 n(D)}{D}
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	\Delta J^{(2)} = -\frac{J^2 n(D)}{\omega - D/2 + J/4}
+\end{aligned}\end{equation}
+For \(\omega < D/2\), we get the flow towards the strong-coupling fixed point.
+That is, there appears a stable fixed point at \(J^* = 4|\omega - D/2|\) for all bare \(J > 0\).
+We also get a decay towards the local moment fixed point \(J^* = 0\) for \(J < 0\).
+For \(\omega = -D/2\) and \(J \ll D\), we get the one-loop PMS form.
+\begin{equation}\begin{aligned}
+	\Delta J^{(2)} = \frac{J^2 n(D)}{D - J/4} \simeq \frac{J^2 n(D)}{D}
+\end{aligned}\end{equation}
 \end{document}

### 2021-11-16 multi-channel-urg.tex
wrote down all explicit effective Hamiltonians for two channel Kondo

@@
-\documentclass[10pt]{revtex4-2}
+\documentclass[12pt]{revtex4-2}
 \usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
@@
 	& \left.- s_\text{tot}^-\left(X^\dagger_{1,\text{tot}}\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 + H_0\frac{1}{E_\text{gs} + \frac{J}{2}s_\text{tot}^z}X^\dagger_\text{1,tot}\right)\right] \\
-	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 \left[s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 H_0 - s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} Z_{1,\text{tot}} H_0\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)}\right]\\
+	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 s_\text{tot}^- s_\text{tot}^+ \left[\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 H_0 - \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} Z_{1,\text{tot}} H_0\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)}\right]
 \end{align}
 At the last step, we dropped the three-particle scattering terms.
+
+The other \(n=2\) term gives
+\begin{equation}\begin{aligned}
+	&s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^-\\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+ H_0 \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^- \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+ H_0 \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\left(s_\text{tot}^- H_0 + X_\text{1,tot}\right) \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 \left[s_\text{tot}^+ H_0 s_\text{tot}^-\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0 + s_\text{tot}^+ H_0\frac{1}{E_\text{gs} - \frac{J}{2}s_\text{tot}^z}X_\text{1,tot}\right] \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+ \left(s_\text{tot}^- H_0 + X_\text{1,tot}\right)\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0 \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 \left[s_\text{tot}^+s_\text{tot}^- H_0 \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0\right] \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+s_\text{tot}^- \left[\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0^2 - \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} Z_{1,\text{tot}} \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0 \right] \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+s_\text{tot}^- \left[H_0^2 \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} - \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} Z_{1,\text{tot}} H_0 \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} \right]
+\end{aligned}\end{equation}
+
 If we look at the effective Hamiltonian for a state \(\ket{S_d^z=\frac{1}{2}, s_\text{tot}, s^z_\text{tot}}\), we can replace the following operators with scalars:
 \begin{gather}
-	\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)} = \gamma_{s_\text{tot}}^{s_\text{tot}^z}\\
-	s_\text{tot}^- s_\text{tot}^+ = s_\text{tot}\left(s_\text{tot} + 1\right) - s^z_\text{tot}\left(s^z_\text{tot} + 1\right) = \chi_{s_\text{tot}}^{s_\text{tot}^z}
+	\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)} = \gamma_{s_\text{tot}}^{s_\text{tot}^z},\\
+	\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} = \gamma_{s_\text{tot}}^{-s_\text{tot}^z}\\
+	s_\text{tot}^- s_\text{tot}^+ = s_\text{tot}\left(s_\text{tot} + 1\right) - s^z_\text{tot}\left(s^z_\text{tot} + 1\right) = \chi_{s_\text{tot}}^{s_\text{tot}^z}\\
+	s_\text{tot}^+ s_\text{tot}^- = s_\text{tot}\left(s_\text{tot} + 1\right) - s^z_\text{tot}\left(s^z_\text{tot} - 1\right) = \chi_{s_\text{tot}}^{-s_\text{tot}^z}
 \end{gather}
+They are not all independent: \(\left(\gamma_{s_\text{tot}}^{s_\text{tot}^z}\right)^{-1} + \left(\gamma_{s_\text{tot}}^{-s_\text{tot}^z}\right)^{-1} =  E_\text{gs} + J, \chi_{s_\text{tot}}^{s_\text{tot}^z} - \chi_{s_\text{tot}}^{-s_\text{tot}^z} = -2 s^z_\text{tot}\).
+
 The effective Hamiltonian for this state becomes
 \begin{equation}\begin{aligned}
-	H_\text{eff}\ket{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}}\bra{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}} = H_0 + \frac{J}{2}s^z_\text{tot} + \frac{J^2}{4}\gamma_{s_\text{tot}}^{s_\text{tot}^z}\chi_{s_\text{tot}}^{s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}} H_0 - \frac{\gamma_{s_\text{tot}}^{s_\text{tot}^z}}{\chi_{s_\text{tot}}^{s_\text{tot}^z}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right]
+	H_\text{eff}^{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}} = H_0 + \frac{J}{2}s^z_\text{tot} + \frac{J^2}{4}\gamma_{s_\text{tot}}^{s_\text{tot}^z}\chi_{s_\text{tot}}^{s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}} H_0 - \frac{\gamma_{s_\text{tot}}^{s_\text{tot}^z}}{\chi_{s_\text{tot}}^{s_\text{tot}^z}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right] \\
++ \frac{J^2}{4}\gamma_{s_\text{tot}}^{-s_\text{tot}^z}\chi_{s_\text{tot}}^{-s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}} H_0 + \frac{\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}{\chi_{s_\text{tot}}^{-s_\text{tot}^z}} s^+_\text{tot}X_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right]
+\end{aligned}\end{equation}
+For the two channel, we have four possible states in total: \(\left( s_\text{tot}, s_\text{tot}^z \right) = \left\{ (0,0), (1,-1), (1,0), (1,1) \right\} \).
+The state with \(s_\text{tot}=0\) cannot be acted on by \(s_\text{tot}^\pm\), so the effective Hamiltonian for this step will consist of only the diagonal part:
+\begin{equation}\begin{aligned}
+	H_\text{eff}^{\frac{1}{2}, 0, 0} = H_0 + \frac{J}{2}s^z_\text{tot} = H_0
+\end{aligned}\end{equation}
+The factors \(\gamma\) and \(\chi\) for the other states are
+\begin{equation}\begin{aligned}
+	s_\text{tot}, s_\text{tot}^z = && (1,-1), && (1,0), && (1,1)\\
+	\gamma_{s_\text{tot}}^{s_\text{tot}^z} = && \frac{1}{E_\text{gs}}, && \frac{1}{E_\text{gs} + J/2}, && -- \\
+	\chi_{s_\text{tot}}^{s_\text{tot}^z} = && 2, && 2, && --\\
+	\gamma_{s_\text{tot}}^{-s_\text{tot}^z} = && --, && \frac{1}{E_\text{gs} + J/2}, && \frac{1}{E_\text{gs}}\\
+	\chi_{s_\text{tot}}^{-s_\text{tot}^z} = && --, && 2, && 2\\
+\end{aligned}\end{equation}
+The complete set of effective Hamiltonians for the two-channel Kondo model can now be written down:
+\begin{equation}\begin{aligned}
+	H_\text{eff}^{\frac{1}{2}, 0, 0} &= H_0\\
+	H_\text{eff}^{\frac{1}{2}, 1, 1} &= H_0 + \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{1}{E_\text{gs}} H_0 + \frac{1}{2 E_\text{gs}} s^+_\text{tot}X_{1,\text{tot}} + \frac{1}{E_\text{gs}^2} H_0^2 - \frac{1}{E_\text{gs}^3} Z_{1,\text{tot}} H_0\right] \\
+	H_\text{eff}^{\frac{1}{2}, 1, -1} &= H_0 - \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{1}{E_\text{gs}} H_0 - \frac{1}{2 E_\text{gs}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + \frac{1}{E_\text{gs}^2} H_0^2 - \frac{1}{E_\text{gs}^3} Z_{1,\text{tot}} H_0\right] \\
+	H_\text{eff}^{\frac{1}{2}, 1, 0} &= H_0 + \frac{J^2}{4}\frac{2}{E_\text{gs} + J/2}\left[1 + \frac{1}{E_\text{gs} + J/2} H_0 + \frac{1}{2 E_\text{gs} + J} \left(s^+_\text{tot}X_{1,\text{tot}} - s^-_\text{tot}X^\dagger_{1,\text{tot}}\right) \right.\\
+					 &\left.+ \frac{2}{\left(E_\text{gs} + J/2\right)^2} H_0^2 - \frac{2}{\left(E_\text{gs} + J/2\right)^3} Z_{1,\text{tot}} H_0\right] \\
+\end{aligned}\end{equation}
+The terms have the following meanings:
+\begin{equation}\begin{aligned}
+	H_0 &= \sum_{k,\sigma,l}\epsilon_k^l \hat n_{k,\sigma,l}\\
+	H_0^2 &= \sum_{k_1,k_2,l_1,l_2,\sigma_1,\sigma_2}\epsilon_k^{l_1}\epsilon_{k_2}^{l_2} \hat n_{k_1,\sigma_1,l_1}\hat n_{k_2,\sigma_2,l_2}\\
+	s^+_\text{tot}X_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \uparrow, l_1}c^\dagger_{q_1, \downarrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{k_2, \downarrow, l_2}c_{q_2, \uparrow, l_2}\\
+	s^-_\text{tot}X^\dagger_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \downarrow, l_1}c^\dagger_{q_1, \uparrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{q_2, \uparrow, l_2}c_{k_2, \downarrow, l_2}\\
+	Z_{1,\text{tot}} H_0 &= \sum_{k_1,q_1,k_2,\sigma_2,l_1,l_2}\left(\epsilon_{k_1}^{l_1} - \epsilon_{q_1}^{l_1}\right) \epsilon_{k_2}^{l_2} \left(c^\dagger_{k_1, \uparrow, l_1}c^\dagger_{q_1, \uparrow, l_1} - c^\dagger_{k_1, \downarrow, l_1}c^\dagger_{q_1, \downarrow, l_1}\right) \hat n_{k_2,\sigma_2,l_2}\\
 \end{aligned}\end{equation}

### 2021-11-16 multi-channel-urg.tex
removed typos and exhausted the list of possible effective Hamiltonians (i missed some prev.)

@@
 \begin{equation}\begin{aligned}
-	H_\text{eff}^{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}} = H_0 + \frac{J}{2}s^z_\text{tot} + \frac{J^2}{4}\gamma_{s_\text{tot}}^{s_\text{tot}^z}\chi_{s_\text{tot}}^{s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}} H_0 - \frac{\gamma_{s_\text{tot}}^{s_\text{tot}^z}}{\chi_{s_\text{tot}}^{s_\text{tot}^z}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right] \\
-+ \frac{J^2}{4}\gamma_{s_\text{tot}}^{-s_\text{tot}^z}\chi_{s_\text{tot}}^{-s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}} H_0 + \frac{\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}{\chi_{s_\text{tot}}^{-s_\text{tot}^z}} s^+_\text{tot}X_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right]
+	H_\text{eff}^{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}} = H_0 + \frac{J}{2}s^z_\text{tot} + \frac{J^2}{4}\left( \frac{1}{2} + S_d^z \right) \gamma_{s_\text{tot}}^{s_\text{tot}^z}\chi_{s_\text{tot}}^{s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}} H_0 - \frac{\gamma_{s_\text{tot}}^{s_\text{tot}^z}}{\chi_{s_\text{tot}}^{s_\text{tot}^z}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right] \\
++ \frac{J^2}{4}\left( \frac{1}{2} - S_d^z \right)\gamma_{s_\text{tot}}^{-s_\text{tot}^z}\chi_{s_\text{tot}}^{-s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}} H_0 + \frac{\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}{\chi_{s_\text{tot}}^{-s_\text{tot}^z}} s^+_\text{tot}X_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	H_\text{eff}^{\frac{1}{2}, 0, 0} &= H_0\\
-	H_\text{eff}^{\frac{1}{2}, 1, 1} &= H_0 + \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{1}{E_\text{gs}} H_0 + \frac{1}{2 E_\text{gs}} s^+_\text{tot}X_{1,\text{tot}} + \frac{1}{E_\text{gs}^2} H_0^2 - \frac{1}{E_\text{gs}^3} Z_{1,\text{tot}} H_0\right] \\
-	H_\text{eff}^{\frac{1}{2}, 1, -1} &= H_0 - \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{1}{E_\text{gs}} H_0 - \frac{1}{2 E_\text{gs}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + \frac{1}{E_\text{gs}^2} H_0^2 - \frac{1}{E_\text{gs}^3} Z_{1,\text{tot}} H_0\right] \\
-	H_\text{eff}^{\frac{1}{2}, 1, 0} &= H_0 + \frac{J^2}{4}\frac{2}{E_\text{gs} + J/2}\left[1 + \frac{1}{E_\text{gs} + J/2} H_0 + \frac{1}{2 E_\text{gs} + J} \left(s^+_\text{tot}X_{1,\text{tot}} - s^-_\text{tot}X^\dagger_{1,\text{tot}}\right) \right.\\
-					 &\left.+ \frac{2}{\left(E_\text{gs} + J/2\right)^2} H_0^2 - \frac{2}{\left(E_\text{gs} + J/2\right)^3} Z_{1,\text{tot}} H_0\right] \\
+	H_\text{eff}^{\pm\frac{1}{2}, 0, 0} &= H_0\\
+	H_\text{eff}^{\pm\frac{1}{2}, 1, \pm 1} &= H_0 + \frac{J}{2}\\
+	H_\text{eff}^{-\frac{1}{2}, 1, 1} &= H_0 + \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{H_0}{E_\text{gs}} + \frac{s^+_\text{tot}X_{1,\text{tot}}}{2 E_\text{gs}} + \frac{H_0^2 }{E_\text{gs}^2} - \frac{Z_{1,\text{tot}} H_0}{E_\text{gs}^3}\right] \\
+	H_\text{eff}^{\frac{1}{2}, 1, -1} &= H_0 - \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{H_0}{E_\text{gs}}  - \frac{s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 E_\text{gs}}  + \frac{H_0^2}{E_\text{gs}^2}  - \frac{ Z_{1,\text{tot}} H_0}{E_\text{gs}^3}\right] \\
+	H_\text{eff}^{-\frac{1}{2}, 1, 0} &= H_0 + \frac{J^2}{4}\frac{2}{E_\text{gs} + J/2}\left[1 + \frac{ H_0}{E_\text{gs} + J/2} + \frac{ s^+_\text{tot}X_{1,\text{tot}}}{2 E_\text{gs} + J} + \frac{H_0^2}{\left(E_\text{gs} + J/2\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + J/2\right)^3} \right] \\
+	H_\text{eff}^{\frac{1}{2}, 1, 0} &= H_0 + \frac{J^2}{4}\frac{2}{E_\text{gs} + J/2}\left[1 + \frac{ H_0}{E_\text{gs} + J/2} - \frac{ s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 E_\text{gs} + J} + \frac{H_0^2}{\left(E_\text{gs} + J/2\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + J/2\right)^3} \right] \\
 \end{aligned}\end{equation}
@@
 	H_0^2 &= \sum_{k_1,k_2,l_1,l_2,\sigma_1,\sigma_2}\epsilon_k^{l_1}\epsilon_{k_2}^{l_2} \hat n_{k_1,\sigma_1,l_1}\hat n_{k_2,\sigma_2,l_2}\\
-	s^+_\text{tot}X_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \uparrow, l_1}c^\dagger_{q_1, \downarrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{k_2, \downarrow, l_2}c_{q_2, \uparrow, l_2}\\
-	s^-_\text{tot}X^\dagger_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \downarrow, l_1}c^\dagger_{q_1, \uparrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{q_2, \uparrow, l_2}c_{k_2, \downarrow, l_2}\\
-	Z_{1,\text{tot}} H_0 &= \sum_{k_1,q_1,k_2,\sigma_2,l_1,l_2}\left(\epsilon_{k_1}^{l_1} - \epsilon_{q_1}^{l_1}\right) \epsilon_{k_2}^{l_2} \left(c^\dagger_{k_1, \uparrow, l_1}c^\dagger_{q_1, \uparrow, l_1} - c^\dagger_{k_1, \downarrow, l_1}c^\dagger_{q_1, \downarrow, l_1}\right) \hat n_{k_2,\sigma_2,l_2}\\
+	s^+_\text{tot}X_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \uparrow, l_1}c_{q_1, \downarrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{k_2, \downarrow, l_2}c_{q_2, \uparrow, l_2}\\
+	s^-_\text{tot}X^\dagger_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \downarrow, l_1}c_{q_1, \uparrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{q_2, \uparrow, l_2}c_{k_2, \downarrow, l_2}\\
+	Z_{1,\text{tot}} H_0 &= \sum_{k_1,q_1,k_2,\sigma_2,l_1,l_2}\left(\epsilon_{k_1}^{l_1} - \epsilon_{q_1}^{l_1}\right) \epsilon_{k_2}^{l_2} \left(c^\dagger_{k_1, \uparrow, l_1}c_{q_1, \uparrow, l_1} - c^\dagger_{k_1, \downarrow, l_1}c_{q_1, \downarrow, l_1}\right) \hat n_{k_2,\sigma_2,l_2}\\
 \end{aligned}\end{equation}

### 2021-11-16 multi-channel-urg.tex
derived eff Ham from K=2 dgnrt. Schr eqtn, dgnrc makes no diff

--- 2021-11-15 multi-channel-urg.tex
@@
-\documentclass[10pt]{revtex4-2}
+\documentclass{revtex4-2}
 \usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
@@
 This behaviour is shown schematically in fig.~\ref{rg_flow_general}. 
-In fig.~\ref{rhomin_vs_D}, we plot \(\rho_\text{min}\) against the bare bandwidth.
-For large \(D_0\), it essentially shrinks to zero, and the numerator becomes the first fixed point for essentially all \(\rho\).
 \begin{figure}[!htb]
 	\centering
-	\includegraphics[width=0.7\textwidth]{./rhomin_D.pdf}
+	\includegraphics[width=0.5\textwidth]{./rhomin_D.pdf}
 	\caption{Red curve shows variation of \(\rho_\text{min}\) against \(D_0\).
@@
 \end{figure}
+In fig.~\ref{rhomin_vs_D}, we plot \(\rho_\text{min}\) against the bare bandwidth.
+For large \(D_0\), it essentially shrinks to zero, and the numerator becomes the first fixed point for essentially all \(\rho\).
 
@@
 
-\section{Derivation of low energy effective Hamiltonian \((k-\text{space})\)}
-Fixed point Hamiltonian is
+\section{Derivation of low energy effective \(k-\)space Hamiltonian }
+The fixed point Hamiltonian is
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
-	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_V
+	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_{V + V^\dagger}
 \end{aligned}\end{equation}
+We define \(V\) as the interaction term that decreases \(s_\text{tot}^z\) by 1: \(V \ket{s_\text{tot}^z} \to \ket{s_\text{tot}^z - 1}\).
+Similarly, we define \(V^\dagger \ket{s_\text{tot}^z} \to \ket{s_\text{tot}^z + 1}\).
 The effective Hamiltonian that has the states \(\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}\) as eigenstates are
@@
 \end{aligned}\end{equation}
-We can easily simplify the \(S_d^z\) in the denominator, because \(S_d^\pm \frac{1}{A + B S_d^z} = S_d^\pm \frac{1}{A \mp \frac{1}{2}B}\).
+This is obtained from the Schrodinger equation for the ground state. If we expand the ground state in terms of \(\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}\), we have 
 \begin{equation}\begin{aligned}
-	H_\text{eff} = \sum_{k,l,\sigma}\epsilon_{k,l}\hat n_{k\sigma,l} + J S_d^z s_\text{tot}^z + \frac{J^2}{4} s_\text{tot}^- \frac{\frac{1}{2} + S_d^z}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^+ + \frac{J^2}{4} s_\text{tot}^+ \frac{\frac{1}{2} - S_d^z}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^-
+	\label{gstate_Expand}
+\ket{\Psi_\text{gs}} = \sum_{S_d^z, s_\text{tot},s_\text{tot}^z}C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}
+\end{aligned}\end{equation}
+The Schrodinger equation for the ground state can be written as
+\begin{equation}\begin{aligned}
+	E_\text{gs}\ket{\Psi_\text{gs}} = H \ket{\Psi_\text{gs}} = \left(H_d + V\right)\ket{\Psi_\text{gs}} \implies \left(E_\text{gs} - H_d\right)\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z} = V\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}
+\end{aligned}\end{equation}
+Since \(V\) only changes \(S_d^z \to -S_d^z\) and \(s^z_\text{tot} \to s^z_\text{tot} \pm 1\), we can simplify the equation into individual smaller equations.
+Let us take the case of two-channel, where the possible states are \(s_\text{tot},s^z_\text{tot} = (0,0), (1,-1), (1,0), (1,1)\).
+The individual equations for this model are
+\begin{gather}
+	\left(E_\text{gs} - H_d\right) \ket{S_d^z, 0, 0} = \left(E_\text{gs} - H_d\right) \ket{-\frac{1}{2}, 1, -1} = \left(E_\text{gs} - H_d\right) \ket{\frac{1}{2}, 1, 1}  = 0 \label{no_V}\\
+	\left(E_\text{gs} - H_d\right) C_{\frac{1}{2}, 1, -1}\ket{\frac{1}{2}, 1, -1} = V C_{-\frac{1}{2}, 1, 0}\ket{-\frac{1}{2}, 1, 0}\label{eq2}\\
+	\left(E_\text{gs} - H_d\right) C_{-\frac{1}{2}, 1, 0}\ket{-\frac{1}{2}, 1, 0} = V^\dagger C_{\frac{1}{2}, 1, -1}\ket{\frac{1}{2}, 1, -1}\label{eq3.2}\\
+	\left(E_\text{gs} - H_d\right) C_{\frac{1}{2}, 1, 0}\ket{\frac{1}{2}, 1, 0} = V C_{-\frac{1}{2}, 1, 1}\ket{-\frac{1}{2}, 1, 1} \label{eq3.1}\\
+	\left(E_\text{gs} - H_d\right) C_{-\frac{1}{2}, 1, 1}\ket{-\frac{1}{2}, 1, 1} = V^\dagger C_{\frac{1}{2}, 1, 0}\ket{\frac{1}{2}, 1, 0}\label{eq4}
+\end{gather}
+From eqs.~\ref{eq2} and \ref{eq4}, we can write
+\begin{equation}\begin{aligned}
+	C_{\frac{1}{2}, 1, -1}\ket{\frac{1}{2}, 1, -1} &= C_{-\frac{1}{2}, 1, 0}\frac{1}{E_\text{gs} - H_d}V \ket{-\frac{1}{2}, 1, 0}, &&C_{-\frac{1}{2}, 1, 1}\ket{-\frac{1}{2}, 1, 1} = C_{\frac{1}{2}, 1, 0}\frac{1}{E_\text{gs} - H_d}V^\dagger \ket{\frac{1}{2}, 1, 0}
+\end{aligned}\end{equation}
+Substituting these into eqs.~\ref{eq3.1} and \ref{eq3.2} gives 
+\begin{equation}\begin{aligned}
+	\label{eff_ham_Sdz_10}
+	E_\text{gs} \ket{\frac{1}{2}, 1, 0} &= \left(H_d + V \frac{1}{E_\text{gs} - H_d}V^\dagger\right) \ket{\frac{1}{2}, 1, 0}\\
+	E_\text{gs} \ket{-\frac{1}{2}, 1, 0} &= \left(H_d + V^\dagger \frac{1}{E_\text{gs} - H_d} V\right) \ket{-\frac{1}{2}, 1, 0}\\
+\end{aligned}\end{equation}
+These equations represent the Schrodinger equation for the states \(\ket{S_d^z, 1, 0}\), and the right hand sides therefore give the effective Hamiltonians for those states.
+If we combine the states into a single subspace \(\ket{1,0}= \left\{\ket{\frac{1}{2}, 1, 0}, \ket{-\frac{1}{2}, 1, 0}\right\}\), the effective Hamiltonian for this composite subspace becomes the sum of the two parts:
+\begin{equation}\begin{aligned}
+	\label{eff_ham_10}
+	H_\text{eff}\ket{1, 0}\bra{1, 0} = \left(H_d + V G_0 V^\dagger + V^\dagger G_0  V\right) \ket{1, 0}
+\end{aligned}\end{equation}
+where \(G_0 = \left(E_\text{gs} - H_d\right)^{-1}\).
+If we expand the subspace as \(\ket{1,0} = \ket{\frac{1}{2}, 1, 0} + \ket{-\frac{1}{2}, 1, 0}\), we recover eqs.~\ref{eff_ham_Sdz_10}.
+Solving similarly for the other states gives
+\begin{equation}\begin{aligned}
+	H_\text{eff}\ket{1,  1}\bra{1,  1} &= \left(H_d + V^\dagger G_0  V\right) \ket{1,  1}\\
+	H_\text{eff}\ket{1, - 1}\bra{1, - 1} &= \left(H_d + V G_0 V^\dagger\right) \ket{1, - 1}
+\end{aligned}\end{equation}
+\textit{One important conclusion that comes out of these calculations is that if the ground state is degenerate, the effective Hamiltonians is independent of which ground state we choose to start from in eq.~\ref{gstate_Expand}.
+This is because the only difference in the various degenerate ground states is in the coefficients \(C_{S_d^z, s_\text{tot},s_\text{tot}^z}\).
+Since the final effective Hamiltonians are independent of these coefficients, they will be the same irrespective of which ground state we start with.}
+
+To calculate these effective Hamiltonians, we will calculate the individual terms.
+We can easily simplify the \(S_d^z\) in the denominator of \(G_0\), because \(S_d^\pm \frac{1}{A + B S_d^z} = S_d^\pm \frac{1}{A \mp \frac{1}{2}B}\):
+\begin{equation}\begin{aligned}
+	V G_0 V^\dagger = \frac{J^2}{4} s_\text{tot}^- \frac{\frac{1}{2} + S_d^z}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^+ \\
+	V^\dagger G_0 V = \frac{J^2}{4} s_\text{tot}^+ \frac{\frac{1}{2} - S_d^z}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^-
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	 s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^+ =  s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0\right] s_\text{tot}^+\\
-	 s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^- =  s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0\right] s_\text{tot}^-
+	 V G_0 V^\dagger =  s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 + \ldots\right] s_\text{tot}^+\\
+	 V^\dagger G_0 V =  s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 + \ldots\right] s_\text{tot}^-
 \end{aligned}\end{equation}
@@
 One of the \(n=2\) terms gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	&s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^+\\
@@
 	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 \left[s_\text{tot}^- s_\text{tot}^+H_0\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 - s_\text{tot}^-\left(X^\dagger_{1,\text{tot}}\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 + H_0\frac{1}{E_\text{gs} + \frac{J}{2}s_\text{tot}^z}X^\dagger_\text{1,tot}\right)\right] \\
-\end{aligned}\end{equation}
+\end{align}
 At this point, we need the commutator between \(H_0\) and \(s_\text{tot}^z\):
@@
 	& \left.- s_\text{tot}^-\left(X^\dagger_{1,\text{tot}}\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 + H_0\frac{1}{E_\text{gs} + \frac{J}{2}s_\text{tot}^z}X^\dagger_\text{1,tot}\right)\right] \\
-	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 \left[s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 H_0 - s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} Z_{1,\text{tot}} H_0\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)}\right]\\
+	&= \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 s_\text{tot}^- s_\text{tot}^+ \left[\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} H_0 H_0 - \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)} Z_{1,\text{tot}} H_0\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z+1\right)}\right]
 \end{align}
 At the last step, we dropped the three-particle scattering terms.
-If we look at the effective Hamiltonian for a state \(\ket{S_d^z=\frac{1}{2}, s_\text{tot}, s^z_\text{tot}}\), we can replace the following operators with scalars:
+
+The other \(n=2\) term gives
+\begin{align}
+	&s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^-\\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+ H_0 \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^- \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+ H_0 \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\left(s_\text{tot}^- H_0 + X_\text{1,tot}\right) \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 \left[s_\text{tot}^+ H_0 s_\text{tot}^-\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0 + s_\text{tot}^+ H_0\frac{1}{E_\text{gs} - \frac{J}{2}s_\text{tot}^z}X_\text{1,tot}\right] \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+ \left(s_\text{tot}^- H_0 + X_\text{1,tot}\right)\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0 \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 \left[s_\text{tot}^+s_\text{tot}^- H_0 \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0\right] \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+s_\text{tot}^- \left[\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0^2 - \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} Z_{1,\text{tot}} \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} H_0 \right] \\
+	&= \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 s_\text{tot}^+s_\text{tot}^- \left[H_0^2 \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} - \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} Z_{1,\text{tot}} H_0 \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} \right]
+\end{align}
+
+If we look at the effective Hamiltonian for a subspace \(\ket{s_\text{tot}, s^z_\text{tot}}\), we can replace the following operators with scalars:
 \begin{gather}
 	\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)} = \gamma_{s_\text{tot}}^{s_\text{tot}^z}\\
-	s_\text{tot}^- s_\text{tot}^+ = s_\text{tot}\left(s_\text{tot} + 1\right) - s^z_\text{tot}\left(s^z_\text{tot} + 1\right) = \chi_{s_\text{tot}}^{s_\text{tot}^z}
+	\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)} = \gamma_{s_\text{tot}}^{-s_\text{tot}^z},\\
+	s_\text{tot}^- s_\text{tot}^+ = s_\text{tot}\left(s_\text{tot} + 1\right) - s^z_\text{tot}\left(s^z_\text{tot} + 1\right) = \chi_{s_\text{tot}}^{s_\text{tot}^z}\\
+	s_\text{tot}^+ s_\text{tot}^- = s_\text{tot}\left(s_\text{tot} + 1\right) - s^z_\text{tot}\left(s^z_\text{tot} - 1\right) = \chi_{s_\text{tot}}^{-s_\text{tot}^z}
 \end{gather}
-The effective Hamiltonian for this state becomes
+They are not all independent: \(\left(\gamma_{s_\text{tot}}^{s_\text{tot}^z}\right)^{-1} + \left(\gamma_{s_\text{tot}}^{-s_\text{tot}^z}\right)^{-1} =  E_\text{gs} + J, \chi_{s_\text{tot}}^{s_\text{tot}^z} - \chi_{s_\text{tot}}^{-s_\text{tot}^z} = -2 s^z_\text{tot}\).
+For the two-channel problem, we have four possible states in total: \(\left( s_\text{tot}, s_\text{tot}^z \right) = \left\{ (0,0), (1,-1), (1,0), (1,1) \right\} \).
+The states in the eq.~\ref{no_V} cannot be acted on by \(V\) or \(V^\dagger\), so the effective Hamiltonian for these states will consist of only the diagonal part:
 \begin{equation}\begin{aligned}
-	H_\text{eff}\ket{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}}\bra{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}} = H_0 + \frac{J}{2}s^z_\text{tot} + \frac{J^2}{4}\gamma_{s_\text{tot}}^{s_\text{tot}^z}\chi_{s_\text{tot}}^{s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}} H_0 - \frac{\gamma_{s_\text{tot}}^{s_\text{tot}^z}}{\chi_{s_\text{tot}}^{s_\text{tot}^z}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right]
+	H_\text{eff} = H_0 + \frac{J}{2}s^z_\text{tot}
+\end{aligned}\end{equation}
+The factors \(\gamma\) and \(\chi\) for the other states are
+\begin{equation}\begin{aligned}
+	s_\text{tot}, s_\text{tot}^z = && (1,-1), && (1,0), && (1,1)\\
+	\gamma_{s_\text{tot}}^{s_\text{tot}^z} = && \frac{1}{E_\text{gs}}, && \frac{1}{E_\text{gs} + J/2}, && -- \\
+	\chi_{s_\text{tot}}^{s_\text{tot}^z} = && 2, && 2, && --\\
+	\gamma_{s_\text{tot}}^{-s_\text{tot}^z} = && --, && \frac{1}{E_\text{gs} + J/2}, && \frac{1}{E_\text{gs}}\\
+	\chi_{s_\text{tot}}^{-s_\text{tot}^z} = && --, && 2, && 2\\
+\end{aligned}\end{equation}
+The effective Hamiltonians for these states are:
+\begin{align}
+	H_\text{eff}^{1, 1} &= H_0 + J S_d^z + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{H_0}{E_\text{gs}} + \frac{s^+_\text{tot}X_{1,\text{tot}}}{2 E_\text{gs}} + \frac{H_0^2 }{E_\text{gs}^2} - \frac{Z_{1,\text{tot}} H_0}{E_\text{gs}^3}\right] \left(\frac{1}{2} - S_d^z\right) \\
+	H_\text{eff}^{1, -1} &= H_0 - J S_d^z + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{H_0}{E_\text{gs}}  - \frac{s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 E_\text{gs}}  + \frac{H_0^2}{E_\text{gs}^2}  - \frac{ Z_{1,\text{tot}} H_0}{E_\text{gs}^3}\right] \left(\frac{1}{2} + S_d^z\right) \\
+	H_\text{eff}^{1, 0} &= H_0 + \frac{J^2}{2\left(E_\text{gs} + J/2\right)}\left[1 + \frac{ H_0 + \left(1/2 + S_d^z\right) s^+_\text{tot}X_{1,\text{tot}} - \left(1/2 - S_d^z\right) s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 \left(E_\text{gs} + J/2\right)} + \frac{H_0^2}{\left(E_\text{gs} + J/2\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + J/2\right)^3} \right] \\
+\end{align}
+The terms have the following meanings:
+\begin{equation}\begin{aligned}
+	H_0 &= \sum_{k,\sigma,l}\epsilon_k^l \hat n_{k,\sigma,l}\\
+	H_0^2 &= \sum_{k_1,k_2,l_1,l_2,\sigma_1,\sigma_2}\epsilon_k^{l_1}\epsilon_{k_2}^{l_2} \hat n_{k_1,\sigma_1,l_1}\hat n_{k_2,\sigma_2,l_2}\\
+	s^+_\text{tot}X_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \uparrow, l_1}c_{q_1, \downarrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{k_2, \downarrow, l_2}c_{q_2, \uparrow, l_2}\\
+	s^-_\text{tot}X^\dagger_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \downarrow, l_1}c_{q_1, \uparrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{q_2, \uparrow, l_2}c_{k_2, \downarrow, l_2}\\
+	Z_{1,\text{tot}} H_0 &= \sum_{k_1,q_1,k_2,\sigma_2,l_1,l_2}\left(\epsilon_{k_1}^{l_1} - \epsilon_{q_1}^{l_1}\right) \epsilon_{k_2}^{l_2} \left(c^\dagger_{k_1, \uparrow, l_1}c_{q_1, \uparrow, l_1} - c^\dagger_{k_1, \downarrow, l_1}c_{q_1, \downarrow, l_1}\right) \hat n_{k_2,\sigma_2,l_2}\\
 \end{aligned}\end{equation}

### 2021-11-17 multi-channel-urg.tex
obtained partition function of general K-channel star graph problem in pursuit of chi

@@
 \begin{equation}\begin{aligned}
-	H^* = H_0 + J^*\sum_{l} \vec{S_d}\cdot\vec{s_\text{tot}}
+	H^* = H_0 + J^* \vec{S_d}\cdot\vec{s_\text{tot}}
 \end{aligned}\end{equation}
@@
 
+\section{Susceptibility from zero-mode fixed-point Hamiltonian}
+The zero-mode approximation of the fixed-point Hamiltonian is a star graph Hamiltonian:
+\begin{equation}\begin{aligned}
+	H = J^* \vec{S_d}\cdot\vec{s}_\text{tot}
+\end{aligned}\end{equation}
+where \(\vec s_\text{tot} = \sum_l \vec s_l\) is the total spin operator for all the channels.
+We insert a magnetic field that acts only on the impurity and then attempt to diagonalize the Hamiltonian.
+\begin{equation}\begin{aligned}
+	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h S_d^z
+\end{aligned}\end{equation}
+The Hamiltonian commutes with \(s_\text{tot}^2\):
+\begin{equation}\begin{aligned}
+\left[s_\text{tot}^2, H(h)\right] = \left[\sum_{i=x,y,z}{s^i_\text{tot}}^2, J^* \sum_{i=x,y,z} S_d^i s^i_\text{tot}\right] = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, \left[s_\text{tot}^i,s_\text{tot}^j\right]\right\} = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, i \epsilon^{ijk}s^k_\text{tot}\right\} = 0
+\end{aligned}\end{equation}
+This means the Hamiltonian is already block-diagonal in the quantum number \(s_\text{tot}\).
+Let us represent the quantum number of \(s_\text{tot}^z\) by \(m\).
+For a particular \(s_\text{tot}\), \(m\) can take values from the set \(\left[-s_\text{tot}, s_\text{tot}\right] \).
+The spin \(S_d^z\) can also take values \(\pm \frac{1}{2}\).
+From now on, we will assume we are in the subspace of a particular \(s_\text{tot} = M\), so we will ignore that quantum number and write the kets simply as \(\ket{S_d^z, m}\).
+So, the notation \(\ket{\uparrow,-1}\) means the state with \(S_d^z = \frac{1}{2}\) and \(m = -1\).
+We will now show that even inside the block of \(2\times s_\text{tot}\) (or \(2\times s_\text{tot} + 1\), depending on where it is odd or even) defined by a particular value of \(s_\text{tot}\), the Hamiltonian actually separates into decoupled \(2\times 2\) blocks.
+To see why, first note that the terminal states \(\ket{\downarrow, -M}\) and \(\ket{\uparrow, M}\) are already eigenstates, because they cannot scatter (the impurity can only flip down, and this would require the bath to flip up, but \(s^z_\text{tot}\) is already at its maximum value \(M\)).
+The other \(2M - 2\) states can be organized into \(2\times 2\) blocks formed by the states \(\ket{\uparrow, m}\) and \(\ket{\downarrow, m+1}\) for \(m \in \left[-M+1, M-2\right] \).
+The fact that this block does not interact with the other blocks can be observation: if there was some other state which when acted upon by the Hamiltonian gave a non-zero projection on \(\ket{\uparrow, m}\), it would have to come from \(S_d^z = \downarrow\), and this would mean the bath spin would have had to flip down.
+This means the bath spin in that state would have to be \(m+1\), and that is precisely the other state in the block.
+
+Defining \(\epsilon^h_m = \frac{1}{2}\left(Jm + h\right) \), the \(2\times 2\) blocks can be written as
+\begin{equation}\begin{aligned}
+	H_m = \begin{pmatrix} \epsilon^h_m & J/2 \\ J/2 & -\left( \epsilon^h_m + J \right)   \end{pmatrix} 
+\end{aligned}\end{equation}
+The eigenvalues are 
+\begin{equation}\begin{aligned}
+	\lambda_{m, \pm}^M(h) = \frac{1}{2}\left[-J \pm \sqrt{2J^2 + 4\epsilon^h_m\left(\epsilon^h_m + J\right) }\right] 
+\end{aligned}\end{equation}
+The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\). The partition function is
+\begin{equation}\begin{aligned}
+	Z(h) = \sum_{M}\left[\sum_{m=-M+1}^{M-1}e^{-\beta \lambda_{m, \pm}^M(h)} + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] 
+\end{aligned}\end{equation}
+
 \appendix

### 2021-11-18 multi-channel-urg.tex
computed first derivative of Z

@@
 \begin{equation}\begin{aligned}
-	\lambda_{m, \pm}^M(h) = \frac{1}{2}\left[-J \pm \sqrt{2J^2 + 4\epsilon^h_m\left(\epsilon^h_m + J\right) }\right] 
+	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J \pm \sqrt{2J^2 + 4\epsilon^h_m\left(\epsilon^h_m + J\right) }\right] = \frac{1}{2}\left[-J \pm \sqrt{J^2 + 4\left(\epsilon^h_m + J/2\right)^2 }\right]= \frac{1}{2}\left[-J \pm \sqrt{J^2 + 4\alpha^2 }\right]
 \end{aligned}\end{equation}
+where \(\alpha = \epsilon^h_m + J/2\).
 The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\). The partition function is
 \begin{equation}\begin{aligned}
-	Z(h) = \sum_{M}\left[\sum_{m=-M+1}^{M-1}e^{-\beta \lambda_{m, \pm}^M(h)} + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] 
+	Z(h) = \sum_{M}\left[\sum_{m=-M+1}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] 
+\end{aligned}\end{equation}
+
+To calculate the impurity magnetic susceptibility, we will use the expression
+\begin{equation}\begin{aligned}
+	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z(h)^{\prime\prime}}{Z(h)} - \left(\frac{Z(h)^{\prime}}{Z(h)}\right)^2 \right] 
+\end{aligned}\end{equation}
+where the \(\prime\) indicates derivative with respect to \(h\). We will now calculate these derivatives. For that we will need
+\begin{gather}
+	\frac{\:\mathrm{d}\epsilon_m^h}{\:\mathrm{d}h} = \frac{1}{2} = \frac{\:\mathrm{d}\alpha}{\:\mathrm{d}h}\\
+	\frac{\:\mathrm{d}\lambda_{m,\pm}^{M, h}}{\:\mathrm{d}h} = \pm\frac{\alpha}{\sqrt{J^2 + 4\alpha^2}}
+\end{gather}
+We are now ready to compute the derivatives of \(Z\):
+\begin{equation}\begin{aligned}
+	Z(h)^\prime &= -\beta\sum_{M}\left[\sum_{m=-M+1}^{M-1}\frac{\left(e^{-\beta \lambda_{m, +}^{M,h}} - e^{-\beta \lambda_{m, -}^{M,h}}\right)\left(\epsilon^h_m + J/2\right)}{\sqrt{2J^2 + 4\epsilon^h_m\left(\epsilon^h_m + J\right) }} + \frac{1}{2}\left(e^{-\beta \epsilon^h_{M}} - e^{\beta \epsilon^h_{- M}}\right)\right] \\
+		    &= \beta\sum_{M}\left[\sum_{m=-M+1}^{M-1}2e^{\beta J/2}\frac{\alpha\sinh \sqrt{J^2 + 4\alpha^2} }{\sqrt{J^2 + 4\alpha^2}} + e^{-\beta JM/2}\sinh \left(\beta h/2\right)\right] \\
 \end{aligned}\end{equation}

### 2021-11-18 multi-channel-urg.tex
obtained general susceptibility for K channel as well as explicit expression for two channel. the two channel goes as 1/T as T to 0

--- 2021-11-17 multi-channel-urg.tex
@@
 To see why, first note that the terminal states \(\ket{\downarrow, -M}\) and \(\ket{\uparrow, M}\) are already eigenstates, because they cannot scatter (the impurity can only flip down, and this would require the bath to flip up, but \(s^z_\text{tot}\) is already at its maximum value \(M\)).
-The other \(2M - 2\) states can be organized into \(2\times 2\) blocks formed by the states \(\ket{\uparrow, m}\) and \(\ket{\downarrow, m+1}\) for \(m \in \left[-M+1, M-2\right] \).
+The other \(2M - 2\) states can be organized into \(2\times 2\) blocks formed by the states \(\ket{\uparrow, m}\) and \(\ket{\downarrow, m+1}\) for \(m \in \left[-M, M-1\right] \).
 The fact that this block does not interact with the other blocks can be observation: if there was some other state which when acted upon by the Hamiltonian gave a non-zero projection on \(\ket{\uparrow, m}\), it would have to come from \(S_d^z = \downarrow\), and this would mean the bath spin would have had to flip down.
@@
 \begin{equation}\begin{aligned}
-	H_m = \begin{pmatrix} \epsilon^h_m & J/2 \\ J/2 & -\left( \epsilon^h_m + J \right)   \end{pmatrix} 
+	H_m = \begin{pmatrix} \epsilon^h_m & J/2 \\ J/2 & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} 
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\lambda_{m, \pm}^M(h) = \frac{1}{2}\left[-J \pm \sqrt{2J^2 + 4\epsilon^h_m\left(\epsilon^h_m + J\right) }\right] 
+	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{5J^2/4 + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2 + 4\left(\epsilon^h_m + J/4\right)^2 }\right]= -J/4 \pm \sqrt{J^2/4 + \alpha^2}
 \end{aligned}\end{equation}
+where \(\alpha = \epsilon^h_m + J/4\).
 The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\). The partition function is
 \begin{equation}\begin{aligned}
-	Z(h) = \sum_{M}\left[\sum_{m=-M+1}^{M-1}e^{-\beta \lambda_{m, \pm}^M(h)} + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] 
+	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
+	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
 \end{aligned}\end{equation}
+where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\).
+To calculate the impurity magnetic susceptibility, we will use the expression
+\begin{equation}\begin{aligned}
+	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z(h)^{\prime\prime}}{Z(h)} - \left(\frac{Z(h)^{\prime}}{Z(h)}\right)^2 \right] 
+\end{aligned}\end{equation}
+where the \(\prime\) indicates derivative with respect to \(h\). We will now calculate these derivatives. For that we w11ill need
+\begin{gather}
+	\frac{\:\mathrm{d}\epsilon_m^h}{\:\mathrm{d}h} = \frac{1}{2} = \frac{\:\mathrm{d}\alpha}{\:\mathrm{d}h}\\
+	\frac{\:\mathrm{d}\lambda_{m,\pm}^{M, h}}{\:\mathrm{d}h} = \pm\frac{\alpha}{\sqrt{J^2 + 4\alpha^2}}
+\end{gather}
+We are now ready to compute the derivatives of \(Z\):
+\begin{equation}\begin{aligned}
+	\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta J/4}\frac{\alpha\sinh \beta\sqrt{J^2/4 + \alpha^2} }{\sqrt{J^2/4 + \alpha^2}} + e^{-\beta JM/2}\sinh \left(\beta h/2\right)\right] \\
+	\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}\left[\frac{1}{2}\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\frac{e^{\beta J/4}}{\sqrt{J^2/4 + \alpha^2}}\left(\sinh \beta\sqrt{J^2/4 + \alpha^2} + \beta\alpha^2 \frac{\cosh\beta\sqrt{J^2/4 + \alpha^2}}{\sqrt{J^2/4 + \alpha^2}} - \frac{\alpha^2 \sinh \beta\sqrt{J^2/4 + \alpha^2}}{J^2/4 + \alpha^2}\right)\right.\\
+						   &\quad \quad\quad \quad\left.+ e^{-\beta JM/2}\frac{\beta}{2}\cosh \left(\beta h/2\right)\right] \\
+\end{aligned}\end{equation}
+We will now take the limit of \(h \to 0\). Note that \(\alpha(h\to 0)=\frac{J}{2}(m+1/2)\) and hence \((J^2/4 + \alpha^2)(h \to 0) = \frac{J^2}{4}\left[1 + (m+1/2)^2\right] \).
+\begin{equation}\begin{aligned}
+	\lim_{h \to 0}Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta \frac{J}{2}\sqrt{1 + (m+1/2)^2} + 2e^{-\beta JM/2}\right] \\
+	\lim_{h \to 0}\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} &=  \beta\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta J/4}(m+1/2)\frac{\sinh \beta\frac{J}{2}\sqrt{1 + (m+1/2)^2} }{\sqrt{1 + (m+1/2)^2}}\right] \\
+	\lim_{h \to 0}\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}\left[\frac{1}{2}\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\frac{e^{\beta J/4}}{\frac{J}{2}\sqrt{1 + (m+1/2)^2}}\left(\sinh \beta\frac{J}{2}\sqrt{1 + (m+1/2)^2} + \beta \frac{J}{2}(m+1/2)^2 \frac{\cosh\beta\frac{J}{2}\sqrt{1 + (m+1/2)^2}}{\sqrt{1 + (m+1/2)^2}} \right.\right.\\
+						   &\quad \quad\quad \quad\left.\left. - \frac{(m+1/2)^2 \sinh \beta\frac{J}{2}\sqrt{1 + (m+1/2)^2}}{1 + (m+1/2)^2}\right)+ e^{-\beta JM/2}\frac{\beta}{2}\right]
+\end{aligned}\end{equation}
+Since the final expressions are formidable, we write down the expressions specifically for the single-channel and two-channel models.
+For single-channel, we have \(M=\frac{1}{2}\) and \(m = \pm \frac{1}{2}\).
+The terminal states are \(S_d^z=-1/2, m=-1/2\) and \(S_d^z=1/2, m=1/2\).
+There is therefore just one \(2\times 2\) block, and that is at \(m=-1/2\).
+\begin{gather}
+	\lim_{h \to 0}Z(h) = 2e^{\beta J/4}\cosh \beta \frac{J}{2} + 2e^{-\beta J/4} \\
+	\lim_{h \to 0}\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} = 0 \\
+	\lim_{h \to 0}\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} = \frac{\beta}{J}\left(e^{\beta J/4}\sinh \beta\frac{J}{2} + e^{-\beta J/4}\frac{J \beta}{2}\right)\\
+	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z(h)^{\prime\prime}}{Z(h)} - \left(\frac{Z(h)^{\prime}}{Z(h)}\right)^2 \right] = \frac{1}{J}\frac{\left(2e^{\beta J/2}\sinh \beta\frac{J}{2} + J \beta\right)}{4e^{\beta J/2}\cosh \beta \frac{J}{2} + 4}
+\end{gather}
+This expression matches with the direct calculation of the susceptibility of the single-channel Kondo model.
+
+For \(K=2\), we have \(M = 0,1\).
+For \(M=0\) there is no scattering and the only eigenvalue is 0.
+For \(M=1\), we have \(m=-1,0,1\).
+The terminal states are \(m=-1, S_d^z=-\frac{1}{2}\) and \(m=1, S_d^z=+\frac{1}{2}\).
+The scattering blocks are \(m=-\frac{1}{2}\) and \(m=0\).
+This means that \((m+1/2)^2 = 1/4\) for all relevant \(m\).
+Substituting all this in the expressions gives
+\begin{equation}\begin{aligned}
+	\lim_{h \to 0}Z(h) &= 2 + 2e^{-\beta J/2} + 2e^{\beta J/4}\sum_{m=-1,0}\cosh \beta \frac{J}{2}\sqrt{1 + (m+1/2)^2} = 2\left(1 + e^{-\beta J/2}\right) + 4e^{\beta J/4}\cosh \frac{\beta J\sqrt 5}{4}\\
+	\lim_{h \to 0}\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} &= \beta\sum_{m=-1,0}e^{\beta J/4}(m+1/2)\frac{\sinh \beta\frac{J}{2}\sqrt{1 + (m+1/2)^2} }{\sqrt{1 + (m+1/2)^2}} = 0\\
+	\lim_{h \to 0}\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \frac{\beta^2}{2}\left(1 + e^{-\beta J/2}\right)+ \frac{\beta}{J}\frac{e^{\beta J/4}}{5}\left(\frac{16}{\sqrt 5}\sinh \beta\frac{J\sqrt 5}{4} + \beta J \cosh\beta\frac{J\sqrt 5}{4}\right)\\
+	\chi &= \frac{\frac{\beta}{2}+ \frac{1}{J}\frac{e^{\beta J/4}}{5\left(1 + e^{-\beta J/2}\right)}\left(\frac{16}{\sqrt 5}\sinh \beta\frac{J\sqrt 5}{4} + \beta J \cosh\beta\frac{J\sqrt 5}{4}\right)}{2 + 4\frac{e^{\beta J/4}}{\left(1 + e^{-\beta J/2}\right)}\cosh \frac{\beta J\sqrt 5}{4}}
+\end{aligned}\end{equation}
+
+The low temperature behaviour is \(\chi(T\to 0) \sim 1/T\).
 

### 2021-11-21 notes/multi-channel-urg.tex
completed the chi analytic derivation, compared with numerical results and obtained low and high temperature limits

--- 2021-11-18 multi-channel-urg.tex
@@
 \usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
+\usepackage[margin=0.2in]{geometry}
 \numberwithin{equation}{section}
@@
 
-Defining \(\epsilon^h_m = \frac{1}{2}\left(Jm + h\right) \), the \(2\times 2\) blocks can be written as
+Defining \(\epsilon^h_m = \frac{1}{2}\left(Jm + h\right) \) and \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
 \begin{equation}\begin{aligned}
-	H_m = \begin{pmatrix} \epsilon^h_m & J/2 \\ J/2 & -\left( \epsilon^h_m + J \right)   \end{pmatrix} 
+	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} 
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J \pm \sqrt{2J^2 + 4\epsilon^h_m\left(\epsilon^h_m + J\right) }\right] = \frac{1}{2}\left[-J \pm \sqrt{J^2 + 4\left(\epsilon^h_m + J/2\right)^2 }\right]= \frac{1}{2}\left[-J \pm \sqrt{J^2 + 4\alpha^2 }\right]
+	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}
 \end{aligned}\end{equation}
-where \(\alpha = \epsilon^h_m + J/2\).
+where \(\alpha = \epsilon^h_m + J/4\).
 The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\). The partition function is
 \begin{equation}\begin{aligned}
-	Z(h) = \sum_{M}\left[\sum_{m=-M+1}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] 
+	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
+	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+\end{aligned}\end{equation}
+where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\).
+This is yet not the complete partition function, because we have not accounted for the possibility that there multiple subspaces of \(M\).
+For example, the \(K=3\) case states can be obtained by adding the third spin-half onto the states \(S=0,1\).
+\(S=0\) gives \(s_\text{tot}=1/2\) and \(S=1\) gives \(s_\text{tot} = 1/2, 3/2\).
+So, \(s_\text{tot} = 1/2\) appears twice.
+These two subspaces are actually orthogonal, because the quantum numbers for the individual channels are different.
+We need to count the number of instances of a particular subspace \(s_\text{tot}=M\).
+It turns out that this number is given by
+\begin{equation}\begin{aligned}
+	r^K_M = {}^{K-1}C_{K/2 - M}
+\end{aligned}\end{equation}
+which means the correct partition function is
+\begin{equation}\begin{aligned}
+	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	Z(h)^\prime &= -\beta\sum_{M}\left[\sum_{m=-M+1}^{M-1}\frac{\left(e^{-\beta \lambda_{m, +}^{M,h}} - e^{-\beta \lambda_{m, -}^{M,h}}\right)\left(\epsilon^h_m + J/2\right)}{\sqrt{2J^2 + 4\epsilon^h_m\left(\epsilon^h_m + J\right) }} + \frac{1}{2}\left(e^{-\beta \epsilon^h_{M}} - e^{\beta \epsilon^h_{- M}}\right)\right] \\
-		    &= \beta\sum_{M}\left[\sum_{m=-M+1}^{M-1}2e^{\beta J/2}\frac{\alpha\sinh \sqrt{J^2 + 4\alpha^2} }{\sqrt{J^2 + 4\alpha^2}} + e^{-\beta JM/2}\sinh \left(\beta h/2\right)\right] \\
+	\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta J/4}\alpha\frac{\sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2} }{\sqrt{J^2x^M_m/4 + \alpha^2}} + e^{-\beta JM/2}\sinh \left(\beta h/2\right)\right] \\
+	\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\frac{1}{2}\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\frac{e^{\beta J/4}}{\sqrt{J^2x^M_m/4 + \alpha^2}}\left(\sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + \beta\alpha^2 \frac{\cosh\beta\sqrt{J^2x^M_m/4 + \alpha^2}}{\sqrt{J^2x^M_m/4 + \alpha^2}} - \frac{\alpha^2 \sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2}}{J^2x^M_m/4 + \alpha^2}\right)\right.\\
+						   &\quad \quad\quad \quad\left.+ e^{-\beta JM/2}\frac{\beta}{2}\cosh \left(\beta h/2\right)\right] \\
+\end{aligned}\end{equation}
+We will now take the limit of \(h \to 0\). Note that \(\alpha(h\to 0)=\frac{J}{2}(m+1/2)\) and hence 
+\begin{equation}\begin{aligned}
+	(J^2x^M_m/4 + \alpha^2)(h \to 0) = \frac{J^2}{4}\left[M(M+1) - m(m+1) + (m+1/2)^2\right] = \frac{J^2}{4}\left( M + 1/2 \right)^2
+\end{aligned}\end{equation}
+For brevity, we define \(\theta_M = \beta J (M+1/2)/2\) and \(\Sigma_M = \sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}(m+1/2)^2\).
+\begin{equation}\begin{aligned}
+	\lim_{h \to 0}Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta \frac{J}{2}\left( M + 1/2 \right) + 2e^{-\beta JM/2}\right] = \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[4Me^{\beta J/4}\cosh \theta_M + 2e^{-\beta JM/2}\right]\\
+	\lim_{h \to 0}\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} &=  \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta J/4}(m+1/2)\frac{\sinh \beta\frac{J}{2}\left( M + 1/2 \right) }{\left( M + 1/2 \right)}\right] = 0\\
+	\lim_{h \to 0}\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \frac{\beta^2}{2}\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\frac{e^{\beta J/4}}{\theta_M}\left(2M\sinh \theta_M + \frac{\beta^2 J^2}{4}\left[\frac{\cosh\theta_M}{\theta_M} - \frac{\sinh \theta_M}{\theta_M^2}\right]\Sigma_M\right)+ e^{-\beta JM/2}\right]\\
+\end{aligned}\end{equation}
+Since the final expressions are formidable, we write down the expressions specifically for the single-channel and two-channel models.
+For single-channel, we have \(M=\frac{1}{2}\) and \(m = \pm \frac{1}{2}\).
+The terminal states are \(S_d^z=-1/2, m=-1/2\) and \(S_d^z=1/2, m=1/2\).
+There is therefore just one \(2\times 2\) block, and that is at \(m=-1/2\).
+\begin{gather}
+	\lim_{h \to 0}Z(h) = 2e^{\beta J/4}\cosh \beta \frac{J}{2} + 2e^{-\beta J/4} \\
+	\lim_{h \to 0}\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} = 0 \\
+	\lim_{h \to 0}\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} = \frac{\beta}{J}\left(e^{\beta J/4}\sinh \beta\frac{J}{2} + e^{-\beta J/4}\frac{J \beta}{2}\right)\\
+	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z(h)^{\prime\prime}}{Z(h)} - \left(\frac{Z(h)^{\prime}}{Z(h)}\right)^2 \right] = \frac{1}{J}\frac{\left(2e^{\beta J/2}\sinh \beta\frac{J}{2} + J \beta\right)}{4e^{\beta J/2}\cosh \beta \frac{J}{2} + 4}
+\end{gather}
+This expression matches with the direct calculation of the susceptibility of the single-channel Kondo model.
+
+At low temperature \(\beta \to \infty\), only the highest value \(M_\text{max}\) will survive:
+\begin{equation}\begin{aligned}
+	Z &\to 2 r^K_{M_\text{max}} M_\text{max} e^{\beta \frac{J}{2}(M_\text{max} + 1)}\\
+	Z^{\prime \prime} &\to r^K_{M_\text{max}}\left(\frac{\beta }{2(M_\text{max} + 1/2)}\right)^2 e^{\beta \frac{J}{2}(M_\text{max} + 1)}\Sigma_\text{max}\\
+	\chi &\to \frac{\beta\Sigma_\text{max}}{2M_\text{max}\left(2M_\text{max}+1\right)^2} = \frac{\beta\Sigma_\text{max}}{K(K+1)^2}
+\end{aligned}\end{equation}
+
+At high temperatures \(\beta \to 0\), we get
+\begin{equation}\begin{aligned}
+	Z &\to \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[4M + 2\right]\\
+	Z^{\prime \prime} &\to \frac{\beta^2}{2}\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[2M + 1\right]\\
+	\chi &\to 1/4
 \end{aligned}\end{equation}

### 2021-11-22 notes/multi-channel-urg.tex
started calculating bath chi, also plotted chi(0) as K \to infty

@@
 
+\section{Bath contribution to Susceptibility from zero-mode fixed-point Hamiltonian}
+We insert a magnetic field that acts only on the bath and then attempt to diagonalize the Hamiltonian.
+\begin{equation}\begin{aligned}
+	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h s^z_\text{tot}
+\end{aligned}\end{equation}
+
+Defining \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
+\begin{equation}\begin{aligned}
+	H_m = mh + \begin{pmatrix} Jm/2 & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & h - J(m+1)/2 \end{pmatrix} 
+\end{aligned}\end{equation}
+The eigenvalues are 
+\begin{equation}\begin{aligned}
+	\lambda_{m, \pm}^{M, h} = -J/4 + mh \pm \sqrt{J^2x^M_m/4 + J^2/16 - Jmh/2}
+\end{aligned}\end{equation}
+The eigenvalues of the terminal states are \(JM/2 \pm hm\). The partition function is
+\begin{equation}\begin{aligned}
+	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
+	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+\end{aligned}\end{equation}
+where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\).
+This is yet not the complete partition function, because we have not accounted for the possibility that there multiple subspaces of \(M\).
+For example, the \(K=3\) case states can be obtained by adding the third spin-half onto the states \(S=0,1\).
+\(S=0\) gives \(s_\text{tot}=1/2\) and \(S=1\) gives \(s_\text{tot} = 1/2, 3/2\).
+So, \(s_\text{tot} = 1/2\) appears twice.
+These two subspaces are actually orthogonal, because the quantum numbers for the individual channels are different.
+We need to count the number of instances of a particular subspace \(s_\text{tot}=M\).
+It turns out that this number is given by
+\begin{equation}\begin{aligned}
+	r^K_M = {}^{K-1}C_{K/2 - M}
+\end{aligned}\end{equation}
+which means the correct partition function is
+\begin{equation}\begin{aligned}
+	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+\end{aligned}\end{equation}
 \appendix

### 2021-11-22 notes/multi-channel-urg.tex
obtained the leading temperature behaviour in chi with field on bath, but they do not match with numerical results

@@
-\documentclass{revtex4-2}
+\documentclass[12pt]{revtex4-2}
 \usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
@@
 \begin{equation}\begin{aligned}
-	H_m = mh + \begin{pmatrix} Jm/2 & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & h - J(m+1)/2 \end{pmatrix} 
+	H_m = \begin{pmatrix} m(J/2 + h) & J\sqrt{x^M_m}/2 \\ J\sqrt{x^M_m}/2 & (m+1)(h - J/2) \end{pmatrix} 
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\lambda_{m, \pm}^{M, h} = -J/4 + mh \pm \sqrt{J^2x^M_m/4 + J^2/16 - Jmh/2}
+	\lambda_{m, \pm}^{M, h} = -J/4 + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2x^M_m + \left[(2m+1)h - J/2\right]^2 - 4m(m+1)(h^2 - J^2/4)} \\
+	= -J/4 + (2m+1)h/2 \pm \phi^M_m
 \end{aligned}\end{equation}
-The eigenvalues of the terminal states are \(JM/2 \pm hm\). The partition function is
+The eigenvalues of the terminal states are \(JM/2 \pm hM\). The partition function is
 \begin{equation}\begin{aligned}
-	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
-	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta JM/2}\left(e^{\beta hM} + e^{-\beta hM}\right)\right] \\
+	     &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(J/4 - (m+1/2)h\right)}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\cosh \beta Mh\right]
 \end{aligned}\end{equation}
-where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\).
-This is yet not the complete partition function, because we have not accounted for the possibility that there multiple subspaces of \(M\).
-For example, the \(K=3\) case states can be obtained by adding the third spin-half onto the states \(S=0,1\).
-\(S=0\) gives \(s_\text{tot}=1/2\) and \(S=1\) gives \(s_\text{tot} = 1/2, 3/2\).
-So, \(s_\text{tot} = 1/2\) appears twice.
-These two subspaces are actually orthogonal, because the quantum numbers for the individual channels are different.
-We need to count the number of instances of a particular subspace \(s_\text{tot}=M\).
-It turns out that this number is given by
+We will now take the derivatives.
 \begin{equation}\begin{aligned}
-	r^K_M = {}^{K-1}C_{K/2 - M}
+	Z^\prime(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(J/4 - (m+1/2)h\right)}\left(-\beta (m+1/2) \cosh \beta\phi^M_m + \beta\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right)+ 2\beta Me^{-\beta JM/2}\sinh \beta Mh\right]\\
+	Z^{\prime\prime}(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2 e^{\beta \left(J/4 - (m+1/2)h\right)}\left(\beta^2 (m+1/2)^2 \cosh \beta\phi^M_m - 2\beta^2 (m+1/2)\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right.\right.\\
+			    &\quad\quad\quad\quad\quad\quad\left.\left.
++ \beta\frac{\:\mathrm{d^2}\phi^M_m}{\:\mathrm{d}h^2}\sinh \beta\phi^M_m + \beta^2\left(\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right)^2 \cosh \beta\phi^M_m\right) + 2\beta^2 M^2 e^{-\beta JM/2}\cosh \beta Mh\right]\\
 \end{aligned}\end{equation}
-which means the correct partition function is
+In the limit of \(h \to 0\), we  have
 \begin{equation}\begin{aligned}
-	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\right]\\
+	Z^\prime(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\left(-\beta (m+1/2) \cosh \beta\phi^M_m + \beta\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right)\right]\\
+	Z^{\prime\prime}(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2 e^{\beta J/4}\left(\beta^2 (m+1/2)^2 \cosh \beta\phi^M_m - 2\beta^2 (m+1/2)\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right.\right.\\
+			    &\quad\quad\quad\quad\quad\quad\left.\left.
++ \beta\frac{\:\mathrm{d^2}\phi^M_m}{\:\mathrm{d}h^2}\sinh \beta\phi^M_m + \beta^2\left(\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right)^2 \cosh \beta\phi^M_m\right) + 2\beta^2 M^2 e^{-\beta JM/2}\right]\\
 \end{aligned}\end{equation}
+The \(\phi\) and the derivatives are actually at \(h\to 0\).
+We are interested in the low temperature behaviour.
+In the limit of \(h \to 0\), \(\phi_m^M \to \phi^M = J(M+1/2)/2\).
+We can also look at the behaviour of the derivative:
+\begin{equation}\begin{aligned}
+	\frac{\:\mathrm{d}\phi_m^M}{\:\mathrm{d}h} &= -\frac{J(m+1/2)/2 + h(4m - 1)/2}{\phi_m^M} \rightarrow \lim_{h \to 0}\rightarrow -\frac{J(m+1/2)/2}{\phi^M}\\
+	\lim_{h \to 0}\frac{\:\mathrm{d}^2\phi_m^M}{\:\mathrm{d}h^2} &= \frac{1/2 -2m}{\phi^M} - \frac{J^2}{4}\frac{(m + 1/2)^2}{\left(\phi^M\right)^3}\\
+\end{aligned}\end{equation}
+Substituting these give
+\begin{equation}\begin{aligned}
+	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\phi^M + 2e^{-\beta JM/2}\right]\\
+	Z^\prime(h \to 0) &=-\beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M2e^{\beta J/4} \left(\cosh \beta\phi^M + \frac{J}{2\phi^M}\sinh \beta\phi^M\right)\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left( m + 1/2 \right)\\
+	Z^{\prime\prime}(h \to 0) &=\beta^2\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[2 e^{\beta J/4}\left(\left(1 + \frac{J^2}{4{\phi^M}^2}\right)  \cosh \beta\phi^M + \frac{J}{\phi^M}\left( 1 - \frac{J}{4\beta{\phi^M}^2}\right)\sinh \beta\phi^M\right)\Sigma_M + 2\beta^2 M^2 e^{-\beta JM/2}\right]\\
+\end{aligned}\end{equation}
+
+If we take the limit of \(\beta \to \infty\), the term with \(\beta\) in \(Z^{\prime\prime}\) drops out because the terms with \(\beta^2\) will grow faster.
+All negative exponentials will also drop out.
+We get
+\begin{equation}\begin{aligned}
+	     Z(\beta\to\infty, h \to 0) &=e^{\beta J/4}\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta\phi^M_m}\right]\\
+	Z^\prime(\beta\to\infty, h \to 0) &=e^{\beta J/4}\beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta\phi^M_m}\left(- (m+1/2) + \frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right)\right]\\
+	Z^{\prime\prime}(\beta\to\infty, h \to 0) &=e^{\beta J/4}\beta^2\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1} e^{\beta\phi^M_m}\left( (m+1/2)^2  - 2 (m+1/2)\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h} + \left(\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right)^2\right)\right]\\
+\end{aligned}\end{equation}
+ In the entire nested summation, only the largest exponential out of all the \(e^{\beta\phi^M_m}\) will survive.
+In the limit of \(h \to 0\), we have \(\phi_m^M(h\to 0) = \frac{J}{2}(M + 1/2)\), which means that the largest exponential \(\Phi_K\) occurs for \(M = M_\text{max}\).
+\begin{equation}\begin{aligned}
+	     Z(\beta\to\infty, h \to 0) &=e^{\beta J/4} e^{\beta \Phi_K}r^K_{M_\text{max}}(2M_\text{max}+1)\\
+	Z^\prime(\beta\to\infty, h \to 0) &=e^{\beta J/4}\beta e^{\beta \Phi_K}r^K_{M_\text{max}}\sum_{m=-M_\text{max}, \atop{m\in \mathbb{Z}}}^{M_\text{max}-1}\left(- (m+1/2) + \frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right) \\
+	Z^{\prime\prime}(\beta\to\infty, h \to 0) &=e^{\beta J/4}\beta^2 e^{\beta\Phi_K}r^K_{M_\text{max}}\sum_{m=-M_\text{max}, \atop{m\in \mathbb{Z}}}^{M_\text{max}-1} \left( (m+1/2)^2  - 2 (m+1/2)\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h} + \left(\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right)^2\right)\\
+\end{aligned}\end{equation}
+Substituting this gives
+\begin{equation}\begin{aligned}
+	     Z(\beta\to\infty, h \to 0) &=e^{\beta J/4} e^{\beta \Phi_K}r^K_{M_\text{max}}2M_\text{max}\\
+	Z^\prime(\beta\to\infty, h \to 0) & -e^{\beta J/4}\beta e^{\beta \Phi_K}r^K_{M_\text{max}}\left(1 + \frac{J}{2\Phi_K}\right) \sum_{m=-M_\text{max}, \atop{m\in \mathbb{Z}}}^{M_\text{max}-1}\left( m + 1/2 \right) = 0\\
+Z^{\prime\prime}(\beta\to\infty, h \to 0) &=e^{\beta J/4}\beta^2 e^{\beta\Phi_K}r^K_{M_\text{max}}\left(1 + \frac{J}{2\Phi_K}\right)^2 \sum_{m=-M_\text{max}, \atop{m\in \mathbb{Z}}}^{M_\text{max}-1} \left(m+1/2\right)^2\\
+\end{aligned}\end{equation}
+
+\begin{equation}\begin{aligned}
+	\chi(T \to 0) = \frac{\beta\left(K+3\right)^2\Sigma_\text{max}}{K(K+1)^2} 
+\end{aligned}\end{equation}
+
 \appendix

### 2021-11-23 notes/multi-channel-urg.tex
improved the analytical derivation for the bath chi, mostly matches with numerics now, funniiy only the K=2 case doesnt match
obtained asymptotic beahviours of bath chi

--- 2021-11-22 notes/multi-channel-urg.tex
@@
 \usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
-\usepackage[margin=0.2in]{geometry}
+\usepackage[margin=0.2in,top=0.5in,bottom=0.5in]{geometry}
 \numberwithin{equation}{section}
@@
 \begin{equation}\begin{aligned}
+	\label{eigenvalue}
 	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}
@@
 where \(\alpha = \epsilon^h_m + J/4\).
-The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\). The partition function is
+The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\).
+For \(h = 0\), the ground state subspace is \(K-\)fold degenerate and is formed by the negative solutions of eq.~\ref{eigenvalue}.
+This common \(K-\)fold degenerate eigenvalue is \(-J(M+1)/2\).
+The partition function is
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
-	\lambda_{m, \pm}^{M, h} = -J/4 + mh \pm \sqrt{J^2x^M_m/4 + J^2/16 - Jmh/2}
+	\lambda_{m, \pm}^{M, h} &= -J/4 + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2x^M_m + \left[(2m+1)h - J/2\right]^2 - 4m(m+1)(h^2 - J^2/4)} \\
+				&= -J/4 + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2(M + 1/2)^2 + h^2 - (2m+1)Jh}	= -J/4 + (2m+1)h/2 \pm \phi^M_m
 \end{aligned}\end{equation}
-The eigenvalues of the terminal states are \(JM/2 \pm hm\). The partition function is
+The eigenvalues of the terminal states are \(JM/2 \pm hM\). The partition function is
 \begin{equation}\begin{aligned}
-	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
-	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta JM/2}\left(e^{\beta hM} + e^{-\beta hM}\right)\right] \\
+	     &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(J/4 - (m+1/2)h\right)}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\cosh \beta Mh\right]
 \end{aligned}\end{equation}
-where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\).
-This is yet not the complete partition function, because we have not accounted for the possibility that there multiple subspaces of \(M\).
-For example, the \(K=3\) case states can be obtained by adding the third spin-half onto the states \(S=0,1\).
-\(S=0\) gives \(s_\text{tot}=1/2\) and \(S=1\) gives \(s_\text{tot} = 1/2, 3/2\).
-So, \(s_\text{tot} = 1/2\) appears twice.
-These two subspaces are actually orthogonal, because the quantum numbers for the individual channels are different.
-We need to count the number of instances of a particular subspace \(s_\text{tot}=M\).
-It turns out that this number is given by
+We will now take the derivatives.
 \begin{equation}\begin{aligned}
-	r^K_M = {}^{K-1}C_{K/2 - M}
+	Z^\prime(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(J/4 - (m+1/2)h\right)}\left(-\beta (m+1/2) \cosh \beta\phi^M_m + \beta\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right)+ 2\beta Me^{-\beta JM/2}\sinh \beta Mh\right]\\
+	Z^{\prime\prime}(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2 e^{\beta \left(J/4 - (m+1/2)h\right)}\left(\beta^2 (m+1/2)^2 \cosh \beta\phi^M_m - 2\beta^2 (m+1/2)\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right.\right.\\
+			    &\quad\quad\quad\quad\quad\quad\left.\left.
++ \beta\frac{\:\mathrm{d^2}\phi^M_m}{\:\mathrm{d}h^2}\sinh \beta\phi^M_m + \beta^2\left(\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right)^2 \cosh \beta\phi^M_m\right) + 2\beta^2 M^2 e^{-\beta JM/2}\cosh \beta Mh\right]\\
 \end{aligned}\end{equation}
-which means the correct partition function is
+In the limit of \(h \to 0\), we  have
 \begin{equation}\begin{aligned}
-	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\right]\\
+	Z^\prime(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\left(-\beta (m+1/2) \cosh \beta\phi^M_m + \beta\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right)\right]\\
+	Z^{\prime\prime}(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2 e^{\beta J/4}\left(\beta^2 (m+1/2)^2 \cosh \beta\phi^M_m - 2\beta^2 (m+1/2)\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right.\right.\\
+			    &\quad\quad\quad\quad\quad\quad\left.\left.
++ \beta\frac{\:\mathrm{d^2}\phi^M_m}{\:\mathrm{d}h^2}\sinh \beta\phi^M_m + \beta^2\left(\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right)^2 \cosh \beta\phi^M_m\right) + 2\beta^2 M^2 e^{-\beta JM/2}\right]\\
 \end{aligned}\end{equation}
+The \(\phi\) and the derivatives are actually at \(h\to 0\).
+We are interested in the low temperature behaviour.
+In the limit of \(h \to 0\), \(\phi_m^M \to \phi^M = J(M+1/2)/2\).
+We can also look at the behaviour of the derivative:
+\begin{equation}\begin{aligned}
+	\lim_{h \to 0}\frac{\:\mathrm{d}\phi_m^M}{\:\mathrm{d}h} &= -\frac{J(m+1/2)}{4\phi^M}\\
+	\lim_{h \to 0}\frac{\:\mathrm{d}^2\phi_m^M}{\:\mathrm{d}h^2} &= \frac{1}{4\phi^M} - \frac{J^2(m + 1/2)^2}{16\left(\phi^M\right)^3}\\
+\end{aligned}\end{equation}
+Substituting these gives
+\begin{equation}\begin{aligned}
+	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\phi^M + 2e^{-\beta JM/2}\right] = \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[4Me^{\beta J/4}\cosh \beta\phi^M + 2e^{-\beta JM/2}\right]\\
+	Z^\prime(h \to 0) &=-\beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M2e^{\beta J/4} \left(\cosh \beta\phi^M + \frac{J}{4\phi^M}\sinh \beta\phi^M\right)\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left( m + 1/2 \right) = 0\\
+Z^{\prime\prime}(h \to 0) &=\beta^2\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[2 e^{\beta J/4}\left\{\left(1 + \frac{J^2}{16{\phi^M}^2}\right) \Sigma_M \cosh \beta\phi^M + \left(\frac{2M}{4\beta\phi^M} + \frac{J}{2\phi^M}\left(1 - \frac{J}{16\beta{\phi^M}^2}\right)\Sigma_M \right) \sinh \beta\phi^M\right\} \right.\\
+			  &\quad\quad\quad\quad\quad\quad\quad\left.+ 2 M^2 e^{-\beta JM/2}\right]\\
+\end{aligned}\end{equation}
+where \(\Sigma_M = \sum_m (m+1/2)^2\).
+
+If we take the limit of \(\beta \to \infty\), the hyperbolic functions can be replaced by exponentials.
+The terms with \(1/\beta\) in \(Z^{\prime\prime}\) drop out.
+All negative exponentials will also drop out.
+Moreover, out of all the positve exponentials, only the largest exponent will survive.
+The largest value \(\Phi\) of \(\phi^M\) occurs at \(M = M_\text{max} = K/2\).
+This maximum value is \(\Phi = J(K+1)/4\).
+We therefore have
+\begin{equation}\begin{aligned}
+	     Z(h \to 0) &= r^K_{K/2} 4Me^{\beta J/4}\frac{1}{2}e^{\beta\Phi}\\
+	     Z^\prime(h \to 0) &= 0\\
+	     Z^{\prime\prime}(h \to 0) &=\beta^2 r^K_{K/2}2 e^{\beta J/4}\frac{1}{2}e^{\beta \Phi}\left(1 + \frac{J}{4\Phi}\right)^2\Sigma_\text{max}\\
+\end{aligned}\end{equation}
+The susceptibility at low temperatures becomes
+\begin{equation}\begin{aligned}
+	\chi(T \to 0) = \frac{2\beta\left(1 + \frac{J}{4\Phi}\right)^2\Sigma_M}{4M} = \frac{\beta \Sigma_\text{max}(K+2)^2}{K(K+1)^2}
+\end{aligned}\end{equation}
+
 \appendix

### 2021-11-23 notes/multi-channel-urg.tex
checked numerically that the  zero temperature free energy is non-differentiable at h=0 for K>1

@@
 
-\section{Susceptibility from zero-mode fixed-point Hamiltonian}
+\section{Impurity Susceptibility from zero-mode fixed-point Hamiltonian}
 The zero-mode approximation of the fixed-point Hamiltonian is a star graph Hamiltonian:
@@
 For brevity, we define \(\theta_M = \beta J (M+1/2)/2\) and \(\Sigma_M = \sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}(m+1/2)^2\).
+It can be shown that this summation, for \(M=M_\text{max}=K/2\), evaluates to \(\Sigma_\text{max} = K(K+1)(K-1)/12\).
 \begin{equation}\begin{aligned}
@@
 	Z^{\prime \prime} &\to r^K_{M_\text{max}}\left(\frac{\beta }{2(M_\text{max} + 1/2)}\right)^2 e^{\beta \frac{J}{2}(M_\text{max} + 1)}\Sigma_\text{max}\\
-	\chi &\to \frac{\beta\Sigma_\text{max}}{2M_\text{max}\left(2M_\text{max}+1\right)^2} = \frac{\beta\Sigma_\text{max}}{K(K+1)^2}
+	\chi &\to \frac{\beta\Sigma_\text{max}}{2M_\text{max}\left(2M_\text{max}+1\right)^2} = \frac{\beta K(K+1)(K-1)/12}{K(K+1)^2} = \frac{\beta(K-1)}{12(K+1)}
 \end{aligned}\end{equation}
@@
 
-\section{Bath contribution to Susceptibility from zero-mode fixed-point Hamiltonian}
+\section{Bath Susceptibility from zero-mode fixed-point Hamiltonian}
 We insert a magnetic field that acts only on the bath and then attempt to diagonalize the Hamiltonian.
@@
 \begin{equation}\begin{aligned}
-	\chi(T \to 0) = \frac{2\beta\left(1 + \frac{J}{4\Phi}\right)^2\Sigma_M}{4M} = \frac{\beta \Sigma_\text{max}(K+2)^2}{K(K+1)^2}
+	\chi(T \to 0) = \frac{2\beta\left(1 + \frac{J}{4\Phi}\right)^2\Sigma_M}{4M} = \frac{\beta (K-1)(K+2)^2}{12(K+1)}
 \end{aligned}\end{equation}
 
+\subsection{Non-analyticity in the free energy}
+For \(K>1\), the Gibbs free energy at \(T=0\) becomes non-analytic under insertion of a magnetic field on the impurity. This was checked numerically.
 \appendix

### 2021-11-23 notes/multi-channel-urg.tex
derived the non-analytic free energy, also added numerical plot, they match

@@
 \begin{equation}\begin{aligned}
+	\label{stargraph_field_hamiltonian}
 	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h S_d^z
@@
 This common \(K-\)fold degenerate eigenvalue is \(-J(M+1)/2\).
+The full list of energy eigenvalues at a particular value of \(M\) is
+\begin{equation}\begin{aligned}
+\label{stargraph_spectrum}
+&		JM/2 - h/2, &&\ket{\downarrow, M, -M}, && m = -M\\
+&-J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}, &&\left\{\ket{\uparrow, M, m}, \ket{\downarrow, M, m+1}\right\}, &&m=-M,\ldots,M-1\\
+&JM/2 + h/2, &&\ket{\uparrow, M, M},&& m = M\\
+\end{aligned}\end{equation}
+
 The partition function is
@@
 \subsection{Non-analyticity in the free energy}
-For \(K>1\), the Gibbs free energy at \(T=0\) becomes non-analytic under insertion of a magnetic field on the impurity. This was checked numerically.
+For \(K>1\), the Gibbs free energy at \(T=0\) becomes non-analytic under insertion of a magnetic field on the impurity. The thermal free energy is given by
+\begin{equation}\begin{aligned}
+	F(h) = -\frac{1}{\beta}\ln Z(h) = -\frac{1}{\beta}\ln\sum_{E_n}e^{-\beta E_n}
+\end{aligned}\end{equation}
+At \(T \to 0\), only the most negative energy \(E_\text{min}\) survives. Assuming a non-degenerate ground state for \(h \neq 0\), the zero temperature free energy becomes
+\begin{equation}\begin{aligned}
+	F(h\neq 0, T\to 0) = -\frac{1}{\beta}\ln e^{-\beta E_\text{min}} = E_\text{min}
+\end{aligned}\end{equation}
+In the star graph Hamiltonian with \(K-\)channels and in the presence of a field on the impurity (eq.~\ref{stargraph_field_hamiltonian}), the energy eigenvalues for a particular value of \(s_\text{tot}\) are given in eq.~\ref{stargraph_spectrum}.
+Within a particular subspace \(M\), the ground state energy will be one of the negative eigenvalues:
+\begin{equation}\begin{aligned}
+	\lambda^{M,h}_{m, -}= -J/4 - \frac{1}{2}\sqrt{J^2x^M_{m}/4 + \alpha^2} = -J/4 - \frac{1}{2}\sqrt{J^2(M+1/2)^2 + h^2 + 2hJ(m+1/2)}
+\end{aligned}\end{equation}
+The minimum eigenvalue is obtained by maximizing \(h(m+1/2)\).
+For \(h>0\), the ground state is renormalized for the most positive value of \(m\), \(M-1\).
+On the other hand, for \(h<0\), it occurs for \(m=-M\), because that is the most negative value it can take.
+Among all the values of \(M\), the global ground state is at the largest value of \(M\), \(K/2\).
+Therefore, the minimal energy eigenvalue is
+\begin{equation}\begin{aligned}
+	E_\text{min}(h) = \begin{cases}
+		-J/4 - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 + hJ(K-1)}, & h>0\\
+		-J/4 - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 - hJ(K-1)}, & h<0\\
+	\end{cases}
+\end{aligned}\end{equation}
+The free energy for a non-zero field is therefore
+\begin{equation}\begin{aligned}
+	F(h\neq 0, T\to 0) = -J/4 - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 + |h|J(K-1)}
+\end{aligned}\end{equation}
+The first derivative of the free energy with respect to the field gives
+\begin{equation}\begin{aligned}
+	F^\prime(h\neq 0, T\to 0) =- \frac{1}{2}\frac{2h + J(K-1)\text{sign}(h)}{2\sqrt{J^2(K+1)^2/4 + h^2 + |h|J(K-1)}}
+\end{aligned}\end{equation}
+There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get
+\begin{equation}\begin{aligned}
+	F^\prime(h \to 0^\pm, T\to 0) = \mp \frac{1}{2}\frac{(K-1)}{(K+1)}
+\end{aligned}\end{equation}
+
+The first derivative of the impurity free energy is therefore discontinuous as \(h\to 0\); it goes to different values depending on the direction in which we take the limit.
+The only case where it is not analytic is when \(K=1\); then the derivative goes to zero from both directions.
+This non-analyticity has also been verified numerically.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../numerics/free_energy_nonanaliticity.pdf}
+	\caption{Non-analytic free energy for \(K>1\) and analytic free energy for \(K=1\).}
+\end{figure}
+
+The non-analyticity for \(K>1\) occurs because the magnetic field is able to flip the ground state.
+For example, for \(K=2\), the states in question are \(\ket{M=1, m=-1,0}\).
+For \(h>0\), the ground state occurs in the subspace \(\ket{S_d^z=1/2, m=-1},\ket{S_d^z=-1/2,m=0}\).
+If we now flip the magnetic field, the ground state subspace flips to \(\ket{S_d^z=1/2, m=0},\ket{S_d^z=-1/2,m=1}\).
+Instead, if we look at the case of \(K=1\), the ground state is in the subspace of \(\ket{S_d^z=1/2,m=-1/2},\ket{S_d^z=-1/2, m=1/2}\), and since there is only this one subspace, the ground state is independent of the field.
+From this discussion, it is clear that the non-analyticity appears because there are multiple values of \(m \in [-M, M-1]\) in the ground state manifold, which means that it is the ground state degeneracy that causes the non-analyticity.
+
 \appendix

### 2021-11-24 notes/multi-channel-urg.tex
added figures to notes

@@
-\documentclass[12pt]{revtex4-2}
+\documentclass{revtex4-2}
 \usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
-\usepackage[margin=0.2in,top=0.5in,bottom=0.5in]{geometry}
+% \usepackage[margin=0.2in,top=0.5in,bottom=0.5in]{geometry}
 \numberwithin{equation}{section}
@@
 \usepackage[T1]{fontenc}
-\usepackage{ebgaramond}
+% \usepackage{ebgaramond}
 \begin{document}
@@
 \end{aligned}\end{equation}
+The RG flows towards the attractive fixed point \(J_1^*\) is shown  in fig.~\ref{rg_flow_K-2}.
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../numerics/rg_flow_K=2.pdf}
+	\caption{Attractive flows towards \(J_1^*\)}
+	\label{rg_flow_K-2}
+\end{figure}
+
 This behaviour is shown schematically in fig.~\ref{rg_flow_general}. 
@@
 	\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta J/4}\alpha\frac{\sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2} }{\sqrt{J^2x^M_m/4 + \alpha^2}} + e^{-\beta JM/2}\sinh \left(\beta h/2\right)\right] \\
-	\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\frac{1}{2}\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\frac{e^{\beta J/4}}{\sqrt{J^2x^M_m/4 + \alpha^2}}\left(\sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + \beta\alpha^2 \frac{\cosh\beta\sqrt{J^2x^M_m/4 + \alpha^2}}{\sqrt{J^2x^M_m/4 + \alpha^2}} - \frac{\alpha^2 \sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2}}{J^2x^M_m/4 + \alpha^2}\right)\right.\\
-						   &\quad \quad\quad \quad\left.+ e^{-\beta JM/2}\frac{\beta}{2}\cosh \left(\beta h/2\right)\right] \\
+	\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\frac{1}{2}\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\frac{e^{\beta J/4}}{\sqrt{J^2x^M_m/4 + \alpha^2}}\left(\sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + \beta\alpha^2 \frac{\cosh\beta\sqrt{J^2x^M_m/4 + \alpha^2}}{\sqrt{J^2x^M_m/4 + \alpha^2}}\right.\right.\\
+						   &\quad \quad\quad \quad\left.\left.
+- \frac{\alpha^2 \sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2}}{J^2x^M_m/4 + \alpha^2}\right) + e^{-\beta JM/2}\frac{\beta}{2}\cosh \left(\beta h/2\right)\right] \\
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
+These expressions have been used to compute the impurity susceptibility for various values of \(K\) in fig.~\ref{chi_mchannel}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../numerics/chi_mchannel.pdf}
+	\caption{Impurity susceptibility for \(K=1,2,4,6\), calculated numerically as well as using the analytical expressions.}
+	\label{chi_mchannel}
+\end{figure}
+
 Since the final expressions are formidable, we write down the expressions specifically for the single-channel and two-channel models.
@@
 
-\subsection{Non-analyticity in the free energy}
+\section{Non-analyticity in the free energy}
 For \(K>1\), the Gibbs free energy at \(T=0\) becomes non-analytic under insertion of a magnetic field on the impurity. The thermal free energy is given by
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../numerics/free_energy_nonanaliticity.pdf}
+	\includegraphics[width=0.6\textwidth]{../numerics/free_energy_nonanaliticity.pdf}
 	\caption{Non-analytic free energy for \(K>1\) and analytic free energy for \(K=1\).}
@@
 \appendix
-
+\clearpage
 \section{URG analysis of the single-channel Kondo model}

### 2021-11-24 notes/multi-channel-urg.tex
wrote general eigenstates and switched numerics to work with global field, QCP still there
completed free energy derivative calculation with global field

@@
 \end{aligned}\end{equation}
+The eigenstates for each value of \(M,m\) are given by
+\begin{equation}\begin{aligned}
+	\left(\pm\frac{1}{2}\sqrt{J^2 {x_m^M}^2 + 4\alpha^2} - \frac{J}{2}\sqrt{x_m^M}\right)\ket{\uparrow, M, m} + \left(\frac{J}{2}(m+\frac{1}{2}) + \frac{h}{2}\right) \ket{\downarrow, M, m+1}
+\end{aligned}\end{equation}
 
@@
 	     Z(h \to 0) &= r^K_{K/2} 4Me^{\beta J/4}\frac{1}{2}e^{\beta\Phi}\\
-	     Z^\prime(h \to 0) &= 0\\
 	     Z^{\prime\prime}(h \to 0) &=\beta^2 r^K_{K/2}2 e^{\beta J/4}\frac{1}{2}e^{\beta \Phi}\left(1 + \frac{J}{4\Phi}\right)^2\Sigma_\text{max}\\
@@
 \end{aligned}\end{equation}
-In the star graph Hamiltonian with \(K-\)channels and in the presence of a field on the impurity (eq.~\ref{stargraph_field_hamiltonian}), the energy eigenvalues for a particular value of \(s_\text{tot}\) are given in eq.~\ref{stargraph_spectrum}.
-Within a particular subspace \(M\), the ground state energy will be one of the negative eigenvalues:
+In the star graph Hamiltonian with \(K-\)channels and a global magnetic field on the impurity
 \begin{equation}\begin{aligned}
-	\lambda^{M,h}_{m, -}= -J/4 - \frac{1}{2}\sqrt{J^2x^M_{m}/4 + \alpha^2} = -J/4 - \frac{1}{2}\sqrt{J^2(M+1/2)^2 + h^2 + 2hJ(m+1/2)}
+	H = J \vec{S_d}\cdot\vec{s}_\text{tot} + h\left(S_d^z + s^z_\text{tot}\right) ~,
 \end{aligned}\end{equation}
-The minimum eigenvalue is obtained by maximizing \(h(m+1/2)\).
-For \(h>0\), the ground state is renormalized for the most positive value of \(m\), \(M-1\).
-On the other hand, for \(h<0\), it occurs for \(m=-M\), because that is the most negative value it can take.
-Among all the values of \(M\), the global ground state is at the largest value of \(M\), \(K/2\).
-Therefore, the minimal energy eigenvalue is
+the energy eigenvalues for a particular value of \(s_\text{tot}=M\) are given by
 \begin{equation}\begin{aligned}
-	E_\text{min}(h) = \begin{cases}
-		-J/4 - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 + hJ(K-1)}, & h>0\\
-		-J/4 - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 - hJ(K-1)}, & h<0\\
+	&\frac{J}{2}M \pm h\left(M + \frac{1}{2}\right),\\
+	&-\frac{J}{4}\pm \frac{J}{2}\left(M + \frac{1}{2}\right) + h\left( m + \frac{1}{2} \right), m \in \left[-M, M-1\right] 
+\end{aligned}\end{equation}
+For small \(h\), the ground state will be \(-\frac{J}{4}- \frac{J}{2}\left(M + \frac{1}{2}\right) + h\left(m_\text{min} + \frac{1}{2} \right)\) for a particular value \(m_\text{min}\) that minimizes this energy.
+This specific value will depend on the sign of \(h\):
+\begin{equation}\begin{aligned}
+	m_\text{min} = \begin{cases}
+		-M, & h >0\\
+		M-1,& h< 0
 	\end{cases}
@@
 \begin{equation}\begin{aligned}
-	F(h\neq 0, T\to 0) = -J/4 - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 + |h|J(K-1)}
+	F(h\neq 0, T\to 0) = -\frac{J}{2}\left( M + 1 \right) - |h|\left(M - \frac{1}{2}\right)
 \end{aligned}\end{equation}
+
 The first derivative of the free energy with respect to the field gives
 \begin{equation}\begin{aligned}
-	F^\prime(h\neq 0, T\to 0) =- \frac{1}{2}\frac{2h + J(K-1)\text{sign}(h)}{2\sqrt{J^2(K+1)^2/4 + h^2 + |h|J(K-1)}}
+	F^\prime(h\neq 0, T\to 0) = -\text{sign}(h)\left(M - \frac{1}{2}\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	F^\prime(h \to 0^\pm, T\to 0) = \mp \frac{1}{2}\frac{(K-1)}{(K+1)}
+	F^\prime(h \to 0^\pm, T\to 0) = \mp\left(M - \frac{1}{2}\right) = \mp \frac{1}{2}\left( K - 1 \right) 
 \end{aligned}\end{equation}

### 2021-11-25 notes/multi-channel-urg.tex
started calculating  real space effective Hamiltonian

@@
 
-\section{Derivation of low energy effective \(k-\)space Hamiltonian }
+\section{Effective Hamiltonian for low-energy excitations: \(k-\)space}
 The fixed point Hamiltonian is
@@
 	\\
-	s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}s_\text{tot}^- = s_\text{tot}^+ s_\text{tot}^- \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}% = \left[s_\text{tot}\left( s_\text{tot}+1 \right)  - s_\text{tot}^z\left( s_\text{tot}^z - 1 \right) \right] \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}
+	s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}s_\text{tot}^- = s_\text{tot}^+ s_\text{tot}^- \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}% = \left[s_\text{tot}\left( s_\text{tot}+1 \right)  - s_\text{tot}^z\left( s_\text{tot}^z - 1 \right) \right] \frac{1}{E_\text{gs} - \frag{J}{2} \left(s_\text{tot}^z - 1\right)}
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
+
+\section{Effective Hamiltonian for low-energy excitations: real space}
+We will obtain the theory for the low-energy excitations of the two-channel Kondo model by treating the hopping between the zeroth site and the first site as a perturbation.
+The zeroth site is just the spin-exchange part of the Hamiltonian:
+\begin{equation}\begin{aligned}
+	H_0 = J \vec{S_d}\cdot\vec{s}_\text{tot}, V = -t \sum_{\sigma,l}c^\dagger_{0\sigma,l}c_{1\sigma,l} + \text{h.c.}
+\end{aligned}\end{equation}
+We will remove this single-particle interaction through a Schrieffer-Wolf transformation and generate higher order interactions in the process.
+The renormalization due to to this process, up to second order, is given by
+\begin{equation}\begin{aligned}
+	\Delta H = V \frac{1}{E_\text{gs} - H_0}V
+\end{aligned}\end{equation}
+The two degenerate ground states are
+\begin{equation}\begin{aligned}
+	\ket{\Psi_\sigma} = \frac{1}{\sqrt 6} \left[\ket{\sigma, \overline \sigma,\overline \sigma} - \ket{\overline \sigma,\sigma,\sigma} - \ket{\overline \sigma,\overline \sigma,\sigma}\right], && \sigma=\pm 1
+\end{aligned}\end{equation}
+where \(\ket{\pm 1} = \ket{\uparrow},\ket{\downarrow}\) and the notation is as follows: the first label is for the impurity spin and the second and third labels are for the zeroth sites of channels 1 and channel 2 respectively.
+We will calculate the effective Hamiltonian in the subspace of a single ground state:
+\begin{equation}\begin{aligned}
+	\Delta H_\sigma = \ket{\Psi_\sigma}\bra{\Psi_\sigma}V \frac{1}{E_\text{gs} - H_0}V\ket{\Psi_\sigma}\bra{\Psi_\sigma}
+\end{aligned}\end{equation}
+Since the perturbation also acts on the first site (the site nearest to the zeroth site), we will need to expand the basis:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_\sigma} = \frac{1}{\sqrt 6} \left[\ket{\sigma, \overline \sigma,\overline \sigma} - \ket{\overline \sigma,\sigma,\sigma} - \ket{\overline \sigma,\overline \sigma,\sigma}\right]\otimes\prod_{\alpha=\pm 1, l=1,2} \sum_{n^1_{\alpha,l}=0,1}\ket{n^1_{\alpha,l}}, && \sigma=\pm 1
+\end{aligned}\end{equation}
+Here, \(n^1_{\alpha,l}\) denotes the number of electrons of spin \(\alpha\) and channel index \(l\) on the first site.
+
+The action of the perturbation on the state is given by
+\begin{equation}\begin{aligned}
+	V\ket{\Psi_\sigma} = \left(-t \sum_{\beta,l}c^\dagger_{0\beta,l}c_{1\beta,l} + \text{h.c.}\right) \frac{1}{\sqrt 6} \left[\ket{\sigma, \overline \sigma,\overline \sigma} - \ket{\overline \sigma,\sigma,\sigma} - \ket{\overline \sigma,\overline \sigma,\sigma}\right]\otimes\prod_{\alpha=\pm 1, l=1,2} \sum_{n^1_{\alpha,l}=0,1}\ket{n^1_{\alpha,l}}
+\end{aligned}\end{equation}
+We will split the perturbation into parts: \(V = \sum_\sigma \left(v_\sigma + v_\sigma^\dagger\right) \), where \(v\) is the part that annihilates an electron on the first site.
 

### 2021-11-26 notes/multi-channel-urg.tex
calculated thermal entropy

@@
 \end{aligned}\end{equation}
-The integration goes over positive energies only because of the \(1 - \hat n\) operator; the upper limit of the integration is chosen so as to make the denominator double, because this preserves the symmetry of the denominator and this is what happens in poor man's scaling.
+The integration limits include only the positive energies, because of the \(1 - \hat n\) operator; the upper limit of the integration is chosen so as to make the denominator double, because this preserves the symmetry of the denominator.
 Performing the integration gives
@@
 \begin{equation}\begin{aligned}
-	\Delta H_1 = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\frac{1}{2}\left( -\frac{1}{4} \right) \sum_{k_1,k_2,\alpha_1,\alpha_2,b} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}\\
-=\frac{1}{16}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4} \sum_{k_1,k_2,\alpha_1,\alpha_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
+	\Delta H_1 = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\frac{1}{2}\left( -\frac{1}{4} \right) \sum_{k_1,k_2,\alpha_1,\alpha_2,b,l_2} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}\\
+=\frac{1}{16}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4} \sum_{k_1,k_2,\alpha_1,\alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
 \end{aligned}\end{equation}
@@
 
+\section{Thermal entropy at \(T=0\)}
+The thermal entropy at temperature \(T\) is given by
+\begin{equation}\begin{aligned}
+	S(T) = -k_B \sum_{n}P_n \ln P_n
+\end{aligned}\end{equation}
+where \(n\) sums over all eigenstates of the system.
+The state \(n\) is understood to have an energy \(E_n\).
+\(P_n\) is the probability to find the system in the state \(n\) from a canonical ensemble at temperature \(T\).
+This probability is given by
+\begin{equation}\begin{aligned}
+	P_n = \frac{e^{-\beta E_n}}{Z}
+\end{aligned}\end{equation}
+where \(Z = \sum_n d_n e^{-\beta E_n}\) and \(d_n\) is the degeneracy of the state \(E_n\). Substituting this gives for the entropy:
+\begin{equation}\begin{aligned}
+	S(T) = -k_B \sum_{n}\frac{e^{-\beta E_n}}{Z} \ln \frac{e^{-\beta E_n}}{Z}
+\end{aligned}\end{equation}
+Taking the limit of \(\beta \to \infty\) gives \(Z \to d_\text{gs}e^{-\beta E_\text{gs}}\):
+\begin{equation}\begin{aligned}
+	S(T) = -k_B \frac{d_\text{gs} e^{-\beta E_\text{gs}}}{d_\text{gs}e^{-\beta E_\text{gs}}} \ln \frac{e^{-\beta E_\text{gs}}}{d_\text{gs}e^{-\beta E_\text{gs}}} = k_B \ln d_\text{gs}
+\end{aligned}\end{equation}
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../numerics/entropy_comparison.pdf}
+	\caption{Comparison of star graph zero temperature entropy with CFT/Bethe ansatz formula}
+\end{figure}
+
 \appendix

### 2021-11-27 notes/multi-channel-urg.tex
compared thermal entropy with that of 1d ising

@@
 \section{Thermal entropy at \(T=0\)}
-The thermal entropy at temperature \(T\) is given by
+Given the Helmholtz free energy \(F = -k_B T \ln Z = - \frac{1}{\beta} \ln\sum_n e^{-\beta E_n}\), the thermal entropy at temperature \(T\) is given by
 \begin{equation}\begin{aligned}
-	S(T) = -k_B \sum_{n}P_n \ln P_n
+	S(T) = - \frac{\partial{F}}{\partial{T}} = k_B \ln\sum_n e^{-\beta E_n} + \frac{\sum_n E_n e^{-\beta E_n}}{T \sum_n e^{-\beta E_n}}
 \end{aligned}\end{equation}
-where \(n\) sums over all eigenstates of the system.
-The state \(n\) is understood to have an energy \(E_n\).
-\(P_n\) is the probability to find the system in the state \(n\) from a canonical ensemble at temperature \(T\).
-This probability is given by
+In the limit of \(T \to 0\), only the lowest energy state \(E_\text{gs}\) will survive. Assuming this state has a degeneracy \(d_\text{gs}\), we have
 \begin{equation}\begin{aligned}
-	P_n = \frac{e^{-\beta E_n}}{Z}
+	S(T \to 0) = k_B \ln\left(d_\text{gs} e^{-\beta E_\text{gs}}\right) + \frac{d_\text{gs} E_\text{gs}e^{-\beta E_\text{gs}}}{T d_\text{gs} e^{-\beta E_\text{gs}}} = k_B \ln d_\text{gs} - \frac{1}{T}E_\text{gs} + \frac{1}{T}E_\text{gs} = k_B \ln d_\text{gs}
 \end{aligned}\end{equation}
-where \(Z = \sum_n d_n e^{-\beta E_n}\) and \(d_n\) is the degeneracy of the state \(E_n\). Substituting this gives for the entropy:
+This is a general result that holds for any system with a \(d_\text{gs}\)-fold degenerate ground state.
+For the star graph problem, we have a \(K-\)fold degenerate ground state, so the \(T=0\) entropy of the star graph Hamiltonian with \(K\) outer spins is
 \begin{equation}\begin{aligned}
-	S(T) = -k_B \sum_{n}\frac{e^{-\beta E_n}}{Z} \ln \frac{e^{-\beta E_n}}{Z}
+	S(T\to 0) = k_B \ln K
 \end{aligned}\end{equation}
-Taking the limit of \(\beta \to \infty\) gives \(Z \to d_\text{gs}e^{-\beta E_\text{gs}}\):
-\begin{equation}\begin{aligned}
-	S(T) = -k_B \frac{d_\text{gs} e^{-\beta E_\text{gs}}}{d_\text{gs}e^{-\beta E_\text{gs}}} \ln \frac{e^{-\beta E_\text{gs}}}{d_\text{gs}e^{-\beta E_\text{gs}}} = k_B \ln d_\text{gs}
-\end{aligned}\end{equation}
+
 \begin{figure}[!ht]
 	\centering
-	\includegraphics[width=0.6\textwidth]{../numerics/entropy_comparison.pdf}
+	\includegraphics[width=0.5\textwidth]{../numerics/entropy_comparison.pdf}
 	\caption{Comparison of star graph zero temperature entropy with CFT/Bethe ansatz formula}
@@
 
+Another related problem for which this result holds is the Ising model on a 1D chain.
+The partition function for that problem is \(Z = \lambda_1^N + \lambda_2^N\), where \(\lambda_{1,2} = e^{\beta J} \pm e^{-\beta J} \) are the eigenvalues of the \(T-\)matrix and \(N\) is the number of particles.
+As we come to \(T \to 0\), we have \(\lambda_{1,2} \simeq e^{\beta J}\) and \(Z \simeq 2 e^{\beta N J}\), so \(F = -k_B T \ln 2 - N J\) and the entropy becomes \(S = - \partial_T F = k_B \ln 2\).
+Note that the factor of 2 in \(Z\) is the degeneracy \(d_\text{gs}\) described above.
+
+\clearpage
 \appendix
-\clearpage
 \section{URG analysis of the single-channel Kondo model}

### 2021-11-29 notes/multi-channel-urg.tex
obtained anisotropic multichannel physics

@@
 Since the denominator fixed point is identical in structure in both problems, its reasonable that the same thing will happen here.
+
+\subsection{Effect of anisotropy}
+For a general anisotropic multi-channel Kondo, the Hamiltonian is
+\begin{equation}\begin{aligned}
+	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + \sum_{kk^\prime,\gamma}J_\gamma \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
+\end{aligned}\end{equation}
+Let us consider the specific case where \(K-1\) channels have the same coupling \(J_1 = J_2 = ...
+= J_{K-1} = J_+\) and the remaining channel has a different coupling \(J_K = J_-\).
+The RG equations for such a model are
+\begin{equation}\begin{aligned}
+	\frac{\Delta J_+}{|\Delta D|} = \frac{J_+^2 \rho}{D - J_+/4} - \frac{\rho^2 J_+}{8}\left[\frac{(K-1)J_+^2}{D - J_+/4} + \frac{J_-^2}{D - J_-/4}\right]\\
+	\frac{\Delta J_-}{|\Delta D|} = \frac{J_-^2 \rho}{D - J_-/4} - \frac{\rho^2 J_-}{8}\left[\frac{(K-1)J_+^2}{D - J_+/4} + \frac{J_-^2}{D - J_-/4}\right]\\
+\end{aligned}\end{equation}
+Setting \(J_+ = J_-\) leads to the critical fixed point at \(J_+^* = J_-^* = J_* = \frac{8}{K \rho}\).
+We now perturb around this fixed-point by defining new variables \(j_\pm = J_\pm - J_*\).
+We also assume that \(D - J_\pm / 4 \simeq D - J_*/4\).
+The RG equations then take the form
+\begin{equation}\begin{aligned}
+	\frac{\Delta j_+}{|\Delta D|} &= \frac{\rho J_+}{D - J_*/4}\left[J_+ - \frac{\rho}{8}\left[(K-1)J_+^2 + J_-^2\right]\right]\\
+				      &= \frac{\rho J_+}{D - J_*/4}\left[j_+ + J_*- \frac{1}{K J_*}\left[(K-1)\left(J_* + j_+\right)^2 + \left(J_* + j_-\right)^2\right]\right]\\
+				      &= \frac{\rho J_+}{K J_*\left(D - J_*/4\right)}\left[KJ_*\left(j_+ + J_*\right) - (K-1)\left(J_* + j_+\right)^2 - \left(J_* + j_-\right)^2\right]\\
+				      &= \frac{\rho J_+}{K J_*\left(D - J_*/4\right)}\left[K\left(J_*j_+ + J_*^2\right) - (K-1)\left(J_*^2 + j_+^2 + 2J_* j_+\right) - \left(J_*^2 + j_-^2 + 2J_* j_-\right)\right]\\
+				      &= \frac{\rho J_+}{K J_*\left(D - J_*/4\right)}\left[KJ_*j_+ - (K-1)\left(j_+^2 + 2J_* j_+\right) - \left(j_-^2 + 2J_* j_-\right)\right]\\
+				      &= \frac{\rho J_+}{K J_*\left(D - J_*/4\right)}\left[-\left(K - 2\right)J_*j_+ - (K-1)j_+^2 - j_-^2 - 2J_* j_-\right]\\
+	\frac{\Delta j_-}{|\Delta D|} &= \frac{J_- \rho}{D - J_*/4}\left[J_- - \frac{\rho}{8}\left[(K-1)J_+^2 + J_-^2\right]\right]\\
+				      &= \frac{J_- \rho}{K J_*\left(D - J_*/4\right)}\left[K\left(J_*j_- + J_*^2\right) - (K-1)\left(J_*^2 + j_+^2 + 2J_* j_+\right) - \left(J_*^2 + j_-^2 + 2J_* j_-\right)\right]\\
+				      &= \frac{J_- \rho}{K J_*\left(D - J_*/4\right)}\left[\left(K - 2\right)J_*j_-  - j_-^2 - (K-1)j_+^2 - 2(K-1)J_* j_+\right]\\
+\end{aligned}\end{equation}
+We will first look at the special case of \(K=2\), the two channel Kondo model. The equations simplify to
+\begin{equation}\begin{aligned}
+	\frac{\Delta j_\pm}{|\Delta D|} = \frac{J_\pm \rho}{K J_*\left(D - J_*/4\right)}\left[- \left(j_+^2 + j_-^2\right) - 2J_* j_\mp\right]\\
+\end{aligned}\end{equation}
+For \(j_- < 0, j_+ > 0\), we have \(\Delta j_- < 0\).
+The coupling \(J_-\) therefore becomes irrelevant, and the problem reduces to the single-channel Kondo problem.
+We already know the URG equation for the single-channel Kondo problem:
+\begin{equation}\begin{aligned}
+	\frac{\Delta j_+}{|\Delta D|} = \frac{J_+^2 \rho}{D - J_+/4}~,
+\end{aligned}\end{equation}
+and it leads to the strong-coupling fixed point
+
+We now look at the general \(K\) channel case.
+Let us first look at the regime \(j_- < 0, j_+ > 0\).
+In this regime, we have \(\Delta j_- < 0\), which means \(j_-\) will flow to larger negative values until it reaches \(j_- = -J_*\) such that \(J_- = J_* + j_- = 0\).
+\(j_+\) is, on the other hand, relevant for small values of \(j_\pm\).
+It will continue to grow until the numerator of \(\Delta j_+\) vanishes.
+This condition is given by
+\begin{equation}\begin{aligned}
+	\left(K - 2\right)J_*j_+ + (K-1)j_+^2 + j_-^2 + 2J_* j_- = 0
+\end{aligned}\end{equation}
+Substituting \(j_- = -J_*\) gives
+\begin{equation}\begin{aligned}
+	(K-1)j_+^2 + \left(K - 2\right)J_*j_+ - J_*^2 = 0
+\end{aligned}\end{equation}
+Solving for \(j_+\) gives
+\begin{equation}\begin{aligned}
+	j_{+,*} = \frac{-J_*(K-2) \pm \sqrt{(K-2)^2 J_*^2 + 4(K-1)J_*^2}}{2(K-1)} = \frac{J_*}{2(K-1)}\left[-(K-2) \pm K\right] = \frac{J_*}{K-1}
+\end{aligned}\end{equation}
+At the final step, we chose the positive solution, because \(j_+\) is relevant in this regime. The new fixed-point value of \(J_+\) is therefore
+\begin{equation}\begin{aligned}
+	J_+ = J_* + \frac{J_*}{K-1} = \frac{\frac{8}{K \rho} K}{K - 1} = \frac{8}{(K-1)\rho}
+\end{aligned}\end{equation}
+In other words, the \(K\) channel fixed-point flows to the \(K-1\) channel fixed-point.
+
+In the opposite regime \(j_- > 0, j_+ < 0\), \(\Delta j_+\) is negative.
+It has been checked numerically that \(J_+\) ultimately flows to zero in this regime (fig.
+\ref{irrel_Jplus}), and \(J_-\) remains relevant.
+Since there is no numerator fixed-point in the relevant coupling \(J_-\) and because all other couplings are irrelevant, the equation for \(J_-\) is replaced by the single-channel Kondo coupling URG equation, and the low-energy physics is then of strong-coupling..
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.45\textwidth]{../numerics/irr_Jp_K=3.pdf}
+	\includegraphics[width=0.45\textwidth]{../numerics/irr_Jp_K=50.pdf}
+	% \caption{../numerics/irr_Jp_K=3.pdf}
+	\label{irrel_Jplus}
+\end{figure}
 

### 2021-11-30 notes/multi-channel-urg.tex
forgot to add xlabel,ylabel,title
explained the difference from CFT entropy,made sure to account for the combinatorial degeneracy in the magnetization and added all the references

@@
 \usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
-% \usepackage[margin=0.2in,top=0.5in,bottom=0.5in]{geometry}
-\numberwithin{equation}{section}
 \allowdisplaybreaks
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-% \usepackage{ebgaramond}
 \begin{document}
@@
 \subsection{Introduction}
-The multi-channel Kondo model is described by the Hamiltonian
+The multi-channel Kondo model \cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik} is described by the Hamiltonian
 \begin{equation}\begin{aligned}
@@
 \(\vec S_d, \vec s\) are the impurity and conduction bath spin vectors.
-The renormalization at step \(j\) is given by
+The renormalization at step \(j\) \cite{anirbanurg1,anirbanurg2,anirbanmott1,anirbanmott2,siddharthacpi,santanukagome} is given by
 \begin{equation}\begin{aligned}
@@
 This equation has a stable fixed point at \(J^* = \frac{8}{\rho K}\).
+The value of the fixed point agrees with the poor man's scaling calculation in \cite{tripathi2018landau}, but differs from the value of \(\frac{2}{\rho K}\) obtained in other references \cite{Kuramoto1998,Kogan_2018} \textbf{[MOST PROBABLY THERE ARE OTHER REFERENCES]}.
 
@@
 For \(j_- < 0, j_+ > 0\), we have \(\Delta j_- < 0\).
-The coupling \(J_-\) therefore becomes irrelevant, and the problem reduces to the single-channel Kondo problem.
-We already know the URG equation for the single-channel Kondo problem:
+The coupling \(J_-\) therefore becomes irrelevant.
+For small \(j_+\), we have \(j_+^2 < 2J_* |j_-|\)  and \(\Delta j_+ > 0\).
+This means that the isotropic fixed-point is repulsive under anisotropy \cite{Noz_blandin_1980}.
+The coupling \(j_+\) being relevant means we have a single-channel Kondo problem.
+We already know the non-perturbative URG equation for the single-channel Kondo problem:
 \begin{equation}\begin{aligned}
@@
 	\includegraphics[width=0.45\textwidth]{../numerics/irr_Jp_K=50.pdf}
-	% \caption{../numerics/irr_Jp_K=3.pdf}
+	\caption{Flow of the coupling \(J_+\) when \(j_+ < 0\) for two values of \(K\)}
 	\label{irrel_Jplus}
@@
 \begin{equation}\begin{aligned}
+	\label{extra_degen}
 	r^K_M = {}^{K-1}C_{K/2 - M}
@@
 \end{aligned}\end{equation}
-At \(T \to 0\), only the most negative energy \(E_\text{min}\) survives. Assuming a non-degenerate ground state for \(h \neq 0\), the zero temperature free energy becomes
+At \(T \to 0\), only the most negative energy \(E_\text{min}\) survives. Assuming a \(d^\prime_\text{gs}-\)fold degenerate ground state for \(h \neq 0\), the zero temperature free energy becomes
 \begin{equation}\begin{aligned}
-	F(h\neq 0, T\to 0) = -\frac{1}{\beta}\ln e^{-\beta E_\text{min}} = E_\text{min}
+	F(h\neq 0, T\to 0) = -\frac{1}{\beta}\ln d^\prime_\text{gs}e^{-\beta E_\text{min}} = E_\text{min}- k_B T\ln d^\prime_\text{gs}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	&\frac{J}{2}M \pm h\left(M + \frac{1}{2}\right),\\
-	&-\frac{J}{4}\pm \frac{J}{2}\left(M + \frac{1}{2}\right) + h\left( m + \frac{1}{2} \right), m \in \left[-M, M-1\right] 
+	(a) \quad&\frac{J}{2}M \pm h\left(M + \frac{1}{2}\right)\\
+	(b) \quad&-\frac{J}{4}\pm \frac{J}{2}\left(M + \frac{1}{2}\right) + h\left( m + \frac{1}{2} \right), m \in \left[-M, M-1\right] 
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
+which means \(E_\text{min} = -\frac{J}{2}\left( M + 1 \right) - |h|\left(M - \frac{1}{2}\right)\). We also know, from eq.~\ref{extra_degen}, that \(d^\prime_\text{gs} = {}^{K-1}C_{K/2 - K/2} = 1\).
 The free energy for a non-zero field is therefore
@@
 This is a general result that holds for any system with a \(d_\text{gs}\)-fold degenerate ground state.
-For the star graph problem, we have a \(K-\)fold degenerate ground state, so the \(T=0\) entropy of the star graph Hamiltonian with \(K\) outer spins is
+For the star graph problem, we have a \(K-\)fold degenerate ground state, so the \(T=0\) entropy of the star graph Hamiltonian with \(K\) outer spins is \(S(T\to 0) = k_B \ln K\).
+The impurity contribution to the total entropy is obtained by subtracting the entropy of the non-interacting bath.
+But we know that the entropy of a free Fermi gas vanishes at low temperatures.
+The impurity contribution is therefore
 \begin{equation}\begin{aligned}
-	S(T\to 0) = k_B \ln K
+	\label{res_entropy}
+	S_\text{imp}(T\to 0) = k_B \ln K
 \end{aligned}\end{equation}
+
+We wish to point out that this value is different from the "standard" result 
+\begin{equation}\begin{aligned}
+\label{cft_entropy}
+S = \ln 2\cos \frac{\pi}{K+2}
+\end{aligned}\end{equation}
+obtained from other methods like the Bethe ansatz (BA) and conformal field theory (CFT) calculations \cite{Gan_Andrei_Coleman_1993,andrei_destri_1984,Tsvelick_weigmann_mchannel_1985,sacramento1989,emery_kivelson,affleck_1991_overscreen}.
+The difference is not only in the value but also in the origin.
+Eq.~\ref{res_entropy} indicates the thermal entropy coming purely from the quantum mechanical degeneracy of the star graph problem (which is the zero mode of the full multi-channel Kondo problem), while the result eq.~\ref{cft_entropy} presumably arises from the lowest-lying excitations on top of the zero mode arising from the conduction bath \(k-\)states.
+Another difference lies in the fact that while eq.~\ref{res_entropy} holds true independent of system size, eq.~\ref{cft_entropy} is correct only in the thermodynamic limit and only if the limit of system \(N \to \infty\) is taken prior to taking the limit of temperature \(T \to 0\) \cite{Gan_Andrei_Coleman_1993,rozhkov_1998,vondelft_prl_1998}.
+We note however that the entropy coming from the degeneracy is larger than that coming from the excitations (fig.~\ref{entropy_comparison}, and consequently plays a very important role in the physics of the multi-channel Kondo problem, being responsible for the non-Fermi liquid physics and the critical behaviour near the fixed point.
 
@@
 	\caption{Comparison of star graph zero temperature entropy with CFT/Bethe ansatz formula}
+	\label{entropy_comparison}
 \end{figure}
@@
 
-\clearpage
 \appendix
@@
 \end{aligned}\end{equation}
+
+\bibliographystyle{apsrev4-1}
+\bibliography{multi-channel-urg}
 \end{document}

### 2021-11-30 notes/multi-channel-urg.tex
added a section on the symmetries of the star graph problem

@@
 \maketitle
-\section{Derivation of URG equations for the multi-channel Kondo model}
-
-\subsection{Introduction}
-The multi-channel Kondo model \cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik} is described by the Hamiltonian
+\section{Introduction of the Hamiltonian and symmetries of the zero mode}
+The isotropic multi-channel Kondo model \cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik} is described by the Hamiltonian
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-It is mostly identical to the single-channel Kondo model: \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels.
+In the above equation, \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels.
 \(\vec S_d, \vec s\) are the impurity and conduction bath spin vectors.
-The renormalization at step \(j\) \cite{anirbanurg1,anirbanurg2,anirbanmott1,anirbanmott2,siddharthacpi,santanukagome} is given by
+The presence of a common spin-exchange coupling \(J\) for all the channels is what makes the problem isotropic with respect to the channels.
+
+The zero mode of this Hamiltonian is obtained by keeping only the central component of the Fourier transform of the kinetic energy part:
 \begin{equation}\begin{aligned}
-	\Delta H_j = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right), && c^\dagger T = J \sum_{k < \Lambda_j, \alpha}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, &H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
+	\epsilon(\vec r) \simeq \delta_{\vec r,0}\epsilon(\vec r = 0) \implies \epsilon_{\vec k} = \sum_{\vec r}\epsilon(\vec r) e^{i \vec{k}\cdot\vec{r}} = \epsilon(\vec r=0) = \sum_q \epsilon_{\vec q}
+\end{aligned}\end{equation}
+Assuming the dispersion already includes the chemical potential \(\mu\), we have 
+\begin{equation}\begin{aligned}
+\sum_q \epsilon_{\vec q} = \rho \Delta \epsilon\sum_{\epsilon=\epsilon_F-D}^{\epsilon_F + D} \left(\epsilon - \mu\right) = \rho\Delta \epsilon\left(\epsilon_F - \mu\right)
+\end{aligned}\end{equation}
+If we set the chemical potential at the Fermi surface, this summation vanishes.
+\begin{equation}\begin{aligned}
+	\epsilon_{\vec k} =  \rho\Delta \epsilon\left(\epsilon_F - \mu\right) = 0
+\end{aligned}\end{equation}
+and the zero mode Hamiltonian is then just the spin-exchange part of the Hamiltonian:
+\begin{equation}\begin{aligned}
+	H_\text{zero mode} = J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
+\end{aligned}\end{equation}
+We can make one more identification: the sum over the spins in momentum space amount to a local interaction at the zeroth sites of the indicates channels: \(\sum_k {c^\gamma_{k\alpha}}^\dagger = {c^\gamma_{\vec r=0, \alpha}}^\dagger\), This suggests we shoud define spin operators for the zeroth sites of the channels:
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime} {s}^a_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime} = {s}^a_{\alpha\alpha^\prime}{c^\gamma_{0\alpha}}^\dagger c^\gamma_{0\alpha^\prime} = s_\gamma^a
+\end{aligned}\end{equation}
+In the terms of the local spin operators \(\vec s_\gamma = (s_\gamma^x,s_\gamma^y,s_\gamma^z)\), we can define the total spin of the zero mode of the bath: \(\vec s_\text{tot} = \sum_\gamma \vec s_\gamma\) and the zero mode Hamiltonian then takes the simpler form
+\begin{equation}\begin{aligned}
+	H_\text{zero mode} = J \vec{S_d}\cdot\vec{s}_\text{tot}
+\end{aligned}\end{equation}
+
+This zero mode Hamiltonian commutes with a number of operators, revealing various symmetries of the problem.
+The first such operators is \(s_\text{tot}^2\).
+Henceforth we will drop the label \(\text{zero mode}\).
+To see the commuation, note that \(s_\text{tot}^2\) can be written as \(s_\text{tot}^2 = \sum_{i=x,y,z}\left(s_\text{tot}^i\right)^2\).
+This then gives
+\begin{equation}\begin{aligned}
+\left[s_\text{tot}^2, H\right] = \left[\sum_{i=x,y,z}{s^i_\text{tot}}^2, J \sum_{i=x,y,z} S_d^i s^i_\text{tot}\right] = \sum_{i,j}J S_d^i \left\{s_\text{tot}^i, \left[s_\text{tot}^i,s_\text{tot}^j\right]\right\} = \sum_{i,j}J S_d^i \left\{s_\text{tot}^i, i \epsilon^{ijk}s^k_\text{tot}\right\} = 0
+\end{aligned}\end{equation}
+The total spin angular  momentum operator \(S^2 = \left(\vec S_d + \vec s_\text{tot}\right)^2 \) also commutes with the Hamiltonian. To see this, note that we can rewrite the operator as
+\begin{equation}\begin{aligned}
+	S^2 = \left(\vec S_d + \vec s_\text{tot}\right)^2 = \frac{3}{4} + s_\text{tot}\left(s_\text{tot} + 1\right) + \frac{2}{J} H
+\end{aligned}\end{equation}
+Since we already know that \(s_\text{tot}\) commutes with \(H\), we have that \(\left[S^2, H\right] = 0\).
+
+One final operator that we will look at is the spin parity operator \(\pi^a = S_d^a \otimes_{i=1}^K s_i^a\).
+\begin{equation}\begin{aligned}
+	\left[H, \pi^a\right] = J\sum_{b,j} \left[S_d^b s_j^b, S_d^a \otimes_{i=1}^K s_i^a\right] = \sum_{bj}\left(S_d^b S_d^a s^b_j s^a_j - S_d^a S_d^b s^a_j s^b_j\right) \otimes_{i<j}s_i^a \otimes_{i>j}s^a_i = 0
+\end{aligned}\end{equation}
+
+\section{Derivation of URG equations for the multi-channel Kondo model}
+
+\subsection{URG procedure}
+The URG method \cite{anirbanurg1,anirbanurg2,anirbanmott1,anirbanmott2,siddharthacpi,santanukagome} involves applying unitary transformations to decouple high energy degrees of freedom.
+The renormalization at step \(j\) is given by
+\begin{equation}\begin{aligned}
+	\Delta H_j = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)~,
+\end{aligned}\end{equation}
+where \(c^\dagger T\) represents the off-diagonal part of the Hamiltonian with respect to the fluctuations of the electron we are decoupling and \(H_D\) is the diagonal part with respect to the same electron.
+Assuming we are decoupling a particular electron \(q\beta\), we have
+\begin{equation}\begin{aligned}
+	c^\dagger T = J \sum_{k < \Lambda_j, \alpha}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, && H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
 \end{aligned}\end{equation}

### 2021-11-30 notes/multi-channel-urg.tex
obtained the pi^x operator that takes us between ground states

@@
 
-One final operator that we will look at is the spin parity operator \(\pi^a = S_d^a \otimes_{i=1}^K s_i^a\).
+One final operator that we will look at is the spin parity operator \(\pi^a = \sigma_d^a \otimes_{i=1}^K \sigma_i^a\).
 \begin{equation}\begin{aligned}
-	\left[H, \pi^a\right] = J\sum_{b,j} \left[S_d^b s_j^b, S_d^a \otimes_{i=1}^K s_i^a\right] = \sum_{bj}\left(S_d^b S_d^a s^b_j s^a_j - S_d^a S_d^b s^a_j s^b_j\right) \otimes_{i<j}s_i^a \otimes_{i>j}s^a_i = 0
+	\left[H, \pi^a\right] = J\sum_{b,j} \left[S_d^b s_j^b, \sigma_d^a \otimes_{i=1}^K \sigma_i^a\right] = \sum_{bj}\left(S_d^b \sigma_d^a s^b_j \sigma^a_j - \sigma_d^a S_d^b \sigma^a_j s^b_j\right) \otimes_{i<j}\sigma_i^a \otimes_{i>j}\sigma^a_i = 0
 \end{aligned}\end{equation}
+
+The zero mode Hamiltonian can be diagonalized.
+Since the Hamiltonian commutes with \(s_\text{tot}^2\), it is already block-diagonal in the quantum number \(s_\text{tot}\).
+Let us represent the quantum number of \(s_\text{tot}^z\) by \(m\).
+For a particular \(s_\text{tot}\), \(m\) can take values from the set \(\left[-s_\text{tot}, s_\text{tot}\right] \).
+The spin \(S_d^z\) can also take values \(\pm \frac{1}{2}\).
+From now on, we will assume we are in the subspace of a particular \(s_\text{tot} = M\), so we will ignore that quantum number and write the kets simply as \(\ket{S_d^z, m}\).
+So, the notation \(\ket{\uparrow,-1}\) means the state with \(S_d^z = \frac{1}{2}\) and \(m = -1\).
+We will now show that even inside the block of \(2\times s_\text{tot}\) (or \(2\times s_\text{tot} + 1\), depending on whether it is odd or even) defined by a particular value of \(s_\text{tot}\), the Hamiltonian actually separates into decoupled \(2\times 2\) blocks.
+To see why, first note that the terminal states \(\ket{\downarrow, -M}\) and \(\ket{\uparrow, M}\) are already eigenstates, because they cannot scatter (the impurity can only flip down, and this would require the bath to flip up, but \(s^z_\text{tot}\) is already at its maximum value \(M\)).
+The other \(2M - 2\) states can be organized into \(2\times 2\) blocks formed by the states \(\ket{\uparrow, m}\) and \(\ket{\downarrow, m+1}\) for \(m \in \left[-M, M-1\right] \).
+The fact that this block does not interact with the other blocks can be easily verified: if there was some other state which when acted upon by the Hamiltonian gave a non-zero projection on \(\ket{\uparrow, m}\), it would have to come from \(S_d^z = \downarrow\), and this would mean the bath spin would have had to flip down.
+This means the bath spin in that state would have to be \(m+1\), and that is precisely the other state in the block.
+
+Defining \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
+\begin{equation}\begin{aligned}
+	H_m = \begin{pmatrix} \frac{Jm}{2} & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\frac{J}{2}(m+1) \end{pmatrix} , m \in \left[-M, M-1\right] 
+\end{aligned}\end{equation}
+The eigenvalues are 
+\begin{equation}\begin{aligned}
+	% \label{eigenvalue}
+	\lambda_{\pm}^{M} = - \frac{J}{4} \pm \frac{J}{2}\left(M + \frac{1}{2}\right) 
+\end{aligned}\end{equation}
+The eigenvalues of the terminal states are \(\frac{JM}{2}\).
+The set of eigenvalues \(\lambda^{M_\text{max}}_-\) form the ground state subspace \(\left\{ \ket{\Psi^M_{m,-}} \right\} \) of degeneracy \(2M_\text{max} = K\).
+This common \(K-\)fold degenerate eigenvalue is \(-\frac{J}{2}(M+1)\).
+The eigenstates for each value of \(M,m\) for the \(2\times 2\) blocks are given by
+\begin{equation}\begin{aligned}
+	\ket{\Psi^M_{m,-}} &= -\sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M + m + 1\right)\ket{\downarrow,M,m+1},& m \in \left[-M, M-1\right] \\
+	\ket{\Psi^M_{m,+}} &= \sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M - m\right)\ket{\downarrow,M,m+1},& m \in \left[-M, M-1\right]
+\end{aligned}\end{equation}
+Note that we are using the index \(m\) simplify to indicate the subsapce from which these eigenstates arise; \(m\) is not a quantum number for that eigenstate.
+The eigenvalue of \(\pi^z\) is, however, a quantum number.
+We have the eigenvalue relation \(\pi^z \ket{S_d^z} = (-1)^{2\left(S_d^z + m\right)}\).
+Applying \(\pi^z\) on these eigenstates gives
+\begin{equation}\begin{aligned}
+	\pi^z\ket{\Psi^M_{m,-}} = -\left( -1 \right)^{2(1/2 + m)}\sqrt{x_m^M}\ket{\uparrow, M, m} + \left( -1 \right)^{2(-1/2 + m + 1)}\left(M + m + 1\right)\ket{\downarrow,M,m+1} = \left( -1 \right) ^{2m+1}\ket{\Psi^M_{m,-}}
+\end{aligned}\end{equation}
+This shows that the operator \(\pi^z\) splits the \(K-\)fold degenerate ground state manifold into two sub-manifolds of \(\pi^z\) parity \(\pm 1\).
+
+It is interesting to calculate the action of the parity operator \(\pi^x\) on these eigenstates. We can write that operator as
+\begin{equation}\begin{aligned}
+	\pi^x = (S_d^+ + S_d^-)\otimes_{i=1}^K \left(s_i^+ + s_i^-\right) 
+\end{aligned}\end{equation}
+We can write the eigenstates of \(s_\text{tot}^z\) in terms of the eigenstates of \(s_i^z\) using their Clebsh-Gordon coefficients:
+\begin{equation}\begin{aligned}
+	\ket{M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}\ket{m_1,m_2,...,m_K} C_{\left\{m_i\right\},m,M}
+\end{aligned}\end{equation}
+where \(C_{\left\{m_i\right\},m,M} = \braket{m_1,m_2,...,m_K|m,M}\) are the Clebsh-Gordon coefficients. Applying the parity operator on the state gives
+\begin{equation}\begin{aligned}
+	\pi^x \ket{S_d^z, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}(S_d^+ + S_d^-)\ket{S_d^z}\otimes_{i=1}^K \left(s_i^+ + s_i^-\right)\ket{m_i} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{-m_i}\\
+	=\sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{-m_i\right\},m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{m_i}
+\end{aligned}\end{equation}
+Using the identity \(\braket{M_1m_1,M_2m_2,\ldots|m,M} = \left( -1 \right)^{\sum_i M_i - M}\braket{M_1, -m_1; M_2 -m_2;\ldots|-m,M}\), we have \(C_{\left\{-m_i\right\},m,M} = C_{\left\{m_i\right\},-m,M}\).
+Substituting this, we get
+\begin{equation}\begin{aligned}
+	\pi^x \ket{S_d^z, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{m_i\right\},-m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{m_i} = \ket{-S_d^z, M, -m}
+\end{aligned}\end{equation}
+The action of \(\pi^x\) on the eigenstates can now be determined:
+\begin{equation}\begin{aligned}
+	\pi^x \ket{\Psi^M_{m,-}} &=-\sqrt{x_m^M}\ket{\downarrow, M, -m} + \left(M + m + 1\right)\ket{\uparrow,M,-m-1} = \ket{\Psi^M_{-m-1,-}}
+\end{aligned}\end{equation}
+The last equality holds up to a minus sign.
+It can be seen that the action of the operator \(\pi^x\) is to interpolate between two ground states of opposite \(\pi^z\) eigenvalues.
+In other words, \(\pi^x\) connects the two sectors of opposite \(\pi^z\) parity.
 

### 2021-11-30 notes/multi-channel-urg.tex
errors in the eigenvalue of pi^z

@@
 \end{aligned}\end{equation}
-Note that we are using the index \(m\) simplify to indicate the subsapce from which these eigenstates arise; \(m\) is not a quantum number for that eigenstate.
+Note that we are using the index \(m\) to indicate the subspace from which these eigenstates arise; \(m\) is not a quantum number for that eigenstate.
 The eigenvalue of \(\pi^z\) is, however, a quantum number.
-We have the eigenvalue relation \(\pi^z \ket{S_d^z} = (-1)^{2\left(S_d^z + m\right)}\).
+We have the eigenvalue relation \(\pi^z \ket{S_d^z} = (-1)^{\frac{1}{2}\left(\sigma^z_d + 2m - 1\right)}\).
 Applying \(\pi^z\) on these eigenstates gives
 \begin{equation}\begin{aligned}
-	\pi^z\ket{\Psi^M_{m,-}} = -\left( -1 \right)^{2(1/2 + m)}\sqrt{x_m^M}\ket{\uparrow, M, m} + \left( -1 \right)^{2(-1/2 + m + 1)}\left(M + m + 1\right)\ket{\downarrow,M,m+1} = \left( -1 \right) ^{2m+1}\ket{\Psi^M_{m,-}}
+	\pi^z\ket{\Psi^M_{m,-}} = -\left(-1\right)^{\frac{1 + 2m - 1}{2}}\sqrt{x_m^M}\ket{\uparrow, M, m} + \left( -1 \right)^{\frac{-1 + 2m + 2 - 1}{2}}\left(M + m + 1\right)\ket{\downarrow,M,m+1} = \left( -1 \right) ^{m}\ket{\Psi^M_{m,-}}
 \end{aligned}\end{equation}
 This shows that the operator \(\pi^z\) splits the \(K-\)fold degenerate ground state manifold into two sub-manifolds of \(\pi^z\) parity \(\pm 1\).
+The odd values of \(m\) form the negative parity sector \(\pi^z = -1\) while the even values form the positive parity sector \(\pi^z = 1\).
 
@@
 \end{aligned}\end{equation}
-We can write the eigenstates of \(s_\text{tot}^z\) in terms of the eigenstates of \(s_i^z\) using their Clebsh-Gordon coefficients:
+We can write the eigenstates of \(s_\text{tot}^z\) in terms of the eigenstates of \(s_i^z\) using their Clebsch-Gordon coefficients:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where \(C_{\left\{m_i\right\},m,M} = \braket{m_1,m_2,...,m_K|m,M}\) are the Clebsh-Gordon coefficients. Applying the parity operator on the state gives
+where \(C_{\left\{m_i\right\},m,M} = \braket{m_1,m_2,...,m_K|m,M}\) are the Clebsch-Gordon coefficients. Applying the parity operator on the state gives
 \begin{equation}\begin{aligned}
@@
 It can be seen that the action of the operator \(\pi^x\) is to interpolate between two ground states of opposite \(\pi^z\) eigenvalues.
-In other words, \(\pi^x\) connects the two sectors of opposite \(\pi^z\) parity.
+In other words, \(\pi^x\) connects the two sectors of opposite \(\pi^z\) parity:
+\begin{equation}\begin{aligned}
+	\pi^x \ket{(-1)^m} = \ket{(-1)^{-1-m}} = \ket{-(-1)^m}
+\end{aligned}\end{equation}
 

### 2021-12-01 notes/multi-channel-urg.tex
wrote mdx in terms of pix

@@
 This common \(K-\)fold degenerate eigenvalue is \(-\frac{J}{2}(M+1)\).
-The eigenstates for each value of \(M,m\) for the \(2\times 2\) blocks are given by
-\begin{equation}\begin{aligned}
-	\ket{\Psi^M_{m,-}} &= -\sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M + m + 1\right)\ket{\downarrow,M,m+1},& m \in \left[-M, M-1\right] \\
-	\ket{\Psi^M_{m,+}} &= \sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M - m\right)\ket{\downarrow,M,m+1},& m \in \left[-M, M-1\right]
-\end{aligned}\end{equation}
-Note that we are using the index \(m\) to indicate the subspace from which these eigenstates arise; \(m\) is not a quantum number for that eigenstate.
-The eigenvalue of \(\pi^z\) is, however, a quantum number.
-We have the eigenvalue relation \(\pi^z \ket{S_d^z} = (-1)^{\frac{1}{2}\left(\sigma^z_d + 2m - 1\right)}\).
+The normalized eigenstates of the \(2\times 2\) blocks for each value of \(m\) are given by
+\begin{equation}\begin{aligned}
+	\ket{\Psi^M_{m,-}} &= \frac{1}{\sqrt{(M+m+1)(1+2M)}}\left[-\sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M + m + 1\right)\ket{\downarrow,M,m+1}\right],& m \in \left[-M, M-1\right] \\
+	\ket{\Psi^M_{m,+}} &= \frac{1}{\sqrt{(M -m)(M - m + 1)}}\left[\sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M - m\right)\ket{\downarrow,M,m+1}\right],& m \in \left[-M, M-1\right]
+\end{aligned}\end{equation}
+Note that the index \(m\) that we are using to label tje eigenvalues is actually related to a conserved quantity; the total spin operator along \(z\), \(S^z\).
+That is, the eigenstates \(\ket{\Psi^M_{m,\pm}}\) have \(S^z = S_d^z + s_\text{tot}^z = m + \frac{1}{2}\).
+
+We can also use the eigenvalues of \(\pi^z\) to label the eigenstates.
+We have the eigenvalue relation \(\pi^z \ket{S^z} = (-1)^{S^z - \frac{1}{2}}\ket{S^z}\).
 Applying \(\pi^z\) on these eigenstates gives
 \begin{equation}\begin{aligned}
-	\pi^z\ket{\Psi^M_{m,-}} = -\left(-1\right)^{\frac{1 + 2m - 1}{2}}\sqrt{x_m^M}\ket{\uparrow, M, m} + \left( -1 \right)^{\frac{-1 + 2m + 2 - 1}{2}}\left(M + m + 1\right)\ket{\downarrow,M,m+1} = \left( -1 \right) ^{m}\ket{\Psi^M_{m,-}}
+	\pi^z\ket{\Psi^M_{m,-}} = \left( -1 \right) ^{m}\ket{\Psi^M_{m,-}}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\pi^x \ket{\Psi^M_{m,-}} &=-\sqrt{x_m^M}\ket{\downarrow, M, -m} + \left(M + m + 1\right)\ket{\uparrow,M,-m-1} = \ket{\Psi^M_{-m-1,-}}
-\end{aligned}\end{equation}
-The last equality holds up to a minus sign.
-It can be seen that the action of the operator \(\pi^x\) is to interpolate between two ground states of opposite \(\pi^z\) eigenvalues.
-In other words, \(\pi^x\) connects the two sectors of opposite \(\pi^z\) parity:
-\begin{equation}\begin{aligned}
-	\pi^x \ket{(-1)^m} = \ket{(-1)^{-1-m}} = \ket{-(-1)^m}
+	\pi^x \ket{\Psi^M_{m,-}} &=-\sqrt{x_m^M}\ket{\downarrow, M, -m} + \left(M + m + 1\right)\ket{\uparrow,M,-m-1} = -\ket{\Psi^M_{-m-1,-}}
+\end{aligned}\end{equation}
+It can be seen that the action of the operator \(\pi^x\) is to interpolate between two ground states of opposite \(\pi^z\) eigenvaluesand, more specifically, opposite \(S^z\) values
+\begin{equation}\begin{aligned}
+	\pi^x \ket{S^z} \to \ket{-S^z}
+\end{aligned}\end{equation}
+
+We can show that the impurity magnetization along the \(x-\)direction in some specific ground states can be related to matrix elements of the string operator \(\pi^x\).
+The most general ground state is obtained by taking a general linear combination of all the normalized ground states:
+\begin{equation}\begin{aligned}
+	\ket{g^n_m} = \frac{1}{\sqrt 2}\left[\ket{\Psi^M_{m,-}} + e^{i\theta}\ket{\Psi^M_{m+n,-1}}\right], m \in \left[-M, M-2\right] , n \in \left[1, M - m - 1\right] 
+\end{aligned}\end{equation}
+The expectation value of the impurity spin along \(x\) in this state is given by
+\begin{equation}\begin{aligned}
+	\left(m_d^x\right)_m^n = \braket{g^n_m | \sigma_d^x | g^n_m}
+\end{aligned}\end{equation}
+The action of \(\sigma_d^x\) is as follows:
+\begin{equation}\begin{aligned}
+	\sigma_d^x \ket{\Psi^M_{m,-}} = \frac{1}{\sqrt{(M+m+1)(1+2M)}}\left[-\sqrt{x_m^M}\ket{\downarrow, M, m} + \left(M + m + 1\right)\ket{\uparrow,M,m+1}\right]
+\end{aligned}\end{equation}
+which means that the only \(\ket{\Psi^M_{m+n,-}}\) with \(n > 0\) that give a non-zero inner product with \(\sigma_d^x \ket{\Psi^M_{m,-}}\) is \(n=1\). This observation then gives
+\begin{equation}\begin{aligned}
+	\left(m_d^x\right)_m^n = \delta_{n,1}\braket{g^1_m | \sigma_d^x | g^1_m} = \delta_{n,1}\left[e^{i\theta}\braket{\Psi^M_{m+1,-}|\sigma_d^x| \Psi^M_{m,-}} + \text{h.c.}\right] = \delta_{n,1}\left[e^{i\theta}\braket{\Psi^M_{m+1,-}|\sigma_d^x \pi^x | \Psi^M_{-m-1,-}} + \text{h.c.}\right]
+\end{aligned}\end{equation}
+\textit{We thus see that the impurity magnetization \(\left(m_d^x\right)_m^n\) along \(x\) for the state \(\ket{g^n_m}\) is determined by the matrix element of the string operator \(\sigma^x_d \pi^x\)}.
+
+For \(m = -M\), we get
+\begin{equation}\begin{aligned}
+	\braket{\Psi^M_{-M+1,-}|\sigma_d^x \pi^x | \Psi^M_{M - 1,-}} = \frac{\sqrt{2M-1}}{2M + 1}
+\end{aligned}\end{equation}
+The ground state manifold is defined by \(M = K/2\). Using this, we can write
+\begin{equation}\begin{aligned}
+	\left(m_d^x\right)_{-M}^1 = \left[\braket{\Psi^M_{1-M,-}|\sigma_d^x \pi^x | \Psi^M_{M - 1,-}} + \text{h.c.}\right] = \frac{2\sqrt{2M-1}}{2M + 1} = \frac{2\sqrt{K-1}}{K+1}
+\end{aligned}\end{equation}
+
+We can similarly calculate the magnetization along the \(z-\)direction. The most general ground state is
+\begin{equation}\begin{aligned}
+	\ket{g} = \sum_{m=-M}^{M-1} C_m \ket{\Psi^M_{m,-}}, &&& m \in \left[-M, M-1\right], &&& \sum_m |C_m|^2 = 1
+\end{aligned}\end{equation}
+The expectation value of \(\sigma^d_z\) will be non-zero only in the diagonal terms: \(\braket{\Psi^M_m | \sigma^z_d | \Psi^M_{m^\prime}} = \delta_{mm^\prime}\braket{\Psi^M_m | \sigma^z_d | \Psi^M_{m}}\).
+Using this, we get
+\begin{equation}\begin{aligned}
+	\braket{g|\sigma^z_d|g} = \sum_{m=-M}^{M-1} |C_m|^2 \frac{\left[x_m^M - \left(M + m + 1\right)^2\right]}{{(M+m+1)(1+2M)}}
+\end{aligned}\end{equation}
+For the simpler case when \(C_m = \delta_{m,\pm (M - \frac{1}{2}) - \frac{1}{2}}\), we get
+\begin{equation}\begin{aligned}
+	\braket{g_\pm|\sigma^z_d|g_\pm} = \pm \frac{2M-1}{2M+1} = \pm \frac{K-1}{K+1}
 \end{aligned}\end{equation}
@@
 The difference is not only in the value but also in the origin.
-Eq.~\ref{res_entropy} indicates the thermal entropy coming purely from the quantum mechanical degeneracy of the star graph problem (which is the zero mode of the full multi-channel Kondo problem), while the result eq.~\ref{cft_entropy} presumably arises from the lowest-lying excitations on top of the zero mode arising from the conduction bath \(k-\)states.
-Another difference lies in the fact that while eq.~\ref{res_entropy} holds true independent of system size, eq.~\ref{cft_entropy} is correct only in the thermodynamic limit and only if the limit of system \(N \to \infty\) is taken prior to taking the limit of temperature \(T \to 0\) \cite{Gan_Andrei_Coleman_1993,rozhkov_1998,vondelft_prl_1998}.
-We note however that the entropy coming from the degeneracy is larger than that coming from the excitations (fig.~\ref{entropy_comparison}, and consequently plays a very important role in the physics of the multi-channel Kondo problem, being responsible for the non-Fermi liquid physics and the critical behaviour near the fixed point.
+Eq.~\ref{res_entropy} describes the thermal entropy coming purely from the quantum mechanical degeneracy of the star graph problem (which is the zero mode of the full multi-channel Kondo problem), while the result eq.~\ref{cft_entropy} presumably arises from the lowest-lying excitations on top of the zero mode arising from the conduction bath \(k-\)states.
+Another difference lies in the fact that while eq.~\ref{res_entropy} holds true independent of system size, eq.~\ref{cft_entropy} is correct only in the thermodynamic limit and only if the limit of system size \(L \to \infty\) is taken prior to taking the limit of temperature \(T \to 0\) \cite{Gan_Andrei_Coleman_1993,rozhkov_1998,vondelft_prl_1998}.
+We note however that the entropy coming from the degeneracy is larger than that coming from the excitations (fig.~\ref{entropy_comparison}), and consequently plays a very important role in the physics of the multi-channel Kondo problem, being responsible for the non-Fermi liquid physics and the critical behaviour near the fixed point.
 

### 2021-12-02 notes/multi-channel-urg.tex
wrote down the required transformation to make the critical point self-dual

@@
 \documentclass{revtex4-2}
-\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
+\usepackage{braket,amsmath,amssymb,graphicx,float,paralist}
+\usepackage[hidelinks]{hyperref}
 \allowdisplaybreaks
@@
 \maketitle
-\section{Introduction of the Hamiltonian and symmetries of the zero mode}
+\tableofcontents
+\section{Introduction of the Hamiltonian and its zero mode}
 The isotropic multi-channel Kondo model \cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik} is described by the Hamiltonian
-\begin{equation}\begin{aligned}
+\begin{align}
+	\label{mc_ham}
 	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
-\end{aligned}\end{equation}
+\end{align}
 In the above equation, \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels.
@@
 The zero mode of this Hamiltonian is obtained by keeping only the central component of the Fourier transform of the kinetic energy part:
-\begin{equation}\begin{aligned}
+\begin{align}
 	\epsilon(\vec r) \simeq \delta_{\vec r,0}\epsilon(\vec r = 0) \implies \epsilon_{\vec k} = \sum_{\vec r}\epsilon(\vec r) e^{i \vec{k}\cdot\vec{r}} = \epsilon(\vec r=0) = \sum_q \epsilon_{\vec q}
-\end{aligned}\end{equation}
+\end{align}
 Assuming the dispersion already includes the chemical potential \(\mu\), we have 
-\begin{equation}\begin{aligned}
+\begin{align}
 \sum_q \epsilon_{\vec q} = \rho \Delta \epsilon\sum_{\epsilon=\epsilon_F-D}^{\epsilon_F + D} \left(\epsilon - \mu\right) = \rho\Delta \epsilon\left(\epsilon_F - \mu\right)
-\end{aligned}\end{equation}
+\end{align}
 If we set the chemical potential at the Fermi surface, this summation vanishes.
-\begin{equation}\begin{aligned}
+\begin{align}
 	\epsilon_{\vec k} =  \rho\Delta \epsilon\left(\epsilon_F - \mu\right) = 0
-\end{aligned}\end{equation}
+\end{align}
 and the zero mode Hamiltonian is then just the spin-exchange part of the Hamiltonian:
-\begin{equation}\begin{aligned}
+\begin{align}
 	H_\text{zero mode} = J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
-\end{aligned}\end{equation}
+\end{align}
 We can make one more identification: the sum over the spins in momentum space amount to a local interaction at the zeroth sites of the indicates channels: \(\sum_k {c^\gamma_{k\alpha}}^\dagger = {c^\gamma_{\vec r=0, \alpha}}^\dagger\), This suggests we shoud define spin operators for the zeroth sites of the channels:
-\begin{equation}\begin{aligned}
+\begin{align}
 	\sum_{kk^\prime} {s}^a_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime} = {s}^a_{\alpha\alpha^\prime}{c^\gamma_{0\alpha}}^\dagger c^\gamma_{0\alpha^\prime} = s_\gamma^a
-\end{aligned}\end{equation}
+\end{align}
 In the terms of the local spin operators \(\vec s_\gamma = (s_\gamma^x,s_\gamma^y,s_\gamma^z)\), we can define the total spin of the zero mode of the bath: \(\vec s_\text{tot} = \sum_\gamma \vec s_\gamma\) and the zero mode Hamiltonian then takes the simpler form
-\begin{equation}\begin{aligned}
+\begin{align}
+	\label{zeromode_ham}
 	H_\text{zero mode} = J \vec{S_d}\cdot\vec{s}_\text{tot}
-\end{aligned}\end{equation}
-
+\end{align}
+
+\section{SYmmetries of the Hamiltonian}
 This zero mode Hamiltonian commutes with a number of operators, revealing various symmetries of the problem.
@@
 This then gives
-\begin{equation}\begin{aligned}
+\begin{align}
 \left[s_\text{tot}^2, H\right] = \left[\sum_{i=x,y,z}{s^i_\text{tot}}^2, J \sum_{i=x,y,z} S_d^i s^i_\text{tot}\right] = \sum_{i,j}J S_d^i \left\{s_\text{tot}^i, \left[s_\text{tot}^i,s_\text{tot}^j\right]\right\} = \sum_{i,j}J S_d^i \left\{s_\text{tot}^i, i \epsilon^{ijk}s^k_\text{tot}\right\} = 0
-\end{aligned}\end{equation}
+\end{align}
 The total spin angular  momentum operator \(S^2 = \left(\vec S_d + \vec s_\text{tot}\right)^2 \) also commutes with the Hamiltonian. To see this, note that we can rewrite the operator as
-\begin{equation}\begin{aligned}
+\begin{align}
 	S^2 = \left(\vec S_d + \vec s_\text{tot}\right)^2 = \frac{3}{4} + s_\text{tot}\left(s_\text{tot} + 1\right) + \frac{2}{J} H
-\end{aligned}\end{equation}
-Since we already know that \(s_\text{tot}\) commutes with \(H\), we have that \(\left[S^2, H\right] = 0\).
+\end{align}
+Since we already know that \(s_\text{tot}\) commutes with \(H\), we have that \(\left[S^2, H\right] = 0\). The \(z-\)component of this total spin operator also commutes with the Hamiltonian:
+\begin{align}
+	\left[S^z, H\right] = \left[S^z, J \left(\frac{1}{2}S^2 - \frac{3}{8} - \frac{1}{2}s_\text{tot}^2\right) \right]  = \frac{J}{2}\left(\left[S^z, S^2\right] - \left[s_\text{tot}^z, s_\text{tot}^2\right] \right) = 0
+\end{align}
 
 One final operator that we will look at is the spin parity operator \(\pi^a = \sigma_d^a \otimes_{i=1}^K \sigma_i^a\).
-\begin{equation}\begin{aligned}
+\begin{align}
 	\left[H, \pi^a\right] = J\sum_{b,j} \left[S_d^b s_j^b, \sigma_d^a \otimes_{i=1}^K \sigma_i^a\right] = \sum_{bj}\left(S_d^b \sigma_d^a s^b_j \sigma^a_j - \sigma_d^a S_d^b \sigma^a_j s^b_j\right) \otimes_{i<j}\sigma_i^a \otimes_{i>j}\sigma^a_i = 0
-\end{aligned}\end{equation}
-
+\end{align}
+
+\section{Eigenvalues and eigenstates}
 The zero mode Hamiltonian can be diagonalized.
@@
 Defining \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
-\begin{equation}\begin{aligned}
+\begin{align}
 	H_m = \begin{pmatrix} \frac{Jm}{2} & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\frac{J}{2}(m+1) \end{pmatrix} , m \in \left[-M, M-1\right] 
-\end{aligned}\end{equation}
+\end{align}
 The eigenvalues are 
-\begin{equation}\begin{aligned}
+\begin{align}
 	% \label{eigenvalue}
 	\lambda_{\pm}^{M} = - \frac{J}{4} \pm \frac{J}{2}\left(M + \frac{1}{2}\right) 
-\end{aligned}\end{equation}
+\end{align}
 The eigenvalues of the terminal states are \(\frac{JM}{2}\).
@@
 The normalized eigenstates of the \(2\times 2\) blocks for each value of \(m\) are given by
-\begin{equation}\begin{aligned}
+\begin{align}
 	\ket{\Psi^M_{m,-}} &= \frac{1}{\sqrt{(M+m+1)(1+2M)}}\left[-\sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M + m + 1\right)\ket{\downarrow,M,m+1}\right],& m \in \left[-M, M-1\right] \\
 	\ket{\Psi^M_{m,+}} &= \frac{1}{\sqrt{(M -m)(M - m + 1)}}\left[\sqrt{x_m^M}\ket{\uparrow, M, m} + \left(M - m\right)\ket{\downarrow,M,m+1}\right],& m \in \left[-M, M-1\right]
-\end{aligned}\end{equation}
+\end{align}
 Note that the index \(m\) that we are using to label tje eigenvalues is actually related to a conserved quantity; the total spin operator along \(z\), \(S^z\).
@@
 
+\section{Parity operators and the impurity magnetization}
 We can also use the eigenvalues of \(\pi^z\) to label the eigenstates.
@@
 Applying \(\pi^z\) on these eigenstates gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	\pi^z\ket{\Psi^M_{m,-}} = \left( -1 \right) ^{m}\ket{\Psi^M_{m,-}}
-\end{aligned}\end{equation}
+\end{align}
 This shows that the operator \(\pi^z\) splits the \(K-\)fold degenerate ground state manifold into two sub-manifolds of \(\pi^z\) parity \(\pm 1\).
@@
 It is interesting to calculate the action of the parity operator \(\pi^x\) on these eigenstates. We can write that operator as
-\begin{equation}\begin{aligned}
+\begin{align}
 	\pi^x = (S_d^+ + S_d^-)\otimes_{i=1}^K \left(s_i^+ + s_i^-\right) 
-\end{aligned}\end{equation}
+\end{align}
 We can write the eigenstates of \(s_\text{tot}^z\) in terms of the eigenstates of \(s_i^z\) using their Clebsch-Gordon coefficients:
-\begin{equation}\begin{aligned}
+\begin{align}
 	\ket{M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}\ket{m_1,m_2,...,m_K} C_{\left\{m_i\right\},m,M}
-\end{aligned}\end{equation}
+\end{align}
 where \(C_{\left\{m_i\right\},m,M} = \braket{m_1,m_2,...,m_K|m,M}\) are the Clebsch-Gordon coefficients. Applying the parity operator on the state gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	\pi^x \ket{S_d^z, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}(S_d^+ + S_d^-)\ket{S_d^z}\otimes_{i=1}^K \left(s_i^+ + s_i^-\right)\ket{m_i} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{-m_i}\\
 	=\sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{-m_i\right\},m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{m_i}
-\end{aligned}\end{equation}
+\end{align}
 Using the identity \(\braket{M_1m_1,M_2m_2,\ldots|m,M} = \left( -1 \right)^{\sum_i M_i - M}\braket{M_1, -m_1; M_2 -m_2;\ldots|-m,M}\), we have \(C_{\left\{-m_i\right\},m,M} = C_{\left\{m_i\right\},-m,M}\).
 Substituting this, we get
-\begin{equation}\begin{aligned}
+\begin{align}
 	\pi^x \ket{S_d^z, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{m_i\right\},-m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{m_i} = \ket{-S_d^z, M, -m}
-\end{aligned}\end{equation}
+\end{align}
 The action of \(\pi^x\) on the eigenstates can now be determined:
-\begin{equation}\begin{aligned}
+\begin{align}
 	\pi^x \ket{\Psi^M_{m,-}} &=-\sqrt{x_m^M}\ket{\downarrow, M, -m} + \left(M + m + 1\right)\ket{\uparrow,M,-m-1} = -\ket{\Psi^M_{-m-1,-}}
-\end{aligned}\end{equation}
+\end{align}
 It can be seen that the action of the operator \(\pi^x\) is to interpolate between two ground states of opposite \(\pi^z\) eigenvaluesand, more specifically, opposite \(S^z\) values
-\begin{equation}\begin{aligned}
+\begin{align}
 	\pi^x \ket{S^z} \to \ket{-S^z}
-\end{aligned}\end{equation}
+\end{align}
 
@@
 The most general ground state is obtained by taking a general linear combination of all the normalized ground states:
-\begin{equation}\begin{aligned}
+\begin{align}
 	\ket{g^n_m} = \frac{1}{\sqrt 2}\left[\ket{\Psi^M_{m,-}} + e^{i\theta}\ket{\Psi^M_{m+n,-1}}\right], m \in \left[-M, M-2\right] , n \in \left[1, M - m - 1\right] 
-\end{aligned}\end{equation}
+\end{align}
 The expectation value of the impurity spin along \(x\) in this state is given by
-\begin{equation}\begin{aligned}
+\begin{align}
 	\left(m_d^x\right)_m^n = \braket{g^n_m | \sigma_d^x | g^n_m}
-\end{aligned}\end{equation}
+\end{align}
 The action of \(\sigma_d^x\) is as follows:
-\begin{equation}\begin{aligned}
+\begin{align}
 	\sigma_d^x \ket{\Psi^M_{m,-}} = \frac{1}{\sqrt{(M+m+1)(1+2M)}}\left[-\sqrt{x_m^M}\ket{\downarrow, M, m} + \left(M + m + 1\right)\ket{\uparrow,M,m+1}\right]
-\end{aligned}\end{equation}
+\end{align}
 which means that the only \(\ket{\Psi^M_{m+n,-}}\) with \(n > 0\) that give a non-zero inner product with \(\sigma_d^x \ket{\Psi^M_{m,-}}\) is \(n=1\). This observation then gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	\left(m_d^x\right)_m^n = \delta_{n,1}\braket{g^1_m | \sigma_d^x | g^1_m} = \delta_{n,1}\left[e^{i\theta}\braket{\Psi^M_{m+1,-}|\sigma_d^x| \Psi^M_{m,-}} + \text{h.c.}\right] = \delta_{n,1}\left[e^{i\theta}\braket{\Psi^M_{m+1,-}|\sigma_d^x \pi^x | \Psi^M_{-m-1,-}} + \text{h.c.}\right]
-\end{aligned}\end{equation}
+\end{align}
 \textit{We thus see that the impurity magnetization \(\left(m_d^x\right)_m^n\) along \(x\) for the state \(\ket{g^n_m}\) is determined by the matrix element of the string operator \(\sigma^x_d \pi^x\)}.
@@
 For \(m = -M\), we get
-\begin{equation}\begin{aligned}
+\begin{align}
 	\braket{\Psi^M_{-M+1,-}|\sigma_d^x \pi^x | \Psi^M_{M - 1,-}} = \frac{\sqrt{2M-1}}{2M + 1}
-\end{aligned}\end{equation}
+\end{align}
 The ground state manifold is defined by \(M = K/2\). Using this, we can write
-\begin{equation}\begin{aligned}
+\begin{align}
 	\left(m_d^x\right)_{-M}^1 = \left[\braket{\Psi^M_{1-M,-}|\sigma_d^x \pi^x | \Psi^M_{M - 1,-}} + \text{h.c.}\right] = \frac{2\sqrt{2M-1}}{2M + 1} = \frac{2\sqrt{K-1}}{K+1}
-\end{aligned}\end{equation}
+\end{align}
 
 We can similarly calculate the magnetization along the \(z-\)direction. The most general ground state is
-\begin{equation}\begin{aligned}
+\begin{align}
 	\ket{g} = \sum_{m=-M}^{M-1} C_m \ket{\Psi^M_{m,-}}, &&& m \in \left[-M, M-1\right], &&& \sum_m |C_m|^2 = 1
-\end{aligned}\end{equation}
+\end{align}
 The expectation value of \(\sigma^d_z\) will be non-zero only in the diagonal terms: \(\braket{\Psi^M_m | \sigma^z_d | \Psi^M_{m^\prime}} = \delta_{mm^\prime}\braket{\Psi^M_m | \sigma^z_d | \Psi^M_{m}}\).
 Using this, we get
-\begin{equation}\begin{aligned}
+\begin{align}
 	\braket{g|\sigma^z_d|g} = \sum_{m=-M}^{M-1} |C_m|^2 \frac{\left[x_m^M - \left(M + m + 1\right)^2\right]}{{(M+m+1)(1+2M)}}
-\end{aligned}\end{equation}
+\end{align}
 For the simpler case when \(C_m = \delta_{m,\pm (M - \frac{1}{2}) - \frac{1}{2}}\), we get
-\begin{equation}\begin{aligned}
+\begin{align}
 	\braket{g_\pm|\sigma^z_d|g_\pm} = \pm \frac{2M-1}{2M+1} = \pm \frac{K-1}{K+1}
-\end{aligned}\end{equation}
+\end{align}
 
@@
 The renormalization at step \(j\) is given by
-\begin{equation}\begin{aligned}
+\begin{align}
 	\Delta H_j = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)~,
-\end{aligned}\end{equation}
+\end{align}
 where \(c^\dagger T\) represents the off-diagonal part of the Hamiltonian with respect to the fluctuations of the electron we are decoupling and \(H_D\) is the diagonal part with respect to the same electron.
 Assuming we are decoupling a particular electron \(q\beta\), we have
-\begin{equation}\begin{aligned}
+\begin{align}
 	c^\dagger T = J \sum_{k < \Lambda_j, \alpha}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, && H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
-\end{aligned}\end{equation}
+\end{align}
 Usually we treat the \(\hat \omega\) as number(s) and study the renormalization in the couplings as functions of the quantum fluctuation scales.
@@
 The expansion we are talking about is
-\begin{equation}\begin{aligned}
+\begin{align}
 	\eta = \frac{1}{\hat \omega - H_D}T^\dagger c = \frac{1}{\omega^\prime - H_D - H_X}T^\dagger c \simeq \frac{1}{\omega^\prime - H_D}T^\dagger c + \frac{1}{\omega^\prime - H_D}H_X \frac{1}{\omega^\prime - H_D} T^\dagger c
-\end{aligned}\end{equation}
+\end{align}
 where \(H_X = J \sum_{k,k^\prime < \Lambda_j, \alpha,\alpha^\prime}\vec{S_d}\cdot\vec{s}_{\alpha \alpha^\prime}c^\dagger_{k\alpha}c_{k^\prime\alpha^\prime}\) is scattering between the entangled electrons.
 With this change, the second and third order renormalizations will take the form
-\begin{equation}\begin{aligned}
+\begin{align}
 	\Delta H^{(2)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c + T^\dagger c \frac{1}{\omega - H_D}c^\dagger T
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
+\end{align}
+\begin{align}
 	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T
-\end{aligned}\end{equation}
+\end{align}
 We will use the identity
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{identity_SSS}
 	S_d^a S_d^z S_d^b = \left(\frac{1}{4}\delta^{az} + \frac{i}{2}\sum_c \epsilon^{azc}S_d^c\right)S_d^b = \left(\frac{1}{4}\delta^{az}S_d^b + \frac{i}{8} \epsilon^{azb}  - \frac{1}{4}\sum_{c_1,c} \epsilon^{azc_1} \epsilon^{c_1 b c} S_d^c\right) = \frac{1}{4}\left(\delta^{az}S_d^b - \delta^{ab}S_d^z + \delta^{bz}S_d^a\right)
-\end{aligned}\end{equation}
+\end{align}
 
 \subsection{Leading order renormalization}
-\begin{equation}\begin{aligned}
+\begin{align}
 	\Delta H^{(2)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c}_\text{first term}~+~\underbrace{T^\dagger c \frac{1}{\omega - H_D}c^\dagger T}_\text{second term}
-\end{aligned}\end{equation}
+\end{align}
 This renormalization is identical to that in the single channel. There is no additional physics due to the presence of multiple channels at this order. It is shown in appendix \ref{1KondoURG}.
@@
 \subsection{Next-to-leading order renormalization}
-\begin{equation}\begin{aligned}
+\begin{align}
 	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term} ~+~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term}
-\end{aligned}\end{equation}
+\end{align}
 A general term of this summation has three sets of spin operators coming from \(c^\dagger T, H_X\) and \(T^\dagger c\).
@@
 An instance of this term (in shorthand) is
-\begin{equation}\begin{aligned}
+\begin{align}
 	S_d^z c^\dagger_{q \uparrow} \frac{1}{\omega - D/2 -\epsilon_k/2 + J/2 S_d^z} S_d^z \frac{1}{\omega - D/2 -\epsilon_k/2 + J/2 S_d^z} S_d^z c_{q \uparrow}\\
-\end{aligned}\end{equation}
+\end{align}
 This can be split into up and down configurations of the impurity spin using the decomposition \(S_d^z = \frac{1}{2}\left(\frac{1}{2} + S_d^z\right) - \frac{1}{2}\left(\frac{1}{2} - S_d^z \right) \).
 These configurations will have different quantum fluctuation scales \(\omega, \omega^\prime\):
-\begin{equation}\begin{aligned}
+\begin{align}
 	\frac{1}{2}S_d^z c^\dagger_{q \uparrow}\left[\frac{\left(\frac{1}{2} + S_d^z\right)}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2} - \frac{\left(\frac{1}{2} - S_d^z\right)}{\left(\omega^\prime - D/2 -\epsilon_k/2 - J/4\right)^2}\right]S_d^z c_{q \uparrow}
-\end{aligned}\end{equation}
+\end{align}
 If we now use poor man's scaling values to relate the two \(\omega\)s, we get \(\omega^\prime - \omega = J/2\).
@@
 \subsubsection{Calculation of first term}
-\begin{equation}\begin{aligned}
+\begin{align}
 	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = J^3\sum_{q, k, k_1,k_2,\atop{\beta, \alpha, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} \frac{c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} c^\dagger_{k\alpha, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha \beta}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2}
-\end{aligned}\end{equation}
+\end{align}
 \(q\) sums over the momenta being decoupled.
@@
 This gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = J^3 n(D)\sum_{k, k_1,k_2,\atop{\beta, \alpha, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} \frac{c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} c^\dagger_{k\alpha, l_1} S_d^c s^c_{\alpha \beta}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2}
-\end{aligned}\end{equation}
+\end{align}
 The operators \(c^\dagger_{k\alpha}\) and its conjugate can be brought together without any change of sign because there will be an even number of flips. The sum over \(k\) gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	\sum_k \frac{1 - \hat n_{k\alpha l_1}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2} =  \rho\int \frac{d\epsilon\left[1 - \hat n(\epsilon)_{\alpha l_1}\right] }{\left(\omega - D/2 -\epsilon/2 + J/4\right)^2} = \rho\int_0^{D-2\left( \omega + J/4 \right) } \frac{d\epsilon}{\left(\omega - D/2 -\epsilon/2 + J/4\right)^2}
-\end{aligned}\end{equation}
+\end{align}
 The integration limits include only the positive energies, because of the \(1 - \hat n\) operator; the upper limit of the integration is chosen so as to make the denominator double, because this preserves the symmetry of the denominator.
 Performing the integration gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	\sum_k \frac{1 - \hat n_{k\alpha l_1}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2} = -\frac{1}{2}\frac{\rho}{\omega - D/2 + J/4}
-\end{aligned}\end{equation}
+\end{align}
 The sum over the channel index \(l_1\) produces a factor of \(K\). \(K = \sum_{l_1}\) is the total number of conduction bath channels. The entire expression is now
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{first_term}
 	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\sum_{\beta, \alpha, \alpha_1,\alpha_2,\atop{a,b,c}} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha_1 \alpha_2} S_d^c s^c_{\alpha \beta} \sum_{k_1,k_2,l_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
-\end{aligned}\end{equation}
+\end{align}
 We now need to simplify the spin products.
@@
 Substituting this gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\frac{1}{2}\sum_{\alpha_1,\alpha_2,a,b} S_d^a S_d^b S_d^a \sum_{k_1,k_2,l_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}s^b_{\alpha_1 \alpha_2}
-\end{aligned}\end{equation}
+\end{align}
 The spin product can now be carried out:
-\begin{equation}\begin{aligned}
+\begin{align}
 	\sum_a S_d^a S_d^b S_d^a = \sum_a S_d^a\left[\frac{1}{4}\delta^{ab} + \frac{i}{2}\sum_c \epsilon^{bac}S_d^c\right] = \frac{1}{4}S_d^b - \frac{1}{4}\sum_{ace}\epsilon^{bac}\epsilon^{ace}S_d^e = \frac{1}{4}S_d^b - \frac{1}{4}S_d^b \sum_{ac}\epsilon^{bac}\epsilon^{acb} \\
 	= -\frac{1}{4}S_d^b
-\end{aligned}\end{equation}
+\end{align}
 The renormalization becomes
-\begin{equation}\begin{aligned}
+\begin{align}
 	\Delta H_1 = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\frac{1}{2}\left( -\frac{1}{4} \right) \sum_{k_1,k_2,\alpha_1,\alpha_2,b,l_2} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}\\
 =\frac{1}{16}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4} \sum_{k_1,k_2,\alpha_1,\alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
-\end{aligned}\end{equation}
+\end{align}
 
@@
 The total renormalization is twice that in the particle sector.
-\begin{equation}\begin{aligned}
+\begin{align}
 	\Delta H^{(3)} = \frac{1}{8}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4} \sum_{k_1,k_2,\alpha_1,\alpha_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
-\end{aligned}\end{equation}
+\end{align}
 Combining with \(\Delta H^{(2)}\) and replacing \(n(D) = \rho |\delta D|\), we get
-\begin{equation}\begin{aligned}
+\begin{align}
 	\frac{\Delta J}{|\Delta D|} = -\frac{J^2 \rho}{\omega - D/2 + J/4} + \frac{1}{8}\frac{J^3 \rho^2 K}{\omega - D/2 + J/4} = -\frac{J^2 \rho}{\omega - D/2 + J/4}\left[1 - \frac{1}{8}J\rho K\right] 
-\end{aligned}\end{equation}
+\end{align}
 We choose \(\omega = -D/2\) to get a clearer idea of what the equations say. 
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{mchannel}
 	\frac{\Delta J}{|\Delta D|} = \frac{J^2 \rho}{D - J/4}\left[1 - \frac{1}{8}J\rho K\right] 
-\end{aligned}\end{equation}
+\end{align}
 Quantities with zero in the subscript will denote their values in the bare Hamiltonian. Using \(\delta D = -|\delta D|\), we can write the continuum form of the equation:
-\begin{equation}\begin{aligned}
+\begin{align}
+	\label{rg_beta}
 	\frac{\:\mathrm{d}J}{\:\mathrm{d}D} = \frac{J^2 \rho}{D - J/4}\left(\frac{1}{8}J\rho K - 1\right)
-\end{aligned}\end{equation}
+\end{align}
 
 For \(D \gg J\), we can ignore the \(J\) in the denominator, and the equation reduces to the one-loop poor man's scaling form
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{pms_mchannel}
 	\frac{\:\mathrm{d}J}{\:\mathrm{d}D} \simeq  \frac{J^2 \rho}{D}\left(\frac{1}{8}J\rho K - 1\right)
-\end{aligned}\end{equation}
+\end{align}
 This equation has a stable fixed point at \(J^* = \frac{8}{\rho K}\).
@@
 The numerator and denominator fixed points, \(J_1^*\) and \(J_2^*\) respectively, are given by
-\begin{equation}\begin{aligned}
+\begin{align}
 	J_1^* = \frac{8}{K \rho}, && D^* = \frac{J_2^*}{4}
-\end{aligned}\end{equation}
+\end{align}
 For a given \(K\), the position of \(J_1^*\) will be governed by \(\rho\).
@@
 For \(\rho < \rho_\text{min}\), \(J\) will grow and hit \(J_2^*\) instead, and \(J_1^* > J_2^*\) now becomes the repulsive fixed point.
-\begin{equation}\begin{aligned}
+\begin{align}
 	\rho_\text{min} = \text{minimum }\left\{\rho, \text{ such that } \frac{8}{K \rho} < 4 D^*(\rho)\right\}
-\end{aligned}\end{equation}
+\end{align}
 The RG flows towards the attractive fixed point \(J_1^*\) is shown  in fig.~\ref{rg_flow_K-2}.
@@
 
-\subsection{Effect of anisotropy}
+\section{Effect of anisotropy on RG flows}
 For a general anisotropic multi-channel Kondo, the Hamiltonian is
-\begin{equation}\begin{aligned}
+\begin{align}
 	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + \sum_{kk^\prime,\gamma}J_\gamma \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
-\end{aligned}\end{equation}
+\end{align}
 Let us consider the specific case where \(K-1\) channels have the same coupling \(J_1 = J_2 = ...
@@
 The RG equations for such a model are
-\begin{equation}\begin{aligned}
+\begin{align}
 	\frac{\Delta J_+}{|\Delta D|} = \frac{J_+^2 \rho}{D - J_+/4} - \frac{\rho^2 J_+}{8}\left[\frac{(K-1)J_+^2}{D - J_+/4} + \frac{J_-^2}{D - J_-/4}\right]\\
-	\frac{\Delta J_-}{|\Delta D|} = \frac{J_-^2 \rho}{D - J_-/4} - \frac{\rho^2 J_-}{8}\left[\frac{(K-1)J_+^2}{D - J_+/4} + \frac{J_-^2}{D - J_-/4}\right]\\
-\end{aligned}\end{equation}
+	\frac{\Delta J_-}{|\Delta D|} = \frac{J_-^2 \rho}{D - J_-/4} - \frac{\rho^2 J_-}{8}\left[\frac{(K-1)J_+^2}{D - J_+/4} + \frac{J_-^2}{D - J_-/4}\right]
+\end{align}
 Setting \(J_+ = J_-\) leads to the critical fixed point at \(J_+^* = J_-^* = J_* = \frac{8}{K \rho}\).
@@
 The RG equations then take the form
-\begin{equation}\begin{aligned}
+\begin{align}
 	\frac{\Delta j_+}{|\Delta D|} &= \frac{\rho J_+}{D - J_*/4}\left[J_+ - \frac{\rho}{8}\left[(K-1)J_+^2 + J_-^2\right]\right]\\
@@
 				      &= \frac{J_- \rho}{K J_*\left(D - J_*/4\right)}\left[\left(K - 2\right)J_*j_-  - j_-^2 - (K-1)j_+^2 - 2(K-1)J_* j_+\right]\\
-\end{aligned}\end{equation}
+\end{align}
 We will first look at the special case of \(K=2\), the two channel Kondo model. The equations simplify to
-\begin{equation}\begin{aligned}
+\begin{align}
 	\frac{\Delta j_\pm}{|\Delta D|} = \frac{J_\pm \rho}{K J_*\left(D - J_*/4\right)}\left[- \left(j_+^2 + j_-^2\right) - 2J_* j_\mp\right]\\
-\end{aligned}\end{equation}
+\end{align}
 For \(j_- < 0, j_+ > 0\), we have \(\Delta j_- < 0\).
@@
 We already know the non-perturbative URG equation for the single-channel Kondo problem:
-\begin{equation}\begin{aligned}
+\begin{align}
 	\frac{\Delta j_+}{|\Delta D|} = \frac{J_+^2 \rho}{D - J_+/4}~,
-\end{aligned}\end{equation}
+\end{align}
 and it leads to the strong-coupling fixed point
@@
 This condition is given by
-\begin{equation}\begin{aligned}
+\begin{align}
 	\left(K - 2\right)J_*j_+ + (K-1)j_+^2 + j_-^2 + 2J_* j_- = 0
-\end{aligned}\end{equation}
+\end{align}
 Substituting \(j_- = -J_*\) gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	(K-1)j_+^2 + \left(K - 2\right)J_*j_+ - J_*^2 = 0
-\end{aligned}\end{equation}
+\end{align}
 Solving for \(j_+\) gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	j_{+,*} = \frac{-J_*(K-2) \pm \sqrt{(K-2)^2 J_*^2 + 4(K-1)J_*^2}}{2(K-1)} = \frac{J_*}{2(K-1)}\left[-(K-2) \pm K\right] = \frac{J_*}{K-1}
-\end{aligned}\end{equation}
+\end{align}
 At the final step, we chose the positive solution, because \(j_+\) is relevant in this regime. The new fixed-point value of \(J_+\) is therefore
-\begin{equation}\begin{aligned}
+\begin{align}
 	J_+ = J_* + \frac{J_*}{K-1} = \frac{\frac{8}{K \rho} K}{K - 1} = \frac{8}{(K-1)\rho}
-\end{aligned}\end{equation}
+\end{align}
 In other words, the \(K\) channel fixed-point flows to the \(K-1\) channel fixed-point.
@@
 
+\section{Duality of the Hamiltonian RG flow}
+The infrared multi-channel Kondo Hamiltonian is given by
+\begin{equation}\begin{aligned}
+	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J_<\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
+\end{aligned}\end{equation}
+where \(J_<\) indicates that it parametrizes the weak-coupling Hamiltonian.
+\textit{Assuming one can also write a strong-coupling Hamiltonian that is identical to the weak-coupling one, the model can then be said to possess S-duality.} This has been demonstrated for the two-channel Kondo \cite{kroha_kolf_2007} by defining fermionic and bosonic operators \(F_\sigma\) and \(B\) from the ground states and excited states respectively of the zero-mode Hamiltonian eq.~\ref{zeromode_ham}, then rewriting the Hamiltonian eq.~\ref{mc_ham} in terms of these fermions and bosons by resolving the Hamiltonian in the eigenbasis of the zero mode Hamiltonian, and finally by decoupling the interaction between the bosons and the fermions through a Schrieffer-Wolff transformation (SWT) and projecting on to the fermionic states.
+The last step is what makes it a strong-coupling Hamiltonian: the SWT and the subsequent projection is perturbative in powers of a new coupling \(J_> = t^2/J_<\) and makes sense only in the strong-coupling limit \(J_< \gg t\).
+In that sense, the SWT removes the interaction between the ground state manifold and the excited levels.
+The result of these three steps is another two-channel Kondo model, but now parametrized by the strong-coupling coupling \(J_>\) \cite{kroha_kolf_2007}.
+
+If a general \(K-\)channel Kondo model possesses S-duality under a transformation \(J_> = \frac{\gamma D^2_0}{J_<} = \frac{\gamma 16t^2}{J_<}\), \(D_0 = 4t\) being the bare cut-off of the problem, we can write Hamiltonians \(H(J_<)\) and \(H(J_>)\) that are identical in form.
+This means that the two Hamiltonians will have identical properties.
+An immediate and obvious conclusion of this is that both the Hamiltonians will have identical RG flows:
+\begin{equation}\begin{aligned}
+	\Delta J_< = \beta(J_<), &&&\Delta J_> = \beta(J_>)
+\end{aligned}\end{equation}
+where \(\beta\) represents the RG beta function.
+From URG calculations, we know that there is a unique attractive fixed point along the RG flow.
+This means that we must have \(J_<^* = J_>^* = J^*\), and that \(\beta(J_>^*) = 0\).
+From eq.~\ref{rg_beta}, we get
+\begin{equation}\begin{aligned}
+	J_>^* = \frac{8}{K \rho} = J_<^* \implies \frac{\gamma 16 t^2}{J_<^*} = J_<^* \implies \gamma = \left(\frac{J^*_<}{4t}\right) ^2 = \left( \frac{2}{K \rho t}\right) ^2
+\end{aligned}\end{equation}
+This, then, is the transformation that makes the critical fixed point self-dual.
+
 \section{Effective Hamiltonian for low-energy excitations: \(k-\)space}
 The fixed point Hamiltonian is
-\begin{equation}\begin{aligned}
+\begin{align}
 	H^* = H_0 + J^* \vec{S_d}\cdot\vec{s_\text{tot}}
-\end{aligned}\end{equation}
+\end{align}
 where \(H_0 = \sum_{k,l,\sigma}\epsilon_{k,l}\hat n_{k\sigma,l}\) and \(\vec s_\text{tot} = \sum_l \vec s_l = \sum_{kk^\prime\alpha\alpha^\prime,l} \vec \sigma_{\alpha\alpha^\prime}c^\dagger_{k\alpha,l}c_{k^\prime\alpha^\prime,l}\).
@@
 This guides the separation of the Hamiltonian into a diagonal and an off-diagonal piece:
-\begin{equation}\begin{aligned}
+\begin{align}
 	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_{V + V^\dagger}
-\end{aligned}\end{equation}
+\end{align}
 We define \(V\) as the interaction term that decreases \(s_\text{tot}^z\) by 1: \(V \ket{s_\text{tot}^z} \to \ket{s_\text{tot}^z - 1}\).
@@
 The effective Hamiltonian that has the states \(\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}\) as eigenstates are
-\begin{equation}\begin{aligned}
+\begin{align}
 	H_\text{eff} = H_d + V \frac{1}{E_\text{gs} - H_d}V = \sum_{k,l,\sigma}\epsilon_{k,l}\hat n_{k\sigma,l} + J S_d^z s_\text{tot}^z + \frac{J}{2}S_d^+ s_\text{tot}^- \frac{1}{E_\text{gs} - J S_d^z s_\text{tot}^z - H_0}\frac{J}{2}S_d^- s_\text{tot}^+\\
 	+\frac{J}{2}S_d^- s_\text{tot}^+ \frac{1}{E_\text{gs} - J S_d^z s_\text{tot}^z - H_0}\frac{J}{2}S_d^+ s_\text{tot}^-
-\end{aligned}\end{equation}
+\end{align}
 This is obtained from the Schrodinger equation for the ground state. If we expand the ground state in terms of \(\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}\), we have 
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{gstate_Expand}
 \ket{\Psi_\text{gs}} = \sum_{S_d^z, s_\text{tot},s_\text{tot}^z}C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}
-\end{aligned}\end{equation}
+\end{align}
 The Schrodinger equation for the ground state can be written as
-\begin{equation}\begin{aligned}
+\begin{align}
 	E_\text{gs}\ket{\Psi_\text{gs}} = H \ket{\Psi_\text{gs}} = \left(H_d + V\right)\ket{\Psi_\text{gs}} \implies \left(E_\text{gs} - H_d\right)\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z} = V\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}
-\end{aligned}\end{equation}
+\end{align}
 Since \(V\) only changes \(S_d^z \to -S_d^z\) and \(s^z_\text{tot} \to s^z_\text{tot} \pm 1\), we can simplify the equation into individual smaller equations.
@@
 From eqs.~\ref{eq2} and \ref{eq4}, we can write
-\begin{equation}\begin{aligned}
+\begin{align}
 	C_{\frac{1}{2}, 1, -1}\ket{\frac{1}{2}, 1, -1} &= C_{-\frac{1}{2}, 1, 0}\frac{1}{E_\text{gs} - H_d}V \ket{-\frac{1}{2}, 1, 0}, &&C_{-\frac{1}{2}, 1, 1}\ket{-\frac{1}{2}, 1, 1} = C_{\frac{1}{2}, 1, 0}\frac{1}{E_\text{gs} - H_d}V^\dagger \ket{\frac{1}{2}, 1, 0}
-\end{aligned}\end{equation}
+\end{align}
 Substituting these into eqs.~\ref{eq3.1} and \ref{eq3.2} gives 
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{eff_ham_Sdz_10}
@@
 	E_\text{gs} \ket{-\frac{1}{2}, 1, 0} &= \left(H_d + V^\dagger \frac{1}{E_\text{gs} - H_d} V\right) \ket{-\frac{1}{2}, 1, 0}\\
-\end{aligned}\end{equation}
+\end{align}
 These equations represent the Schrodinger equation for the states \(\ket{S_d^z, 1, 0}\), and the right hand sides therefore give the effective Hamiltonians for those states.
 If we combine the states into a single subspace \(\ket{1,0}= \left\{\ket{\frac{1}{2}, 1, 0}, \ket{-\frac{1}{2}, 1, 0}\right\}\), the effective Hamiltonian for this composite subspace becomes the sum of the two parts:
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{eff_ham_10}
 	H_\text{eff}\ket{1, 0}\bra{1, 0} = \left(H_d + V G_0 V^\dagger + V^\dagger G_0  V\right) \ket{1, 0}
-\end{aligned}\end{equation}
+\end{align}
 where \(G_0 = \left(E_\text{gs} - H_d\right)^{-1}\).
@@
 Solving similarly for the other states gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	H_\text{eff}\ket{1,  1}\bra{1,  1} &= \left(H_d + V^\dagger G_0  V\right) \ket{1,  1}\\
 	H_\text{eff}\ket{1, - 1}\bra{1, - 1} &= \left(H_d + V G_0 V^\dagger\right) \ket{1, - 1}
-\end{aligned}\end{equation}
+\end{align}
 \textit{One important conclusion that comes out of these calculations is that if the ground state is degenerate, the effective Hamiltonians is independent of which ground state we choose to start from in eq.~\ref{gstate_Expand}.
@@
 We can easily simplify the \(S_d^z\) in the denominator of \(G_0\), because \(S_d^\pm \frac{1}{A + B S_d^z} = S_d^\pm \frac{1}{A \mp \frac{1}{2}B}\):
-\begin{equation}\begin{aligned}
+\begin{align}
 	V G_0 V^\dagger = \frac{J^2}{4} s_\text{tot}^- \frac{\frac{1}{2} + S_d^z}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^+ \\
 	V^\dagger G_0 V = \frac{J^2}{4} s_\text{tot}^+ \frac{\frac{1}{2} - S_d^z}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z - H_0} s_\text{tot}^-
-\end{aligned}\end{equation}
+\end{align}
 Since \(H_0\) does not commute with the spin operators, we will need to expand the denominator to make sense of this Hamiltonian.
-\begin{equation}\begin{aligned}
+\begin{align}
 	 V G_0 V^\dagger =  s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 + \ldots\right] s_\text{tot}^+\\
 	 V^\dagger G_0 V =  s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\left[1 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 + \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0\frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 + \ldots\right] s_\text{tot}^-
-\end{aligned}\end{equation}
+\end{align}
 This is an expansion in \(H_0^n/J^{n+1}, n=0,1,2,\ldots\). The \(n=0\) terms give
-\begin{equation}\begin{aligned}
+\begin{align}
 	s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}s_\text{tot}^+ = s_\text{tot}^- s_\text{tot}^+ \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)} %= \left[s_\text{tot}\left( s_\text{tot}+1 \right)  - s_\text{tot}^z\left( s_\text{tot}^z + 1 \right) \right] \frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\\
@@
 	s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}s_\text{tot}^- = s_\text{tot}^+ s_\text{tot}^- \frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}% = \left[s_\text{tot}\left( s_\text{tot}+1 \right)  - s_\text{tot}^z\left( s_\text{tot}^z - 1 \right) \right] \frac{1}{E_\text{gs} - \frag{J}{2} \left(s_\text{tot}^z - 1\right)}
-\end{aligned}\end{equation}
+\end{align}
 
 One of the \(n=1\) terms gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^+ =  \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 s_\text{tot}^- H_0 s_\text{tot}^+
-\end{aligned}\end{equation}
+\end{align}
 Next we calculate the commutator:
-\begin{equation}\begin{aligned}
+\begin{align}
 	\left[s_\text{tot}^+, H_0\right] = X^\dagger_{1,\text{tot}} = \sum_l X_{1,l}^\dagger = \sum_{kk^\prime,l}\left(\epsilon_k - \epsilon_{k^\prime}\right) c^\dagger_{k^\prime \uparrow} c_{k \downarrow}
-\end{aligned}\end{equation}
+\end{align}
 where \(X_{n,l} \equiv \sum_{k,k^\prime}\left(\epsilon_k - \epsilon_{k^\prime}\right)^n c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \).
 Substituting this commutator gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	s_\text{tot}^- \frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} + \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^+ =  \left(\frac{1}{E_\text{gs} + \frac{J}{2} \left(s_\text{tot}^z + 1\right)}\right)^2 \left(s_\text{tot}^- s_\text{tot}^+ H_0 - s_\text{tot}^- X^\dagger_{1,\text{tot}}\right)
-\end{aligned}\end{equation}
+\end{align}
 The other \(n=1\) term gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	s_\text{tot}^+ \frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}\frac{1}{E_\text{gs} - \frac{J}{2} s_\text{tot}^z}H_0 s_\text{tot}^- =  \left(\frac{1}{E_\text{gs} - \frac{J}{2} \left(s_\text{tot}^z - 1\right)}\right)^2 \left(s_\text{tot}^+ s_\text{tot}^- H_0 + s_\text{tot}^+ X_{1,\text{tot}}\right)
-\end{aligned}\end{equation}
+\end{align}
 One of the \(n=2\) terms gives
@@
 At this point, we need the commutator between \(H_0\) and \(s_\text{tot}^z\):
-\begin{equation}\begin{aligned}
+\begin{align}
 	\left[H_0, s_\text{tot}^z\right] = Z_{1,\text{tot}} = \sum_l Z_{1, l} = \sum_{k,k^\prime,l}\left( \epsilon_k - \epsilon_{k^\prime} \right) \frac{1}{2}\left(c^\dagger_{k \uparrow,l}c_{k^\prime \uparrow,l} - c^\dagger_{k \downarrow,l}c_{k^\prime \downarrow,l}\right)
-\end{aligned}\end{equation}
+\end{align}
 This gives the relation
-\begin{equation}\begin{aligned}
+\begin{align}
 	H_0 (a + b s_\text{tot}^z) = (a + b s_\text{tot}^z) H_0 + Z_{1,\text{tot}} \implies \frac{1}{a + b s_\text{tot}^z} H_0 = H_0 \frac{1}{a + b s_\text{tot}^z} + \frac{1}{a + b s_\text{tot}^z} Z_{1,\text{tot}} \frac{1}{a + b s_\text{tot}^z}
-\end{aligned}\end{equation}
+\end{align}
 Using this, we get
@@
 The states in the eq.~\ref{no_V} cannot be acted on by \(V\) or \(V^\dagger\), so the effective Hamiltonian for these states will consist of only the diagonal part:
-\begin{equation}\begin{aligned}
+\begin{align}
 	H_\text{eff} = H_0 + \frac{J}{2}s^z_\text{tot}
-\end{aligned}\end{equation}
+\end{align}
 The factors \(\gamma\) and \(\chi\) for the other states are
-\begin{equation}\begin{aligned}
+\begin{align}
 	s_\text{tot}, s_\text{tot}^z = && (1,-1), && (1,0), && (1,1)\\
@@
 	\chi_{s_\text{tot}}^{-s_\text{tot}^z} = && --, && 2, && 2\\
-\end{aligned}\end{equation}
+\end{align}
 The effective Hamiltonians for these states are:
@@
 The terms have the following meanings:
-\begin{equation}\begin{aligned}
+\begin{align}
 	H_0 &= \sum_{k,\sigma,l}\epsilon_k^l \hat n_{k,\sigma,l}\\
@@
 	Z_{1,\text{tot}} H_0 &= \sum_{k_1,q_1,k_2,\sigma_2,l_1,l_2}\left(\epsilon_{k_1}^{l_1} - \epsilon_{q_1}^{l_1}\right) \epsilon_{k_2}^{l_2} \left(c^\dagger_{k_1, \uparrow, l_1}c_{q_1, \uparrow, l_1} - c^\dagger_{k_1, \downarrow, l_1}c_{q_1, \downarrow, l_1}\right) \hat n_{k_2,\sigma_2,l_2}\\
-\end{aligned}\end{equation}
+\end{align}
 
@@
 The zero-mode approximation of the fixed-point Hamiltonian is a star graph Hamiltonian:
-\begin{equation}\begin{aligned}
+\begin{align}
 	H = J^* \vec{S_d}\cdot\vec{s}_\text{tot}
-\end{aligned}\end{equation}
+\end{align}
 where \(\vec s_\text{tot} = \sum_l \vec s_l\) is the total spin operator for all the channels.
 We insert a magnetic field that acts only on the impurity and then attempt to diagonalize the Hamiltonian.
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{stargraph_field_hamiltonian}
 	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h S_d^z
-\end{aligned}\end{equation}
+\end{align}
 The Hamiltonian commutes with \(s_\text{tot}^2\):
-\begin{equation}\begin{aligned}
+\begin{align}
 \left[s_\text{tot}^2, H(h)\right] = \left[\sum_{i=x,y,z}{s^i_\text{tot}}^2, J^* \sum_{i=x,y,z} S_d^i s^i_\text{tot}\right] = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, \left[s_\text{tot}^i,s_\text{tot}^j\right]\right\} = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, i \epsilon^{ijk}s^k_\text{tot}\right\} = 0
-\end{aligned}\end{equation}
+\end{align}
 This means the Hamiltonian is already block-diagonal in the quantum number \(s_\text{tot}\).
@@
 Defining \(\epsilon^h_m = \frac{1}{2}\left(Jm + h\right) \) and \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
-\begin{equation}\begin{aligned}
+\begin{align}
 	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} 
-\end{aligned}\end{equation}
+\end{align}
 The eigenvalues are 
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{eigenvalue}
 	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}
-\end{aligned}\end{equation}
+\end{align}
 where \(\alpha = \epsilon^h_m + J/4\).
@@
 The full list of energy eigenvalues at a particular value of \(M\) is
-\begin{equation}\begin{aligned}
+\begin{align}
 \label{stargraph_spectrum}
@@
 &JM/2 + h/2, &&\ket{\uparrow, M, M},&& m = M\\
-\end{aligned}\end{equation}
+\end{align}
 The eigenstates for each value of \(M,m\) are given by
-\begin{equation}\begin{aligned}
+\begin{align}
 	\left(\pm\frac{1}{2}\sqrt{J^2 {x_m^M}^2 + 4\alpha^2} - \frac{J}{2}\sqrt{x_m^M}\right)\ket{\uparrow, M, m} + \left(\frac{J}{2}(m+\frac{1}{2}) + \frac{h}{2}\right) \ket{\downarrow, M, m+1}
-\end{aligned}\end{equation}
+\end{align}
 
 The partition function is
-\begin{equation}\begin{aligned}
+\begin{align}
 	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
 	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
-\end{aligned}\end{equation}
+\end{align}
 where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\).
@@
 It turns out that this number is given by
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{extra_degen}
 	r^K_M = {}^{K-1}C_{K/2 - M}
-\end{aligned}\end{equation}
+\end{align}
 which means the correct partition function is
-\begin{equation}\begin{aligned}
+\begin{align}
 	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
-\end{aligned}\end{equation}
+\end{align}
 
 To calculate the impurity magnetic susceptibility, we will use the expression
-\begin{equation}\begin{aligned}
+\begin{align}
 	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z(h)^{\prime\prime}}{Z(h)} - \left(\frac{Z(h)^{\prime}}{Z(h)}\right)^2 \right] 
-\end{aligned}\end{equation}
+\end{align}
 where the \(\prime\) indicates derivative with respect to \(h\). We will now calculate these derivatives. For that we will need
@@
 We are now ready to compute the derivatives of \(Z\):
-\begin{equation}\begin{aligned}
+\begin{align}
 	\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta J/4}\alpha\frac{\sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2} }{\sqrt{J^2x^M_m/4 + \alpha^2}} + e^{-\beta JM/2}\sinh \left(\beta h/2\right)\right] \\
@@
 - \frac{\alpha^2 \sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2}}{J^2x^M_m/4 + \alpha^2}\right) + e^{-\beta JM/2}\frac{\beta}{2}\cosh \left(\beta h/2\right)\right] \\
-\end{aligned}\end{equation}
+\end{align}
 We will now take the limit of \(h \to 0\). Note that \(\alpha(h\to 0)=\frac{J}{2}(m+1/2)\) and hence 
-\begin{equation}\begin{aligned}
+\begin{align}
 	(J^2x^M_m/4 + \alpha^2)(h \to 0) = \frac{J^2}{4}\left[M(M+1) - m(m+1) + (m+1/2)^2\right] = \frac{J^2}{4}\left( M + 1/2 \right)^2
-\end{aligned}\end{equation}
+\end{align}
 For brevity, we define \(\theta_M = \beta J (M+1/2)/2\) and \(\Sigma_M = \sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}(m+1/2)^2\).
 It can be shown that this summation, for \(M=M_\text{max}=K/2\), evaluates to \(\Sigma_\text{max} = K(K+1)(K-1)/12\).
-\begin{equation}\begin{aligned}
+\begin{align}
 	\lim_{h \to 0}Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta \frac{J}{2}\left( M + 1/2 \right) + 2e^{-\beta JM/2}\right] = \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[4Me^{\beta J/4}\cosh \theta_M + 2e^{-\beta JM/2}\right]\\
@@
 	\lim_{h \to 0}\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \frac{\beta^2}{2}\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\frac{e^{\beta J/4}}{\theta_M}\left(2M\sinh \theta_M + \frac{\beta^2 J^2}{4}\left[\frac{\cosh\theta_M}{\theta_M} - \frac{\sinh \theta_M}{\theta_M^2}\right]\Sigma_M\right)+ e^{-\beta JM/2}\right]\\
-\end{aligned}\end{equation}
+\end{align}
 These expressions have been used to compute the impurity susceptibility for various values of \(K\) in fig.~\ref{chi_mchannel}.
@@
 At low temperature \(\beta \to \infty\), only the highest value \(M_\text{max}\) will survive:
-\begin{equation}\begin{aligned}
+\begin{align}
 	Z &\to 2 r^K_{M_\text{max}} M_\text{max} e^{\beta \frac{J}{2}(M_\text{max} + 1)}\\
@@
 	\chi &\to \frac{\beta\Sigma_\text{max}}{2M_\text{max}\left(2M_\text{max}+1\right)^2} = \frac{\beta K(K+1)(K-1)/12}{K(K+1)^2} = \frac{\beta(K-1)}{12(K+1)}
-\end{aligned}\end{equation}
+\end{align}
 
 At high temperatures \(\beta \to 0\), we get
-\begin{equation}\begin{aligned}
+\begin{align}
 	Z &\to \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[4M + 2\right]\\
@@
 	\chi &\to 1/4
-\end{aligned}\end{equation}
+\end{align}
 
@@
 We insert a magnetic field that acts only on the bath and then attempt to diagonalize the Hamiltonian.
-\begin{equation}\begin{aligned}
+\begin{align}
 	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h s^z_\text{tot}
-\end{aligned}\end{equation}
+\end{align}
 
 Defining \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
-\begin{equation}\begin{aligned}
+\begin{align}
 	H_m = \begin{pmatrix} m(J/2 + h) & J\sqrt{x^M_m}/2 \\ J\sqrt{x^M_m}/2 & (m+1)(h - J/2) \end{pmatrix} 
-\end{aligned}\end{equation}
+\end{align}
 The eigenvalues are 
-\begin{equation}\begin{aligned}
+\begin{align}
 	\lambda_{m, \pm}^{M, h} &= -J/4 + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2x^M_m + \left[(2m+1)h - J/2\right]^2 - 4m(m+1)(h^2 - J^2/4)} \\
 				&= -J/4 + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2(M + 1/2)^2 + h^2 - (2m+1)Jh}	= -J/4 + (2m+1)h/2 \pm \phi^M_m
-\end{aligned}\end{equation}
+\end{align}
 The eigenvalues of the terminal states are \(JM/2 \pm hM\). The partition function is
-\begin{equation}\begin{aligned}
+\begin{align}
 	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta JM/2}\left(e^{\beta hM} + e^{-\beta hM}\right)\right] \\
 	     &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(J/4 - (m+1/2)h\right)}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\cosh \beta Mh\right]
-\end{aligned}\end{equation}
+\end{align}
 We will now take the derivatives.
-\begin{equation}\begin{aligned}
+\begin{align}
 	Z^\prime(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(J/4 - (m+1/2)h\right)}\left(-\beta (m+1/2) \cosh \beta\phi^M_m + \beta\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right)+ 2\beta Me^{-\beta JM/2}\sinh \beta Mh\right]\\
@@
 + \beta\frac{\:\mathrm{d^2}\phi^M_m}{\:\mathrm{d}h^2}\sinh \beta\phi^M_m + \beta^2\left(\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right)^2 \cosh \beta\phi^M_m\right) + 2\beta^2 M^2 e^{-\beta JM/2}\cosh \beta Mh\right]\\
-\end{aligned}\end{equation}
+\end{align}
 In the limit of \(h \to 0\), we  have
-\begin{equation}\begin{aligned}
+\begin{align}
 	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\right]\\
@@
 + \beta\frac{\:\mathrm{d^2}\phi^M_m}{\:\mathrm{d}h^2}\sinh \beta\phi^M_m + \beta^2\left(\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right)^2 \cosh \beta\phi^M_m\right) + 2\beta^2 M^2 e^{-\beta JM/2}\right]\\
-\end{aligned}\end{equation}
+\end{align}
 The \(\phi\) and the derivatives are actually at \(h\to 0\).
@@
 We can also look at the behaviour of the derivative:
-\begin{equation}\begin{aligned}
+\begin{align}
 	\lim_{h \to 0}\frac{\:\mathrm{d}\phi_m^M}{\:\mathrm{d}h} &= -\frac{J(m+1/2)}{4\phi^M}\\
 	\lim_{h \to 0}\frac{\:\mathrm{d}^2\phi_m^M}{\:\mathrm{d}h^2} &= \frac{1}{4\phi^M} - \frac{J^2(m + 1/2)^2}{16\left(\phi^M\right)^3}\\
-\end{aligned}\end{equation}
+\end{align}
 Substituting these gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\phi^M + 2e^{-\beta JM/2}\right] = \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[4Me^{\beta J/4}\cosh \beta\phi^M + 2e^{-\beta JM/2}\right]\\
@@
 			  &\quad\quad\quad\quad\quad\quad\quad\left.+ 2 M^2 e^{-\beta JM/2}\right]\\
-\end{aligned}\end{equation}
+\end{align}
 where \(\Sigma_M = \sum_m (m+1/2)^2\).
@@
 We therefore have
-\begin{equation}\begin{aligned}
+\begin{align}
 	     Z(h \to 0) &= r^K_{K/2} 4Me^{\beta J/4}\frac{1}{2}e^{\beta\Phi}\\
 	     Z^{\prime\prime}(h \to 0) &=\beta^2 r^K_{K/2}2 e^{\beta J/4}\frac{1}{2}e^{\beta \Phi}\left(1 + \frac{J}{4\Phi}\right)^2\Sigma_\text{max}\\
-\end{aligned}\end{equation}
+\end{align}
 The susceptibility at low temperatures becomes
-\begin{equation}\begin{aligned}
+\begin{align}
 	\chi(T \to 0) = \frac{2\beta\left(1 + \frac{J}{4\Phi}\right)^2\Sigma_M}{4M} = \frac{\beta (K-1)(K+2)^2}{12(K+1)}
-\end{aligned}\end{equation}
+\end{align}
 
@@
 For \(K>1\), the Gibbs free energy at \(T=0\) becomes non-analytic under insertion of a magnetic field on the impurity. The thermal free energy is given by
-\begin{equation}\begin{aligned}
+\begin{align}
 	F(h) = -\frac{1}{\beta}\ln Z(h) = -\frac{1}{\beta}\ln\sum_{E_n}e^{-\beta E_n}
-\end{aligned}\end{equation}
+\end{align}
 At \(T \to 0\), only the most negative energy \(E_\text{min}\) survives. Assuming a \(d^\prime_\text{gs}-\)fold degenerate ground state for \(h \neq 0\), the zero temperature free energy becomes
-\begin{equation}\begin{aligned}
+\begin{align}
 	F(h\neq 0, T\to 0) = -\frac{1}{\beta}\ln d^\prime_\text{gs}e^{-\beta E_\text{min}} = E_\text{min}- k_B T\ln d^\prime_\text{gs}
-\end{aligned}\end{equation}
+\end{align}
 In the star graph Hamiltonian with \(K-\)channels and a global magnetic field on the impurity
-\begin{equation}\begin{aligned}
+\begin{align}
 	H = J \vec{S_d}\cdot\vec{s}_\text{tot} + h\left(S_d^z + s^z_\text{tot}\right) ~,
-\end{aligned}\end{equation}
+\end{align}
 the energy eigenvalues for a particular value of \(s_\text{tot}=M\) are given by
-\begin{equation}\begin{aligned}
+\begin{align}
 	(a) \quad&\frac{J}{2}M \pm h\left(M + \frac{1}{2}\right)\\
 	(b) \quad&-\frac{J}{4}\pm \frac{J}{2}\left(M + \frac{1}{2}\right) + h\left( m + \frac{1}{2} \right), m \in \left[-M, M-1\right] 
-\end{aligned}\end{equation}
+\end{align}
 For small \(h\), the ground state will be \(-\frac{J}{4}- \frac{J}{2}\left(M + \frac{1}{2}\right) + h\left(m_\text{min} + \frac{1}{2} \right)\) for a particular value \(m_\text{min}\) that minimizes this energy.
 This specific value will depend on the sign of \(h\):
-\begin{equation}\begin{aligned}
+\begin{align}
 	m_\text{min} = \begin{cases}
@@
 	\end{cases}
-\end{aligned}\end{equation}
+\end{align}
 which means \(E_\text{min} = -\frac{J}{2}\left( M + 1 \right) - |h|\left(M - \frac{1}{2}\right)\). We also know, from eq.~\ref{extra_degen}, that \(d^\prime_\text{gs} = {}^{K-1}C_{K/2 - K/2} = 1\).
 The free energy for a non-zero field is therefore
-\begin{equation}\begin{aligned}
+\begin{align}
 	F(h\neq 0, T\to 0) = -\frac{J}{2}\left( M + 1 \right) - |h|\left(M - \frac{1}{2}\right)
-\end{aligned}\end{equation}
+\end{align}
 
 The first derivative of the free energy with respect to the field gives
-\begin{equation}\begin{aligned}
+\begin{align}
 	F^\prime(h\neq 0, T\to 0) = -\text{sign}(h)\left(M - \frac{1}{2}\right)
-\end{aligned}\end{equation}
+\end{align}
 There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get
-\begin{equation}\begin{aligned}
+\begin{align}
 	F^\prime(h \to 0^\pm, T\to 0) = \mp\left(M - \frac{1}{2}\right) = \mp \frac{1}{2}\left( K - 1 \right) 
-\end{aligned}\end{equation}
+\end{align}
 
@@
 Given the Helmholtz free energy \(F = -k_B T \ln Z = - \frac{1}{\beta} \ln\sum_n e^{-\beta E_n}\), the thermal entropy at temperature \(T\) is given by
-\begin{equation}\begin{aligned}
+\begin{align}
 	S(T) = - \frac{\partial{F}}{\partial{T}} = k_B \ln\sum_n e^{-\beta E_n} + \frac{\sum_n E_n e^{-\beta E_n}}{T \sum_n e^{-\beta E_n}}
-\end{aligned}\end{equation}
+\end{align}
 In the limit of \(T \to 0\), only the lowest energy state \(E_\text{gs}\) will survive. Assuming this state has a degeneracy \(d_\text{gs}\), we have
-\begin{equation}\begin{aligned}
+\begin{align}
 	S(T \to 0) = k_B \ln\left(d_\text{gs} e^{-\beta E_\text{gs}}\right) + \frac{d_\text{gs} E_\text{gs}e^{-\beta E_\text{gs}}}{T d_\text{gs} e^{-\beta E_\text{gs}}} = k_B \ln d_\text{gs} - \frac{1}{T}E_\text{gs} + \frac{1}{T}E_\text{gs} = k_B \ln d_\text{gs}
-\end{aligned}\end{equation}
+\end{align}
 This is a general result that holds for any system with a \(d_\text{gs}\)-fold degenerate ground state.
@@
 The impurity contribution is therefore
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{res_entropy}
 	S_\text{imp}(T\to 0) = k_B \ln K
-\end{aligned}\end{equation}
+\end{align}
 
 We wish to point out that this value is different from the "standard" result 
-\begin{equation}\begin{aligned}
+\begin{align}
 \label{cft_entropy}
 S = \ln 2\cos \frac{\pi}{K+2}
-\end{aligned}\end{equation}
+\end{align}
 obtained from other methods like the Bethe ansatz (BA) and conformal field theory (CFT) calculations \cite{Gan_Andrei_Coleman_1993,andrei_destri_1984,Tsvelick_weigmann_mchannel_1985,sacramento1989,emery_kivelson,affleck_1991_overscreen}.
@@
 \label{1KondoURG}
-\begin{equation}\begin{aligned}
+\begin{align}
 	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{k,l} J^z S_d^z s^z_{kl} + \frac{1}{2}\sum_{k,l} J^t \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right)
-\end{aligned}\end{equation}
+\end{align}
 where \(s^z_{kl} = \frac{1}{2}\left(c^\dagger_{k\uparrow}c_{l \uparrow} - c^\dagger_{k\downarrow}c_{l \downarrow}\right)\), \(s^-_{kl} = c^\dagger_{k \downarrow}c_{l \uparrow}\) and \(s^+_{kl} = {s^-_{lk}}^\dagger\).
@@
 The scheme is that we will disentangle an electron \(q\beta\) from the Hamiltonian, \(q\) being the momentum and \(\beta\) the spin. The diagonal part of the Hamiltonian under this scheme is
-\begin{equation}\begin{aligned}
+\begin{align}
 \label{kondodiag}
 H^D_{q\beta} = \epsilon_q \tau_{q\beta} + J^z S_d^z s_{qq}^z
-\end{aligned}\end{equation}
+\end{align}
 The off-diagonal parts at a particular RG step \(H^I_1\) and \(H^I_0\), that start from particle and hole states respectively, are
-\begin{equation}\begin{aligned}
+\begin{align}
 	H^I_1 = \sum_{|k|<\Lambda,q} J^z S_d^z s^z_{kq} + \frac{1}{2}\sum_{|k|<\Lambda,q} J^t \left(S_d^+ s^-_{kq} + S_d^- s^+_{kq}\right)\\
 	H^I_0 = \sum_{|k|<\Lambda,q} J^z S_d^z s^z_{qk} + \frac{1}{2}\sum_{|k|<\Lambda,q} J^t \left(S_d^+ s^-_{qk}  + S_d^- s^+_{qk}\right)
-\end{aligned}\end{equation}
+\end{align}
 \(H^I_1\) is the Hamiltonian term that scatters from the occupied configuration of \(q\), \(H^I_0\) is the same from the unoccupied configuration.
@@
 The particle sector involves integrating out those states which are occupied (\(\hat n_{q\beta}=1\)). We will work at an energy  shell \(\epsilon_q = -D\). The renormalization is
-\begin{equation}\begin{aligned}
+\begin{align}
 	H^I_0 \frac{1}{\omega - H^D_{q\beta}} H^I_1
-\end{aligned}\end{equation}
+\end{align}
 
@@
 Substituting all this, we get
-\begin{equation}\begin{aligned}
+\begin{align}
 	\frac{1}{\omega - D/2 + J/4}\sum_{|k,k^\prime|<\Lambda,q}\left[\frac{1}{2}J^z J^t \left(S_d^z S_d^+ s^z_{qk^\prime}s^-_{kq} + S_d^z S_d^- s^z_{qk^\prime}s^+_{kq}\right) + \frac{1}{2}J^t J^z \left(S_d^+ S_d^z s^-_{qk^\prime}s^z_{kq} + S_d^- S_d^z s^+_{qk^\prime}s^z_{kq}\right)\right.\\
 +\left.\frac{1}{4}{J^t}^2 \left(S_d^- S_d^+ s^+_{qk^\prime}s^-_{kq} + S_d^+ S_d^- s^-_{qk^\prime}s^+_{kq}\right)\right]
-\end{aligned}\end{equation}
+\end{align}
 We now simplify the products and keep only terms diagonal in \(q\).
@@
 The renormalization becomes
-\begin{equation}\begin{aligned}
+\begin{align}
 	\frac{1}{\omega - D/2 + J/4}\sum_{|k,k^\prime|<\Lambda,q}\left[\frac{1}{4}J^z J^t \left(-\frac{1}{2}S_d^+ \hat n_{q}s^-_{kk^\prime} - \frac{1}{4}S_d^- \hat n_{q} s^z_{kk^\prime}\right) - \frac{1}{4}{J^t}^2 S_d^z\left(-\hat n_{q \uparrow}c^\dagger_{k \downarrow}c_{k^\prime \downarrow} + \hat n_{q \downarrow}c^\dagger_{k \uparrow}c_{k^\prime \uparrow}\right)\right]
-\end{aligned}\end{equation}
+\end{align}
 We now replace \(\sum_q \hat n_{q\sigma} = n(D)\). The renormalization due to excitations coming from the particle sector is
-\begin{equation}\begin{aligned}
+\begin{align}
 	\Delta H_1 = -\frac{1}{2}\frac{n(D)}{\omega - D/2 + J/4}\sum_{|k,k^\prime|<\Lambda}\left[J^z J^t \frac{1}{2}\left(S_d^+ s^-_{kk^\prime} + S_d^- s^z_{kk^\prime}\right) + {J^t}^2 S_d^z s^z_{kk^\prime}\right]
-\end{aligned}\end{equation}
+\end{align}
 The renormalization in the couplings coming from the particle sector is therefore,
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{kondo_part}
 	\Delta J^z = -\frac{1}{2}\frac{{J^t}^2n(D)}{\omega - D/2 + J/4}, && \Delta J^t = -\frac{1}{2}\frac{J^z J^tn(D)}{\omega - D/2 + J/4}
-\end{aligned}\end{equation}
+\end{align}
 
@@
 The hole sector involves integrating out those states which are vacant (\(\hat n_{q\beta}=1\)). We will work at an energy  shell \(\epsilon_q = D\). The renormalization is
-\begin{equation}\begin{aligned}
+\begin{align}
 	H^I_1 \frac{1}{\omega - H^D_{q\beta}} H^I_0
-\end{aligned}\end{equation}
+\end{align}
 The same considerations as those in the particle sector apply here, and the denominator becomes \(\omega - D/2 + J/4\), while the numerator is \(H^I_1 H^I_0\).
@@
 Since the renormalization in the hole sector is equal to that in the particle sector, the total renormalization is simply twice that in the particle sector (eqs.~\ref{kondo_part}):
-\begin{equation}\begin{aligned}
+\begin{align}
 	\Delta J^z = -\frac{{J^t}^2n(D)}{\omega - D/2 + J/4}, && \Delta J^t = -\frac{J^z J^tn(D)}{\omega - D/2 + J/4}
-\end{aligned}\end{equation}
+\end{align}
 If we set \(J_z = J_t = J\), we have an SU(2)-symmetric Kondo model \(J \vec{S_d}\cdot\vec{s}\).
-\begin{equation}\begin{aligned}
+\begin{align}
 	\label{kondosym}
 	\Delta J = - \frac{J^2 n(D)}{\omega - D/2 + \frac{1}{4}J}
-\end{aligned}\end{equation}
+\end{align}
 To recover the one-loop form, we can replace \(\omega\) with the bare value \(-D/2\) and ignore the \(J\) in the denominator (small \(J\)).
-\begin{equation}\begin{aligned}
+\begin{align}
 	\Delta J \approx \frac{J^2 n(D)}{D}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
+\end{align}
+\begin{align}
 	\Delta J^{(2)} = -\frac{J^2 n(D)}{\omega - D/2 + J/4}
-\end{aligned}\end{equation}
+\end{align}
 For \(\omega < D/2\), we get the flow towards the strong-coupling fixed point.
@@
 For \(\omega = -D/2\) and \(J \ll D\), we get the one-loop PMS form.
-\begin{equation}\begin{aligned}
+\begin{align}
 	\Delta J^{(2)} = \frac{J^2 n(D)}{D - J/4} \simeq \frac{J^2 n(D)}{D}
-\end{aligned}\end{equation}
+\end{align}
 

### 2021-12-07 notes/multi-channel-urg.tex
started connecting the NFL to the k-space MFL of hubbard work

@@
 \section{Introduction of the Hamiltonian and its zero mode}
-The isotropic multi-channel Kondo model \cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik} is described by the Hamiltonian
+The isotropic multi-channel Kondo model \cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact} is described by the Hamiltonian
 \begin{align}
@@
 
-\section{SYmmetries of the Hamiltonian}
+\section{Symmetries of the Hamiltonian}
 This zero mode Hamiltonian commutes with a number of operators, revealing various symmetries of the problem.
@@
 Setting \(J_+ = J_-\) leads to the critical fixed point at \(J_+^* = J_-^* = J_* = \frac{8}{K \rho}\).
-We now perturb around this fixed-point by defining new variables \(j_\pm = J_\pm - J_*\).
+We now perturb around this fixed point by defining new variables \(j_\pm = J_\pm - J_*\).
 We also assume that \(D - J_\pm / 4 \simeq D - J_*/4\).
@@
 For small \(j_+\), we have \(j_+^2 < 2J_* |j_-|\)  and \(\Delta j_+ > 0\).
-This means that the isotropic fixed-point is repulsive under anisotropy \cite{Noz_blandin_1980}.
+This means that the isotropic fixed point is repulsive under anisotropy \cite{Noz_blandin_1980}.
 The coupling \(j_+\) being relevant means we have a single-channel Kondo problem.
@@
 \end{align}
-At the final step, we chose the positive solution, because \(j_+\) is relevant in this regime. The new fixed-point value of \(J_+\) is therefore
+At the final step, we chose the positive solution, because \(j_+\) is relevant in this regime. The new fixed point value of \(J_+\) is therefore
 \begin{align}
@@
 \end{align}
-In other words, the \(K\) channel fixed-point flows to the \(K-1\) channel fixed-point.
+In other words, the \(K\) channel fixed point flows to the \(K-1\) channel fixed point.
 
@@
 \ref{irrel_Jplus}), and \(J_-\) remains relevant.
-Since there is no numerator fixed-point in the relevant coupling \(J_-\) and because all other couplings are irrelevant, the equation for \(J_-\) is replaced by the single-channel Kondo coupling URG equation, and the low-energy physics is then of strong-coupling..
+Since there is no numerator fixed point in the relevant coupling \(J_-\) and because all other couplings are irrelevant, the equation for \(J_-\) is replaced by the single-channel Kondo coupling URG equation, and the low-energy physics is then of strong-coupling..
 \begin{figure}[htpb]
@@
 
+\section{MFL and orthogonality catastrophe in low-energy excitations of 2-CKM}
+At the stable fixed point \(J ^* = J_1^* = \frac{8}{K \rho}\), the ground states of the Hamiltonian are those of the star graph model, with a degeneracy of \(K\).
+We now specialise to the two-channel Kondo model.
+To find the low-energy excitations on top of this ground state manifold, one can insert a tight-binding nearest-neighbour hopping between the zeroth site (the one that holds the impurity) and the first site (site that's nearest to the zeroth site) as a perturbation and calculate the diagonal and off-diagonal terms generated by this perturbation.
+It is found that when we trace out the impurity, we are left only with real space off-diagonal terms:
+\begin{equation}\begin{aligned}
+	\label{nfl_terms}
+	V_\text{eff} = \frac{2t^2}{J^*}\left[\left(\sigma^z_{0,1}\right)^2 s^+_{0,2} + \left(\sigma^z_{0,2}\right)^2 s^+_{0,1}\right] \left(s^-_{1,1} + s^-_{1,2}\right) + \text{h.c.}
+\end{aligned}\end{equation}
+where \(\sigma^z_{0,l} = \hat n_{0\uparrow,l} - \hat n_{0\downarrow,l}, s^+ = c^\dagger_{0 \uparrow,l}c_{0 \downarrow,l}\) and \(s^- = \left(s^+\right)^\dagger\).
+The notation \(0\sigma,l\) has the site index \(i=0,1,2,\ldots\) as the first label, the spin index \(\sigma=\uparrow,\downarrow\) as the second label and the channel index \(l=1,2\) as the third index.
+
+These are the terms that are generated because of the presence of the impurity.
+Such a non-Fermi liquid contribution to the effective Hamiltonian and the absence of any Fermi-liquid term should be contrasted with the local Fermi liquid excitations induced by the singlet ground state of the single-channel Kondo model at fourth order.
+We wish to point out that such non-Fermi liquid terms were also obtained by Coleman, et al.~\cite{Coleman_tsvelik} in terms of Majorana fermions at the zeroth site and the first site.
+They then went on to compute a single-particle self-energy renormalization coming from this non-Fermi liquid term that matches the phenomenological \cite{varma2002singular} and microscopic forms of the marginal Fermi liquid self-energy \cite{anirbanmott1,anirbanurg1}.
+We take a different route in order to calculate the self-energy contribution coming from eq.~\ref{nfl_terms}, one that involves \cite{anirbanmott1}.
+
+In \cite{anirbanurg1}, it was found that the normal phase of the Mott insulator was a marginal Fermi liquid in momentum space, defined by the interaction term 
+\begin{equation}\begin{aligned}
+	\label{mfl_urg}
+	H_\text{MFL} = \sum_{k,k^\prime,k^{\prime\prime},\sigma}R \hat n_{k} \hat n_{k^\prime \overline\sigma}\left(1 - \hat n_{k^{\prime\prime}\sigma}\right) 
+\end{aligned}\end{equation}
+We wish to look for such a term in the effective Hamiltonian.
+For this, we will perform a perturbative treatment of the hopping at strong-coupling \(J \to \infty\) where the perturbative coupling \(t^2/J\) is arbitrarily small and again obtain eq.~\ref{nfl_terms}.
+Sicne we are looking for a 2 particle-1 hole term in \(k-\)space, we will keep only those terms that can produce such a term:
+\begin{equation}\begin{aligned}
+	V_\text{eff} = \frac{2t^2}{J}\sum_{l=1,2}\left(\sum_\sigma \hat n_{0\sigma,l}\right) s^+_{0,\bar l}s^-_{1,\bar l} + \text{h.c.}
+\end{aligned}\end{equation}
+where \(\bar l = 3 - l\). To compare with eq.~\ref{mfl_urg}, we will fourier transform this effective Hamiltonian (after inserting the kinetic energy of the bath) into \(k-\)space.
+\begin{equation}\begin{aligned}
+	\label{k_space_od}
+	H_\text{eff} = \sum_{k\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + \sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \text{h.c.}
+\end{aligned}\end{equation}
+This form of the Hamiltonian is very similar to the three-particle interaction term in Appendix B of \cite{anirbanmott1}.
+The channel indices in eq.~\ref{k_space_od} can be mapped to the normal directions in \cite{anirbanmott1}.
+Eq.~\ref{k_space_od} has a diagonal component.
+
 \section{Effective Hamiltonian for low-energy excitations: \(k-\)space}
@@
 
-\section{Impurity Susceptibility from zero-mode fixed-point Hamiltonian}
-The zero-mode approximation of the fixed-point Hamiltonian is a star graph Hamiltonian:
+\section{Impurity susceptibility from zero-mode fixed point Hamiltonian}
+The zero-mode approximation of the fixed point Hamiltonian is a star graph Hamiltonian:
 \begin{align}
@@
 
-\section{Bath Susceptibility from zero-mode fixed-point Hamiltonian}
+\section{Bath Susceptibility from zero-mode fixed point Hamiltonian}
 We insert a magnetic field that acts only on the bath and then attempt to diagonalize the Hamiltonian.
@@
 \bibliography{multi-channel-urg}
+
 \end{document}

### 2021-12-08 notes/multi-channel-urg.tex
completed line of arguments that provide self-energy and Z from the Hubbard work

@@
 
-\section{Duality of the Hamiltonian RG flow}
-The infrared multi-channel Kondo Hamiltonian is given by
-\begin{equation}\begin{aligned}
-	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J_<\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
-\end{aligned}\end{equation}
-where \(J_<\) indicates that it parametrizes the weak-coupling Hamiltonian.
-\textit{Assuming one can also write a strong-coupling Hamiltonian that is identical to the weak-coupling one, the model can then be said to possess S-duality.} This has been demonstrated for the two-channel Kondo \cite{kroha_kolf_2007} by defining fermionic and bosonic operators \(F_\sigma\) and \(B\) from the ground states and excited states respectively of the zero-mode Hamiltonian eq.~\ref{zeromode_ham}, then rewriting the Hamiltonian eq.~\ref{mc_ham} in terms of these fermions and bosons by resolving the Hamiltonian in the eigenbasis of the zero mode Hamiltonian, and finally by decoupling the interaction between the bosons and the fermions through a Schrieffer-Wolff transformation (SWT) and projecting on to the fermionic states.
-The last step is what makes it a strong-coupling Hamiltonian: the SWT and the subsequent projection is perturbative in powers of a new coupling \(J_> = t^2/J_<\) and makes sense only in the strong-coupling limit \(J_< \gg t\).
-In that sense, the SWT removes the interaction between the ground state manifold and the excited levels.
-The result of these three steps is another two-channel Kondo model, but now parametrized by the strong-coupling coupling \(J_>\) \cite{kroha_kolf_2007}.
-
-If a general \(K-\)channel Kondo model possesses S-duality under a transformation \(J_> = \frac{\gamma D^2_0}{J_<} = \frac{\gamma 16t^2}{J_<}\), \(D_0 = 4t\) being the bare cut-off of the problem, we can write Hamiltonians \(H(J_<)\) and \(H(J_>)\) that are identical in form.
-This means that the two Hamiltonians will have identical properties.
-An immediate and obvious conclusion of this is that both the Hamiltonians will have identical RG flows:
-\begin{equation}\begin{aligned}
-	\Delta J_< = \beta(J_<), &&&\Delta J_> = \beta(J_>)
-\end{aligned}\end{equation}
-where \(\beta\) represents the RG beta function.
-From URG calculations, we know that there is a unique attractive fixed point along the RG flow.
-This means that we must have \(J_<^* = J_>^* = J^*\), and that \(\beta(J_>^*) = 0\).
-From eq.~\ref{rg_beta}, we get
-\begin{equation}\begin{aligned}
-	J_>^* = \frac{8}{K \rho} = J_<^* \implies \frac{\gamma 16 t^2}{J_<^*} = J_<^* \implies \gamma = \left(\frac{J^*_<}{4t}\right) ^2 = \left( \frac{2}{K \rho t}\right) ^2
-\end{aligned}\end{equation}
-This, then, is the transformation that makes the critical fixed point self-dual.
-
 \section{MFL and orthogonality catastrophe in low-energy excitations of 2-CKM}
@@
 For this, we will perform a perturbative treatment of the hopping at strong-coupling \(J \to \infty\) where the perturbative coupling \(t^2/J\) is arbitrarily small and again obtain eq.~\ref{nfl_terms}.
-Sicne we are looking for a 2 particle-1 hole term in \(k-\)space, we will keep only those terms that can produce such a term:
+Such a change from the strong-coupling model with parameter \(J\) to a weak-coupling model with parameter \(t^2/J\) amounts to a duality transformation \cite{kroha_kolf_2007,zitko_fabrozio_2017}.
+It can be shown that the duality transformation leads to an identical multi-channel Kondo model \cite{kroha_kolf_2007} (self-duality), which implies we can have identical RG flows, and our transformation simply extracts the non-Fermi liquid piece from the dual model.
+The self-duality also implies that the critical intermediate-coupling fixed point is unique and can be reached from either of the models.
+
+Since we are looking for a 2 particle-1 hole term in \(k-\)space, we will keep only those terms that can produce such a term:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where \(\bar l = 3 - l\). To compare with eq.~\ref{mfl_urg}, we will fourier transform this effective Hamiltonian (after inserting the kinetic energy of the bath) into \(k-\)space.
+where \(\bar l = 3 - l\) is the channel index complementary to \(l\).
+To compare with eq.~\ref{mfl_urg}, we will fourier transform this effective Hamiltonian (after inserting the kinetic energy of the bath) into \(k-\)space.
 \begin{equation}\begin{aligned}
@@
 The channel indices in eq.~\ref{k_space_od} can be mapped to the normal directions in \cite{anirbanmott1}.
-Eq.~\ref{k_space_od} has a diagonal component.
+As specualted eariler, the three-particle interaction in eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
+\begin{equation}\begin{aligned}
+	H_\text{eff,MFL} = \sum_{\sigma, k, k_1, k_2, l} \frac{2t^2}{J}e^{i\left(k_1 - k_2\right)a} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \text{h.c.} = \sum_{\sigma, k, k_1, k_2, l} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right)
+\end{aligned}\end{equation}
+The largest term is obtained by choosing \(k_1 = k_2 = k^\prime\):
+\begin{equation}\begin{aligned}
+	\label{mfl_large}
+	H^*_\text{eff,MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)
+\end{aligned}\end{equation}
+Following \cite{anirbanmott1}, one can follow the RG evolution of the dual coupling \(J^\prime = \frac{4t^2}{J}\), leading to a \(k-\)space-averaged self-energy for each channel (eq.
+33 of \cite{anirbanmott1})
+\begin{equation}\begin{aligned}
+	\Sigma_l(\omega_l) \sim \omega_l \ln |\omega_l|\\
+\end{aligned}\end{equation}
+where \(\omega_l\) is the fluctuation scale for a particular channel. The self-energy also provides the quasiparticle residue for each channel\cite{anirbanmott1}:
+\begin{equation}\begin{aligned}
+	Z_l(\omega_l) = \left(2 - \ln \omega_l\right) ^{-1}
+\end{aligned}\end{equation}
+As the energy scales \(\omega_l \to 0\), the \(Z_l\) vanishes, implying that the ground state and lowest-lying excitations, in the presence of the non-Fermi liquid terms, are not adiabatically connected to the Fermi gas.
+This is the orthogonality catastrophe in the two-channel Kondo problem, and it is brought about by the presence of the terms in eq.~\ref{mfl_large}.
+Such terms were absent in the similar perturbative expansion of the single-channel Kondo model, because there was no multiply-degenerate ground state manifold that allowed scattering.
+This line of argument shows that the extra degeneracy of the ground state subspace that comes about when one upgrades from the single-channel Kondo model to the multi-channel Kondo models is at the heart of the non-Fermi liquid behaviour, and the orthogonality catastrophe should be a general feature of all multi-channel Kondo models, even though we have demonstrated this only for the two-channel case.
 

### 2021-12-08 notes/multi-channel-urg.tex
added the sigma tau model and tried sketching the RG and self energy derivation but got stuck, waiting for AM to reply

@@
 \documentclass{revtex4-2}
-\usepackage{braket,amsmath,amssymb,graphicx,float,paralist}
+\usepackage{braket,amsmath,amssymb,graphicx,float,paralist,color}
 \usepackage[hidelinks]{hyperref}
@@
 \begin{align}
-	c^\dagger T = J \sum_{k < \Lambda_j, \alpha}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, && H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
+	c^\dagger T = J \sum_{|k| < \Lambda_j, \atop{\alpha=\uparrow,\downarrow}}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, ~H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
 \end{align}
@@
 This equation has a stable fixed point at \(J^* = \frac{8}{\rho K}\).
-The value of the fixed point agrees with the poor man's scaling calculation in \cite{tripathi2018landau}, but differs from the value of \(\frac{2}{\rho K}\) obtained in other references \cite{Kuramoto1998,Kogan_2018} \textbf{[MOST PROBABLY THERE ARE OTHER REFERENCES]}.
+The value of the fixed point agrees with the poor man's scaling calculation in \cite{tripathi2018landau}, but differs from the value of \(\frac{2}{\rho K}\) obtained in other references \cite{Kuramoto1998,Kogan_2018}.
 
@@
 \end{figure}
-For \(D\) not so large, the denominator also comes into play, and eq.\ref{mchannel} holds. We get the possibility of two fixed points - one from the numerator and the other from the numerator.
+For \(D\) not so large, the denominator also comes into play, and Eq.~\ref{mchannel} holds. We get the possibility of two fixed points - one from the numerator and the other from the numerator.
 \begin{figure}[!htb]
@@
 As shown in fig.~\ref{rhomin_vs_D}, we have \(J_1^* \ll D_0\).
-If we start with \(J_0\) in the neighborhood of \(J_1^*\), we can use \(J_1^* \ll D_0\) to ignore \(J\) in the denominator and the RG equation reduces to the poor man's scaling form eq.~\ref{pms_mchannel}.
+If we start with \(J_0\) in the neighborhood of \(J_1^*\), we can use \(J_1^* \ll D_0\) to ignore \(J\) in the denominator and the RG equation reduces to the poor man's scaling form Eq.~\ref{pms_mchannel}.
 The denominator fixed point has effectively moved off to infinity.
@@
 These are the terms that are generated because of the presence of the impurity.
-Such a non-Fermi liquid contribution to the effective Hamiltonian and the absence of any Fermi-liquid term should be contrasted with the local Fermi liquid excitations induced by the singlet ground state of the single-channel Kondo model at fourth order.
-We wish to point out that such non-Fermi liquid terms were also obtained by Coleman, et al.~\cite{Coleman_tsvelik} in terms of Majorana fermions at the zeroth site and the first site.
-They then went on to compute a single-particle self-energy renormalization coming from this non-Fermi liquid term that matches the phenomenological \cite{varma2002singular} and microscopic forms of the marginal Fermi liquid self-energy \cite{anirbanmott1,anirbanurg1}.
-We take a different route in order to calculate the self-energy contribution coming from eq.~\ref{nfl_terms}, one that involves \cite{anirbanmott1}.
+Such a non-Fermi liquid (NFL) contribution to the effective Hamiltonian and the absence of any Fermi-liquid term should be contrasted with the local Fermi liquid excitations induced by the singlet ground state of the single-channel Kondo model at fourth order.
+We wish to point out that such NFL terms were also obtained by Coleman, et al.~\cite{Coleman_tsvelik} in terms of Majorana fermions at the zeroth site and the first site.
+They then went on to compute a single-particle self-energy renormalization coming from this NFL term that matches the phenomenological \cite{varma2002singular} and microscopic forms of the marginal Fermi liquid self-energy \cite{anirbanmott1,anirbanurg1}.
+We take a different route in order to calculate the self-energy contribution coming from Eq.~\ref{nfl_terms}, one that involves \cite{anirbanmott1}.
 
@@
 We wish to look for such a term in the effective Hamiltonian.
-For this, we will perform a perturbative treatment of the hopping at strong-coupling \(J \to \infty\) where the perturbative coupling \(t^2/J\) is arbitrarily small and again obtain eq.~\ref{nfl_terms}.
+For this, we will perform a perturbative treatment of the hopping at strong-coupling \(J \to \infty\) where the perturbative coupling \(t^2/J\) is arbitrarily small and again obtain Eq.~\ref{nfl_terms}.
 Such a change from the strong-coupling model with parameter \(J\) to a weak-coupling model with parameter \(t^2/J\) amounts to a duality transformation \cite{kroha_kolf_2007,zitko_fabrozio_2017}.
-It can be shown that the duality transformation leads to an identical multi-channel Kondo model \cite{kroha_kolf_2007} (self-duality), which implies we can have identical RG flows, and our transformation simply extracts the non-Fermi liquid piece from the dual model.
+It can be shown that the duality transformation leads to an identical multi-channel Kondo model \cite{kroha_kolf_2007} (self-duality), which implies we can have identical RG flows, and our transformation simply extracts the NFL piece from the dual model.
 The self-duality also implies that the critical intermediate-coupling fixed point is unique and can be reached from either of the models.
@@
 where \(\bar l = 3 - l\) is the channel index complementary to \(l\).
-To compare with eq.~\ref{mfl_urg}, we will fourier transform this effective Hamiltonian (after inserting the kinetic energy of the bath) into \(k-\)space.
+To compare with Eq.~\ref{mfl_urg}, we will fourier transform this effective Hamiltonian (after inserting the kinetic energy of the bath) into \(k-\)space.
 \begin{equation}\begin{aligned}
@@
 This form of the Hamiltonian is very similar to the three-particle interaction term in Appendix B of \cite{anirbanmott1}.
-The channel indices in eq.~\ref{k_space_od} can be mapped to the normal directions in \cite{anirbanmott1}.
-As specualted eariler, the three-particle interaction in eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
+The channel indices in Eq.~\ref{k_space_od} can be mapped to the normal directions in \cite{anirbanmott1}.
+As specualted eariler, the three-particle interaction in Eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-Following \cite{anirbanmott1}, one can follow the RG evolution of the dual coupling \(J^\prime = \frac{4t^2}{J}\), leading to a \(k-\)space-averaged self-energy for each channel (eq.
-33 of \cite{anirbanmott1})
+Following \cite{anirbanmott1}, one can follow the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\text{rh}\) RG step, in the form of the URG equation
 \begin{equation}\begin{aligned}
+	\Delta R_j = \frac{R_j^2}{\bar\omega - \epsilon_{j}/2 + R_j/8}
+\end{aligned}\end{equation}
+In the RG equation, \(\epsilon_{j}\) represents the energy of the \(j^\text{th}\) isoenergetic shell.
+It is seen from the RG equation that \(R\) is relevant in the range of \(\bar\omega = \epsilon_j -\omega\) that has been used throughout \((\omega < \epsilon_j/2)\), \textcolor{red}{leading to a fixed-point at \(R_*/8 = \bar\omega - \epsilon_*/2)\)}.
+The relevance of \(R\) is expected because the strong-coupling \(J\) is irrelevant and \(R \sim 1/J\).
+
+The renormalization in \(R\) leads to a renormalization in the single-particle self-energy \cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalization is
+\begin{equation}\begin{aligned}
+	\Delta \Sigma_l(\omega) = \rho R_*^2\int_0^{\epsilon_*} \frac{d\epsilon}{\bar\omega - \epsilon_j/2 + R_*/8}
+\end{aligned}\end{equation}
+leading to a \(k-\)space-averaged self-energy for each channel (eq. 33 of \cite{anirbanmott1})
+\begin{equation}\begin{aligned}
+	\label{self_energy}
 	\Sigma_l(\omega_l) \sim \omega_l \ln |\omega_l|\\
@@
 \end{aligned}\end{equation}
-As the energy scales \(\omega_l \to 0\), the \(Z_l\) vanishes, implying that the ground state and lowest-lying excitations, in the presence of the non-Fermi liquid terms, are not adiabatically connected to the Fermi gas.
-This is the orthogonality catastrophe in the two-channel Kondo problem, and it is brought about by the presence of the terms in eq.~\ref{mfl_large}.
+As the energy scales \(\omega_l \to 0\), the \(Z_l\) vanishes, implying that the ground state and lowest-lying excitations, in the presence of the NFL terms, are not adiabatically connected to the Fermi gas.
+This is the orthogonality catastrophe in the two-channel Kondo problem, and it is brought about by the presence of the terms in Eq.~\ref{mfl_large}.
 Such terms were absent in the similar perturbative expansion of the single-channel Kondo model, because there was no multiply-degenerate ground state manifold that allowed scattering.
-This line of argument shows that the extra degeneracy of the ground state subspace that comes about when one upgrades from the single-channel Kondo model to the multi-channel Kondo models is at the heart of the non-Fermi liquid behaviour, and the orthogonality catastrophe should be a general feature of all multi-channel Kondo models, even though we have demonstrated this only for the two-channel case.
-
+This line of argument shows that the extra degeneracy of the ground state subspace that comes about when one upgrades from the single-channel Kondo model to the multi-channel Kondo models is at the heart of the NFL behaviour, and the orthogonality catastrophe should be a general feature of all multi-channel Kondo models, even though we have demonstrated this only for the two-channel case.
+
+The fact that the marginal Fermi liquid term in eq.~\ref{mfl_large} involves all momenta means it is localised in real space.
+This can also be understood from the fact that the parent NFL term in eq.~\ref{nfl_terms} is also local.
+A local NFL term with a self-energy of the form in eq.~\ref{self_energy} was also obtained in the \(\sigma-\tau\) model by Coleman et al.
+\cite{Coleman_tsvelik}.
+The common features show the universality between the two-channel Kondo and the \(\sigma-\tau\) models.
 \section{Effective Hamiltonian for low-energy excitations: \(k-\)space}
@@
 \end{align}
-\textit{One important conclusion that comes out of these calculations is that if the ground state is degenerate, the effective Hamiltonians is independent of which ground state we choose to start from in eq.~\ref{gstate_Expand}.
+\textit{One important conclusion that comes out of these calculations is that if the ground state is degenerate, the effective Hamiltonians is independent of which ground state we choose to start from in Eq.~\ref{gstate_Expand}.
 This is because the only difference in the various degenerate ground states is in the coefficients \(C_{S_d^z, s_\text{tot},s_\text{tot}^z}\).
@@
 For the two-channel problem, we have four possible states in total: \(\left( s_\text{tot}, s_\text{tot}^z \right) = \left\{ (0,0), (1,-1), (1,0), (1,1) \right\} \).
-The states in the eq.~\ref{no_V} cannot be acted on by \(V\) or \(V^\dagger\), so the effective Hamiltonian for these states will consist of only the diagonal part:
+The states in the Eq.~\ref{no_V} cannot be acted on by \(V\) or \(V^\dagger\), so the effective Hamiltonian for these states will consist of only the diagonal part:
 \begin{align}
@@
 The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\).
-For \(h = 0\), the ground state subspace is \(K-\)fold degenerate and is formed by the negative solutions of eq.~\ref{eigenvalue}.
+For \(h = 0\), the ground state subspace is \(K-\)fold degenerate and is formed by the negative solutions of Eq.~\ref{eigenvalue}.
 This common \(K-\)fold degenerate eigenvalue is \(-J(M+1)/2\).
@@
 \end{align}
-which means \(E_\text{min} = -\frac{J}{2}\left( M + 1 \right) - |h|\left(M - \frac{1}{2}\right)\). We also know, from eq.~\ref{extra_degen}, that \(d^\prime_\text{gs} = {}^{K-1}C_{K/2 - K/2} = 1\).
+which means \(E_\text{min} = -\frac{J}{2}\left( M + 1 \right) - |h|\left(M - \frac{1}{2}\right)\). We also know, from Eq.~\ref{extra_degen}, that \(d^\prime_\text{gs} = {}^{K-1}C_{K/2 - K/2} = 1\).
 The free energy for a non-zero field is therefore
@@
 The difference is not only in the value but also in the origin.
-Eq.~\ref{res_entropy} describes the thermal entropy coming purely from the quantum mechanical degeneracy of the star graph problem (which is the zero mode of the full multi-channel Kondo problem), while the result eq.~\ref{cft_entropy} presumably arises from the lowest-lying excitations on top of the zero mode arising from the conduction bath \(k-\)states.
-Another difference lies in the fact that while eq.~\ref{res_entropy} holds true independent of system size, eq.~\ref{cft_entropy} is correct only in the thermodynamic limit and only if the limit of system size \(L \to \infty\) is taken prior to taking the limit of temperature \(T \to 0\) \cite{Gan_Andrei_Coleman_1993,rozhkov_1998,vondelft_prl_1998}.
-We note however that the entropy coming from the degeneracy is larger than that coming from the excitations (fig.~\ref{entropy_comparison}), and consequently plays a very important role in the physics of the multi-channel Kondo problem, being responsible for the non-Fermi liquid physics and the critical behaviour near the fixed point.
+Eq.~\ref{res_entropy} describes the thermal entropy coming purely from the quantum mechanical degeneracy of the star graph problem (which is the zero mode of the full multi-channel Kondo problem), while the result Eq.~\ref{cft_entropy} presumably arises from the lowest-lying excitations on top of the zero mode arising from the conduction bath \(k-\)states.
+Another difference lies in the fact that while Eq.~\ref{res_entropy} holds true independent of system size, Eq.~\ref{cft_entropy} is correct only in the thermodynamic limit and only if the limit of system size \(L \to \infty\) is taken prior to taking the limit of temperature \(T \to 0\) \cite{Gan_Andrei_Coleman_1993,rozhkov_1998,vondelft_prl_1998}.
+We note however that the entropy coming from the degeneracy is larger than that coming from the excitations (fig.~\ref{entropy_comparison}), and consequently plays a very important role in the physics of the multi-channel Kondo problem, being responsible for the NFL physics and the critical behaviour near the fixed point.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../numerics/entropy_comparison.pdf}
+	\includegraphics[width=0.4\textwidth]{../numerics/entropy_comparison.pdf}
 	\caption{Comparison of star graph zero temperature entropy with CFT/Bethe ansatz formula}
@@
 
+\clearpage
 \appendix
 \section{URG analysis of the single-channel Kondo model}
+The single-channel SU(2) Kondo model consists of a spin-half impurity interacting with a band of itinerant conduction electrons through a spin-exchange coupling:
 \label{1KondoURG}
@@
 \end{align}
-where \(s^z_{kl} = \frac{1}{2}\left(c^\dagger_{k\uparrow}c_{l \uparrow} - c^\dagger_{k\downarrow}c_{l \downarrow}\right)\), \(s^-_{kl} = c^\dagger_{k \downarrow}c_{l \uparrow}\) and \(s^+_{kl} = {s^-_{lk}}^\dagger\).
+Here, \(s^z_{kl} = \frac{1}{2}\left(c^\dagger_{k\uparrow}c_{l \uparrow} - c^\dagger_{k\downarrow}c_{l \downarrow}\right)\), \(s^-_{kl} = c^\dagger_{k \downarrow}c_{l \uparrow}\) and \(s^+_{kl} = {s^-_{lk}}^\dagger\).
 Also, \(\tau = \hat n - \frac{1}{2}\).
-\(k,l\) sum over the momentum states.
-\(\vec S_d\) is the impurity spin operator.
+The indices \(k,l\) sum over the momentum states.
+\(\vec S_d\) is the impurity spin operator with \(S_d^z = \pm 1/2\).
 

### 2021-12-08 notes/multi-channel-urg.tex
started writing the importance of zero mode Hamiltonian

@@
 	\label{zeromode_ham}
-	H_\text{zero mode} = J \vec{S_d}\cdot\vec{s}_\text{tot}
-\end{align}
-
-\section{Symmetries of the Hamiltonian}
+	H_\text{zero mode} = J \vec{S_d}\cdot\vec{s}_\text{tot}~.
+\end{align}
+This Hamiltonian is shown schematically in fig.~\ref{stargraph}.
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.3\textwidth]{./stargraph.pdf}
+	\caption{Zero mode of the \(K-\)channel Kondo model, represented as a "star graph".
+The central red node denotes the impurity spin \(\vec S_d\), while the outer nodes denote the spins \(\vec s_\gamma\) of the zeroth sites of the channels \(\gamma=1,2,\ldots,K\).
+The straight lines represent the spin-exchange interaction between the central node and the outer nodes mediated by the coupling \(J\).}
+	\label{stargraph}
+\end{figure}
+
+\section{Symmetries of the zero mode Hamiltonian}
 This zero mode Hamiltonian commutes with a number of operators, revealing various symmetries of the problem.
-The first such operators is \(s_\text{tot}^2\).
+The first of such operators is \(s_\text{tot}^2\).
 Henceforth we will drop the label \(\text{zero mode}\).
@@
 \begin{align}
-	S^2 = \left(\vec S_d + \vec s_\text{tot}\right)^2 = \frac{3}{4} + s_\text{tot}\left(s_\text{tot} + 1\right) + \frac{2}{J} H
+	S^2 = \left(\vec S_d + \vec s_\text{tot}\right)^2 = \frac{3}{4} + s^2_\text{tot} + \frac{2}{J} H
 \end{align}
@@
 \end{align}
+
+\section{Importance of the zero mode Hamiltonian}
+Methods like CFT, Bethe ansatz and NRG \cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991} have shown that neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the multi-channel Kondo models.
+Instead, the RG flows converge to an intermediate coupling fixed point.
+The RG flows were found to preserve the degeneracy of the ground state \cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}.
+For example, the two-channel and the three-channel Kondo models are found to be have ground state degeneracies of 2 and 3 respectively, throughout the RG flow.
+It was also revealed that the two and three-channel models enjoy a weak-strong duality: the model at strong coupling can also be thought of as a Kondo model but at weak coupling, possibly with a modified central complex.
+For example, in the two channel Kondo model, the model at strong coupling can be mapped onto the same model with a coupling parameter, but with the central Kondo spin-half impurity replaced by a new, composite spin-half object formed by the doubly-degenerate ground state of the strong coupling model \cite{kroha_kolf_2007}.
+The case of the three-channel model is different: there, the central impurity gets replaced by a new spin-1 impurity formed by the triply-degenerate ground state.
+In the former case, the strong and weak coupling models are formally identical and the model is self-dual.
+We will now show that these qualitative features can be captured very simply by the zero mode Hamiltonian.
 
@@
 For this, we will perform a perturbative treatment of the hopping at strong-coupling \(J \to \infty\) where the perturbative coupling \(t^2/J\) is arbitrarily small and again obtain Eq.~\ref{nfl_terms}.
-Such a change from the strong-coupling model with parameter \(J\) to a weak-coupling model with parameter \(t^2/J\) amounts to a duality transformation \cite{kroha_kolf_2007,zitko_fabrozio_2017}.
+Such a change from the strong-coupling model with parameter \(J\) to a weak-coupling model with parameter \(t^2/J\) amounts to a duality transformation \cite{kroha_kolf_2007,zitko_fabrizio_2017}.
 It can be shown that the duality transformation leads to an identical multi-channel Kondo model \cite{kroha_kolf_2007} (self-duality), which implies we can have identical RG flows, and our transformation simply extracts the NFL piece from the dual model.

### 2021-12-09 notes/multi-channel-urg.tex
added justification of zero mode

@@
 \section{Introduction of the Hamiltonian and its zero mode}
-The isotropic multi-channel Kondo model \cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact} is described by the Hamiltonian
+The isotropic multi-channel Kondo model~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact} is described by the Hamiltonian
 \begin{align}
@@
 \end{align}
-
-\section{Importance of the zero mode Hamiltonian}
-Methods like CFT, Bethe ansatz and NRG \cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991} have shown that neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the multi-channel Kondo models.
-Instead, the RG flows converge to an intermediate coupling fixed point.
-The RG flows were found to preserve the degeneracy of the ground state \cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}.
-For example, the two-channel and the three-channel Kondo models are found to be have ground state degeneracies of 2 and 3 respectively, throughout the RG flow.
-It was also revealed that the two and three-channel models enjoy a weak-strong duality: the model at strong coupling can also be thought of as a Kondo model but at weak coupling, possibly with a modified central complex.
-For example, in the two channel Kondo model, the model at strong coupling can be mapped onto the same model with a coupling parameter, but with the central Kondo spin-half impurity replaced by a new, composite spin-half object formed by the doubly-degenerate ground state of the strong coupling model \cite{kroha_kolf_2007}.
-The case of the three-channel model is different: there, the central impurity gets replaced by a new spin-1 impurity formed by the triply-degenerate ground state.
-In the former case, the strong and weak coupling models are formally identical and the model is self-dual.
-We will now show that these qualitative features can be captured very simply by the zero mode Hamiltonian.
 
@@
 \end{align}
-Note that the index \(m\) that we are using to label tje eigenvalues is actually related to a conserved quantity; the total spin operator along \(z\), \(S^z\).
+Note that the index \(m\) that we are using to label the eigenvalues is actually related to a conserved quantity; the total spin operator along \(z\), \(S^z\).
 That is, the eigenstates \(\ket{\Psi^M_{m,\pm}}\) have \(S^z = S_d^z + s_\text{tot}^z = m + \frac{1}{2}\).
+
+\section{Importance of the zero mode Hamiltonian}
+Methods like CFT, Bethe ansatz and NRG~\cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991} have shown that \textit{neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the multi-channel Kondo models}.
+Instead, the RG flows converge to an intermediate coupling fixed point.
+The RG flows \textit{preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}.
+For example, the two-channel and the three-channel Kondo models have ground state degeneracies of 2 and 3 respectively, throughout the RG flow.
+Analytic and numerical studies also showed that \textit{the two and three-channel models enjoy a weak-strong duality}~\cite{kroha_kolf_2007,zitko_fabrizio_2017}: the model at strong coupling, when projected onto the ground state basis, can also be thought of as a Kondo model at weak coupling, but possibly with a modified central spin.
+For example, in the two channel Kondo model, the model at strong coupling can be mapped onto the same model with a small coupling parameter, but with the central Kondo spin-half impurity replaced by a new, composite spin-half object formed by the doubly-degenerate ground state of the strong coupling model~\cite{kroha_kolf_2007}.
+The case of the three-channel model is different~\cite{zitko_fabrizio_2017} because there, the central impurity gets replaced by a new \textit{spin-1} impurity formed by the triply-degenerate ground state.
+In the former case, the strong and weak coupling models are formally identical and the model is self-dual.
+We will now show that these qualitative features can be captured very simply by the zero mode Hamiltonian.
+
+At weak coupling \(J \to 0^+\), the central spin is weakly coupled to the outer spins and can freely flip like a local moment.
+\textit{This makes it prone to screening because of the \(s^\pm\) terms in the zero mode Hamiltonian}.
+At strong coupling \(J \to \infty^-\), the outer spin-half objects tightly bind with the central spin-half object to form a single spin.
+The remaining states in the conduction bath channels form new zero modes and create a new outer ring of spins that interact with the new central spin, \textit{leading to another multi-channel Kondo problem with a new and small exchange coupling which is RG relevant, so the strong coupling fixed point \(J \to \infty^-\) is unstable}.
+This shows that it can be argued, even from the zero mode, that the two limits of the model cannot be stable fixed points, and the actual fixed point has to lie somewhere in between.
+
+The ground state of the \(K-\)channel zero mode is \(K-\)fold degenerate.
+Since the zero mode conserves the total magnetization operator \(S^z = S_d^z + s_\text{tot}^z\), the ground states are eigenstates of \(S^z\) with distinct eigenvalues \(\frac{K+1}{2}, \frac{K-1}{2},\ldots,\frac{-K-1}{2}\).
+\textit{This feature - the equality of energy eigenvalue for distinct values of \(S^z\) - persists for all values of \(J \in \left[0^+, \infty^-\right]\)}.
+This is because, the gap between the degenerate subspace and the next excited level is \(J\) or \(J/2\), depending on whether \(K\) is even or odd, and the gap is always non-zero as long as \(J\) lies in the regime of RG flow.
+In other words, as the exchange coupling grows(shrinks) from \(0^+\left(\infty^-\right)\) towards the fixed point value \(J^*\), the degeneracy remains protected at \(K\).
+
+The fact that the strong coupling fixed point can be seen as a new zero mode problem with a modifed central spin reveals the duality mentioned before.
+At strong coupling \(J \gg 1\), we can obtain a new zero mode Hamiltonian by defining a new spin-\(\left(\frac{K-1}{2}\right)\) object from the \(K-\)fold degenerate ground state manifold and letting this interact with the new outer spins formed by the remaining sites of the conduction channels.
+This new interaction is generated by the minimal hopping that exists between the zeroth site and the first sites of each of the conduction bath channels, and is characterised by the small coupling \(J^\prime \sim t^2/J\).
+\textit{The conclusion is that a large \(J\) model with a central spin-half object can be transformed into a small \(J^\prime\) model with a central spin-\(\left(\frac{K-1}{2}\right)\) object}.
+The former is RG irrelevant while the latter is relevant, both flowing towards the stable fixed point \(J = J^\prime = J^*\).
+For \(K=2\), the central spin for the \(J^\prime\)-problem is of size \(\frac{K-1}{2} = 1/2\), which is the same as the \(J\)-problem, so the models are self-dual, as mentioned previously.
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.43\textwidth]{./duality.pdf}
+	\caption{Duality of the RG flows as seen in the star graph Hamiltonian.
+The red circle and the thick arrows \(\Uparrow, \Downarrow\) denote the impurity, while the green circles and the normal arrows \(\uparrow,\downarrow\) denote the conduction bath spins.
+At large \(J\), the red circle binds with one of the green spins to form a singlet while the other green spin remains free to interact with the remaining spin of the conduction bath, denoted by the yellow circle.
+The fixed point consists of the red and green circles binding to form a doubly degenerate ground state that interacts with the yellow cirlces through the hopping.}
+	\label{fig:-duality-pdf}
+\end{figure}
 
@@
 \subsection{URG procedure}
-The URG method \cite{anirbanurg1,anirbanurg2,anirbanmott1,anirbanmott2,siddharthacpi,santanukagome} involves applying unitary transformations to decouple high energy degrees of freedom.
+The URG method~\cite{anirbanurg1,anirbanurg2,anirbanmott1,anirbanmott2,siddharthacpi,santanukagome} involves applying unitary transformations to decouple high energy degrees of freedom.
 The renormalization at step \(j\) is given by
@@
 This equation has a stable fixed point at \(J^* = \frac{8}{\rho K}\).
-The value of the fixed point agrees with the poor man's scaling calculation in \cite{tripathi2018landau}, but differs from the value of \(\frac{2}{\rho K}\) obtained in other references \cite{Kuramoto1998,Kogan_2018}.
+The value of the fixed point agrees with the poor man's scaling calculation in~\cite{tripathi2018landau}, but differs from the value of \(\frac{2}{\rho K}\) obtained in other references~\cite{Kuramoto1998,Kogan_2018}.
 
@@
 That this is true can also be argued from the single-channel Kondo model URG results.
-There, we saw that when the bandwidth is scaled to larger values, the strong-coupling fixed point was stable at successively larger values of \(J^*\).
+There, we saw that when the bandwidth is scaled to larger values, the strong coupling fixed point was stable at successively larger values of \(J^*\).
 Since the denominator fixed point is identical in structure in both problems, its reasonable that the same thing will happen here.
@@
 For small \(j_+\), we have \(j_+^2 < 2J_* |j_-|\)  and \(\Delta j_+ > 0\).
-This means that the isotropic fixed point is repulsive under anisotropy \cite{Noz_blandin_1980}.
+This means that the isotropic fixed point is repulsive under anisotropy~\cite{Noz_blandin_1980}.
 The coupling \(j_+\) being relevant means we have a single-channel Kondo problem.
@@
 \end{align}
-and it leads to the strong-coupling fixed point
+and it leads to the strong coupling fixed point
 
@@
 \ref{irrel_Jplus}), and \(J_-\) remains relevant.
-Since there is no numerator fixed point in the relevant coupling \(J_-\) and because all other couplings are irrelevant, the equation for \(J_-\) is replaced by the single-channel Kondo coupling URG equation, and the low-energy physics is then of strong-coupling..
+Since there is no numerator fixed point in the relevant coupling \(J_-\) and because all other couplings are irrelevant, the equation for \(J_-\) is replaced by the single-channel Kondo coupling URG equation, and the low-energy physics is then of strong coupling..
 \begin{figure}[htpb]
@@
 We wish to point out that such NFL terms were also obtained by Coleman, et al.~\cite{Coleman_tsvelik} in terms of Majorana fermions at the zeroth site and the first site.
-They then went on to compute a single-particle self-energy renormalization coming from this NFL term that matches the phenomenological \cite{varma2002singular} and microscopic forms of the marginal Fermi liquid self-energy \cite{anirbanmott1,anirbanurg1}.
-We take a different route in order to calculate the self-energy contribution coming from Eq.~\ref{nfl_terms}, one that involves \cite{anirbanmott1}.
-
-In \cite{anirbanurg1}, it was found that the normal phase of the Mott insulator was a marginal Fermi liquid in momentum space, defined by the interaction term 
+They then went on to compute a single-particle self-energy renormalization coming from this NFL term that matches the phenomenological~\cite{varma2002singular} and microscopic forms of the marginal Fermi liquid self-energy~\cite{anirbanmott1,anirbanurg1}.
+We take a different route in order to calculate the self-energy contribution coming from Eq.~\ref{nfl_terms}, one that involves~\cite{anirbanmott1}.
+
+In~\cite{anirbanurg1}, it was found that the normal phase of the Mott insulator was a marginal Fermi liquid in momentum space, defined by the interaction term 
 \begin{equation}\begin{aligned}
@@
 We wish to look for such a term in the effective Hamiltonian.
-For this, we will perform a perturbative treatment of the hopping at strong-coupling \(J \to \infty\) where the perturbative coupling \(t^2/J\) is arbitrarily small and again obtain Eq.~\ref{nfl_terms}.
-Such a change from the strong-coupling model with parameter \(J\) to a weak-coupling model with parameter \(t^2/J\) amounts to a duality transformation \cite{kroha_kolf_2007,zitko_fabrizio_2017}.
-It can be shown that the duality transformation leads to an identical multi-channel Kondo model \cite{kroha_kolf_2007} (self-duality), which implies we can have identical RG flows, and our transformation simply extracts the NFL piece from the dual model.
+For this, we will perform a perturbative treatment of the hopping at strong coupling \(J \to \infty\) where the perturbative coupling \(t^2/J\) is arbitrarily small and again obtain Eq.~\ref{nfl_terms}.
+Such a change from the strong coupling model with parameter \(J\) to a weak-coupling model with parameter \(t^2/J\) amounts to a duality transformation~\cite{kroha_kolf_2007,zitko_fabrizio_2017}.
+It can be shown that the duality transformation leads to an identical multi-channel Kondo model~\cite{kroha_kolf_2007} (self-duality), which implies we can have identical RG flows, and our transformation simply extracts the NFL piece from the dual model.
 The self-duality also implies that the critical intermediate-coupling fixed point is unique and can be reached from either of the models.
@@
 \end{aligned}\end{equation}
-This form of the Hamiltonian is very similar to the three-particle interaction term in Appendix B of \cite{anirbanmott1}.
-The channel indices in Eq.~\ref{k_space_od} can be mapped to the normal directions in \cite{anirbanmott1}.
+This form of the Hamiltonian is very similar to the three-particle interaction term in Appendix B of~\cite{anirbanmott1}.
+The channel indices in Eq.~\ref{k_space_od} can be mapped to the normal directions in~\cite{anirbanmott1}.
 As specualted eariler, the three-particle interaction in Eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
@@
 \end{aligned}\end{equation}
-Following \cite{anirbanmott1}, one can follow the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\text{rh}\) RG step, in the form of the URG equation
+Following~\cite{anirbanmott1}, one can follow the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\text{rh}\) RG step, in the form of the URG equation
 \begin{equation}\begin{aligned}
@@
 It is seen from the RG equation that \(R\) is relevant in the range of \(\bar\omega = \epsilon_j -\omega\) that has been used throughout \((\omega < \epsilon_j/2)\), \textcolor{red}{leading to a fixed-point at \(R_*/8 = \bar\omega - \epsilon_*/2)\)}.
-The relevance of \(R\) is expected because the strong-coupling \(J\) is irrelevant and \(R \sim 1/J\).
-
-The renormalization in \(R\) leads to a renormalization in the single-particle self-energy \cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalization is
+The relevance of \(R\) is expected because the strong coupling \(J\) is irrelevant and \(R \sim 1/J\).
+
+The renormalization in \(R\) leads to a renormalization in the single-particle self-energy~\cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalization is
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-leading to a \(k-\)space-averaged self-energy for each channel (eq. 33 of \cite{anirbanmott1})
+leading to a \(k-\)space-averaged self-energy for each channel (eq. 33 of~\cite{anirbanmott1})
 \begin{equation}\begin{aligned}
@@
 This can also be understood from the fact that the parent NFL term in eq.~\ref{nfl_terms} is also local.
-A local NFL term with a self-energy of the form in eq.~\ref{self_energy} was also obtained in the \(\sigma-\tau\) model by Coleman et al.
-\cite{Coleman_tsvelik}.
+A local NFL term with a self-energy of the form in eq.~\ref{self_energy} was also obtained in the \(\sigma-\tau\) model by Coleman et al.~\cite{Coleman_tsvelik}.
 The common features show the universality between the two-channel Kondo and the \(\sigma-\tau\) models.
@@
 \end{align}
-obtained from other methods like the Bethe ansatz (BA) and conformal field theory (CFT) calculations \cite{Gan_Andrei_Coleman_1993,andrei_destri_1984,Tsvelick_weigmann_mchannel_1985,sacramento1989,emery_kivelson,affleck_1991_overscreen}.
+obtained from other methods like the Bethe ansatz (BA) and conformal field theory (CFT) calculations~\cite{Gan_Andrei_Coleman_1993,andrei_destri_1984,Tsvelick_weigmann_mchannel_1985,sacramento1989,emery_kivelson,affleck_1991_overscreen}.
 The difference is not only in the value but also in the origin.
 Eq.~\ref{res_entropy} describes the thermal entropy coming purely from the quantum mechanical degeneracy of the star graph problem (which is the zero mode of the full multi-channel Kondo problem), while the result Eq.~\ref{cft_entropy} presumably arises from the lowest-lying excitations on top of the zero mode arising from the conduction bath \(k-\)states.
-Another difference lies in the fact that while Eq.~\ref{res_entropy} holds true independent of system size, Eq.~\ref{cft_entropy} is correct only in the thermodynamic limit and only if the limit of system size \(L \to \infty\) is taken prior to taking the limit of temperature \(T \to 0\) \cite{Gan_Andrei_Coleman_1993,rozhkov_1998,vondelft_prl_1998}.
+Another difference lies in the fact that while Eq.~\ref{res_entropy} holds true independent of system size, Eq.~\ref{cft_entropy} is correct only in the thermodynamic limit and only if the limit of system size \(L \to \infty\) is taken prior to taking the limit of temperature \(T \to 0\)~\cite{Gan_Andrei_Coleman_1993,rozhkov_1998,vondelft_prl_1998}.
 We note however that the entropy coming from the degeneracy is larger than that coming from the excitations (fig.~\ref{entropy_comparison}), and consequently plays a very important role in the physics of the multi-channel Kondo problem, being responsible for the NFL physics and the critical behaviour near the fixed point.
@@
 \end{align}
-For \(\omega < D/2\), we get the flow towards the strong-coupling fixed point.
+For \(\omega < D/2\), we get the flow towards the strong coupling fixed point.
 That is, there appears a stable fixed point at \(J^* = 4|\omega - D/2|\) for all bare \(J > 0\).

### 2021-12-09 notes/multi-channel-urg.tex
incorporated sir's suggestions into zero mode argument part

@@
 \end{align}
-In the terms of the local spin operators \(\vec s_\gamma = (s_\gamma^x,s_\gamma^y,s_\gamma^z)\), we can define the total spin of the zero mode of the bath: \(\vec s_\text{tot} = \sum_\gamma \vec s_\gamma\) and the zero mode Hamiltonian then takes the simpler form
+In the terms of the local spin operators \(\vec s_\gamma = (s_\gamma^x,s_\gamma^y,s_\gamma^z)\), we can define the total spin of the zero mode of the bath: \(\vec s_\text{tot} = \sum_\gamma \vec s_\gamma\) and the zero mode Hamiltonian then takes the simpler form of a star graph Hamiltonian:
 \begin{align}
@@
 \end{align}
-This Hamiltonian is shown schematically in fig.~\ref{stargraph}.
+This star graph is shown schematically in fig.~\ref{stargraph}.
 
@@
 
-\section{Symmetries of the zero mode Hamiltonian}
-This zero mode Hamiltonian commutes with a number of operators, revealing various symmetries of the problem.
+\section{Symmetries of the star graph}
+This star graph commutes with a number of operators, revealing various symmetries of the problem.
 The first of such operators is \(s_\text{tot}^2\).
@@
 \section{Eigenvalues and eigenstates}
-The zero mode Hamiltonian can be diagonalized.
+The star graph can be diagonalized.
 Since the Hamiltonian commutes with \(s_\text{tot}^2\), it is already block-diagonal in the quantum number \(s_\text{tot}\).
@@
 
-\section{Importance of the zero mode Hamiltonian}
-Methods like CFT, Bethe ansatz and NRG~\cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991} have shown that \textit{neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the multi-channel Kondo models}.
+\section{Importance of the star graph}
+Methods like CFT, Bethe ansatz, bosonization and NRG~\cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991,emery_kivelson,vondelft_prl_1998} have shown that \textit{neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the multi-channel Kondo models}.
 Instead, the RG flows converge to an intermediate coupling fixed point.
-The RG flows \textit{preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}.
+The RG flows \textit{preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}, because the Hamiltonian commutes with the total magnetization operator \(S^z = S_d^z + s_\text{tot}^z\)~\cite{vondelft_prl_1998}.
 For example, the two-channel and the three-channel Kondo models have ground state degeneracies of 2 and 3 respectively, throughout the RG flow.
@@
 For example, in the two channel Kondo model, the model at strong coupling can be mapped onto the same model with a small coupling parameter, but with the central Kondo spin-half impurity replaced by a new, composite spin-half object formed by the doubly-degenerate ground state of the strong coupling model~\cite{kroha_kolf_2007}.
+The strong and weak coupling models are formally identical and the model is self-dual.
 The case of the three-channel model is different~\cite{zitko_fabrizio_2017} because there, the central impurity gets replaced by a new \textit{spin-1} impurity formed by the triply-degenerate ground state.
-In the former case, the strong and weak coupling models are formally identical and the model is self-dual.
-We will now show that these qualitative features can be captured very simply by the zero mode Hamiltonian.
+Compared to the self-duality of the two-channel model, this case corresponds to a cross duality between a spin-1/2 and a spin-1 model.
+We will now show that these qualitative features can be captured very simply by the star graph.
 
 At weak coupling \(J \to 0^+\), the central spin is weakly coupled to the outer spins and can freely flip like a local moment.
-\textit{This makes it prone to screening because of the \(s^\pm\) terms in the zero mode Hamiltonian}.
+\textit{This makes it prone to screening because of the \(s^\pm\) terms in the star graph}.
 At strong coupling \(J \to \infty^-\), the outer spin-half objects tightly bind with the central spin-half object to form a single spin.
@@
 
-The ground state of the \(K-\)channel zero mode is \(K-\)fold degenerate.
-Since the zero mode conserves the total magnetization operator \(S^z = S_d^z + s_\text{tot}^z\), the ground states are eigenstates of \(S^z\) with distinct eigenvalues \(\frac{K+1}{2}, \frac{K-1}{2},\ldots,\frac{-K-1}{2}\).
+Just like the full Hamiltonian, the star graph conserves the total spin \(S^z\), and this leads to a \(K-\)fold degeneracy in the ground state of the \(K-\)channel zero mode.
+Since \(S^z\) commutes with the star graph, the ground states are eigenstates of \(S^z\) with distinct eigenvalues \(\frac{K+1}{2}, \frac{K-1}{2},\ldots,\frac{-K-1}{2}\).
 \textit{This feature - the equality of energy eigenvalue for distinct values of \(S^z\) - persists for all values of \(J \in \left[0^+, \infty^-\right]\)}.
@@
 The fact that the strong coupling fixed point can be seen as a new zero mode problem with a modifed central spin reveals the duality mentioned before.
-At strong coupling \(J \gg 1\), we can obtain a new zero mode Hamiltonian by defining a new spin-\(\left(\frac{K-1}{2}\right)\) object from the \(K-\)fold degenerate ground state manifold and letting this interact with the new outer spins formed by the remaining sites of the conduction channels.
-This new interaction is generated by the minimal hopping that exists between the zeroth site and the first sites of each of the conduction bath channels, and is characterised by the small coupling \(J^\prime \sim t^2/J\).
+At strong coupling \(J \gg 1\), we can obtain a new star graph by defining a new spin-\(\left(\frac{K-1}{2}\right)\) object from the \(K-\)fold degenerate ground state manifold and letting this interact with the new outer spins formed by the remaining sites of the conduction channels.
+This new interaction is generated by the minimal hopping that exists between the zeroth site and the first sites of each of the conduction bath channels, and is characterised by the small superexchange coupling \(J^\prime \sim t^2/J\).
 \textit{The conclusion is that a large \(J\) model with a central spin-half object can be transformed into a small \(J^\prime\) model with a central spin-\(\left(\frac{K-1}{2}\right)\) object}.
+This is shown schematically in Fig.~\ref{duality_fig}.
 The former is RG irrelevant while the latter is relevant, both flowing towards the stable fixed point \(J = J^\prime = J^*\).
@@
 	\centering
-	\includegraphics[width=0.43\textwidth]{./duality.pdf}
+	\includegraphics[width=0.45\textwidth]{./duality.pdf}
 	\caption{Duality of the RG flows as seen in the star graph Hamiltonian.
-The red circle and the thick arrows \(\Uparrow, \Downarrow\) denote the impurity, while the green circles and the normal arrows \(\uparrow,\downarrow\) denote the conduction bath spins.
-At large \(J\), the red circle binds with one of the green spins to form a singlet while the other green spin remains free to interact with the remaining spin of the conduction bath, denoted by the yellow circle.
-The fixed point consists of the red and green circles binding to form a doubly degenerate ground state that interacts with the yellow cirlces through the hopping.}
-	\label{fig:-duality-pdf}
+The red and green circles represent the impurity and zeroth site spins respectively.
+At large \(J\), the red circle binds with the green circles to form an effective spin \(\frac{K-1}{2}\) object (yellow) that interacts with the remaining spin of the conduction bath (blue circles).
+The fixed point consists of the red (purple) and green (yellow) circles binding to form a doubly degenerate ground state (orange) that interacts with the zero mode of the remaining sites (brown) through the hopping.}
+	\label{duality_fig}
 \end{figure}

### 2021-12-10 notes/multi-channel-urg.tex
started writing spin-S impurity Kondo URG

@@
-\documentclass{revtex4-2}
+\documentclass[12pt]{revtex4-2}
 \usepackage{braket,amsmath,amssymb,graphicx,float,paralist,color}
@@
 
-\section{Eigenvalues and eigenstates}
+\section{Eigenvalues and eigenstates of the star graph}
 The star graph can be diagonalized.
@@
 
-\section{Importance of the star graph}
+\section{Importance of the star graph in determining the physics of the problem}
 Methods like CFT, Bethe ansatz, bosonization and NRG~\cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991,emery_kivelson,vondelft_prl_1998} have shown that \textit{neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the multi-channel Kondo models}.
@@
 \appendix
-\section{URG analysis of the single-channel Kondo model}
+\section{URG equations for the single-channel Kondo model}
 The single-channel SU(2) Kondo model consists of a spin-half impurity interacting with a band of itinerant conduction electrons through a spin-exchange coupling:
+\begin{align}
 \label{1KondoURG}
-\begin{align}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{k,l} J^z S_d^z s^z_{kl} + \frac{1}{2}\sum_{k,l} J^t \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right)
+	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{kl} J^z S_d^z s^z_{kl} + \frac{1}{2}\sum_{kl} J^t \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right)
 \end{align}
@@
 
+\section{URG equations for the single-channel Kondo model with spin-\(S\) impurity}
+The Hamiltonian is the same as eq.~\ref{1KondoURG}, but the impurity is now a spin-\(S\) object, such that \(S_d^z \in \left[-S, -S+1,\ldots,S-1,S\right] \).
+We will also choose different couplings \(J_m\) for each of the eigenvalues of \(S_d^z\):
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{k}\sum_{m=-S}^S J^z_m S_d^z s^z_{k}\ket{m}\bra{m} + \frac{1}{2}\sum_{k}\sum_{m=-S}^S J^t_m \left(S_d^+ s^-_{k} \ket{m}\bra{m} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+The states \(\ket{m}\) act purely on the Hilbert space of the impurity spin and are defined as \(S_d^z\ket{m} = m\ket{m}\). We will use the relations:
+\begin{equation}\begin{aligned}
+	S_d^\pm S_d^z &= S_d^z S_d^\pm \mp S_d^\pm\\
+	S_d^z S_d^\pm &= S_d^\pm S_d^z \pm S_d^\pm\\
+	S_d^\pm S_d^\mp &= \vec S_d^2 - {S_d^z}^2 \pm S_d^z
+\end{aligned}\end{equation}
+The various terms that renormalize the Hamiltonian can be described in terms of the impurity spin operators that come into them.
+For example, the term that has \(S_d^z\) on both sides of the intervening Greens function can be represented as \(z-z\).
+There are 7 such terms: \(z|z, \pm|\mp, z|\pm, \pm|z\).
+Each of these terms occur both in the particle and the hole sectors.
+\subsection{Particle sector}
+We will now calculate each of these terms for the particle sector. The particle sector consists of those processes that start from an occupied state \(\hat n_{q\beta} = 1\).
+\paragraph{\(z|z: \beta=\uparrow\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m}\frac{1}{4}{J^z_m}^2 c^\dagger_{q \uparrow} c_{k^\prime \uparrow} S_d^z \ket{m}\bra{m} \frac{1}{\omega_{m, \uparrow} - D/2 + \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^z c^\dagger_{k \uparrow}c_{q \uparrow} = -\frac{1}{4}n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^z_m}^2{S_d^z}^2 c^\dagger_{k \uparrow}c_{k^\prime\uparrow} \ket{m}\bra{m}}{\omega_{m, \uparrow} - D/2 + \frac{Jm}{2}}
+\end{aligned}\end{equation}
+
+\paragraph{\(z|z: \beta=\downarrow\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m}\frac{1}{4}{J^z_m}^2 c^\dagger_{q \downarrow} c_{k^\prime \downarrow} S_d^z \ket{m}\bra{m} \frac{1}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^z c^\dagger_{k \downarrow}c_{q \downarrow} = -\frac{1}{4}n_{q \downarrow}\sum_{kk^\prime,m}\frac{{J^z_m}^2{S_d^z}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m, \downarrow} - D/2 - \frac{Jm}{2}}
+\end{aligned}\end{equation}
+
+\paragraph{\(+|-\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m}\frac{1}{4}{J^t_m}^2 c^\dagger_{q \downarrow} c_{k^\prime \uparrow} S_d^+ \ket{m}\bra{m} \frac{1}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^- c^\dagger_{k \uparrow}c_{q \downarrow} = -\frac{1}{4}n_{q \downarrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2S_d^+ \ket{m}\bra{m} S_d^- c^\dagger_{k \uparrow}c_{k^\prime\uparrow} }{\omega_{m, \downarrow} - D/2 - \frac{Jm}{2}}
+\end{aligned}\end{equation}
+
+\paragraph{\(-|+\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m}\frac{1}{4}{J^t_m}^2 c^\dagger_{q \uparrow} c_{k^\prime \downarrow} S_d^- \ket{m}\bra{m} \frac{1}{\omega_{m, \uparrow} - D/2 + \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^+ c^\dagger_{k \downarrow}c_{q \uparrow} = -\frac{1}{4}n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2S_d^- \ket{m}\bra{m} S_d^+ c^\dagger_{k \downarrow}c_{k^\prime\downarrow} }{\omega_{m, \uparrow} - D/2 + \frac{Jm}{2}}
+\end{aligned}\end{equation}
+
+\paragraph{\(z|+\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m}\frac{1}{4}{J^z_m} J^t_m c^\dagger_{q \uparrow} c_{k^\prime \uparrow} S_d^z \ket{m}\bra{m} \frac{1}{\omega_{m, \uparrow} - D/2 + \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^+ c^\dagger_{k \downarrow}c_{q \uparrow} = -\frac{1}{4}n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^z_m} J^t_m \ket{m}\bra{m} S_d^z S_d^+ c^\dagger_{k \downarrow}c_{k^\prime\uparrow}}{\omega_{m, \uparrow} - D/2 + \frac{Jm}{2}}
+\end{aligned}\end{equation}
+
+\paragraph{\(-|z\)}
+This is equal to the h.c. of the renormalization coming from \(z|+\), because \(-|z = \left(z|+\right)^\dagger \).
+
+\paragraph{\(z|-\)}
+\begin{equation}\begin{aligned}
+	-\sum_{kk^\prime,m}\frac{1}{4}{J^t_m} J^z_m c^\dagger_{q \downarrow} c_{k^\prime \downarrow} S_d^z \ket{m}\bra{m} \frac{1}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}S_d^z} \ket{m}\bra{m} S_d^- c^\dagger_{k \uparrow}c_{q \downarrow} = \frac{1}{4}n_{q \downarrow}\sum_{kk^\prime,m}\frac{{J^t_m} J^z_m \ket{m}\bra{m} S_d^z S_d^- c^\dagger_{k \uparrow}c_{k^\prime\downarrow}}{\omega_{m, \downarrow} - D/2 - \frac{Jm}{2}}
+\end{aligned}\end{equation}
+
+\paragraph{\(+|z\)}
+This is equal to the h.c. of the renormalization coming from \(z|-\), because \(+|z = \left(z|-\right)^\dagger \).
+
+The first four terms generate and renormalize a new three-particle term in the Hamiltonian, of the form \(J^{zz}{S_d^z}^2\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma}\).
+The third and fourth terms also renormalize the \(J^z_m\) coupling.
+The terms e through h renormalize \(J^t_m\).
+To compare with the spin-\(\frac{1}{2}\) Kondo URG, we redefine the \(\omega_{m\sigma} \to \omega + \frac{J}{2}\left(-\sigma m + \frac{1}{2}\right) \).
+We also use \(\sum_\sigma \hat n_{q\sigma}= n(D)\).
+The total renormalization from the first four terms is
+\begin{equation}\begin{aligned}
+	-\frac{1}{4}\sum_{kk^\prime\sigma}\frac{n(D)\left({J^z}^2 - {J^t}^2\right) {S_d^z}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma}}{\omega - D/2 + \frac{J}{4}} - \frac{1}{2}\sum_{kk^\prime}\frac{n(D){J_m^t}^2 {S_d^z} s^z_{kk^\prime}}{\omega - D/2 + \frac{J}{4}}
+\end{aligned}\end{equation}
+The renormalization from the last four terms is
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\sum_{kk^\prime, m}\frac{n(D)J^z_m J^t_m \left(S_d^+ s^-_{kk^\prime} + \text{h.c.}\right) m\ket{m}\bra{m}}{\omega - D/2 + \frac{J}{4}}
+\end{aligned}\end{equation}
+
 \bibliographystyle{apsrev4-1}

### 2021-12-11 notes/multi-channel-urg.tex
single-channel spin-S impurity complete!

--- 2021-12-09 notes/multi-channel-urg.tex
@@
 
+\section{URG equations for the single-channel Kondo model with spin-\(S\) impurity}
+The Hamiltonian is the same as eq.~\ref{1KondoURG}, but the impurity is now a spin-\(S\) object, such that \(S_d^z \in \left[-S, -S+1,\ldots,S-1,S\right] \).
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{kl} J S_d^z s^z_{kl} + \frac{1}{2}\sum_{kl} J \left(S_d^+ s^-_{kl}  + \text{h.c.}\right)
+\end{aligned}\end{equation}
+It is easier to see the RG flow of the couplings if we write the Hamiltonian in terms of the eigenstates of \(S_d^z\).
+These eigenstates are defined by \(S_d^z\ket{m} = m\ket{m}, m \in \left[-S, S\right]\).
+In terms of these eigenstates, the Hamiltonian becomes
+\begin{equation}\begin{aligned}
+	\mathcal{H} &= \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{kl} J S_d^z\sum_m \ket{m}\bra{m} s^z_{kl} + \frac{1}{2}\sum_{kl} J \left(S_d^+ s^-_{kl}  + \text{h.c.}\right)\sum_m \ket{m}\bra{m} \\
+		    &= \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{m=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_m \ket{m}\bra{m} c^\dagger_{k \sigma}c_{l \sigma} + \sum_{kl} \sum_{m=-S}^{S-1} J^t_{m} \left(\ket{m+1}\bra{m} s^-_{kl}  + \text{h.c.}\right)
+\end{aligned}\end{equation}
+where \(J^\sigma_m = \frac{1}{2} \sigma m J\) in the UV Hamiltonian, and \(J^t_{m} = J\frac{1}{2}\sqrt{S(S+1) - m(m+1)}\) is the coupling that connects \(\ket{m}\) and \(\ket{m+1}\).
+
+% We will use the relations:
+% \begin{equation}\begin{aligned}
+% 	S_d^\pm S_d^z &= S_d^z S_d^\pm \mp S_d^\pm\\
+% 	S_d^z S_d^\pm &= S_d^\pm S_d^z \pm S_d^\pm\\
+% 	S_d^\pm S_d^\mp &= \vec S_d^2 - {S_d^z}^2 \pm S_d^z
+% \end{aligned}\end{equation}
+The various terms that renormalize the Hamiltonian can be described in terms of the bath spin operators that come into them.
+For example, the term that has \(s^z\) on both sides of the intervening Greens function can be represented as \(z|z\).
+There are 7 such terms: \(z|z, \pm|\mp, z|\pm, \pm|z\).
+Each of these terms occur both in the particle and the hole sectors.
+
+\subsection{Particle sector}
+We will now calculate each of these terms for the particle sector. The particle sector consists of those processes that start from an occupied state \(\left(\hat n_{q\beta} = 1\right)\).
+\paragraph{\(z|z\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m,\sigma} c^\dagger_{q \sigma} c_{k^\prime \sigma} \ket{m}\bra{m}\frac{{J^\sigma_m}^2}{\omega - D/2 + \frac{J}{2}\sigma S_d^z}\ket{m}\bra{m} c^\dagger_{k \sigma}c_{q \sigma} = -\sum_{kk^\prime,m,\sigma}n_{q \sigma}\frac{{J^\sigma_m}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma} \ket{m}\bra{m}}{\omega_{m, \sigma} - D/2 + \frac{J}{2}\sigma m}
+\end{aligned}\end{equation}
+
+\paragraph{\(+|-\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}^2}{\omega - D/2 + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m+1, \uparrow} - D/2 + \frac{J}{2}\left( m+1 \right) }
+\end{aligned}\end{equation}
+
+\paragraph{\(-|+\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m}\frac{{J^t_m}^2}{\omega - D/2 - \frac{J}{2}S_d^z}\ket{m}\bra{m+1} c^\dagger_{k \uparrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \uparrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m+1}}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}m}
+\end{aligned}\end{equation}
+
+\paragraph{\(z|+\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \downarrow} \ket{m}\bra{m}\frac{J^\downarrow_m{J^t_m}}{\omega - D/2 - \frac{J}{2}S_d^z}\ket{m}\bra{m+1} c^\dagger_{k \uparrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{J^\downarrow_m J^t_m c^\dagger_{k \uparrow}c_{k^\prime\downarrow} \ket{m}\bra{m+1}}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}m}
+\end{aligned}\end{equation}
+
+\paragraph{\(+|z\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m} c^\dagger_{q \uparrow}c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}J^\uparrow_{m+1}}{\omega - D/2 + \frac{J}{2}S_d^z} \ket{m+1}\bra{m+1} c^\dagger_{k \uparrow} c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{J^\uparrow_{m+1} J^t_m c^\dagger_{k \uparrow}c_{k^\prime\downarrow} \ket{m}\bra{m+1}}{\omega_{m+1, \downarrow} - D/2 + \frac{J}{2}\left(m+1\right) }
+\end{aligned}\end{equation}
+
+\paragraph{\(z|-\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m+1}\frac{J^\uparrow_{m+1}{J^t_m}}{\omega - D/2 + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{J^\uparrow_{m+1} J^t_m c^\dagger_{k \downarrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m}}{\omega_{m+1, \uparrow} - D/2 + \frac{J}{2}(m+1)}
+\end{aligned}\end{equation}
+
+\paragraph{\(-|z\)}
+\begin{equation}\begin{aligned}
+	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m}\frac{J^\downarrow_{m}{J^t_m}}{\omega - D/2 - \frac{J}{2}S_d^z}\ket{m}\bra{m} c^\dagger_{k \downarrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{J^\downarrow_{m} J^t_m c^\dagger_{k \downarrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m}}{\omega_{m, \uparrow} - D/2 - \frac{J}{2}(m)}
+\end{aligned}\end{equation}
+The first four terms renormalize \(J^\sigma_m\):
+\begin{equation}\begin{aligned}
+	\Delta J^\sigma_{m} = -\frac{\left( J^\sigma_m \right) ^2 + \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - D/2 + J/4}
+\end{aligned}\end{equation}
+Here, we have defined \(J^t_m = 0\) for \( |m| > S\).
+Two relations can be obtained from this RG equation, the RG equations for the sum and difference of the couplings.
+These sum and difference are defined by rewriting the Ising part of the Hamiltonian in the following fashion:
+\begin{equation}\begin{aligned}
+	\sum_{m=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_m \ket{m}\bra{m} c^\dagger_{k \sigma}c_{l \sigma} = \sum_{m=-S}^S \sum_{\sigma=\uparrow,\downarrow} J^+_m \ket{m}\bra{m} \sum_\sigma \hat n_{0\sigma}  + \sum_{m=-S}^S J^-_m \ket{m}\bra{m} 2s^z_0
+\end{aligned}\end{equation}
+where \(2J^\pm_m = J^\uparrow_m \pm J^\downarrow_m\).
+The RG equation for the sum of the couplings is
+\begin{equation}\begin{aligned}
+	\Delta J^+_m = -\frac{1}{2}\frac{\sum_\sigma \left( J^\sigma_m \right) ^2 + \sum_\sigma \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - D/2 + J/4} = -\frac{J^2}{4}\frac{S(S+1)}{\omega - D/2 + J/4}
+\end{aligned}\end{equation}
+This is an \(m-\)independent piece, so it can be summed over to produce an impurity-independent potential scattering term:
+\begin{equation}\begin{aligned}
+	\sum_{m=-S}^S \sum_{\sigma=\uparrow,\downarrow} J^+ \ket{m}\bra{m} \sum_\sigma \hat n_{0\sigma} = J^+ \mathbb{I}\sum_\sigma \hat n_{0\sigma}
+\end{aligned}\end{equation}
+Since this term does not have any Kondo physics, we drop this piece and say that \(\Delta J^+ = 0\) and so \(\Delta J^\uparrow_m = - \Delta J^\downarrow_m \implies J^\uparrow_m = -J^\downarrow_m\) throughout the RG flow.
+
+The second is the RG equation for the difference of the couplings:
+\begin{equation}\begin{aligned}
+	\Delta J^-_m = -\frac{1}{2}\frac{\left( J^t_{m-1} \right) ^2 - \left(J^t_{m}\right) ^2}{\omega - D/2 + J/4} = -\frac{1}{4}\frac{m J^2}{\omega - D/2 + J/4}
+\end{aligned}\end{equation}
+The usual \(J^z\) Kondo coupling is defined as \(J^z = 2J^-_m/m\). Substituting this gives 
+\begin{equation}\begin{aligned}
+	\Delta J^z = -\frac{1}{2}\frac{J^2}{\omega - D/2 + J/4}
+\end{aligned}\end{equation}
+
+The last four terms renormalize \(J^t_m\):
+\begin{equation}\begin{aligned}
+	\Delta J^t_m = - \frac{J^t_m \left( J^\downarrow_m + J^\uparrow_{m+1} \right) }{\omega - D/2 + J/4} = -\frac{1}{2}\frac{J^t_m J}{\omega - D/2 + J/4} \implies J^t = -\frac{1}{2}\frac{J^2}{\omega - D/2 + J/4}
+\end{aligned}\end{equation}
+\(J^t\) is the transverse coupling. Since we started from an isotropic model \(\left( J^z = J^t= J \right) \), we obtain \(\Delta J^z = \Delta J^t\).
+
+\subsection{Hole sector}
+The RG equation in this sector is identical to that in the hole sector, because the renormalization terms are Hermitian conjugate to this in the particle sector.
+
 \bibliographystyle{apsrev4-1}

### 2021-12-13 notes/multi-channel-urg.tex
obtained all processes for the spin-S multichannel RG

@@
-\documentclass[12pt]{revtex4-2}
+\documentclass{revtex4-2}
 \usepackage{braket,amsmath,amssymb,graphicx,float,paralist,color}
@@
 
+\section{Derivation of URG equations for the multi-channel spin-\(S\) impurity Kondo model}
+The leading order renormalization is the same as the single-channel model, and is shown in the appendix. Following that calculation, the Hamiltonian we will work with is 
+\begin{equation}\begin{aligned}
+		    H = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{m=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_m \ket{m}\bra{m} c^\dagger_{k \sigma}c_{l \sigma} + \sum_{kl} \sum_{m=-S}^{S-1} J^t_{m} \left(\ket{m+1}\bra{m} s^-_{kl}  + \text{h.c.}\right)
+\end{aligned}\end{equation}
+where \(\left\{\ket{m}\right\} \) are the eigenstates of \(S_d^z\), \(J^\sigma_m = \frac{1}{2} \sigma m J\) in the UV Hamiltonian, and \(J^t_{m} = J\frac{1}{2}\sqrt{S(S+1) - m(m+1)}\) is the coupling that connects \(\ket{m}\) and \(\ket{m+1}\).
+
+The next order renormalization is of the form
+\begin{equation}\begin{aligned}
+	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term (particle sector)} ~+~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term (hole sector)}
+\end{aligned}\end{equation}
+
+Before we start, we will make another simplification. A general term of \(\Delta H\) will be of the form
+\begin{equation}\begin{aligned}
+	\sum_{q,k,l_1} c^\dagger_{q\beta, l_1}c_{k \alpha, l_1}\ket{m_1}\bra{m_2} \frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z} \ket{m_2} c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \bra{m_3}\frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z}\ket{m_3}\bra{m_4}c^\dagger_{k\alpha, l_1}c_{q\beta, l_1}
+\end{aligned}\end{equation}
+We have not bothered to write all the summations and the couplings correctly, because we will only simplify the denominator here. Evaluating the inner products gives
+\begin{equation}\begin{aligned}
+	\ket{m_1}\bra{m_4}\sum_k c^\dagger_{q\beta}c_{k \alpha} \frac{1}{\omega_{m_2,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_2}{4}}  c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \frac{1}{\omega_{m_3,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_3}{4}}c^\dagger_{k\alpha}c_{q\beta}
+\end{aligned}\end{equation}
+To compare with the spin-\(\frac{1}{2}\) RG equations, we will transform the general spin-\(S\) \(\omega\) to the spin-\(\frac{1}{2}\) \( \omega\), using \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).
+\begin{equation}\begin{aligned}
+	\hat n_{q\beta}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}\sum_k \left( 1 - \hat n_{k\alpha} \right) \left(\frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}}\right)^2
+\end{aligned}\end{equation}
+We can set \(\sum_q \hat n_{q\beta} = n(D)\). Performing the sums over \(k\) and \(l_1\) in the same fashion as previously gives
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}
+\end{aligned}\end{equation}
+Reinstating the complete summation and the couplings gives
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4}\sum_{k_1,k_2,l_2,\sigma_1\sigma_2}\lambda_{1}\lambda_{2}\lambda_{3}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}
+\end{aligned}\end{equation}
+There is no sum over \(m_2\) and \(m_3\) because they are constrained by \(m_1\) and \(m_4\) respectively. \(\lambda_i\) represent the couplings present at the three interaction vertices.
+
+The various terms in each sector can be represented as \(a|b|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three stages.
+We will only calculate the terms in the particle sector, the ones in hole sector will be equal to these because of particle-hole symmetry.
+\paragraph{\(z|z|z\)}
+\begin{equation}\begin{aligned}
+	- \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_\beta \sum_{m}\sum_{k_1,k_2,l_2,\sigma} \left(J^\beta_m\right)^2 J^\sigma_m \ket{m}\bra{m}c^\dagger_{k_1 \sigma, l_2}c_{k_2 \sigma,l_2}
+\end{aligned}\end{equation}
+
+\paragraph{\(-|z|+\)}
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2,\sigma} \left( J^t_m \right) ^2 J^\sigma_m \ket{m+1}\bra{m+1}c^\dagger_{k_1 \sigma, l_2}c_{k_2 \sigma,l_2}
+\end{aligned}\end{equation}
+\paragraph{\(+|z|-\)}
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2,\sigma} \left( J^t_m \right) ^2 J^\sigma_{m+1} \ket{m}\bra{m}c^\dagger_{k_1 \sigma, l_2}c_{k_2 \sigma,l_2}
+\end{aligned}\end{equation}
+\paragraph{\(+|+|-\)}
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} J^t_m \left( J^t_{m+1} \right)^2 \ket{m}\bra{m+1}c^\dagger_{k_1 \uparrow, l_2}c_{k_2 \downarrow,l_2}
+\end{aligned}\end{equation}
+\paragraph{\(+|-|-\)}
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} J^t_m \left( J^t_{m+1} \right)^2 \ket{m+1}\bra{m}c^\dagger_{k_1 \downarrow, l_2}c_{k_2 \uparrow,l_2}
+\end{aligned}\end{equation}
+\paragraph{\(-|-|+\)}
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} \left( J^t_{m} \right)^2 J^t_{m+1}\ket{m+2}\bra{m+1}c^\dagger_{k_1 \downarrow, l_2}c_{k_2 \uparrow,l_2}
+\end{aligned}\end{equation}
+\paragraph{\(-|+|+\)}
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} \left( J^t_{m} \right)^2 J^t_{m+1}\ket{m+1}\bra{m+2}c^\dagger_{k_1 \uparrow, l_2}c_{k_2 \downarrow,l_2}
+\end{aligned}\end{equation}
+
 \section{MFL and orthogonality catastrophe in low-energy excitations of 2-CKM}
@@
 
-% We will use the relations:
-% \begin{equation}\begin{aligned}
-% 	S_d^\pm S_d^z &= S_d^z S_d^\pm \mp S_d^\pm\\
-% 	S_d^z S_d^\pm &= S_d^\pm S_d^z \pm S_d^\pm\\
-% 	S_d^\pm S_d^\mp &= \vec S_d^2 - {S_d^z}^2 \pm S_d^z
-% \end{aligned}\end{equation}
 The various terms that renormalize the Hamiltonian can be described in terms of the bath spin operators that come into them.
@@
 \begin{equation}\begin{aligned}
-	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m}\frac{J^\downarrow_{m}{J^t_m}}{\omega - D/2 - \frac{J}{2}S_d^z}\ket{m}\bra{m} c^\dagger_{k \downarrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{J^\downarrow_{m} J^t_m c^\dagger_{k \downarrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m}}{\omega_{m, \uparrow} - D/2 - \frac{J}{2}(m)}
-\end{aligned}\end{equation}
+	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m}\frac{J^\downarrow_{m}{J^t_m}}{\omega - D/2 - \frac{J}{2}S_d^z}\ket{m}\bra{m} c^\dagger_{k \downarrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{J^\downarrow_{m} J^t_m c^\dagger_{k \downarrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m}}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}(m)}
+\end{aligned}\end{equation}
+To compare with the spin-\(\frac{1}{2}\) RG equations, we will transform the general spin-\(S\) \(\omega\) to the spin-\(\frac{1}{2}\) \( \omega\), using \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).
 The first four terms renormalize \(J^\sigma_m\):

### 2021-12-13 notes/multi-channel-urg.tex
redid the URG calculation for the spin-1/2 impurity by taking the extra process at third order, this gives back the correct 2/K rho form

@@
 The case of the three-channel model is different~\cite{zitko_fabrizio_2017} because there, the central impurity gets replaced by a new \textit{spin-1} impurity formed by the triply-degenerate ground state.
-Compared to the self-duality of the two-channel model, this case corresponds to a cross duality between a spin-1/2 and a spin-1 model.
+Compared to the self-duality of the two-channel model, this case corresponds to a cross duality between a spin-\(\frac{1}{2}\) and a spin-1 model.
 We will now show that these qualitative features can be captured very simply by the star graph.
@@
 \textit{This feature - the equality of energy eigenvalue for distinct values of \(S^z\) - persists for all values of \(J \in \left[0^+, \infty^-\right]\)}.
-This is because, the gap between the degenerate subspace and the next excited level is \(J\) or \(J/2\), depending on whether \(K\) is even or odd, and the gap is always non-zero as long as \(J\) lies in the regime of RG flow.
+This is because, the gap between the degenerate subspace and the next excited level is \(J\) or \(\frac{J}{2}\), depending on whether \(K\) is even or odd, and the gap is always non-zero as long as \(J\) lies in the regime of RG flow.
 In other words, as the exchange coupling grows(shrinks) from \(0^+\left(\infty^-\right)\) towards the fixed point value \(J^*\), the degeneracy remains protected at \(K\).
@@
 The former is RG irrelevant while the latter is relevant, both flowing towards the stable fixed point \(J = J^\prime = J^*\).
-For \(K=2\), the central spin for the \(J^\prime\)-problem is of size \(\frac{K-1}{2} = 1/2\), which is the same as the \(J\)-problem, so the models are self-dual, as mentioned previously.
+For \(K=2\), the central spin for the \(J^\prime\)-problem is of size \(\frac{K-1}{2} = \frac{1}{2}\), which is the same as the \(J\)-problem, so the models are self-dual, as mentioned previously.
 
@@
 
-\section{Derivation of URG equations for the multi-channel Kondo model}
+\clearpage
+\section{URG equations for the multi-channel Kondo model}
 
@@
 
-The expansion we are talking about is
-\begin{align}
-	\eta = \frac{1}{\hat \omega - H_D}T^\dagger c = \frac{1}{\omega^\prime - H_D - H_X}T^\dagger c \simeq \frac{1}{\omega^\prime - H_D}T^\dagger c + \frac{1}{\omega^\prime - H_D}H_X \frac{1}{\omega^\prime - H_D} T^\dagger c
+We therefore need the generator of the unitary transformation that incorporates third order scattering scatterings explicitly.
+We should take account of all possible processes that render the set of states \(\left\{\ket{\hat n_{q\beta}=1},\ket{\hat n_{q\beta}=0}\right\}\) diagonal.
+The higher order generator itself has two scattering processes, such that the entire renormalization term \(c^\dagger_{q\beta} T \eta\) has in total three coherent processes.
+The way to make the state \(q\beta\) diagonal is to ensure that \(c^\dagger_{q\beta} T \eta\) does not change \(\hat n_{q\beta}\).
+This is done by letting exactly one of the scattering process in \(\eta\)  be \(T^\dagger c_{q\beta}\), while the other process in \(\eta\) has to be some internal scattering between the degrees of freedom other than \(q\beta\).
+This, however, does not fix the sequence in which the processes occur within \(\eta\).
+Kepeing this in mind, the complete generator upto third order can be written as
+\begin{align}
+	% \eta = \frac{1}{\hat \omega - H_D}T^\dagger c = \frac{1}{\omega^\prime - H_D - H_X}T^\dagger c \simeq \frac{1}{\omega^\prime - H_D}T^\dagger c + \frac{1}{\omega^\prime - H_D}H_X \frac{1}{\omega^\prime - H_D} T^\dagger c
+	\eta = \frac{1}{\hat \omega - H_D}T^\dagger c \simeq \frac{1}{\omega^\prime - H_D}T^\dagger c + \frac{1}{\omega^\prime - H_D}H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X
 \end{align}
 where \(H_X = J \sum_{k,k^\prime < \Lambda_j, \alpha,\alpha^\prime}\vec{S_d}\cdot\vec{s}_{\alpha \alpha^\prime}c^\dagger_{k\alpha}c_{k^\prime\alpha^\prime}\) is scattering between the entangled electrons.
+There are two third order terms in the above equation corresponding to the two possible sequences in which the processes can occur while keeping the total renormalization \(c^\dagger_{q\beta}T \eta\) diagonal in \(q\beta\).
+
 With this change, the second and third order renormalizations will take the form
@@
 \begin{align}
-	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T
-\end{align}
-We will use the identity
-\begin{align}
-	\label{identity_SSS}
-	S_d^a S_d^z S_d^b = \left(\frac{1}{4}\delta^{az} + \frac{i}{2}\sum_c \epsilon^{azc}S_d^c\right)S_d^b = \left(\frac{1}{4}\delta^{az}S_d^b + \frac{i}{8} \epsilon^{azb}  - \frac{1}{4}\sum_{c_1,c} \epsilon^{azc_1} \epsilon^{c_1 b c} S_d^c\right) = \frac{1}{4}\left(\delta^{az}S_d^b - \delta^{ab}S_d^z + \delta^{bz}S_d^a\right)
+	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X + T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T + \nonumber\\
+	T^\dagger c \frac{1}{\omega - H_D} c^\dagger T \frac{1}{\omega - H_D} H_X
 \end{align}
@@
 \subsection{Next-to-leading order renormalization}
-\begin{align}
-	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term} ~+~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term}
-\end{align}
-A general term of this summation has three sets of spin operators coming from \(c^\dagger T, H_X\) and \(T^\dagger c\).
-If we had expressed the spin operators in terms of \(S^z, S^\pm\), most of the terms would have atleast one \(S^+\) or \(S^-\), and by the same argument as in the single-channel case, the denominator will have anti-parallel spins and the Ising term will be negative, leading to the form: \(\omega - D/2 - \epsilon_k/2 + J/4\).
+\begin{align*}
+	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X}_\text{particle sector}\\
+	+ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T + T^\dagger c \frac{1}{\omega - H_D} c^\dagger T \frac{1}{\omega - H_D} H_X}_\text{hole sector}
+\end{align*}
+A general term of this expression has three sets of spin operators coming from \(c^\dagger T, H_X\) and \(T^\dagger c\).
+If we had expressed the spin operators in terms of \(S^z, S^\pm\), most of the terms would have atleast one \(S^+\) or \(S^-\), and by the same argument as in the single-channel case, the denominator of the first terms in the particle and hole sectors will have anti-parallel spins and the Ising term will be negative, leading to the form: \(\omega - \frac{D}{2} -  \frac{\epsilon_k}{2} + \frac{J}{4}\).
 \(\epsilon_k\) is the energy of the other electron that will be summed over.
@@
 \begin{align}
-	S_d^z c^\dagger_{q \uparrow} \frac{1}{\omega - D/2 -\epsilon_k/2 + J/2 S_d^z} S_d^z \frac{1}{\omega - D/2 -\epsilon_k/2 + J/2 S_d^z} S_d^z c_{q \uparrow}\\
+	S_d^z c^\dagger_{q \uparrow} \frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{2} S_d^z} S_d^z \frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{2} S_d^z} S_d^z c_{q \uparrow}\\
 \end{align}
@@
 \begin{align}
-	\frac{1}{2}S_d^z c^\dagger_{q \uparrow}\left[\frac{\left(\frac{1}{2} + S_d^z\right)}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2} - \frac{\left(\frac{1}{2} - S_d^z\right)}{\left(\omega^\prime - D/2 -\epsilon_k/2 - J/4\right)^2}\right]S_d^z c_{q \uparrow}
-\end{align}
-If we now use poor man's scaling values to relate the two \(\omega\)s, we get \(\omega^\prime - \omega = J/2\).
-Substituting this will make both the denominators identical: \(\omega - D/2 -\epsilon_k/2 + J/4\).
-This means that the denominator for all non-zero terms that renormalize the Hamiltonian is \(\omega - D/2 - \epsilon_k/2 + J/4\).
-
-\subsubsection{Calculation of first term}
-\begin{align}
-	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = J^3\sum_{q, k, k_1,k_2,\atop{\beta, \alpha, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} \frac{c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} c^\dagger_{k\alpha, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha \beta}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2}
+	\frac{1}{2}S_d^z c^\dagger_{q \uparrow}\left[\frac{\left(\frac{1}{2} + S_d^z\right)}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2} - \frac{\left(\frac{1}{2} - S_d^z\right)}{\left(\omega^\prime - \frac{D}{2} - \frac{\epsilon_k}{2} - \frac{J}{4}\right)^2}\right]S_d^z c_{q \uparrow}
+\end{align}
+If we now use poor man's scaling values to relate the two \(\omega\)s, we get \(\omega^\prime - \omega = \frac{J}{2}\).
+Substituting this will make both the denominators identical: \(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\).
+This means that the total denominator for all non-zero terms that renormalize the Hamiltonian is \(\left(\omega - \frac{D}{2} -  \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2\).
+
+For the second term in both the sectors, the first denominator will again be \(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\), but the second denominator will be different.
+This is because, in contrast to the other terms where the denominator was to the left of \(T^\dagger c\), the denominator here is positioned to the right of the operator, which means all the energy scales will be flipped (the particles tranform to holes).
+The total denominator in the second terms is therefore \(-\left(\omega - \frac{D}{2} -  \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2\), which is the negative of the other terms.
+
+\subsubsection*{\textbf{Particle sector renormalization}}
+The two terms in the particle sector have the form
+\begin{align}
+	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = J^3\sum_{q, k, k_1,k_2,\atop{\beta, \alpha, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} \frac{c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k\alpha, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha \beta}}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2}\\
+	c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X = J^3\sum_{q, k, k_1,k_2,\atop{\beta, \alpha, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} \frac{c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} c^\dagger_{k\alpha, l_1} c_{q\beta, l_1} S_d^c s^c_{\alpha \beta} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} S_d^b s^b_{\alpha_1 \alpha_2}}{-\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2}
 \end{align}
@@
 \begin{align}
-	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = J^3 n(D)\sum_{k, k_1,k_2,\atop{\beta, \alpha, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} \frac{c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} c^\dagger_{k\alpha, l_1} S_d^c s^c_{\alpha \beta}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2}
-\end{align}
-The operators \(c^\dagger_{k\alpha}\) and its conjugate can be brought together without any change of sign because there will be an even number of flips. The sum over \(k\) gives
-\begin{align}
-	\sum_k \frac{1 - \hat n_{k\alpha l_1}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2} =  \rho\int \frac{d\epsilon\left[1 - \hat n(\epsilon)_{\alpha l_1}\right] }{\left(\omega - D/2 -\epsilon/2 + J/4\right)^2} = \rho\int_0^{D-2\left( \omega + J/4 \right) } \frac{d\epsilon}{\left(\omega - D/2 -\epsilon/2 + J/4\right)^2}
+	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = J^3 n(D)\sum_{k, k_1,k_2,\atop{\beta, \alpha, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} \frac{c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} c^\dagger_{k\alpha, l_1} S_d^c s^c_{\alpha \beta}}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2}\\
+	c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X = J^3 n(D) \sum_{k, k_1,k_2,\atop{\beta, \alpha, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}} \frac{c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha} c^\dagger_{k\alpha, l_1} S_d^c s^c_{\alpha \beta} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} S_d^b s^b_{\alpha_1 \alpha_2}}{-\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2}
+\end{align}
+The operators \(c^\dagger_{k\alpha}\) and its conjugate can be brought together without any change of sign because there will be an even number of flips. The sum over \(k\) for the first term gives
+\begin{align}
+	\sum_k \frac{1 - \hat n_{k\alpha l_1}}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2} =  \rho\int \frac{d\epsilon\left[1 - \hat n(\epsilon)_{\alpha l_1}\right] }{\left(\omega - \frac{D}{2} -\epsilon/2 + \frac{J}{4}\right)^2} = \rho\int_0^{D-2\left( \omega + \frac{J}{4} \right) } \frac{d\epsilon}{\left(\omega - \frac{D}{2} -\epsilon/2 + \frac{J}{4}\right)^2}
 \end{align}
@@
 \begin{align}
-	\sum_k \frac{1 - \hat n_{k\alpha l_1}}{\left(\omega - D/2 -\epsilon_k/2 + J/4\right)^2} = -\frac{1}{2}\frac{\rho}{\omega - D/2 + J/4}
-\end{align}
-The sum over the channel index \(l_1\) produces a factor of \(K\). \(K = \sum_{l_1}\) is the total number of conduction bath channels. The entire expression is now
+	\sum_k \frac{1 - \hat n_{k\alpha l_1}}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2} = -\frac{1}{2}\frac{\rho}{\omega - \frac{D}{2} + \frac{J}{4}}
+\end{align}
+Similarly, the sum over \(k\) for the second term gives
+\begin{align}
+	-\sum_k \frac{1 - \hat n_{k\alpha l_1}}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2} = \frac{1}{2}\frac{\rho}{\omega - \frac{D}{2} + \frac{J}{4}}
+\end{align}
+
+The sum over the channel index \(l_1\) produces a factor of \(K\), where \(K = \sum_{l_1}\) is the total number of conduction bath channels. The entire expression is now
 \begin{align}
 	\label{first_term}
-	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\sum_{\beta, \alpha, \alpha_1,\alpha_2,\atop{a,b,c}} S_d^a s^a_{\beta \alpha} S_d^b s^b_{\alpha_1 \alpha_2} S_d^c s^c_{\alpha \beta} \sum_{k_1,k_2,l_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
+	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{\beta, \alpha, \alpha_1,\alpha_2,\atop{a,b,c}} S_d^a S_d^b S_d^c s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2} s^c_{\alpha \beta} \sum_{k_1,k_2,l_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}\\
+	c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X = \frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{\beta, \alpha, \alpha_1,\alpha_2,\atop{a,b,c}} S_d^a S_d^c S_d^b s^a_{\beta \alpha} s^c_{\alpha \beta} s^b_{\alpha_1 \alpha_2} \sum_{k_1,k_2,l_2}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
 \end{align}
@@
 \begin{align}
-	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\frac{1}{2}\sum_{\alpha_1,\alpha_2,a,b} S_d^a S_d^b S_d^a \sum_{k_1,k_2,l_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}s^b_{\alpha_1 \alpha_2}
-\end{align}
-The spin product can now be carried out:
-\begin{align}
-	\sum_a S_d^a S_d^b S_d^a = \sum_a S_d^a\left[\frac{1}{4}\delta^{ab} + \frac{i}{2}\sum_c \epsilon^{bac}S_d^c\right] = \frac{1}{4}S_d^b - \frac{1}{4}\sum_{ace}\epsilon^{bac}\epsilon^{ace}S_d^e = \frac{1}{4}S_d^b - \frac{1}{4}S_d^b \sum_{ac}\epsilon^{bac}\epsilon^{acb} \\
-	= -\frac{1}{4}S_d^b
-\end{align}
-The renormalization becomes
-\begin{align}
-	\Delta H_1 = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4}\frac{1}{2}\left( -\frac{1}{4} \right) \sum_{k_1,k_2,\alpha_1,\alpha_2,b,l_2} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}\\
-=\frac{1}{16}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4} \sum_{k_1,k_2,\alpha_1,\alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
-\end{align}
-
-\subsubsection{Calculation of second term}
+	c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - \frac{D}{2} + \frac{J}{4}}\frac{1}{2}\sum_{\alpha_1,\alpha_2,a,b} S_d^a S_d^b S_d^a \sum_{k_1,k_2,l_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}s^b_{\alpha_1 \alpha_2} \\
+	c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X = \frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - \frac{D}{2} + \frac{J}{4}} \frac{1}{2} \sum_{\alpha_1,\alpha_2,a,b} S_d^a S_d^a S_d^b \sum_{k_1,k_2,l_2}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}s^b_{\alpha_1 \alpha_2}
+\end{align}
+
+Adding the two terms gives
+\begin{equation}\begin{aligned}
+	\Delta H_\text{p-sector} = -\frac{1}{4}\frac{J^3 n(D) \rho K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{\alpha_1,\alpha_2,a,b} S_d^a \left[S_d^b, S_d^a\right] \sum_{k_1,k_2,l_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}s^b_{\alpha_1 \alpha_2}
+\end{aligned}\end{equation}
+The spin part can be simplified as follows:
+\begin{equation}\begin{aligned}
+	\sum_a S_d^a \left[S_d^b, S_d^a\right] = \sum_{a,e}S_d^a i \epsilon^{bae}S_d^e = -\frac{1}{2}\sum_{aef}\epsilon^{bae}\epsilon^{aef}S_d^f = -S_d^b\frac{1}{2}\sum_{ae}\left(\epsilon^{bae}\right)^2 = -S_d^b\frac{1}{2}\sum_{a\neq b, e\neq b, e \neq a} = - S_d^b
+\end{aligned}\end{equation}
+Substituting this gives
+\begin{equation}\begin{aligned}
+	\Delta H_\text{p-sector} = \frac{1}{4}\frac{J^3 n(D) \rho K}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{k_1,k_2,l_2,\alpha_1,\alpha_2,b} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} S_d^b s^b_{\alpha_1 \alpha_2} = \frac{1}{4}\frac{J^3 n(D) \rho K}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{k_1,k_2,l_2,\alpha_1,\alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2}
+\end{aligned}\end{equation}
+
+% The spin product can now be carried out:
+% \begin{align}
+% 	\sum_a S_d^a S_d^b S_d^a = \sum_a S_d^a\left[\frac{1}{4}\delta^{ab} + \frac{i}{2}\sum_c \epsilon^{bac}S_d^c\right] = \frac{1}{4}S_d^b - \frac{1}{4}\sum_{ace}\epsilon^{bac}\epsilon^{ace}S_d^e = \frac{1}{4}S_d^b - \frac{1}{4}S_d^b \sum_{ac}\epsilon^{bac}\epsilon^{acb} \\
+% 	= -\frac{1}{4}S_d^b
+% \end{align}
+% The renormalization becomes
+% \begin{align}
+% 	\Delta H_1 = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c = -\frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - \frac{D}{2} + \frac{J}{4}}\frac{1}{2}\left( -\frac{1}{4} \right) \sum_{k_1,k_2,\alpha_1,\alpha_2,b,l_2} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}\\
+% =\frac{1}{16}\frac{J^3 n(D) \rho K}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{k_1,k_2,\alpha_1,\alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
+% \end{align}
+
+\subsubsection*{\textbf{Hole sector renormalization}}
 Like the single-channel case, the renormalization coming from the hole excitations is exactly the Hermitian conjugate of that in the particle sector.
@@
 \begin{align}
-	\Delta H^{(3)} = \frac{1}{8}\frac{J^3 n(D) \rho K}{\omega - D/2 + J/4} \sum_{k_1,k_2,\alpha_1,\alpha_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
+	\Delta H^{(3)} = \frac{1}{2}\frac{J^3 n(D) \rho K}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{k_1,k_2,\alpha_1,\alpha_2} \vec{S_d}\cdot\vec{s}_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2}
 \end{align}
@@
 \begin{align}
-	\frac{\Delta J}{|\Delta D|} = -\frac{J^2 \rho}{\omega - D/2 + J/4} + \frac{1}{8}\frac{J^3 \rho^2 K}{\omega - D/2 + J/4} = -\frac{J^2 \rho}{\omega - D/2 + J/4}\left[1 - \frac{1}{8}J\rho K\right] 
-\end{align}
-We choose \(\omega = -D/2\) to get a clearer idea of what the equations say. 
+	\frac{\Delta J}{|\Delta D|} = -\frac{J^2 \rho}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{2}\frac{J^3 \rho^2 K}{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{J^2 \rho}{\omega - \frac{D}{2} + \frac{J}{4}}\left[1 - \frac{1}{2}J\rho K\right]
+\end{align}
+We choose \(\omega = -\frac{D}{2}\) to get a clearer idea of what the equations say. 
 \begin{align}
 	\label{mchannel}
-	\frac{\Delta J}{|\Delta D|} = \frac{J^2 \rho}{D - J/4}\left[1 - \frac{1}{8}J\rho K\right] 
+	\frac{\Delta J}{|\Delta D|} = \frac{J^2 \rho}{D - \frac{J}{4}}\left[1 - \frac{1}{2}J\rho K\right] 
 \end{align}
@@
 	\label{rg_beta}
-	\frac{\:\mathrm{d}J}{\:\mathrm{d}D} = \frac{J^2 \rho}{D - J/4}\left(\frac{1}{8}J\rho K - 1\right)
+	\frac{\:\mathrm{d}J}{\:\mathrm{d}D} = \frac{J^2 \rho}{D - \frac{J}{4}}\left(\frac{1}{2}J\rho K - 1\right)
 \end{align}
@@
 	\label{pms_mchannel}
-	\frac{\:\mathrm{d}J}{\:\mathrm{d}D} \simeq  \frac{J^2 \rho}{D}\left(\frac{1}{8}J\rho K - 1\right)
-\end{align}
-This equation has a stable fixed point at \(J^* = \frac{8}{\rho K}\).
-The value of the fixed point agrees with the poor man's scaling calculation in~\cite{tripathi2018landau}, but differs from the value of \(\frac{2}{\rho K}\) obtained in other references~\cite{Kuramoto1998,Kogan_2018}.
+	\frac{\:\mathrm{d}J}{\:\mathrm{d}D} \simeq  \frac{J^2 \rho}{D}\left(\frac{1}{2}J\rho K - 1\right)
+\end{align}
+This equation has a stable fixed point at \(J^* = \frac{2}{\rho K}\).
+% The value of the fixed point agrees with the poor man's scaling calculation in~\cite{tripathi2018landau}, but differs from the value of \(\frac{2}{\rho K}\) obtained in other references~\cite{Kuramoto1998,Kogan_2018}.
 
@@
 \begin{align}
-	J_1^* = \frac{8}{K \rho}, && D^* = \frac{J_2^*}{4}
+	J_1^* = \frac{2}{K \rho}, && D^* = \frac{J_2^*}{4}
 \end{align}
@@
 \begin{align}
-	\rho_\text{min} = \text{minimum }\left\{\rho, \text{ such that } \frac{8}{K \rho} < 4 D^*(\rho)\right\}
+	\rho_\text{min} = \text{minimum }\left\{\rho, \text{ such that } \frac{2}{K \rho} < 4 D^*(\rho)\right\}
 \end{align}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{./rhomin_D.pdf}
+	\includegraphics[width=0.5\textwidth]{../numerics/rhomin_D.pdf}
 	\caption{Red curve shows variation of \(\rho_\text{min}\) against \(D_0\).
@@
 
-\section{Derivation of URG equations for the multi-channel spin-\(S\) impurity Kondo model}
+\section{URG equations for the multi-channel spin-\(S\) Kondo model}
 The leading order renormalization is the same as the single-channel model, and is shown in the appendix. Following that calculation, the Hamiltonian we will work with is 
@@
 \end{aligned}\end{equation}
+
+\paragraph{\(z|+|z\)}
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_\beta \sum_{m}\sum_{k_1,k_2,l_2}J^\beta_m J^t_m J^\beta_{m+1}\ket{m}\bra{m+1}c^\dagger_{k_1 \uparrow, l_2}c_{k_2 \downarrow,l_2}
+\end{aligned}\end{equation}
+
+\paragraph{\(z|-|z\)}
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_\beta \sum_{m}\sum_{k_1,k_2,l_2} J^\beta_{m+1} J^t_m J^\beta_m \ket{m+1}\bra{m}c^\dagger_{k_1 \downarrow, l_2}c_{k_2 \uparrow,l_2}
+\end{aligned}\end{equation}
+
 \paragraph{\(+|+|-\)}
@@
 	s_\text{tot}, s_\text{tot}^z = && (1,-1), && (1,0), && (1,1)\\
-	\gamma_{s_\text{tot}}^{s_\text{tot}^z} = && \frac{1}{E_\text{gs}}, && \frac{1}{E_\text{gs} + J/2}, && -- \\
+	\gamma_{s_\text{tot}}^{s_\text{tot}^z} = && \frac{1}{E_\text{gs}}, && \frac{1}{E_\text{gs} + \frac{J}{2}}, && -- \\
 	\chi_{s_\text{tot}}^{s_\text{tot}^z} = && 2, && 2, && --\\
-	\gamma_{s_\text{tot}}^{-s_\text{tot}^z} = && --, && \frac{1}{E_\text{gs} + J/2}, && \frac{1}{E_\text{gs}}\\
+	\gamma_{s_\text{tot}}^{-s_\text{tot}^z} = && --, && \frac{1}{E_\text{gs} + \frac{J}{2}}, && \frac{1}{E_\text{gs}}\\
 	\chi_{s_\text{tot}}^{-s_\text{tot}^z} = && --, && 2, && 2\\
@@
 	H_\text{eff}^{1, -1} &= H_0 - J S_d^z + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{H_0}{E_\text{gs}}  - \frac{s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 E_\text{gs}}  + \frac{H_0^2}{E_\text{gs}^2}  - \frac{ Z_{1,\text{tot}} H_0}{E_\text{gs}^3}\right] \left(\frac{1}{2} + S_d^z\right) \\
-	H_\text{eff}^{1, 0} &= H_0 + \frac{J^2}{2\left(E_\text{gs} + J/2\right)}\left[1 + \frac{ H_0 + \left(1/2 + S_d^z\right) s^+_\text{tot}X_{1,\text{tot}} - \left(1/2 - S_d^z\right) s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 \left(E_\text{gs} + J/2\right)} + \frac{H_0^2}{\left(E_\text{gs} + J/2\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + J/2\right)^3} \right] \\
+	H_\text{eff}^{1, 0} &= H_0 + \frac{J^2}{2\left(E_\text{gs} + \frac{J}{2}\right)}\left[1 + \frac{ H_0 + \left(\frac{1}{2} + S_d^z\right) s^+_\text{tot}X_{1,\text{tot}} - \left(\frac{1}{2} - S_d^z\right) s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 \left(E_\text{gs} + \frac{J}{2}\right)} + \frac{H_0^2}{\left(E_\text{gs} + \frac{J}{2}\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + \frac{J}{2}\right)^3} \right] \\
 \end{align}
@@
 \begin{align}
-	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} 
+	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + \frac{J}{2} \right)   \end{pmatrix} 
 \end{align}
@@
 	\label{eigenvalue}
-	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}
-\end{align}
-where \(\alpha = \epsilon^h_m + J/4\).
+	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-\frac{J}{2} \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + \frac{J}{2}\right) }\right] = -\frac{J}{4} \pm \sqrt{J^2x^M_m/4 + \alpha^2}
+\end{align}
+where \(\alpha = \epsilon^h_m + \frac{J}{4}\).
 The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\).
@@
 &		JM/2 - h/2, &&\ket{\downarrow, M, -M}, && m = -M\\
-&-J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}, &&\left\{\ket{\uparrow, M, m}, \ket{\downarrow, M, m+1}\right\}, &&m=-M,\ldots,M-1\\
+&-\frac{J}{4} \pm \sqrt{J^2x^M_m/4 + \alpha^2}, &&\left\{\ket{\uparrow, M, m}, \ket{\downarrow, M, m+1}\right\}, &&m=-M,\ldots,M-1\\
 &JM/2 + h/2, &&\ket{\uparrow, M, M},&& m = M\\
@@
 	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
-	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
-\end{align}
-where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\).
+	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \frac{J}{4}}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+\end{align}
+where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(\frac{1}{2}\).
 This is yet not the complete partition function, because we have not accounted for the possibility that there multiple subspaces of \(M\).
 For example, the \(K=3\) case states can be obtained by adding the third spin-half onto the states \(S=0,1\).
-\(S=0\) gives \(s_\text{tot}=1/2\) and \(S=1\) gives \(s_\text{tot} = 1/2, 3/2\).
-So, \(s_\text{tot} = 1/2\) appears twice.
+\(S=0\) gives \(s_\text{tot}=\frac{1}{2}\) and \(S=1\) gives \(s_\text{tot} = \frac{1}{2}, 3/2\).
+So, \(s_\text{tot} = \frac{1}{2}\) appears twice.
 These two subspaces are actually orthogonal, because the quantum numbers for the individual channels are different.
@@
 \begin{align}
-	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \frac{J}{4}}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
 \end{align}
@@
 \begin{align}
-	\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta J/4}\alpha\frac{\sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2} }{\sqrt{J^2x^M_m/4 + \alpha^2}} + e^{-\beta JM/2}\sinh \left(\beta h/2\right)\right] \\
-	\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\frac{1}{2}\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\frac{e^{\beta J/4}}{\sqrt{J^2x^M_m/4 + \alpha^2}}\left(\sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + \beta\alpha^2 \frac{\cosh\beta\sqrt{J^2x^M_m/4 + \alpha^2}}{\sqrt{J^2x^M_m/4 + \alpha^2}}\right.\right.\\
+	\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta \frac{J}{4}}\alpha\frac{\sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2} }{\sqrt{J^2x^M_m/4 + \alpha^2}} + e^{-\beta JM/2}\sinh \left(\beta h/2\right)\right] \\
+	\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\frac{1}{2}\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\frac{e^{\beta \frac{J}{4}}}{\sqrt{J^2x^M_m/4 + \alpha^2}}\left(\sinh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + \beta\alpha^2 \frac{\cosh\beta\sqrt{J^2x^M_m/4 + \alpha^2}}{\sqrt{J^2x^M_m/4 + \alpha^2}}\right.\right.\\
 						   &\quad \quad\quad \quad\left.\left.
@@
 \end{align}
-We will now take the limit of \(h \to 0\). Note that \(\alpha(h\to 0)=\frac{J}{2}(m+1/2)\) and hence 
-\begin{align}
-	(J^2x^M_m/4 + \alpha^2)(h \to 0) = \frac{J^2}{4}\left[M(M+1) - m(m+1) + (m+1/2)^2\right] = \frac{J^2}{4}\left( M + 1/2 \right)^2
-\end{align}
-For brevity, we define \(\theta_M = \beta J (M+1/2)/2\) and \(\Sigma_M = \sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}(m+1/2)^2\).
+We will now take the limit of \(h \to 0\). Note that \(\alpha(h\to 0)=\frac{J}{2}(m+\frac{1}{2})\) and hence 
+\begin{align}
+	(J^2x^M_m/4 + \alpha^2)(h \to 0) = \frac{J^2}{4}\left[M(M+1) - m(m+1) + (m+\frac{1}{2})^2\right] = \frac{J^2}{4}\left( M + \frac{1}{2} \right)^2
+\end{align}
+For brevity, we define \(\theta_M = \beta J (M+\frac{1}{2})/2\) and \(\Sigma_M = \sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}(m+\frac{1}{2})^2\).
 It can be shown that this summation, for \(M=M_\text{max}=K/2\), evaluates to \(\Sigma_\text{max} = K(K+1)(K-1)/12\).
 \begin{align}
-	\lim_{h \to 0}Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta \frac{J}{2}\left( M + 1/2 \right) + 2e^{-\beta JM/2}\right] = \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[4Me^{\beta J/4}\cosh \theta_M + 2e^{-\beta JM/2}\right]\\
-	\lim_{h \to 0}\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} &=  \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta J/4}(m+1/2)\frac{\sinh \beta\frac{J}{2}\left( M + 1/2 \right) }{\left( M + 1/2 \right)}\right] = 0\\
-	\lim_{h \to 0}\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \frac{\beta^2}{2}\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\frac{e^{\beta J/4}}{\theta_M}\left(2M\sinh \theta_M + \frac{\beta^2 J^2}{4}\left[\frac{\cosh\theta_M}{\theta_M} - \frac{\sinh \theta_M}{\theta_M^2}\right]\Sigma_M\right)+ e^{-\beta JM/2}\right]\\
+	\lim_{h \to 0}Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \frac{J}{4}}\cosh \beta \frac{J}{2}\left( M + \frac{1}{2} \right) + 2e^{-\beta JM/2}\right] = \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[4Me^{\beta \frac{J}{4}}\cosh \theta_M + 2e^{-\beta JM/2}\right]\\
+	\lim_{h \to 0}\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} &=  \beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}e^{\beta \frac{J}{4}}(m+\frac{1}{2})\frac{\sinh \beta\frac{J}{2}\left( M + \frac{1}{2} \right) }{\left( M + \frac{1}{2} \right)}\right] = 0\\
+	\lim_{h \to 0}\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} &= \frac{\beta^2}{2}\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\frac{e^{\beta \frac{J}{4}}}{\theta_M}\left(2M\sinh \theta_M + \frac{\beta^2 J^2}{4}\left[\frac{\cosh\theta_M}{\theta_M} - \frac{\sinh \theta_M}{\theta_M^2}\right]\Sigma_M\right)+ e^{-\beta JM/2}\right]\\
 \end{align}
@@
 For single-channel, we have \(M=\frac{1}{2}\) and \(m = \pm \frac{1}{2}\).
-The terminal states are \(S_d^z=-1/2, m=-1/2\) and \(S_d^z=1/2, m=1/2\).
-There is therefore just one \(2\times 2\) block, and that is at \(m=-1/2\).
+The terminal states are \(S_d^z=-\frac{1}{2}, m=-\frac{1}{2}\) and \(S_d^z=\frac{1}{2}, m=\frac{1}{2}\).
+There is therefore just one \(2\times 2\) block, and that is at \(m=-\frac{1}{2}\).
 \begin{gather}
-	\lim_{h \to 0}Z(h) = 2e^{\beta J/4}\cosh \beta \frac{J}{2} + 2e^{-\beta J/4} \\
+	\lim_{h \to 0}Z(h) = 2e^{\beta \frac{J}{4}}\cosh \beta \frac{J}{2} + 2e^{-\beta \frac{J}{4}} \\
 	\lim_{h \to 0}\frac{\:\mathrm{d}Z(h)}{\:\mathrm{d}h} = 0 \\
-	\lim_{h \to 0}\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} = \frac{\beta}{J}\left(e^{\beta J/4}\sinh \beta\frac{J}{2} + e^{-\beta J/4}\frac{J \beta}{2}\right)\\
-	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z(h)^{\prime\prime}}{Z(h)} - \left(\frac{Z(h)^{\prime}}{Z(h)}\right)^2 \right] = \frac{1}{J}\frac{\left(2e^{\beta J/2}\sinh \beta\frac{J}{2} + J \beta\right)}{4e^{\beta J/2}\cosh \beta \frac{J}{2} + 4}
+	\lim_{h \to 0}\frac{\:\mathrm{d}^2Z(h)}{\:\mathrm{d}h^2} = \frac{\beta}{J}\left(e^{\beta \frac{J}{4}}\sinh \beta\frac{J}{2} + e^{-\beta \frac{J}{4}}\frac{J \beta}{2}\right)\\
+	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z(h)^{\prime\prime}}{Z(h)} - \left(\frac{Z(h)^{\prime}}{Z(h)}\right)^2 \right] = \frac{1}{J}\frac{\left(2e^{\beta \frac{J}{2}}\sinh \beta\frac{J}{2} + J \beta\right)}{4e^{\beta \frac{J}{2}}\cosh \beta \frac{J}{2} + 4}
 \end{gather}
@@
 	Z &\to 2 r^K_{M_\text{max}} M_\text{max} e^{\beta \frac{J}{2}(M_\text{max} + 1)}\\
-	Z^{\prime \prime} &\to r^K_{M_\text{max}}\left(\frac{\beta }{2(M_\text{max} + 1/2)}\right)^2 e^{\beta \frac{J}{2}(M_\text{max} + 1)}\Sigma_\text{max}\\
+	Z^{\prime \prime} &\to r^K_{M_\text{max}}\left(\frac{\beta }{2(M_\text{max} + \frac{1}{2})}\right)^2 e^{\beta \frac{J}{2}(M_\text{max} + 1)}\Sigma_\text{max}\\
 	\chi &\to \frac{\beta\Sigma_\text{max}}{2M_\text{max}\left(2M_\text{max}+1\right)^2} = \frac{\beta K(K+1)(K-1)/12}{K(K+1)^2} = \frac{\beta(K-1)}{12(K+1)}
@@
 \begin{align}
-	H_m = \begin{pmatrix} m(J/2 + h) & J\sqrt{x^M_m}/2 \\ J\sqrt{x^M_m}/2 & (m+1)(h - J/2) \end{pmatrix} 
+	H_m = \begin{pmatrix} m(\frac{J}{2} + h) & J\sqrt{x^M_m}/2 \\ J\sqrt{x^M_m}/2 & (m+1)(h - \frac{J}{2}) \end{pmatrix} 
 \end{align}
@@
 \begin{align}
-	\lambda_{m, \pm}^{M, h} &= -J/4 + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2x^M_m + \left[(2m+1)h - J/2\right]^2 - 4m(m+1)(h^2 - J^2/4)} \\
-				&= -J/4 + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2(M + 1/2)^2 + h^2 - (2m+1)Jh}	= -J/4 + (2m+1)h/2 \pm \phi^M_m
+	\lambda_{m, \pm}^{M, h} &= -\frac{J}{4} + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2x^M_m + \left[(2m+1)h - \frac{J}{2}\right]^2 - 4m(m+1)(h^2 - J^2/4)} \\
+				&= -\frac{J}{4} + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2(M + \frac{1}{2})^2 + h^2 - (2m+1)Jh}	= -\frac{J}{4} + (2m+1)h/2 \pm \phi^M_m
 \end{align}
@@
 	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta JM/2}\left(e^{\beta hM} + e^{-\beta hM}\right)\right] \\
-	     &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(J/4 - (m+1/2)h\right)}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\cosh \beta Mh\right]
+	     &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(\frac{J}{4} - (m+\frac{1}{2})h\right)}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\cosh \beta Mh\right]
 \end{align}
@@
 \begin{align}
-	Z^\prime(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(J/4 - (m+1/2)h\right)}\left(-\beta (m+1/2) \cosh \beta\phi^M_m + \beta\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right)+ 2\beta Me^{-\beta JM/2}\sinh \beta Mh\right]\\
-	Z^{\prime\prime}(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2 e^{\beta \left(J/4 - (m+1/2)h\right)}\left(\beta^2 (m+1/2)^2 \cosh \beta\phi^M_m - 2\beta^2 (m+1/2)\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right.\right.\\
+	Z^\prime(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(\frac{J}{4} - (m+\frac{1}{2})h\right)}\left(-\beta (m+\frac{1}{2}) \cosh \beta\phi^M_m + \beta\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right)+ 2\beta Me^{-\beta JM/2}\sinh \beta Mh\right]\\
+	Z^{\prime\prime}(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2 e^{\beta \left(\frac{J}{4} - (m+\frac{1}{2})h\right)}\left(\beta^2 (m+\frac{1}{2})^2 \cosh \beta\phi^M_m - 2\beta^2 (m+\frac{1}{2})\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right.\right.\\
 			    &\quad\quad\quad\quad\quad\quad\left.\left.
@@
 \begin{align}
-	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\right]\\
-	Z^\prime(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\left(-\beta (m+1/2) \cosh \beta\phi^M_m + \beta\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right)\right]\\
-	Z^{\prime\prime}(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2 e^{\beta J/4}\left(\beta^2 (m+1/2)^2 \cosh \beta\phi^M_m - 2\beta^2 (m+1/2)\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right.\right.\\
+	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \frac{J}{4}}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\right]\\
+	Z^\prime(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \frac{J}{4}}\left(-\beta (m+\frac{1}{2}) \cosh \beta\phi^M_m + \beta\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right)\right]\\
+	Z^{\prime\prime}(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2 e^{\beta \frac{J}{4}}\left(\beta^2 (m+\frac{1}{2})^2 \cosh \beta\phi^M_m - 2\beta^2 (m+\frac{1}{2})\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right.\right.\\
 			    &\quad\quad\quad\quad\quad\quad\left.\left.
@@
 We are interested in the low temperature behaviour.
-In the limit of \(h \to 0\), \(\phi_m^M \to \phi^M = J(M+1/2)/2\).
+In the limit of \(h \to 0\), \(\phi_m^M \to \phi^M = J(M+\frac{1}{2})/2\).
 We can also look at the behaviour of the derivative:
 \begin{align}
-	\lim_{h \to 0}\frac{\:\mathrm{d}\phi_m^M}{\:\mathrm{d}h} &= -\frac{J(m+1/2)}{4\phi^M}\\
-	\lim_{h \to 0}\frac{\:\mathrm{d}^2\phi_m^M}{\:\mathrm{d}h^2} &= \frac{1}{4\phi^M} - \frac{J^2(m + 1/2)^2}{16\left(\phi^M\right)^3}\\
+	\lim_{h \to 0}\frac{\:\mathrm{d}\phi_m^M}{\:\mathrm{d}h} &= -\frac{J(m+\frac{1}{2})}{4\phi^M}\\
+	\lim_{h \to 0}\frac{\:\mathrm{d}^2\phi_m^M}{\:\mathrm{d}h^2} &= \frac{1}{4\phi^M} - \frac{J^2(m + \frac{1}{2})^2}{16\left(\phi^M\right)^3}\\
 \end{align}
@@
 \begin{align}
-	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\phi^M + 2e^{-\beta JM/2}\right] = \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[4Me^{\beta J/4}\cosh \beta\phi^M + 2e^{-\beta JM/2}\right]\\
-	Z^\prime(h \to 0) &=-\beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M2e^{\beta J/4} \left(\cosh \beta\phi^M + \frac{J}{4\phi^M}\sinh \beta\phi^M\right)\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left( m + 1/2 \right) = 0\\
-Z^{\prime\prime}(h \to 0) &=\beta^2\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[2 e^{\beta J/4}\left\{\left(1 + \frac{J^2}{16{\phi^M}^2}\right) \Sigma_M \cosh \beta\phi^M + \left(\frac{2M}{4\beta\phi^M} + \frac{J}{2\phi^M}\left(1 - \frac{J}{16\beta{\phi^M}^2}\right)\Sigma_M \right) \sinh \beta\phi^M\right\} \right.\\
+	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \frac{J}{4}}\cosh \beta\phi^M + 2e^{-\beta JM/2}\right] = \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[4Me^{\beta \frac{J}{4}}\cosh \beta\phi^M + 2e^{-\beta JM/2}\right]\\
+	Z^\prime(h \to 0) &=-\beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M2e^{\beta \frac{J}{4}} \left(\cosh \beta\phi^M + \frac{J}{4\phi^M}\sinh \beta\phi^M\right)\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left( m + \frac{1}{2} \right) = 0\\
+Z^{\prime\prime}(h \to 0) &=\beta^2\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[2 e^{\beta \frac{J}{4}}\left\{\left(1 + \frac{J^2}{16{\phi^M}^2}\right) \Sigma_M \cosh \beta\phi^M + \left(\frac{2M}{4\beta\phi^M} + \frac{J}{2\phi^M}\left(1 - \frac{J}{16\beta{\phi^M}^2}\right)\Sigma_M \right) \sinh \beta\phi^M\right\} \right.\\
 			  &\quad\quad\quad\quad\quad\quad\quad\left.+ 2 M^2 e^{-\beta JM/2}\right]\\
 \end{align}
-where \(\Sigma_M = \sum_m (m+1/2)^2\).
+where \(\Sigma_M = \sum_m (m+\frac{1}{2})^2\).
 
@@
 \begin{align}
-	     Z(h \to 0) &= r^K_{K/2} 4Me^{\beta J/4}\frac{1}{2}e^{\beta\Phi}\\
-	     Z^{\prime\prime}(h \to 0) &=\beta^2 r^K_{K/2}2 e^{\beta J/4}\frac{1}{2}e^{\beta \Phi}\left(1 + \frac{J}{4\Phi}\right)^2\Sigma_\text{max}\\
+	     Z(h \to 0) &= r^K_{K/2} 4Me^{\beta \frac{J}{4}}\frac{1}{2}e^{\beta\Phi}\\
+	     Z^{\prime\prime}(h \to 0) &=\beta^2 r^K_{K/2}2 e^{\beta \frac{J}{4}}\frac{1}{2}e^{\beta \Phi}\left(1 + \frac{J}{4\Phi}\right)^2\Sigma_\text{max}\\
 \end{align}
@@
 For example, for \(K=2\), the states in question are \(\ket{M=1, m=-1,0}\).
-For \(h>0\), the ground state occurs in the subspace \(\ket{S_d^z=1/2, m=-1},\ket{S_d^z=-1/2,m=0}\).
-If we now flip the magnetic field, the ground state subspace flips to \(\ket{S_d^z=1/2, m=0},\ket{S_d^z=-1/2,m=1}\).
-Instead, if we look at the case of \(K=1\), the ground state is in the subspace of \(\ket{S_d^z=1/2,m=-1/2},\ket{S_d^z=-1/2, m=1/2}\), and since there is only this one subspace, the ground state is independent of the field.
+For \(h>0\), the ground state occurs in the subspace \(\ket{S_d^z=\frac{1}{2}, m=-1},\ket{S_d^z=-\frac{1}{2},m=0}\).
+If we now flip the magnetic field, the ground state subspace flips to \(\ket{S_d^z=\frac{1}{2}, m=0},\ket{S_d^z=-\frac{1}{2},m=1}\).
+Instead, if we look at the case of \(K=1\), the ground state is in the subspace of \(\ket{S_d^z=\frac{1}{2},m=-\frac{1}{2}},\ket{S_d^z=-\frac{1}{2}, m=\frac{1}{2}}\), and since there is only this one subspace, the ground state is independent of the field.
 From this discussion, it is clear that the non-analyticity appears because there are multiple values of \(m \in [-M, M-1]\) in the ground state manifold, which means that it is the ground state degeneracy that causes the non-analyticity.
@@
 The indices \(k,l\) sum over the momentum states.
-\(\vec S_d\) is the impurity spin operator with \(S_d^z = \pm 1/2\).
+\(\vec S_d\) is the impurity spin operator with \(S_d^z = \pm \frac{1}{2}\).
 
@@
 Both \(H^I_0\) and \(H^I_1\) have all three operators \(S_d^z, S_d^\pm\).
-We call \(S_d^z\) the spin-keep term and the others spin-flip terms.
 The entire product will thus have \(3\times 3 = 9\) terms.
@@
 This means we can identically replace \(S_d^z s^z_{qq} = -\frac{1}{4}\).
-Also, in the particle sector, the Greens function always has \(c_{q\beta}\) in front of it, so \(\epsilon_q \tau_{q\beta} = D/2\).
+Also, in the particle sector, the Greens function always has \(c_{q\beta}\) in front of it, so \(\epsilon_q \tau_{q\beta} = \frac{D}{2}\).
 Substituting all this, we get
 \begin{align}
-	\frac{1}{\omega - D/2 + J/4}\sum_{|k,k^\prime|<\Lambda,q}\left[\frac{1}{2}J^z J^t \left(S_d^z S_d^+ s^z_{qk^\prime}s^-_{kq} + S_d^z S_d^- s^z_{qk^\prime}s^+_{kq}\right) + \frac{1}{2}J^t J^z \left(S_d^+ S_d^z s^-_{qk^\prime}s^z_{kq} + S_d^- S_d^z s^+_{qk^\prime}s^z_{kq}\right)\right.\\
+	\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{|k,k^\prime|<\Lambda,q}\left[\frac{1}{2}J^z J^t \left(S_d^z S_d^+ s^z_{qk^\prime}s^-_{kq} + S_d^z S_d^- s^z_{qk^\prime}s^+_{kq}\right) + \frac{1}{2}J^t J^z \left(S_d^+ S_d^z s^-_{qk^\prime}s^z_{kq} + S_d^- S_d^z s^+_{qk^\prime}s^z_{kq}\right)\right.\\
 +\left.\frac{1}{4}{J^t}^2 \left(S_d^- S_d^+ s^+_{qk^\prime}s^-_{kq} + S_d^+ S_d^- s^-_{qk^\prime}s^+_{kq}\right)\right]
@@
 \begin{align}
-	\frac{1}{\omega - D/2 + J/4}\sum_{|k,k^\prime|<\Lambda,q}\left[\frac{1}{4}J^z J^t \left(-\frac{1}{2}S_d^+ \hat n_{q}s^-_{kk^\prime} - \frac{1}{4}S_d^- \hat n_{q} s^z_{kk^\prime}\right) - \frac{1}{4}{J^t}^2 S_d^z\left(-\hat n_{q \uparrow}c^\dagger_{k \downarrow}c_{k^\prime \downarrow} + \hat n_{q \downarrow}c^\dagger_{k \uparrow}c_{k^\prime \uparrow}\right)\right]
+	\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{|k,k^\prime|<\Lambda,q}\left[\frac{1}{4}J^z J^t \left(-\frac{1}{2}S_d^+ \hat n_{q}s^-_{kk^\prime} - \frac{1}{4}S_d^- \hat n_{q} s^z_{kk^\prime}\right) - \frac{1}{4}{J^t}^2 S_d^z\left(-\hat n_{q \uparrow}c^\dagger_{k \downarrow}c_{k^\prime \downarrow} + \hat n_{q \downarrow}c^\dagger_{k \uparrow}c_{k^\prime \uparrow}\right)\right]
 \end{align}
@@
 \begin{align}
-	\Delta H_1 = -\frac{1}{2}\frac{n(D)}{\omega - D/2 + J/4}\sum_{|k,k^\prime|<\Lambda}\left[J^z J^t \frac{1}{2}\left(S_d^+ s^-_{kk^\prime} + S_d^- s^z_{kk^\prime}\right) + {J^t}^2 S_d^z s^z_{kk^\prime}\right]
+	\Delta H_1 = -\frac{1}{2}\frac{n(D)}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{|k,k^\prime|<\Lambda}\left[J^z J^t \frac{1}{2}\left(S_d^+ s^-_{kk^\prime} + S_d^- s^z_{kk^\prime}\right) + {J^t}^2 S_d^z s^z_{kk^\prime}\right]
 \end{align}
@@
 	\label{kondo_part}
-	\Delta J^z = -\frac{1}{2}\frac{{J^t}^2n(D)}{\omega - D/2 + J/4}, && \Delta J^t = -\frac{1}{2}\frac{J^z J^tn(D)}{\omega - D/2 + J/4}
+	\Delta J^z = -\frac{1}{2}\frac{{J^t}^2n(D)}{\omega - \frac{D}{2} + \frac{J}{4}}, && \Delta J^t = -\frac{1}{2}\frac{J^z J^tn(D)}{\omega - \frac{D}{2} + \frac{J}{4}}
 \end{align}
@@
 \end{align}
-The same considerations as those in the particle sector apply here, and the denominator becomes \(\omega - D/2 + J/4\), while the numerator is \(H^I_1 H^I_0\).
+The same considerations as those in the particle sector apply here, and the denominator becomes \(\omega - \frac{D}{2} + \frac{J}{4}\), while the numerator is \(H^I_1 H^I_0\).
 Since this is just the Hermitian conjugate of the particle sector form, we do not need to calculate this separately, because the renormalization here will be \(\Delta H_0 = \Delta H_1^\dagger = \Delta H_1\).
@@
 \begin{align}
-	\Delta J^z = -\frac{{J^t}^2n(D)}{\omega - D/2 + J/4}, && \Delta J^t = -\frac{J^z J^tn(D)}{\omega - D/2 + J/4}
+	\Delta J^z = -\frac{{J^t}^2n(D)}{\omega - \frac{D}{2} + \frac{J}{4}}, && \Delta J^t = -\frac{J^z J^tn(D)}{\omega - \frac{D}{2} + \frac{J}{4}}
 \end{align}
@@
 	\label{kondosym}
-	\Delta J = - \frac{J^2 n(D)}{\omega - D/2 + \frac{1}{4}J}
-\end{align}
-To recover the one-loop form, we can replace \(\omega\) with the bare value \(-D/2\) and ignore the \(J\) in the denominator (small \(J\)).
+	\Delta J = - \frac{J^2 n(D)}{\omega - \frac{D}{2} + \frac{1}{4}J}
+\end{align}
+To recover the one-loop form, we can replace \(\omega\) with the bare value \(-\frac{D}{2}\) and ignore the \(J\) in the denominator (small \(J\)).
 \begin{align}
@@
 \begin{align}
-	\Delta J^{(2)} = -\frac{J^2 n(D)}{\omega - D/2 + J/4}
-\end{align}
-For \(\omega < D/2\), we get the flow towards the strong coupling fixed point.
-That is, there appears a stable fixed point at \(J^* = 4|\omega - D/2|\) for all bare \(J > 0\).
+	\Delta J^{(2)} = -\frac{J^2 n(D)}{\omega - \frac{D}{2} + \frac{J}{4}}
+\end{align}
+For \(\omega < \frac{D}{2}\), we get the flow towards the strong coupling fixed point.
+That is, there appears a stable fixed point at \(J^* = 4|\omega - \frac{D}{2}|\) for all bare \(J > 0\).
 We also get a decay towards the local moment fixed point \(J^* = 0\) for \(J < 0\).
-For \(\omega = -D/2\) and \(J \ll D\), we get the one-loop PMS form.
-\begin{align}
-	\Delta J^{(2)} = \frac{J^2 n(D)}{D - J/4} \simeq \frac{J^2 n(D)}{D}
+For \(\omega = -\frac{D}{2}\) and \(J \ll D\), we get the one-loop PMS form.
+\begin{align}
+	\Delta J^{(2)} = \frac{J^2 n(D)}{D - \frac{J}{4}} \simeq \frac{J^2 n(D)}{D}
 \end{align}
@@
 \begin{equation}\begin{aligned}
-	\sum_{kk^\prime,m,\sigma} c^\dagger_{q \sigma} c_{k^\prime \sigma} \ket{m}\bra{m}\frac{{J^\sigma_m}^2}{\omega - D/2 + \frac{J}{2}\sigma S_d^z}\ket{m}\bra{m} c^\dagger_{k \sigma}c_{q \sigma} = -\sum_{kk^\prime,m,\sigma}n_{q \sigma}\frac{{J^\sigma_m}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma} \ket{m}\bra{m}}{\omega_{m, \sigma} - D/2 + \frac{J}{2}\sigma m}
+	\sum_{kk^\prime,m,\sigma} c^\dagger_{q \sigma} c_{k^\prime \sigma} \ket{m}\bra{m}\frac{{J^\sigma_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}\sigma S_d^z}\ket{m}\bra{m} c^\dagger_{k \sigma}c_{q \sigma} = -\sum_{kk^\prime,m,\sigma}n_{q \sigma}\frac{{J^\sigma_m}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma} \ket{m}\bra{m}}{\omega_{m, \sigma} - \frac{D}{2} + \frac{J}{2}\sigma m}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}^2}{\omega - D/2 + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m+1, \uparrow} - D/2 + \frac{J}{2}\left( m+1 \right) }
+	\sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m+1, \uparrow} - \frac{D}{2} + \frac{J}{2}\left( m+1 \right) }
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m}\frac{{J^t_m}^2}{\omega - D/2 - \frac{J}{2}S_d^z}\ket{m}\bra{m+1} c^\dagger_{k \uparrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \uparrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m+1}}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}m}
+	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m}\frac{{J^t_m}^2}{\omega - \frac{D}{2} - \frac{J}{2}S_d^z}\ket{m}\bra{m+1} c^\dagger_{k \uparrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \uparrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m+1}}{\omega_{m, \downarrow} - \frac{D}{2} - \frac{J}{2}m}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \downarrow} \ket{m}\bra{m}\frac{J^\downarrow_m{J^t_m}}{\omega - D/2 - \frac{J}{2}S_d^z}\ket{m}\bra{m+1} c^\dagger_{k \uparrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{J^\downarrow_m J^t_m c^\dagger_{k \uparrow}c_{k^\prime\downarrow} \ket{m}\bra{m+1}}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}m}
+	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \downarrow} \ket{m}\bra{m}\frac{J^\downarrow_m{J^t_m}}{\omega - \frac{D}{2} - \frac{J}{2}S_d^z}\ket{m}\bra{m+1} c^\dagger_{k \uparrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{J^\downarrow_m J^t_m c^\dagger_{k \uparrow}c_{k^\prime\downarrow} \ket{m}\bra{m+1}}{\omega_{m, \downarrow} - \frac{D}{2} - \frac{J}{2}m}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\sum_{kk^\prime,m} c^\dagger_{q \uparrow}c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}J^\uparrow_{m+1}}{\omega - D/2 + \frac{J}{2}S_d^z} \ket{m+1}\bra{m+1} c^\dagger_{k \uparrow} c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{J^\uparrow_{m+1} J^t_m c^\dagger_{k \uparrow}c_{k^\prime\downarrow} \ket{m}\bra{m+1}}{\omega_{m+1, \downarrow} - D/2 + \frac{J}{2}\left(m+1\right) }
+	\sum_{kk^\prime,m} c^\dagger_{q \uparrow}c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}J^\uparrow_{m+1}}{\omega - \frac{D}{2} + \frac{J}{2}S_d^z} \ket{m+1}\bra{m+1} c^\dagger_{k \uparrow} c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{J^\uparrow_{m+1} J^t_m c^\dagger_{k \uparrow}c_{k^\prime\downarrow} \ket{m}\bra{m+1}}{\omega_{m+1, \downarrow} - \frac{D}{2} + \frac{J}{2}\left(m+1\right) }
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m+1}\frac{J^\uparrow_{m+1}{J^t_m}}{\omega - D/2 + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{J^\uparrow_{m+1} J^t_m c^\dagger_{k \downarrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m}}{\omega_{m+1, \uparrow} - D/2 + \frac{J}{2}(m+1)}
+	\sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m+1}\frac{J^\uparrow_{m+1}{J^t_m}}{\omega - \frac{D}{2} + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{J^\uparrow_{m+1} J^t_m c^\dagger_{k \downarrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m}}{\omega_{m+1, \uparrow} - \frac{D}{2} + \frac{J}{2}(m+1)}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m}\frac{J^\downarrow_{m}{J^t_m}}{\omega - D/2 - \frac{J}{2}S_d^z}\ket{m}\bra{m} c^\dagger_{k \downarrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{J^\downarrow_{m} J^t_m c^\dagger_{k \downarrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m}}{\omega_{m, \downarrow} - D/2 - \frac{J}{2}(m)}
+	\sum_{kk^\prime,m} c^\dagger_{q \downarrow} c_{k^\prime \uparrow} \ket{m+1}\bra{m}\frac{J^\downarrow_{m}{J^t_m}}{\omega - \frac{D}{2} - \frac{J}{2}S_d^z}\ket{m}\bra{m} c^\dagger_{k \downarrow}c_{q \downarrow} = -n_{q \downarrow}\sum_{kk^\prime,m}\frac{J^\downarrow_{m} J^t_m c^\dagger_{k \downarrow}c_{k^\prime\uparrow} \ket{m+1}\bra{m}}{\omega_{m, \downarrow} - \frac{D}{2} - \frac{J}{2}(m)}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J^\sigma_{m} = -\frac{\left( J^\sigma_m \right) ^2 + \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - D/2 + J/4}
+	\Delta J^\sigma_{m} = -\frac{\left( J^\sigma_m \right) ^2 + \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J^+_m = -\frac{1}{2}\frac{\sum_\sigma \left( J^\sigma_m \right) ^2 + \sum_\sigma \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - D/2 + J/4} = -\frac{J^2}{4}\frac{S(S+1)}{\omega - D/2 + J/4}
+	\Delta J^+_m = -\frac{1}{2}\frac{\sum_\sigma \left( J^\sigma_m \right) ^2 + \sum_\sigma \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{J^2}{4}\frac{S(S+1)}{\omega - \frac{D}{2} + \frac{J}{4}}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J^-_m = -\frac{1}{2}\frac{\left( J^t_{m-1} \right) ^2 - \left(J^t_{m}\right) ^2}{\omega - D/2 + J/4} = -\frac{1}{4}\frac{m J^2}{\omega - D/2 + J/4}
+	\Delta J^-_m = -\frac{1}{2}\frac{\left( J^t_{m-1} \right) ^2 - \left(J^t_{m}\right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{4}\frac{m J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J^z = -\frac{1}{2}\frac{J^2}{\omega - D/2 + J/4}
+	\Delta J^z = -\frac{1}{2}\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J^t_m = - \frac{J^t_m \left( J^\downarrow_m + J^\uparrow_{m+1} \right) }{\omega - D/2 + J/4} = -\frac{1}{2}\frac{J^t_m J}{\omega - D/2 + J/4} \implies J^t = -\frac{1}{2}\frac{J^2}{\omega - D/2 + J/4}
+	\Delta J^t_m = - \frac{J^t_m \left( J^\downarrow_m + J^\uparrow_{m+1} \right) }{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{2}\frac{J^t_m J}{\omega - \frac{D}{2} + \frac{J}{4}} \implies J^t = -\frac{1}{2}\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
 \end{aligned}\end{equation}

### 2021-12-13 notes/multi-channel-urg.tex
corrected the anisotropic section with the modified fixed point

@@
 \begin{align}
-	\frac{\Delta J_+}{|\Delta D|} = \frac{J_+^2 \rho}{D - J_+/4} - \frac{\rho^2 J_+}{8}\left[\frac{(K-1)J_+^2}{D - J_+/4} + \frac{J_-^2}{D - J_-/4}\right]\\
-	\frac{\Delta J_-}{|\Delta D|} = \frac{J_-^2 \rho}{D - J_-/4} - \frac{\rho^2 J_-}{8}\left[\frac{(K-1)J_+^2}{D - J_+/4} + \frac{J_-^2}{D - J_-/4}\right]
-\end{align}
-Setting \(J_+ = J_-\) leads to the critical fixed point at \(J_+^* = J_-^* = J_* = \frac{8}{K \rho}\).
+	\frac{\Delta J_+}{|\Delta D|} = \frac{J_+^2 \rho}{D - J_+/4} - \frac{\rho^2 J_+}{2}\left[\frac{(K-1)J_+^2}{D - J_+/4} + \frac{J_-^2}{D - J_-/4}\right]\\
+	\frac{\Delta J_-}{|\Delta D|} = \frac{J_-^2 \rho}{D - J_-/4} - \frac{\rho^2 J_-}{2}\left[\frac{(K-1)J_+^2}{D - J_+/4} + \frac{J_-^2}{D - J_-/4}\right]
+\end{align}
+Setting \(J_+ = J_-\) leads to the critical fixed point at \(J_+^* = J_-^* = J_* = \frac{2}{K \rho}\).
 We now perturb around this fixed point by defining new variables \(j_\pm = J_\pm - J_*\).
@@
 \begin{align}
-	\frac{\Delta j_+}{|\Delta D|} &= \frac{\rho J_+}{D - J_*/4}\left[J_+ - \frac{\rho}{8}\left[(K-1)J_+^2 + J_-^2\right]\right]\\
+	\frac{\Delta j_+}{|\Delta D|} &= \frac{\rho J_+}{D - J_*/4}\left[J_+ - \frac{\rho}{2}\left[(K-1)J_+^2 + J_-^2\right]\right]\\
 				      &= \frac{\rho J_+}{D - J_*/4}\left[j_+ + J_*- \frac{1}{K J_*}\left[(K-1)\left(J_* + j_+\right)^2 + \left(J_* + j_-\right)^2\right]\right]\\
@@
 				      &= \frac{\rho J_+}{K J_*\left(D - J_*/4\right)}\left[-\left(K - 2\right)J_*j_+ - (K-1)j_+^2 - j_-^2 - 2J_* j_-\right]\\
-	\frac{\Delta j_-}{|\Delta D|} &= \frac{J_- \rho}{D - J_*/4}\left[J_- - \frac{\rho}{8}\left[(K-1)J_+^2 + J_-^2\right]\right]\\
+	\frac{\Delta j_-}{|\Delta D|} &= \frac{J_- \rho}{D - J_*/4}\left[J_- - \frac{\rho}{2}\left[(K-1)J_+^2 + J_-^2\right]\right]\\
 				      &= \frac{J_- \rho}{K J_*\left(D - J_*/4\right)}\left[K\left(J_*j_- + J_*^2\right) - (K-1)\left(J_*^2 + j_+^2 + 2J_* j_+\right) - \left(J_*^2 + j_-^2 + 2J_* j_-\right)\right]\\
@@
 \begin{align}
-	J_+ = J_* + \frac{J_*}{K-1} = \frac{\frac{8}{K \rho} K}{K - 1} = \frac{8}{(K-1)\rho}
-\end{align}
-In other words, the \(K\) channel fixed point flows to the \(K-1\) channel fixed point.
+	J_{+,*} = J_* + \frac{J_*}{K-1} = \frac{\frac{2}{K \rho} K}{K - 1} = \frac{2}{(K-1)\rho}
+\end{align}
+In other words, the \(K\) channel fixed point flows to the \(K-1\) channel fixed point. This is shown numerically in fig.~\ref{K_to_K-1}.
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.4\textwidth]{../numerics/K to K-1.pdf}
+	\caption{Flow of \(J_-\) to zero when \(j_< 0\) and \(J_+\) to the fixed point of the \(K-1\) channel Kondo model.}
+	\label{K_to_K-1}
+\end{figure}
 
@@
 	\includegraphics[width=0.45\textwidth]{../numerics/irr_Jp_K=50.pdf}
-	\caption{Flow of the coupling \(J_+\) when \(j_+ < 0\) for two values of \(K\)}
+	\caption{Flow of the couplings \(J_+\) when \(j_+ < 0\) when \(j_- > 0, j_+ < 0\), for two values of \(K\).}
 	\label{irrel_Jplus}

### 2021-12-14 notes/mck_urg.tex
completed RG of spin-S impurity, RG equations are independent of S

--- 2021-12-13 notes/multi-channel-urg.tex
@@
 
-\section{Importance of the star graph in determining the physics of the problem}
+\section{Role of the star graph in determining the physics of the problem}
 Methods like CFT, Bethe ansatz, bosonization and NRG~\cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991,emery_kivelson,vondelft_prl_1998} have shown that \textit{neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the multi-channel Kondo models}.
@@
 This new interaction is generated by the minimal hopping that exists between the zeroth site and the first sites of each of the conduction bath channels, and is characterised by the small superexchange coupling \(J^\prime \sim t^2/J\).
-\textit{The conclusion is that a large \(J\) model with a central spin-half object can be transformed into a small \(J^\prime\) model with a central spin-\(\left(\frac{K-1}{2}\right)\) object}.
+\textit{The conclusion is that a large \(J\) model with a central spin-half object can be transformed into a small \(J^\prime\) overscreened model with a central spin-\(\left(\frac{K-1}{2}\right)\) object}.
 This is shown schematically in Fig.~\ref{duality_fig}.
@@
 
-\clearpage
 \section{URG equations for the multi-channel Kondo model}
@@
 \subsection{Next-to-leading order renormalization}
-\begin{align*}
-	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X}_\text{particle sector}\\
+\begin{align}
+	\label{3rd_oder_terms}
+	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X}_\text{particle sector}\nonumber\\
 	+ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T + T^\dagger c \frac{1}{\omega - H_D} c^\dagger T \frac{1}{\omega - H_D} H_X}_\text{hole sector}
-\end{align*}
+\end{align}
 A general term of this expression has three sets of spin operators coming from \(c^\dagger T, H_X\) and \(T^\dagger c\).
@@
 \begin{align}
+	\label{term2_sum}
 	-\sum_k \frac{1 - \hat n_{k\alpha l_1}}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2} = \frac{1}{2}\frac{\rho}{\omega - \frac{D}{2} + \frac{J}{4}}
@@
 	\includegraphics[width=0.8\textwidth]{../numerics/rg_flow_K=2.pdf}
-	\caption{Attractive flows towards \(J_1^*\)}
+	\caption{Flow of \(J\) towards the attractive fixed point \(J_1^*\), both from \(J<J_1^*\) (left panel) as well as from \(J>J_1^*\) (right panel).}
 	\label{rg_flow_K-2}
@@
 
-\section{URG equations for the multi-channel spin-\(S\) Kondo model}
+\section{URG equations for the overscreened spin-\(S\) multi-channel Kondo model}
 The leading order renormalization is the same as the single-channel model, and is shown in the appendix. Following that calculation, the Hamiltonian we will work with is 
 \begin{equation}\begin{aligned}
+	\label{H_spin_S}
     H = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{m=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_m \ket{m}\bra{m} c^\dagger_{k \sigma}c_{l \sigma} + \sum_{kl} \sum_{m=-S}^{S-1} J^t_{m} \left(\ket{m+1}\bra{m} s^-_{kl}  + \text{h.c.}\right)
@@
 
-The next order renormalization is of the form
-\begin{equation}\begin{aligned}
-	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term (particle sector)} ~+~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term (hole sector)}
-\end{aligned}\end{equation}
-
-Before we start, we will make another simplification. A general term of \(\Delta H\) will be of the form
+Following eq.~\ref{3rd_oder_terms}, the next order renormalization is of the form
+\begin{equation}\begin{aligned}
+	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X}_\text{particle sector}\nonumber\\
+	+ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T + T^\dagger c \frac{1}{\omega - H_D} c^\dagger T \frac{1}{\omega - H_D} H_X}_\text{hole sector}
+\end{aligned}\end{equation}
+
+Because of eq.~\ref{H_spin_S}, the first term of the particle sector will be of the form
 \begin{equation}\begin{aligned}
@@
 
-The various terms in each sector can be represented as \(a|b|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three stages.
+Similarly, using arguments identical to those used in the spin-\(\frac{1}{2}\) URG derivation (eq.~\ref{term2_sum}), the second term in the particle sector takes the form
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4}\sum_{k_1,k_2,l_2,\sigma_1\sigma_2}\lambda_{1}\lambda_{3}\lambda_{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}
+\end{aligned}\end{equation}
+
+The first group of terms in the particle sector can be represented as \(a|b^\prime|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three stages.
+The \(\prime\) on \(b\) indicates that it is the state of the electrons \textit{not being decoupled}.
+The second group of terms are therefore represented as \(a|b|c^\prime\), because in this group, the interaction \(H_X\) between the electrons not being decoupled occur at the very end.
+
 We will only calculate the terms in the particle sector, the ones in hole sector will be equal to these because of particle-hole symmetry.
-\paragraph{\(z|z|z\)}
+\paragraph{\(z|z^\prime|z\)}
 \begin{equation}\begin{aligned}
@@
 
-\paragraph{\(-|z|+\)}
+\paragraph{\(z|z|z^\prime\)}
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_\beta \sum_{m}\sum_{k_1,k_2,l_2,\sigma} \left(J^\beta_m\right)^2 J^\sigma_m \ket{m}\bra{m}c^\dagger_{k_1 \sigma, l_2}c_{k_2 \sigma,l_2}
+\end{aligned}\end{equation}
+
+\paragraph{\(-|z^\prime|+\)}
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-\paragraph{\(+|z|-\)}
+
+\paragraph{\(-|+|z^\prime\)}
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2,\sigma} \left( J^t_m \right) ^2 J^\sigma_{m+1} \ket{m+1}\bra{m+1}c^\dagger_{k_1 \sigma, l_2}c_{k_2 \sigma,l_2}
+\end{aligned}\end{equation}
+
+\paragraph{\(+|z^\prime|-\)}
 \begin{equation}\begin{aligned}
@@
 
-\paragraph{\(z|+|z\)}
+\paragraph{\(+|-|z^\prime\)}
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2,\sigma} \left( J^t_m \right) ^2 J^\sigma_{m} \ket{m}\bra{m}c^\dagger_{k_1 \sigma, l_2}c_{k_2 \sigma,l_2}
+\end{aligned}\end{equation}
+
+\paragraph{\(z|+^\prime|z\)}
 \begin{equation}\begin{aligned}
@@
 
-\paragraph{\(z|-|z\)}
+\paragraph{\(z|-^\prime|z\)}
 \begin{equation}\begin{aligned}
@@
 
-\paragraph{\(+|+|-\)}
+\paragraph{\(+|+^\prime|-\)}
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-\paragraph{\(+|-|-\)}
+\paragraph{\(+|-^\prime|-\)}
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-\paragraph{\(-|-|+\)}
+\paragraph{\(-|-^\prime|+\)}
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-\paragraph{\(-|+|+\)}
+\paragraph{\(-|+^\prime|+\)}
 \begin{equation}\begin{aligned}
 	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} \left( J^t_{m} \right)^2 J^t_{m+1}\ket{m+1}\bra{m+2}c^\dagger_{k_1 \uparrow, l_2}c_{k_2 \downarrow,l_2}
+\end{aligned}\end{equation}
+
+\paragraph{\(z|z|+^\prime\)}
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_\beta \sum_{m}\sum_{k_1,k_2,l_2}\left(J^\beta_m\right)^2 J^t_m \ket{m}\bra{m+1}c^\dagger_{k_1 \uparrow, l_2}c_{k_2 \downarrow,l_2}
+\end{aligned}\end{equation}
+
+\paragraph{\(z|z|-^\prime\)}
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_\beta \sum_{m}\sum_{k_1,k_2,l_2}\left(J^\beta_m\right)^2 J^t_m \ket{m+1}\bra{m} c^\dagger_{k_1 \uparrow, l_2}c_{k_2 \downarrow,l_2}
+\end{aligned}\end{equation}
+
+\paragraph{\(+|-|+^\prime\)}
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} \left( J^t_{m} \right)^3 \ket{m}\bra{m+1}c^\dagger_{k_1 \uparrow, l_2}c_{k_2 \downarrow,l_2}
+\end{aligned}\end{equation}
+
+\paragraph{\(+|-|-^\prime\)}
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} J^t_m \left( J^t_{m+1} \right)^2 \ket{m+1}\bra{m}c^\dagger_{k_1 \downarrow, l_2}c_{k_2 \uparrow,l_2}
+\end{aligned}\end{equation}
+\paragraph{\(-|+|-^\prime\)}
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} \left( J^t_{m} \right)^3\ket{m+1}\bra{m}c^\dagger_{k_1 \downarrow, l_2}c_{k_2 \uparrow,l_2}
+\end{aligned}\end{equation}
+
+\paragraph{\(-|+|+^\prime\)}
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m}\sum_{k_1,k_2,l_2} \left( J^t_{m} \right)^2 J^t_{m+1}\ket{m+1}\bra{m+2}c^\dagger_{k_1 \uparrow, l_2}c_{k_2 \downarrow,l_2}
+\end{aligned}\end{equation}
+
+The terms \(a,l\) and \(j\) cancel out \(b,r\) and \(p\) respectively. The terms \(b\) through \(f\) renormalize \(J^\sigma_m\):
+\begin{equation}\begin{aligned}
+	\Delta J^\sigma_m = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\left[\left( J^t_{m-1} \right)^2 J^\sigma_m + \left( J^t_m \right)^2 J^\sigma_m - \left( J^t_{m-1} \right)^2 J^\sigma_{m-1} - \left(J^t_m\right)^2 J^\sigma_{m+1} \right] = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3 m \sigma
+\end{aligned}\end{equation}
+Since we had defined \(J^\sigma_m \equiv \frac{1}{2}J m \sigma\), we have \(\Delta J = \frac{2}{m\sigma}\Delta J^\sigma_m\), and we get
+\begin{equation}\begin{aligned}
+	\Delta_\text{p sector} J = \frac{1}{4}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3
+\end{aligned}\end{equation}
+
+Since we started with an \(SU(2S+1)\times SU(2K+1)\) symmetric model, we can recover the RG equation for \(J\) from the transverse part as well.
+The transverse coupling \(J^t_m\) is renormalized by the terms \(g,i,m\) and \(o\).
+\begin{equation}\begin{aligned}
+	\Delta J^t_m = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\left[J^t_m\sum_\beta J^\beta_m\left(J^\beta_m - J^\beta_{m+1}\right) + J^t_m \left\{ \left( J^t_m \right) ^2 - \left( J^t_{m+1} \right) ^2 \right\} \right] = \frac{1}{4}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}} J^2 J^t_m
+\end{aligned}\end{equation}
+Using \(J^t_m \equiv J\lambda_m\), we have
+\begin{equation}\begin{aligned}
+	\Delta_\text{h sector} J = \frac{1}{4}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}} J^3
+\end{aligned}\end{equation}
+which is the same as the one previously obtained from the Ising part.
+The conclusion therefore is that the renormalization in the Kondo coupling for the overscreened models is independent of the impurity spin multiplicity.
+
+The hole sector gives an identical contribution to the RG equation, so that the total renormalization in the Kondo coupling for an overscreened spin-\(S\) impurity is
+\begin{equation}\begin{aligned}
+	\Delta J = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}} J^3
 \end{aligned}\end{equation}
@@
 \bibliographystyle{apsrev4-1}
-\bibliography{multi-channel-urg}
+\bibliography{mck_urg}
 

### 2021-12-14 notes/mck_urg.tex
completed the duality transformation

@@
 \section{Introduction of the Hamiltonian and its zero mode}
-The isotropic multi-channel Kondo model~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact} is described by the Hamiltonian
+The isotropic multi-channel Kondo (MCK) model~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact} is described by the Hamiltonian
 \begin{align}
@@
 \section{Role of the star graph in determining the physics of the problem}
-Methods like CFT, Bethe ansatz, bosonization and NRG~\cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991,emery_kivelson,vondelft_prl_1998} have shown that \textit{neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the multi-channel Kondo models}.
+Methods like CFT, Bethe ansatz, bosonization and NRG~\cite{affleck_1991_overscreen,Tsvelick_Weigmann_mchannel_1984,Gan_mchannel_1994,pang_cox_1991,emery_kivelson,vondelft_prl_1998} have shown that \textit{neither the weak coupling nor the strong coupling Hamiltonians are stable fixed points of the MCK models}.
 Instead, the RG flows converge to an intermediate coupling fixed point.
@@
 At strong coupling \(J \to \infty^-\), the outer spin-half objects tightly bind with the central spin-half object to form a single spin.
-The remaining states in the conduction bath channels form new zero modes and create a new outer ring of spins that interact with the new central spin, \textit{leading to another multi-channel Kondo problem with a new and small exchange coupling which is RG relevant, so the strong coupling fixed point \(J \to \infty^-\) is unstable}.
-This shows that it can be argued, even from the zero mode, that the two limits of the model cannot be stable fixed points, and the actual fixed point has to lie somewhere in between.
-
-Just like the full Hamiltonian, the star graph conserves the total spin \(S^z\), and this leads to a \(K-\)fold degeneracy in the ground state of the \(K-\)channel zero mode.
+The remaining states in the conduction bath channels form new zero modes and create a new outer ring of spins that interact with the new central spin, \textit{leading to another MCK problem with a new and small exchange coupling which is RG relevant, so the strong coupling fixed point \(J \to \infty^-\) is unstable}.
+This shows that it can be argued, even from the star graph, that the two limits of the model cannot be stable fixed points, and the actual fixed point has to lie somewhere in between.
+
+Just like the full Hamiltonian, the star graph conserves the total spin \(S^z\), and this leads to a \(K-\)fold degeneracy in the ground state of the \(K-\)channel star graph.
 Since \(S^z\) commutes with the star graph, the ground states are eigenstates of \(S^z\) with distinct eigenvalues \(\frac{K+1}{2}, \frac{K-1}{2},\ldots,\frac{-K-1}{2}\).
@@
 
-The fact that the strong coupling fixed point can be seen as a new zero mode problem with a modifed central spin reveals the duality mentioned before.
+The fact that the strong coupling fixed point can be seen as a new star graph problem with a modifed central spin reveals the duality mentioned before.
 At strong coupling \(J \gg 1\), we can obtain a new star graph by defining a new spin-\(\left(\frac{K-1}{2}\right)\) object from the \(K-\)fold degenerate ground state manifold and letting this interact with the new outer spins formed by the remaining sites of the conduction channels.
@@
 At large \(J\), the red circle binds with the green circles to form an effective spin \(\frac{K-1}{2}\) object (yellow) that interacts with the remaining spin of the conduction bath (blue circles).
-The fixed point consists of the red (purple) and green (yellow) circles binding to form a doubly degenerate ground state (orange) that interacts with the zero mode of the remaining sites (brown) through the hopping.}
+The fixed point consists of the red (purple) and green (yellow) circles binding to form a doubly degenerate ground state (orange) that interacts with the star graph of the remaining sites (brown) through the hopping.}
 	\label{duality_fig}
@@
 \section{Effect of anisotropy on RG flows}
-For a general anisotropic multi-channel Kondo, the Hamiltonian is
+For a general anisotropic MCK, the Hamiltonian is
 \begin{align}
@@
 
+\section{Strong-weak duality of the multi-channel Kondo RG flows}
+If we start from a strong coupling \((J \to \infty)\) MCK Hamiltonian
+\begin{equation}\begin{aligned}
+	\label{strong_ham}
+	H(J) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + J \vec{S_d}\cdot\vec{s}_\text{tot}
+\end{aligned}\end{equation}
+where \(\vec s_\text{tot}\) is the total spin \(\sum_l \sum_{kk^\prime \alpha\beta} \vec \sigma_{\alpha\beta}c^\dagger_{k\alpha,l}c_{k^\prime\beta,l}\) of all the zero modes, the ground states of the star graph eq.~\ref{zeromode_ham} act as a good starting point for a perturbative expansion.
+There are \(K\) such ground states for a \(K-\)channel model, labelled by the \(K\) values of the total spin angular momentum \(S^z = S_d^z + s_\text{tot}^z\), \(S^z = -\frac{K+1}{2}, -\frac{K-1}{2}, \ldots, \frac{K-1}{2}\).
+To leverage the large coupling, one can define a composite impurity out of this \(K-\)fold degenerate ground state.
+That is, just like a spin-\(\frac{1}{2}\) impurity is essentially a degenerate two-level system (at least as long as it is decoupled), one can similarly define a composite spin that is \(K-\)fold degenerate, and hence has \(\mathbb{S}_d = \frac{K-1}{2}\).
+The states of this spin are defined as
+\begin{equation}\begin{aligned}
+	\mathbb{S}_d^z \ket{S^z} = S^z \ket{S^z}, &&\mathbb{S}_d^\pm \ket{S^z} \sim \ket{S^z \pm 1}
+\end{aligned}\end{equation}
+The excited states of the star graph can be used to define bosons \cite{kroha_kolf_2007}, and the hopping into the lattice can then be re-written using these bosons.
+One can then remove the single-particle hoping between the zero modes and the first sites using a Schrieffer-Wolff transformation in the small coupling \(J^\prime = \gamma \frac{4t^2}{J}\), and generate an exchange-coupling between new composite spin \(\vec {\mathbb{S}}_d\) and the new zero modes formed out of the remaining sites in the lattice \cite{kroha_kolf_2007} (by remaining, we mean those real space sites that have not been consumed into forming the composite spin).
+The new Hamiltonian, characterised by the small superexchange  coupling \(J^\prime\), has the form
+\begin{equation}\begin{aligned}
+	H^\prime(J^\prime) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + J^\prime \vec{\mathbb{S}_d}\cdot\vec{s^\prime}_\text{tot}
+\end{aligned}\end{equation}
+The prime on \(s_\text{tot}\) indicates that is the formed by the new zero modes.
+This Hamiltonian is very similar to the one in eq.~\ref{strong_ham}, and that is the essence of the strong-weak duality: One can go from the strong coupling spin-\(\frac{1}{2}\) MCK model to a weak coupling spin-\(\frac{K-1}{2}\) MCK model.
+For the case of \(K=2\), both \(S_d\) and \(\mathbb{S}_d\) are spin-\(\frac{1}{2}\) objects, and the models are said to be self-dual.
+
+One important consequence of the duality is that the RG equations are also dual; while the strong coupling model has an irrelevant coupling \(J\) that flows down to the intermediate fixed point \(J^*\), the weak coupling model has a relevant coupling \(J^\prime\) that flows up to the same fixed point \({J^\prime}^* = J^*\).
+From the RG equation for the general spin-\(S\) MCK model, we know that \({J^\prime}^* = \frac{2}{K \rho^\prime}\), where \(\rho^\prime\) is the DOS for the bath of the weak coupling Hamiltonian.
+This constrains the form of the scaling factor \(\gamma\):
+\begin{equation}\begin{aligned}
+	{J^\prime}^* = \frac{\gamma 4t^2}{J^*} = \frac{2}{K \rho^\prime} \implies \gamma = \frac{1}{4t^2} {J^*}^2 = \frac{1}{K^2 t^2 \rho \rho^\prime}
+\end{aligned}\end{equation}
+
 \section{MFL and orthogonality catastrophe in low-energy excitations of 2-CKM}
@@
 For this, we will perform a perturbative treatment of the hopping at strong coupling \(J \to \infty\) where the perturbative coupling \(t^2/J\) is arbitrarily small and again obtain Eq.~\ref{nfl_terms}.
-Such a change from the strong coupling model with parameter \(J\) to a weak-coupling model with parameter \(t^2/J\) amounts to a duality transformation~\cite{kroha_kolf_2007,zitko_fabrizio_2017}.
-It can be shown that the duality transformation leads to an identical multi-channel Kondo model~\cite{kroha_kolf_2007} (self-duality), which implies we can have identical RG flows, and our transformation simply extracts the NFL piece from the dual model.
+Such a change from the strong coupling model with parameter \(J\) to a weak coupling model with parameter \(t^2/J\) amounts to a duality transformation~\cite{kroha_kolf_2007,zitko_fabrizio_2017}.
+It can be shown that the duality transformation leads to an identical MCK model~\cite{kroha_kolf_2007} (self-duality), which implies we can have identical RG flows, and our transformation simply extracts the NFL piece from the dual model.
 The self-duality also implies that the critical intermediate-coupling fixed point is unique and can be reached from either of the models.
@@
 Such terms were absent in the similar perturbative expansion of the single-channel Kondo model, because there was no multiply-degenerate ground state manifold that allowed scattering.
-This line of argument shows that the extra degeneracy of the ground state subspace that comes about when one upgrades from the single-channel Kondo model to the multi-channel Kondo models is at the heart of the NFL behaviour, and the orthogonality catastrophe should be a general feature of all multi-channel Kondo models, even though we have demonstrated this only for the two-channel case.
+This line of argument shows that the extra degeneracy of the ground state subspace that comes about when one upgrades from the single-channel Kondo model to the MCK models is at the heart of the NFL behaviour, and the orthogonality catastrophe should be a general feature of all MCK models, even though we have demonstrated this only for the two-channel case.
 
@@
 The difference is not only in the value but also in the origin.
-Eq.~\ref{res_entropy} describes the thermal entropy coming purely from the quantum mechanical degeneracy of the star graph problem (which is the zero mode of the full multi-channel Kondo problem), while the result Eq.~\ref{cft_entropy} presumably arises from the lowest-lying excitations on top of the zero mode arising from the conduction bath \(k-\)states.
+Eq.~\ref{res_entropy} describes the thermal entropy coming purely from the quantum mechanical degeneracy of the star graph problem (which is the star graph of the full MCK problem), while the result Eq.~\ref{cft_entropy} presumably arises from the lowest-lying excitations on top of the star graph arising from the conduction bath \(k-\)states.
 Another difference lies in the fact that while Eq.~\ref{res_entropy} holds true independent of system size, Eq.~\ref{cft_entropy} is correct only in the thermodynamic limit and only if the limit of system size \(L \to \infty\) is taken prior to taking the limit of temperature \(T \to 0\)~\cite{Gan_Andrei_Coleman_1993,rozhkov_1998,vondelft_prl_1998}.
-We note however that the entropy coming from the degeneracy is larger than that coming from the excitations (fig.~\ref{entropy_comparison}), and consequently plays a very important role in the physics of the multi-channel Kondo problem, being responsible for the NFL physics and the critical behaviour near the fixed point.
+We note however that the entropy coming from the degeneracy is larger than that coming from the excitations (fig.~\ref{entropy_comparison}), and consequently plays a very important role in the physics of the MCK problem, being responsible for the NFL physics and the critical behaviour near the fixed point.
 

### 2021-12-14 notes/mck_urg.tex
reinserted impurity free energy non-analyticity

@@
 
-\section{Non-analyticity in the free energy}
+\section{Non-analyticity in the free energy (Discontinuity in magnetization)}
+
+\subsection{Field coupled to impurity}
 For \(K>1\), the Gibbs free energy at \(T=0\) becomes non-analytic under insertion of a magnetic field on the impurity. The thermal free energy is given by
-\begin{align}
+\begin{equation}\begin{aligned}
 	F(h) = -\frac{1}{\beta}\ln Z(h) = -\frac{1}{\beta}\ln\sum_{E_n}e^{-\beta E_n}
-\end{align}
-At \(T \to 0\), only the most negative energy \(E_\text{min}\) survives. Assuming a \(d^\prime_\text{gs}-\)fold degenerate ground state for \(h \neq 0\), the zero temperature free energy becomes
-\begin{align}
-	F(h\neq 0, T\to 0) = -\frac{1}{\beta}\ln d^\prime_\text{gs}e^{-\beta E_\text{min}} = E_\text{min}- k_B T\ln d^\prime_\text{gs}
-\end{align}
-In the star graph Hamiltonian with \(K-\)channels and a global magnetic field on the impurity
-\begin{align}
-	H = J \vec{S_d}\cdot\vec{s}_\text{tot} + h\left(S_d^z + s^z_\text{tot}\right) ~,
-\end{align}
-the energy eigenvalues for a particular value of \(s_\text{tot}=M\) are given by
-\begin{align}
-	(a) \quad&\frac{J}{2}M \pm h\left(M + \frac{1}{2}\right)\\
-	(b) \quad&-\frac{J}{4}\pm \frac{J}{2}\left(M + \frac{1}{2}\right) + h\left( m + \frac{1}{2} \right), m \in \left[-M, M-1\right] 
-\end{align}
-For small \(h\), the ground state will be \(-\frac{J}{4}- \frac{J}{2}\left(M + \frac{1}{2}\right) + h\left(m_\text{min} + \frac{1}{2} \right)\) for a particular value \(m_\text{min}\) that minimizes this energy.
-This specific value will depend on the sign of \(h\):
-\begin{align}
-	m_\text{min} = \begin{cases}
-		-M, & h >0\\
-		M-1,& h< 0
+\end{aligned}\end{equation}
+At \(T \to 0\), only the most negative energy \(E_\text{min}\) survives. Assuming a non-degenerate ground state for \(h \neq 0\), the zero temperature free energy becomes
+\begin{equation}\begin{aligned}
+	F(h\neq 0, T\to 0) = -\frac{1}{\beta}\ln e^{-\beta E_\text{min}} = E_\text{min}
+\end{aligned}\end{equation}
+In the star graph Hamiltonian with \(K-\)channels and in the presence of a field on the impurity (eq.~\ref{stargraph_field_hamiltonian}), the energy eigenvalues for a particular value of \(s_\text{tot}\) are given in eq.~\ref{stargraph_spectrum}.
+Within a particular subspace \(M\), the ground state energy will be one of the negative eigenvalues:
+\begin{equation}\begin{aligned}
+	\lambda^{M,h}_{m, -}= -J/4 - \frac{1}{2}\sqrt{J^2x^M_{m}/4 + \alpha^2} = -J/4 - \frac{1}{2}\sqrt{J^2(M+1/2)^2 + h^2 + 2hJ(m+1/2)}
+\end{aligned}\end{equation}
+The minimum eigenvalue is obtained by maximizing \(h(m+1/2)\).
+For \(h>0\), the ground state is renormalized for the most positive value of \(m\), \(M-1\).
+On the other hand, for \(h<0\), it occurs for \(m=-M\), because that is the most negative value it can take.
+Among all the values of \(M\), the global ground state is at the largest value of \(M\), \(K/2\).
+Therefore, the minimal energy eigenvalue is
+\begin{equation}\begin{aligned}
+	E_\text{min}(h) = \begin{cases}
+		-J/4 - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 + hJ(K-1)}, & h>0\\
+		-J/4 - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 - hJ(K-1)}, & h<0\\
 	\end{cases}
-\end{align}
-which means \(E_\text{min} = -\frac{J}{2}\left( M + 1 \right) - |h|\left(M - \frac{1}{2}\right)\). We also know, from Eq.~\ref{extra_degen}, that \(d^\prime_\text{gs} = {}^{K-1}C_{K/2 - K/2} = 1\).
+\end{aligned}\end{equation}
 The free energy for a non-zero field is therefore
-\begin{align}
-	F(h\neq 0, T\to 0) = -\frac{J}{2}\left( M + 1 \right) - |h|\left(M - \frac{1}{2}\right)
-\end{align}
-
+\begin{equation}\begin{aligned}
+	F(h\neq 0, T\to 0) = -J/4 - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 + |h|J(K-1)}
+\end{aligned}\end{equation}
 The first derivative of the free energy with respect to the field gives
-\begin{align}
-	F^\prime(h\neq 0, T\to 0) = -\text{sign}(h)\left(M - \frac{1}{2}\right)
-\end{align}
+\begin{equation}\begin{aligned}
+	F^\prime(h\neq 0, T\to 0) =- \frac{1}{2}\frac{2h + J(K-1)\text{sign}(h)}{2\sqrt{J^2(K+1)^2/4 + h^2 + |h|J(K-1)}}
+\end{aligned}\end{equation}
 There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get
-\begin{align}
-	F^\prime(h \to 0^\pm, T\to 0) = \mp\left(M - \frac{1}{2}\right) = \mp \frac{1}{2}\left( K - 1 \right) 
-\end{align}
+\begin{equation}\begin{aligned}
+	F^\prime(h \to 0^\pm, T\to 0) = \mp \frac{1}{2}\frac{(K-1)}{(K+1)}
+\end{aligned}\end{equation}
 
@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{../numerics/free_energy_nonanaliticity.pdf}
+	\includegraphics[width=0.6\textwidth]{../numerics/disc_mag_imp.pdf}
+	\caption{Non-analytic free energy for \(K>1\) and analytic free energy for \(K=1\).}
+\end{figure}
+
+The non-analyticity for \(K>1\) occurs because the magnetic field is able to flip the ground state.
+For example, for \(K=2\), the states in question are \(\ket{M=1, m=-1,0}\).
+For \(h>0\), the ground state occurs in the subspace \(\ket{S_d^z=1/2, m=-1},\ket{S_d^z=-1/2,m=0}\).
+If we now flip the magnetic field, the ground state subspace flips to \(\ket{S_d^z=1/2, m=0},\ket{S_d^z=-1/2,m=1}\).
+Instead, if we look at the case of \(K=1\), the ground state is in the subspace of \(\ket{S_d^z=1/2,m=-1/2},\ket{S_d^z=-1/2, m=1/2}\), and since there is only this one subspace, the ground state is independent of the field.
+From this discussion, it is clear that the non-analyticity appears because there are multiple values of \(m \in [-M, M-1]\) in the ground state manifold, which means that it is the ground state degeneracy that causes the non-analyticity.
+
+\subsection{Global field}
+For \(K>1\), the Gibbs free energy at \(T=0\) becomes non-analytic under insertion of a magnetic field on the impurity. The thermal free energy is given by
+\begin{align}
+	F(h) = -\frac{1}{\beta}\ln Z(h) = -\frac{1}{\beta}\ln\sum_{E_n}e^{-\beta E_n}
+\end{align}
+At \(T \to 0\), only the most negative energy \(E_\text{min}\) survives. Assuming a \(d^\prime_\text{gs}-\)fold degenerate ground state for \(h \neq 0\), the zero temperature free energy becomes
+\begin{align}
+	F(h\neq 0, T\to 0) = -\frac{1}{\beta}\ln d^\prime_\text{gs}e^{-\beta E_\text{min}} = E_\text{min}- k_B T\ln d^\prime_\text{gs}
+\end{align}
+In the star graph Hamiltonian with \(K-\)channels and a global magnetic field on the impurity
+\begin{align}
+	H = J \vec{S_d}\cdot\vec{s}_\text{tot} + h\left(S_d^z + s^z_\text{tot}\right) ~,
+\end{align}
+the energy eigenvalues for a particular value of \(s_\text{tot}=M\) are given by
+\begin{align}
+	(a) \quad&\frac{J}{2}M \pm h\left(M + \frac{1}{2}\right)\\
+	(b) \quad&-\frac{J}{4}\pm \frac{J}{2}\left(M + \frac{1}{2}\right) + h\left( m + \frac{1}{2} \right), m \in \left[-M, M-1\right] 
+\end{align}
+For small \(h\), the ground state will be \(-\frac{J}{4}- \frac{J}{2}\left(M + \frac{1}{2}\right) + h\left(m_\text{min} + \frac{1}{2} \right)\) for a particular value \(m_\text{min}\) that minimizes this energy.
+This specific value will depend on the sign of \(h\):
+\begin{align}
+	m_\text{min} = \begin{cases}
+		-M, & h >0\\
+		M-1,& h< 0
+	\end{cases}
+\end{align}
+which means \(E_\text{min} = -\frac{J}{2}\left( M + 1 \right) - |h|\left(M - \frac{1}{2}\right)\). We also know, from Eq.~\ref{extra_degen}, that \(d^\prime_\text{gs} = {}^{K-1}C_{K/2 - K/2} = 1\).
+The free energy for a non-zero field is therefore
+\begin{align}
+	F(h\neq 0, T\to 0) = -\frac{J}{2}\left( M + 1 \right) - |h|\left(M - \frac{1}{2}\right)
+\end{align}
+
+The first derivative of the free energy with respect to the field gives
+\begin{align}
+	F^\prime(h\neq 0, T\to 0) = -\text{sign}(h)\left(M - \frac{1}{2}\right)
+\end{align}
+There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get
+\begin{align}
+	F^\prime(h \to 0^\pm, T\to 0) = \mp\left(M - \frac{1}{2}\right) = \mp \frac{1}{2}\left( K - 1 \right) 
+\end{align}
+
+The first derivative of the impurity free energy is therefore discontinuous as \(h\to 0\); it goes to different values depending on the direction in which we take the limit.
+The only case where it is not analytic is when \(K=1\); then the derivative goes to zero from both directions.
+This non-analyticity has also been verified numerically.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../numerics/disc_mag_global.pdf}
 	\caption{Non-analytic free energy for \(K>1\) and analytic free energy for \(K=1\).}

### 2021-12-14 notes/mck_urg.tex
added bath free energy non-analyticity

@@
 \begin{align}
+	\label{bath_field_ham}
 	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h s^z_\text{tot}
@@
 \begin{align}
-	\lambda_{m, \pm}^{M, h} &= -\frac{J}{4} + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2x^M_m + \left[(2m+1)h - \frac{J}{2}\right]^2 - 4m(m+1)(h^2 - J^2/4)} \\
-				&= -\frac{J}{4} + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2(M + \frac{1}{2})^2 + h^2 - (2m+1)Jh}	= -\frac{J}{4} + (2m+1)h/2 \pm \phi^M_m
-\end{align}
+	\lambda_{m, \pm}^{M, h} &= -\frac{J}{4} + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2x^M_m + \left[(2m+1)h - \frac{J}{2}\right]^2 - 4m(m+1)(h^2 - J^2/4)} \nonumber\\
+				&= -\frac{J}{4} + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2(M + \frac{1}{2})^2 + h^2 - (2m+1)Jh} \nonumber\\
+				&= -\frac{J}{4} + (2m+1)h/2 \pm \phi^M_m \label{bath_field_ens}
+\end{align}
+where \(\phi^M_m = \frac{1}{2}\sqrt{J^2(M + \frac{1}{2})^2 + h^2 - (2m+1)Jh}\).
 The eigenvalues of the terminal states are \(JM/2 \pm hM\). The partition function is
@@
 From this discussion, it is clear that the non-analyticity appears because there are multiple values of \(m \in [-M, M-1]\) in the ground state manifold, which means that it is the ground state degeneracy that causes the non-analyticity.
+
+\subsection{Field coupled to bath zero modes}
+Assuming a non-degenerate ground state for \(h \neq 0\), the zero temperature free energy becomes
+\begin{equation}\begin{aligned}
+	F(h\neq 0, T\to 0) = -\frac{1}{\beta}\ln e^{-\beta E_\text{min}} = E_\text{min}
+\end{aligned}\end{equation}
+In the star graph Hamiltonian with \(K-\)channels and in the presence of a field on the bath zero modes (eq.~\ref{bath_field_ham}), the energy eigenvalues for a particular value of \(s_\text{tot}\) are given in eq.~\ref{bath_field_ens}.
+For small field \(h\), the global ground state will lie in the subspace of \(s_\text{tot} = M_\text{max} = K/2\).
+The ground state energy will be one of the negative eigenvalues:
+\begin{equation}\begin{aligned}
+	\lambda^{M_\text{max},h}_{m, -} = -J/4 + \left( 2m+1 \right)\frac{h}{2} - \frac{1}{2}\sqrt{J^2(M_\text{max}+\frac{1}{2})^2 + h^2 - \left( 2m+1 \right) Jh}
+\end{aligned}\end{equation}
+The minimum eigenvalue is obtained by minimizing \(h(2m+1)\).
+For \(h>0\), the ground state is realized for the most negative value of \(m\), \(-M_\text{max}\).
+On the other hand, for \(h<0\), it occurs for \(m=M_\text{max}-1\), because that is the most positive value it can take.
+Therefore, the minimal energy eigenvalue is
+\begin{equation}\begin{aligned}
+	E_\text{min}(h) = \begin{cases}
+		-J/4 - \frac{h}{2}\left(K-1\right) - \frac{1}{2}\sqrt{\frac{1}{4}J^2(K+1)^2 + h^2 + \left(K-1\right) Jh}, & h>0\\
+		-J/4 + \frac{h}{2}\left(K-1\right) - \frac{1}{2}\sqrt{\frac{1}{4}J^2(K+1)^2 + h^2 - \left(K-1\right) Jh}, & h<0\\
+	\end{cases}
+\end{aligned}\end{equation}
+The free energy for a non-zero field is therefore
+\begin{equation}\begin{aligned}
+	F(h\neq 0, T\to 0) = -J/4 - \frac{|h|}{2}\left(K-1\right) - \frac{1}{4}\sqrt{J^2(K+1)^2 + 4h^2 + 4\left(K-1\right) J |h|}
+\end{aligned}\end{equation}
+The first derivative of the free energy with respect to the field gives
+\begin{equation}\begin{aligned}
+	F^\prime(h\neq 0, T\to 0) = - \frac{1}{2}(K-1)\text{sign}(h) - \frac{h + \frac{1}{2}J(K-1)\text{sign}(h)}{\sqrt{J^2(K+1)^2 + 4h^2 + 4\left(K-1\right) J |h|}}
+\end{aligned}\end{equation}
+There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get
+\begin{equation}\begin{aligned}
+	F^\prime(h \to 0^\pm, T\to 0) = \mp \frac{1}{2}\frac{(K-1)(K+2)}{K+1}
+\end{aligned}\end{equation}
+The first derivative of the free energy is therefore discontinuous as the field coupled to the bath \(h\to 0\); it goes to different values depending on the direction in which we take the limit.
+The only case where it is not analytic is when \(K=1\); then the derivative goes to zero from both directions.
+This non-analyticity has also been verified numerically.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../numerics/disc_mag_bath.pdf}
+	\caption{Non-analytic free energy for \(K>1\) and analytic free energy for \(K=1\).}
+\end{figure}
 

### 2021-12-14 notes/mck_urg.tex
obtained constraint between mag x and magz in terms of K

@@
 
-\section{Parity operators and the impurity magnetization}
+\section{Parity operators and impurity magnetization}
+
+\subsection{Action of \(\pi^x\)}
 We can also use the eigenvalues of \(\pi^z\) to label the eigenstates.
@@
 \end{align}
-The action of \(\pi^x\) on the eigenstates can now be determined:
-\begin{align}
-	\pi^x \ket{\Psi^M_{m,-}} &=-\sqrt{x_m^M}\ket{\downarrow, M, -m} + \left(M + m + 1\right)\ket{\uparrow,M,-m-1} = -\ket{\Psi^M_{-m-1,-}}
-\end{align}
-It can be seen that the action of the operator \(\pi^x\) is to interpolate between two ground states of opposite \(\pi^z\) eigenvaluesand, more specifically, opposite \(S^z\) values
-\begin{align}
-	\pi^x \ket{S^z} \to \ket{-S^z}
-\end{align}
-
+The action of \(\pi^x\) on the eigenstates \(\ket{\Psi^M_{m,-}}\) can now be determined:
+\begin{align}
+	\pi^x \ket{\Psi^M_{m,-}} &=- \frac{1}{N^M_m}\left(-\sqrt{x^M_m}\ket{\downarrow,M,-m} + (M+m+1)\ket{\uparrow,M,-(m+1)}\right)
+\end{align}
+where \(N^M_m = \sqrt{(M+m+1)(1+2M)}\) is the normalization factor. We have the relation \(\frac{\sqrt{x^M_m}}{M+m+1} = \frac{M-m}{\sqrt{x^M_{-m-1}}}\). Using this, we can write
+\begin{equation}\begin{aligned}
+	\pi^x \ket{\Psi^M_{m,-}} &=-\frac{\sqrt{x^M_m}}{M-m}\frac{1}{N^M_m}\left((M-m)\ket{\downarrow,M,-m} + \sqrt{x^M_{-m-1}}\ket{\uparrow,M,-(m+1)}\right) \\
+				 &= -\frac{1}{N^M_{-m-1}}\left((M-m)\ket{\downarrow,M,-m} + \sqrt{x^M_{-m-1}}\ket{\uparrow,M,-(m+1)}\right) \\
+				 &= -\ket{\Psi^M_{-m-1,-}}
+\end{aligned}\end{equation}
+
+It can be seen that the action of the operator \(\pi^x\) is to interpolate between two ground states of opposite \(\pi^z\) eigenvalues and, more specifically, opposite \(S^z\) values
+\begin{align}
+	\pi^x \ket{S^z} = -\ket{-S^z}
+\end{align}
+
+\subsection{Impurity magnetization along \(x\) in terms of matrix elements of the string operator \(\pi^x\)}
 We can show that the impurity magnetization along the \(x-\)direction in some specific ground states can be related to matrix elements of the string operator \(\pi^x\).
-The most general ground state is obtained by taking a general linear combination of all the normalized ground states:
-\begin{align}
-	\ket{g^n_m} = \frac{1}{\sqrt 2}\left[\ket{\Psi^M_{m,-}} + e^{i\theta}\ket{\Psi^M_{m+n,-1}}\right], m \in \left[-M, M-2\right] , n \in \left[1, M - m - 1\right] 
+We take a linear combination of two \(S^z\) eigenstates as the ground state:
+\begin{align}
+	\ket{g^n_m} = \frac{1}{\sqrt 2}\left[\ket{\Psi^M_{m,-}} + \ket{\Psi^M_{m+n,-1}}\right], m \in \left[-M, M-2\right] , n \in \left[1, M - m - 1\right] 
 \end{align}
@@
 \begin{align}
-	\left(m_d^x\right)_m^n = \braket{g^n_m | \sigma_d^x | g^n_m}
+	\left<\sigma^x_d\right>_m^n = \braket{g^n_m | \sigma_d^x | g^n_m}
 \end{align}
@@
 \begin{align}
-	\left(m_d^x\right)_m^n = \delta_{n,1}\braket{g^1_m | \sigma_d^x | g^1_m} = \delta_{n,1}\left[e^{i\theta}\braket{\Psi^M_{m+1,-}|\sigma_d^x| \Psi^M_{m,-}} + \text{h.c.}\right] = \delta_{n,1}\left[e^{i\theta}\braket{\Psi^M_{m+1,-}|\sigma_d^x \pi^x | \Psi^M_{-m-1,-}} + \text{h.c.}\right]
-\end{align}
-\textit{We thus see that the impurity magnetization \(\left(m_d^x\right)_m^n\) along \(x\) for the state \(\ket{g^n_m}\) is determined by the matrix element of the string operator \(\sigma^x_d \pi^x\)}.
+	\left<\sigma^x_d\right>_m^n =\frac{1}{2}\delta_{n,1}\braket{g^1_m | \sigma_d^x | g^1_m} = \frac{1}{2}\delta_{n,1}\left[\braket{\Psi^M_{m+1,-}|\sigma_d^x| \Psi^M_{m,-}} + \text{h.c.}\right] = -\frac{1}{2}\delta_{n,1}\left[\braket{\Psi^M_{m+1,-}|\sigma_d^x \pi^x | \Psi^M_{-m-1,-}} + \text{h.c.}\right]
+\end{align}
+\textit{We thus see that the impurity magnetization \(\left<\sigma^x_d\right>_m^n\) along \(x\) for the state \(\ket{g^n_m}\) is determined by the matrix element of the string operator \(\sigma^x_d \pi^x\)}.
+A general matrix element has the form
+\begin{equation}\begin{aligned}
+	\braket{\Psi^M_{m+1,-}|\sigma^x_d \pi^x | \Psi^M_{-(m+1),-}} = \frac{\sqrt{M + m +1}\sqrt{x^M_{m+1}}}{(1+2M)\sqrt{M+m+2}} = \frac{\sqrt{M^2 - \left(m+1\right)^2}}{\left(1+2M\right)}
+\end{aligned}\end{equation}
+The ground state manifold is defined by \(M = K/2\). Using this, we can write
+\begin{equation}\begin{aligned}
+	\left<\sigma^x_d\right>_m^1 = -\frac{1}{2}\left[\braket{\Psi^M_{m+1,-}|\sigma_d^x \pi^x | \Psi^M_{-m-1,-}} + \text{h.c.}\right] = -\frac{\sqrt{K^2 - \left(2m+2\right)^2}}{2\left(1+K\right)}\label{mag_x}
+\end{aligned}\end{equation}
 
 For \(m = -M\), we get
-\begin{align}
-	\braket{\Psi^M_{-M+1,-}|\sigma_d^x \pi^x | \Psi^M_{M - 1,-}} = \frac{\sqrt{2M-1}}{2M + 1}
-\end{align}
-The ground state manifold is defined by \(M = K/2\). Using this, we can write
-\begin{align}
-	\left(m_d^x\right)_{-M}^1 = \left[\braket{\Psi^M_{1-M,-}|\sigma_d^x \pi^x | \Psi^M_{M - 1,-}} + \text{h.c.}\right] = \frac{2\sqrt{2M-1}}{2M + 1} = \frac{2\sqrt{K-1}}{K+1}
-\end{align}
-
-We can similarly calculate the magnetization along the \(z-\)direction. The most general ground state is
-\begin{align}
-	\ket{g} = \sum_{m=-M}^{M-1} C_m \ket{\Psi^M_{m,-}}, &&& m \in \left[-M, M-1\right], &&& \sum_m |C_m|^2 = 1
-\end{align}
+\begin{gather}
+	\braket{\Psi^M_{-M+1,-}|\sigma_d^x \pi^x | \Psi^M_{M - 1,-}} = \frac{\sqrt{2M-1}}{2M + 1}\\
+	\left<\sigma^x_d\right>_{-M}^1 = -\frac{1}{2}\left[\braket{\Psi^M_{-M+1,-}|\sigma_d^x \pi^x | \Psi^M_{M - 1,-}} + \text{h.c.}\right] = -\frac{\sqrt{2M-1}}{2M + 1} = -\frac{\sqrt{K-1}}{K+1}
+\end{gather}
+
+We can similarly calculate the magnetization along the \(z-\)direction in the state \(\ket{g^1_m}\).
 The expectation value of \(\sigma^d_z\) will be non-zero only in the diagonal terms: \(\braket{\Psi^M_m | \sigma^z_d | \Psi^M_{m^\prime}} = \delta_{mm^\prime}\braket{\Psi^M_m | \sigma^z_d | \Psi^M_{m}}\).
 Using this, we get
-\begin{align}
-	\braket{g|\sigma^z_d|g} = \sum_{m=-M}^{M-1} |C_m|^2 \frac{\left[x_m^M - \left(M + m + 1\right)^2\right]}{{(M+m+1)(1+2M)}}
-\end{align}
-For the simpler case when \(C_m = \delta_{m,\pm (M - \frac{1}{2}) - \frac{1}{2}}\), we get
-\begin{align}
-	\braket{g_\pm|\sigma^z_d|g_\pm} = \pm \frac{2M-1}{2M+1} = \pm \frac{K-1}{K+1}
-\end{align}
+\begin{equation}\begin{aligned}
+	\braket{g_m^1|\sigma^z_d|g_m^1} &= \frac{1}{2}\left[\braket{\Psi^M_{m,-}|\sigma_d^z | \Psi^M_{m,-}} + \braket{\Psi^M_{m+1,-}|\sigma_d^z | \Psi^M_{m+1,-}}\right]\\
+					&= \frac{1}{2}\left[\frac{x^M_m - \left( M+m+1 \right) ^2}{\left( N^M_m \right) ^2} + \frac{x^M_{m+1} - \left( M+m+2 \right) ^2}{\left( N^M_{m+1} \right) ^2}\right]\\
+					&= -\frac{1}{2}\left[\frac{2m+1}{2M+1} + \frac{2m+3}{2M+1}\right]\\
+					&= - \frac{2\left( m+1 \right) }{K+1}
+\end{aligned}\end{equation}
+
+Combining this with eq.~\ref{mag_x}, we get
+\begin{equation}\begin{aligned}
+	\left(\left<\sigma^x_d\right>_m^1\right)^2 + \left(\frac{1}{2}\left<\sigma^z_d\right>_m^1\right)^2 = \left[\frac{K}{2\left( 1+K \right) }\right] ^2
+\end{aligned}\end{equation}
+This relation constrains the magnetization along \(z\) in terms of the magnetization along \(x\) (which is related to the t'hooft loop \(\pi^x\)) and a function of \(K\) (the function is quantized because \(K\) can only take integer values).
 

### 2021-12-15 notes/mck_urg.tex
obtained constraint between the magnetizations

@@
 \end{align}
-We can write the eigenstates of \(s_\text{tot}^z\) in terms of the eigenstates of \(s_i^z\) using their Clebsch-Gordon coefficients:
+We can write the simultaneous eigenstates of \(s^2_\text{tot}\) and \(s_\text{tot}^z\) in terms of the eigenstates of \(s_i^z\) using their Clebsch-Gordon coefficients:
 \begin{align}
@@
 \end{align}
-where \(C_{\left\{m_i\right\},m,M} = \braket{m_1,m_2,...,m_K|m,M}\) are the Clebsch-Gordon coefficients. Applying the parity operator on the state gives
-\begin{align}
-	\pi^x \ket{S_d^z, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}(S_d^+ + S_d^-)\ket{S_d^z}\otimes_{i=1}^K \left(s_i^+ + s_i^-\right)\ket{m_i} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{-m_i}\\
-	=\sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{-m_i\right\},m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{m_i}
-\end{align}
+The state \(\ket{M,m}\) is defined by \(s_\text{tot}^2\ket{M,m} = M(M+1), s^z_\text{tot}\ket{M,m} = m\).
+The Clebsch-Gordon coefficients are defined as \(C_{\left\{m_i\right\},m,M} = \braket{m_1,m_2,...,m_K|m,M}\).
+We also define the simultaneous eigenstate \(\ket{m_d, M, m}\) of \(S_d^z,s_\text{tot}^z\) and \(s^2_\text{tot}\): \(S_d^z\ket{m_d, M, m} = m_d\ket{m_d, M, m}\).
+Applying \(\pi^x\) on this state gives
+\begin{align}
+	\pi^x \ket{m_d, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}(S_d^+ + S_d^-)\ket{m_d}\otimes_{i=1}^K \left(s_i^+ + s_i^-\right)\ket{m_i} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}\ket{-m_d}\otimes_{i=1}^K\ket{-m_i}\\
+	=\sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{-m_i\right\},m,M}\ket{-m_d}\otimes_{i=1}^K\ket{m_i}
+\end{align}
+In the ground state subspace, we have \(M = \frac{K}{2}\), and we always have \(\sum_i M_i = \frac{K}{2}\).
 Using the identity \(\braket{M_1m_1,M_2m_2,\ldots|m,M} = \left( -1 \right)^{\sum_i M_i - M}\braket{M_1, -m_1; M_2 -m_2;\ldots|-m,M}\), we have \(C_{\left\{-m_i\right\},m,M} = C_{\left\{m_i\right\},-m,M}\).
@@
 \begin{align}
-	\pi^x \ket{S_d^z, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{m_i\right\},-m,M}\ket{-S_d^z}\otimes_{i=1}^K\ket{m_i} = \ket{-S_d^z, M, -m}
+	\pi^x \ket{m_d, M,m} = \sum_{\left\{m_i\right\}\atop{\sum_i m_i = -m}}C_{\left\{m_i\right\},-m,M}\ket{-m_d}\otimes_{i=1}^K\ket{m_i} = \ket{-m_d, M, -m}
 \end{align}
@@
 \begin{align}
-	\ket{g^n_m} = \frac{1}{\sqrt 2}\left[\ket{\Psi^M_{m,-}} + \ket{\Psi^M_{m+n,-1}}\right], m \in \left[-M, M-2\right] , n \in \left[1, M - m - 1\right] 
+	\ket{g^n_m} = \frac{1}{\sqrt 2}\left[\ket{\Psi^M_{m,-}} + e^{i\theta}\ket{\Psi^M_{m+n,-1}}\right], m \in \left[-M, M-2\right] , n \in \left[1, M - m - 1\right] 
 \end{align}
@@
 \begin{align}
-	\left<\sigma^x_d\right>_m^n =\frac{1}{2}\delta_{n,1}\braket{g^1_m | \sigma_d^x | g^1_m} = \frac{1}{2}\delta_{n,1}\left[\braket{\Psi^M_{m+1,-}|\sigma_d^x| \Psi^M_{m,-}} + \text{h.c.}\right] = -\frac{1}{2}\delta_{n,1}\left[\braket{\Psi^M_{m+1,-}|\sigma_d^x \pi^x | \Psi^M_{-m-1,-}} + \text{h.c.}\right]
+	\left<\sigma^x_d\right>_m^n =\frac{1}{2}\delta_{n,1}\braket{g^1_m | \sigma_d^x | g^1_m} = \frac{1}{2}\delta_{n,1}\left[\braket{\Psi^M_{m+1,-}|\sigma_d^x| \Psi^M_{m,-}}e^{-i\theta} + \text{h.c.}\right] = -\frac{1}{2}\delta_{n,1}\left[\braket{\Psi^M_{m+1,-}|\sigma_d^x \pi^x | \Psi^M_{-m-1,-}}e^{-i\theta} + \text{h.c.}\right]
 \end{align}
@@
 \begin{equation}\begin{aligned}
-	\left<\sigma^x_d\right>_m^1 = -\frac{1}{2}\left[\braket{\Psi^M_{m+1,-}|\sigma_d^x \pi^x | \Psi^M_{-m-1,-}} + \text{h.c.}\right] = -\frac{\sqrt{K^2 - \left(2m+2\right)^2}}{2\left(1+K\right)}\label{mag_x}
-\end{aligned}\end{equation}
-
+	\left<\sigma^x_d\right>_m^1 = -\frac{1}{2}\left[\braket{\Psi^M_{m+1,-}|\sigma_d^x \pi^x | \Psi^M_{-m-1,-}}e^{-i\theta} + \text{h.c.}\right] = -\frac{\sqrt{K^2 - \left(2m+2\right)^2}}{2\left(1+K\right)}\cos\theta
+	\label{mag_x}
+\end{aligned}\end{equation}
 For \(m = -M\), we get
@@
 	\braket{\Psi^M_{-M+1,-}|\sigma_d^x \pi^x | \Psi^M_{M - 1,-}} = \frac{\sqrt{2M-1}}{2M + 1}\\
-	\left<\sigma^x_d\right>_{-M}^1 = -\frac{1}{2}\left[\braket{\Psi^M_{-M+1,-}|\sigma_d^x \pi^x | \Psi^M_{M - 1,-}} + \text{h.c.}\right] = -\frac{\sqrt{2M-1}}{2M + 1} = -\frac{\sqrt{K-1}}{K+1}
+	\left<\sigma^x_d\right>_{-M}^1 = -\frac{1}{2}\left[\braket{\Psi^M_{-M+1,-}|\sigma_d^x \pi^x | \Psi^M_{M - 1,-}}e^{-\theta} + \text{h.c.}\right] = -\frac{\sqrt{2M-1}}{2M + 1}\cos\theta = -\frac{\sqrt{K-1}}{K+1}\cos\theta
 \end{gather}
 
-We can similarly calculate the magnetization along the \(z-\)direction in the state \(\ket{g^1_m}\).
+\subsection{Constraint on magnetization values}
+We can similarly calculate the magnetization along the \(y\) and \(z\) directions in the same state \(\ket{g^1_m}\).
+The magnetization along \(y\) can again be shown to depend on the matrix elements of the string parity operator \(\pi^y = \sigma_d^y \otimes_{i=1}^K \sigma^y_i\).
+The action of this operator on the eigenstates \(\ket{m_d, M, m}\) can be shown to be identical to that of \(\pi^x\) up to a phase factor:
+\begin{align}
+	\sigma_d^y \ket{m_d} &= \frac{1}{i}\left(S_d^+ - S_d^-\right) \ket{m_d} = \left(-1\right)^{m_d + \frac{1}{2}} \frac{1}{i}\ket{-m_d}\\
+	\pi^y \ket{m_d, M,m} &= \frac{1}{i^{K+1}}\sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}(S_d^+ - S_d^-)\ket{m_d}\otimes_{i=1}^K \left(s_i^+ - s_i^-\right)\ket{m_i}\\
+			     &= \frac{\left( -1 \right)^{S^z + \frac{K+1}{2} }}{i^{K+1}}\sum_{\left\{m_i\right\}\atop{\sum_i m_i = m}}C_{\left\{m_i\right\},m,M}\ket{-m_d}\otimes_{i=1}^K\ket{-m_i}\\
+			     &= \frac{\left( -1 \right)^{S^z + \frac{K+1}{2} }}{i^{K+1}}\pi^x \ket{m_d, M, m}\\
+			     &= \frac{\left( -1 \right)^{S^z + \frac{K+1}{2} }}{i^{K+1}} \ket{-m_d, M, -m}
+\end{align}
+Here, \(S^z = m_d + m\) is the total spin angular momentum along \(z\). Since the eigenstates \(\ket{\Psi^M_{m,-}}\) satisfy \(S^z = m + \frac{1}{2}\), we can write
+\begin{equation}\begin{aligned}
+	\pi^y \ket{\Psi^M_{m,-}} = \frac{\left( -1 \right)^{m + 1 + \frac{K}{2}}}{i^{K+1}} \pi^x\ket{\Psi^M_{m,-}} = \frac{\left( -1 \right)^{m + 2 + \frac{K}{2}}}{i^{K+1}} \ket{\Psi^M_{-m-1,-}}
+\end{aligned}\end{equation}
+The magnetization along \(y\) in the ground state \(\ket{g^1_m}\) can again be written in terms of matrix elements of the string operator \(\sigma_d^y \pi^y\):
+\begin{equation}\begin{aligned}
+	\label{mag_y}
+	\braket{g^1_m | \sigma^y_d | g^1_m} = \frac{1}{2}\left[\braket{\Psi^M_{m+1,-}|\sigma_d^y \pi^y|\Psi^M_{-m-1,-}} i^{K+1}\left( -1 \right)^{-m + 1 + \frac{K}{2}}e^{-i\theta} + \text{h.c.}\right] = -\frac{\sqrt{K^2 - \left( 2m+2 \right) ^2}}{2\left( 1+K \right) }\sin\theta
+\end{aligned}\end{equation}
+
 The expectation value of \(\sigma^d_z\) will be non-zero only in the diagonal terms: \(\braket{\Psi^M_m | \sigma^z_d | \Psi^M_{m^\prime}} = \delta_{mm^\prime}\braket{\Psi^M_m | \sigma^z_d | \Psi^M_{m}}\).
@@
 
-Combining this with eq.~\ref{mag_x}, we get
-\begin{equation}\begin{aligned}
-	\left(\left<\sigma^x_d\right>_m^1\right)^2 + \left(\frac{1}{2}\left<\sigma^z_d\right>_m^1\right)^2 = \left[\frac{K}{2\left( 1+K \right) }\right] ^2
-\end{aligned}\end{equation}
-This relation constrains the magnetization along \(z\) in terms of the magnetization along \(x\) (which is related to the t'hooft loop \(\pi^x\)) and a function of \(K\) (the function is quantized because \(K\) can only take integer values).
+Combining this with eqs.~\ref{mag_x} and ~\ref{mag_y}, we get
+\begin{equation}\begin{aligned}
+	\frac{1}{\cos^2\theta}\left(\left<\sigma^x_d\right>_m^1\right)^2 + \frac{1}{\sin^2\theta}\left(\left<\sigma^y_d\right>_m^1\right)^2 + \frac{1}{2}\left(\left<\sigma^z_d\right>_m^1\right)^2 = \frac{1}{2}\left(\frac{K}{1+K}\right)^2
+\end{aligned}\end{equation}
+This relation constrains the values of the magnetization along all the directions: the \(x\) and \(y\) magnetization values have already been shown to be related to the string operators \(\pi^x\) and \(\pi^y\) respectively (which are 't Hooft loops, and can be related to one another ), and the magnetization along \(z\) is therefore constrained in terms of the string operators on the left-hand side and the quantized fucntion on the right-hand side (the function is quantized because \(K\) can only take integer values).
+All the expectation values are calculated in the state \(\ket{g^1_m} = \ket{g^\theta_{S^z}} = \frac{1}{\sqrt 2}\left(\ket{S^z} + \ket{S^z+1}e^{i\theta}\right) \).
+For the specific value of \(\theta = \frac{\pi}{4}\), the constraint achieves global spin-rotation symmetry:
+\begin{equation}\begin{aligned}
+	\sum_{i=x,y,z}\left(\left<\sigma^i_d\right>_m^1\right)^2 = \left(\frac{K}{1+K}\right)^2
+\end{aligned}\end{equation}
 

### 2021-12-16 notes/mck_urg.tex
generalised the duality to spin-S and added the degeneracy part to the star graph importance section

@@
 \section{Introduction of the Hamiltonian and its zero mode}
-The isotropic multi-channel Kondo (MCK) model~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact} is described by the Hamiltonian
+The isotropic multi-channel Kondo (MCK) model~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact,coleman_pepin_2003,roch_nicolas_costi_2009,schiller_avraham_2008,Durganandini_2011} is described by the Hamiltonian
 \begin{align}
@@
 \end{align}
-We can make one more identification: the sum over the spins in momentum space amount to a local interaction at the zeroth sites of the indicates channels: \(\sum_k {c^\gamma_{k\alpha}}^\dagger = {c^\gamma_{\vec r=0, \alpha}}^\dagger\), This suggests we shoud define spin operators for the zeroth sites of the channels:
+This procedure is equivalent to taking a zero-bandwidth approximation on the full Hamiltonian \cite{zitko_fabrizio_2017}; the final Hamiltonian then correspond to the degrees of freedom on the Fermi surface, and we recover the zero mode Hamiltonian again once we set the energy of the Fermi surface to zero.
+
+We can make one more identification: the sum over the momentum space states amounts to a local state at the zeroth sites of the indicates channels: \(\sum_k {c^\gamma_{k\alpha}}^\dagger = {c^\gamma_{\vec r=0, \alpha}}^\dagger\), This suggests we shoud define spin operators for the zeroth sites of the channels:
 \begin{align}
@@
 Instead, the RG flows converge to an intermediate coupling fixed point.
-The RG flows \textit{preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}, because the Hamiltonian commutes with the total magnetization operator \(S^z = S_d^z + s_\text{tot}^z\)~\cite{vondelft_prl_1998}.
+The RG flows \textit{preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}\textcolor{red}{, because the Hamiltonian commutes with the total magnetization operator \(S^z = S_d^z + s_\text{tot}^z\)~\cite{vondelft_prl_1998}}.
 For example, the two-channel and the three-channel Kondo models have ground state degeneracies of 2 and 3 respectively, throughout the RG flow.
@@
 
-Just like the full Hamiltonian, the star graph conserves the total spin \(S^z\), and this leads to a \(K-\)fold degeneracy in the ground state of the \(K-\)channel star graph.
+\textcolor{red}{Just like the full Hamiltonian}, the star graph conserves the total spin \(S^z\), and this leads to a \(K-\)fold degeneracy in the ground state of the \(K-\)channel star graph.
 Since \(S^z\) commutes with the star graph, the ground states are eigenstates of \(S^z\) with distinct eigenvalues \(\frac{K+1}{2}, \frac{K-1}{2},\ldots,\frac{-K-1}{2}\).
@@
 In other words, as the exchange coupling grows(shrinks) from \(0^+\left(\infty^-\right)\) towards the fixed point value \(J^*\), the degeneracy remains protected at \(K\).
+This is qualitatively different from the case of the single-channel Kondo model; there, the \(2-\)fold degeneracy of the local moment fixed point crosses over into a stable and unique singlet ground state at low temperatures/energies.
+
+It can be demonstrated very simply that the ground state degeneracy of the star graph lies at the heart of the MCK problem.
+It can be argued that the ground state degeneracy of the more general MCK model with a spin-\(S\) impurity is given by \(d(S) = |K - 2S|+1\).
+This is because, if we write the star graph Hamiltonian in eq.~\ref{stargraph} as \(H = J\left[J^2 - S_d^2 - s^2_\text{tot}\right] \) (where \(\vec J = \vec S_d + \vec s_\text{tot}\)), we can see that the ground state is realized when \(s_\text{tot}\) and \(S_d\) takes their maximum values of \(S\) and \(\frac{K}{2}\) respectively, and \(J\) takes its corresponding minimum value of \(|\frac{K}{2} - S|\).
+For this value of \(J\), \(J^z\) can take \(2J+1 = |K - 2S|+1\) values, and since the Hamiltonian (and hence the ground state energy) depends only on \(J\) and not on \(J^z\), all these \(2J+1\) states labelled by the distinct quantum numbers are degenerate.
+If we now ask when the degeneracy is exactly unity, we get the condition \(K=2S\).
+The cases of multiple degeneracy lie either in \(K>2S\) or \(K<2S\).
+The case of \(K=2S\) is that of exact screening, where we know that the ground state is a singlet described by a local Fermi liquid phase \cite{wilson1975,nozieres1974fermi,Noz_blandin_1980,andreiKondoreview,tsvelickKondoreview}~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact,coleman_pepin_2003,roch_nicolas_costi_2009,schiller_avraham_2008,Durganandini_2011}.
+The cases of \(K>2S\) and \(K<2S\) correspond to over-screened and under-screened systems, both of which are known to exhibit non-Fermi liquid behaviour.
+This shows that the ground state degeneracy can be used to classify the low energy phases into Fermi liquids and non-Fermi liquids.
 
@@
 
-\subsection{Leading order renormalization}
-\begin{align}
-	\Delta H^{(2)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c}_\text{first term}~+~\underbrace{T^\dagger c \frac{1}{\omega - H_D}c^\dagger T}_\text{second term}
-\end{align}
-This renormalization is identical to that in the single channel. There is no additional physics due to the presence of multiple channels at this order. It is shown in appendix \ref{1KondoURG}.
-
-\subsection{Next-to-leading order renormalization}
+The second order renormalization is identical to that in the single channel.
+There is no additional physics due to the presence of multiple channels at this order.
+It is shown in appendix \ref{1KondoURG}.
+
+At third order, we have
 \begin{align}
@@
 
-\subsubsection*{\textbf{Particle sector renormalization}}
+\subsection{Particle sector renormalization}
 The two terms in the particle sector have the form
@@
 
-\subsubsection*{\textbf{Hole sector renormalization}}
+\subsection{Hole sector renormalization}
 Like the single-channel case, the renormalization coming from the hole excitations is exactly the Hermitian conjugate of that in the particle sector.
@@
 
-For \(D \gg J\), we can ignore the \(J\) in the denominator, and the equation reduces to the one-loop poor man's scaling form
+For \(D \gg J\), we can ignore the \(J\) in the denominator, and the equation reduces to the one-loop poor man's scaling form \cite{Kogan_2018,Kuramoto1998}
 \begin{align}
@@
 \section{Strong-weak duality of the multi-channel Kondo RG flows}
-If we start from a strong coupling \((J \to \infty)\) MCK Hamiltonian
+We start from a strong coupling \((J \to \infty)\) spin-\(S\) impurity MCK Hamiltonian in the over-screened regime \(\left( K > 2S \right) \),
 \begin{equation}\begin{aligned}
 	\label{strong_ham}
-	H(J) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + J \vec{S_d}\cdot\vec{s}_\text{tot}
-\end{aligned}\end{equation}
-where \(\vec s_\text{tot}\) is the total spin \(\sum_l \sum_{kk^\prime \alpha\beta} \vec \sigma_{\alpha\beta}c^\dagger_{k\alpha,l}c_{k^\prime\beta,l}\) of all the zero modes, the ground states of the star graph eq.~\ref{zeromode_ham} act as a good starting point for a perturbative expansion.
-There are \(K\) such ground states for a \(K-\)channel model, labelled by the \(K\) values of the total spin angular momentum \(S^z = S_d^z + s_\text{tot}^z\), \(S^z = -\frac{K+1}{2}, -\frac{K-1}{2}, \ldots, \frac{K-1}{2}\).
-To leverage the large coupling, one can define a composite impurity out of this \(K-\)fold degenerate ground state.
-That is, just like a spin-\(\frac{1}{2}\) impurity is essentially a degenerate two-level system (at least as long as it is decoupled), one can similarly define a composite spin that is \(K-\)fold degenerate, and hence has \(\mathbb{S}_d = \frac{K-1}{2}\).
-The states of this spin are defined as
-\begin{equation}\begin{aligned}
-	\mathbb{S}_d^z \ket{S^z} = S^z \ket{S^z}, &&\mathbb{S}_d^\pm \ket{S^z} \sim \ket{S^z \pm 1}
+	H(J) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + J \vec{S_d}\cdot\vec{s}_\text{tot}~.
+\end{aligned}\end{equation}
+Here, \(\vec s_\text{tot}\) is the total spin \(\sum_l \sum_{kk^\prime \alpha\beta} \vec \sigma_{\alpha\beta}c^\dagger_{k\alpha,l}c_{k^\prime\beta,l}\) of all the zero modes.
+At strong-coupling, the ground states of the star graph eq.~\ref{zeromode_ham} act as a good starting point for a perturbative expansion.
+As argued previously, there are \(K-2S+1\) ground states, labelled by the \(K\) values of the total spin angular momentum \(S^z = S_d^z + s_\text{tot}^z = -\frac{K}{2} + S, -\frac{K}{2} + S + 1, \ldots, \frac{K}{2} - S\).
+To leverage the large coupling, one can define a new spin impurity \(\mathbb{S}\) out of this ground state manifold.
+Since the degeneracy of a spin is given by its multiplicity \(2S^\prime + 1\), we have \(2S^\prime + 1 = K-2S+1 \implies S^\prime = \frac{K}{2} - S\).
+That is, the spin-\(S\) impurity has a dual described by a spin-\((K-2S+1)\) impurity.
+The states of this new spin are defined by
+\begin{equation}\begin{aligned}
+	\mathbb{S}_d^z \ket{m_d^z} = m_d^z \ket{m_d^z}, &&\mathbb{S}_d^\pm \ket{m_d^z} \sim \ket{m_d^z \pm 1}
 \end{aligned}\end{equation}
 The excited states of the star graph can be used to define bosons \cite{kroha_kolf_2007}, and the hopping into the lattice can then be re-written using these bosons.
-One can then remove the single-particle hoping between the zero modes and the first sites using a Schrieffer-Wolff transformation in the small coupling \(J^\prime = \gamma \frac{4t^2}{J}\), and generate an exchange-coupling between new composite spin \(\vec {\mathbb{S}}_d\) and the new zero modes formed out of the remaining sites in the lattice \cite{kroha_kolf_2007} (by remaining, we mean those real space sites that have not been consumed into forming the composite spin).
+One can then remove the single-particle hoping between the zero modes and the first sites using a Schrieffer-Wolff transformation in the small coupling \(J^\prime = \gamma \frac{4t^2}{J}\), and generate an exchange-coupling between the new impurity \(\vec {\mathbb{S}}_d\) and the new zero modes formed out of the remaining sites in the lattice \cite{kroha_kolf_2007} (by remaining, we mean those real space sites that have not been consumed into forming the new spin).
 The new Hamiltonian, characterised by the small superexchange  coupling \(J^\prime\), has the form
@@
 \end{aligned}\end{equation}
-The prime on \(s_\text{tot}\) indicates that is the formed by the new zero modes.
-This Hamiltonian is very similar to the one in eq.~\ref{strong_ham}, and that is the essence of the strong-weak duality: One can go from the strong coupling spin-\(\frac{1}{2}\) MCK model to a weak coupling spin-\(\frac{K-1}{2}\) MCK model.
-For the case of \(K=2\), both \(S_d\) and \(\mathbb{S}_d\) are spin-\(\frac{1}{2}\) objects, and the models are said to be self-dual.
-
-One important consequence of the duality is that the RG equations are also dual; while the strong coupling model has an irrelevant coupling \(J\) that flows down to the intermediate fixed point \(J^*\), the weak coupling model has a relevant coupling \(J^\prime\) that flows up to the same fixed point \({J^\prime}^* = J^*\).
+The prime on \(s_\text{tot}\) indicates that it is formed by the new zero modes.
+This Hamiltonian is very similar to the one in eq.~\ref{strong_ham}, and that is the essence of the strong-weak duality: One can go from the over-screened strong coupling spin-\(S\) MCK model to another over-screened weak coupling spin-\((K-2S+1)\) MCK model.
+For the case of \(K=4S\), we have \(S^\prime = S\), and both \(S_d\) and \(\mathbb{S}_d\) describe the same spin objects (at least formally).
+The two models are then said to be self-dual.
+For example, for the case of spin-half MCK model, two-channel model is self-dual.
+
+One important consequence of the duality relationship between the two overscreened models is that the RG equations are also dual; while the strong coupling model has an irrelevant coupling \(J\) that flows down to the intermediate fixed point \(J^*\), the weak coupling model has a relevant coupling \(J^\prime\) that flows up to the same fixed point \({J^\prime}^* = J^*\).
 From the RG equation for the general spin-\(S\) MCK model, we know that \({J^\prime}^* = \frac{2}{K \rho^\prime}\), where \(\rho^\prime\) is the DOS for the bath of the weak coupling Hamiltonian.
@@
 \end{aligned}\end{equation}
-There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get
-\begin{equation}\begin{aligned}
-	F^\prime(h \to 0^\pm, T\to 0) = \mp \frac{1}{2}\frac{(K-1)}{(K+1)}
-\end{aligned}\end{equation}
-
-The first derivative of the impurity free energy is therefore discontinuous as \(h\to 0\); it goes to different values depending on the direction in which we take the limit.
+There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get the magnetization of the impurity
+\begin{equation}\begin{aligned}
+	m = F^\prime(h \to 0^\pm, T\to 0) = \mp \frac{1}{2}\frac{(K-1)}{(K+1)}
+\end{aligned}\end{equation}
+
+The magnetization is therefore discontinuous as \(h\to 0\); it goes to different values depending on the direction in which we take the limit.
 The only case where it is not analytic is when \(K=1\); then the derivative goes to zero from both directions.
@@
 \end{aligned}\end{equation}
-There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get
+There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we find that the bath magnetization is discontinuous:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-The first derivative of the free energy is therefore discontinuous as the field coupled to the bath \(h\to 0\); it goes to different values depending on the direction in which we take the limit.
-The only case where it is not analytic is when \(K=1\); then the derivative goes to zero from both directions.
-This non-analyticity has also been verified numerically.
 \begin{figure}[htpb]
@@
 \end{align}
-There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get
+There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get the total magnetization, and find that it is discontinuous:
 \begin{align}
@@
 
-The first derivative of the impurity free energy is therefore discontinuous as \(h\to 0\); it goes to different values depending on the direction in which we take the limit.
-The only case where it is not analytic is when \(K=1\); then the derivative goes to zero from both directions.
-This non-analyticity has also been verified numerically.
 \begin{figure}[htpb]
@@
 
-The non-analyticity for \(K>1\) occurs because the magnetic field is able to flip the ground state.
-For example, for \(K=2\), the states in question are \(\ket{M=1, m=-1,0}\).
-For \(h>0\), the ground state occurs in the subspace \(\ket{S_d^z=\frac{1}{2}, m=-1},\ket{S_d^z=-\frac{1}{2},m=0}\).
-If we now flip the magnetic field, the ground state subspace flips to \(\ket{S_d^z=\frac{1}{2}, m=0},\ket{S_d^z=-\frac{1}{2},m=1}\).
-Instead, if we look at the case of \(K=1\), the ground state is in the subspace of \(\ket{S_d^z=\frac{1}{2},m=-\frac{1}{2}},\ket{S_d^z=-\frac{1}{2}, m=\frac{1}{2}}\), and since there is only this one subspace, the ground state is independent of the field.
-From this discussion, it is clear that the non-analyticity appears because there are multiple values of \(m \in [-M, M-1]\) in the ground state manifold, which means that it is the ground state degeneracy that causes the non-analyticity.
-
 \section{Thermal entropy at \(T=0\)}
@@
 In the limit of \(T \to 0\), only the lowest energy state \(E_\text{gs}\) will survive. Assuming this state has a degeneracy \(d_\text{gs}\), we have
-\begin{align}
+\begin{equation}
 	S(T \to 0) = k_B \ln\left(d_\text{gs} e^{-\beta E_\text{gs}}\right) + \frac{d_\text{gs} E_\text{gs}e^{-\beta E_\text{gs}}}{T d_\text{gs} e^{-\beta E_\text{gs}}} = k_B \ln d_\text{gs} - \frac{1}{T}E_\text{gs} + \frac{1}{T}E_\text{gs} = k_B \ln d_\text{gs}
-\end{align}
+\end{equation}
 This is a general result that holds for any system with a \(d_\text{gs}\)-fold degenerate ground state.
@@
 The impurity contribution is therefore
-\begin{align}
+\begin{equation}
 	\label{res_entropy}
 	S_\text{imp}(T\to 0) = k_B \ln K
-\end{align}
-
-We wish to point out that this value is different from the "standard" result 
-\begin{align}
-\label{cft_entropy}
-S = \ln 2\cos \frac{\pi}{K+2}
-\end{align}
-obtained from other methods like the Bethe ansatz (BA) and conformal field theory (CFT) calculations~\cite{Gan_Andrei_Coleman_1993,andrei_destri_1984,Tsvelick_weigmann_mchannel_1985,sacramento1989,emery_kivelson,affleck_1991_overscreen}.
+\end{equation}
+
+We wish to point out that this value is different from the more commonly cited result \(S = \ln 2\cos \frac{\pi}{K+2}\) obtained from other methods like the Bethe ansatz (BA) and conformal field theory (CFT) calculations~\cite{Gan_Andrei_Coleman_1993,andrei_destri_1984,Tsvelick_weigmann_mchannel_1985,sacramento1989,emery_kivelson,affleck_1991_overscreen}.
 The difference is not only in the value but also in the origin.
-Eq.~\ref{res_entropy} describes the thermal entropy coming purely from the quantum mechanical degeneracy of the star graph problem (which is the star graph of the full MCK problem), while the result Eq.~\ref{cft_entropy} presumably arises from the lowest-lying excitations on top of the star graph arising from the conduction bath \(k-\)states.
-Another difference lies in the fact that while Eq.~\ref{res_entropy} holds true independent of system size, Eq.~\ref{cft_entropy} is correct only in the thermodynamic limit and only if the limit of system size \(L \to \infty\) is taken prior to taking the limit of temperature \(T \to 0\)~\cite{Gan_Andrei_Coleman_1993,rozhkov_1998,vondelft_prl_1998}.
+Eq.~\ref{res_entropy} describes the thermal entropy coming purely from the quantum mechanical degeneracy of the star graph problem (which is the star graph of the full MCK problem), while the second result presumably arises from the zero-modes of the lowest-lying excitations above the star graph ground state, arising from a thermodynamically-large continuous bath with Dirac-like linear dispersion.
+Another difference is that while Eq.~\ref{res_entropy} holds true independent of system size, the second result is obtained only if the limit of system size \(L \to \infty\) is taken prior to taking the limit of temperature \(T \to 0\)~\cite{Gan_Andrei_Coleman_1993,rozhkov_1998,vondelft_prl_1998}.
 We note however that the entropy coming from the degeneracy is larger than that coming from the excitations (fig.~\ref{entropy_comparison}), and consequently plays a very important role in the physics of the MCK problem, being responsible for the NFL physics and the critical behaviour near the fixed point.
-
-\begin{figure}[!ht]
+\begin{figure}[!htpb]
 	\centering
-	\includegraphics[width=0.4\textwidth]{../numerics/entropy_comparison.pdf}
+	\includegraphics[width=0.5\textwidth]{../numerics/entropy_comparison.pdf}
 	\caption{Comparison of star graph zero temperature entropy with CFT/Bethe ansatz formula}
@@
 
-Another related problem for which this result holds is the Ising model on a 1D chain.
-The partition function for that problem is \(Z = \lambda_1^N + \lambda_2^N\), where \(\lambda_{1,2} = e^{\beta J} \pm e^{-\beta J} \) are the eigenvalues of the \(T-\)matrix and \(N\) is the number of particles.
-As we come to \(T \to 0\), we have \(\lambda_{1,2} \simeq e^{\beta J}\) and \(Z \simeq 2 e^{\beta N J}\), so \(F = -k_B T \ln 2 - N J\) and the entropy becomes \(S = - \partial_T F = k_B \ln 2\).
-Note that the factor of 2 in \(Z\) is the degeneracy \(d_\text{gs}\) described above.
-
-\clearpage
 \appendix

### 2021-12-17 notes/mck_urg.tex
typo

@@
 Instead, the RG flows converge to an intermediate coupling fixed point.
-The RG flows \textit{preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}\textcolor{red}{, because the Hamiltonian commutes with the total magnetization operator \(S^z = S_d^z + s_\text{tot}^z\)~\cite{vondelft_prl_1998}}.
+The RG flows \textit{preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}\textcolor{red}.
 For example, the two-channel and the three-channel Kondo models have ground state degeneracies of 2 and 3 respectively, throughout the RG flow.
@@
 
-\textcolor{red}{Just like the full Hamiltonian}, the star graph conserves the total spin \(S^z\), and this leads to a \(K-\)fold degeneracy in the ground state of the \(K-\)channel star graph.
+The star graph conserves the total spin \(S^z\), and this leads to a \(K-\)fold degeneracy in the ground state of the \(K-\)channel spin-half star graph.
 Since \(S^z\) commutes with the star graph, the ground states are eigenstates of \(S^z\) with distinct eigenvalues \(\frac{K+1}{2}, \frac{K-1}{2},\ldots,\frac{-K-1}{2}\).
@@
 \begin{equation}\begin{aligned}
-	\mathbb{S}_d^z \ket{m_d^z} = m_d^z \ket{m_d^z}, &&\mathbb{S}_d^\pm \ket{m_d^z} \sim \ket{m_d^z \pm 1}
+	\mathbb{S}_d^z \ket{S^z} = S^z \ket{S^z}, &&\mathbb{S}_d^\pm \ket{S^z} = \sqrt{S^\prime\left( S^\prime + 1 \right) - S^z\left( S^z \pm 1\right)} \ket{S^z \pm 1}
 \end{aligned}\end{equation}

### 2021-12-29 notes/mck_urg.tex
started doing RG of easy axis anisotropy, write down all terms

@@
 
+\subsection{Degree of compensation: a measure of the frustration}
+One can quantify the amount of screening of the local moment at the impurity site by defining a degree of compensation \(\kappa\).
+Such a quantity also measures the inherent singlet frustration in the problem: the higher the degree of compensation, the better the spin can be screened into a singlet and lower is the frustration.
+It is given by the antiferromagnetic correlation existing between the impurity spin and conduction electron channels:
+\begin{equation}\begin{aligned}
+	\Gamma \equiv - \left< \vec{S_d}\cdot \vec{s}_\text{tot}\right>
+\end{aligned}\end{equation}
+where \(\vec s_\text{tot} = \sum_l \vec s_l\).
+The expectation value is calculated in the ground state.
+Since the inner product is simply the ground state energy of a spin-\(S\) impurity \(K-\)channel MCK model in units of the exchange coupling \(J\), we have
+\begin{equation}\begin{aligned}
+	\Gamma = \frac{1}{2} \left[ l_\text{imp}^2 + l_c^2 - g^S_K\left( g^S_K - 1 \right)\right]
+\end{aligned}\end{equation}
+\(l_\text{imp}^2 = S(S+1)\) is the length-squared of the impurity spin.
+Similarly, \(l_c^2 = \frac{K}{2}\left(\frac{K}{2} + 1\right) \) is the length-squared of the total conduction bath spin.
+\(g^S_K = |\frac{K}{2} - S| + 1\) is the ground state degeneracy.
+We will explore the three regimes of screening by defining \(K = K_0 + \delta, S = \frac{K_0}{2} - \delta\).
+\(\delta=0\) represents the exactly-screened case of \(K = 2S = K_0\).
+Non-zero \(\delta\) represents either over- or under-screening.
+In terms of \(K_0\) and \(\delta\), the degree of compensation becomes
+\begin{equation}\begin{aligned}
+	\label{gamma}
+	\Gamma = \frac{1}{4}\left[\left( K_0 + 1 \right) ^2 - \left(|\delta| + 1 \right) ^2\right] 
+\end{aligned}\end{equation}
+\textit{For a given \(K_0\), the degree of compensation is maximised for exact screening \(\delta=0\), and is reduced for \(\delta \neq 0\).
+This shows the inability of the system to form a unique singlet ground state and reveals the quantum-mechanical frustration inherent in the zero mode Hamiltonian and therefore in the entire problem.} The degree of compensation is symmetric under the Hamiltonian transformation \(\delta \to -\delta\), and this represents a duality transformation between over-screened and under-screened MCK models.
+This topic will be discussed in more detail later.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.45\textwidth]{../numerics/deg_of_comp.pdf}
+	\caption{Variation of the degree of compensation as we tune the system from under-screening to over-screening. The maximum spin compensation occurs at exact-screening \(\delta=0\).}
+\end{figure}
+
 \section{Parity operators and impurity magnetization}
@@
 
-\section{Strong-weak duality of the multi-channel Kondo RG flows}
+\section{RG flow of axis anisotropy term}
+We now insert a symmetry-breaking term in the Hamiltonian and study the RG flow of this term:
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{kl} J S_d^z s^z_{kl} + \frac{1}{2}\sum_{kl} J \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right) + X \left(J^z\right)^2
+\end{aligned}\end{equation}
+Here, \(s^z_{kl} = \frac{1}{2}\left(c^\dagger_{k\uparrow}c_{l \uparrow} - c^\dagger_{k\downarrow}c_{l \downarrow}\right)\), \(s^-_{kl} = c^\dagger_{k \downarrow}c_{l \uparrow}\) and \(s^+_{kl} = {s^-_{lk}}^\dagger\).
+Also, \(\tau = \hat n - \frac{1}{2}\).
+The indices \(k,l\) sum over the momentum states.
+\(\vec S_d\) is the impurity spin operator with \(S_d^z = \pm \frac{1}{2}\).
+\(X\) is the symmetry-breaking coupling, and \(J^z = S_d^z + s^z_\text{tot}\) is the total spin.
+Using \(\left(J^z\right)^2 = \frac{1}{4} + 2S_d^z s^z_\text{tot} + \left(s^z_\text{tot}\right)^2 \), we can rewrite the Hamiltonian as
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{kl} J_\parallel S_d^z s^z_{kl} + \frac{1}{2}\sum_{kl} J_\perp \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right) + X \sum_{k_1,k_2,k_1^\prime,\atop{k_2^\prime,l_1,l_2,\atop{\sigma_1,\sigma_2}}}\frac{\sigma_1\sigma_2}{4} c^\dagger_{k_1\sigma_1,l_1}c_{k_1^\prime\sigma_1,l_1}c^\dagger_{k_2\sigma_2,l_2}c_{k_2^\prime\sigma_2,l_2}
+\end{aligned}\end{equation}
+
+The following terms renormalize \(X\):
+\paragraph{\(+|-|z\)}
+\paragraph{\(-|+|z\)}
+\paragraph{\(+|z|-\)}
+\paragraph{\(-|z|+\)}
+\paragraph{\(z|+|-\)}
+\paragraph{\(z|-|+\)}
+\paragraph{\(z|z|X\)}
+\paragraph{\(+|-|X\)}
+\paragraph{\(-|+|X\)}
+
+\section{Duality in the MCK model}
 We start from a strong coupling \((J \to \infty)\) spin-\(S\) impurity MCK Hamiltonian in the over-screened regime \(\left( K > 2S \right) \),
@@
 
-\section{MFL and orthogonality catastrophe in low-energy excitations of 2-CKM}
-At the stable fixed point \(J ^* = J_1^* = \frac{8}{K \rho}\), the ground states of the Hamiltonian are those of the star graph model, with a degeneracy of \(K\).
+There exists another set of dual points in the MCK model.
+This was hinted at when we looked at the degree of compassion in eq.~\ref{gamma}.
+Since \(\Gamma\) depends only on the magnitude of \(\delta\), both \(\pm \delta\) will give the same degree of compensation, same ground state energy and same ground state degeneracy \(\left(g^S_K = |\delta|+1\right)\).
+The definition of \(\delta\) gives the duality transformation as \(K \to 2S, S \to \frac{K}{2}\).
+That is, we transform from a \(K-\)channel MCK model with spin-\(S\) impurity, to a \(2S\)-channel MCK with a spin-\(\frac{K}{2}\) impurity.
+The exactly-screened model \(K=2S\) maps on to itself and is therefore self-dual under this transformation.
+
+For \(K \neq 2S\), we transform an over-screened model into an under-screened model and vice versa.
+This duality relationship allows us to infer the RG scaling behaviour of one of the models if we know that of the other.
+If we know that for a certain pair of values \(K\) and \(S\), the \(K-\)channel MCK model with spin-\(S\) impurity has an intermediate fixed point, we can immediately conclude that the \(2S\)-channel spin-\(\frac{K}{2}\) model has a strong coupling fixed point.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.45\textwidth]{./duality2.pdf}
+	\caption{./duality2.pdf}
+	\label{fig:-duality2-pdf}
+\end{figure}
+
+\subsection{Presence of a marginal Fermi liquid: Orthogonality catastrophe in two-channel MCK model}
+At the stable fixed point \(J ^* = J_1^* = \frac{2}{K \rho}\), the ground states of the Hamiltonian are those of the star graph model, with a degeneracy of \(K\).
 We now specialise to the two-channel Kondo model.
-To find the low-energy excitations on top of this ground state manifold, one can insert a tight-binding nearest-neighbour hopping between the zeroth site (the one that holds the impurity) and the first site (site that's nearest to the zeroth site) as a perturbation and calculate the diagonal and off-diagonal terms generated by this perturbation.
+To find the low-energy excitations on top of this ground state manifold, we insert a tight-binding nearest-neighbour hopping between the zeroth site (the one that holds the impurity) and the first site (site that's nearest to the zeroth site) as a perturbation and calculate the diagonal and off-diagonal terms generated by this perturbation.
 It is found that when we trace out the impurity, we are left only with real space off-diagonal terms:
@@
 These are the terms that are generated because of the presence of the impurity.
-Such a non-Fermi liquid (NFL) contribution to the effective Hamiltonian and the absence of any Fermi-liquid term should be contrasted with the local Fermi liquid excitations induced by the singlet ground state of the single-channel Kondo model at fourth order.
-We wish to point out that such NFL terms were also obtained by Coleman, et al.~\cite{Coleman_tsvelik} in terms of Majorana fermions at the zeroth site and the first site.
-They then went on to compute a single-particle self-energy renormalization coming from this NFL term that matches the phenomenological~\cite{varma2002singular} and microscopic forms of the marginal Fermi liquid self-energy~\cite{anirbanmott1,anirbanurg1}.
-We take a different route in order to calculate the self-energy contribution coming from Eq.~\ref{nfl_terms}, one that involves~\cite{anirbanmott1}.
-
-In~\cite{anirbanurg1}, it was found that the normal phase of the Mott insulator was a marginal Fermi liquid in momentum space, defined by the interaction term 
+Such a non-Fermi liquid (NFL) contribution to the effective Hamiltonian and the absence of any Fermi-liquid term at the same order should be contrasted with the local Fermi liquid excitations induced by the singlet ground state of the single-channel Kondo model~\cite{nozieres1974fermi,wilson1975renormalization,hewson1993}.
+We wish to point out that such NFL terms were also obtained by Coleman, et al.~\cite{Coleman_tsvelik} in terms of Majorana fermions at the zeroth site and the first site of the \(\sigma-\tau\) version of the two-channel Kondo model.
+They then went on to compute a single-particle self-energy renormalisation coming from this NFL term that matches the phenomenological~\cite{varma2002singular} and microscopic forms of the marginal Fermi liquid self-energy~\cite{anirbanmott1,anirbanurg1}.
+We take a different route in order to calculate the self-energy contribution coming from Eq.~\ref{nfl_terms}.
+
+In the URG analysis of the 2D Hubbard model at half-filling~\cite{anirbanurg1}, it was found that the normal phase of the Mott insulator was a metal with properties that have been phenomenologically attributed to the marginal Fermi liquid.
+The excitations of such a phase are described by a two particle-one hole composite object:
 \begin{equation}\begin{aligned}
 	\label{mfl_urg}
-	H_\text{MFL} = \sum_{k,k^\prime,k^{\prime\prime},\sigma}R \hat n_{k} \hat n_{k^\prime \overline\sigma}\left(1 - \hat n_{k^{\prime\prime}\sigma}\right) 
+	H_\text{MFL} = \sum_{k,k^\prime,k^{\prime\prime},\sigma}R \hat n_{k\sigma} \hat n_{k^\prime \overline\sigma}\left(1 - \hat n_{k^{\prime\prime}\sigma}\right) 
 \end{aligned}\end{equation}
@@
 It can be shown that the duality transformation leads to an identical MCK model~\cite{kroha_kolf_2007} (self-duality), which implies we can have identical RG flows, and our transformation simply extracts the NFL piece from the dual model.
-The self-duality also implies that the critical intermediate-coupling fixed point is unique and can be reached from either of the models.
-
-Since we are looking for a 2 particle-1 hole term in \(k-\)space, we will keep only those terms that can produce such a term:
+The self-duality also ensures that the critical intermediate-coupling fixed point is unique and can be reached from either of the models.
+
+The diagonal part of eq.~\ref{nfl_terms} is
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where \(\bar l = 3 - l\) is the channel index complementary to \(l\).
-To compare with Eq.~\ref{mfl_urg}, we will fourier transform this effective Hamiltonian (after inserting the kinetic energy of the bath) into \(k-\)space.
+where \(\bar l = 3 - l\) is the channel index complementary to \(l\). We will fourier transform this effective Hamiltonian into \(k-\)space. The NFL part becomes
 \begin{equation}\begin{aligned}
 	\label{k_space_od}
-	H_\text{eff} = \sum_{k\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + \sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \text{h.c.}
+	\sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \text{h.c.}
 \end{aligned}\end{equation}
@@
 The channel indices in Eq.~\ref{k_space_od} can be mapped to the normal directions in~\cite{anirbanmott1}.
-As specualted eariler, the three-particle interaction in Eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
-\begin{equation}\begin{aligned}
-	H_\text{eff,MFL} = \sum_{\sigma, k, k_1, k_2, l} \frac{2t^2}{J}e^{i\left(k_1 - k_2\right)a} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \text{h.c.} = \sum_{\sigma, k, k_1, k_2, l} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right)
-\end{aligned}\end{equation}
-The largest term is obtained by choosing \(k_1 = k_2 = k^\prime\):
+As specualted eariler, the 2 particle-1 hole interaction in Eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
+\begin{equation}\begin{aligned}
+	H_\text{eff,MFL} = \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{2t^2e^{i\left(k_1 - k_2\right)a}}{J} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \text{h.c.}\\
+	= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right)
+\end{aligned}\end{equation}
+The most dominant contribution comes from \(k_1 = k_2 = k^\prime\), revealing the non-Fermi liquid metal~\cite{cox_jarrell_two_channel_rev,andrei_jerez_1995}:
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
-	\Delta R_j = \frac{R_j^2}{\bar\omega - \epsilon_{j}/2 + R_j/8}
+	\Delta R_j =- \frac{R_j^2}{\omega - \epsilon_{j}/2 - R_j/8}
 \end{aligned}\end{equation}
 In the RG equation, \(\epsilon_{j}\) represents the energy of the \(j^\text{th}\) isoenergetic shell.
-It is seen from the RG equation that \(R\) is relevant in the range of \(\bar\omega = \epsilon_j -\omega\) that has been used throughout \((\omega < \epsilon_j/2)\), \textcolor{red}{leading to a fixed-point at \(R_*/8 = \bar\omega - \epsilon_*/2)\)}.
+It is seen from the RG equation that \(R\) is relevant in the range of \(\omega < \frac{1}{2}\epsilon_j\) that has been used throughout, leading to a fixed-point at \(R^*/8 = \omega - \frac{1}{2}\epsilon^*)\).
 The relevance of \(R\) is expected because the strong coupling \(J\) is irrelevant and \(R \sim 1/J\).
 
-The renormalization in \(R\) leads to a renormalization in the single-particle self-energy~\cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalization is
-\begin{equation}\begin{aligned}
-	\Delta \Sigma_l(\omega) = \rho R_*^2\int_0^{\epsilon_*} \frac{d\epsilon}{\bar\omega - \epsilon_j/2 + R_*/8}
-\end{aligned}\end{equation}
-leading to a \(k-\)space-averaged self-energy for each channel (eq. 33 of~\cite{anirbanmott1})
+The renormalisation in \(R\) leads to a renormalisation in the single-particle self-energy~\cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalisation is
+\begin{equation}\begin{aligned}
+	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}
+\end{aligned}\end{equation}
+The density of states can be approximated to be \(N^*/R^*\), where \(N^*\) is the total number of states over the interval \(R^*\).
+As suggested by the fixed point value of \(R_j\), we can approximate its behaviour near the fixed point by a linear dependence of the dispersion \(\epsilon_j\).
+The two limits of the integration are the start and end points of the RG.
+We start the RG very close to the Fermi surface and move towards the fixed point \(\epsilon^*\).
+Near the start point, we substitute \(\epsilon = 0\) and \(R = \omega\), following the fixed point condition.
+From the the fixed point condition, we also substitute \(R^*/8 = \omega - \frac{1}{2}\epsilon^*\).
+On defining \(\bar \omega = N^* \left(\omega - \frac{1}{2}\epsilon^*\right)\), we can write
 \begin{equation}\begin{aligned}
 	\label{self_energy}
-	\Sigma_l(\omega_l) \sim \omega_l \ln |\omega_l|\\
-\end{aligned}\end{equation}
-where \(\omega_l\) is the fluctuation scale for a particular channel. The self-energy also provides the quasiparticle residue for each channel\cite{anirbanmott1}:
-\begin{equation}\begin{aligned}
-	Z_l(\omega_l) = \left(2 - \ln \omega_l\right) ^{-1}
-\end{aligned}\end{equation}
-As the energy scales \(\omega_l \to 0\), the \(Z_l\) vanishes, implying that the ground state and lowest-lying excitations, in the presence of the NFL terms, are not adiabatically connected to the Fermi gas.
-This is the orthogonality catastrophe in the two-channel Kondo problem, and it is brought about by the presence of the terms in Eq.~\ref{mfl_large}.
-Such terms were absent in the similar perturbative expansion of the single-channel Kondo model, because there was no multiply-degenerate ground state manifold that allowed scattering.
-This line of argument shows that the extra degeneracy of the ground state subspace that comes about when one upgrades from the single-channel Kondo model to the MCK models is at the heart of the NFL behaviour, and the orthogonality catastrophe should be a general feature of all MCK models, even though we have demonstrated this only for the two-channel case.
-
-The fact that the marginal Fermi liquid term in eq.~\ref{mfl_large} involves all momenta means it is localised in real space.
-This can also be understood from the fact that the parent NFL term in eq.~\ref{nfl_terms} is also local.
+	\Delta \Sigma(\omega) \sim  \bar \omega \ln \frac{N^* \omega}{\bar \omega}
+\end{aligned}\end{equation}
+The self-energy also provides the quasiparticle residue for each channel\cite{anirbanmott1}:
+\begin{equation}\begin{aligned}
+	Z(\bar\omega) = \left(2 - \ln \frac{2\bar\omega}{N^* \omega}\right) ^{-1}
+\end{aligned}\end{equation}
+\textit{As the energy scale \(\omega \to 0\), the \(Z\) vanishes, implying that the ground state and lowest-lying excitations, in the presence of the NFL terms, are not adiabatically connected to the Fermi gas.
+This is the orthogonality catastrophe~\cite{varma2002singular,anderson_infraredcat,yamada_catastrophe,yamada1979orthogonality} in the two-channel Kondo problem, and it is brought about by the presence of the terms in Eq.~\ref{mfl_large}}.
+Such terms were absent in the single-channel Kondo model, because there was no multiply-degenerate ground state manifold that allowed scattering.
+This line of argument shows that the extra degeneracy of the ground state subspace and the frustration of the singlet order that comes about when one upgrades from the single-channel Kondo model to the MCK models is at the heart of the NFL behaviour, and the orthogonality catastrophe should be a general feature of all such frustrated MCK models.
 A local NFL term with a self-energy of the form in eq.~\ref{self_energy} was also obtained in the \(\sigma-\tau\) model by Coleman et al.~\cite{Coleman_tsvelik}.
 The common features show the universality between the two-channel Kondo and the \(\sigma-\tau\) models.
+
 \section{Effective Hamiltonian for low-energy excitations: \(k-\)space}

### 2021-12-31 notes/mck_urg.tex
computed most of the terms, two left
almost completed calculating all the terms, some combinations are left
obtained RG equations for X and J in presence of X

@@
 \section{RG flow of axis anisotropy term}
-We now insert a symmetry-breaking term in the Hamiltonian and study the RG flow of this term:
-\begin{equation}\begin{aligned}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{kl} J S_d^z s^z_{kl} + \frac{1}{2}\sum_{kl} J \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right) + X \left(J^z\right)^2
-\end{aligned}\end{equation}
-Here, \(s^z_{kl} = \frac{1}{2}\left(c^\dagger_{k\uparrow}c_{l \uparrow} - c^\dagger_{k\downarrow}c_{l \downarrow}\right)\), \(s^-_{kl} = c^\dagger_{k \downarrow}c_{l \uparrow}\) and \(s^+_{kl} = {s^-_{lk}}^\dagger\).
-Also, \(\tau = \hat n - \frac{1}{2}\).
-The indices \(k,l\) sum over the momentum states.
+In this section, we will study the effect of an axis-symmetry-breaking term in the Hamiltonian. We start with the Hamiltonian:
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{a,l} J_a S_d^a s^a_{l}+ \sum_a X_a {J^a}^2
+\end{aligned}\end{equation}
+Here, \(s^a_l = \frac{1}{2}\sum_{k,k^\prime,\alpha\beta}\sigma^a_{\alpha\beta}c^\dagger_{k\alpha,l}c_{k^\prime\beta, l}\) and \(\tau = \hat n - \frac{1}{2}\).
+The indices \(k,k^\prime\) sum over the momentum states while \(l\) sums over the channels.
 \(\vec S_d\) is the impurity spin operator with \(S_d^z = \pm \frac{1}{2}\).
-\(X\) is the symmetry-breaking coupling, and \(J^z = S_d^z + s^z_\text{tot}\) is the total spin.
-Using \(\left(J^z\right)^2 = \frac{1}{4} + 2S_d^z s^z_\text{tot} + \left(s^z_\text{tot}\right)^2 \), we can rewrite the Hamiltonian as
-\begin{equation}\begin{aligned}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{kl} J_\parallel S_d^z s^z_{kl} + \frac{1}{2}\sum_{kl} J_\perp \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right) + X \sum_{k_1,k_2,k_1^\prime,\atop{k_2^\prime,l_1,l_2,\atop{\sigma_1,\sigma_2}}}\frac{\sigma_1\sigma_2}{4} c^\dagger_{k_1\sigma_1,l_1}c_{k_1^\prime\sigma_1,l_1}c^\dagger_{k_2\sigma_2,l_2}c_{k_2^\prime\sigma_2,l_2}
-\end{aligned}\end{equation}
-
-The following terms renormalize \(X\):
-\paragraph{\(+|-|z\)}
-\paragraph{\(-|+|z\)}
-\paragraph{\(+|z|-\)}
-\paragraph{\(-|z|+\)}
-\paragraph{\(z|+|-\)}
-\paragraph{\(z|-|+\)}
-\paragraph{\(z|z|X\)}
-\paragraph{\(+|-|X\)}
-\paragraph{\(-|+|X\)}
+\(X\) is the symmetry-breaking coupling, and \(J^a = S_d^a + s^a_\text{tot}\) is the total spin.
+Using \(\left(J^a\right)^2 = \frac{1}{4} + 2S_d^a s^a_\text{tot} + \left(s^a_\text{tot}\right)^2 \), we can rewrite the Hamiltonian as
+\begin{equation}\begin{aligned}
+	\mathcal{H} &= \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{a,l} J_a S_d^a s^a_{l} + \sum_a X_a \left(s^a_\text{tot}\right)^2 \\
+		    &= \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{a,l} J_a S_d^a s^a_{l} + \sum_{k_1,k_2,k_1^\prime,\atop{k_2^\prime,l_1,l_2,\atop{\alpha_1,\alpha_2,a}}}X_a \frac{1}{4}\sigma^a_{\alpha_1\alpha_1^\prime}\sigma^a_{\alpha_2\alpha_2^\prime} c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}c^\dagger_{k_2\alpha_2,l_2}c_{k_2^\prime\alpha^\prime_2,l_2}
+\end{aligned}\end{equation}
+\(J_a\) has been redefined after absorbing the new \(2S_d^a s_\text{tot}^a\) piece.
+
+\subsection{Renormalisation of \(J_a\)}
+The additional set of processes that renormalise \(J_a\) are those that involve one vertex of \(X\) and one vertex of \(J\). The first such term is
+\begin{equation}\begin{aligned}
+	\frac{J_a X_b}{4} S_d^a \frac{1}{2}\sigma^a_{\beta\alpha}c^\dagger_{q\beta,l_2}c_{k\alpha,l_2}\frac{1}{\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}} \left(\sigma^b_{\alpha\beta}\sigma^b_{\alpha_1\alpha_1^\prime}c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}c^\dagger_{k\alpha,l_2}c_{q\beta,l_2} + \sigma^b_{\alpha\alpha^\prime_1}\sigma^b_{\alpha_1\beta}c^\dagger_{k\alpha,l_2}c_{k_1^\prime\alpha^\prime_1,l_2}c^\dagger_{k_1\alpha_1,l_2}c_{q\beta,l_2}\right)
+\end{aligned}\end{equation}
+All indices are summed over. Performing the sums over \(q, l_2\) and \(k\) (wherever applicable) gives
+\begin{equation}\begin{aligned}
+	&\sum\frac{J_a X_b n(D)}{8\left(\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}\right)} S_d^a \sigma^a_{\beta\alpha}N(D)\left(K \sigma^b_{\alpha\beta}\sigma^b_{\alpha_1\alpha_1^\prime}c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1} + \sigma^b_{\alpha\alpha^\prime_1}\sigma^b_{\alpha_1\beta}c_{k_1^\prime\alpha^\prime_1,l_2}c^\dagger_{k_1\alpha_1,l_2}\right)\\
+	&=\sum\frac{J_a X_b n(D)}{8\left(\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}\right)} S_d^a \sigma^a_{\beta\alpha} c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}N(D)\left(K \sigma^b_{\alpha\beta}\sigma^b_{\alpha_1\alpha_1^\prime} - \sigma^b_{\alpha\alpha^\prime_1}\sigma^b_{\alpha_1\beta}\right)
+\end{aligned}\end{equation}
+Performing the sum over \(\alpha,\beta\) gives
+\begin{equation}\begin{aligned}
+	&\sum\frac{J_a X_b n(D)}{8\left(\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}\right)} S_d^a c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}N(D)\left(K 2\delta^{ab}\sigma^a_{\alpha_1\alpha_1^\prime} - \left( \sigma^b \sigma^a \sigma^b \right)_{\alpha_1\alpha_1^\prime}\right)\\
+	&=\sum\frac{J_a X_b n(D)}{8\left(\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}\right)} S_d^a c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}\sigma^a_{\alpha_1\alpha_1^\prime}N(D)\left[\left(2K- 1\right)\delta^{ab} + \delta^{a\neq b}\right]\\
+	&=\sum\frac{J_a n(D)}{8\left(\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}\right)} S_d^a c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}\sigma^a_{\alpha_1\alpha_1^\prime} N(D)\left[\left(2K - 1\right)X_a + X_{a+1} + X_{a-1}\right]\\
+\end{aligned}\end{equation}
+
+The second such terms are obtained by switching \(X\) and \(J\):
+\begin{equation}\begin{aligned}
+	\frac{J_a X_b}{4} \left(\sigma^b_{\beta\alpha}\sigma^b_{\alpha_1\alpha_1^\prime}c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}c^\dagger_{q\beta,l_2}c_{k\alpha,l_2} + \sigma^b_{\beta\alpha^\prime_1}\sigma^b_{\alpha_1\alpha}c^\dagger_{k_1\alpha_1,l_2}c_{k\alpha,l_2}c^\dagger_{q\beta,l_2}c_{k_1^\prime\alpha_1^\prime,l_2}\right)\frac{1}{\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}} S_d^a \frac{1}{2}\sigma^a_{\alpha\beta}c^\dagger_{k\alpha,l_2}c_{q\beta,l_2}
+\end{aligned}\end{equation}
+Performing similar manipulations as above gives
+\begin{equation}\begin{aligned}
+	&\sum\frac{J_a X_b n(D)}{8\left(\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}\right)} S_d^a \sigma^a_{\alpha\beta}N(D)\left(K \sigma^b_{\beta\alpha}\sigma^b_{\alpha_1\alpha_1^\prime}c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1} + \sigma^b_{\beta\alpha^\prime_1}\sigma^b_{\alpha_1\alpha}c_{k_1^\prime\alpha^\prime_1,l_2}c^\dagger_{k_1\alpha_1,l_2}\right)\\
+	&=\sum\frac{J_a X_b n(D)}{8\left(\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}\right)} S_d^a \sigma^a_{\alpha\beta} c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}N(D)\left(K \sigma^b_{\beta\alpha}\sigma^b_{\alpha_1\alpha_1^\prime} - \sigma^b_{\beta\alpha^\prime_1}\sigma^b_{\alpha_1\alpha}\right)\\
+	&=\sum\frac{J_a X_b n(D)}{8\left(\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}\right)} S_d^a c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}N(D)\left(K 2\delta^{ab}\sigma^a_{\alpha_1\alpha_1^\prime} - \left( \sigma^b \sigma^a \sigma^b \right)_{\alpha_1\alpha_1^\prime}\right)\\
+	&=\sum\frac{J_a n(D)}{8\left(\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}\right)} S_d^a c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}\sigma^a_{\alpha_1\alpha_1^\prime}N(D)\left[\left(2K  - 1\right)X_a + X_{a+1} + X_{a-1}\right]\\
+\end{aligned}\end{equation}
+The addition renormalisation of \(J_a\) coming from the particle sector because of the presence of \(X_a\) is therefore
+\begin{equation}\begin{aligned}
+	\Delta J_a\bigg\vert_\text{p-sector} = \frac{J_a n(D)}{4\left(\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}\right)} N(D) \left[\left(2K - 1\right)X_a + X_{a+1} + X_{a-1}\right]
+\end{aligned}\end{equation}
+
+The renormalisation in the hole sector is identical to this, so the total renormalisation coming due to the presence of \(X\) is
+\begin{equation}\begin{aligned}
+	\Delta J_a = \frac{J_a n(D) N(D)}{2\left(\omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J_z}{4}\right)} \left[\left(2K - 1\right)X_a + X_{a+1} + X_{a-1}\right]
+\end{aligned}\end{equation}
+This makes \(J_a\) irrelevant.
+
+\subsection{Renormalisation of \(X_a\)}
+The only process that renormalises \(X_a\) is that of two consecutive \(X\):
+\begin{equation}\begin{aligned}
+	&c^\dagger_{q\beta,l_2}c_{k\alpha,l_2}\left(\sigma^a_{\beta\alpha}\sigma^a_{\alpha_1\alpha_1^\prime}c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1} + \sigma^a_{\beta\alpha^\prime_1}\sigma^a_{\alpha_1\alpha}c_{k_1^\prime\alpha^\prime_1,l_2}c^\dagger_{k_1\alpha_1,l_2}\right) \frac{X_a X_b}{16\left(\omega - \frac{D}{2} + \frac{X_z}{2}\right)}c^\dagger_{k\alpha,l_2}c_{q\beta,l_2}\\
+	&\quad\times\left(\sigma^b_{\alpha\beta}\sigma^b_{\alpha_2\alpha_2^\prime}c^\dagger_{k_2\alpha_2,l_3}c_{k_2^\prime\alpha^\prime_2,l_3} + \sigma^b_{\alpha\alpha^\prime_2}\sigma^b_{\alpha_2\beta}c_{k_2^\prime\alpha^\prime_2,l_2}c^\dagger_{k_2\alpha_2,l_2}\right)\\
+	&=c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}\left(\sigma^a_{\beta\alpha}\sigma^a_{\alpha_1\alpha_1^\prime} - \delta_{l_1,l_2}\sigma^a_{\beta\alpha^\prime_1}\sigma^a_{\alpha_1\alpha}\right) \frac{X_a X_b\hat n_{q\beta,l_2}\left(1 - \hat n_{k\alpha,l_2}\right)}{16\left(\omega - \frac{D}{2} + \frac{X_z}{2}\right)}c^\dagger_{k_2\alpha_2,l_3}c_{k_2^\prime\alpha^\prime_2,l_3}\left(\sigma^b_{\alpha\beta}\sigma^b_{\alpha_2\alpha_2^\prime} - \delta_{l_2,l_3}\sigma^b_{\alpha\alpha^\prime_2}\sigma^b_{\alpha_2\beta}\right)\\
+	&=c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}\left(K\sigma^a_{\beta\alpha}\sigma^a_{\alpha_1\alpha_1^\prime} - \sigma^a_{\beta\alpha^\prime_1}\sigma^a_{\alpha_1\alpha}\right) \frac{X_a X_b n(D) N(D)}{16\left(\omega - \frac{D}{2} + \frac{X_z}{2}\right)}c^\dagger_{k_2\alpha_2,l_3}c_{k_2^\prime\alpha^\prime_2,l_3}\left(K\sigma^b_{\alpha\beta}\sigma^b_{\alpha_2\alpha_2^\prime} - \sigma^b_{\alpha\alpha^\prime_2}\sigma^b_{\alpha_2\beta}\right)\\
+	&=\frac{X_a X_b n(D) N(D)}{16\left(\omega - \frac{D}{2} + \frac{X_z}{2}\right)}\left[2K \delta^{ab}\sigma^a_{\alpha_1\alpha_1^\prime}\sigma^b_{\alpha_2\alpha_2^\prime} - K \sigma^a_{\alpha_1\alpha_1^\prime}\left(\sigma^b \sigma^a \sigma^b\right)_{\alpha_2\alpha_2^\prime} - K \left(\sigma^a \sigma^b \sigma^a\right)_{\alpha_1\alpha_1^\prime}\sigma^b_{\alpha_2\alpha_2^\prime} + \left(\sigma^a \sigma^b\right)_{\alpha_1\alpha_2^\prime}\left(\sigma^b \sigma^a\right)_{\alpha_2\alpha_1^\prime}\right]\\
+	&\quad\times c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}c^\dagger_{k_2\alpha_2,l_3}c_{k_2^\prime\alpha^\prime_2,l_3}\\
+	&=\frac{X_a X_b n(D) N(D)}{16\left(\omega - \frac{D}{2} + \frac{X_z}{2}\right)}\left[K \delta^{a \neq b}\sigma^a_{\alpha_1\alpha_1^\prime}\sigma^b_{\alpha_2\alpha_2^\prime} - \sigma^{a+b}_{\alpha_1\alpha_2^\prime}\sigma^{a+b}_{\alpha_2\alpha_1^\prime}\right]c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}c^\dagger_{k_2\alpha_2,l_3}c_{k_2^\prime\alpha^\prime_2,l_3}
+\end{aligned}\end{equation}
+The \(\delta^{a \neq b}\) term does not renormalise the \(X_a\) term, but the second term does:
+\begin{equation}\begin{aligned}
+	& -\sum_{k_1,k_1^\prime,k_2,k_2^\prime,l_1,l_3,\alpha_1,\alpha_1^\prime,\alpha_2,\alpha_2^\prime,a\neq b}\frac{X_a X_b n(D) N(D)}{16\left(\omega - \frac{D}{2} + \frac{X_z}{2}\right)}\sigma^{a+b}_{\alpha_1\alpha_2^\prime}\sigma^{a+b}_{\alpha_2\alpha_1^\prime}c^\dagger_{k_1\alpha_1,l_1}c_{k_1^\prime\alpha^\prime_1,l_1}c^\dagger_{k_2\alpha_2,l_3}c_{k_2^\prime\alpha^\prime_2,l_3}\\
+	&= \sum_{k_1,k_1^\prime,k_2,k_2^\prime,l_1,l_3,\alpha_1,\alpha_1^\prime,\alpha_2,\alpha_2^\prime,c}\frac{X_{c-1} X_{c+1} n(D) N(D)}{16\left(\omega - \frac{D}{2} + \frac{X_z}{2}\right)}\sigma^{c}_{\alpha_1\alpha_2^\prime}\sigma^{c}_{\alpha_2\alpha_1^\prime}c^\dagger_{k_1\alpha_1,l_1}c_{k_2^\prime\alpha^\prime_2,l_3}c^\dagger_{k_2\alpha_2,l_3}c_{k_1^\prime\alpha^\prime_1,l_1}
+\end{aligned}\end{equation}
+This gives
+\begin{equation}\begin{aligned}
+	\Delta X_c = \frac{X_{c-1} X_{c+1} n(D) N(D)}{16\left(\omega - \frac{D}{2} + \frac{X_z}{2}\right)}
+\end{aligned}\end{equation}
+which is marginal for \(X_a = \delta_{az}X_z\).
+
+At a higher order, the following process comes into play: \(S_d^a|S_d^b|S_d^c\).
+\begin{equation}\begin{aligned}
+	&\frac{J_a J_b J_c}{\left( \omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J}{4} \right)^2} S_d^a S_d^b S_d^c s^a_{\beta\alpha}s^b_{\alpha_1\alpha_1^\prime}s^c_{\alpha^\prime\beta} c^\dagger_{q\beta,l_2}c_{k\alpha,l_2}c^\dagger_{k_1\alpha_1, l_1}c_{k_1^\prime\alpha_1^\prime,l_1} c^\dagger_{k^\prime\alpha^\prime, l_2}c_{q\beta,l_2}\\
+	&= -\frac{J_a J_b J_c \hat n_{q\beta, l_2}}{\left( \omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J}{4} \right)^2} S_d^a S_d^b S_d^c s^a_{\beta\alpha}s^b_{\alpha_1\alpha_1^\prime}s^c_{\alpha^\prime\beta} c^\dagger_{k_1\alpha_1, l_1}c_{k_1^\prime\alpha_1^\prime,l_1} c^\dagger_{k^\prime\alpha^\prime, l_2}c_{k\alpha,l_2}\\
+	&= -\frac{J_a J_b J_c n(D)}{\left( \omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J}{4} \right)^2} S_d^a S_d^b S_d^c s^a_{\beta\alpha}s^b_{\alpha_1\alpha_1^\prime}s^c_{\alpha^\prime\beta} c^\dagger_{k_1\alpha_1, l_1}c_{k_1^\prime\alpha_1^\prime,l_1} c^\dagger_{k^\prime\alpha^\prime, l_2}c_{k\alpha,l_2}\\
+\end{aligned}\end{equation}
+Another contribution can be obtained by switching the sequence of \(S_d^b,S_d^c\). Combining these gives
+\begin{equation}\begin{aligned}
+	& -\frac{J_a J_b J_c n(D)}{\left( \omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J}{4} \right)^2} S_d^a \left[S_d^b, S_d^c\right] s^a_{\beta\alpha}s^b_{\alpha_1\alpha_1^\prime}s^c_{\alpha^\prime\beta} c^\dagger_{k_1\alpha_1, l_1}c_{k_1^\prime\alpha_1^\prime,l_1} c^\dagger_{k^\prime\alpha^\prime, l_2}c_{k\alpha,l_2}\\
+\end{aligned}\end{equation}
+Such a term will renormalise \(X_a\) only if \(a,b,c\) are distinct. For such combinations, we can write
+\begin{equation}\begin{aligned}
+	S_d^a S_d^b S_d^c = S_d^e S_d^{e \pm 1} S_d^{e \mp 1} = \pm S_d^e S_d^{e+1} S_d^{e-1} = \frac{i}{8}\epsilon^{abc} \implies S_d^a \left[S_d^b, S_d^c\right] = \frac{i}{4}\epsilon^{abc}
+\end{aligned}\end{equation}
+Substituting this and summing over \(\beta\) gives
+\begin{equation}\begin{aligned}
+	& -\frac{J_a J_b J_c n(D)}{\left( \omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J}{4} \right)^2} \frac{i}{4}\epsilon^{abc} \left(s^c s^a\right)_{\alpha^\prime\alpha}s^b_{\alpha_1\alpha_1^\prime} c^\dagger_{k_1\alpha_1, l_1}c_{k_1^\prime\alpha_1^\prime,l_1} c^\dagger_{k^\prime\alpha^\prime, l_2}c_{k\alpha,l_2}\\
+	&=  s^b_{\alpha^\prime\alpha}s^b_{\alpha_1\alpha_1^\prime} c^\dagger_{k_1\alpha_1, l_1}c_{k_1^\prime\alpha_1^\prime,l_1} c^\dagger_{k^\prime\alpha^\prime, l_2}c_{k\alpha,l_2} \sum_{a=b\pm 1, c=b \mp 1}\frac{J_a J_b J_c n(D)}{\left( \omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J}{4} \right)^2} \frac{1}{8}\\
+	&=  s^b_{\alpha^\prime\alpha}s^b_{\alpha_1\alpha_1^\prime} c^\dagger_{k_1\alpha_1, l_1}c_{k_1^\prime\alpha_1^\prime,l_1} c^\dagger_{k^\prime\alpha^\prime, l_2}c_{k\alpha,l_2} \frac{J_x J_y J_z n(D)}{4\left( \omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J}{4} \right)^2}\\
+\end{aligned}\end{equation}
+Getting identical contribution from hole sector gives
+\begin{equation}\begin{aligned}
+	\Delta X_a = \frac{J_x J_y J_z n(D)}{2\left( \omega + \frac{X_z}{2} - \frac{D}{2} + \frac{J}{4} \right)^2}
+\end{aligned}\end{equation}
+This is relevant for \(X_a = \delta^{az}X_z\).
 

### 2022-01-12 combined_manuscript/backups/MultiChannelKondo_manuscript_29_Dec_448.tex
combined manuscripts, separated into main and supplementary, changed Kondo coupling to curly J

\documentclass[reprint,prb,superscriptaddress]{revtex4-1}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,color,ulem,soul,lipsum}
\allowdisplaybreaks
\bibliographystyle{apsrev4-1}
\usepackage{xcolor}

%\pagecolor[rgb]{0.5,0.5,0.5}
%\color[rgb]{1,1,1}

\begin{document}

\tableofcontents

\section{Stargraph and its properties}
\subsection{Hamiltonian and wavefunctions}
\noindent As shown in the previous section, at the heart of multi channel Kondo there is a stargraph problem whic is the zero mode of the lowenergy fixed point Hamiltonian of the Multi channel Kondo. In this section our focus will be on the stargraph problem itself.
\begin{figure}[!h]
\centering
\includegraphics[scale=0.4]{plt/stargraph_first}
\caption{This is a stargraph model with one central spin $\vec{S}_d$ and $K$ outer spin $1/2$s. The central spin is coupled with all the outer spins with Heisenberg coupling with coupling strength $\alpha$.}
\label{fig:stargraph_first}
\end{figure}
As shown in the Fig.\ref{fig:stargraph_first} above one central spin ($\vec{S}_d$) is connected with $K$ spins forming a $K$ channel stargraph problem corresponding to the $K$-channel Kondo problem. The Hamiltonian of this above model is given as 
\begin{eqnarray}
H &=& \alpha \vec{S}_d.\sum_{i=1}^{K}\vec{S}_i=\alpha \vec{S}_d.\vec{S} \nonumber\\
&=& \frac{\alpha}{2} (\vec{J}^2-\vec{S}^2-\vec{S}_d^2)~,~~\alpha >0.
\label{eq:stargraph_hamiltonian}
\end{eqnarray}
where $\vec{J}=\vec{S}+\vec{S}_d$ and $\vec{S}=\sum_{i=1}^{K} \vec{S}_i$. One can see that the large psin $S$ can take many possible values as this is made out of $K$ spin 1/2s. We can see $[H,J]=0=[H,J^i]$ for  $i=x,y,z$, $[J^i,J^j]\neq 0$ for $i\neq j$. Also the operators $\hat{Z}=2^{K+1}S_d^z\prod_{i=1}^{K} S_i^z $ and $\hat{X}=2^{K+1}S_d^x\prod_{i=1}^{K} S_i^x $ commutes with the Hamiltonian, $[H,\hat{Z}]=0=[H,\hat{X}]$ though $[\hat{Z},\hat{X}]\neq 0$, in general.
 Thus we can form the CSCO with $H,J,J^z,S,S_d$. For a particular value $S$, $J$ can take two values $S\pm S_d$ with the energies $-\alpha S_d(S_d+1\mp J)$ respectively. $S_d$ is fixed thus the energy values only depends on the corresponding $J$ value of the state. As the energy does not depends on the $J^z$, all $2J+1$ $J^z$ states labeled by $|S_d,S;J,J^z\rangle$ are degenerate. It is easy to see that the ground state has energy $E=-\alpha S_d(S_d+1+J)$ with  $J=S-S_d$, thus $E_g=-\alpha S_d(S_{max}+1)$ with $S$ taking the maximum possible value $S_{max}=K/2$.

\subsubsection{Ground state wavefunction}
\noindent Above calculations show stargraph with $K$ channels has $K$-fold ground state degeneracy, states labeled as $|S_d,S;J,J^z\rangle$ where $J^z$ takes $K=2J+1$ distinct values, $J^z=\{-J,\cdots,+J \}$. Here our goal is to find the wavefunction in the fundamental spin basis $|S_d^z,S_1^z,\cdots,S_K^z\rangle$. To achieve that we use the Clebsch-gordon coefficients, we know for two spins $j_1$ and $j_2$  with total spin $J$ and $J^z=M$ one can expand the state as 
\begin{eqnarray}
|j_1,j_2;J,M\rangle &=& \displaystyle\sum_{\substack{m_1=\{-j_1,\cdots,j_1\} \\ m_2=\{-j_2,\cdots,j_2\} }}   \mathcal{C}^{j_1,m_1;j_2,m_2}_{j_1,j_2;J,M} |j_1,m_1;j_2,m_2 \rangle ,~~~~
\end{eqnarray}
where $j_1^z=m_1$ and $j_2^z=m_2$ and $\mathcal{C}^{j_1,m_1;j_2,m_2}_{j_1,j_2;J,M}$ is the Clebs-Gordon coefficient. In our problem two spins $S_d$ and $S$ are forming one large spin $J$ represented by the state $|S_d,S;J,J^z\rangle$, in the ground state $J=S-1/2$. Thus the ground state $|S_d,S; (S-\frac{1}{2} ),M\rangle \equiv |\alpha\rangle$ can be expanded as
%{%\tiny
\begin{eqnarray}
%&&\bigg|S_d,S;\bigg(S-\frac{1}{2}\bigg),M\bigg\rangle = ww\\
&&|\alpha\rangle= \displaystyle\sum_{\substack{m_1=\{-S_d,\cdots,S_d\} \\ m_2=\{-S,\cdots,S\} }} \mathcal{C}^{S_d,m_1;S,m_2}_{S_d,S;J,M} ~~   | S_d,m_1 \rangle \otimes  |S,m_2  \rangle ,~~~~
\end{eqnarray}
%}
Because in the ground state $S$ is maximum, the state $|S,S^z\rangle$ can be decomposed in terms of a two spin problem of spin $1/2$ and $S-1/2$ forming the state $|1/2,S-1/2;S,S^z\rangle$ which can be further expanded in the basis $ |1/2,m'_1 \rangle \otimes  |S-1/2,m'_2  \rangle $ where $m'_1,m'_2$ are the z-components of the spin $1/2$ and $S-1/2$. Next we decompose the state $|S-1/2,m'_2\rangle$ in further smaller spin problem and so on. This way we finally arrive at the ground state wavefunction in terms of the fundamental basis $|S_d^z,S_1^z,\cdots,S_K^z\rangle$, give as
\begin{eqnarray}
|S_d,S;J,M\rangle &=& \sum_{S_d^z,\{S_i^z\}} \mathcal{D}_{S_d^z,\{S_i^z\}} |S_d^z,S_1^z,\cdots,S_K^z\rangle
\label{eq:wf_fundamental_basis}
\end{eqnarray}
where $\{S_i^z\}\equiv(S_1^z,\cdots,S_K^z)$ and the coefficient $\mathcal{D}_{S_d^z,\{S_i^z\}}$ is given as 
\begin{eqnarray}
\mathcal{D}_{S_d^z,\{S_i^z\}}  &=& \displaystyle\sum_{\substack{m_2=[-S,S]\\ m_4=[-(S-1/2),(S-1/2)]\\~.~\\  m_{2N-4}=[-1,1]   }} \mathcal{M}^{S_d^z,S_1^z,~.~.~ ,S_K^z}_{m_2,m_4,~.~.~ ,m_{2N-2}}~,~~~~~~
\end{eqnarray}
and further the coefficients $\mathcal{M}^{S_d^z,S_1^z,~.~.~ ,S_K^z}_{m_2,m_4,~.~.~, m_{2N-2}} \equiv\Sigma$, are made out of the products of Clebsh-Gordon Coefficients
\begin{eqnarray}
%\mathcal{M}^{\{m^{(1)}\}}_{\{m^{(2)}\}} &=& 
\Sigma=\mathcal{C}^{S_d,S_d^z;S,m_2}_{S_d,S;J,M} ~~ \mathcal{C}^{S_1,S_1^z;(S-1/2),m_4}_{S_1,(S-1/2);S,m_2} \cdots  \mathcal{C}^{S_{K-1},S_{K-1}^z;S_K,S_K^z}_{S_{K-1},S_{K};1,m_{2N-4}}~,~~~~
\end{eqnarray}
Using these wavefunctions we can calculate various entanglement features of this stargraph problem.

\subsection{Entanglement properties}
\noindent Using the above exact wavefunctions we can numerically compute various entanglement properties of this stargraph model.

\subsubsection{Impurity entanglement entropy}
\begin{figure}[!h]
\centering
\includegraphics[scale=0.32]{plt/EE_multi_channel_ANN.png}
\caption{Caption }
\label{fig:EE_d}
\end{figure}
\noindent Here we are interested in finding the entanglement of the central impurity spin with the rest of the multi-channel bath zero mode. For single channel case the the ground state is unique and is $|J=0,J_z=0 \rangle = \frac{1}{\sqrt{2}} (|\uparrow_{d}\downarrow_0\rangle -|\downarrow_d \uparrow_0\rangle)$. Thus, one can easily calculate the reduced density matrix of the impurity by tracing out the $0^{th}$ state. From that reduced denisty matrix the entanglement entropy is $\log 2$, which is maximum possible for a spin-1/2. In the case of multi-channel problem there are $K$ orthogonal set of ground states $|J^z\rangle$, for each such state the entaglement is different. The state $|J^z\rangle \equiv |S_d=1/2,S=K/2;(S-1/2),J^z\rangle$ can be written in the fundamental basis as shown in the Eq.\eqref{eq:wf_fundamental_basis}. Then the density matrix is $\rho=|J^z\rangle\langle J^z|$ from which we can calculate the reduced density matrix by partial tracing the impurity degree of freedom 
%$\rho_{d}=\textrm{Tr}_{d} \rho=\sum_{S_d^z} \langle S_d^z| \rho | S^z_d\rangle$. 
\begin{eqnarray}
\rho_{d}&=& \textrm{Tr}_{d} \rho=\sum_{S_d^z} \langle S_d^z| \rho | S^z_d\rangle ~,~~EE_d = -\rho_{d} \log \rho_{d}
\end{eqnarray}
\noindent The eigenvalues of this reduced density matrix given by $\lambda_i$ is called entanglement spectrum. We are interested in the von-Neumann entanglement entropy of the impurity spin with thte rest ($EE_d$). We are intersted in the scaling of this entanglement entropy with the channel number. As shown in the Fig.\ref{fig:EE_d} the x-axis is the channel number and for a particular channel there are may possible entanglement values corresponding to different $J^z$ states. The minimum entanglement entropy state (associated with the $J^z=J$ state) decreases show the classical nature of this maximally polarized state. On the other hand the maximum entanglement entropy (associated with $J^z_{min}$ state) for a particular channel $K$ is saturating to $\log K$ in the large $K$ limit. Another important result that we see, for any odd value of $K$ the minimum entanglement entropy associated with $J^z=0$ is $\log 2$ shows a formation of perfectly entangled state made out of more than 2 spins (e.g; singlet). In this state $|J^z=0\rangle$ all the $K$(odd) outer spins participate in quantum scattering with the central impurity spin in such a way the central spin is maximally entangled which is not the case for any other $J^z$ state. In the large $K$ limit irrespective it's even and odd nature there are always a $J^z_{min}$ state where the central impurity spin is maximally entangled.
\begin{figure}[!h]
\centering
\includegraphics[scale=0.32]{plt/outer_EE_multi_channel_ANN.png}
\caption{caption}
\label{fig:EE_outer}
\end{figure}
In a $K$ channel system all the outer spins are equivalent (has $Z_N$ symmetry), thus studying the entanglement of any one outer spin with the rest is enough. Here we do a similar entanglement entropy study where we get the reduced density matrix ($\rho_o$) by partial tracing out any one outer spin say the $l^{th}$ ($1\leq l \leq K$) one $S^z_{l}$. 
\begin{eqnarray}
\rho_{o} &=& \textrm{Tr}_{l} \rho =\displaystyle\sum_{S^z_{l}} \langle S^z_l | \rho | S^z_{l} \rangle~,~EE_o=-\rho_{o}\log \rho_{o}
\end{eqnarray}
We do a similar entanglement scaling with the channel number $K$. We find that minimum entanglement entropy associated with the state $J^z=J$ is approaching zero in the limit $K\gg 1$. In contrast the minimum entanglement entropy associated with $J^z_{min}$ state is saturating at $\log 2$ in the large $K$. Thus in the state $J^z=0$ for any $K$ (or $J^z=\pm 1/2$ for $K\gg 1$) any outer spin is maximally entangled with the rest.

\par The above entanglement studies Fig.(\ref{fig:EE_d},\ref{fig:EE_outer}) show  that for odd channel case there exist a state $J^z=0$ where the central spin $S_d$ and any outer spin $S_i$ is maximally entangled with the rest. This shows the special and unique property of the stargraph ground state where you can create state made out of morethan 2 spins where each any every one is maximally entangled with the rest. Thus this stargraph ground state is very important in the quantum information theory. 
\textbf{write here}

\subsubsection{Macroscopic singlet state}
\noindent  The $|J^z=0\rangle_{K} $ state of a $K$(odd) channel stargraph problem can be very genrally written as
\begin{eqnarray}
|J^z=0\rangle_K &=& \frac{1}{\sqrt{2}} \bigg[ |\Uparrow\rangle_d \otimes |\gamma_{\downarrow}\rangle_K -  |\Downarrow\rangle_d \otimes |\gamma_{\uparrow}\rangle_K \bigg]  
\label{eq:maximally_entangled_state}
\end{eqnarray}
where $|\Uparrow\rangle_d$ and $|\Downarrow\rangle_d$ represents the impurity state $S_d^z=\pm 1/2$ respectively. Let's define $U_{+}$ represents the set of all possible sub-systems of the set $[K]$ with $(K+1)/2$ numbers of elements in it. We define complement of any one set $g\in U_+$ , $g^{c}$ such that $g\cup g^{c}=[K]$.
\begin{eqnarray}
|\gamma_{\sigma} \rangle_K &=& \frac{1}{\sqrt{{K \choose \frac{K+1}{2}} }} \displaystyle\sum_{\substack{ g\in U_{+} }} \prod_{\substack{i\in g \\j\in g^c}} |\sigma_i\rangle \otimes |\bar{\sigma}_j \rangle~,~ 
\end{eqnarray}
where $\sigma_i=\pm 1/2$ and $\bar{\sigma}_i=-\sigma_i$, $\pm 1/2$ representing the state $\uparrow_i,\downarrow_i$ respectively for the $i^{th}$ spin. Thus the density matrix for this state $|J^z=0\rangle_K$ can be written as $\rho=|J^z=0\rangle_K \langle J^z=0|_K$. For this state one can simply verify that $\rho_{d}=\textrm{Tr}_d \rho=\frac{1}{2} (|\gamma_{\downarrow}\rangle_K \langle\gamma_{\downarrow}|_K + |\gamma_{\uparrow}\rangle_K \langle\gamma_{\uparrow}|_K)$  which has eigenvalues $1/2,1/2$ leading to the entanglement entropy $S_{d}= \log 2$. Similary one can verify that the entanglement entropy of any other spin with the rest is $\log 2$. Thus all the spins in the state eq.\eqref{eq:maximally_entangled_state} is maximally entangled with the rest representing a macroscopic singlet state with morethan $2$ spins.

\subsubsection{Mutual Information}

\begin{figure}[!h]
\includegraphics[scale=0.32]{plt/I_2_vs_Nch_0_1}
\caption{ds}
\label{fig:MI_d_o}
\end{figure}
\noindent In the above study our focus was on the von-Neumann entanglement entropy, now we are interested in the correlation signatures present in the stargraph grounds states. Mutual inforamtion is one such measure which captures the correlations present between two subsystems (A,B) in a particular state defined as
\begin{eqnarray}
I^2(A:B)=S_A+S_B-S_{A\cup B}
\end{eqnarray}
where $S_{A}$ is the von-Neumann entanglement entropy of the subsystem $A$ with the rest. Here we are interested in computing two types of mutual inforamtions first, study the mutual information between the impurity-spin and one outer spin $I^2(d:o)$. Because all the outer spins are symmetric, the mutual information between impurity-spin with any one outer spin is same and can capture the correlation between two $A$ and $B$. We have done a scaling study of this mutual information for different channel numbers $K$. As shown in the Fig.\ref{fig:MI_d_o} in the large $K$ limit the maxima of the mutual information associated with the state $J^z_{min}$ is saturating at $1.076$ and the Mutual information associated with the state $J^z=J$ is decreasing showing the classical limit.
\begin{figure}[!h]
\includegraphics[scale=0.32]{plt/I_2_vs_Nch_1_2}
\caption{ds}
\label{fig:MI_o_o}
\end{figure}
Next, we have done a similar study by calculating the mutual information between two outer spin $I^2(o:o)$. In this also we find that the maximum mutual information between any outer spins saturates at the value $1.076$ similar to the $I^2(d:o)$ case.

\par As can be seen from the above Figure.(\ref{fig:MI_d_o},\ref{fig:MI_o_o}) that  both the maximum mutual information of $I^2(d:o)$ and $I^2(o:o)$ try to saturate near the same value. Thus in the large $K$ limit in the $J^z_{min}$ state mutual information between any two spins in the stargrah model is same saturating at a constant value ($1.076$). Though the difference can be seen in the state $J^z=J$ where the mutual information thus correlation s between two outer spins vanishes in the large $K$ limit faster than the mutual information between the impurity and any one outer spin. Thus correlation wise there is no difference between impurity-outer pair and outer-outer pair in the large $K$ limit.

\subsubsection{Multi-partite information}
\noindent Similar to the mutual inforamtion one can calculate any higher order mutli-partie inforamtion to find the nature of the correlations present in different ground states. We define the tripartite information among three subsystems $A,B,C$ as $I^3_{ABC} = (S_A+S_B+S_C)-(S_{AB}+S_{BC}+S_{CA})+S_{ABC}~$. This tri-parite information scaling with the number of channels $K$ also shown behavior similar to the mutual information case, the highest tri-partite information is associated with the $J^z_{min}$ state and saturating in the limit of $K\gg 1$. One can measure $N-$partite information for a collection of subsystems (CSS) $\{\mathcal{A}\}\equiv\{A_1,A_2,\cdots,A_K\}$. To define the $N-$partite information, we first define the power set of the CSS $\{\mathcal{A}_N\}$ as $\mathcal{P}(\{\mathcal{A}_{N}\})$, and the collection of all subsets of $\mathcal{P}(\{\mathcal{A}_{N}\})$ with $m$ subsystems in it as $\mathcal{B}_m(\{\mathcal{A}_N\})\equiv \{ Q~| ~Q\subset \mathcal{P}(\{\mathcal{A}_{N}\}), |Q|=m \}$. We also define the union and intersection of all the subsystems present in $Q$ as ${V}_{\cup}({Q})\equiv \bigcup_{A\in Q} A$ and ${V}_{\cap}({Q})\equiv \bigcap_{A\in Q} A$ respectively. Finally, the von Neumann entanglement entropy of the subsystem $A$ is given by $S_{A} $. Then the $N-$partite information that we are interested in is defined as
\begin{eqnarray}
I^{N}_{\{\mathcal{A}_N\}} &=& \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.~~~~
\label{eq:I_N_definition}
\end{eqnarray}
Studying these mutli-partite informations one can understand the nature of the correlations present among the outer spins.
\begin{figure}
\includegraphics[scale=0.32]{plt/I_N_vs_N_N9.png}
\caption{This figure shows how the $m-partite$ information varies with $m$ showing the entanglement distribution amond different number of outer-spins.}
\label{fig:Im_vs_m}
\end{figure}
\noindent Our study of this multi-partite information presented in the above Fig.\eqref{fig:Im_vs_m} shows that the higher oreder multi partite informations decreaseas as you increase the order folloring a power law. \textbf{Show the fittings.}

\subsection{Correlation Studies}
Apart from the entanglement studies one can calculate various correlation and energy studies in the various degenerate ground state of this stargraph model.
\subsubsection{Quantum energy}
\begin{figure}[!h]
\centering
\includegraphics[scale=0.34]{plt/Quantum_Energy_per_channel}
\caption{This shows the variation of quantum energy per channel with $1/N$, where $N=N_{ch}+1$ is the total number of spins in the systems including the impurity spins. }
\label{fig:quantum_energy}
\end{figure}
\noindent In the stargraph model Hamiltonian there is a classical ising term ($S_d^zS^z$) and a quantum fluctuation term. Here we are interested in the energy expectation value arising from the quantum fluctuation part of the Hamiltonian (eq.\ref{eq:stargraph_hamiltonian}). We define ising enregy $E_{ising}$ and quantum energy $E_{Q}$ in the ground state $|\psi_g\rangle$ as,
\begin{eqnarray}
E_{ising} = |\langle \psi_g | \mathcal{H}^c_0 | \psi_g \rangle|, E_{Q} &=& |\langle \psi_g | \mathcal{H}^Q_0 | \psi_g \rangle|=|E_g|-|E_{ising}|~, \nonumber\\
&=& {\alpha S_d(S+1)}- |E_{ising}|.
\end{eqnarray}  
This quantum energy $E_Q$ is generated by the spin-flips between the impurity spin and the outer spin. Our goal here to understand the nature of this $E_Q$ as we go to the large $K$ limit, whether there are some remenant quantum fluctuation even in the thermodynamic limit. To answer that questio we intrduce another important parameter, quantum enrgy per channel, $e_Q=|E_Q|/K$ . We know in the gorund state $K=2S$ thus,
\begin{eqnarray}
e_Q &=& \frac{\alpha S_d(S+1)}{K} - \frac{|E_{ising}|}{K} ~,~\nonumber\\
%&=& \alpha\frac{(N_{ch}+2)}{4N_{ch}}-\frac{|E_{ising}|}{N_{ch}} ~,~ \nonumber\\
%&=& \alpha \bigg(\frac{1}{4} +\frac{1}{2N_{ch}} \bigg)-\frac{|E_{ising}|}{N_{ch}}~,~\nonumber\\
&=& \frac{\alpha S_d}{2} -\frac{1}{K} \bigg(|E_{ising}| -\alpha S_d  \bigg)~,~
\end{eqnarray}
Thus from the above equation of quantum energy per channel one can see that in the large channel limit 
\begin{eqnarray}
e_Q = \frac{\alpha S_d}{2}- \frac{|E_{ising}|}{K} < \frac{\alpha S_d}{2}~,~K\rightarrow \infty, 
\end{eqnarray}
As shown in the above Fig.\ref{fig:quantum_energy} for the case of $S_d=1/2$, for a particular channel $K$ the maximum quantum energy corresponds to the $|J^z|_{min}$ state and the minimum is related to the $|J^z|=J$ state. In the large channel limit one can see the quatnum energy associated with the $|J^z|=J$ vanishes showing the classical nature of this state where there is no quantum fluctuation present. Whereas, in the state $|J^z|_{min}$ there are finite non-zero quantum fluctuation present in it, showing the true quantum nature of this macroscpic singlet state as we have already discussed.

\subsubsection{Staggerred magnetization}
\noindent  One can reqrite the Hamiltonian as $\alpha \vec{S}_d.\vec{S}=(\alpha/4) [( \vec{S}+\vec{S}_d)^2-( \vec{S}-\vec{S}_d)^2]$, this shows that $\vec{J}$ and the staggered magnetization $\vec{M}_s=\vec{S}-\vec{S}_d$ is both good quantum number for in this stargraph model. For single channel case $K=1$, ground state is an unique 2-spin singlet $|\psi_g\rangle =\frac{1}{\sqrt{2}} (|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle = |J=0,J_z=0\rangle$, which showns the prefect screening. Our goal here to capture the breakdown of the screening by calculating this staggerd magnetization for a multichannel problem. 
\begin{figure}
\includegraphics[scale=0.36]{plt/Staggered_mag_50.png}
\caption{This shows how the staggered magnetization changes with the number of channels $N_{ch}$.}
\label{fig:st_mag}
\end{figure}
%
%
%For the single channel case both the $\vec{S}_d$ and $\vec{S}$ are spin-1/2 object and the total spin is defined as $\vec{J}=\vec{S}_d+\vec{S}$. Here $\vec{S}$ is the total outer spin.
%
%\begin{eqnarray}
%M_s^2 = \langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle &=& \langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle \nonumber\\
%&=& 2 \langle \psi_g | \vec{S}_d^2 +\vec{S}^2 |\psi_g\rangle \nonumber\\
%&=& 3
%\end{eqnarray}
For a general $K$ cahnnel we find that 
\begin{eqnarray}
M_s^2 &=& \langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle \nonumber\\
%&=&    2\bigg(S_d(S_d+1)+ \frac{K(K+2)}{4}\bigg)- \frac{(K+1)(K-1)}{4}   \nonumber\\
%&=& 2S_d(S_d+1) + \frac{1}{2}(K^2+2K) - \frac{1}{4}(K^2-1)\\
&=& 2S_d(S_d+1) +\frac{K^2}{4} + K +\frac{1}{4}
%%%%&=& \frac{N_{ch}^2}{4}+N_{ch}+\frac{7}{4}
\end{eqnarray}

\noindent Thus, staggered magnetization squared per channel,
\begin{eqnarray}
m_s^2=\frac{M_s^2}{K^2}= \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}
%=\frac{1}{4}+\frac{1}{N_{ch}}+\frac{7}{4N_{ch}^2} \xrightarrow[]{N_{ch}\gg 1} \frac{1}{4}+\frac{1}{N_{ch}}~,
\end{eqnarray}
Which shows, in the large channel limit this staggered magnetization , $m^2_s\Rightarrow 1/4.$ for any finite $S_d$.
Using the $SU(2)$ property of our problem, we can define $m_s$ for each spatial direction, in 3D there are three independent spatial direction.
\begin{eqnarray}
\langle(m_s^x)^2\rangle=\langle(m_s^y)^2\rangle=\langle(m_s^z)^2\rangle=\frac{1}{3}m_s^2~,~~   
\end{eqnarray}
Just to recall, for the single channel case $\langle (m_s^z)^2 \rangle =1$ showing the perfect screening, on the otherhand in the large channel limit this becomes $\langle (m_s^z)^2 \rangle =1/12$ showing the breakdown of the screening. For the $S_d=1/2$ case we have shown how this staggered magnetization perchannel decreases in the multichannel case in the Fig.\ref{fig:st_mag}. This clearly shown that this staggerd magnetization is maximum.

%\begin{eqnarray}
%\frac{\vec{J}^2}{N_{ch}^2}&=&\frac{(\vec{S}_d+\vec{S})^2}{N_{ch}^2}= \frac{N^2_{ch}-1}{4N^2_{ch}} \xrightarrow[]{N_{ch}\gg 1} \frac{1}{4}~. \nonumber 
%\end{eqnarray}
%
%
%To begin with we first recall that for single channel case $M_s^2=3$.
%
%We define $m_Q^2=m_s^2-1/4$ which in the the large $N_{ch}$ limit becomes $1/N_{ch}$ and eventually vanishes in the $N_{ch}\rightarrow \infty$ limit. 
%
%
%\noindent Thus to summarize,
%\begin{enumerate}
%\item In the single channel problem, $\langle (m_s^z)^2 \rangle=1$. 
%\item In the multi-channel case,  
%$\langle (m_s^z)^2 \rangle=\frac{1}{3N_{ch}}+\frac{1}{12}+\frac{7}{12N_{ch}^2} \xrightarrow[]{N_{ch}\gg 1} \frac{1}{12}+\frac{1}{3N_{ch}}\rightarrow \frac{1}{12}$. 
%This show partial screening.
%\end{enumerate}

Thus it is important to find the scaling of

\begin{enumerate}
%\item $M_s^2$ vs $N_{ch}$.
\item Uncompensated Quantum Fluctuation vs $N_{ch}$.
\end{enumerate}

\subsubsection{Correlation study}
Here we want to calculate various correlation functions in the ground state. We start with the expectation value of $J_z^2$ in the ground state $|\psi_g\rangle$,
\begin{eqnarray}
j_z^2&=&\frac{1}{N_{ch}}\langle \psi_g | J_z^2 | \psi_g \rangle~=\frac{1}{N_{ch}} \bigg[ J^2-(J_x^2+J_y^2) \bigg] ~,\nonumber\\
%&=& \frac{1}{N_{ch}} \bigg[ (S^2-1/4)-(J_x^2+J_y^2) \bigg] \nonumber\\
&=& \frac{1}{N_{ch}} \bigg[ \frac{(N_{ch}^2-1)}{4}-(J_x^2+J_y^2) \bigg]
\end{eqnarray}

\begin{eqnarray}
\langle \psi_g | J_{z}^2 | \psi_g \rangle_{max} &=& \bigg(\frac{N_{ch}-1}{2}\bigg)^2~,\nonumber\\
\langle \psi_g | J_{z}^2 | \psi_g \rangle_{min} = \bigg(\frac{N_{ch}-(N_{ch}-1)}{2}\bigg)^2&=&\frac{1}{4}~,~\textrm{for $N_{ch}$ even}.\nonumber\\
&=& 0 ~,~\textrm{for $N_{ch}$ odd}.
\end{eqnarray}
Thus,
\begin{eqnarray}
\langle (J_x)^2+(J_y)^2 \rangle_{max}&=&\langle J^2 \rangle - \langle J_z^2 \rangle_{min} ~,\nonumber\\
&=& \frac{N_{ch}^2-1}{4}-\frac{1}{4}=\frac{N_{ch}^2-2}{4}~, \textrm{for $N_{ch}$ even } \nonumber\\
&=& \frac{N_{ch}^2-1}{4}~, \textrm{for $N_{ch}$ odd } \nonumber
\end{eqnarray}
Which shows, for single channel case $N_{ch}=1$, this quntum fluctuation expectation value vanishes, while for multi channel this takes non-zero values. Thus 
\begin{eqnarray}
\frac{1}{N_{ch}}\langle (J_x)^2+(J_y)^2 \rangle_{max}
&=& \frac{N_{ch}}{4}-\frac{1}{2N_{ch}}  ~, \textrm{for $N_{ch}$ even } \nonumber\\
&=& \frac{N_{ch}}{4}-\frac{1}{4N_{ch}}~, \textrm{for $N_{ch}$ odd } \nonumber
\end{eqnarray}
Thus in the large channel number limit $N_{ch}\gg 1$, one can see that 
\begin{eqnarray}
\frac{1}{N_{ch}}\langle (J_x)^2+(J_y)^2 \rangle_{max}
\rightarrow \frac{N_{ch}}{4}~,~\textrm{for both even and odd $N_{ch}$}
\end{eqnarray}
\noindent $J_z$ can take values $\{-J,-J+1,\cdots,J-1,J\}$ in the ground state, where $J=S-1/2=(N_{ch}-1)/2$.

\subsection{Calculating thermodynamic quantities}
We take the stargraph Hamiltonian and do the exact diagonalization and find the entire eigenspectrum. Using the full eigenspectrum we calculate the partition function $Z=\sum_i e^{-\beta E_i}$, where $E_i$ is the energy of the $i^{th}$ state. One can rewrite this partition function interms of the state degeneracies as $Z=\sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon} $, where $d(\epsilon)$ is the degeneracy of the state with energy $\epsilon$. Thus the free energy is given as $\mathcal{F}=-k_BT\log Z$. 
\subsubsection{Thermal entropy}
Thermal entropy is defined as $S=-(\frac{\partial \mathcal{F}}{\partial T})_H$, where $H$ represents a constant magnetic field. In ourcase we will be interested in the zero field case. 
\begin{eqnarray}
\mathcal{F}&=& -k_B T\log Z \nonumber\\
S &=& -(\frac{\partial \mathcal{F}}{\partial T}) = -k_B \log Z -k_B T \frac{1}{Z} \frac{dZ}{dT}
\end{eqnarray}
%Now 
%\begin{eqnarray}
%Z =\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon} ~~\Rightarrow ~~  \frac{dZ}{dT} &=& \sum_\epsilon d(\epsilon) e^{-\beta \epsilon}  (-\epsilon) \frac{d\beta}{dT} \nonumber\\
%&=& \sum_\epsilon d(\epsilon) e^{-\beta \epsilon}   \frac{ \epsilon}{k_B T^2} =k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   
%\end{eqnarray}
Thus we get
\begin{eqnarray}
S &=& -k_B \log \sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon}  -\frac{1}{\beta} \frac{k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   }{\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon}} \nonumber\\
\lim_{\beta\rightarrow \infty} S &=& -k_B \log_2 d(\epsilon_{G})~,~~\lim_{\beta\rightarrow 0} S = -k_B \log \sum_\epsilon d(\epsilon)  \nonumber
\end{eqnarray}
\begin{figure}
\centering
\includegraphics[scale=0.36]{plt/ThermalEntanglementVS_LogTemperature_}
\caption{This shows the variation of thermal entropy with the temperature.}
\label{fig:thermal_entropy}
\end{figure}

Thus at the extreme temperature it is easy to calculate the termal entropy, but it is difficult to visualize for any intermediate temperatures. Thus we plot the thermal entropy (unit $\log 2$) for different tempertures and for different channels in Fig.\ref{fig:thermal_entropy}. This shows at the extreme temperature the termal entropy saturates and at the intermediate temperature it changes from one to the other like a soliton like solution. At low temperature the thermal enttropy in the unit of $\log 2$ is not always quanlized but at high temperature it is. To understad this let's say at low temperature $S_T/k_B\log T=\Omega=\log_2 d(\epsilon_{G})$. Here $d(\epsilon_{G})$ is always integer and equal to the channel number $K$. Thus 
\begin{eqnarray}
d(\epsilon_{G}) &=& 2^{\Omega}=K
\end{eqnarray}
From our study we can see that for some channel number we get $S_T/k_B\log T$ tobe integer. One can easily see that those $K=2^n$ channel cases, $n$ is an integer will have integer thermal entropy. Thus between $m$ and $m+1$ integer thermal entropy plateau there will be $(2^m-1)$ number of fractional thermal entropy plateau, which is always odd.

\subsubsection{Suseptibility}
\noindent Here we want to calculate the field suseptibility of the stargraph. For that we need the entire spectrum of the stargraph Hamiltonian in the presence of field. There are two ways one can capture the suseptibility of the stargraph, first, by putting a small field to the central impurity and the other way is put a uniform field on all the outer spins and capture the suseptibility.

\textit{Impurity-field susceptibility :} Now we add small magnetic field to the impurity spin and calculte the suseptibility as a function of temperatur for different channel cases.
\begin{figure}
\centering
\includegraphics[scale=0.36]{plt/Central_Field_Chi_Powerlaw_}
\caption{Impurity susseptibility vs temperature.}
\label{fig:suseptibility_impurity}
\end{figure}
As shown in the Figure.\ref{fig:suseptibility_impurity} above, for all $K>2$ case we can see that, at low temperature the suseptibility follows power law as afunction of temperature. 
\begin{eqnarray}
\chi_{imp}(T) \sim T^{-1} ~,~ \chi_{outer} \sim T^{-1}
\end{eqnarray}
The exponent for all the channels $K>2$ is $-1$. This shows the presence of an universality class. The powerlaw shows the critical nature of the system.

\textit{Outer-field suseptibility: } Similar study can be done by putting an uniform field on all outer spins and calculating the suseptibility. Here also for all channles $K>2$ the exponent is $-1$ and supports the existance of universality and criticality.
\begin{figure}
\centering
\includegraphics[scale=0.36]{plt/Outer_Field_Chi_Powerlaw_}
\caption{Outer susseptibility vs temperature.}
\label{fig:suseptibility_outer}
\end{figure}
This susceptibility clearly shown the breakdown of screening in the multichannel cases with degenerate ground states in constrast to the single channel suseptibility which saturates at a finite value at low temperature.

\section{Excitation properties}
Here we start with the low energy zero mode fixed point Hamiltonian for the two-channel Kondo obtained under URG treatment. Our goal here is to add excitations on top of this ground state and using the perterbation theory. In doing so we consider the leading order scatter apprearing in the lowest order in the perturbative expansion. Note, in the fixed point zero mode Hamiltonian impurity spin is coupled with the bath electrons via spin exchange coupling, there is no charge exchange coupling present. 
\begin{eqnarray}
H^{(2)}&=& \alpha \vec{S}_{imp}.(\vec{S}_1+\vec{S}_2)~~,~~\vec{S}_i =  \frac{1}{2}~ c_{i,\alpha}^{\dagger}~ \vec{\sigma}_{\alpha,\beta}~ c_{i,\beta}
\label{eq:channel-2-spin}
\end{eqnarray}
Here $\vec{S}_i=1,2$ represents the spin degree of freedom present in the origin of the $i^{th}$ channel. Thus one can rewrite the Eq.\eqref{eq:channel-2-spin} interms of the electronic degree of freedom as,
\begin{eqnarray}
&&\mathcal{H}_0= H_{0_1}+H_{0_2} \nonumber\\
&=&\sum_{i=\{1,2\}}\bigg[ \alpha S^z_{imp}. (n_{i,\uparrow}-n_{i,\downarrow})/2 + \frac{1}{2}  ( S_{imp}^{+} c^{\dagger}_{i,\downarrow} c_{i,\uparrow} + \textrm{h.c.}  )\nonumber \bigg]
\end{eqnarray}
Here the basis we are interested in is $\{\mathcal{B}\}=\{|S^z_{imp},n_{1,\uparrow},n_{1,\downarrow},n_{2,\uparrow},n_{2,\downarrow}\rangle \}$. In this basis we write down all $2^3=8$ states of the spin Hamiltonian eq.\eqref{eq:channel-2-spin}
First the two degenerate ground states with energy $-\alpha= E_{\alpha_0}= E_{\alpha_1}$ is given as,
\begin{eqnarray}
|\alpha_0\rangle &=& \frac{1}{\sqrt{6}} \bigg[2|\Downarrow,1,0,1,0\rangle-|\Uparrow,0,1,1,0\rangle-|\Uparrow,1,0,0,1\rangle\bigg] \nonumber\\
|\alpha_1\rangle &=& \frac{1}{\sqrt{6}} \bigg[2|\Uparrow,0,1,0,1\rangle-|\Downarrow,1,0,0,1\rangle-|\Downarrow,0,1,1,0\rangle\bigg] \nonumber
\end{eqnarray}
The doubly degenerate lowestlying excited state has energy $E_{\beta_1}=E_{\beta_2}=0$.
\begin{eqnarray}
|\beta_0\rangle &=& \frac{1}{\sqrt{2}}\bigg[|\Downarrow,1,0,0,1\rangle-|\Downarrow,0,1,1,0\rangle \bigg] \nonumber\\
|\beta_1\rangle &=& \frac{1}{\sqrt{2}} \bigg[ |\Uparrow,1,0,0,1\rangle-|\Uparrow,0,1,1,0\rangle \bigg]
\end{eqnarray}
Above these two excited states there are another dengenerate excited state manifold with energy $ E_{\gamma_0}=E_{\gamma_1}=E_{\gamma_2}=E_{\gamma_3}=\frac{\alpha}{2}$.
\begin{eqnarray}
|\gamma_{0}\rangle &=&\frac{1}{\sqrt{3}} \bigg[|\Uparrow,0,1,0,1\rangle+|\Downarrow,1,0,0,1\rangle+|\Downarrow,0,1,1,0\rangle \bigg] \nonumber\\
|\gamma_{1}\rangle &=& \frac{1}{\sqrt{3}}\bigg[ |\Uparrow,1,0,0,1\rangle+|\Uparrow,0,1,1,0\rangle+|\Downarrow,1,0,1,0\rangle \bigg] \nonumber\\
|\gamma_{2}\rangle &=& |\Uparrow,1,0,1,0\rangle~,~~|\gamma_{3}\rangle = |\Downarrow,0,1,0,1\rangle 
\end{eqnarray}
Note this spin Hamiltonian has total $8$ states, where ground state is double degenerate with energy $-\alpha$ and the lowest exicites state with energy $0$ is also double degnerate and the second excited state with energy $\alpha/2$ is 4-fold degenerate. 
\par On top of the zero mode spin-channel interactions we want to consider the effect of the momentum space kinetic energy term $\sum_{k}\epsilon_k (n_{1,k}+n_{2,k})$. We assume identical dispersion for both the channels. Our zero mode spin Hamiltonian is written in the real space, thus it will be easier to do the perterbation theory on the real space. The fourier transformation of the momentum space kinetic energy  term leads to real space hopping term. For simplicity we will be considering the neareast neighbor hoppings between sites within each channels. The real space hopping contributino to the Hamiltonian $H_X$ with the hooping strength is 
\begin{eqnarray}
H_{X} &=& -t \displaystyle\sum_{\substack{<1,l_1> \\ <2,l_2>}} (c^{\dagger}_{1,\sigma}c_{l_1,\sigma}+c^{\dagger}_{2,\sigma}c_{l_2,\sigma}+ ~\textrm{h.c.})
\end{eqnarray}
Here $l_i$ represents the nearest site to the origin of the $i^{th}$ channel. Thus here we are interested in studying the Hamiltonian $\mathcal{H}_0+H_X$. The perterbating term $H_x$ contains scattering which takes the states of the zero mode Hamltonain out of spin-channel scattering space. Thus befor we start the perturbation theroy we must expand the basis of the zero mode Hamiltonian itself. Thus the basis which contains the nearest neighbor sites of both the channels is given as 
\begin{eqnarray}
&&\{\mathcal{B}_{extnd}\} \equiv  \{\mathcal{B}\} \otimes  \{|n_{l_1,\uparrow},n_{l_1,\downarrow},n_{l_2,\uparrow},n_{l_2,\downarrow}\rangle\} \nonumber\\
&=& \{|S^z_{imp},n_{1,\uparrow},n_{1,\downarrow},n_{2,\uparrow},n_{2,\downarrow}\rangle \otimes |n_{l_1,\uparrow},n_{l_1,\downarrow},n_{l_2,\uparrow},n_{l_2,\downarrow}\rangle\} \nonumber\\
\end{eqnarray}
Note there are $2^4=16$ elements in the subspace $\{|n_{l_1,\uparrow},n_{l_1,\downarrow},n_{l_2,\uparrow},n_{l_2,\downarrow}\rangle\}$. In the spin-channel basis $\{\mathcal{B}\}$ there $2$ degenerate ground states. Because the unpurterbed Hamiltonian $\mathcal{H}_0$ has no scattering terms outside the spin sector, in the extended basis $\{\mathcal{B}_{extnd}\}$ the total ground state deneracy becomes simply $2\times 2^4$, $32$ fold. Thus the total hamiltonian we are interested in is 
\begin{eqnarray}
\mathcal{H} &=& \frac{\alpha\hbar}{2}~ \vec{S}_d. \displaystyle\sum_{i=\{1,2\}} \displaystyle\sum_{\alpha,\beta\in\{\uparrow,\downarrow\}}c_{i\alpha}^{\dagger} \vec{\sigma}_{\alpha\beta} c_{i\alpha} +H_X
%-t\displaystyle\sum_{i=\{1,2\}}\displaystyle\sum_{\substack{\langle i,l_i \rangle\\ \sigma}}(c^{\dagger}_{i,\sigma} c_{l_i,\sigma}+ \textrm{h.c.}) 
%\\
%&=& \displaystyle\sum_{i=1,2} \bigg[ \alpha\hbar~ \vec{S}_d. \vec{S}_i -t\displaystyle\sum_{\substack{\langle i,l_i \rangle\\ \sigma}}(c^{\dagger}_{i,\sigma} c_{l_i,\sigma}+ \textrm{h.c.}) \bigg] \nonumber\\
%&=& \mathcal{H}_0+H_X
\end{eqnarray}
There are two degenrate states $|\alpha_1\rangle$ and $|\alpha_2\rangle$. Thus the two degenerate ground states in the above basis is give as,
\begin{eqnarray}
|\tilde{\alpha}_0\rangle &=&| {\alpha}_0\rangle\otimes |n_{l_1,\uparrow},n_{l_1,\downarrow},n_{l_2,\uparrow},n_{l_2,\downarrow}\rangle \\
|\tilde{\alpha}_1\rangle &=& | {\alpha}_1\rangle\otimes |n_{l_1,\uparrow},n_{l_1,\downarrow},n_{l_2,\uparrow},n_{l_2,\downarrow}\rangle
\end{eqnarray}
Using degenerate perturbation theory we calculate the first and the second order corrections to the Hamiltonian. The first order and the second order low energy effective Hamiltonian is given as 
\begin{eqnarray}
H^{(1)} &=& \sum_{ij} |\alpha_i\rangle \langle \alpha_i  | V| \alpha_j \rangle \langle \alpha_j |~\nonumber\\
H^{(2)} &=& \sum_{ij} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j |
\end{eqnarray}
where $|\alpha_i\rangle$ represents the ground states with energy $E_0$ and $\mu_l$ represents the ecvited states with energy $E_l$. One can easily check the diagonal term in effective Hamiltonain coming from the $1^{st}$ or any $odd$ order correction is zero as the state never returns to the original starting state via odd number of scatterings. For the case of first order it is easy to see that the off-diagonal correction to the effective Hamiltonian is also zero. Thus the lowest order where we expect the non-zero corrections is the second order. We first calculate the diagonal correction in the first order
\begin{eqnarray}
H^{(2)}_{diag} &=& \sum_{i} \sum_l |\alpha_i\rangle\langle \alpha_i | \frac{|\langle \alpha_i  | V| \mu_l \rangle|^2 }{E_0-E_{l}}
\end{eqnarray}
As single scattering always takes the state outside of the spin-channel, the state $V|\alpha_i\rangle$ is an excited state with energy $0$ ($=E_l$). This $\alpha_i$ representing the ground state can take total $32$ configurations as discussed. Out of this $32$ states $| {\alpha}_0\rangle\otimes |n_{l_1,\uparrow},n_{l_1,\downarrow},n_{l_2,\uparrow},n_{l_2,\downarrow}\rangle$ can take $16$ configurations and $| {\alpha}_1\rangle\otimes |n_{l_1,\uparrow},n_{l_1,\downarrow},n_{l_2,\uparrow},n_{l_2,\downarrow}\rangle$ can take the rest 16 configurations. Note the two degnereate states $|\tilde{\alpha}_0\rangle$  and $|\tilde{\alpha}_1\rangle$ is labeled by the $J^z$ eigenvalue $\pm 1/2$ respectively, where $J^z$ is the total z-component of the impurity and zero modes of the baths. Thus these $32$ ground states can be seperated in two 16 state groups labeled by the $J^z=\pm 1/2$ eigenvalues. For the $J^z=1/2$ sector we get the effective Hamiltonian
\begin{eqnarray}
H^{(2)}_{diag} (1/2) &=& \frac{2t^2}{E_0} \hat{I} - \frac{2t^2}{3E_0} ( S_{l_1}^z + S_{l_2}^z)
%= \frac{2t^2}{E_0} \hat{I} - \frac{4t^2}{3E_0} \bigg[S_{l_1}^z+S_{l_2}^z\bigg]
\end{eqnarray}
Similarly the for $J^z=-1/2$ we get 
\begin{eqnarray}
H^{(2)}_{diag} (-1/2) &=& \frac{2t^2}{E_0} \hat{I} + \frac{2t^2}{3E_0} (S_{l_1}^z+S_{l_2}^z)
%= \frac{2t^2}{E_0} \hat{I} + \frac{4t^2}{3E_0} \bigg[S_{l_1}^z+S_{l_2}^z\bigg]
\end{eqnarray}
where $S_{l_i}^z=(n_{l_i\uparrow}-n_{l_i\downarrow})/2.$ This above result shows that the diagonal correlation to the LEH coming from the ground states $J^z=\pm 1/2$ has a emergent field term. 
\begin{eqnarray}
H^{(2)}_{diag} &=& -4t^2 \hat{I}
\end{eqnarray}
But the total contribution shows the trivial nature of the diagonal part in the LEH. This clearly shown that there is no Fermi liquid terms present in low energy in the 2-channel Kondo problem. Here, $\hat{I}$ is the identity operator made out of all $2^4=16$ possible number operator combinations as shown below
\begin{eqnarray}
\hat{I} &=& \sum_{\hat{o}=\hat{n},(1-\hat{n})} \hat{o}_{l_1,\uparrow}\hat{o}_{l_1,\downarrow} \hat{o}_{l_2,\uparrow}\hat{o}_{l_2,\downarrow}
\end{eqnarray}
Due to the ground state degeneracy in the 2-channel problem, there are possible quantum scattering within the ground state manifold among those degenerate states. This leads to a low energy effective Hamiltonian which is offdiagonal in nature as shown below,
\begin{eqnarray}
H_{NFL}&=&H^{(2)}_{off} = \sum_{i\neq j} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j | \nonumber\\
&=& -\frac{8t^2}{3} [ (S_1^z)^2 c_{2\uparrow}^{\dagger}c_{2\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) \nonumber\\
&+& (S_2^z)^2 c_{1\uparrow}^{\dagger}c_{1\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) ] + \textrm{h.c.} ~,~~~~
\label{eq:hamiltonian_NFL}
\end{eqnarray}
This LEH is purely a non-Fermi liquid. The emergenec of non-Fermi liquid is primarily coming due to the degenerate ground states present in the stargraph problem in the absence of the realspace hopping terms. One can see that though there was no prior inter channel direct interactions, the LEH shows the emergence of such terms through correlated quantum scatterings.

\subsection{Studying the LEH}
\noindent In order to understnad this non-Fermi liquid we calculate some thermodyanmic quantities like impurity specific heat and suseptibility. First we calcualte the self energy of this NFL hamiltonian. In the real space one can get a diagonal piece from the above equation by using the Fermionic anticommutation relations.
\begin{eqnarray}
H_{eff}^{off,(2)} |_{diag} &=& -(16t^2/3) [ (S_1^z)^2+ (S_2^z)^2 ]   
\end{eqnarray}
We can find the corresponding momentum space Hamiltonian by doing the fouries transforamtion to the Hamiltonian  $H_{eff}^{off,(2)} |_{diag} $ as.
\begin{eqnarray}
%&&-\frac{16t^2}{3}\bigg[\bigg(\frac{1}{4N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{2N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow} \bigg) + \bigg(\frac{1}{4N} \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma}-\frac{1}{2N^2} \displaystyle\sum_{k_1,k_2} \tilde{n}_{k_1\uparrow} \tilde{n}_{k_2\downarrow} \bigg) \bigg] \nonumber\\
H_{eff}^{off,(2)} |_{diag}&=& -\frac{4t^2}{3} \frac{1}{N} \bigg[ \displaystyle\sum_{k,\sigma} n_{k\sigma}(1-\frac{1}{N} \displaystyle\sum_{k_2}  n_{k_2,-\sigma}  ) \nonumber\\
&&+ \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma} ( 1-\frac{1}{N} \displaystyle\sum_{ k_2} \tilde{n}_{k_2,-\sigma}  ) \bigg]  
\end{eqnarray}
The above relation leads to the correction to the kinetic energy, which is
\begin{eqnarray}
%\bar{\epsilon}_k&=& \epsilon_k+\Sigma_k \nonumber\\
\bar{\epsilon}
_k-\epsilon_k=\Sigma_k 
% -\frac{4t^2}{3N} \bigg(1-\frac{1}{N} \displaystyle\sum_{k_2}  \langle n_{k_2,-\sigma} \rangle \bigg) \nonumber\\
&&= -\frac{4t^2}{3N^2}\bigg(1-\frac{N}{e^{(\epsilon_k-\mu)/k_BT}+1}\bigg)
\label{eq:self-energy-NFL}
\end{eqnarray}
Using the self-energy we calculate the impurity speciftic heat defined as $C_{imp}=C(J^*)-C(0)$ which is defined as
\begin{eqnarray}
C_{imp} &=& \sum_{\Lambda,\sigma} \beta \bigg[ \frac{(\bar{\epsilon}_{\Lambda})^2 e^{\beta \bar{\epsilon}_{\Lambda}}}{( e^{\beta \bar{\epsilon}_{\Lambda}} +1)^2}  -\frac{({\epsilon}_{\Lambda})^2 e^{\beta {\epsilon}_{\Lambda}}}{( e^{\beta {\epsilon}_{\Lambda}} +1)^2} \bigg]
\end{eqnarray}
Here we are intersted in the low temperature behavior of this impurity specific-heat. Using the self-energy obtained above we calculate the impurity susecptibility for $t=0.1$ and $\alpha=1$. 
\begin{figure}
\centering
\includegraphics[scale=0.36]{plt/FINAL_fitted_Cv_t_0p1.png}
\caption{This figure shows the variation of the impurity specific heat with the temperature.}
\label{fig:Cv_imp}
\end{figure}
The above Fig.\ref{fig:Cv_imp} shows that at low temperature follows logarithmic behavior for the single channel case which is in agreement with the results known in the literature [CITE].
\begin{eqnarray}
\frac{C_{imp}}{T} \propto \log T
\end{eqnarray}
%\subsubsection{Exact diagonalization}
Apart from this impurity specific heat one can calculate the magnetic susceptibilty. For that we do the exact diagonalizaton of the NFL Hamiltonian eq.\eqref{eq:hamiltonian_NFL} and get the entire eigenspectrum. On all those different state we can calculate teh expectation value of the magnetization squared $\langle (S^z)^2 \rangle$. Using these expectation values we can calculate the suseptibility by using the formula
\begin{eqnarray}
\chi &=& \beta\bigg[\frac{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} \langle \bar{S}^{z2} \rangle}{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} } -\frac{\sum e^{-\beta \epsilon_{\Lambda}} \langle S^{z2 }\rangle }{\sum e^{-\beta \epsilon_{\Lambda}} } \bigg] 
\end{eqnarray}
We numerically compute the $\chi$ from the definition above and study it's dependence on temperature.
\begin{figure}[!h]
\centering
\includegraphics[scale=0.36]{plt/NFL_Chi_log_0p1}
\caption{Suseptibility}
\label{fig:NFL_susecptibility}
\end{figure}
The above figure shows that at low temperture the suseptibility follows the logarithmic behavior.
\begin{eqnarray}
\chi(T) &\propto& \log T
\end{eqnarray}

\noindent As expected both the $C_{imp}/T$ and $\chi$ follows the logarithmic behavior which is known in the literature for the two channel Kondo problem. From the slopes we can calculate the Wilson ratio $C_{imp}/T\chi$, we find that in our case where we have taken upto two nearest neighbors to each zeroth sides of two channels the Wilson ratio is $\approx 8.3$ which is greater than the actual value. For a smaller system with only one nearest neighbor to the zeroth site of both the channels we find the Wilson number if even higher shows that in a larger system the Wilson ratio approaches a smaller value. Direct fourier transformation on the $H^{(2)}_{off}$ leads to the LEH in momentum space showing higher order scattering involving electronic degree of freedoms. For simplicility we only focus on the diagonal piece which is $H_k$ given as
\begin{eqnarray}
H_k&=&-\frac{4t^2}{3 N^4} \displaystyle\sum_{\substack{k_1,k_2\in (1),\\ k_3,k_4\in (2)\\ \sigma,\sigma'}} n_{k_1,\sigma} (1-n_{k_2,-\sigma})  \tilde{n}_{k_3,\sigma'} (1-\tilde{n}_{k_4,-\sigma'}) ~,~~~~\nonumber
\end{eqnarray}
where (1) and (2) represnts the sets of momentum space points in two channels respectively. The local NFL has a fourth order contribution to the diagonal momentum space density-density interaction, this is a multiplication of MFL terms of two channels. There are lower order contributions also as shown in the above sections.

%\begin{eqnarray}
%H_{eff}^{off,(2)} \bigg|_{diag} &=&  \frac{4t^2}{3\alpha} \bigg[ \frac{1}{N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} n_{k_1,\sigma} n_{k_2,-\sigma} \bigg] \times \bigg[\frac{1}{N} \displaystyle\sum_{k_1,\sigma} \tilde{n}_{k_1,\sigma} -  \frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} \tilde{n}_{k_1\sigma}\tilde{n}_{k_2,-\sigma}\bigg] \nonumber\\
%\end{eqnarray}
%The Fourier transformation of the electronic creation operator gives
%\begin{eqnarray}
%c_{r\sigma}^{\dagger} &=& \frac{1}{\sqrt{N}} \displaystyle\sum_{k} e^{-ikr} c_{k\sigma}^{\dagger}~,~\rightarrow c_{r\sigma} = \frac{1}{\sqrt{N}} \displaystyle\sum_{k} e^{ikr} c_{k\sigma} \nonumber\\
%c_{r,\sigma}^{\dagger} c_{r,-\sigma} &=& \frac{1}{N} \displaystyle\sum_{k,k'} e^{-i(k-k')r} c_{k,\sigma}^{\dagger} c_{k',-\sigma}    \nonumber\\
%n_{r\sigma}&=& c_{r\sigma}^{\dagger}c_{r\sigma} = \frac{1}{N} \displaystyle\sum_{k,k'} e^{-i(k-k')r} c_{k\sigma}^{\dagger} c_{k'\sigma} \nonumber\\
%n_{r\uparrow}n_{r\downarrow} &=& \frac{1}{N^2} \displaystyle\sum_{\substack{k_1,k_2\\k_3,k_4}} e^{-i(k_1-k_2)r} e^{-i(k_3-k_4)r} c_{k_1\uparrow}^{\dagger} c_{k_2\uparrow} c_{k_3\downarrow}^{\dagger} c_{k_4\downarrow}  
%\end{eqnarray}
%
%\begin{eqnarray}
%n_{r\uparrow}+n_{r\downarrow}-2n_{r\uparrow}n_{r\downarrow} &=& \frac{1}{N} \displaystyle\sum_{k,k',\sigma} e^{-i(k-k')r} c_{k\sigma}^{\dagger} c_{k'\sigma} -\frac{2}{N^2} \displaystyle\sum_{\substack{k_1,k_2\\k_3,k_4}} e^{-i(k_1-k_2)r} e^{-i(k_3-k_4)r} c_{k_1\uparrow}^{\dagger} c_{k_2\uparrow} c_{k_3\downarrow}^{\dagger} c_{k_4\downarrow}   \nonumber\\
%\textrm{The diagonal piece from this}  &\Downarrow & \nonumber\\
%&& \frac{1}{N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{2}{N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow}
%\end{eqnarray}

%
%Thus one gets,
%\begin{eqnarray}
%(S_1^z)^2 \bigg|_{diag} &=& \frac{1}{4} (n_{1\uparrow}-n_{1\downarrow})^2\bigg|_{diag}=(n_{1\uparrow}+n_{1\downarrow}-2n_{1\uparrow}n_{1\downarrow})/4 \bigg|_{diag}\nonumber\\
%%&=& \frac{1}{4N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{2N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow} \nonumber\\
%&=& \frac{1}{4N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{4N^2} \displaystyle\sum_{k_1,k_2,\sigma} n_{k_1,\sigma} n_{k_2,-\sigma}
%\end{eqnarray}
%We know that the diagoanl peice of the following terms is given as
%%\begin{eqnarray}
%%c_{r,\uparrow}^{\dagger} c_{r,\downarrow}  c_{r',\uparrow} c^{\dagger}_{r',\downarrow} &=& \frac{1}{N^2} \displaystyle\sum_{\substack{k_1,k_2\\k_3,k_4}} e^{-i(k_1-k_2)r} e^{-i(k_3-k_4)r} c_{k_1,\uparrow}^{\dagger} c_{k_2,\downarrow} c_{k_4,\uparrow}c_{k_3,\downarrow}^{\dagger}  \bigg|_{diag} \nonumber\\
%%%&\Downarrow & \nonumber\\
%%%&& \frac{1}{N^2} \displaystyle\sum_{\substack{k_1,k_2}} e^{-i(k_1-k_2)r} e^{-i(k_2-k_1)r} c_{k_1,\uparrow}^{\dagger} c_{k_2,\downarrow} c_{k_1,\uparrow}c_{k_2,\downarrow}^{\dagger}  \bigg|_{diag} \nonumber\\
%%&=& -\frac{1}{N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow}(1-n_{k_2\downarrow})
%%\end{eqnarray}
%
%Thus the diagonal piece coming from the term,
%\begin{eqnarray}
%&& c_{2\uparrow}^{\dagger}c_{2\downarrow} \bigg(  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger} \bigg)\Rightarrow \frac{1}{N} \displaystyle\sum_{k,k'} e^{-i(k-k')r} c_{k,\sigma}^{\dagger} c_{k',-\sigma}  \nonumber
%\end{eqnarray}

%\begin{widetext}
%\begin{eqnarray}
%H_{eff}^{off,(2)} \bigg|_{diag} &=& -\frac{8t^2}{3} \bigg[ \frac{1}{4N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{2N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow} \bigg] \times \bigg[\frac{1}{N^2} \displaystyle\sum_{k_1,k_2} \tilde{n}_{k_1\uparrow}(1-\tilde{n}_{k_2\downarrow}) + (\uparrow \rightarrow \downarrow)\bigg] \times 2 \nonumber\\
%%&=& -\frac{2t^2}{3} \bigg[ \frac{1}{N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{2}{N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow} \bigg] \times \bigg[\frac{1}{N} \displaystyle\sum_{k_1,\sigma} \tilde{n}_{k_1,\sigma} -  \frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} \tilde{n}_{k_1\sigma}\tilde{n}_{k_2,-\sigma}\bigg]\times 2 \nonumber\\
%&=& -\frac{4t^2}{3} \bigg[ \frac{1}{N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} n_{k_1,\sigma} n_{k_2,-\sigma} \bigg] \times \bigg[\frac{1}{N} \displaystyle\sum_{k_1,\sigma} \tilde{n}_{k_1,\sigma} -  \frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} \tilde{n}_{k_1\sigma}\tilde{n}_{k_2,-\sigma}\bigg]~,~~~~ 
%\end{eqnarray}
%%
%%
%%\begin{eqnarray}
%%H_{eff}^{off,(2)} \bigg|_{diag} &=&  -\frac{4t^2}{3} \bigg[ \frac{1}{N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{N^2} \displaystyle\sum_{k_1,k_2} n_{k_1,\sigma} n_{k_2,-\sigma} \bigg] \times \bigg[\frac{1}{N} \displaystyle\sum_{k_1,\sigma} \tilde{n}_{k_1,\sigma} -  \frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} \tilde{n}_{k_1\sigma}\tilde{n}_{k_2,-\sigma}\bigg] \nonumber\\
%%\label{eq:off-ham-110}
%%\end{eqnarray}
%
%
%\end{widetext}

Similar to the two channel case, our calculation of the diagonal LEH for the three channel case shown the absence of local Fermi liquid term. In this case we get non-zero contribution from all the three ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$.
We get the diagonal contribution to the LEH in the second order is 
\begin{eqnarray}
H^{(2)}_{eff, diag} &=& - \frac{7.2 J^2}{\alpha} \hat{I}
\end{eqnarray}
The contribution associater to different ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$ is given respectively as $- \frac{2.4 J^2}{\alpha} \hat{I} + \hat{\mathcal{F}},- \frac{2.4 J^2}{\alpha} \hat{I} ,- \frac{2.4 J^2}{\alpha} \hat{I} - \hat{\mathcal{F} }$,
\noindent where $\hat{\mathcal{F}}$ is a function of diagonal number oprators of sites nearest neighbor to the zeroth site of each channels. We also get offdiagonal terms in the LEH which is shown in the Appendix.\ref{ap:three-channel}.

\section{Channel Anisotropy and Berry phase}
\noindent So far we have talked the stargraph problem where all the outer spin is coupled with the central impurity spin with Heisenberg cuopling of equal strength. This model has a special symmetry where any rearrangement of the outer spins keeps the stargraph Hamiltonian invariant. Here we wish to break this symmetry of this Hamiltonian by choosing the individual coupling strength of the outer spin with the central impurity spin different. We start with the general coupling Hamiltonian written as 
\begin{eqnarray}
H (\vec{\Lambda}) &=& \sum_{i=1}^{K} \lambda_i\vec{S}_d.\vec{S}_i
\end{eqnarray}
where $\lambda \equiv (\lambda_1,\cdots,\lambda_K)$. So far we have considered the case where $\lambda_i=\alpha,~\forall i$.

\noindent Here we start with the multi-channel zero mode model, any put anisotropy in the counping $\alpha$. Let's start with a simpe possibility where there are two coupling $\alpha_1$ and $\alpha_2$, where both the $\alpha_1,\alpha_2$ are positive and negative. We write down the Hamiltonian corresponding to these cases,
\begin{eqnarray}
H_{an}&=& \alpha_1 \vec{S}_d.\vec{S}_1 + \alpha_2 \vec{S}_d.\vec{S}_2 %\\
%&=& \frac{\alpha_1}{2} (J_1^2-S_d^2-S_1^2) + \frac{\alpha_2}{2} (J_2^2-S_d^2-S_2^2)
\end{eqnarray}
%Now let's find out the CSCO for this above Hamiltonian. The operators which commutes with the Hamiltonian are $J_1,J_2,S_d,S_1,S_2$. Now can we choose the basis to be, 
%\begin{eqnarray}
%|J_1^z,S_1^z\rangle \otimes |S_d^z\rangle \otimes |J_2^z,S_2^z\rangle
%\end{eqnarray}
%In the ground state both the $S_1$ and $S_2$ will be maximum and $J_1$ and $J_2$ will be minimum. 
%\begin{enumerate}
%\item Term 1: $S_1=N_1/2$, where $N_1$ is the number of outer spin connected with the central spin with the coupling constant $J_1$. There are two possible $J_1$ values $J_1=(S_1+1/2)$ and $J_1=(S_1-1/2)$. In the ground state the being maximum $J_1=(S_1-1/2)$. Thus the energy contribution to the ground state from the the first term is 
%\begin{eqnarray}
%-\frac{\alpha_1(S_1+1)}{2}
%\end{eqnarray}
%
%\item Term 2: Similar calculation show the contribution of the second term in the ground state energy is
%\begin{equation}
%-\frac{\alpha_2(S_2+1)}{2}
%\end{equation}
%Thus total ground state energy is 
%\begin{eqnarray}
%E_g  &=& -\frac{\alpha_1(S_1+1)}{2}-\frac{\alpha_2(S_2+1)}{2}
%\end{eqnarray}
%
%\end{enumerate}
%
%
%%In this ground state there are $2S_1$ number of $J_1^z$ eigen values with same energy contribution and similarly there are $2S_2$ number of $J_2^z$ states with same energy. Thus we can write down the ground state as 
%%\begin{eqnarray}
%%&& |J_1^z,S_1^z\rangle \otimes |S_d^z\rangle \otimes |J_2^z,S_2^z\rangle \nonumber\\
%%&=& |J_1,J_1^z\rangle \otimes |J_2,J_2^z\rangle
%%\end{eqnarray}
%
%
%One cna solve this problem in another way by rewriting the Hamiltonian as
%\begin{eqnarray}
%H=
%\end{eqnarray}
%
There are $K_1$ and $K_2$ numbers of outer spins respectivelty which are connected to the central spin with the coupling with $\alpha_1$ and $\alpha_2$. Thus the total number of channels is $K=K_1+K_2$. When $\alpha_1=0, \alpha_2\neq 0$ then we end up with a multi-channel problem with $K_1$ number of channels thus the degeneracy becomes $K_1$ and for $\alpha_2=0, \alpha_1\neq 0$ the degneracy becomes $K_2$. Though this can be trivially verified from the above Hamiltonian, the important property of this problem is the robustness of the ground state degeneracy. As we vary $\alpha_1$ and $\alpha_2$, to study the ground state degeneracy. We find that for any values $\alpha_1$  and $\alpha_2$ such that $\alpha_1/\alpha_2\neq 0$ and $\alpha_2/\alpha_1\neq 0$ the ground state degeneracy remains constant at $K=K_1+K_2$. It is known in the literature [CITE someone] that under above mentioned an-isotropy the low energy effective Hamiltonian becomes a multi-channel Kondo with smaller number of channels.

\begin{figure}\centering
\includegraphics[width=0.5\textwidth]{plt/Anisotropy_Channel:3}
%{example-image-a}
\caption{Add proper figures.}
\end{figure}

%
%\subsection{Berry phase}
%
%We start with the general multi-channel problem where the coupling strength with the central impurity spin of the $i^{th}$ channel is $\alpha_i$. Here our goal is to use the robustness of the ground state degeneracy of the star-graph model to build the gaue theoretic structure. We define the hamiltonian of star-graph as 
%\begin{eqnarray}
%H_{st}(\vec{\alpha}) &=& \displaystyle\sum_{i=1}^{K} \alpha_i \vec{S}_d.\vec{S}_i
%\end{eqnarray}
%We define the $K$-dimensional soupling space where one possible sonfiguration is denoted by the vector $\vec{\alpha}=\mathcal{N}(\alpha_1,\alpha_2,\cdots,\alpha_K)$, where $\mathcal{N}$ is the normalization factor, where $\alpha_i\neq 0$ and $\alpha_i\neq \infty $, $\forall i\in[K]$. The Schrodinger equation for the Hamiltonian reads as 
%\begin{eqnarray}
%H_{st}(\vec{\alpha}) \Psi_{m} (\vec{\alpha}) = E_{m} (\vec{\alpha}) \Psi_{m} (\vec{\alpha})
%\end{eqnarray}
%Here, we are only interested in the ground state manifold, where the energy of the state is $E_{g}$. Due to the degeneracy ($K$-fold) there are $K$ states in that manifold with the same energy labeled by say $k$. Thus the equation for the ground state manifold reads
%\begin{eqnarray}
%H_{st}(\vec{\alpha}) \Psi^{k}_{g} (\vec{\alpha}) = E_{g} (\vec{\alpha}) \Psi^{k}_{g} (\vec{\alpha})
%\end{eqnarray}
%One can do a simple transformation to make the ground state energy zero. Thus
%\begin{eqnarray}
%H_{st}(\vec{\alpha}) \Psi^{k}_{g} (\vec{\alpha}) &=&  0 \nonumber\\
%i\hbar \frac{\partial \Psi(\vec{\alpha(t)}) }{\partial t} &=& H_{st}(\vec{\alpha(t)}) \Psi(\vec{\alpha(t)}) =0
%\label{eq:hamiltonian_eq}
%\end{eqnarray}
%As the ground state is degenerate one can take any linera combinations of the states to create arbitrary basis state (orthogonal and normalized). Let's say $\psi_k(\vec{\alpha}(t))$ represents the arbitrary basis state, which should  be smooth in $t$ locally and follow the Schrodinger equation,
%\begin{eqnarray}
%H_{st}(\vec{\alpha}(t)) \psi_k(\vec{\alpha}(t)) &=&  0 
%\end{eqnarray}
%We here try to find the solution of the Eq.\eqref{eq:hamiltonian_eq}, we start with the trial solution 
%\begin{eqnarray}
%\eta_a(t) &=& U_{ab}(t) \psi_b(t)
%\end{eqnarray}
%
%\textbf{Finish this section.}

 \section{Topology and Gauge theory}

%\subsection{Gauge theory and Wilson Loops}
%
%%\subsection{Twist-translation operator}
%\noindent We define a translation operator $\hat{T}$ and twist operator $\hat{O}$ to describe the ground state manifold. The ground state manifold has $K$ fold degeneracy, labeled by the eigenvalue of the translation operator. The hamiltonain H commutes with the translation operator $[H,\hat{T}]=0$. We define the twist and tranlation operators in terms of an exponential of another operators as shown below.
%
%\begin{eqnarray}
%\hat{T}&=& e^{i\hat{P}} ~,~~\hat{O}=e^{i\hat{Q}}
%\end{eqnarray}
%We label the K degenerate eigenstates as $|p_i\rangle$ where $i\in [K]$ and the action of the translation operator on those states are given as 
%\begin{eqnarray}
%\hat{T} |p_m\rangle &=& e^{ip_m}~,~\textrm{where $\hat{P} |p_m\rangle=p_m |p_m\rangle$}
%\end{eqnarray}
%Now we discuss the property of the twist operator. The twist operator takes one state $|p_m\rangle$ to the nearest state $|p_{m+1}\rangle$.
%\begin{eqnarray}
%\hat{O} |p_m\rangle &=& |p_{m+1}\rangle~. ~~\textrm{or very generally} \\
%\hat{O}^{n} |p_m\rangle &=& |p_{(m+n) \textrm{mod} K}\rangle~.
%\end{eqnarray}
%Thus the above two equation seeks the wilson loop relation as
%\begin{eqnarray}
%\hat{T}\hat{O}^{n} |p_{m}\rangle &=&  \hat{T} |p_{(m+n) \textrm{mod} K} \rangle = e^{i\gamma_{m,n}} |p_{(m+n) \textrm{mod} K} \rangle \\
%\hat{O}^{n} \hat{T} |p_{m}\rangle &=& \hat{O}^{n} e^{ip_m} |p_{m}\rangle = e^{ip_m} |p_{(m+n) \textrm{mod} K} \rangle 
%\end{eqnarray}
%where $\gamma_{m,n}=p_{(m+n) \textrm{mod} K}+ (K-m)$. Thus we get the phase difference
%\begin{eqnarray}
%\langle p_{m} | \hat{T}^{\dagger} \hat{O}^{n \dagger} \hat{T}\hat{O}^{n} |p_{m}\rangle &=& e^{i[\gamma_{m,n}-p_{m}]} \equiv e^{i\frac{2n\pi}{K}}
%\end{eqnarray}
%
%
%Another way of finding out the structure of $\hat{O}$ is to use the BCH expansion. We know that for a two genral oeprators $X,Y$ we get 
%\begin{eqnarray}
%e^{X}Ye^{-X} &=& Y+[X,Y]+\frac{1}{2!}[X,[X,Y]]+\frac{1}{3!}[X,[X,[X,Y]]]+ \cdots.
%\end{eqnarray}
%Using the above formula we can calculate
%\begin{eqnarray}
%\hat{T}\hat{O}^{n}\hat{T}^{\dagger} &=& e^{i\hat{P}} \hat{O}^{n} e^{-i\hat{P}} = \hat{O}^{n} e^{in\theta} \nonumber\\
%&=& \hat{O}^n + [i\hat{P},\hat{O}^n] + \frac{1}{2!} [i\hat{P},[i\hat{P},\hat{O}^n]] + \frac{1}{3!} [i\hat{P}, [i\hat{P},[i\hat{P},\hat{O}^n]]] + \cdots  \nonumber\\
%&=& \hat{O}^{n} \bigg[ 1+ (in\theta) + \frac{(in\theta)^2}{2!} + \frac{(in\theta)^3}{3!} + \cdots \bigg]
%\end{eqnarray}
%Assummption from the above equation is 
%\begin{eqnarray}
%[i\hat{P},\hat{O}^n] &=& i(n\theta) \hat{O}^{n} ~,~\textrm{which leads to }
%\end{eqnarray}
%\begin{eqnarray}
%[i\hat{P},[i\hat{P},\hat{O}^n]] &=&  [i\hat{P},\hat{O}^{n}] i(n\theta)  =\hat{O}^n (in\theta)^2
%\end{eqnarray}
%and so on. Thus the assumption is correct. Thus we get the commutation relation
%\begin{eqnarray}
%[ \hat{P},\hat{O}^n] &=& ( n\theta) \hat{O}^n 
%\end{eqnarray}
%\begin{eqnarray}
%[\hat{P},e^{in\hat{Q}}] &=& (n\theta) e^{in\hat{Q}}~,~\textrm{$\forall n$.}
%\end{eqnarray}
%%This implies,
%%\begin{eqnarray}
%%[\hat{P},e^{in\hat{Q}}] &=& [\hat{P},1+(in\hat{Q})+\frac{(in\hat{Q})^2}{2!}+\frac{(in\hat{Q})^3}{3!} +\cdots]  \nonumber\\
%%&=& [\hat{P},1]+  [\hat{P},(in\hat{Q})]+  [\hat{P},\frac{(in\hat{Q})^2}{2!}]+  [\hat{P},\frac{(in\hat{Q})^3}{3!} +\cdots] \nonumber\\
%%&=& (n\theta) \bigg[ 1+ (in\hat{Q}) + \frac{(in\hat{Q})^2}{2!} +\frac{(in\hat{Q})^3}{3!} +\cdots \bigg]
%%\end{eqnarray}
%%Above equation leads to a trial solustion 
%%\begin{eqnarray}
%%[\hat{P},(in\hat{Q})^r]=(n\theta) (in\hat{Q})^r~,~r=0,1,2,\cdots
%%\end{eqnarray}
%
%
%\noindent We are intrested in the simple case where $[\hat{P},\hat{Q}]=\hat{\Gamma} \neq 0$ and $[\hat{\Gamma},\hat{P}]=0=[\hat{\Gamma},\hat{Q}]$. In this case we get 
%\begin{eqnarray}
%e^{i\hat{P}} e^{i\hat{Q}} e^{-i\hat{P}} &=& e^{i\hat{Q}} e^{-[\hat{P},\hat{Q}]}
%\end{eqnarray}

%
%\subsection{LSM style calculation}
%
%\noindent In standard LSM style study and in it's various generalizations we usually define two operators, translation $\hat{T}$ and twist operator $\hat{O}$. We take the system and add a periodic boundary condition along one direction, let's say $\hat{x}$. Then we insert the gauge flux through that closed loop formed by the periodic $x-$direction. Let's for example take a spin problem shere each point along the $x-$axis there is a spin-1/2 object sitting. The Hamiltonian of that spin problem is $H_{lsm}$. By construction, this Hamiltonian has the translation symmetry along the $x-$direction. Thus this hamiltonian commutes with the translation operator along the $x-$direction denoted as $\hat{T}_x$, and the commutation reads $[\hat{T}_x,\hat{H}_{lsm}]=0$. Now we define the twist operator $\hat{O}$ as 
%\begin{eqnarray}
%\hat{O} &=& e^{i\frac{2\pi}{N_x} \displaystyle\sum_{\vec{r}} x S_{\vec{r}}^z }~.~
%\end{eqnarray}
%This twist operator inserts one full $2\pi$ flux into the system. In genral this full twist operator does not commutes with the Hamiltonian, we first study the commutation ralation.
%\begin{eqnarray}
%[\hat{H}_{lsm},\hat{O}] &\neq & 0
%\end{eqnarray}
%This commutation relation totally depends on the microscopic structure of the Hamiltonian $H_{slm}$. We can though study the commutation relation between this twist operator and the translation operator. This does not needs the microscopic knowledge of the Hamiltonian. This is assuming the fact that the spins are equally spaced along the $x-$direction and $xS^z_{\vec{r}}\equiv x\sum_{y} S^z_{(x,y)}$, where $\vec{r}=(x,y)$. In the general cases where the arrangement of the spin along the $x-$direction is non-trivial function of the $x-$coordinate, we can write the twist operator as 
%\begin{eqnarray}
%\hat{O} &=& e^{i\frac{2\pi}{N_x} \displaystyle\sum_{\vec{r}, x=1}^{N_x} f_x S_{\vec{r}}^z }~.~
%\end{eqnarray}
%Whatever be the general structure there should be translation invariance in the problem. The the brading rules between the twist and the translation operators for the simle case of problems where the spacings are uniform/trivial are given as 
%\begin{eqnarray}
%\hat{T} \hat{O} \hat{T}^{\dagger} &=&  \hat{O}  \times e^{-\frac{2\pi}{N_x} S^z_{tot}} \times  e^{i 2\pi \sum_{y} S^z_{1,x}}
%\end{eqnarray}
%Sofar the calculations are in the operetor level, now we invoke the ground state property. We take the ground state value of the total magnetizaion $S^z_{tot}$. For the special case, where in the ground state $S^z_{tot}=0$, we get
%\begin{eqnarray}
%\hat{T} \hat{O} \hat{T}^{\dagger} &=&  \hat{O}    \times  e^{i 2\pi \sum_{y} S^z_{1,x}}
%\end{eqnarray}
%Now based on the value of $\sum_{y} S^z_{1,x}$ integer/half-integer we get trivial/non-trivial braiding rules between the twist and translation operators. We are interested in the non-trivial case here, which yields
%\begin{eqnarray}
%\hat{T} \hat{O} \hat{T}^{\dagger} &=&  \hat{O}    e^{\pm i\pi}
%\label{eq:TOTpOp_pi}
%\end{eqnarray}
%Now, let's assume that $|\psi_0\rangle$ is the ground state of the problem. Sofar, we have no idea about the nature of the gruond state and the excited states. As the translation operator is commuting, then the generator of this translation opertion $\hat{P}$ ($\hat{T}=e^{i\hat{P}}$) will also commute with the Hamiltonian.  Thus we can label the states with the eigenvalules of this operator $\hat{P}$.
%\begin{eqnarray}
%\hat{T} |p_1\rangle &=& e^{ip_1} |p_1\rangle~,~
%\end{eqnarray}
%Now from the eq.\eqref{eq:TOTpOp_pi} we can check the action of the operator $\hat{O}$ on the ground state $|p_1\rangle \equiv |\psi_0\rangle$. We find that
%\begin{equation}
%\langle p_1| \hat{O}|p_1\rangle =0
%\end{equation}
%Thus $|p_1^{(1)}\rangle \equiv \hat{O} |p_1\rangle$ is orthogonal to the ground state $|p_1\rangle$. Now we need to find out the energy difference between $|p_1\rangle$ and $|p_1^{(1)}\rangle$. To calculate that we need to find out the expectation value
%\begin{eqnarray}
%\Delta E &=&  \langle p_1^{(1)}| \hat{H}_{lsm}|p_1^{(1)}\rangle - \langle p_1| \hat{H}_{lsm}|p_1\rangle  \nonumber\\
%  &=&  \langle p_1 | \hat{O} \hat{H}_{lsm} \hat{O}^{\dagger} |p_1\rangle - \langle p_1| \hat{H}_{lsm}|p_1\rangle 
%\end{eqnarray}
%\noindent In the case where the twist operator commutes with the Hamiltonian $[\hat{H}_{lsm},\hat{O}]=0$, we will get $\Delta E=0$ in the operator level, independent of the system size. For the case $\Delta E=0$ we can say that ground state is doubly degenerate, labeled by the two eigen values of the momentum operator $0$ and $\pi$.
%
%\par But in the LSM case this twist operator does not commute with the Hamiltonian, thus in general $\Delta E\neq 0$. For this case we can see that the twisted state is an excited state. In special problem it can be shown that in the termodynamic limit this gap $\Delta E$ vanishes, showing either the double degenerate ground state (if one can show a gap above) or gapless spectrum.
%
%\subsubsection{Special case in fractional QHE}
%\noindent In the quantum hall problem, we can write down the Hamiltonian as 
%\begin{eqnarray}
%H_{qh} &=& \frac{1}{2m} \bigg[ \Pi_x^2 + \Pi_y^2\bigg]~,~  \textrm{where}~~ \vec{\Pi}=-i\hbar \vec{\nabla} + e\vec{A}
%\end{eqnarray}
%We know $[\Pi_x,\Pi_y]\neq 0$ thus the Hamiltonian also does not commutes with these operators individually. But one can define a pseudo-momentum $\tilde{\Pi}_{x/y}$ which commutes with the Hamiltonian in a particular gauge choice. For an example in Tao \& Haldane 1985, landau gauge was chosen $\vec{A}=(0,Bx,0)$. In this Landau gauge thepseudo momentum defined was ${\tilde{\Pi}}_x=p_x+eBy$ and ${\tilde{\Pi}}_y=p_y$. This pseudo-momentum operators commutes with the Hamiltonian and does not commutes with each other thus, following the algebra of $\hat{P}$ and $\hat{Q}$ as described in the above section. One can easily check that $[\tilde{\Pi}_x,\tilde{\Pi}_y]=i\hbar eB$.\\
%
%
%\par \textit{Question:} Now the question is, for a general Hamiltonian $H_{gen}$, if the ground state is multiply degeenrate (morethan one mutually orthogonal states with same minimum energy available). Can we always find out two operators $\hat{P},\hat{Q}$ such that $[\hat{H},\hat{P}]=[\hat{H},\hat{Q}]=0$ and $[\hat{P},\hat{Q}]\neq i\hbar c$, where $c$ is a constant.

\subsection{In our case of stargraph model}
\noindent In our model we find two string operators $\hat{\mathbb{Z}}=\sigma_d^z\Pi_{i=1}^{K} \sigma_i^z$ and $\hat{\mathbb{X}}=\sigma_d^x\Pi_{i=1}^{K} \sigma_i^x$, where $K$ is the number of channels. These two operators commutes with the Hamiltonian $H$ of this stargraph.
\begin{eqnarray}
[H,\hat{\mathbb{Z}}] &=& 0 = [H,\hat{\mathbb{X}}]
\end{eqnarray}

We can rewrite the operators in the form of a twist operator as,
\begin{eqnarray}
\mathbb{Z} &=& \sigma_d^z\displaystyle\prod_{i=1}^{K} \sigma_i^z = \frac{1}{i^{K+1}} e^{i\frac{\pi}{2} \sum_{i} \sigma^z_i}=e^{i\frac{\pi}{2} \sum_{i} (\sigma^z_i -1) } =e^{i\pi \sum_{i} (S^z_i -1/2) }
\end{eqnarray}
Similarly one can rewrite
\begin{eqnarray}
\mathbb{X} &=& \sigma_d^x\displaystyle\prod_{i=1}^{K} \sigma_i^x =e^{i\pi \sum_{i} (S^x_i -1/2) }
\end{eqnarray}
The commutation between these two operators are given as
\begin{eqnarray}
[\mathbb{Z},\mathbb{X}] &=& \prod_{i=d,1}^{K} \sigma^z_{i} \prod_{i=d,1}^{K} \sigma^x_{i} \bigg[1-(-1)^{K+1}\bigg]
\end{eqnarray}
Thus we can see that for case where number of channels is odd that means $K+1$ is even, these two string operators commutes with each other forming a CSCO ($H,\hat{\mathbb{Z}},\hat{\mathbb{X}}$). On the other hand in the case where number of channels $K$ is even, these two operators does not commute with each other. Let's discuss these two cases seperately.
%\subsubsection{$K=odd$} 
In the case where the number of channels $K$ is odd, we get $[\mathbb{Z},\mathbb{X}]=0$. Thus forming a CSCO with elements $H,\hat{\mathbb{Z}},\hat{\mathbb{X}}$. Thus one can label the states using the eigenvalues of these operators. For the case of $K=2n+1$ channels, the grounf state is $K$ fold degenerate and labeled by the eigenvalues of the operator $J^z$ which can take values $J^z=[-J,-J+1,\cdots, J-1, J]$, where $J=(K-1)/2$. For the odd channel case $J^z$ can take zero value. Thus 
\begin{eqnarray}
|J^z\rangle \equiv |Z,X \rangle
\end{eqnarray}
where the eigenvalue $Z$ can take $(K+1)/2$ values related to the absolute $|J^z|$ but cannot distinguish between $\pm J^z$ and $X$ can take two values $\pm 1$ which breaks the degenercy between $\pm J^z$. Thus these two operators together can uniquely label all the degenerate states.
% Note, the states $|Z=\rangle$

\subsection{Main}

\par We can define two operators, for convenience let's call translation and twist operator respectively, $\hat{T}$ and $\hat{O}$ defined as 
\begin{eqnarray}
\hat{T} &=& e^{i\frac{2\pi}{K} \hat{\Sigma}} ~,~\hat{O} = e^{i\hat{\phi}}~,~~\hat{\Sigma}=[\hat{J}^z-(K-1)/2]
\end{eqnarray}
One can see that the generators of these above operators commutes with the Hamiltoninan, $[H,J^x]=[H,J^z]=[H,J^z]=0$. In the large channel limit we can do semiclaassical approximation. As $J^x$ and $J^y$ both commutes with the Hamiltonian $H$ then $[H,J^y{(J^{x})}^{-1}]=0$, and any non-singular function of these operators must also commute with the Hamiltonian, thus we can say that
\begin{eqnarray}
\hat{\phi}=\tan^{-1}(\hat{J}^y(\hat{J}^x)^{-1})
\end{eqnarray}
Then we get $[\hat{\phi},\hat{H}]=0$. We can label the ground states by the eigen values of the translation operator $\hat{T}$. We can also use the ground states labeled by the eigenvalues of $J^z$ ($M$, say). Then the ground states are 
\begin{eqnarray}
|M_1\rangle,|M_2\rangle,|M_2\rangle,\cdots ,|M_K\rangle
\end{eqnarray}
Then the operations of the translation operators on this states are give below.
\begin{eqnarray}
\hat{T}|M_i\rangle &=& e^{i\frac{2\pi}{K} [M_i-(K-1)/2]} |M_i\rangle = e^{i2\pi\frac{p_i}{K} } |M_i\rangle~,~p_i\in[1,\cdots,K]
\end{eqnarray}
Now we check the braiding rule between the twist and the translation operators, we find
\begin{eqnarray}
\hat{T}\hat{O}\hat{T}^{\dagger}\hat{O}^{\dagger} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},i\hat{\phi}]}=e^{i\frac{2\pi }{K}} \nonumber\\
\hat{T}\hat{O}^m\hat{T}^{\dagger}\hat{O}^{\dagger m} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},im\hat{\phi}]}=e^{i2\pi \frac{m}{K}}
\end{eqnarray}

Next we shown that the states $\hat{O}^m |M_i\rangle$ are orthogonal to each other and with the state $|M_i\rangle$.

\begin{eqnarray}
\hat{T} \hat{O}^m |M_i\rangle &=& \hat{O}^m \hat{T} e^{i2\pi \frac{m}{K}} |M_i\rangle =\hat{O}^m e^{i \frac{2\pi(m+p_i)}{K} } |M_i\rangle \nonumber\\
\hat{T} \bigg(\hat{O}^m |M_i\rangle \bigg) &=&  e^{i \frac{2\pi(m+p_i)}{K} } \bigg( \hat{O}^m |M_i\rangle \bigg)
\end{eqnarray}
Thus different states $ \hat{O}^m |M_i\rangle$ for different $m$ are labeled by different eigenvalues of the translation operations, thus are orthogonal to each other. Now as the twist operator $\hat{O}$ commutes with the Hamiltonian, thus we can see that 
\begin{eqnarray}
\langle M_i| \hat{O}^{m \dagger}  H \hat{O}^m |M_i\rangle =\langle M_i|  H |M_i\rangle 
\end{eqnarray}
Thus the energy eigen values of all the orthogonal states are equal. Thus all the K mutually orthogonal states are degenerate.

\subsection{Fractional statistics}

\section{Local Mottliquid}

\noindent Using the unitary renormalization group method we decouple the impurity spin from the zero-modes of the $K$ channels. We start with the Hamiltonian. The zero mode Hamiltonian is a stargraph model 
\begin{eqnarray}
H &=& \alpha \vec{S}_d.\displaystyle\sum_i \vec{S}_i =\alpha S_d^zS^z + \frac{\alpha}{2} (S_d^+S^-+ S_d^-S^+) \nonumber\\
H_D &=& \alpha S^z_d S^z~,~~ H_X = \frac{\alpha}{2} (S_d^+S^-+ S_d^-S^+)
\end{eqnarray}
Here we want to remove the quantum fluctuations between the impurity spin and the rest, for that we do one step URG.

\begin{eqnarray}
\Delta H &=& H_X \frac{1}{\hat{\omega}-H_D} H_X \nonumber\\ 
%&=&\frac{\alpha^2}{4} \bigg[ S^- S_d^+ \frac{1}{\omega_{\uparrow}-\alpha S_d^zS^z} S^-_d  S^+  \bigg] +\frac{\alpha^2}{4} \bigg[ S^+ S_d^- \frac{1}{\omega_{\uparrow}-\alpha S_d^zS^z} S^+_d  S^-  \bigg] \nonumber\\
%&=&\frac{\alpha^2}{4} \bigg[ S^-S^+ S_d^+S^-_d \frac{1}{\omega_{\uparrow}-\alpha (S_d^z-1)(S^z+1)}     \bigg] +\frac{\alpha^2}{4} \bigg[ S^+S^- S_d^-S^+_d \frac{1}{\omega_{\downarrow}-\alpha (S_d^z+1)(S^z-1)}     \bigg] \nonumber\\
%&=&\frac{\alpha^2}{4} \bigg[ S^-S^+(1/2+S^z_d) \frac{1}{\omega_{\uparrow}-\alpha (S_d^z-1)(S^z+1)}     \bigg] +\frac{\alpha^2}{4} \bigg[ S^+S^-(1/2-S_d^z) \frac{1}{\omega_{\downarrow}-\alpha (S_d^z+1)(S^z-1)}     \bigg] \nonumber\\
\end{eqnarray}
In the zero mode IR fixed point ground state (stargraph) of multi-cahnnel ground state $J^z$ is a good quantum number but $S^z$ is not. There is no net $S^z$ field thus in the ground state manifold the average $S^z$ is vanishing, $\langle S^z \rangle=0$. We use this expectation value to replace the denominator of the above RG equation.

%\begin{eqnarray}
%\Delta H &=& \frac{\alpha^2}{4} \bigg[ S^-S^+ (1/2+S^z_d) \frac{1}{\omega_{\uparrow}-\alpha (S_d^z-1)(\langle S^z \rangle +1)}     \bigg] +\frac{\alpha^2}{4} \bigg[ S^+S^- (1/2-S_d^z) \frac{1}{\omega_{\downarrow}-\alpha (S_d^z+1)(\langle S^z \rangle-1)}     \bigg] \nonumber\\
%%&=& \frac{\alpha^2}{4} \bigg[ S^-S^+ (1/2+S^z_d) \frac{1}{\omega_{\uparrow}-\alpha (S_d^z-1 )}     \bigg] +\frac{\alpha^2}{4} \bigg[ S^+S^- (1/2-S_d^z) \frac{1}{\omega_{\downarrow}+\alpha (S_d^z+1) }     \bigg] \nonumber\\
%%&=& \frac{\alpha^2}{4} \bigg[ S^-S^+ (1/2+S^z_d) \Gamma_{\uparrow}\bigg] +\frac{\alpha^2}{4} \bigg[ S^+S^- (1/2-S_d^z) \Gamma_{\downarrow} \bigg] \nonumber\\
%&=& \frac{\alpha^2}{4} \bigg[ (S^2-S^{z2}- S^z)(1/2+S^z_d) \Gamma_{\uparrow} \bigg]+\frac{\alpha^2}{4} \bigg[ (S^2-S^{z2}+ S^z)(1/2-S^z_d) \Gamma_{\downarrow} \bigg] \nonumber\\
%\end{eqnarray}
%Due to unitary condition the $\omega_{\uparrow}$ and $\omega_{\downarrow}$ are constrained, which makes $\Gamma_{\uparrow}=\Gamma_{\downarrow}$. Thus we get
%\begin{eqnarray}
%\Delta H &=& \frac{\alpha^2}{4} \bigg[ (S^2-S^{z2}- S^z)(1/2+S^z_d)_{\uparrow} \Gamma_{\uparrow} \bigg]+\frac{\alpha^2}{4} \bigg[ (S^2-S^{z2}+ S^z)(1/2-S^z_d)_{\downarrow} \Gamma_{\downarrow} \bigg] \nonumber\\
%&=& \frac{\alpha^2}{4} \Gamma_{\uparrow} \bigg[ (S^2-S^{z2}- S^z)(1/2+S^z_d)_{\uparrow} + (S^2-S^{z2}+ S^z)(1/2-S^z_d)_{\downarrow}  \bigg] \nonumber\\
%&=& \frac{\alpha^2}{4} \Gamma_{\uparrow} \bigg[ (S^2-S^{z2}- S^z)(S^2_{d}-S^{z2}_d)  + (S^2-S^{z2}+ S^z)(S^2_{d}-S^{z2}_d)  \bigg]\nonumber\\
%&=& \frac{\alpha^2}{2} \Gamma_{\uparrow} \bigg[ (S^2-S^{z2})(S^2_{d}-S^{z2}_d)  \bigg]~,~~ \textrm{where $S_d^+S_{d}^-=(S_d^2-S_{d}^{z2}+S_d^z)=1/2+S_d^z$}
%\end{eqnarray}

\begin{eqnarray}
\beta_{\uparrow} (\alpha,\omega_{\uparrow})&=& \frac{\alpha^2 \Gamma_{\uparrow}}{2} \nonumber\\
\Gamma_{\uparrow}&=& \frac{1}{\omega_{\uparrow}-\alpha(S_d^z-1)}
\end{eqnarray}

Thus we get the effective Hamiltonian is

\begin{eqnarray}
H_{eff} &=& \frac{\alpha^2 \Gamma_{\uparrow}}{2} (S^2-S^{z2})(\tau^2_{d}-\tau^z_d)  \nonumber\\
&=& \beta_{\uparrow}(\alpha,\omega_{\uparrow})(S^2-S^{z2})(\tau^2_{d}-\tau^z_d)\\
%~,~~~\frac{\alpha^2 \Gamma_{\uparrow}}{2} =\beta_{\uparrow}(\alpha,\omega_{\uparrow}) \nonumber\\
&=& \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} (S^2-S^{z2})  \nonumber\\
&& =\frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)   
\end{eqnarray}
. In terms of the electronics degree of freedom this looks 
\begin{eqnarray}
&&H_{eff}(\omega,\alpha)  \nonumber\\
&=& \frac{ \beta_{\uparrow}(\alpha,\omega_{\uparrow}) }{4}    \displaystyle\sum_{i\neq j}\displaystyle\sum_{\substack{ \alpha_i,\beta_i\in \{\uparrow,\downarrow\}\\ \alpha_j,\beta_j\in \{\uparrow,\downarrow\}}}\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)}    c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)}\nonumber\\
&&~~~~ ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ +\textrm{h.c.}   
\label{eq:all-to-all_1}
\end{eqnarray}
We will study the two cases of the above effective Hamiltonian depending on the sign of the prefactor. The case $\frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} >0$ is the ferromagnetic case where in the ground state $S$ takes the minimum value and $S^z$ takes the possible maximum value. For an example, in the case of $K$ channels the minimum value of $S$ will be $0$ or $1/2$ for $K$ being $even $ or $odd$ respectively.  We will be interested in the other case where $\frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} <0$. In this case the ground state corresponds to $S$ being maximum and $S^z$ being minimum case. The effective Hamiltonian can be re-written in this case as

\begin{eqnarray}
H_{eff}   =-\frac{|\beta_{\uparrow}(\alpha,\omega_{\uparrow})|}{4} (S^+S^{-}+ S^-S^{+})    
\end{eqnarray}

\noindent The CSCO of this Hamiltonian contains $H,S,S^z$. In the ground state $S$ is maximum thus $S=K/2$ and $S^z$ can take $2S+1=K+1$ values. Thus in the largest $S$ sector there are $K+1$ states. One can explore different states via a flux tuning mechanism. In the presence of the flux the Hamiltonian looks like
\begin{eqnarray}
H &=& -\frac{|\beta_{\uparrow}(\alpha,\omega_{\uparrow})|}{2} S^2   +\frac{|\beta_{\uparrow}(\alpha,\omega_{\uparrow})|}{2} \bigg(S^{z}-\frac{\Phi}{\Phi_0} \bigg)^2 
\label{eq:flux_spectral}
\end{eqnarray}

\subsection{Mapping with the degenerate ground state of stargraph}

\noindent Now we are going to discuss about the mapping of $K$ degenerate ground states of the parent $K-$channel stargraph model with the states of this flux-insterted all-to-all model obtained by removing inpurity-bath quantum fluctuations. In the stargraph model the K ground states is labeled by the $J^z$ eigenvalues. In the stargraph ground state $J=S-1/2$, where $S$ is maximum with value $S=K/2$. Thus there are $2J+1=K$ unique $J_z$ eigenvalues corresponding to the $J$ sector labeling different eigenstates. The gound state Hilbert space $\mathcal{H}_{gr}$ contains the $J^z$ states
\begin{eqnarray}
\mathcal{H}_{gr}=\{\textcolor{blue}{-(K-1)/2,-(K-3)/2,\cdots , (K-3)/2,(K-1)/2}\} \nonumber\\
\label{eq:stargraph_states}
\end{eqnarray}

\par Now we shift our focus to the low energy Hamiltonian with flux shown in the eq.\eqref{eq:flux_spectral}. We can see that there is a unique ground state labeled by the $S^z$ eigenvalues. By tuning the flux ($\Phi/\Phi_0$) one can go from one ground state to another ground state or change the ground state. We can see that ground state energy is independent of the configuration of the impurity spin ($S_d^z=\pm 1/2$). Thus for each of those two possibilities we get two set of ground states labeled by the $S^z$ and the $J^z=S^z+S^z_d$. Similar to the stargraph case here also the ground state corresponds to the largest $S$ sector, $S=K/2$. Thus total number of $S^z$ eigenvalues are $2S+1=K+1$ taking values $\{ -K/2, -(K-2)/2, \cdots, (K-2)/2, K/2 \}$.

\begin{widetext}
\begin{eqnarray}
S_d^z &=& +1/2~,~ \{J^z\}=\{ \textcolor{blue}{-(K-1)/2, -(K-3)/2, \cdots, (K-1)/2}, (K+1)/2\} \nonumber\\
S_d^z &=& -1/2~,~ \{J^z\}=\{-(K+1)/2,\textcolor{blue}{ -(K-1)/2, \cdots, (K-3)/2, (K-1)/2 } \}
\label{eq:all_to_all_states}
\end{eqnarray}
\end{widetext}

\begin{figure}[!hb]
\centering
\includegraphics[scale=0.68]{plt/stargraph-to-alltoall}
\caption{This figure shows the comparison and mapping between the stargraph degenerate ground states and the states of the quantum fluctuation resolved all to all model.}
\label{fig:stargraph-to-alltoall}
\end{figure}
Thus one can see that the ground state degeneracy of the stargraph model with different $J^z$ values gets lifted in the quantum fluctuation resolved all-to-all model. Depending on the value of the flux there is an unique ground state labeled by the $J^z$ value. Tuning the fluc one can go from one ground state to the other. This shows how one can explore different degenerate ground states of the parent stargraph model via the insertion of flux in the corresponding quantum fluctuation resolved all-to-all effective Hamiltonian.

\subsection{Local mott-liquid}
Impurity-bath quantum fluctuation resolved all-to-all effective Hamiltonian is written in terms of the spinor spin operators which are individually made out of two electronic degree of freedom. This is defined as $\vec{S}_i=\frac{\hbar}{2} \displaystyle\sum_{\substack{ \alpha,\beta\in \{\uparrow,\downarrow\}}}  c_{0\alpha}^{(i)\dagger} \vec{\sigma}_{\alpha\beta} c_{0\beta}^{(i)}$. In the above eq.\eqref{eq:all-to-all_1} we see the $U(1)$ symmetry of the effective Hamiltonian. Using the spinor repersentation one can see the spin creation operation in terms of the electronic degree of freedom is 
\begin{eqnarray}
S_i^+ &=& \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{+}_{\alpha\beta} c_{0\beta}^{(i)}
% = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger}   c_{0\beta}^{(i)} \delta_{\uparrow,\alpha} \delta_{\downarrow,\beta} 
=\frac{\hbar}{2} c_{0\uparrow}^{(i)\dagger} c_{0\downarrow}^{(i)}  \\
S_i^z &=& \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{z}_{\alpha\beta} c_{0\beta}^{(i)} =\frac{\hbar}{2} (c_{0\uparrow}^{(i)\dagger} c_{0\uparrow}^{(i)} - c_{0\downarrow}^{(i)\dagger} c_{0\downarrow}^{(i)} )~,~~~~
\end{eqnarray}
Thus this spinor spins are nothing but the Anderson pseudospin formulation in the spin channel. The spin creation opertor ($S_i^+$) shows simultaneous creation of an electron-hole pair at the realspace origin of the $i^{th}$ channel. The condensation of such electron-hole pais has already been shown in [CITE: mott]. Thus for this effective Hamiltonian one can define twist-translation oeprations to construct the gauge theory and unveiling any hidden degeneracy. Let's recall the effective Hamiltonian
\begin{eqnarray}
H_{eff} &=& \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{4} \bigg[ \displaystyle\sum_{ij} S_i^+S_j^- ~+ \textrm{h.c.} \bigg]~,
\end{eqnarray}
where $i,j$ are the channel indices. Due to the all-to-all nature of the connectivity one can draw total $K!$ possible unique closed paths ($\mathcal{C}_{\mu}$) where each nodes (channels) is being touched only once. One can thus define total $K!$ number of translation operators ($\hat{T}_{\mu}$) which keeps the Hamiltonian invariant. Let's define one of such translation operator $\hat{T}_{\mu}$ thich gives a periodic shifts along the closed path $\mathcal{C}_{\mu}$. Let's define twist operator along the path $\mathcal{C}_{\mu}$
\begin{eqnarray}
\hat{\mathcal{O}}_{\mu} &=& \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{C}_{\mu}}}^{K} j S_j^z} )~,~~\hat{T}_{\mu}=e^{i\hat{P}^{cm}_{{\mu}}}
\end{eqnarray}
The  operation of the translation operator $\hat{T}_{\mu}$ is defined as $\hat{T}_{\mu} S_j^z = S_{j+1}^z$ where $j+1$ and $j$ are the nearest neighbor on the closed path $\mathcal{C}_{\mu}$. Then the braiding rule between the twist and translation operators are give as
\begin{eqnarray}
\hat{T}_{\mu}\hat{\mathcal{O}}_{\mu} \hat{T}^{\dagger}_{\mu} \hat{\mathcal{O}}_{\mu}^{\dagger}  &=&  \exp\{i[2\pi S_1^z-\frac{2\pi}{K}S^z]\} \nonumber\\
&=& \exp\{i[\pm \pi - \frac{2\pi}{K} S^z]\} =\exp(i\frac{2\pi p}{q})
\end{eqnarray}
The availability of the non-trivial braiding staatistics between these twist and translation operators is possible if $p\neq 0$ and $q\neq \infty$. Further simplification leads to the condition
\begin{eqnarray}
 \pm\pi -\frac{2\pi}{K} S^z = \frac{2\pi p}{q} ~~ &\Rightarrow & \pm\frac{1}{2}-\frac{S^z}{K} = \frac{p}{q} \nonumber\\
&& \frac{(\pm K-2S^z)}{2K} = \frac{p}{q}~,~
\end{eqnarray} 
$p,q$ are mutual prime, We knwo that the $S^z$ can take values $(\mp K/2\pm m)$ where $m$ is a integer $0 \leq m \leq K$. Putting this value in the above equation leads to two possible solutions.
\begin{eqnarray}
\frac{(K-m)}{K} &=& \frac{p}{q} ~,~~ \frac{-m}{K}=\frac{p}{q}
\end{eqnarray}
For the first case $K-m=p$ we can see that $m=K$ makes $p$ trivial hus the allowed values are $m=0,\cdots,K-1$, which represents the corresponding $S^z$ eigen values 
\begin{eqnarray}
&&-K/2,-K/2+1,\cdots,K/2-2,K/2-1
\end{eqnarray}
Similarly the second case implies, $-m=p$, but $p=0$ is not allowed as this makes the braiding statistics trivial, thus the possible $S^z$ values are 
\begin{eqnarray}
&&\hspace{2.2cm} -K/2+1,-K/2+2,\cdots,K/2-1,K/2
\end{eqnarray}

\noindent Thus we get the general braiding statistics between the twist and the translation 
\begin{eqnarray}
\hat{T}_{\mu}\hat{\mathcal{O}_{\mu}} \hat{T}^{\dagger}_{\mu}\hat{\mathcal{O}_{\mu}}^{\dagger} &=& e^{i\frac{2\pi p}{K}}
\end{eqnarray}
where $p$ corresponds to different $S^z$ states, related as $p=\pm K/2-S^z$. Thus we can see that there are $K$ possible $S^z$ plaleau states in the all-to-all model where each plateaux is $K$ fold degenerate. This $p/K$ is similar to the filling factor of the fractional quantum Hall effect. There are possibly $K!$ pairs of twist and translation operator corresponding to different closed paths $\mathcal{C}_{\mu}$ which can probe this degeneracy.

\subsubsection{Action on the Hamiltonian}
Now we findout the action of these twist operators on the Hamiltonian. The Hamiltonian is written as 
\begin{eqnarray}
H_{eff}&=& \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} (S^{x2} +S^{y2})   
\end{eqnarray}
Due the all-to-all nature of the effetive Hamiltonian one can find $K!$ possible relative arrangement of those $K$ channels which keeps the Hamiltonian invariant. Here we briefly discuss the choice of the closed loop $\mathcal{C}_{\mu}$ and the insertion of the flux. As shown in the Fig.\ref{fig:stargraph-to-alltoall}(b) we have chosen a particular closed path which crosses all the outer spin only once. We embed that closed loop on a plane and put the flux perpendiculr to the plane through the closed loop. One can find a different closed loop where the ordering of the outer spins will be different. The action of the translation operator shifts the outer spins along this closed curve by one step.

The action of the twist operator on the $S^x$ is determined in the follwoing calculation
\begin{eqnarray}
\hat{O}_{\mu} S^x \hat{O}^{\dagger}_{\mu} &=& \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} ) ~~S^x ~~ \exp({-i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} )= e^{X} S^x e^{-X} \nonumber\\
&=& S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots  
\end{eqnarray}
For simplicity of thte calculation we define $i\frac{2\pi}{K}=\Omega$, thus $X=\Omega\sum_j jS^z_j$.
%\begin{eqnarray}
%&& [X,S^x] = [\Omega\sum_j jS^z_j,\sum_{l} S^x_l] =\Omega \sum_j j[S^z_j,S^x_j] = (i\Omega) \sum_j j S^y_j \nonumber\\
%&& [X,S^y] = [\Omega\sum_j jS^z_j,\sum_{l} S^y_l] =\Omega \sum_j j[S^z_j,S^y_j] = -(i\Omega) \sum_j j S^x_j  \nonumber\\
%&& [X,[X,S^x]] = [X,i\Omega \sum_j j S^y_j] = [\Omega\sum_{l}l S_l^z,i\Omega \sum_j j S^y_j] =i\Omega^2\sum_{l} l^2[ S_l^z, S^y_j] =-(i^2\Omega^2)\sum_{l} l^2 S_l^x ~,~~~~ \nonumber\\
%&& [X,[X,S^y]] = [X,-i\Omega \sum_j j S^x_j] = [\Omega\sum_{l}l S_l^z,-i\Omega \sum_j j S^x_j] =-i\Omega^2\sum_{l} l^2[ S_l^z, S^x_j] =-(i^2\Omega^2)\sum_{l} l^2 S_l^y ~,~~~~~~~~ \nonumber\\
%&& [X, [X,[X,S^x]]] = [\Omega\sum_j jS^z_j,-i^2\Omega^2 \sum_l l^2 S_l^x ]=-i^2\Omega^3 \sum_l l^3[S^z_l,S^x_l] =-(i^3\Omega^3) \sum_l l^3 S^y_l  \nonumber\\
%&& [X, [X,[X,S^y]]] = [\Omega\sum_j jS^z_j,-i^2\Omega^2 \sum_l l^2 S_l^y ]=-i^2\Omega^3 \sum_l l^3[S^z_l,S^y_l] =(i^3\Omega^3) \sum_l l^3 S^x_l 
%\end{eqnarray}
Thus we get
\begin{eqnarray}
e^X S^x e^{-X}&=& S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots  \nonumber\\
%&=& \sum_l S_l^x + (i\Omega)\sum_l l S^y_l + \frac{-(i\Omega)^2}{2!}\sum_{l} l^2 S_l^x + \frac{-(i\Omega)^3}{3!} \sum_l l^3 S_l^y+ \cdots \nonumber\\
%&=& \sum_l S_l^x \bigg[1-\frac{(il\Omega)^2}{2!}  +\cdots \bigg] + \sum_{l} S_l^y \bigg[ (il\Omega)- \frac{(il\Omega)^3}{3!} +\cdots \bigg] \nonumber\\
%&=& \sum_l \bigg[ S^x_l \cos (il\Omega) +  S_l^y \sin(il\Omega) \bigg] =  \sum_l \bigg[ S^x_l \cos (-\frac{2\pi l}{K}) +  S_l^y \sin(-\frac{2\pi l}{K}) \bigg]  \nonumber\\
&=& \sum_l ( S^x_l \cos \theta_l -  S_l^y \sin \theta_l ) ~,~~~\theta_l=\frac{2\pi l}{K}
\end{eqnarray}

\begin{eqnarray}
e^X S^y e^{-X}&=& S^y+[X,S^y] + \frac{1}{2!}[X,[X,S^y]] +\cdots  \nonumber\\
%&=& \sum_l S_l^y - (i\Omega)\sum_l l S^x_l + \frac{-(i\Omega)^2}{2!}\sum_{l} l^2 S_l^y + \frac{(i\Omega)^3}{3!} \sum_l l^3 S_l^x+ \cdots \nonumber\\
%&=& \sum_l S^y_l \bigg[ 1 -\frac{(il\Omega)^2}{2!} + \cdots \bigg]- \sum_l S^x_l \bigg[ (il\Omega) - \frac{(il\Omega)^3}{3!} +\cdots \bigg] \nonumber\\
&=& \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)
\end{eqnarray}
As already defined, $\theta_l=\frac{2\pi l}{K}=\frac{2\pi (K-n)}{K}$, where $n$ is an integer. We can see that in the large channel limit $\theta_l $ becomes inter multiple of $2\pi$. Thus in the large channel limit

%\begin{eqnarray}
%\hat{\mathcal{O}}_{\mu} S^{\nu} \hat{\mathcal{O}}^{\dagger}_{\mu} &\xRightarrow[]{K \rightarrow \infty } S^{\nu}~,~~\nu=x,y 
%\end{eqnarray}

%%%%\textbf{\textit{Fix this LaTeX issue (equation)}} ################

Thus in the large channel limit
\begin{eqnarray}
&& \lim_{K\rightarrow \infty}\hat{\mathcal{O}}_{\mu} H_{eff} \hat{\mathcal{O}}_{\mu}^{\dagger}\nonumber\\
 &=& \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[ \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger}  + \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger}  \bigg]\nonumber\\
&=&\frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[  S^{x2}+S^{y2}  \bigg] = H_{eff} \nonumber\\
&&\lim_{K\rightarrow \infty } [\hat{\mathcal{O}},H_{eff}] = 0
\label{eq:hamiltonian_twisted}
\end{eqnarray}

\noindent The translation operator $\hat{T}_{\mu}=e^{i\hat{\mathcal{P}}_{\mu}}$ commutes with the Hamiltonian thus the generator $\hat{\mathcal{P}}_{\mu}$ also commutes with the Hamiltonian. We can label the $j^{th}$ state with the eigenvalues of this operator $\hat{\mathcal{P}_{\mu}}$ as $|p^{j}_{\mu}\rangle$. We here discuss the action of these twist and translation operators on these states.
\begin{eqnarray}
\hat{T}_{\mu} |p^j_{\mu} \rangle &=& e^{i\hat{\mathcal{P}}_{\mu}} |p^j_{\mu} \rangle = e^{ip^j_{\mu}} |p^j_{\mu}\rangle \nonumber\\
\hat{T}_{\mu} \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle &=&  \hat{\mathcal{O}}_{\mu} \hat{T}_{\mu} e^{i\frac{2\pi m}{K}} |p^j_{\mu}\rangle~~, \nonumber\\
&&~~\textrm{here $m$ signifies different $S^z$ plateaux.} \nonumber\\ \nonumber\\
&=& \hat{\mathcal{O}}_{\mu}   e^{i(\frac{2\pi m}{K}+p_{\mu}^j)} |p^j_{\mu}\rangle~,~~ \frac{2\pi m}{K} \equiv p_{\mu}^{m} \nonumber\\
\hat{T}_{\mu} \bigg( \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle  \bigg) &=& e^{i(p_{\mu}^{m}+p_{\mu}^j)} \bigg( \hat{\mathcal{O}}_{\mu}    |p^j_{\mu}\rangle \bigg)    
\end{eqnarray}
Thus we can see that  $\hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle $ is a state of the traslation operator with different eiven value than $|p^j_{\mu} \rangle $, thus orthogonal to each other. Simiarly one can generally show that $\langle p^j_{\mu} | \hat{\mathcal{O}}^{q}_{\mu} |p^j_{\mu} \rangle=0$, where $q$ is any integer. Also in the large $K$ limit we can see from the eq.\eqref{eq:hamiltonian_twisted} that these differnt twisted states has same energy. Which shows that at each plateau state labeled by the $S^z$ eigenvalue has $K$ fold degenerate eigenstates labeled by the eigenvalue of the translation operators. Thus the CSCO is formed by $H,S^z,\hat{T}$. Thus states can be lebeled as  $|E,S^z_j,P^j_{\mu}\rangle$.

\appendix

\begin{widetext}
\section{Three channel case: NFL}
\label{ap:three-channel}
\noindent Thus the off-diagonal part of the effective low energy Hamiltonian in the 2nd order is
\begin{eqnarray}
&&H_{eff, off}^{(2)} 
= \frac{J^2}{\alpha}\bigg[ c_{1\uparrow}c_{1\downarrow}^{\dagger} \bigg(-\alpha\beta \bigg\{\Sigma_{3,2} + c_{3\uparrow}^{\dagger} c_{3\downarrow} c_{2\uparrow} c_{2\downarrow}^{\dagger} \bigg\}-\alpha\gamma \Omega_{3,2}\bigg) +c_{2\uparrow}c_{2\downarrow}^{\dagger} \bigg(-\alpha\beta \bigg\{\Sigma_{1,3} + c_{1\uparrow}^{\dagger} c_{1\downarrow} c_{3\uparrow} c_{3\downarrow}^{\dagger} \bigg\}-\alpha\gamma \Omega_{1,3}\bigg) \nonumber\\
&&~~~~~+c_{3\uparrow}c_{3\downarrow}^{\dagger} \bigg(-\alpha\beta \bigg\{\Sigma_{2,1} + c_{2\uparrow}^{\dagger} c_{2\downarrow} c_{1\uparrow} c_{1\downarrow}^{\dagger} \bigg\}-\alpha\gamma \Omega_{2,1}\bigg) + \textrm{h.c.} \bigg]
 \otimes \bigg[ c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.}\bigg] \nonumber
\end{eqnarray} 
 \begin{eqnarray}
\Sigma_{i,j} &=&-8S_i^zS_j^z  [  (C^z_i-C^z_j  )^2  + (S_i^z-S_j^z  )^2  ] \\
\Omega_{i,j} &=& 4S_i^z S_j^z (C_i^z+C_i^z)(C_j^z+C_j^z)
\end{eqnarray}
\end{widetext}

\end{document}

### 2022-01-12 combined_manuscript/other/send_abhirup/MultiChannelKondo_manuscript.tex
combined manuscripts, separated into main and supplementary, changed Kondo coupling to curly J

--- 2022-01-12 combined_manuscript/backups/MultiChannelKondo_manuscript_29_Dec_448.tex
@@
 &=& \frac{\alpha}{2} (\vec{J}^2-\vec{S}^2-\vec{S}_d^2)~,~~\alpha >0.
-\label{eq:stargraph_hamiltonian}
 \end{eqnarray}
@@
 |S_d,S;J,M\rangle &=& \sum_{S_d^z,\{S_i^z\}} \mathcal{D}_{S_d^z,\{S_i^z\}} |S_d^z,S_1^z,\cdots,S_K^z\rangle
-\label{eq:wf_fundamental_basis}
 \end{eqnarray}
@@
 \subsubsection{Impurity entanglement entropy}
+\noindent Here we are interested in finding the entanglement of the central impurity spin with the rest of the multi-channel bath zero mode.
+We know that for multi channel case the ground state is degenerate, thus for each degenerate state we can calculate the entanglement entropy.
+As we have already discussed for $N_{ch}$ number of channels there are $N_{ch}$ number of degenerate ground states, labeled by the $J_z$ quantum number.\\
+\par For single channel case the the ground state is unique and is 
+\begin{eqnarray}
+|J=0,J_z=0 \rangle &=& \frac{1}{\sqrt{2}} (|\uparrow_{d}\downarrow_0\rangle -|\downarrow_d \uparrow_0\rangle)
+\end{eqnarray}
+Thus, one can easily calculate the reduced density matrix of the impurity by tracing out the $0^{th}$ state.
+From that reduced denisty matrix the entanglement entropy is $\log 2$, which is maximum possible for a spin-1/2.
+\par Next, we are interested in findig this entanglement entropy for the multi-channel case $N_{ch}>1$.
+We have generated the degenerate ground states analytically using the Clebsch-Gordon coefficients.
+On this wavefunctions we do various entanglement and correlation studies.
+We start with the ground state wavefunction, $|\psi_g\rangle_{J_z}=|1/2_{d},S;J,J_z\rangle$, starting with one of those degenerate ground states labeled by $J_z$ we calculate the density matrix.
+\begin{eqnarray}
+\rho_{J_z}=|\psi_g\rangle_{J_z} \langle\psi_g|_{J_z}
+\end{eqnarray}
+
 \begin{figure}[!h]
@@
 \includegraphics[scale=0.32]{plt/EE_multi_channel_ANN.png}
-\caption{Caption }
-\label{fig:EE_d}
-\end{figure}
-\noindent Here we are interested in finding the entanglement of the central impurity spin with the rest of the multi-channel bath zero mode.
-For single channel case the the ground state is unique and is $|J=0,J_z=0 \rangle = \frac{1}{\sqrt{2}} (|\uparrow_{d}\downarrow_0\rangle -|\downarrow_d \uparrow_0\rangle)$.
-Thus, one can easily calculate the reduced density matrix of the impurity by tracing out the $0^{th}$ state.
-From that reduced denisty matrix the entanglement entropy is $\log 2$, which is maximum possible for a spin-1/2.
-In the case of multi-channel problem there are $K$ orthogonal set of ground states $|J^z\rangle$, for each such state the entaglement is different.
-The state $|J^z\rangle \equiv |S_d=1/2,S=K/2;(S-1/2),J^z\rangle$ can be written in the fundamental basis as shown in the Eq.\eqref{eq:wf_fundamental_basis}.
-Then the density matrix is $\rho=|J^z\rangle\langle J^z|$ from which we can calculate the reduced density matrix by partial tracing the impurity degree of freedom
-%$\rho_{d}=\textrm{Tr}_{d} \rho=\sum_{S_d^z} \langle S_d^z| \rho | S^z_d\rangle$. 
-\begin{eqnarray}
-\rho_{d}&=& \textrm{Tr}_{d} \rho=\sum_{S_d^z} \langle S_d^z| \rho | S^z_d\rangle ~,~~EE_d = -\rho_{d} \log \rho_{d}
-\end{eqnarray}
-\noindent The eigenvalues of this reduced density matrix given by $\lambda_i$ is called entanglement spectrum.
-We are interested in the von-Neumann entanglement entropy of the impurity spin with thte rest ($EE_d$).
-We are intersted in the scaling of this entanglement entropy with the channel number.
-As shown in the Fig.\ref{fig:EE_d} the x-axis is the channel number and for a particular channel there are may possible entanglement values corresponding to different $J^z$ states.
-The minimum entanglement entropy state (associated with the $J^z=J$ state) decreases show the classical nature of this maximally polarized state.
-On the other hand the maximum entanglement entropy (associated with $J^z_{min}$ state) for a particular channel $K$ is saturating to $\log K$ in the large $K$ limit.
-Another important result that we see, for any odd value of $K$ the minimum entanglement entropy associated with $J^z=0$ is $\log 2$ shows a formation of perfectly entangled state made out of more than 2 spins (e.g; singlet).
-In this state $|J^z=0\rangle$ all the $K$(odd) outer spins participate in quantum scattering with the central impurity spin in such a way the central spin is maximally entangled which is not the case for any other $J^z$ state.
-In the large $K$ limit irrespective it's even and odd nature there are always a $J^z_{min}$ state where the central impurity spin is maximally entangled.
-\begin{figure}[!h]
-\centering
 \includegraphics[scale=0.32]{plt/outer_EE_multi_channel_ANN.png}
-\caption{caption}
-\label{fig:EE_outer}
-\end{figure}
-In a $K$ channel system all the outer spins are equivalent (has $Z_N$ symmetry), thus studying the entanglement of any one outer spin with the rest is enough.
-Here we do a similar entanglement entropy study where we get the reduced density matrix ($\rho_o$) by partial tracing out any one outer spin say the $l^{th}$ ($1\leq l \leq K$) one $S^z_{l}$.
-\begin{eqnarray}
-\rho_{o} &=& \textrm{Tr}_{l} \rho =\displaystyle\sum_{S^z_{l}} \langle S^z_l | \rho | S^z_{l} \rangle~,~EE_o=-\rho_{o}\log \rho_{o}
-\end{eqnarray}
-We do a similar entanglement scaling with the channel number $K$.
-We find that minimum entanglement entropy associated with the state $J^z=J$ is approaching zero in the limit $K\gg 1$.
-In contrast the minimum entanglement entropy associated with $J^z_{min}$ state is saturating at $\log 2$ in the large $K$.
-Thus in the state $J^z=0$ for any $K$ (or $J^z=\pm 1/2$ for $K\gg 1$) any outer spin is maximally entangled with the rest.
-
-\par The above entanglement studies Fig.(\ref{fig:EE_d},\ref{fig:EE_outer}) show  that for odd channel case there exist a state $J^z=0$ where the central spin $S_d$ and any outer spin $S_i$ is maximally entangled with the rest.
-This shows the special and unique property of the stargraph ground state where you can create state made out of morethan 2 spins where each any every one is maximally entangled with the rest.
-Thus this stargraph ground state is very important in the quantum information theory.
-\textbf{write here}
-
-\subsubsection{Macroscopic singlet state}
-\noindent  The $|J^z=0\rangle_{K} $ state of a $K$(odd) channel stargraph problem can be very genrally written as
-\begin{eqnarray}
-|J^z=0\rangle_K &=& \frac{1}{\sqrt{2}} \bigg[ |\Uparrow\rangle_d \otimes |\gamma_{\downarrow}\rangle_K -  |\Downarrow\rangle_d \otimes |\gamma_{\uparrow}\rangle_K \bigg]  
-\label{eq:maximally_entangled_state}
-\end{eqnarray}
-where $|\Uparrow\rangle_d$ and $|\Downarrow\rangle_d$ represents the impurity state $S_d^z=\pm 1/2$ respectively.
-Let's define $U_{+}$ represents the set of all possible sub-systems of the set $[K]$ with $(K+1)/2$ numbers of elements in it.
-We define complement of any one set $g\in U_+$ , $g^{c}$ such that $g\cup g^{c}=[K]$.
-\begin{eqnarray}
-|\gamma_{\sigma} \rangle_K &=& \frac{1}{\sqrt{{K \choose \frac{K+1}{2}} }} \displaystyle\sum_{\substack{ g\in U_{+} }} \prod_{\substack{i\in g \\j\in g^c}} |\sigma_i\rangle \otimes |\bar{\sigma}_j \rangle~,~
-\end{eqnarray}
-where $\sigma_i=\pm 1/2$ and $\bar{\sigma}_i=-\sigma_i$, $\pm 1/2$ representing the state $\uparrow_i,\downarrow_i$ respectively for the $i^{th}$ spin.
-Thus the density matrix for this state $|J^z=0\rangle_K$ can be written as $\rho=|J^z=0\rangle_K \langle J^z=0|_K$.
-For this state one can simply verify that $\rho_{d}=\textrm{Tr}_d \rho=\frac{1}{2} (|\gamma_{\downarrow}\rangle_K \langle\gamma_{\downarrow}|_K + |\gamma_{\uparrow}\rangle_K \langle\gamma_{\uparrow}|_K)$  which has eigenvalues $1/2,1/2$ leading to the entanglement entropy $S_{d}= \log 2$.
-Similary one can verify that the entanglement entropy of any other spin with the rest is $\log 2$.
-Thus all the spins in the state eq.\eqref{eq:maximally_entangled_state} is maximally entangled with the rest representing a macroscopic singlet state with morethan $2$ spins.
+\caption{Y-axis shows the impurity entanglement entropy with the rest and X-axis shows the number of channels $N_{ch}$.
+For one value of $N_{ch}>1$, there are $N_{ch}$ degenerate ground states and their corresponding impurity entanglement entropy.
+}
+\end{figure}
+
+\noindent Using the wavefunction we can do the partial tracing on the impurity spin to get the reduced denisty matrix of the rest.
+From that we get entanglement entropy for different number of channels.
+For even number of channel cases $J_z$ and $-J_z$ sector has same entanglement entropy.
+For the case of odd $N_{ch}$ there also $\pm J_z$ sectors shares same entanglement entropy, but there is a state $J_z=0$ which has entanglement entropy $\log 2$.
+Thus from the above we can see that $J_z=0$ state corresponding to odd number of channels shows perfect screenig interms of the maximum entanglement entropy and $J_z=0$ magnetization.
 
 \subsubsection{Mutual Information}
+
+Mutual information between two sub-systems $A, B$ is defined as, 
+\begin{eqnarray}
+I^2(A:B)=S_A+S_B-S_{A\cup B}
+\end{eqnarray}
 
@@
 \includegraphics[scale=0.32]{plt/I_2_vs_Nch_0_1}
-\caption{ds}
-\label{fig:MI_d_o}
-\end{figure}
-\noindent In the above study our focus was on the von-Neumann entanglement entropy, now we are interested in the correlation signatures present in the stargraph grounds states.
-Mutual inforamtion is one such measure which captures the correlations present between two subsystems (A,B) in a particular state defined as
-\begin{eqnarray}
-I^2(A:B)=S_A+S_B-S_{A\cup B}
-\end{eqnarray}
-where $S_{A}$ is the von-Neumann entanglement entropy of the subsystem $A$ with the rest.
-Here we are interested in computing two types of mutual inforamtions first, study the mutual information between the impurity-spin and one outer spin $I^2(d:o)$.
-Because all the outer spins are symmetric, the mutual information between impurity-spin with any one outer spin is same and can capture the correlation between two $A$ and $B$.
-We have done a scaling study of this mutual information for different channel numbers $K$.
-As shown in the Fig.\ref{fig:MI_d_o} in the large $K$ limit the maxima of the mutual information associated with the state $J^z_{min}$ is saturating at $1.076$ and the Mutual information associated with the state $J^z=J$ is decreasing showing the classical limit.
+\includegraphics[scale=0.32]{plt/I_2_vs_Nch_1_2}
+\caption{\textit{Left:} Y-axis is the mutual information between the impurity-spin and one outer spin and x-axis is the number of channel $N_{ch}$.
+\textit{Right:} This shows the variation of mutual inforamtion between two outer spins.}
+\label{fig:MI_vs_Nch}
+\end{figure}
+
+We first study the mutual information between the impurity-spin and one outer spin $I^2(d:o)$.
+Because all the outer spins are symmetric, the mutual information between impurity-spin with any one outer spin is same.
+Next we calculate the mutual information between two outer spin $I^2(o:o)$.
+One can see that the maximum mutual information for both the cases are from the $(J_z)_{min}$ state.
+For odd number of channels $(J_z)_{min}=0$ and for even number of channels $\pm (J_z)_{min}=\pm 1/2$.
+And the minimum mutual information corresponds to the $\pm (J_z)_{max}=\pm J$ state.\\
+
+\par As can be seen from the above Figure.\ref{fig:MI_vs_Nch} that  both the maximum mutual information of $I^2(d:o)$ and $I^2(o:o)$ try to saturate near the same value.
+Thus in the lowest $J_z$ sector the entanglement distribution between impurity and outer vs outer and outer is same.
+Which suggests that even though there were no coupling among the outer spins explicitly, there are entanglement among them.
+The minimum of the mutual information coming from the largest $J_z$ sector, the $I^2(o:o)$ corresponding to this sector asymptotically approach zero for large $N_{ch}$ limit.
+Which shows that in the large channel limit $N_{ch}\gg 1$ though the $min~I^2(o:o)$ pparoach zero the $min~ I^2(d:o)$
+
+\subsubsection{Tri-partite information}
+\noindent Apart from Mutual information we can calculate the tri-partie information also. This tri-partite information is defined among three sub-systems $A,B,C$ , as
+
+\begin{eqnarray}
+I^3_{A,B,C} &=& (S_A+S_B+S_C)-(S_{AB}+S_{BC}+S_{CA})+S_{ABC}~,
+\end{eqnarray}
+
 \begin{figure}[!h]
-\includegraphics[scale=0.32]{plt/I_2_vs_Nch_1_2}
-\caption{ds}
-\label{fig:MI_o_o}
-\end{figure}
-Next, we have done a similar study by calculating the mutual information between two outer spin $I^2(o:o)$.
-In this also we find that the maximum mutual information between any outer spins saturates at the value $1.076$ similar to the $I^2(d:o)$ case.
-
-\par As can be seen from the above Figure.(\ref{fig:MI_d_o},\ref{fig:MI_o_o}) that  both the maximum mutual information of $I^2(d:o)$ and $I^2(o:o)$ try to saturate near the same value.
-Thus in the large $K$ limit in the $J^z_{min}$ state mutual information between any two spins in the stargrah model is same saturating at a constant value ($1.076$).
-Though the difference can be seen in the state $J^z=J$ where the mutual information thus correlation s between two outer spins vanishes in the large $K$ limit faster than the mutual information between the impurity and any one outer spin.
-Thus correlation wise there is no difference between impurity-outer pair and outer-outer pair in the large $K$ limit.
-
-\subsubsection{Multi-partite information}
-\noindent Similar to the mutual inforamtion one can calculate any higher order mutli-partie inforamtion to find the nature of the correlations present in different ground states.
-We define the tripartite information among three subsystems $A,B,C$ as $I^3_{ABC} = (S_A+S_B+S_C)-(S_{AB}+S_{BC}+S_{CA})+S_{ABC}~$.
-This tri-parite information scaling with the number of channels $K$ also shown behavior similar to the mutual information case, the highest tri-partite information is associated with the $J^z_{min}$ state and saturating in the limit of $K\gg 1$.
-One can measure $N-$partite information for a collection of subsystems (CSS) $\{\mathcal{A}\}\equiv\{A_1,A_2,\cdots,A_K\}$.
-To define the $N-$partite information, we first define the power set of the CSS $\{\mathcal{A}_N\}$ as $\mathcal{P}(\{\mathcal{A}_{N}\})$, and the collection of all subsets of $\mathcal{P}(\{\mathcal{A}_{N}\})$ with $m$ subsystems in it as $\mathcal{B}_m(\{\mathcal{A}_N\})\equiv \{ Q~| ~Q\subset \mathcal{P}(\{\mathcal{A}_{N}\}), |Q|=m \}$.
-We also define the union and intersection of all the subsystems present in $Q$ as ${V}_{\cup}({Q})\equiv \bigcup_{A\in Q} A$ and ${V}_{\cap}({Q})\equiv \bigcap_{A\in Q} A$ respectively.
-Finally, the von Neumann entanglement entropy of the subsystem $A$ is given by $S_{A} $.
-Then the $N-$partite information that we are interested in is defined as
-\begin{eqnarray}
-I^{N}_{\{\mathcal{A}_N\}} &=& \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.~~~~
-\label{eq:I_N_definition}
-\end{eqnarray}
-Studying these mutli-partite informations one can understand the nature of the correlations present among the outer spins.
+\includegraphics[scale=0.32]{plt/I_3_vs_Nch_1_2_3}
+%\includegraphics[scale=0.32]{plt/I_4_vs_Nch_1_2_3_4}
+\caption{This plot shows the variation of the tri-partite information with the number of channels $N_{ch}$.}
+\label{fig:I3_vs_Nch}
+\end{figure}
+\noindent Our tri-partite infrmation measure (Fig.\ref{fig:I3_vs_Nch}) among the outer spins shows that the just like the mutual information the minimum tri-partite information asymptotically approaches zero in the $N_{ch}\gg 1$ limit.
+Same is the case for 4-partite information also.
+
+\subsubsection{$I_N$ vs N}
+\noindent Here we are intersted in understading the entanglement dristribution among different number of outter spins.
+To find that out we take a multi-channel stargraph model with $N_{ch}$ noumber of outer spins.
+We calculate different multi partite inforamtions $I^m, m\in \{2,\cdots,N_{ch}\}$ on it's $N_{ch}$ degenerate ground states.
+
 \begin{figure}
@@
 \end{figure}
-\noindent Our study of this multi-partite information presented in the above Fig.\eqref{fig:Im_vs_m} shows that the higher oreder multi partite informations decreaseas as you increase the order folloring a power law.
-\textbf{Show the fittings.}
+\noindent Our above study (Fig.\ref{fig:Im_vs_m}) shows that the mutual imformation has the maximum value and higher odere multi-parite informations is smaller and smaller approaching zero.
 
 \subsection{Correlation Studies}
-Apart from the entanglement studies one can calculate various correlation and energy studies in the various degenerate ground state of this stargraph model.
+
 \subsubsection{Quantum energy}
+\noindent Here we are interested in the energy expectation value arising from the quantum fluctuation part of the Hamiltonian (\ref{eq:zero_mode}).
+We define ising enregy $E_{ising}$ and quantum energy $E_{Q}$ in the ground state $|\psi_g\rangle$ as,
+\begin{eqnarray}
+E_{ising} = |\langle \psi_g | \mathcal{H}^c_0 | \psi_g \rangle| ,~~ E_{Q} &=& |\langle \psi_g | \mathcal{H}^Q_0 | \psi_g \rangle|=|E_g|-|E_{ising}|~, \nonumber\\
+&=& \frac{\alpha(S+1)}{2} - |E_{ising}|.
+\end{eqnarray}  
+This quantum energy $E_Q$ is generated by the spin-flips between the impurity spin and the outer spin.
+Thus it is interesting to findout how this quantum energy changes with the increase of the number of channels $(N_{ch})$.
+Another important parameter is the Quantum enrgy per channel, $e_Q=|E_Q|/N_{ch}$, and it's variation towards the infinity channel limit.
+We know in the gorund state $N_{ch}=2S$ thus,
+\begin{eqnarray}
+e_Q &=& \frac{\alpha(S+1)}{4S} - \frac{|E_{ising}|}{2S} ~,~\nonumber\\
+%&=& \alpha\frac{(N_{ch}+2)}{4N_{ch}}-\frac{|E_{ising}|}{N_{ch}} ~,~ \nonumber\\
+%&=& \alpha \bigg(\frac{1}{4} +\frac{1}{2N_{ch}} \bigg)-\frac{|E_{ising}|}{N_{ch}}~,~\nonumber\\
+&=& \frac{\alpha}{4} -\frac{1}{N_{ch}} \bigg(|E_{ising}| -\frac{\alpha}{2}  \bigg)~,~
+\end{eqnarray}
+Thus from the above equation of quantum energy per channel one can see that in the inifinity-channel limit $N_{ch}\rightarrow \infty$,
+
+\begin{eqnarray}
+e_Q = \frac{\alpha}{4}- \frac{|E_{ising}|}{N_{ch}} < \frac{\alpha}{4}~,~
+\end{eqnarray}
+
 \begin{figure}[!h]
@@
 \caption{This shows the variation of quantum energy per channel with $1/N$, where $N=N_{ch}+1$ is the total number of spins in the systems including the impurity spins. }
-\label{fig:quantum_energy}
-\end{figure}
-\noindent In the stargraph model Hamiltonian there is a classical ising term ($S_d^zS^z$) and a quantum fluctuation term.
-Here we are interested in the energy expectation value arising from the quantum fluctuation part of the Hamiltonian (eq.\ref{eq:stargraph_hamiltonian}).
-We define ising enregy $E_{ising}$ and quantum energy $E_{Q}$ in the ground state $|\psi_g\rangle$ as,
-\begin{eqnarray}
-E_{ising} = |\langle \psi_g | \mathcal{H}^c_0 | \psi_g \rangle|, E_{Q} &=& |\langle \psi_g | \mathcal{H}^Q_0 | \psi_g \rangle|=|E_g|-|E_{ising}|~, \nonumber\\
-&=& {\alpha S_d(S+1)}- |E_{ising}|.
-\end{eqnarray}  
-This quantum energy $E_Q$ is generated by the spin-flips between the impurity spin and the outer spin.
-Our goal here to understand the nature of this $E_Q$ as we go to the large $K$ limit, whether there are some remenant quantum fluctuation even in the thermodynamic limit.
-To answer that questio we intrduce another important parameter, quantum enrgy per channel, $e_Q=|E_Q|/K$ .
-We know in the gorund state $K=2S$ thus,
-\begin{eqnarray}
-e_Q &=& \frac{\alpha S_d(S+1)}{K} - \frac{|E_{ising}|}{K} ~,~\nonumber\\
-%&=& \alpha\frac{(N_{ch}+2)}{4N_{ch}}-\frac{|E_{ising}|}{N_{ch}} ~,~ \nonumber\\
-%&=& \alpha \bigg(\frac{1}{4} +\frac{1}{2N_{ch}} \bigg)-\frac{|E_{ising}|}{N_{ch}}~,~\nonumber\\
-&=& \frac{\alpha S_d}{2} -\frac{1}{K} \bigg(|E_{ising}| -\alpha S_d  \bigg)~,~
-\end{eqnarray}
-Thus from the above equation of quantum energy per channel one can see that in the large channel limit 
-\begin{eqnarray}
-e_Q = \frac{\alpha S_d}{2}- \frac{|E_{ising}|}{K} < \frac{\alpha S_d}{2}~,~K\rightarrow \infty, 
-\end{eqnarray}
-As shown in the above Fig.\ref{fig:quantum_energy} for the case of $S_d=1/2$, for a particular channel $K$ the maximum quantum energy corresponds to the $|J^z|_{min}$ state and the minimum is related to the $|J^z|=J$ state.
-In the large channel limit one can see the quatnum energy associated with the $|J^z|=J$ vanishes showing the classical nature of this state where there is no quantum fluctuation present.
-Whereas, in the state $|J^z|_{min}$ there are finite non-zero quantum fluctuation present in it, showing the true quantum nature of this macroscpic singlet state as we have already discussed.
+\end{figure}
+
+\subsubsection{Correlation study}
+Here we want to calculate various correlation functions in the ground state. We start with the expectation value of $J_z^2$ in the ground state $|\psi_g\rangle$,
+\begin{eqnarray}
+j_z^2&=&\frac{1}{N_{ch}}\langle \psi_g | J_z^2 | \psi_g \rangle~=\frac{1}{N_{ch}} \bigg[ J^2-(J_x^2+J_y^2) \bigg] ~,\nonumber\\
+%&=& \frac{1}{N_{ch}} \bigg[ (S^2-1/4)-(J_x^2+J_y^2) \bigg] \nonumber\\
+&=& \frac{1}{N_{ch}} \bigg[ \frac{(N_{ch}^2-1)}{4}-(J_x^2+J_y^2) \bigg]
+\end{eqnarray}
+
+\begin{eqnarray}
+\langle \psi_g | J_{z}^2 | \psi_g \rangle_{max} &=& \bigg(\frac{N_{ch}-1}{2}\bigg)^2~,\nonumber\\
+\langle \psi_g | J_{z}^2 | \psi_g \rangle_{min} = \bigg(\frac{N_{ch}-(N_{ch}-1)}{2}\bigg)^2&=&\frac{1}{4}~,~\textrm{for $N_{ch}$ even}.\nonumber\\
+&=& 0 ~,~\textrm{for $N_{ch}$ odd}.
+\end{eqnarray}
+Thus,
+\begin{eqnarray}
+\langle (J_x)^2+(J_y)^2 \rangle_{max}&=&\langle J^2 \rangle - \langle J_z^2 \rangle_{min} ~,\nonumber\\
+&=& \frac{N_{ch}^2-1}{4}-\frac{1}{4}=\frac{N_{ch}^2-2}{4}~, \textrm{for $N_{ch}$ even } \nonumber\\
+&=& \frac{N_{ch}^2-1}{4}~, \textrm{for $N_{ch}$ odd } \nonumber
+\end{eqnarray}
+Which shows, for single channel case $N_{ch}=1$, this quntum fluctuation expectation value vanishes, while for multi channel this takes non-zero values. Thus 
+\begin{eqnarray}
+\frac{1}{N_{ch}}\langle (J_x)^2+(J_y)^2 \rangle_{max}
+&=& \frac{N_{ch}}{4}-\frac{1}{2N_{ch}}  ~, \textrm{for $N_{ch}$ even } \nonumber\\
+&=& \frac{N_{ch}}{4}-\frac{1}{4N_{ch}}~, \textrm{for $N_{ch}$ odd } \nonumber
+\end{eqnarray}
+Thus in the large channel number limit $N_{ch}\gg 1$, one can see that 
+\begin{eqnarray}
+\frac{1}{N_{ch}}\langle (J_x)^2+(J_y)^2 \rangle_{max}
+\rightarrow \frac{N_{ch}}{4}~,~\textrm{for both even and odd $N_{ch}$}
+\end{eqnarray}
+\noindent $J_z$ can take values $\{-J,-J+1,\cdots,J-1,J\}$ in the ground state, where $J=S-1/2=(N_{ch}-1)/2$.
 
 \subsubsection{Staggerred magnetization}
-\noindent  One can reqrite the Hamiltonian as $\alpha \vec{S}_d.\vec{S}=(\alpha/4) [( \vec{S}+\vec{S}_d)^2-( \vec{S}-\vec{S}_d)^2]$, this shows that $\vec{J}$ and the staggered magnetization $\vec{M}_s=\vec{S}-\vec{S}_d$ is both good quantum number for in this stargraph model.
-For single channel case $K=1$, ground state is an unique 2-spin singlet $|\psi_g\rangle =\frac{1}{\sqrt{2}} (|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle = |J=0,J_z=0\rangle$, which showns the prefect screening.
-Our goal here to capture the breakdown of the screening by calculating this staggerd magnetization for a multichannel problem.
+One can analytically check the single channel Kondo results. $N_{ch}=1$, thus here the ground state is unique.
+\begin{eqnarray}
+|\psi_g\rangle &=& \frac{1}{\sqrt{2}} \bigg(|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle\bigg)= |J=0,J_z=0\rangle
+\end{eqnarray}
+Thus in this ground state $\langle J_z \rangle=0$ and the  entanglement entropy is $\log 2$ the maximum value. Now we define a staggered magnetization (\ref{fig:st_mag}) operator $M_s$ measure,
+
 \begin{figure}
@@
 \end{figure}
-%
-%
-%For the single channel case both the $\vec{S}_d$ and $\vec{S}$ are spin-1/2 object and the total spin is defined as $\vec{J}=\vec{S}_d+\vec{S}$. Here $\vec{S}$ is the total outer spin.
-%
-%\begin{eqnarray}
-%M_s^2 = \langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle &=& \langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle \nonumber\\
-%&=& 2 \langle \psi_g | \vec{S}_d^2 +\vec{S}^2 |\psi_g\rangle \nonumber\\
-%&=& 3
-%\end{eqnarray}
-For a general $K$ cahnnel we find that 
-\begin{eqnarray}
+
+\begin{enumerate}
+\item For the single channel case both the $\vec{S}_d$ and $\vec{S}$ are spin-1/2 object and the total spin is defined as $\vec{J}=\vec{S}_d+\vec{S}$. Here $\vec{S}$ is the total outer spin.
+
+\begin{eqnarray}
+M_s^2 = \langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle &=& \langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle \nonumber\\
+&=& 2 \langle \psi_g | \vec{S}_d^2 +\vec{S}^2 |\psi_g\rangle \nonumber\\
+&=& 3
+\end{eqnarray}
+
+\item \begin{eqnarray}
 M_s^2 &=& \langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle \nonumber\\
-%&=&    2\bigg(S_d(S_d+1)+ \frac{K(K+2)}{4}\bigg)- \frac{(K+1)(K-1)}{4}   \nonumber\\
-%&=& 2S_d(S_d+1) + \frac{1}{2}(K^2+2K) - \frac{1}{4}(K^2-1)\\
-&=& 2S_d(S_d+1) +\frac{K^2}{4} + K +\frac{1}{4}
-%%%%&=& \frac{N_{ch}^2}{4}+N_{ch}+\frac{7}{4}
-\end{eqnarray}
+&=&  \bigg\langle \psi_g \bigg| 2\bigg(\frac{3}{4}+ \frac{N_{ch}(N_{ch}+2)}{4}\bigg)- \frac{(N_{ch}+1)(N_{ch}-1)}{4} \bigg|\psi_g \bigg\rangle \nonumber\\
+&=& \frac{N_{ch}^2}{4}+N_{ch}+\frac{7}{4}
+\end{eqnarray}
+
+\end{enumerate}
 
@@
 \begin{eqnarray}
-m_s^2=\frac{M_s^2}{K^2}= \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}
-%=\frac{1}{4}+\frac{1}{N_{ch}}+\frac{7}{4N_{ch}^2} \xrightarrow[]{N_{ch}\gg 1} \frac{1}{4}+\frac{1}{N_{ch}}~,
-\end{eqnarray}
-Which shows, in the large channel limit this staggered magnetization , $m^2_s\Rightarrow 1/4.$ for any finite $S_d$.
+m_s^2=\frac{M_s^2}{N_{ch}^2}=\frac{1}{4}+\frac{1}{N_{ch}}+\frac{7}{4N_{ch}^2} \xrightarrow[]{N_{ch}\gg 1} \frac{1}{4}+\frac{1}{N_{ch}}~,
+\end{eqnarray}
+\begin{eqnarray}
+\frac{\vec{J}^2}{N_{ch}^2}&=&\frac{(\vec{S}_d+\vec{S})^2}{N_{ch}^2}= \frac{N^2_{ch}-1}{4N^2_{ch}} \xrightarrow[]{N_{ch}\gg 1} \frac{1}{4}~. \nonumber 
+\end{eqnarray}
+
 Using the $SU(2)$ property of our problem, we can define $m_s$ for each spatial direction, in 3D there are three independent spatial direction.
@@
 \end{eqnarray}
-Just to recall, for the single channel case $\langle (m_s^z)^2 \rangle =1$ showing the perfect screening, on the otherhand in the large channel limit this becomes $\langle (m_s^z)^2 \rangle =1/12$ showing the breakdown of the screening.
-For the $S_d=1/2$ case we have shown how this staggered magnetization perchannel decreases in the multichannel case in the Fig.\ref{fig:st_mag}.
-This clearly shown that this staggerd magnetization is maximum.
-
-%\begin{eqnarray}
-%\frac{\vec{J}^2}{N_{ch}^2}&=&\frac{(\vec{S}_d+\vec{S})^2}{N_{ch}^2}= \frac{N^2_{ch}-1}{4N^2_{ch}} \xrightarrow[]{N_{ch}\gg 1} \frac{1}{4}~. \nonumber 
-%\end{eqnarray}
-%
-%
-%To begin with we first recall that for single channel case $M_s^2=3$.
-%
-%We define $m_Q^2=m_s^2-1/4$ which in the the large $N_{ch}$ limit becomes $1/N_{ch}$ and eventually vanishes in the $N_{ch}\rightarrow \infty$ limit. 
-%
-%
-%\noindent Thus to summarize,
-%\begin{enumerate}
-%\item In the single channel problem, $\langle (m_s^z)^2 \rangle=1$. 
-%\item In the multi-channel case,  
-%$\langle (m_s^z)^2 \rangle=\frac{1}{3N_{ch}}+\frac{1}{12}+\frac{7}{12N_{ch}^2} \xrightarrow[]{N_{ch}\gg 1} \frac{1}{12}+\frac{1}{3N_{ch}}\rightarrow \frac{1}{12}$. 
-%This show partial screening.
-%\end{enumerate}
+We define $m_Q^2=m_s^2-1/4$ which in the the large $N_{ch}$ limit becomes $1/N_{ch}$ and eventually vanishes in the $N_{ch}\rightarrow \infty$ limit.
+
+\noindent Thus to summarize,
+\begin{enumerate}
+\item In the single channel problem, $\langle (m_s^z)^2 \rangle=1$. 
+\item In the multi-channel case,  
+$\langle (m_s^z)^2 \rangle=\frac{1}{3N_{ch}}+\frac{1}{12}+\frac{7}{12N_{ch}^2} \xrightarrow[]{N_{ch}\gg 1} \frac{1}{12}+\frac{1}{3N_{ch}}\rightarrow \frac{1}{12}$. 
+This show partial screening.
+\end{enumerate}
 
@@
 \begin{enumerate}
-%\item $M_s^2$ vs $N_{ch}$.
+\item $M_s^2$ vs $N_{ch}$.
 \item Uncompensated Quantum Fluctuation vs $N_{ch}$.
 \end{enumerate}
-
-\subsubsection{Correlation study}
-Here we want to calculate various correlation functions in the ground state. We start with the expectation value of $J_z^2$ in the ground state $|\psi_g\rangle$,
-\begin{eqnarray}
-j_z^2&=&\frac{1}{N_{ch}}\langle \psi_g | J_z^2 | \psi_g \rangle~=\frac{1}{N_{ch}} \bigg[ J^2-(J_x^2+J_y^2) \bigg] ~,\nonumber\\
-%&=& \frac{1}{N_{ch}} \bigg[ (S^2-1/4)-(J_x^2+J_y^2) \bigg] \nonumber\\
-&=& \frac{1}{N_{ch}} \bigg[ \frac{(N_{ch}^2-1)}{4}-(J_x^2+J_y^2) \bigg]
-\end{eqnarray}
-
-\begin{eqnarray}
-\langle \psi_g | J_{z}^2 | \psi_g \rangle_{max} &=& \bigg(\frac{N_{ch}-1}{2}\bigg)^2~,\nonumber\\
-\langle \psi_g | J_{z}^2 | \psi_g \rangle_{min} = \bigg(\frac{N_{ch}-(N_{ch}-1)}{2}\bigg)^2&=&\frac{1}{4}~,~\textrm{for $N_{ch}$ even}.\nonumber\\
-&=& 0 ~,~\textrm{for $N_{ch}$ odd}.
-\end{eqnarray}
-Thus,
-\begin{eqnarray}
-\langle (J_x)^2+(J_y)^2 \rangle_{max}&=&\langle J^2 \rangle - \langle J_z^2 \rangle_{min} ~,\nonumber\\
-&=& \frac{N_{ch}^2-1}{4}-\frac{1}{4}=\frac{N_{ch}^2-2}{4}~, \textrm{for $N_{ch}$ even } \nonumber\\
-&=& \frac{N_{ch}^2-1}{4}~, \textrm{for $N_{ch}$ odd } \nonumber
-\end{eqnarray}
-Which shows, for single channel case $N_{ch}=1$, this quntum fluctuation expectation value vanishes, while for multi channel this takes non-zero values. Thus 
-\begin{eqnarray}
-\frac{1}{N_{ch}}\langle (J_x)^2+(J_y)^2 \rangle_{max}
-&=& \frac{N_{ch}}{4}-\frac{1}{2N_{ch}}  ~, \textrm{for $N_{ch}$ even } \nonumber\\
-&=& \frac{N_{ch}}{4}-\frac{1}{4N_{ch}}~, \textrm{for $N_{ch}$ odd } \nonumber
-\end{eqnarray}
-Thus in the large channel number limit $N_{ch}\gg 1$, one can see that 
-\begin{eqnarray}
-\frac{1}{N_{ch}}\langle (J_x)^2+(J_y)^2 \rangle_{max}
-\rightarrow \frac{N_{ch}}{4}~,~\textrm{for both even and odd $N_{ch}$}
-\end{eqnarray}
-\noindent $J_z$ can take values $\{-J,-J+1,\cdots,J-1,J\}$ in the ground state, where $J=S-1/2=(N_{ch}-1)/2$.
 
@@
 \end{eqnarray}
-%Now 
-%\begin{eqnarray}
-%Z =\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon} ~~\Rightarrow ~~  \frac{dZ}{dT} &=& \sum_\epsilon d(\epsilon) e^{-\beta \epsilon}  (-\epsilon) \frac{d\beta}{dT} \nonumber\\
-%&=& \sum_\epsilon d(\epsilon) e^{-\beta \epsilon}   \frac{ \epsilon}{k_B T^2} =k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   
-%\end{eqnarray}
+Now 
+\begin{eqnarray}
+Z =\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon} ~~\Rightarrow ~~  \frac{dZ}{dT} &=& \sum_\epsilon d(\epsilon) e^{-\beta \epsilon}  (-\epsilon) \frac{d\beta}{dT} \nonumber\\
+&=& \sum_\epsilon d(\epsilon) e^{-\beta \epsilon}   \frac{ \epsilon}{k_B T^2} =k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   
+\end{eqnarray}
 Thus we get
@@
 S &=& -k_B \log \sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon}  -\frac{1}{\beta} \frac{k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   }{\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon}} \nonumber\\
-\lim_{\beta\rightarrow \infty} S &=& -k_B \log_2 d(\epsilon_{G})~,~~\lim_{\beta\rightarrow 0} S = -k_B \log \sum_\epsilon d(\epsilon)  \nonumber
+\lim_{\beta\rightarrow \infty} S &=& -k_B \log_2 d(\epsilon_{G})  ~~, \textrm{and}~~ \lim_{\beta\rightarrow 0} S = -k_B \log \sum_\epsilon d(\epsilon) 
 \end{eqnarray}
@@
 \subsubsection{Suseptibility}
-\noindent Here we want to calculate the field suseptibility of the stargraph.
-For that we need the entire spectrum of the stargraph Hamiltonian in the presence of field.
-There are two ways one can capture the suseptibility of the stargraph, first, by putting a small field to the central impurity and the other way is put a uniform field on all the outer spins and capture the suseptibility.
-
-\textit{Impurity-field susceptibility :} Now we add small magnetic field to the impurity spin and calculte the suseptibility as a function of temperatur for different channel cases.
+\begin{enumerate}
+\item Impurity-field susceptibility : Now we add small magnetic field to the impurity spin and calculte the suseptibility as a function of temperatur for different channel cases.
 \begin{figure}
@@
 \end{figure}
-As shown in the Figure.\ref{fig:suseptibility_impurity} above, for all $K>2$ case we can see that, at low temperature the suseptibility follows power law as afunction of temperature. 
-\begin{eqnarray}
-\chi_{imp}(T) \sim T^{-1} ~,~ \chi_{outer} \sim T^{-1}
-\end{eqnarray}
-The exponent for all the channels $K>2$ is $-1$. This shows the presence of an universality class. The powerlaw shows the critical nature of the system.
-
-\textit{Outer-field suseptibility: } Similar study can be done by putting an uniform field on all outer spins and calculating the suseptibility.
-Here also for all channles $K>2$ the exponent is $-1$ and supports the existance of universality and criticality.
+
+\item Outer-field suseptibility: Now we add a unifor magnetic field on the outer spins and calculate the suseptibility for different chanel cases.
 \begin{figure}
@@
 \end{figure}
-This susceptibility clearly shown the breakdown of screening in the multichannel cases with degenerate ground states in constrast to the single channel suseptibility which saturates at a finite value at low temperature.
+\end{enumerate}
+As can be seen from the above results that the both impurity and outer field suseptibility follows a power law in temperature for $K>1$ case. 
+\begin{eqnarray}
+\chi_{imp}(T) \sim T^{-1} ~,~\chi_{outer} \sim T^{-1}
+\end{eqnarray}
+This shows an universality among the greater than one channels.
 
@@
 \begin{eqnarray}
-&&\mathcal{H}_0= H_{0_1}+H_{0_2} \nonumber\\
-&=&\sum_{i=\{1,2\}}\bigg[ \alpha S^z_{imp}. (n_{i,\uparrow}-n_{i,\downarrow})/2 + \frac{1}{2}  ( S_{imp}^{+} c^{\dagger}_{i,\downarrow} c_{i,\uparrow} + \textrm{h.c.}  )\nonumber \bigg]
+\mathcal{H}_0= H_{0_1}+H_{0_2} &=& \alpha S^z_{imp}.\bigg(\frac{n_{1,\uparrow}-n_{1,\downarrow}}{2} \bigg) + \frac{1}{2} \bigg( S_{imp}^{+} c^{\dagger}_{1,\downarrow} c_{1,\uparrow} - S_{imp}^{-} c_{1,\uparrow}^{\dagger} c_{1,\downarrow} \bigg)\nonumber\\
+&& ~~~+~~ \alpha S^z_{imp}.\bigg(\frac{n_{2,\uparrow}-n_{2,\downarrow}}{2} \bigg) + \frac{1}{2} \bigg( S_{imp}^{+} c^{\dagger}_{2,\downarrow} c_{2,\uparrow} - S_{imp}^{-} c_{2,\uparrow}^{\dagger} c_{2,\downarrow} \bigg)
 \end{eqnarray}
@@
 In this basis we write down all $2^3=8$ states of the spin Hamiltonian eq.\eqref{eq:channel-2-spin}
-First the two degenerate ground states with energy $-\alpha= E_{\alpha_0}= E_{\alpha_1}$ is given as,
 \begin{eqnarray}
 |\alpha_0\rangle &=& \frac{1}{\sqrt{6}} \bigg[2|\Downarrow,1,0,1,0\rangle-|\Uparrow,0,1,1,0\rangle-|\Uparrow,1,0,0,1\rangle\bigg] \nonumber\\
-|\alpha_1\rangle &=& \frac{1}{\sqrt{6}} \bigg[2|\Uparrow,0,1,0,1\rangle-|\Downarrow,1,0,0,1\rangle-|\Downarrow,0,1,1,0\rangle\bigg] \nonumber
-\end{eqnarray}
-The doubly degenerate lowestlying excited state has energy $E_{\beta_1}=E_{\beta_2}=0$.
+|\alpha_1\rangle &=& \frac{1}{\sqrt{6}} \bigg[2|\Uparrow,0,1,0,1\rangle-|\Downarrow,1,0,0,1\rangle-|\Downarrow,0,1,1,0\rangle\bigg] \nonumber\\
+&& E_{\alpha_0}= E_{\alpha_1}= -\alpha
+\end{eqnarray}
 \begin{eqnarray}
 |\beta_0\rangle &=& \frac{1}{\sqrt{2}}\bigg[|\Downarrow,1,0,0,1\rangle-|\Downarrow,0,1,1,0\rangle \bigg] \nonumber\\
-|\beta_1\rangle &=& \frac{1}{\sqrt{2}} \bigg[ |\Uparrow,1,0,0,1\rangle-|\Uparrow,0,1,1,0\rangle \bigg]
-\end{eqnarray}
-Above these two excited states there are another dengenerate excited state manifold with energy $ E_{\gamma_0}=E_{\gamma_1}=E_{\gamma_2}=E_{\gamma_3}=\frac{\alpha}{2}$.
+|\beta_1\rangle &=& \frac{1}{\sqrt{2}} \bigg[ |\Uparrow,1,0,0,1\rangle-|\Uparrow,0,1,1,0\rangle \bigg]\nonumber\\
+&& E_{\beta_1}=E_{\beta_2}=0
+\end{eqnarray}
 \begin{eqnarray}
@@
 |\gamma_{1}\rangle &=& \frac{1}{\sqrt{3}}\bigg[ |\Uparrow,1,0,0,1\rangle+|\Uparrow,0,1,1,0\rangle+|\Downarrow,1,0,1,0\rangle \bigg] \nonumber\\
-|\gamma_{2}\rangle &=& |\Uparrow,1,0,1,0\rangle~,~~|\gamma_{3}\rangle = |\Downarrow,0,1,0,1\rangle 
+|\gamma_{2}\rangle &=& |\Uparrow,1,0,1,0\rangle \nonumber\\
+|\gamma_{3}\rangle &=& |\Downarrow,0,1,0,1\rangle \\
+&& E_{\gamma_0}=E_{\gamma_1}=E_{\gamma_2}=E_{\gamma_3}=\frac{\alpha}{2}
 \end{eqnarray}
@@
 \mathcal{H} &=& \frac{\alpha\hbar}{2}~ \vec{S}_d.
-\displaystyle\sum_{i=\{1,2\}} \displaystyle\sum_{\alpha,\beta\in\{\uparrow,\downarrow\}}c_{i\alpha}^{\dagger} \vec{\sigma}_{\alpha\beta} c_{i\alpha} +H_X
-%-t\displaystyle\sum_{i=\{1,2\}}\displaystyle\sum_{\substack{\langle i,l_i \rangle\\ \sigma}}(c^{\dagger}_{i,\sigma} c_{l_i,\sigma}+ \textrm{h.c.}) 
+\displaystyle\sum_{i=\{1,2\}} \displaystyle\sum_{\alpha,\beta\in\{\uparrow,\downarrow\}}c_{i\alpha}^{\dagger} \vec{\sigma}_{\alpha\beta} c_{i\alpha} -t\displaystyle\sum_{i=\{1,2\}}\displaystyle\sum_{\substack{\langle i,l_i \rangle\\ \sigma}}(c^{\dagger}_{i,\sigma} c_{l_i,\sigma}+ \textrm{h.c.})
 %\\
@@
 \begin{eqnarray}
-H^{(2)}_{diag} (1/2) &=& \frac{2t^2}{E_0} \hat{I} - \frac{2t^2}{3E_0} ( S_{l_1}^z + S_{l_2}^z)
+H^{(2)}_{diag} (1/2) &=& \frac{2t^2}{E_0} \hat{I} - \frac{2t^2}{3E_0} \bigg[ (n_{l_1\uparrow}-n_{l_1\downarrow}) +(n_{l_2\uparrow}-n_{l_2\downarrow}) \bigg]
 %= \frac{2t^2}{E_0} \hat{I} - \frac{4t^2}{3E_0} \bigg[S_{l_1}^z+S_{l_2}^z\bigg]
@@
 \begin{eqnarray}
-H^{(2)}_{diag} (-1/2) &=& \frac{2t^2}{E_0} \hat{I} + \frac{2t^2}{3E_0} (S_{l_1}^z+S_{l_2}^z)
+H^{(2)}_{diag} (1/2) &=& \frac{2t^2}{E_0} \hat{I} + \frac{2t^2}{3E_0} \bigg[ (n_{l_1\uparrow}-n_{l_1\downarrow}) +(n_{l_2\uparrow}-n_{l_2\downarrow}) \bigg]
 %= \frac{2t^2}{E_0} \hat{I} + \frac{4t^2}{3E_0} \bigg[S_{l_1}^z+S_{l_2}^z\bigg]
 \end{eqnarray}
-where $S_{l_i}^z=(n_{l_i\uparrow}-n_{l_i\downarrow})/2.$ This above result shows that the diagonal correlation to the LEH coming from the ground states $J^z=\pm 1/2$ has a emergent field term. 
-\begin{eqnarray}
-H^{(2)}_{diag} &=& -4t^2 \hat{I}
-\end{eqnarray}
-But the total contribution shows the trivial nature of the diagonal part in the LEH.
-This clearly shown that there is no Fermi liquid terms present in low energy in the 2-channel Kondo problem.
-Here, $\hat{I}$ is the identity operator made out of all $2^4=16$ possible number operator combinations as shown below
+Thus the diagonal part of the effective Hamiltonian in the second order is 
+\begin{eqnarray}
+H^{(2)}_{diag} &=& \sum_{i} \sum_l |\alpha_i\rangle\langle \alpha_i | \frac{|\langle \alpha_i  | V| \mu_l \rangle|^2 }{E_0-E_{l}} \nonumber\\
+%= H^{(2)}_{diag} (1/2)+H^{(2)}_{diag} (-1/2)= \frac{4t^2}{E_0} \hat{I}\nonumber\\
+&=& -4t^2 \hat{I}
+\end{eqnarray}
+where $\hat{I}$ is the identity operator made out of all $2^4=16$ possible number operator combinations as shown below
 \begin{eqnarray}
@@
 \end{eqnarray}
-Due to the ground state degeneracy in the 2-channel problem, there are possible quantum scattering within the ground state manifold among those degenerate states.
-This leads to a low energy effective Hamiltonian which is offdiagonal in nature as shown below,
-\begin{eqnarray}
-H_{NFL}&=&H^{(2)}_{off} = \sum_{i\neq j} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j | \nonumber\\
-&=& -\frac{8t^2}{3} [ (S_1^z)^2 c_{2\uparrow}^{\dagger}c_{2\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) \nonumber\\
-&+& (S_2^z)^2 c_{1\uparrow}^{\dagger}c_{1\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) ] + \textrm{h.c.} ~,~~~~
+Now we are interested in calcualting the offdiagonal term present in the second order low energy effective Hamiltonian which is given as
+\begin{eqnarray}
+H^{(2)}_{off} &=& \sum_{i\neq j} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j | \nonumber\\
+&=& -\frac{8t^2}{3} \bigg[ (S_1^z)^2 c_{2\uparrow}^{\dagger}c_{2\downarrow} \bigg(  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger} \bigg) \nonumber\\
+&+& (S_2^z)^2 c_{1\uparrow}^{\dagger}c_{1\downarrow} \bigg(  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger} \bigg)\bigg] + \textrm{h.c.} \nonumber\\
 \label{eq:hamiltonian_NFL}
 \end{eqnarray}
-This LEH is purely a non-Fermi liquid.
-The emergenec of non-Fermi liquid is primarily coming due to the degenerate ground states present in the stargraph problem in the absence of the realspace hopping terms.
-One can see that though there was no prior inter channel direct interactions, the LEH shows the emergence of such terms through correlated quantum scatterings.
-
 \subsection{Studying the LEH}
-\noindent In order to understnad this non-Fermi liquid we calculate some thermodyanmic quantities like impurity specific heat and suseptibility.
-First we calcualte the self energy of this NFL hamiltonian.
+\subsubsection{Self energy and Specific heat}
+Here we study this LEH to understant valrious features like change in the self-energy, and the nature of the momentum space Hamiltonian.
+To calculate the self energy we fo Hartee-Fock to get the shift in the kinetic energy.
 In the real space one can get a diagonal piece from the above equation by using the Fermionic anticommutation relations.
 \begin{eqnarray}
-H_{eff}^{off,(2)} |_{diag} &=& -(16t^2/3) [ (S_1^z)^2+ (S_2^z)^2 ]   
-\end{eqnarray}
-We can find the corresponding momentum space Hamiltonian by doing the fouries transforamtion to the Hamiltonian  $H_{eff}^{off,(2)} |_{diag} $ as.
+H_{eff}^{off,(2)} |_{diag} &=& -\frac{16t^2}{3} [ (S_1^z)^2+ (S_2^z)^2 ]  \nonumber\\
+\end{eqnarray}
+We can find the corresponding momentum space Hamiltonian by doing the fouries transforamtion to the Hamiltonian $H_{eff}^{off,(2)} |_{diag} $.
 \begin{eqnarray}
 %&&-\frac{16t^2}{3}\bigg[\bigg(\frac{1}{4N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{2N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow} \bigg) + \bigg(\frac{1}{4N} \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma}-\frac{1}{2N^2} \displaystyle\sum_{k_1,k_2} \tilde{n}_{k_1\uparrow} \tilde{n}_{k_2\downarrow} \bigg) \bigg] \nonumber\\
-H_{eff}^{off,(2)} |_{diag}&=& -\frac{4t^2}{3} \frac{1}{N} \bigg[ \displaystyle\sum_{k,\sigma} n_{k\sigma}(1-\frac{1}{N} \displaystyle\sum_{k_2}  n_{k_2,-\sigma}  ) \nonumber\\
-&&+ \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma} ( 1-\frac{1}{N} \displaystyle\sum_{ k_2} \tilde{n}_{k_2,-\sigma}  ) \bigg]  
-\end{eqnarray}
-The above relation leads to the correction to the kinetic energy, which is
+H_{eff}^{off,(2)} |_{diag}&=& -\frac{4t^2}{3} \frac{1}{N} \bigg[ \displaystyle\sum_{k,\sigma} n_{k\sigma}\bigg(1-\frac{1}{N} \displaystyle\sum_{k_2}  n_{k_2,-\sigma} \bigg) \nonumber\\
+&&+ \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma}\bigg( 1-\frac{1}{N} \displaystyle\sum_{ k_2} \tilde{n}_{k_2,-\sigma} \bigg) \bigg] \nonumber\\
+\end{eqnarray}
+in momentum space we can do again the Hartee-Fock to measure the self-energy
 \begin{eqnarray}
@@
 \bar{\epsilon}
-_k-\epsilon_k=\Sigma_k 
-% -\frac{4t^2}{3N} \bigg(1-\frac{1}{N} \displaystyle\sum_{k_2}  \langle n_{k_2,-\sigma} \rangle \bigg) \nonumber\\
+_k-\epsilon_k=\Sigma_k &=& -\frac{4t^2}{3N} \bigg(1-\frac{1}{N} \displaystyle\sum_{k_2}  \langle n_{k_2,-\sigma} \rangle \bigg) \nonumber\\
 &&= -\frac{4t^2}{3N^2}\bigg(1-\frac{N}{e^{(\epsilon_k-\mu)/k_BT}+1}\bigg)
@@
 \end{eqnarray}
-Using the self-energy we calculate the impurity speciftic heat defined as $C_{imp}=C(J^*)-C(0)$ which is defined as
+Using the self-energy we calculate the impurity speciftic heat defined as $C_{imp}=C(J^*)-C(0)$.
 \begin{eqnarray}
@@
 \end{eqnarray}
-%\subsubsection{Exact diagonalization}
-Apart from this impurity specific heat one can calculate the magnetic susceptibilty.
-For that we do the exact diagonalizaton of the NFL Hamiltonian eq.\eqref{eq:hamiltonian_NFL} and get the entire eigenspectrum.
-On all those different state we can calculate teh expectation value of the magnetization squared $\langle (S^z)^2 \rangle$.
-Using these expectation values we can calculate the suseptibility by using the formula
+
+\subsubsection{Exact diagonalization}
+Here we do the exact diagonalization the NFL Hamiltonian eq.\eqref{eq:hamiltonian_NFL} and find the eigenspectrum.
+Using this eigen spectrum  we computer various quantitites like $\chi$.
+We can compute other quantities from this exact diagonalization.
 \begin{eqnarray}
@@
 \includegraphics[scale=0.36]{plt/NFL_Chi_log_0p1}
-\caption{Suseptibility}
-\label{fig:NFL_susecptibility}
-\end{figure}
-The above figure shows that at low temperture the suseptibility follows the logarithmic behavior.
+\end{figure}
+The above figure shows that at low temperture
 \begin{eqnarray}
@@
 \end{eqnarray}
-
-\noindent As expected both the $C_{imp}/T$ and $\chi$ follows the logarithmic behavior which is known in the literature for the two channel Kondo problem.
-From the slopes we can calculate the Wilson ratio $C_{imp}/T\chi$, we find that in our case where we have taken upto two nearest neighbors to each zeroth sides of two channels the Wilson ratio is $\approx 8.3$ which is greater than the actual value.
-For a smaller system with only one nearest neighbor to the zeroth site of both the channels we find the Wilson number if even higher shows that in a larger system the Wilson ratio approaches a smaller value.
+This matches with the already known result of the literature.
+The ratio $\frac{\chi(T)}{C_{imp}/T} \sim 8.3$ greater than the Wilson ration.
+One can check this quantity for larger system size and at lower temperature for an better agreement.
+
+\subsubsection{Momentum space structure of the NFL}
 Direct fourier transformation on the $H^{(2)}_{off}$ leads to the LEH in momentum space showing higher order scattering involving electronic degree of freedoms.
-For simplicility we only focus on the diagonal piece which is $H_k$ given as
-\begin{eqnarray}
-H_k&=&-\frac{4t^2}{3 N^4} \displaystyle\sum_{\substack{k_1,k_2\in (1),\\ k_3,k_4\in (2)\\ \sigma,\sigma'}} n_{k_1,\sigma} (1-n_{k_2,-\sigma})  \tilde{n}_{k_3,\sigma'} (1-\tilde{n}_{k_4,-\sigma'}) ~,~~~~\nonumber
-\end{eqnarray}
-where (1) and (2) represnts the sets of momentum space points in two channels respectively.
-The local NFL has a fourth order contribution to the diagonal momentum space density-density interaction, this is a multiplication of MFL terms of two channels.
-There are lower order contributions also as shown in the above sections.
-
 %\begin{eqnarray}
@@
 %\end{eqnarray}
-%The Fourier transformation of the electronic creation operator gives
+The Fourier transformation of the electronic creation operator gives
 %\begin{eqnarray}
@@
 
-%
-%Thus one gets,
-%\begin{eqnarray}
-%(S_1^z)^2 \bigg|_{diag} &=& \frac{1}{4} (n_{1\uparrow}-n_{1\downarrow})^2\bigg|_{diag}=(n_{1\uparrow}+n_{1\downarrow}-2n_{1\uparrow}n_{1\downarrow})/4 \bigg|_{diag}\nonumber\\
-%%&=& \frac{1}{4N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{2N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow} \nonumber\\
-%&=& \frac{1}{4N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{4N^2} \displaystyle\sum_{k_1,k_2,\sigma} n_{k_1,\sigma} n_{k_2,-\sigma}
-%\end{eqnarray}
-%We know that the diagoanl peice of the following terms is given as
-%%\begin{eqnarray}
-%%c_{r,\uparrow}^{\dagger} c_{r,\downarrow}  c_{r',\uparrow} c^{\dagger}_{r',\downarrow} &=& \frac{1}{N^2} \displaystyle\sum_{\substack{k_1,k_2\\k_3,k_4}} e^{-i(k_1-k_2)r} e^{-i(k_3-k_4)r} c_{k_1,\uparrow}^{\dagger} c_{k_2,\downarrow} c_{k_4,\uparrow}c_{k_3,\downarrow}^{\dagger}  \bigg|_{diag} \nonumber\\
-%%%&\Downarrow & \nonumber\\
-%%%&& \frac{1}{N^2} \displaystyle\sum_{\substack{k_1,k_2}} e^{-i(k_1-k_2)r} e^{-i(k_2-k_1)r} c_{k_1,\uparrow}^{\dagger} c_{k_2,\downarrow} c_{k_1,\uparrow}c_{k_2,\downarrow}^{\dagger}  \bigg|_{diag} \nonumber\\
-%%&=& -\frac{1}{N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow}(1-n_{k_2\downarrow})
-%%\end{eqnarray}
-%
-%Thus the diagonal piece coming from the term,
-%\begin{eqnarray}
-%&& c_{2\uparrow}^{\dagger}c_{2\downarrow} \bigg(  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger} \bigg)\Rightarrow \frac{1}{N} \displaystyle\sum_{k,k'} e^{-i(k-k')r} c_{k,\sigma}^{\dagger} c_{k',-\sigma}  \nonumber
-%\end{eqnarray}
-
-%\begin{widetext}
-%\begin{eqnarray}
-%H_{eff}^{off,(2)} \bigg|_{diag} &=& -\frac{8t^2}{3} \bigg[ \frac{1}{4N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{2N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow} \bigg] \times \bigg[\frac{1}{N^2} \displaystyle\sum_{k_1,k_2} \tilde{n}_{k_1\uparrow}(1-\tilde{n}_{k_2\downarrow}) + (\uparrow \rightarrow \downarrow)\bigg] \times 2 \nonumber\\
-%%&=& -\frac{2t^2}{3} \bigg[ \frac{1}{N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{2}{N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow} \bigg] \times \bigg[\frac{1}{N} \displaystyle\sum_{k_1,\sigma} \tilde{n}_{k_1,\sigma} -  \frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} \tilde{n}_{k_1\sigma}\tilde{n}_{k_2,-\sigma}\bigg]\times 2 \nonumber\\
-%&=& -\frac{4t^2}{3} \bigg[ \frac{1}{N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} n_{k_1,\sigma} n_{k_2,-\sigma} \bigg] \times \bigg[\frac{1}{N} \displaystyle\sum_{k_1,\sigma} \tilde{n}_{k_1,\sigma} -  \frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} \tilde{n}_{k_1\sigma}\tilde{n}_{k_2,-\sigma}\bigg]~,~~~~
-%\end{eqnarray}
-%%
-%%
-%%\begin{eqnarray}
-%%H_{eff}^{off,(2)} \bigg|_{diag} &=&  -\frac{4t^2}{3} \bigg[ \frac{1}{N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{N^2} \displaystyle\sum_{k_1,k_2} n_{k_1,\sigma} n_{k_2,-\sigma} \bigg] \times \bigg[\frac{1}{N} \displaystyle\sum_{k_1,\sigma} \tilde{n}_{k_1,\sigma} -  \frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} \tilde{n}_{k_1\sigma}\tilde{n}_{k_2,-\sigma}\bigg] \nonumber\\
-%%\label{eq:off-ham-110}
-%%\end{eqnarray}
-%
-%
-%\end{widetext}
-
-Similar to the two channel case, our calculation of the diagonal LEH for the three channel case shown the absence of local Fermi liquid term.
+Thus one gets,
+\begin{eqnarray}
+(S_1^z)^2 \bigg|_{diag} &=& \frac{1}{4} (n_{1\uparrow}-n_{1\downarrow})^2\bigg|_{diag}=(n_{1\uparrow}+n_{1\downarrow}-2n_{1\uparrow}n_{1\downarrow})/4 \bigg|_{diag}\nonumber\\
+%&=& \frac{1}{4N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{2N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow} \nonumber\\
+&=& \frac{1}{4N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{4N^2} \displaystyle\sum_{k_1,k_2,\sigma} n_{k_1,\sigma} n_{k_2,-\sigma}
+\end{eqnarray}
+We know that the diagoanl peice of the following terms is given as
+%\begin{eqnarray}
+%c_{r,\uparrow}^{\dagger} c_{r,\downarrow}  c_{r',\uparrow} c^{\dagger}_{r',\downarrow} &=& \frac{1}{N^2} \displaystyle\sum_{\substack{k_1,k_2\\k_3,k_4}} e^{-i(k_1-k_2)r} e^{-i(k_3-k_4)r} c_{k_1,\uparrow}^{\dagger} c_{k_2,\downarrow} c_{k_4,\uparrow}c_{k_3,\downarrow}^{\dagger}  \bigg|_{diag} \nonumber\\
+%%&\Downarrow & \nonumber\\
+%%&& \frac{1}{N^2} \displaystyle\sum_{\substack{k_1,k_2}} e^{-i(k_1-k_2)r} e^{-i(k_2-k_1)r} c_{k_1,\uparrow}^{\dagger} c_{k_2,\downarrow} c_{k_1,\uparrow}c_{k_2,\downarrow}^{\dagger}  \bigg|_{diag} \nonumber\\
+%&=& -\frac{1}{N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow}(1-n_{k_2\downarrow})
+%\end{eqnarray}
+
+Thus the diagonal piece coming from the term,
+\begin{eqnarray}
+&& c_{2\uparrow}^{\dagger}c_{2\downarrow} \bigg(  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger} \bigg)\Rightarrow \frac{1}{N} \displaystyle\sum_{k,k'} e^{-i(k-k')r} c_{k,\sigma}^{\dagger} c_{k',-\sigma}  \nonumber
+\end{eqnarray}
+\begin{widetext}
+Thus we get the diagonal correction of effective Hamiltonian in the momoentum spcae,
+\begin{eqnarray}
+H_{eff}^{off,(2)} \bigg|_{diag} &=& -\frac{8t^2}{3} \bigg[ \frac{1}{4N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{2N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow} \bigg] \times \bigg[\frac{1}{N^2} \displaystyle\sum_{k_1,k_2} \tilde{n}_{k_1\uparrow}(1-\tilde{n}_{k_2\downarrow}) + (\uparrow \rightarrow \downarrow)\bigg] \times 2 \nonumber\\
+%&=& -\frac{2t^2}{3} \bigg[ \frac{1}{N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{2}{N^2} \displaystyle\sum_{k_1,k_2} n_{k_1\uparrow} n_{k_2\downarrow} \bigg] \times \bigg[\frac{1}{N} \displaystyle\sum_{k_1,\sigma} \tilde{n}_{k_1,\sigma} -  \frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} \tilde{n}_{k_1\sigma}\tilde{n}_{k_2,-\sigma}\bigg]\times 2 \nonumber\\
+&=& -\frac{4t^2}{3} \bigg[ \frac{1}{N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} n_{k_1,\sigma} n_{k_2,-\sigma} \bigg] \times \bigg[\frac{1}{N} \displaystyle\sum_{k_1,\sigma} \tilde{n}_{k_1,\sigma} -  \frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} \tilde{n}_{k_1\sigma}\tilde{n}_{k_2,-\sigma}\bigg]~,~~~~
+\end{eqnarray}
+%
+%
+%\begin{eqnarray}
+%H_{eff}^{off,(2)} \bigg|_{diag} &=&  -\frac{4t^2}{3} \bigg[ \frac{1}{N} \displaystyle\sum_{k,\sigma} n_{k\sigma}-\frac{1}{N^2} \displaystyle\sum_{k_1,k_2} n_{k_1,\sigma} n_{k_2,-\sigma} \bigg] \times \bigg[\frac{1}{N} \displaystyle\sum_{k_1,\sigma} \tilde{n}_{k_1,\sigma} -  \frac{1}{N^2} \displaystyle\sum_{k_1,k_2,\sigma} \tilde{n}_{k_1\sigma}\tilde{n}_{k_2,-\sigma}\bigg] \nonumber\\
+%\label{eq:off-ham-110}
+%\end{eqnarray}
+
+\end{widetext}
+
+\noindent Where $n_{k,\sigma}$ and $\tilde{n}_{k,\sigma}$ are the occupation of the states $k,\sigma$ corresponding to two different channels.
+One can define the charge density of $i^{th}$ channel with the spin-$\sigma$ as
+\begin{eqnarray}
+q_{i,\sigma}=\frac{Q_{i,\sigma}}{N}=\frac{1}{N}  \displaystyle\sum_{k} n_{k,\sigma}
+\end{eqnarray}
+Thus one can re-write the abeove equation as,
+\begin{eqnarray}
+H_{eff}^{off,(2)} \bigg|_{diag} &=& -\frac{4t^2}{3} \prod_{i=\{1,2\}} \bigg[q_{i,\uparrow}+q_{i,\downarrow}-q_{i,\uparrow}q_{i,\downarrow}\bigg] \nonumber\\
+\end{eqnarray}
+This shows the inter-channel charge coupling present in the excitation spectrum.
+
+\subsection{Third order}
+
+\noindent Thus the off-diagonal part of the effective low energy Hamiltonian in the 2nd order is
+\begin{eqnarray}
+&&H_{eff, off}^{(2)} 
+= \frac{J^2}{\alpha}\bigg[ c_{1\uparrow}c_{1\downarrow}^{\dagger} \bigg(-\alpha\beta \bigg\{\Sigma_{3,2} + c_{3\uparrow}^{\dagger} c_{3\downarrow} c_{2\uparrow} c_{2\downarrow}^{\dagger} \bigg\}-\alpha\gamma \Omega_{3,2}\bigg) \nonumber\\
+&&~~~~+c_{2\uparrow}c_{2\downarrow}^{\dagger} \bigg(-\alpha\beta \bigg\{\Sigma_{1,3} + c_{1\uparrow}^{\dagger} c_{1\downarrow} c_{3\uparrow} c_{3\downarrow}^{\dagger} \bigg\}-\alpha\gamma \Omega_{1,3}\bigg) \nonumber\\
+&&~~+c_{3\uparrow}c_{3\downarrow}^{\dagger} \bigg(-\alpha\beta \bigg\{\Sigma_{2,1} + c_{2\uparrow}^{\dagger} c_{2\downarrow} c_{1\uparrow} c_{1\downarrow}^{\dagger} \bigg\}-\alpha\gamma \Omega_{2,1}\bigg) + \textrm{h.c.} \bigg]
+\nonumber\\
+&&~~~~~~~~~~~~~~~\otimes \bigg[ c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.}\bigg] \nonumber
+\end{eqnarray} 
+ \begin{eqnarray}
+\Sigma_{i,j} &=&-8S_i^zS_j^z  [  (C^z_i-C^z_j  )^2  + (S_i^z-S_j^z  )^2  ] \\
+\Omega_{i,j} &=& 4S_i^z S_j^z (C_i^z+C_i^z)(C_j^z+C_j^z)
+\end{eqnarray}
+
+\noindent Now we are interested calculating the diagonal part of the effective Hamiltonian.
 In this case we get non-zero contribution from all the three ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$.
@@
 The contribution associater to different ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$ is given respectively as $- \frac{2.4 J^2}{\alpha} \hat{I} + \hat{\mathcal{F}},- \frac{2.4 J^2}{\alpha} \hat{I} ,- \frac{2.4 J^2}{\alpha} \hat{I} - \hat{\mathcal{F} }$,
-\noindent where $\hat{\mathcal{F}}$ is a function of diagonal number oprators of sites nearest neighbor to the zeroth site of each channels.
-We also get offdiagonal terms in the LEH which is shown in the Appendix.\ref{ap:three-channel}.
+\noindent where $\hat{\mathcal{F}}$ is a function of diagonal number oprators of the nearest-neighbor site degree of freedom $l_1,l_2,l_3$ etc.
 
 \section{Channel Anisotropy and Berry phase}
-\noindent So far we have talked the stargraph problem where all the outer spin is coupled with the central impurity spin with Heisenberg cuopling of equal strength.
-This model has a special symmetry where any rearrangement of the outer spins keeps the stargraph Hamiltonian invariant.
-Here we wish to break this symmetry of this Hamiltonian by choosing the individual coupling strength of the outer spin with the central impurity spin different.
-We start with the general coupling Hamiltonian written as
-\begin{eqnarray}
-H (\vec{\Lambda}) &=& \sum_{i=1}^{K} \lambda_i\vec{S}_d.\vec{S}_i
-\end{eqnarray}
-where $\lambda \equiv (\lambda_1,\cdots,\lambda_K)$. So far we have considered the case where $\lambda_i=\alpha,~\forall i$.
-
-\noindent Here we start with the multi-channel zero mode model, any put anisotropy in the counping $\alpha$.
+
+noindent Here we start with the multi-channel zero mode model, any put anisotropy in the counping $\alpha$.
 Let's start with a simpe possibility where there are two coupling $\alpha_1$ and $\alpha_2$, where both the $\alpha_1,\alpha_2$ are positive and negative.
@@
 
-%
-%\subsection{Berry phase}
-%
-%We start with the general multi-channel problem where the coupling strength with the central impurity spin of the $i^{th}$ channel is $\alpha_i$.
+\subsection{Berry phase}
+
+We start with the general multi-channel problem where the coupling strength with the central impurity spin of the $i^{th}$ channel is $\alpha_i$.
 Here our goal is to use the robustness of the ground state degeneracy of the star-graph model to build the gaue theoretic structure.
 We define the hamiltonian of star-graph as
-%\begin{eqnarray}
-%H_{st}(\vec{\alpha}) &=& \displaystyle\sum_{i=1}^{K} \alpha_i \vec{S}_d.\vec{S}_i
-%\end{eqnarray}
-%We define the $K$-dimensional soupling space where one possible sonfiguration is denoted by the vector $\vec{\alpha}=\mathcal{N}(\alpha_1,\alpha_2,\cdots,\alpha_K)$, where $\mathcal{N}$ is the normalization factor, where $\alpha_i\neq 0$ and $\alpha_i\neq \infty $, $\forall i\in[K]$.
+\begin{eqnarray}
+H_{st}(\vec{\alpha}) &=& \displaystyle\sum_{i=1}^{K} \alpha_i \vec{S}_d.\vec{S}_i
+\end{eqnarray}
+We define the $K$-dimensional soupling space where one possible sonfiguration is denoted by the vector $\vec{\alpha}=\mathcal{N}(\alpha_1,\alpha_2,\cdots,\alpha_K)$, where $\mathcal{N}$ is the normalization factor, where $\alpha_i\neq 0$ and $\alpha_i\neq \infty $, $\forall i\in[K]$.
 The Schrodinger equation for the Hamiltonian reads as
-%\begin{eqnarray}
-%H_{st}(\vec{\alpha}) \Psi_{m} (\vec{\alpha}) = E_{m} (\vec{\alpha}) \Psi_{m} (\vec{\alpha})
-%\end{eqnarray}
-%Here, we are only interested in the ground state manifold, where the energy of the state is $E_{g}$.
+\begin{eqnarray}
+H_{st}(\vec{\alpha}) \Psi_{m} (\vec{\alpha}) = E_{m} (\vec{\alpha}) \Psi_{m} (\vec{\alpha})
+\end{eqnarray}
+Here, we are only interested in the ground state manifold, where the energy of the state is $E_{g}$.
 Due to the degeneracy ($K$-fold) there are $K$ states in that manifold with the same energy labeled by say $k$.
 Thus the equation for the ground state manifold reads
-%\begin{eqnarray}
-%H_{st}(\vec{\alpha}) \Psi^{k}_{g} (\vec{\alpha}) = E_{g} (\vec{\alpha}) \Psi^{k}_{g} (\vec{\alpha})
-%\end{eqnarray}
-%One can do a simple transformation to make the ground state energy zero. Thus
-%\begin{eqnarray}
-%H_{st}(\vec{\alpha}) \Psi^{k}_{g} (\vec{\alpha}) &=&  0 \nonumber\\
-%i\hbar \frac{\partial \Psi(\vec{\alpha(t)}) }{\partial t} &=& H_{st}(\vec{\alpha(t)}) \Psi(\vec{\alpha(t)}) =0
-%\label{eq:hamiltonian_eq}
-%\end{eqnarray}
-%As the ground state is degenerate one can take any linera combinations of the states to create arbitrary basis state (orthogonal and normalized).
+\begin{eqnarray}
+H_{st}(\vec{\alpha}) \Psi^{k}_{g} (\vec{\alpha}) = E_{g} (\vec{\alpha}) \Psi^{k}_{g} (\vec{\alpha})
+\end{eqnarray}
+One can do a simple transformation to make the ground state energy zero. Thus
+\begin{eqnarray}
+H_{st}(\vec{\alpha}) \Psi^{k}_{g} (\vec{\alpha}) &=&  0 \nonumber\\
+i\hbar \frac{\partial \Psi(\vec{\alpha(t)}) }{\partial t} &=& H_{st}(\vec{\alpha(t)}) \Psi(\vec{\alpha(t)}) =0
+\label{eq:hamiltonian_eq}
+\end{eqnarray}
+As the ground state is degenerate one can take any linera combinations of the states to create arbitrary basis state (orthogonal and normalized).
 Let's say $\psi_k(\vec{\alpha}(t))$ represents the arbitrary basis state, which should  be smooth in $t$ locally and follow the Schrodinger equation,
-%\begin{eqnarray}
-%H_{st}(\vec{\alpha}(t)) \psi_k(\vec{\alpha}(t)) &=&  0 
-%\end{eqnarray}
-%We here try to find the solution of the Eq.\eqref{eq:hamiltonian_eq}, we start with the trial solution 
-%\begin{eqnarray}
-%\eta_a(t) &=& U_{ab}(t) \psi_b(t)
-%\end{eqnarray}
-%
-%\textbf{Finish this section.}
+\begin{eqnarray}
+H_{st}(\vec{\alpha}(t)) \psi_k(\vec{\alpha}(t)) &=&  0 
+\end{eqnarray}
+We here try to find the solution of the Eq.\eqref{eq:hamiltonian_eq}, we start with the trial solution 
+\begin{eqnarray}
+\eta_a(t) &=& U_{ab}(t) \psi_b(t)
+\end{eqnarray}
+
+\textbf{Finish this section.}
 
@@
 Let's discuss these two cases seperately.
-%\subsubsection{$K=odd$} 
+\subsubsection{$K=odd$} 
 In the case where the number of channels $K$ is odd, we get $[\mathbb{Z},\mathbb{X}]=0$.
@@
 
-\begin{eqnarray}
-\beta_{\uparrow} (\alpha,\omega_{\uparrow})&=& \frac{\alpha^2 \Gamma_{\uparrow}}{2} \nonumber\\
-\Gamma_{\uparrow}&=& \frac{1}{\omega_{\uparrow}-\alpha(S_d^z-1)}
-\end{eqnarray}
-
 Thus we get the effective Hamiltonian is
@@
 H_{eff} &=& \frac{\alpha^2 \Gamma_{\uparrow}}{2} (S^2-S^{z2})(\tau^2_{d}-\tau^z_d)  \nonumber\\
-&=& \beta_{\uparrow}(\alpha,\omega_{\uparrow})(S^2-S^{z2})(\tau^2_{d}-\tau^z_d)\\
-%~,~~~\frac{\alpha^2 \Gamma_{\uparrow}}{2} =\beta_{\uparrow}(\alpha,\omega_{\uparrow}) \nonumber\\
-&=& \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} (S^2-S^{z2})  \nonumber\\
-&& =\frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)   
+&=& \beta_{\uparrow}(\alpha,\omega_{\uparrow})(S^2-S^{z2})(\tau^2_{d}-\tau^z_d)~,~~~\frac{\alpha^2 \Gamma_{\uparrow}}{2} =\beta_{\uparrow}(\alpha,\omega_{\uparrow}) \nonumber\\
+&=& \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} (S^2-S^{z2})   =\frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)   
 \end{eqnarray}
@@
 \begin{eqnarray}
-&&H_{eff}(\omega,\alpha)  \nonumber\\
-&=& \frac{ \beta_{\uparrow}(\alpha,\omega_{\uparrow}) }{4}    \displaystyle\sum_{i\neq j}\displaystyle\sum_{\substack{ \alpha_i,\beta_i\in \{\uparrow,\downarrow\}\\ \alpha_j,\beta_j\in \{\uparrow,\downarrow\}}}\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)}    c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)}\nonumber\\
-&&~~~~ ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ +\textrm{h.c.}   
+H_{eff}(\omega,\alpha) &=& \frac{ \beta_{\uparrow}(\alpha,\omega_{\uparrow}) }{4}    \displaystyle\sum_{i\neq j}\displaystyle\sum_{\substack{ \alpha_i,\beta_i\in \{\uparrow,\downarrow\}\\ \alpha_j,\beta_j\in \{\uparrow,\downarrow\}}}\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)}    c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)}\nonumber\\
+&& ~~ +\textrm{h.c.}   
 \label{eq:all-to-all_1}
@@
 \centering
-\includegraphics[scale=0.68]{plt/stargraph-to-alltoall}
+\includegraphics[scale=0.8]{plt/stargraph-to-alltoall}
 \caption{This figure shows the comparison and mapping between the stargraph degenerate ground states and the states of the quantum fluctuation resolved all to all model.}
@@
 The action of the twist operator on the $S^x$ is determined in the follwoing calculation
-\begin{eqnarray}
-\hat{O}_{\mu} S^x \hat{O}^{\dagger}_{\mu} &=& \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} ) ~~S^x ~~ \exp({-i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} )= e^{X} S^x e^{-X} \nonumber\\
-&=& S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots  
-\end{eqnarray}
-For simplicity of thte calculation we define $i\frac{2\pi}{K}=\Omega$, thus $X=\Omega\sum_j jS^z_j$.
+%\begin{eqnarray}
+%\hat{O}_{\mu} S^x \hat{O}^{\dagger}_{\mu} &=& \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} ) ~~S^x ~~ \exp({-i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} )= e^{X} S^x e^{-X} \nonumber\\
+%&=& S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots  
+%\end{eqnarray}
+%For simplicity of thte calculation we define $i\frac{2\pi}{K}=\Omega$, thus $X=\Omega\sum_j jS^z_j$.
 %\begin{eqnarray}
@@
 %\end{eqnarray}
-Thus we get
-\begin{eqnarray}
-e^X S^x e^{-X}&=& S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots  \nonumber\\
+%Thus we get
+%\begin{eqnarray}
+%e^X S^x e^{-X}&=& S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots  \nonumber\\
 %&=& \sum_l S_l^x + (i\Omega)\sum_l l S^y_l + \frac{-(i\Omega)^2}{2!}\sum_{l} l^2 S_l^x + \frac{-(i\Omega)^3}{3!} \sum_l l^3 S_l^y+ \cdots \nonumber\\
@@
 %&=& \sum_l \bigg[ S^x_l \cos (il\Omega) +  S_l^y \sin(il\Omega) \bigg] =  \sum_l \bigg[ S^x_l \cos (-\frac{2\pi l}{K}) +  S_l^y \sin(-\frac{2\pi l}{K}) \bigg]  \nonumber\\
-&=& \sum_l ( S^x_l \cos \theta_l -  S_l^y \sin \theta_l ) ~,~~~\theta_l=\frac{2\pi l}{K}
-\end{eqnarray}
-
-\begin{eqnarray}
-e^X S^y e^{-X}&=& S^y+[X,S^y] + \frac{1}{2!}[X,[X,S^y]] +\cdots  \nonumber\\
+%&=& \sum_l ( S^x_l \cos \theta_l -  S_l^y \sin \theta_l ) ~,~~~\theta_l=\frac{2\pi l}{K}
+%\end{eqnarray}
+%
+%\begin{eqnarray}
+%e^X S^y e^{-X}&=& S^y+[X,S^y] + \frac{1}{2!}[X,[X,S^y]] +\cdots  \nonumber\\
 %&=& \sum_l S_l^y - (i\Omega)\sum_l l S^x_l + \frac{-(i\Omega)^2}{2!}\sum_{l} l^2 S_l^y + \frac{(i\Omega)^3}{3!} \sum_l l^3 S_l^x+ \cdots \nonumber\\
 %&=& \sum_l S^y_l \bigg[ 1 -\frac{(il\Omega)^2}{2!} + \cdots \bigg]- \sum_l S^x_l \bigg[ (il\Omega) - \frac{(il\Omega)^3}{3!} +\cdots \bigg] \nonumber\\
-&=& \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)
-\end{eqnarray}
-As already defined, $\theta_l=\frac{2\pi l}{K}=\frac{2\pi (K-n)}{K}$, where $n$ is an integer.
+%&=& \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)
+%\end{eqnarray}
+%As already defined, $\theta_l=\frac{2\pi l}{K}=\frac{2\pi (K-n)}{K}$, where $n$ is an integer.
 We can see that in the large channel limit $\theta_l $ becomes inter multiple of $2\pi$.
 Thus in the large channel limit
-
-%\begin{eqnarray}
-%\hat{\mathcal{O}}_{\mu} S^{\nu} \hat{\mathcal{O}}^{\dagger}_{\mu} &\xRightarrow[]{K \rightarrow \infty } S^{\nu}~,~~\nu=x,y 
-%\end{eqnarray}
-
-%%%%\textbf{\textit{Fix this LaTeX issue (equation)}} ################
+%
+%%\begin{eqnarray}
+%%\hat{\mathcal{O}}_{\mu} S^{\nu} \hat{\mathcal{O}}^{\dagger}_{\mu} &\xRightarrow[]{K \rightarrow \infty } S^{\nu}~,~~\nu=x,y 
+%%\end{eqnarray}
+%
+%\textbf{\textit{Fix this LaTeX issue (equation)}}
 
@@
 
-\appendix
-
-\begin{widetext}
-\section{Three channel case: NFL}
-\label{ap:three-channel}
-\noindent Thus the off-diagonal part of the effective low energy Hamiltonian in the 2nd order is
-\begin{eqnarray}
-&&H_{eff, off}^{(2)} 
-= \frac{J^2}{\alpha}\bigg[ c_{1\uparrow}c_{1\downarrow}^{\dagger} \bigg(-\alpha\beta \bigg\{\Sigma_{3,2} + c_{3\uparrow}^{\dagger} c_{3\downarrow} c_{2\uparrow} c_{2\downarrow}^{\dagger} \bigg\}-\alpha\gamma \Omega_{3,2}\bigg) +c_{2\uparrow}c_{2\downarrow}^{\dagger} \bigg(-\alpha\beta \bigg\{\Sigma_{1,3} + c_{1\uparrow}^{\dagger} c_{1\downarrow} c_{3\uparrow} c_{3\downarrow}^{\dagger} \bigg\}-\alpha\gamma \Omega_{1,3}\bigg) \nonumber\\
-&&~~~~~+c_{3\uparrow}c_{3\downarrow}^{\dagger} \bigg(-\alpha\beta \bigg\{\Sigma_{2,1} + c_{2\uparrow}^{\dagger} c_{2\downarrow} c_{1\uparrow} c_{1\downarrow}^{\dagger} \bigg\}-\alpha\gamma \Omega_{2,1}\bigg) + \textrm{h.c.} \bigg]
- \otimes \bigg[ c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.}\bigg] \nonumber
-\end{eqnarray} 
- \begin{eqnarray}
-\Sigma_{i,j} &=&-8S_i^zS_j^z  [  (C^z_i-C^z_j  )^2  + (S_i^z-S_j^z  )^2  ] \\
-\Omega_{i,j} &=& 4S_i^z S_j^z (C_i^z+C_i^z)(C_j^z+C_j^z)
-\end{eqnarray}
-\end{widetext}
-
 \end{document}

### 2022-04-26 manuscript/mscript_mck_full.tex
made final changes after several months

\documentclass[reprint,prb,superscriptaddress]{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,color,ulem,soul,lipsum}
\usepackage[hidelinks]{hyperref}
\bibliographystyle{apsrev4-1}
\begin{document}

\title{Frustration shapes multi-channel Kondo physics: A star graph perspective}
\author{Siddhartha Patra}
\email{sp14ip022@iiserkol.ac.in }
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\author{Abhirup Mukherjee}
\email{am18ip014@iiserkol.ac.in }
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\author{Anirban Mukherjee}
\email{mukherjee.anirban.anirban@gmail.com }
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\affiliation{Ames Laboratory, Ames, Iowa 50011, USA}
\author{A. Taraphder}
\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
\author{Siddhartha Lal}
\email{slal@iiserkol.ac.in}
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\date{\today}
\begin{abstract}
Our study of the multi-channel Kondo (MCK) model using the recently developed unitary renormalization group (URG) technique shows the importance of ground state degeneracy in explaining various important properties like the breakdown of screening and the presence of local non-Fermi liquids. The impurity susceptibility of the zero-bandwidth intermediate coupling fixed point Hamiltonian shows power-law divergence at low temperature, signaling its critical nature. Despite the absence of inter-channel coupling in the MCK Hamiltonian, the study of mutual information between two channels shows non-zero correlation among them. The presence of non-local twist and translation operators shows the topological nature of the degenerate ground state manifold. Upon disentangling the impurity spin, we find the presence of local Mott-liquid made out of inter-channel quantum scatterings. We derive the low energy effective Hamiltonian (LEH) upon the addition of excitation to the zero-bandwidth RG fixed point Hamiltonian for the two and three-channel cases, both of which show the absence of local Fermi liquid phase due to exact cancellation coming from different degenerate ground states, and the presence of non-Fermi liquids with inter-channel quantum fluctuations. Computation of various thermodynamic quantities like specific heat and susceptibility in the ground state of that non-Fermi liquid shows logarithmic scaling in low temperature, which agrees with the known result in the literature. The presence of local marginal Fermi liquid shows the orthogonality catastrophe in the two-channel Kondo model. Discontinuity in various entanglement measures as we add the excitations on top of the zero-bandwidth model by tuning the real space nearest-neighbor hopping strength reinforces the presence of orthogonality catastrophe. Strong and weak coupling duality also sheds light on the presence of an intermediate coupling fixed point in the MCK problem. The study of channel anisotropy under URG reveals series of quantum phase transitions due to the change in ground state degeneracy.  Our work thus shows a template of studying the zero-bandwidth model followed by the systematic addition of excitations, which can be used to study other impurity problems.

\end{abstract}

\maketitle

%\tableofcontents

\section{Introduction}
%{\color{blue}
Local antiferromagnetic exchange interaction between a spin-\(\frac{1}{2}\) impurity and a metal gives rise to the well-understood phenomenon of Kondo effect~\cite{hewson1993}. Here, the impurity local moment is screened by the conduction electrons at temperatures below a certain scale called the Kondo temperature~\cite{anderson1969exact,anderson1970exact,anderson1970,wilson1975,andreiKondoreview,
tsvelickKondoreview,affleck1993exact,affleck1995conformal}, leading to a spin singlet ground state and local Fermi liquid excitations above that ground state~\cite{nozieres1974fermi,hewsonp}. The screening manifests as an {\color{blue}initial increase at temperatures below the Kondo temperature, followed by a saturation} of the resistivity of the metal~\cite{Kondo,Zhang2013}, and in the saturation of the impurity contribution to the magnetic susceptibility at low temperatures~\cite{wilson1975,andreiKondoreview,tsvelickKondoreview}.
Generalisations of this model are obtained by taking impurities of higher spin~\cite{hewson1993,Noz_blandin_1980,affleck1993exact}, adding interactions between them~\cite{affleck_1992,affleck_ludwig_jones_1992,georges_1999,zarand_chung_2006,
mitchell_logan_2011,mitchell_sela_2012,konig_coleman_2021}, by promoting to a Kondo lattice of impurities~\cite{coleman_1987,millis_lee_1987,auerbach_1986,rice_ueda_1986,stewart_1984} or by considering a correlated metal~\cite{granath_1998}. One can also construct multi-channel Kondo (MCK) models by allowing \(K\) conduction electron channels \( \left(K > 1\right) \) to interact with a spin-\(\frac{1}{2}\) impurity~($S_{d}$)~\cite{Noz_blandin_1980,zawadowski_1980,cox_zawadowski_1998} via a common exchange coupling \(\mathcal{J}\).
Using conformal field theory~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005}, bosonization~\cite{emery_kivelson,clarke_giamarchi_1993,zarand_2000,vondelft_prl_1998,schofield_1997}, numerical renormalization group~\cite{bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991}, Bethe ansatz~\cite{andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002} and other methods~\cite{sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}, it has been shown that for the overscreened systems \(\left(K > 2S_d\right)\), the low energy physics is of the non-Fermi liquid type, displaying anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (ensuring that temperature is taken to zero before the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
This anomalous divergent behaviour is actually a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: it is susceptible to perturbations that introduce channel isotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}. This makes the experimental realisation of such states quite challening.
Nevertheless, several features of the two-channel Kondo model have been reproduced using structural two-level systems~\cite{zawadowski_1980,vladar_1983} interacting with a conduction bath~\cite{cichorek_2005,ralph_buhrman_1992,ralph_ludwig_1994,Iftikhar2015,Zhu2016}.
More recently, it has become possible to tune a two-channel quantum dot system across the quantum phase transition~\cite{Potok2007,Keller2015}, revealing the fractionalisation of the low-energy degrees of freedom~\cite{emery1995,Coleman_tsvelik,mebrahtu_2013}.

The role of ground state degeneracy and quantum-mechanical frustration in the MCK problem has not received sufficient attention, even though they play crucial roles in determining the non-Fermi liquid physics and the quantum criticality of the system. This is, at least partially, due to the lack of an intermediate-coupling effective Hamiltonian that describes the low-energy physics of the MCK (i.e., reveals the nature of the excitations). The term frustration in this context refers to the inability of the impurity spin to bind with the conduction channels and get completely screened by forming a maximally-entangled singlet. The absence of such frustration in the single-channel spin-1/2 Kondo model (and more generally, the exact screening variant of the MCK) means that imperfect screening \((K \neq 2S_d)\) should lead to dramatic differences in the multi-channel models. Indeed, we demonstrate that there exists an orthogonality catastrophe in the imperfectly screened MCK models leading to the non-Fermi liquid behaviour of its low-energy excitations, and that it is directly related to the existence of a degenerate ground state manifold.
The effects of these non-Fermi liquid low energy excitations are expected to show up in measures of many-particle entanglement; the lack of an intermediate coupling Hamiltonian has, however, prevented the study of the renormalisation group (RG) evolution of such measures~\cite{alkurtass_affleck_2016,kim_shim_2021}. 
Our approach enables a comparison of, for instance, the inter-channel mutual information along the RG flow and as functions of the excitation energies, providing insight into the nature of the fixed point theory.
%}

To obtain the RG flow of the MCK model, we have employed the recently developed unitary renormalization group (URG) technique~\cite{anirbanurg1,anirbanurg2}. The method has been applied on several fermionic and spin problems like the single-channel Kondo model~\cite{kondo_urg}, the kagome antiferromagnet~\cite{santanukagome}, the 1D~\cite{1dhubjhep} and 2D Hubbard models~\cite{anirbanmott1,anirbanmott2}, the reduced-BCS model~\cite{siddharthacpi} as well as other generalised models of interacing electrons with and without translation invariance~\cite{anirbanurg2}.
The URG proceeds by decoupling number fluctuations in the high energy electronic states.
Iteratively applying this URG method on the channel-isotropic MCK model leads to a low energy fixed point Hamiltonian at intermediate Kondo coupling. In further analysing the effective Hamiltonian, we focus initially on the zero bandwidth limit of this Hamiltonian (which corresponds to a frustrated quantum spin model on a star graph). We show thereby that several important properties of the MCK problem, such as the ground state degeneracy and breakdown of screening, can be understood from the zero bandwidth problem.
We then proceed to studying the low energy effective Hamiltonian for the non-Fermi liquid excitations lying above the degenerate ground state manifold. This enables the computation of a plethora of quantities, such as various thermodynamic measures (e.g., pecific heat and susceptibility), many-particle entanglement and the self-energy of the propagating degrees of freedom. We also explore various signatures of criticality, and various duality transformations of the MCK Hamiltonian. Finally, we investigate the evolution of ground state degeneracy under RG of the channel anisotropic MCK model.

\subsection*{Summary of Main Results}
We start in section \ref{rg_section} by describing the URG flows for the MCK, the intermediate coupling URG fixed point Hamiltonian and the features of the zero bandwidth (star graph) limit of the effective Hamiltonian.
In section \ref{sec:props_star}, we explore some properties of the zero bandwidth model: namely, the degree of compensation, impurity magnetisation and impurity susceptibility.
The degree of compensation is simply the average correlation between the impurity spin and the conduction channel local spins; it is found to be maximum at exact screening, and decreases for both over- and under-screening.
The magnetisation and susceptibility of the star graph model show critical behaviour in the form a discontinuity and a \(T^{-1}\) divergence respectively.
We also explore the topological properties of the degenerate groundstate manifold of the star graph model using non-local twist and translation operators.
On decoupling the impurity spin from the conduction spin degrees of freedom within the star graph, we obtain an all-to-all Hamiltonian that represents a local Mott liquid phase.
In section ~\ref{sec:excitations}, we obtain the low energy effective Hamiltonian for the low-lying excitations by including a dispersion into the conduction bath.
Notable features of this effective Hamiltonian include (i) the complete absence of local Fermi liquid terms, and (ii) the emergence of local non-Fermi liquid terms.
Both are shown to result from the ground state degeneracy of the underlying star graph model.
The excitations of the two-channel Kondo problem are found to pertain to a local marginal Fermi liquid, signalling an orthogonality catastrophe.

In section \ref{sec:ent_prop}, we study various entanglement signatures (like the von-Neumann entanglement entropy, mutual information, multipartite information, Bures distance) of the low energy fixed-point ground state of the MCK problem, with and without excitaitons. They reveal clear distinctions between the single- and MCK problems in the form of discontinuities.
In \ref{sec:duality}, we discuss two duality transformations that exist for the MCK model - a strong-weak duality and an overscreened-underscreened duality. It is found that the transformations are constrained by the fixed point structure, and they impose relations between the underscreened and overscreened models.
In \ref{anisotropic_rg}, we show the robustness of the ground state degeneracy of the star graph model against the impurity-channel coupling anisotropy, and correlate it with a URG treatment of the channel anisotropic MCK.
The isotropic fixed point is found to be unstable to asymmetry, leading to impurity phase transitions that lead to dramatic changes in the ground state degeneracy.
For the sake of brevity, some supporting evidence as well as the details of certain lengthy calculations are presented in Supplementary Materials.

\section{Fixed point theory of over-screened MCK model}
\label{rg_section}
\subsection{RG flows towards intermediate coupling}
\label{rg_flow_section}
We start with the \(K\)- conduction channel Kondo model Hamiltonian with isotropic couplings \cite{Noz_blandin_1980}:
\begin{gather}
	\label{mc_ham}
	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\beta= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~,~~
\end{gather}
where \(\mathcal{J}\) is the Kondo spin-exchange coupling, \(c_{k\alpha,l}\) is the fermionic field operator at momentum \(k\), spin \(\alpha\) and channel \(l\), \(\epsilon_{k,l}\) represents the dispersion of the \(l^\text{th}\) conduction channel, \(\vec \sigma\) is the vector of Pauli matrices and \(\vec S_d = \frac{1}{2}\vec \sigma_d\) is the impurity spin operator. Here, \(l\) sums over the \(K\) channels of the conduction bath, \(k,k^\prime\) sum over all the momentum states of the bath and \(\alpha,\beta\) sum over the two spin indices of a single electron.

We now perform a renormalisation group analysis of the MCK Hamiltonian using the recently developed URG method \cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome,1dhubjhep}.
The RG proceeds {by applying unitary transformations in order to block-diagonalize the Hamiltonian by removing number fluctuations of the high energy degrees of freedom}.
Given the most energetic electronic state at the \(j^\text{th}\) RG step is \(\ket{j}\) and defined by the energy \(D_{(j)}\), the Hamiltonian will in general not conserve the number of particles in this state: \(\left[H_{(j)}, \hat n_{j}\right] \neq 0\).
The unitary transformation \(U_{(j)}\) will remove this number fluctuation at the next RG step~\cite{anirbanurg1,anirbanurg2}:
\begin{equation}\begin{aligned}
	H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}~, ~\left[H_{(j-1)}, \hat n_{j}\right] =0~.
\end{aligned}\end{equation}
The unitary transformations are given in terms of a fermionic generator \(\eta_{(j)}\)~\cite{anirbanurg1,anirbanurg2}:
\begin{equation}\begin{aligned}
	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ \quad\left\{ \eta_{(j)},\eta_{(j)}^\dagger \right\}_\pm = 1~,
\end{aligned}\end{equation}
where \(\left\{A,B\right\}_\pm = AB \pm BA\). The generator itself is given by the expression~\cite{anirbanurg1,anirbanurg2}
\begin{equation}\begin{aligned}
	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \text{Tr}\left(H_{(j)}c_{j}\right)~.
\end{aligned}\end{equation}
The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms in the Hamiltonian:
\begin{equation}\begin{aligned}
	\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)}~.
\end{aligned}\end{equation}
\(H^i_{(j)}\) is that part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does not commute with at least one \(\hat n_l\) for \(l < j\). The RG flow continues up to energy \(D^*\), where a fixed point is reached from the vanishing of the RG function. 
%from either the numerator or the denominator.

The derivation of the RG equation for the over-screened regime \((2S < K)\) of the spin-\(S\)-impurity \(K\)-channel Kondo problem is shown in detail in the Supplementary Materials (CITE).
On decoupling circular iso-energetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\text{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
\begin{equation}\begin{aligned}
	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{1}{2}\rho {\mathcal{J}}_{(j)} K \right)~, 
\end{aligned}\end{equation}
where \(\mathcal{N}_{(j)}\) is the number of electronic states at the energy shell \(D_{(j)}\). We work in the low quantum fluctuation regime \(\omega_{(j)} < \frac{D_{(j)}}{2}\). There are three fixed points of the RG equation. One arises from the vanishing of the denominator, and was present in the single-channel Kondo RG equation as well \cite{kondo_urg}. As shown there, this fixed-point goes to \({\mathcal{J}}^* = \infty\) as the bare bandwidth of the conduction electrons is made large. The other trivial fixed point is the trivial one at \({\mathcal{J}}^* = 0\). The third fixed point is reached when the numerator vanishes: \({\mathcal{J}}^* = \frac{2}{K \rho}\) \cite{Gan_mchannel_1994,Kogan_2018,Kuramoto1998,Noz_blandin_1980}. Only the intermediate fixed point is found to be stable. This is consistent with results from Bethe ansatz calculations~\cite{Tsvelick_Weigmann_mchannel_1984,andrei_destri_1984,zarand_costi_2002,andrei_jerez_1995,Tsvelick_1985,Tsvelick1984}, CFT calculations~\cite{affleck_1991_overscreen,affleck1993exact,affleck_ludwig_1991}, bosonization treatments~\cite{emery_kivelson,vondelft_prl_1998} and NRG analysis~\cite{pang_cox_1991,mitchell_bulla_2014}.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.45\textwidth]{plt/rg_flow.pdf}
	\caption{The three fixed points of the over-screened RG equation. Only the intermediate one is stable.}
	\label{rg_flow}
\end{figure}

The RG equation reduces to the perturbative form \(\Delta {\mathcal{J}}_{(j)} \simeq \frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{D_{(j)}}\left( 1 - \frac{1}{2}\rho {\mathcal{J}}_{(j)} K \right)\)~\cite{Kogan_2018,Kuramoto1998,Noz_blandin_1980,tripathi2018landau} when one replaces \(\omega_{(j)}\) with the ground state energy \(-\frac{D_{(j)}}{2}\) and assumes \({\mathcal{J}} \ll D_{(j)}\).

\subsection{The star graph as the zero-bandwidth limit of the fixed point Hamiltonian}
\label{sec:star graph}
The fixed point Hamiltonian takes the form
\begin{equation}\begin{aligned}
	H^* = \sum_l\left[ \sum^*_{k}\epsilon_{k,l} \hat n_{k\alpha,l} + {\mathcal{J}}\sum_{kk^\prime}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}~.\right]
\end{aligned}\end{equation}
We have not explicitly written the decoupled degrees of freedom \(D_{(j)} > D^*\) in the Hamiltonian. The \(*\) over the summations indicate that only the momenta inside the window \(D^*\) enter the summation. There is an implied summation over the spin indices \(\alpha,\beta\).

We will first study the zero bandwidth limit of the fixed point Hamiltonian, obtained by compressing the sum over the momentum states to a single state at the Fermi surface. Upon setting the chemical potential equal to the Fermi energy, the kinetic energy part vanishes and the zero bandwidth model becomes a Heisenberg spin-exchange Hamiltonian.
\begin{equation}\begin{aligned}
	\label{star graph}
	H^* = {\mathcal{J}}\sum_l\sum_{kk^\prime}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l} = {\mathcal{J}}\vec{S_d}\cdot\vec S~.
\end{aligned}\end{equation}
At the last step, we defined the total bath local spin operator \(S = \sum_l \vec{S}_l = \frac{1}{2}\sigma_l = \frac{1}{2}\sum_{kk^\prime}^*\sum_{\alpha\beta}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\).
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.30\textwidth]{plt/stargraph.pdf}
	\caption{Zero bandwidth limit of the fixed point Hamiltonian. The central yellow node is the impurity; it is interacting with the \(K\) green outer nodes that represent the local spins of the channels.}
	\label{fig:star graph}
\end{figure}
The star graph commutes with several operators, including the total spin operator \(J^z = S_d^z + S^z\) along \(z\), the total bath local spin operator \(S^2\) and the string operators 
\begin{equation}\begin{aligned}
\pi^{x,y,z} = \sigma_d^{x,y,z} \otimes_{l=1}^K \sigma_l^{x,y,z}~.
\end{aligned}\end{equation}
If we define the global spin operator \(\vec J = \vec S + \vec S_d\), the star graph Hamiltonian can be written as \(\frac{1}{2}\mathcal{J}\left[J^2 - S_d^2 - S^2\right] \).
\begin{itemize}
	\item The ground state is achieved for the maximal value of \(S\), \(S=\frac{K}{2}\), and the corresponding minimal value of \(J\), \(J = |\frac{K}{2} - S_d|\). The {\bf ground state energy} is therefore 
\begin{equation}\begin{aligned}
\label{ground-state-energy}
E_g = \frac{1}{2}\mathcal{J}\left[J(J+1) - S_d(S_d+1) - S(S+1)\right] \\
= \begin{cases}
	-\mathcal{J}S_d\left(\frac{K}{2} + 1\right), & \text{ when } K \geq 2S_d\\
	-\mathcal{J}\frac{K}{2}\left(S_d + 1\right), & \text{ otherwise}
\end{cases}
\end{aligned}\end{equation}
	\item The value of \(J\) corresponds to a multiplicity of \(2J+1 = |K - 2S_d|+1\) in \(J^z\), and since the Hamiltonian does not depend on \(J^z\), these orthogonal states \(\ket{J^z}\) constitute a degeneracy of \(g^{S_d}_K = |K - 2S_d|+1\).
\end{itemize}
The \(\pi^z\) acts on the eigenstates \(\ket{J^z}\) and reveals the odd-even parity of the eigenvalue \(J^z\), and is hence a parity operator. Interestingly, {the string operator \(\pi^z\) is a Wilson loop operator~\cite{fradkin2013field} that wraps around all the nodes of the star graph}:
\begin{equation}\begin{aligned}
	\label{w_loop}
	\pi^z = \exp\left[i \frac{\pi}{2} \left(\sigma_d^z + \sum_{l=1}^K \sigma^z_l - K\right)\right] = e^{i \pi \left(J^z - \frac{1}{2}K\right)}
\end{aligned}\end{equation}
\(\pi^x\) and \(\pi^y\) are 't Hooft operators~\cite{fradkin2013field} and mix states of opposite parity. For example, it can be shown that \(\pi^x \ket{J^z} = -\ket{J^z}\).

There are several reasons for working with the star graph in particular and zero mode Hamiltonians in general.
In the single-channel Kondo model, the star graph is just the two spin Heisenberg, and it reveals the stabilization of the Kondo model ground state, as well as certain thermodynamic properties (e.g., the impurity contribution to the susceptibility)~\cite{varma_yafet_1976,yosida_1966,wilson1975renormalization,moca_zarand_2021,varma_yafet_1976,kondo_urg}.
Similarly in the MCK model, the star graph is able to mimic the nature of the RG flows. At weak coupling \({\mathcal{J}} \to 0^+\), the central spin is weakly coupled to the outer spins and  prone to screening because of the \(S^\pm\) terms in the star graph; at strong coupling \({\mathcal{J}} \to \infty^-\), the outer spin-half objects tightly bind with the central spin-half object to form a single spin object that interacts with the remaining states through an exchange coupling which is RG relevant.
This renders both the terminal fixed points unstable.
The true stable fixed point must then lie somewhere in between, and we recover the schematic phase diagram of fig.~\ref{rg_flow}.

Moreover, the RG flows of the MCK model have been show to {preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}, and the star graph captures this degeneracy in its entirety.
This is important, because it will be shown in a later section that the lowest excitations of the intermediate fixed point is described a non-Fermi liquid phase, and it can be argued that this non-Fermi liquid physics arises solely from the ground state degeneracy of the underlying zero mode Hamiltonian.
As mentioned previously, the ground state degeneracy of the more general star graph with a spin-\({S_d}\) impurity and \(K\) channels is given by \(g^{S_d}_K = |K - 2{S_d}|+1\).
The cases of \(K=2{S_d}\), \(K<2{S_d}\) and \(K>2{S_d}\) correspond to exactly screened, under-screened and over-screened regimes respectively.
The latter two cases correspond to a multiply-degenerate manifold \(g^S_K > 1\), and simultaneously have non-Fermi liquid phases~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact,coleman_pepin_2003,roch_nicolas_costi_2009,schiller_avraham_2008,Durganandini_2011}, while the first regime has a unique ground state \(g^S_K = 1\) and is described by a local Fermi liquid (LFL) phase \cite{wilson1975,nozieres1974fermi,Noz_blandin_1980,andreiKondoreview,tsvelickKondoreview}, thereby substantiating the claim that a degeneracy greater than unity is closely tied to non-Fermi liquid physics.

In the following sections, we will show how the inherent quantum-mechanical frustration of singlet order that is present in the Hamiltonian leads to the non-trivial physics of the fixed points in terms of non-Fermi liquid phase, diverging thermodynamic quantities, quantum criticality as well as emergent gauge theories.
\section{Important Properties of the Star Graph}
\label{sec:props_star}

\subsection{Degree of compensation: a measure of the frustration}
\label{sec:deg_of_comp}
One can quantify the amount of screening of the local moment at the impurity site by defining a degree of compensation \(\kappa\). Such a quantity also measures the inherent singlet frustration in the problem: the higher the degree of compensation, the better the spin can be screened into a singlet and lower is the frustration. It is given by the antiferromagnetic correlation existing between the impurity spin and conduction electron channels: $\Gamma \equiv - \left< \vec{S_d}\cdot \vec{S}\right>$.
The expectation value is calculated in the ground state. Since the inner product is simply the ground state energy of a spin-\(S\) impurity \(K-\)channel MCK model in units of the exchange coupling \(J\), we have \(\Gamma = \frac{1}{2} \left[ l_\text{imp}^2 + l_c^2 - g^S_K\left( g^S_K - 1 \right)\right]\), where \(l_\text{imp}^2 = S_d(S_d+1)\) is the length-squared of the impurity spin. Similarly, \(l_c^2 = \frac{K}{2}\left(\frac{K}{2} + 1\right) \) is the length-squared of the total conduction bath spin. \(g^S_K = |K - S_d| + 1\) is the ground state degeneracy. We will explore the three regimes of screening by defining \(K = K_0 + \delta, S = \frac{K_0}{2} - \delta\). \(\delta=0\) represents the exactly-screened case of \(K = 2S = K_0\). Non-zero \(\delta\) represents either over- or under-screening. In terms of \(K_0\) and \(\delta\), the degree of compensation becomes
\begin{equation}\begin{aligned}
	\label{gamma}
	\Gamma = \frac{1}{4}\left[\left( K_0 + 1 \right) ^2 - \left(|\delta| + 1 \right) ^2\right] 
\end{aligned}\end{equation}
{For a given \(K_0\), the degree of compensation is maximised for exact screening \(\delta=0\), and is reduced for \(\delta \neq 0\). This shows the inability of the system to form a unique singlet ground state and reveals the quantum-mechanical frustration inherent in the zero mode Hamiltonian and therefore in the entire problem.} The degree of compensation is symmetric under the Hamiltonian transformation \(\delta \to -\delta\), and this represents a duality transformation between over-screened and under-screened MCK models. This topic will be discussed in more detail later.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.45\textwidth]{plt/deg_of_comp.pdf}
	\caption{Variation of the degree of compensation as we tune the system from under-screening to over-screening. The maximum spin compensation occurs at exact-screening \(\delta=0\).}
\end{figure}

\subsection{Impurity magnetization and susceptibility}
\label{sec:imp_suscept}
In order to obtain the magnetic susceptibility, We insert a magnetic field that acts only on the impurity and then diagonalize the Hamiltonian.
\begin{align}
	\label{star graph_field_hamiltonian}
	H(h) = {\mathcal{J}^*} \vec{S_d}\cdot\vec{S} + h S_d^z
\end{align}
The Hamiltonian commutes with \(S\), so it is already block-diagonal in terms of the eigenvalues \(M\) of \(S\). \(M\) takes values in the range \(\left[M_\text{min}, M_\text{max}\right]\), where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(\frac{1}{2}\). Defining \(\alpha = \frac{1}{2}\left({\mathcal{J}}m + h\right) + \frac{{\mathcal{J}}}{4}\) and \(x^M_m = M(M+1) - m(m+1)\), the partition function can be written as
\begin{eqnarray}
Z(h) &=&\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\bigg[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \frac{{\mathcal{J}}}{4}}\cosh \beta\sqrt{{\mathcal{J}}^2x^M_m/4 + \alpha^2} \nonumber\\
&&\hspace{2cm}+ 2e^{-\beta {\mathcal{J}}M/2}\cosh \beta h/2\bigg]
\end{eqnarray}
Here, \(\beta = \frac{1}{k_B T}\), \(M\) sums over the eigenvalues of \(S\) while \(m\) sums over \({\mathcal{J}}^z - \frac{1}{2}\) and the additional degeneracy factor \(r^K_M= {}^{K-1}C_{K/2 - M}\) arises from the possibility that there are multiple subspaces defined by \(S=M\). 
To calculate the impurity magnetic susceptibility, we will use the expression
\begin{align}
	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z^{\prime\prime}(h)}{Z(h)} - \left(\frac{Z^{\prime}(h)}{Z(h)}\right)^2 \right] 
\end{align}
where the \(\prime\) indicates derivative with respect to \(h\). For brevity, we define \(\theta_M = \beta {\mathcal{J}} (M+\frac{1}{2})/2\) and \(\Sigma_M = \sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}(m+\frac{1}{2})^2\). At low temperatures, the derivatives are 
\begin{align}
	Z &\to 2 r^K_{M_\text{max}} M_\text{max} e^{\beta \frac{J}{2}(M_\text{max} + 1)}\\
	Z^{\prime \prime} &\to r^K_{M_\text{max}}\left(\frac{\beta }{2(M_\text{max} + \frac{1}{2})}\right)^2 e^{\beta \frac{J}{2}(M_\text{max} + 1)}\Sigma_{M_\text{max}}\\
	\chi &\to \frac{\beta\Sigma_\text{max}}{2M_\text{max}\left(2M_\text{max}+1\right)^2} = \frac{\beta(K-1)}{12(K+1)} \sim \frac{1}{T}
\end{align}

\begin{figure}[!htpb]
\centering
\includegraphics[width=0.49\textwidth]{plt/CentralFieldChiPowerlaw.pdf}
\caption{Variation of impurity susceptibility against temperature. The exactly screened case ($\delta=0$) saturates to a constant value at low temperatures, indicating complete screening. The cases of inexact screening show a divergence of the susceptibility, which means there is a remnant local spin at the impurity. Since the axes are in log scale, the behaviour is $\log T \sim -\log \chi$ which translates to $\chi \sim 1/T$.  }
\label{fig:suseptibility_impurity}
\end{figure}

The \(\chi\) is seen to diverge as \(T^{-1}\) at low temperatures. Such a non-analyticity in a response function is a signature of the critical nature of the Hamiltonian. This is in contrast to the behaviour in the non-critical exactly-screened fixed point where the ground state is unique. There, the susceptibility becomes constant at low temperatures: \(\chi(T\to 0) = \frac{W}{4 T_K}\), \(T_K\) being the single-channel Kondo temperature and \(W\) the Wilson number \cite{wilson1975renormalization,nozieres1974fermi,bullaNRGreview,kondo_urg}. We have checked the case of general spin-\(S\) impurity numerically (fig.~\ref{fig:suseptibility_impurity}), and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit. A similar divergence is also seen in the susceptibility of the outer spins, calculated by inserting a magnetic field purely on the outer spins.

A second non-analyticity arises when we consider the impurity free energy and the magnetization. The thermal free energy is given by
\begin{equation}\begin{aligned}
	F(h) = -\frac{1}{\beta}\ln Z(h) = -\frac{1}{\beta}\ln\sum_{E_n}e^{-\beta E_n}
\end{aligned}\end{equation}
At \(T \to 0\), only the most negative energy \(E_\text{min}\) survives. The minimal energy eigenvalue is
\begin{equation}\begin{aligned}
	E_\text{min} = - \frac{J}{4} - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 + |h|J(K-1)}
\end{aligned}\end{equation}
The first derivative of the free energy with respect to the field gives
\begin{equation}\begin{aligned}
	F^\prime(h\neq 0, T\to 0) =- \frac{2h + J(K-1)\text{sign}(h)}{4\sqrt{\frac{J^2}{4}(K+1)^2 + h^2 + |h|J(K-1)}}
\end{aligned}\end{equation}
There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get the magnetization of the impurity
\begin{equation}\begin{aligned}
	m = F^\prime(h \to 0^\pm, T\to 0) = \mp \frac{1}{2}\frac{(K-1)}{(K+1)}
\end{aligned}\end{equation}
\begin{figure}[!htpb]
	\centering
	\includegraphics[width=0.49\textwidth]{plt/disc_mag_imp_gen.pdf}
	\caption{Behaviour of the impurity magnetization for three values of \(\left(K, 2S\right) = \left(2, 4\right), \left( 3,3 \right), \left(4, 2\right)  \). Only the case of \(K=2S=3 \left(\delta=0\right)\) is analytic near zero. The non-analyticity of the other cases arises because of the frustration brought about by the degeneracy of the star graph ground state.}
	\label{mag_crit}
\end{figure}

The magnetization is therefore discontinuous as \(h\to 0\); it goes to different values depending on the direction in which we take the limit. The non-analyticity for \(K>1\) occurs because there is at least one pair of ground state with non-zero parity \(\pi^z\) and magnetic field is able to flip one ground state into the state of opposite parity. This available space for scattering is simply the frustration that we discussed earlier. Indeed, we have checked numerically (see fig.~\ref{mag_crit}) that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S\) is the deviation from exact screening.

\subsection{Topological properties of ground state manifold}
\label{sec:topo_ground_state}
We now present the non-local twist and translation operators which can be used to explore the degenerate ground state manifold of the star graph model.
First we define two operators $\hat{T}$ and $\hat{O}$, which we will call the translation and twist operators respectively: 
\begin{eqnarray}
\hat{T} &=& e^{i\frac{2\pi}{K} \hat{\Sigma}} ~,~\hat{O} = e^{i\hat{\phi}}~,~~\hat{\Sigma}=[\hat{J}^z-(K-1)/2]
\end{eqnarray}
One can see that the generators of these above operators commute with the Hamiltonian: $[H,J^x]=[H,J^z]=[H,J^z]=0$. In the large \(K\) limit, we can perform a semi-classical approximation. As $J^x$ and $J^y$ both commute with the Hamiltonian $H$, we can write $[H,J^y{(J^{x})}^{-1}]=0$, and any non-singular function of these operators must also commute with the Hamiltonian, which leads us to conclude that
\begin{eqnarray}
\hat{\phi}=\tan^{-1}(\hat{J}^y(\hat{J}^x)^{-1})
\end{eqnarray}
Then we get $[\hat{\phi},\hat{H}]=0$. We can label the ground states by the eigenvalues of the translation operator $\hat{T}$. We can also use the ground states labeled by the eigenvalues of $J^z$ (say $M$). Then the ground states are 
\begin{eqnarray}
|M_1\rangle,|M_2\rangle,|M_2\rangle,\cdots ,|M_K\rangle
\end{eqnarray}
Then the operations of the translation operators on this states are given by
\begin{eqnarray}
\hat{T}|M_i\rangle &=& e^{i\frac{2\pi}{K} [M_i-(K-1)/2]} |M_i\rangle = e^{i2\pi\frac{p_i}{K} } |M_i\rangle~,~p_i\in[K]
\end{eqnarray}
The braiding rule between the twist and the translation operators is
\begin{eqnarray}
\hat{T}\hat{O}\hat{T}^{\dagger}\hat{O}^{\dagger} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},i\hat{\phi}]}=e^{i\frac{2\pi }{K}} \nonumber\\
\hat{T}\hat{O}^m\hat{T}^{\dagger}\hat{O}^{\dagger m} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},im\hat{\phi}]}=e^{i2\pi \frac{m}{K}}
\end{eqnarray}
Next, we shown that the states $\hat{O}^m |M_i\rangle$ are orthogonal to each other and with the state $|M_i\rangle$.
\begin{gather}
\hat{T} \hat{O}^m |M_i\rangle = \hat{O}^m \hat{T} e^{i2\pi \frac{m}{K}} |M_i\rangle =\hat{O}^m e^{i \frac{2\pi(m+p_i)}{K} } |M_i\rangle \\
\hat{T} \bigg(\hat{O}^m |M_i\rangle \bigg) = e^{i \frac{2\pi(m+p_i)}{K} } \bigg( \hat{O}^m |M_i\rangle \bigg)
\end{gather}
Different states $\hat{O}^m |M_i\rangle$ for different $m$ are therefore labeled by different eigenvalues of the translation operations, and are thus orthogonal to each other. As the twist operator $\hat{O}$ commutes with the Hamiltonian, we can write
\begin{eqnarray}
\langle M_i| \hat{O}^{m \dagger}  H \hat{O}^m |M_i\rangle =\langle M_i|  H |M_i\rangle 
\end{eqnarray}
Thus the energy eigenvalues of all the orthogonal states are equal, and they form the $K$ fold degenerate ground state subspace. By the application of the twist operator $\hat{O}$, one can go from one degenerate ground state to another.

\subsection{Local Mott liquid}
\label{sec:loc_mott_liquid}
By applying the unitary renormalization group method on the zero mode star graph Hamiltonian, we decouple the impurity spin from the zero-modes of the $K$ channels: 
\begin{gather}
H = {\mathcal{J}} \vec{S}_d.\displaystyle\sum_i \vec{S}_i ={\mathcal{J}} S_d^zS^z + \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+) \nonumber\\
H_D = {\mathcal{J}} S^z_d S^z~,~~ H_X = \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+)
\end{gather}
In order to remove the quantum fluctuations between the impurity spin and the rest, we perform one step of URG:
\begin{eqnarray}
\Delta H &=& H_X ({\hat{\omega}-H_D})^{-1} H_X 
\end{eqnarray}
The total bath spin operator \(S^z\) is not a good quantum number for the zero mode ground state, and because there is no net $S^z$ field, the ground state manifold has a vanishing expectation value of $S^z$, $\langle S^z \rangle=0$. We use this expectation value to replace the denominator of the above RG equation.
\begin{equation}
\beta_{\uparrow} ({\mathcal{J}},\omega_{\uparrow}) = ({\mathcal{J}}^2 \Gamma_{\uparrow})/2 ~,~~\Gamma_{\uparrow}=(\omega_{\uparrow}-{\mathcal{J}}(S_d^z-1))^{-1}
\end{equation}
The effective Hamiltonian is therefore
\begin{eqnarray}
H_{eff} 
 =\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)   
\end{eqnarray}
In terms of the electronics degree of freedom, it has the form
\begin{eqnarray}
&& \frac{ \beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow}) }{4}   \displaystyle\sum_{\substack{i\neq j \\ \alpha_i,\beta_i\in \{\uparrow,\downarrow\}\\ \alpha_j,\beta_j\in \{\uparrow,\downarrow\}}}\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)}    c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)} +\textrm{h.c.}   \nonumber
\label{eq:all-to-all_1}
\end{eqnarray}
The antiferromagnetic case is for $\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{2} <0$. In this case, the ground state is realised for $S$ being maximum and $S^z$ being minimum. The effective Hamiltonian can be rewritten in this case as
\begin{eqnarray}
H_{eff}   =-|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})| \times(S^+S^{-}+ S^-S^{+}) /4   
\end{eqnarray}
The complete set of commuting observables for this Hamiltonian contains $H,S,S^z$. In the ground state, $S$ is maximum, and  therefore $S=K/2$, and $S^z$ can take $2S+1=K+1$ values. In the largest $S$ sector there are $K+1$ states. Defining the dual operator \(\hat \phi\) with the algbera \([\hat{\phi,S^z}]=i\), we get the twist operator $\hat{Q}=\exp(i\hat{\phi}\Phi/\Phi_0)$. Applying this operator, we get the twisted Hamiltonian 
\begin{eqnarray}
H(\Phi) &=& -\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} S^2   +\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} \bigg(S^{z}-\frac{\Phi}{\Phi_0} \bigg)^2 ~,~~
\label{eq:flux_spectral}
\end{eqnarray}
One can thus explore different $S^z$ ground states via such flux tuning mechanism.

For a $K$ channel star graph problem the ground state is $K$ fold degenerate associated with different $J^z$ values $\{-(K-1)/2,-(K-3)/2,\cdots  ,(K-1)/2 \}$. After removing the quantum fluctuations between the impurity spin and the outer spins, we get an all-to-all model (eq.\eqref{eq:flux_spectral}) as the effective Hamltonian. The eigenstates of this all-to-all Hamiltonian can be labeled by the eigenvalues of $S^z$. There are $K+1$ such states made out of only the outer spins. The total state including the impurity spin can be written as $|J^z\rangle = |S_d^z\rangle \otimes |S^z\rangle$ labeled by $J^z=S_d^z+S^z$. As the all-to-all model has $Z_2$ symmetry in impurity sector, there are $2(K+1)$ total states. For $S_d^z=1/2$, $ \{J^z\}=\{ -(K-1)/2, \cdots, (K-1)/2, (K+1)/2 \}$ and for $S_d^z=-1/2$, $\{J^z\}=\{-(K+1)/2, -(K-1)/2, \cdots,  (K-1)/2  \}$. We can see that in both the cases, all $K$ states of the star graph ground state manifold are present in the spectrum of the all-to-all model, one of them being the ground state. Using the twist operator, we can cycle between the various states.

\section{Local non-Fermi liquid excitations of the 2CK model}
\label{sec:excitations}

\subsection{Effective Hamiltonian}
\label{sec:eff_ham_2ch}

We will now proceed to extract the nature of the low-energy excitations of the two-channel Kondo problem. This will be done by adding real-space hopping to the zero-bandwidth Hamiltonian and treating this hopping as a perturbation above the zero-bandwidth Hamiltonian. The zero-bandwidth Hamiltonian obtained from the URG of the two-channel Kondo problem then acts as the zeroth-level Hamiltonian Here:
\begin{eqnarray}
H^{(2)}&=& {\mathcal{J}} \vec{S}_d.(\vec{S}_1+\vec{S}_2)~~,~~\vec{S}_i =  \frac{1}{2}~ c_{i,\alpha}^{\dagger}~ \vec{\sigma}_{\alpha,\beta}~ c_{i,\beta}~~
\label{eq:channel-2-spin}
\end{eqnarray}
Here, $\vec{S}_i=1,2$ represents the spin degree of freedom present at the origin of the $i^{th}$ channel. This zeroth-level Hamiltonian has two degnerate ground states labeled by $\ket{J^z=\pm 1/2}$ with energy $-\mathcal{J}$ and $6$ excited states~\cite{kunj_slal_1999}.
The perturbation Hamiltonian is the real-space hopping:
\begin{eqnarray}
H_{X} &=& -t \displaystyle\sum_{\substack{<1,l_1> \\ <2,l_2>}} (c^{\dagger}_{1,\sigma}c_{l_1,\sigma}+c^{\dagger}_{2,\sigma}c_{l_2,\sigma}+ ~\textrm{h.c.})~,
\end{eqnarray}
and it will be accounted for using degenerate perturbation theory. Here $l_i$ represents the nearest site to the origin of the $i^{th}$ channel.

Since the perturbation is a single-particle hopping that transfers electrons, we need to rewrite the spin operators in the zeroth Hamiltonian in terms of fermionic operators:
\begin{eqnarray}
\mathcal{H} &=& \frac{{\mathcal{J}}\hbar}{2}~ \vec{S}_d. \displaystyle\sum_{i=\{1,2\}} \displaystyle\sum_{\alpha,\beta\in\{\uparrow,\downarrow\}}c_{i\alpha}^{\dagger} \vec{\sigma}_{\alpha\beta} c_{i\beta} + H_X
\label{eq:excitation_hamiltonian}
\end{eqnarray}
In this expanded basis, there are $32$ degenerate ground states:
\begin{equation}
\label{gstate-set}
\left\{ \ket{\alpha_i} \right\} = \left\{ \ket{J^z}\otimes\ket{n_{l_1,\uparrow},n_{l_1,\downarrow},n_{l_2,\uparrow},n_{l_2,\downarrow}} \right\}
\end{equation}
The \(32-\)fold degeneracy arises from the two-fold degeneracy of \(J^z\) (\(J^z = \pm 1/2\)) multiplying the \(16-\)fold degeneracy of the rest of the sites \(n_{l_i,\sigma}\) (each of the four \(n_{l_i,\sigma}\) can be 0 or 1, leading to a \(2^4\)-fold degeneracy).

The first and the second order corrections to the low energy effective Hamiltonian are
\begin{eqnarray}
H^{(1)} &=& \sum_{ij} |\alpha_i\rangle \langle \alpha_i  | V| \alpha_j \rangle \langle \alpha_j |~\nonumber\\
H^{(2)} &=& \sum_{ij} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j |~.
\end{eqnarray}
Here, $|\alpha_i\rangle$ represents the ground states with energy $E_0$ and is the set of states defined in eq.~\ref{gstate-set}, and $\mu_l$ represents the excited states with energy $E_l$. It is easy to see that the diagonal contribution at any odd order is zero - the final state is never equal to the initial state. The off-diagonal part at first order is also zero. At second order we get both diagonal and off-diagonal contribitions to the effective Hamiltonian.

\subsubsection{Diagonal renormalisation}
We first calculate the diagonal renormalisation at second order coming from each of the states \(\ket{\tilde \alpha_0} = \ket{J^z = \frac{1}{2}}\otimes\ket{\psi_\text{rest}}, \ket{\tilde \alpha_1} = \ket{J^z = -\frac{1}{2}}\otimes\ket{\psi_\text{rest}}\), where \(\ket{\psi_\text{rest}}\) refers to the configuration of the remaining sites apart from the two that form the zeroth Hamiltonian. These second order corrections are given by
\begin{equation}
H^{(2)}_\text{diag}\left(\tilde \alpha_0\right)  = \frac{2t^2}{E_0} \hat{I} - \Omega_l, ~ ~ H^{(2)}_\text{diag}\left(\tilde \alpha_1\right) = \frac{2t^2}{E_0} \hat{I} + \Omega_l ~,
\end{equation}
where $S_{l_i}^z=(n_{l_i\uparrow}-n_{l_i\downarrow})/2$ and $\Omega_l=\frac{2t^2}{3E_0} ( S_{l_1}^z + S_{l_2}^z)$.  The total diagonal second-order contribution to the effective Hamiltonian is obtained by adding these two contributions, and the result is a trivial shift: $H^{(2)}_\text{diag} = H^{(2)}_\text{diag}\left(\tilde \alpha_0\right) + H^{(2)}_\text{diag}\left(\tilde \alpha_1\right) = -4t^2 \hat{I}$. The fact there is no non-trivial diagonal renormalisation to the low-energy excitations shows the absence of (local) Fermi liquid terms, and this occurs becasuse of the exact cancellation of the field terms \(\pm \Omega_l\).

\subsubsection{Off-diagonal renormalisation}
The off-diagonal contribution to the second order effective Hamiltonian is 
\begin{eqnarray}
H_{NFL}&=&H^{(2)}_{off} = \sum_{i\neq j} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j | \nonumber\\
&=& -\frac{8t^2}{3} [ (S_1^z)^2 c_{2\uparrow}^{\dagger}c_{2\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) \nonumber\\
&+& (S_2^z)^2 c_{1\uparrow}^{\dagger}c_{1\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) ] + \textrm{h.c.} ~,~~~~
\label{eq:hamiltonian_NFL}
\end{eqnarray}
This effective Hamiltonian is purely of the non-Fermi liquid kind, arising due to the degeneracy of the ground state manifold. Using this low energy effective Hamiltonian we have calculated different thermodynamic quatitites like susceptibility, specific heat and the Wilson ratio. The first two measures show logarithmic behavior at low temperatures, in agreement with known results in the literature. These results are shown in the supplementary material.

Following this method, we have also calculated the effective Hamiltonian for the three channel Kondo model. We again find the absence of all Fermi liquid terms upto $2^{nd}$ order, and the presence of non-Fermi liquid terms in the off-diagonal part of the effective Hamiltonian, and these are also shown in the supplementary material.

\subsection{Local marginal Fermi liquid and orthogonality catastrophe}
\label{sec:MFL}

The real space local low energy Hamiltonian that takes into account the excitations above the ground state is given by eq.~\ref{eq:hamiltonian_NFL} and can be written as
\begin{equation}\begin{aligned}
	\label{nfl_terms}
	V_\text{eff} = \frac{2t^2}{{\mathcal{J}^*}}\left[\left(\sigma^z_{0,1}\right)^2 s^+_{0,2} + \left(\sigma^z_{0,2}\right)^2 s^+_{0,1}\right] \left(s^-_{1,1} + s^-_{1,2}\right) + \text{h.c.}~;
\end{aligned}\end{equation}
here, \(\sigma^z_{0,l} = \hat n_{0\uparrow,l} - \hat n_{0\downarrow,l}, s^+ = c^\dagger_{0 \uparrow,l}c_{0 \downarrow,l}\) and \(s^- = \left(s^+\right)^\dagger\). The notation \(0\sigma,l\) has the site index \(i=0,1,2,\ldots\) as the first label, the spin index \(\sigma=\uparrow,\downarrow\) as the second label and the channel index \(l=1,2\) as the third index.
Such non-Fermi liquid (NFL) terms in the effective Hamiltonian and the absence of any Fermi-liquid term at the same order should be contrasted with the local Fermi liquid excitations induced by the singlet ground state of the single-channel Kondo model~\cite{nozieres1974fermi,wilson1975renormalization,hewson1993}.
We now take the MCK Hamiltonian to strong-coupling, and perform a perturbative treatment of the hopping.
At \(J \to \infty\), the perturbative coupling \(t^2/J\) is arbitrarily small and we again obtain Eq.~\ref{nfl_terms}. Such a change from the strong coupling model with parameter \(J\) to a weak coupling model with parameter \(t^2/J\) amounts to a duality transformation~\cite{kroha_kolf_2007,zitko_fabrizio_2017}.
It can be shown that the duality transformation leads to an identical MCK model~\cite{kroha_kolf_2007} (self-duality), which implies we can have identical RG flows, and our transformation simply extracts the NFL piece from the dual model.
The self-duality also ensures that the critical intermediate-coupling fixed point is unique and can be reached from either of the models.

The diagonal part of eq.~\ref{nfl_terms} is
\begin{equation}\begin{aligned}
	V_\text{eff} = \frac{2t^2}{J}\sum_{l=1,2}\left(\sum_\sigma \hat n_{0\sigma,l}\right) s^+_{0,\bar l}s^-_{1,\bar l} + \text{h.c.}
\end{aligned}\end{equation}
where \(\bar l = 3 - l\) is the channel index complementary to \(l\). We will Fourier transform this effective Hamiltonian into \(k-\)space. The NFL part becomes
\begin{equation}\begin{aligned}
	\label{k_space_od}
	\sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \text{h.c.} 
\end{aligned}\end{equation}
This form of the Hamiltonian is very similar to the three-particle interaction term in Appendix B of~\cite{anirbanmott1}. The channel indices in Eq.~\ref{k_space_od} can be mapped to the normal directions in~\cite{anirbanmott1}. The 2 particle-1 hole interaction in Eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
\begin{equation}\begin{aligned}
	H_\text{eff,MFL} = \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{2t^2e^{i\left(k_1 - k_2\right)a}}{J} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \text{h.c.}\\
	= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right)
\end{aligned}\end{equation}
The most dominant contribution comes from \(k_1 = k_2 = k^\prime\), revealing the non-Fermi liquid metal~\cite{cox_jarrell_two_channel_rev,andrei_jerez_1995}:
\begin{equation}\begin{aligned}
	\label{mfl_large}
	H^*_\text{eff,MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)
\end{aligned}\end{equation}
A non-local version of this effective Hamiltonian was found to describe the normal phase of the Mott insulator of the 2D Hubbard model, as seen from a URG analysis~\cite{anirbanmott1,anirbanmott2}. Following~\cite{anirbanmott1}, one can track the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\text{rh}\) RG step, in the form of the URG equation
\begin{equation}\begin{aligned}
	\Delta R_j =- \frac{R_j^2}{\omega - \epsilon_{j}/2 - R_j/8}
\end{aligned}\end{equation}
In the RG equation, \(\epsilon_{j}\) represents the energy of the \(j^\text{th}\) isoenergetic shell. It is seen from 
the RG equation that \(R\) is relevant in the range of \(\omega < \frac{1}{2}\epsilon_j\) that has been used throughout, leading to a fixed-point at \(R^*/8 = \omega - \frac{1}{2}\epsilon^*)\). The relevance of \(R\) is expected because the strong coupling \(J\) is irrelevant and \(R \sim 1/J\).

The renormalisation in \(R\) leads to a renormalisation in the single-particle self-energy~\cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalisation is
\begin{equation}\begin{aligned}
	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}
\end{aligned}\end{equation}
The density of states can be approximated to be \(N^*/R^*\), where \(N^*\) is the total number of states over the interval \(R^*\). As suggested by the fixed point value of \(R_j\), we can approximate its behaviour near the fixed point by a linear dependence of the dispersion \(\epsilon_j\). The two limits of the integration are the start and end points of the RG. We start the RG very close to the Fermi surface and move towards the fixed point \(\epsilon^*\). Near the start point, we substitute \(\epsilon = 0\) and \(R = \omega\), following the fixed point condition. From the fixed point condition, we also substitute \(R^*/8 = \omega - \frac{1}{2}\epsilon^*\). On defining \(\bar \omega = N^* \left(\omega - \frac{1}{2}\epsilon^*\right)\), we can write
\begin{equation}\begin{aligned}
	\label{self_energy}
	\Delta \Sigma(\omega) \sim  \bar \omega \ln \frac{N^* \omega}{\bar \omega}
\end{aligned}\end{equation}
The self-energy also provides the quasiparticle residue for each channel\cite{anirbanmott1}:
\begin{equation}\begin{aligned}
	Z(\bar\omega) = \left(2 - \ln \frac{2\bar\omega}{N^* \omega}\right) ^{-1}
\end{aligned}\end{equation}
As \(\omega \to 0\), the \(Z\) vanishes, implying that the ground state is not adiabatically connected to the Fermi gas in the presence of the NFL terms.
This is the orthogonality catastrophe~\cite{varma2002singular,anderson_infraredcat,yamada_catastrophe,yamada1979orthogonality} in the two-channel Kondo problem, and it is brought about by the presence of the channel-non diagonal terms in Eq.~\ref{mfl_large}.
Such terms were absent in the single-channel Kondo model, because there was no multiply-degenerate ground state manifold that allowed scattering.
This line of argument shows that the extra degeneracy of the ground state subspace and the frustration of the singlet order that comes about when one upgrades from the single-channel Kondo model to the MCK models is at the heart of the NFL behaviour, and the orthogonality catastrophe is expected to be a general feature of all such frustrated MCK models.
A local NFL term and a similar self-energy was also obtained by Coleman, et al.~\cite{Coleman_tsvelik} in terms of Majorana fermions at the strong-coupling fixed point of the \(\sigma-\tau\) model, which they claimed was equivalent to the intermediate-coupling fixed point of the two-channel Kondo model.
Along with the work by Schofield~\cite{schofield_1997}, this demonstration shows the universality between the two-channel Kondo and the \(\sigma-\tau\) models.

\section{Entanglement properties}
\label{sec:ent_prop}

\subsection{Entanglement properties of the star graph}
\label{sec:EE_star graph}

We will now present the results of our study of various entanglement measures in each of the $K$ degenerate ground states $|J^z\rangle$ of a $K$ channel star graph, labeled by the eigenvalues of $J^z$.
\subsubsection{Entanglement entropy between impurity and the rest}
In a 1-channel Kondo model, the ground state is unique and a singlet~\cite{wilson1975renormalization}: \(\ket{J,J_z=0,0} = \frac{1}{\sqrt{2}} \left(\ket{\uparrow_{d},\downarrow_0} - \ket{\downarrow_d, \uparrow_0}\right)\), and the impurity entanglement entropy ($EE_d$) is at the  maximum possible value of $\log 2$.
We will now calculate the same quantify for the ground states 
\begin{equation}\begin{aligned}
\ket{J^z} \equiv \ket{S_d=1/2,S=K/2;J=(S-1/2),J^z}
\end{aligned}\end{equation}
of the $K$ channel model.

In order to compute \(EE_d\) for a particular state \(\ket{J^z}\), we calculate the von-Neumann entropy of the reduced density matrix \(\rho_d\) obtained by partially tracing the density matrix $\rho=|J^z\rangle\langle J^z|$ associated with the state \(\ket{J^z}\) over the impurity states \(\ket{S_d^z = \pm \frac{1}{2}}\): 
\begin{eqnarray}
\rho_{d}&=& \textrm{Tr}_{d} \rho=\sum_{S_d^z} \langle S_d^z| \rho | S^z_d\rangle ~,~~EE_d = -\rho_{d} \log \rho_{d}~~~
\end{eqnarray}

\begin{figure}[!htpb]
\centering
\includegraphics[width=0.49\textwidth]{plt/EE_multi_channel_ANN.png}
\caption{Variation of impurity entanglement entropy ($EE_d$) for multiple values of \(K\). The maximum \(EE_d\) at large \(K\) is $\log 2$.}
\label{fig:EE_d}
\end{figure}
The \(EE_d\) for states of various \(J^z\) are shown as functions of the number of channels \(K\) in fig.~\ref{fig:EE_d}. At any given value of \(K\) on the \(x-\)axis, all the points directly above it represent values of \(EE_d\) for various values of \(J^z\) in the ground state manifold of the MCK problem defined by that particular value of \(K\). The minimum entanglement entropy occurs in the maximum \(J^z\) state $\left(|J^z=J\rangle\right)$, and this minimum value decreases with increase in \(K\). On the other hand, the maximum entanglement entropy is attained in the state with minimum \(J^z\). This maximum value of the entanglement entopy is always \(\ln 2\) for odd values of \(K\); for even values of \(K\), the value asymptotically reaches $\log 2$ at large \(K\).

A very similar computation gives the entanglent entropy between one outer spin and the rest of the spins, and it is shown in Fig.~\ref{fig:EE_outer}.
We again find that the minimum entanglement entropy is associated with the state $|J^z=J\rangle$ and it falls with increasing \(K\), approaching zero asymptotically; the maximum entanglement entropy is, as before, associated with the state $|\left(J^z\right)_\mathrm{min}\rangle$ and it rises to $\log 2$ in the limit $K\gg 1$.
\begin{figure}[!htpb]
\centering
\includegraphics[width=0.49\textwidth]{plt/outer_EE_multi_channel_ANN.png}
\caption{Variation of the entanglement entropy of an outer spin ($EE_o$) with the rest for different channels $(K)$. The maximum entanglement entropy in the large $K$ limit is $\log 2$.}
\label{fig:EE_outer}
\end{figure}

Two interesting features emerge from the study:
\begin{itemize}
	\item For the odd \(K\) models, the impurity is maximally entangled with the other spins in the minimum \(J^z\), $|J^z=0\rangle$, member of the ground state manifold.
	At large \(K\), the even \(K\) models also acquire this property, the minimum \(J^z\) there being \(\pm \frac{1}{2}\).
	\item 
	Both \(EE_d\) and \(EE_0\) are individually equal for the states $|\pm J^z\rangle$, which shows that both types of entanglement entropy are invariant under the transformation \(\ket{J^z} \to \pi \ket{J^z}\). This reflects a parity symmetry in the state space in terms of entanglement.
\end{itemize}

\subsubsection{Mutual Information}

\begin{figure}[!htpb]
\includegraphics[width=0.49\textwidth]{plt/NEW31Dec_I_2_vs_Nch_[0,1]}
\caption{Variation of mutual information $I^2(d:o)$ of the impurity with the rest, for different values of $K$. The maximum $I^2(d:o)$ is $0.37$.}
\label{fig:MI_d_o}
\end{figure}

Mutual information is a measure which captures the correlations present between two subsystems (A,B), in a particular state. It is defined as
\begin{eqnarray}
I^2(A:B)=S_A+S_B-S_{A\cup B}~,
\end{eqnarray}
where $S_{A(B)}$ is the von-Neumann entanglement entropy of the subsystem $A(B)$ with the rest, and \(S_{A\cup B}\) is the von-Neumann entanglement entropy of \(A\) and \(B\) with the rest.
We are interested in two types of mutual information: firstly, the mutual information $I^2(d:o)$ between the impurity and one of the other spins, and secondly, the mutual information $I^2(o:o)$ between any two of the outer spins.
Both of these have been computed for various channel numbers \(K\), and plotted in Figs.~\ref{fig:MI_d_o} and ~\ref{fig:MI_o_o}.

\begin{figure}[!htpb]
\includegraphics[width=0.49\textwidth]{plt/NEW31Dec_I_2_vs_Nch_[1,2]}
\caption{Variation of mutual information $I^2(o:o)$ between 2 outer spins, for multiple $K$. $I^2(o:o)$ vanishes for large $K$.}
\label{fig:MI_o_o}
\end{figure}

In both cases we find that the maximum and minimum mutual information are associated with the $|\left(J^z\right)_\mathrm{min}\rangle$ and $|J^z=J\rangle$ states respectively.
We also find that the  mutual information is the same in the states $|J^z\rangle$ and $\pi^x|J^z\rangle$, indicating the parity symmetry in the mutual information measure.
In the large channel limit ($K\gg 1$), the maximum \(I^2(d:o)\) and \(I^2(o:o)\) saturate to the common value of $0.375$.

\subsubsection{Multipartite information}
Similar to mutual information, one can calculate higher order multipartite information to study the nature of correlations present in different ground states. We define the tripartite information among three subsystems $A,B,C$ as $I^3_{ABC} = (S_A+S_B+S_C)-(S_{AB}+S_{BC}+S_{CA})+S_{ABC}~$. \(I^3\) shows behavior similar to the mutual information - the highest \(I^2\) value is associated with the $\left(J^z\right)_\mathrm{min}$ state and it saturates in the limit of $K\gg 1$. One can measure $N-$partite information for a collection of subsystems (CSS) $\{\mathcal{A}_N\}\equiv\{A_1,A_2,\cdots,A_N\}$. To define the $N-$partite information, we first define the power set of the CSS $\{\mathcal{A}_N\}$ as $\mathcal{P}(\{\mathcal{A}_{N}\})$, and the collection of all subsets of $\mathcal{P}(\{\mathcal{A}_{N}\})$ with $m$ subsystems in it as $\mathcal{B}_m(\{\mathcal{A}_N\})\equiv \{ Q~| ~Q\subset \mathcal{P}(\{\mathcal{A}_{N}\}), |Q|=m \}$. We also define the union and intersection of all the subsystems present in $Q$ as ${V}_{\cup}({Q})\equiv \bigcup_{A\in Q} A$ and ${V}_{\cap}({Q})\equiv \bigcap_{A\in Q} A$ respectively. Then, the $N-$partite information that we are interested in is defined as
\begin{eqnarray}
I^{N}_{\{\mathcal{A}_N\}} &=& \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.~~~~
\label{eq:I_N_definition}
\end{eqnarray}
\begin{figure}
\includegraphics[width=0.49\textwidth]{plt/2022_IN_vs_N_K8.png}
\caption{Variation of multipartite information $I^N$ among \(N\) outer spins as a function of $N$, for $K=8$. The inset shows $I^N$ vs $N$ for an all-to-all model. Both show power law behavior.}
\label{fig:Im_vs_m}
\end{figure}

The study of such measures of multipartite information reveals the nature of the multi-party correlations present among the outer spins of the star graph. Our study, as presented in fig.~\eqref{fig:Im_vs_m}, shows that the higher order multi-partite correlations ($I^N$) decrease as you increase the order ($N$), and the behaviour follows a power law. In the inset of the same figure, we have shown the $I^N$ vs $N$ plot that is observed in the ground state of the all-to-all effective Hamiltonian (Eq.\ref{eq:flux_spectral}), and it shows a similar power-law behaviour. The similarities in the behavior suggest that one can capture entanglement properties either from the star graph or from the corresponding all-to-all model.

\subsection{Entanglement properties at the fixed point of the MCK model}
\label{sec:EE_excitation}

\begin{figure}[!htpb]
\includegraphics[width=0.49\textwidth]{plt/hopping_fock_states}
\caption{This is a schematic diagram of (a) single channel and (b) two channel problem. $S_d$ is the impurity spin. For more details refer to the text.}
\label{fig:schematic_hopping}
\end{figure}

To study the nature of correlations at the MCK fixed point, we introduce excitations into the star graph ground state. We will work with the Hamiltonian Eq.\eqref{eq:excitation_hamiltonian} where we consider nearest-neighbor real space hopping \(t\) from the zeroth site into the lattice (Fig.~\ref{fig:schematic_hopping}). Setting $t=0$ recovers the zero bandwidth version of the MCK. In the \(K=1\) single channel case, the impurity ($S_d$) is coupled to the spin degree of freedom at the real space origin ($\{1_{\uparrow},1_{\downarrow}\}$) of the single conduction bath via a Heisenberg spin-exchange coupling. For $K=2$, the impurity is interacting with $2$ distinct local spins $\{1_{\uparrow},1_{\downarrow}\}$ and $\{2_{\uparrow},2_{\downarrow}\}$ belonging to zeroth sites of different conduction channels, and the real space hopping connects these zeroth sites to their nearest neighbor sites. As we increase the hopping strength $t$ from zero to non-zero, the lattice sites start interacting with each other.

\subsubsection{Impurity entanglement entropy}
The impurity entanglement entropy $EE_d(t)$ in the ground state is shown as a function of $t$ in Fig.~\ref{fig:EE_imp_vs_t_K} for three values of channel number \(K\). At low hopping strength ($0<t\ll 1$), $EE_{d}$ is independent of $t$ and achieves a constant value. This value decreases with increasing \(K\). We also find that in this range of \(t\), \(EE_d\) decreases with increasing \(K\). This behaviour is reversed at high $t$, and \(EE_d\) is seen to increase with increasing \(K\). Though the values of the impurity entanglement entropy for various values of \(K\) are quite similar at low hopping strength, there is a difference in the behaviour as a function of \(t\): the single channel \(EE_d\) varies smoothly at \(t \to 0^+\), whereas the \(EE_d\) for \(K > 1\) show a discontinuity at $t \to 0^+$.

\begin{figure}[!htpb]
\centering
\includegraphics[width=0.49\textwidth]{plt/A_I1_ch123_['d']}
\caption{Variation of impurity entanglement entropy $EE_{imp}$ against $t$, for $K=1,2,3$. }
\label{fig:EE_imp_vs_t_K}
\end{figure}

\subsubsection{Intra-channel Mutual information}
Here, we will calculate the mutual information between two electronic states in the ground state wavefunction, as a function of the hopping strength $t$.

\par \textit{Case 1:} We first study the mutual information $MI(d,1\uparrow)$ between the impurity spin $S_d$ and the state $1_\uparrow$ (fig.~\ref{fig:schematic_hopping}), where $1$ represents real-space origin of the $1^\text{st}$ conduction channel. For a single channel model, this site is unique because there is just one channel, but in the presence of $K$ channel, there are $K$ possible choices corresponding to each of the channels. However, because of the symmetry of the Hamiltonian under the exchange of the channel indices, all such choices will show identical mutual information signatures. Similarly, due to the $SU(2)$ spin-rotation symmetry of the Hamiltonian, $MI(d,1\downarrow)$ will be identical to $MI(d,1\uparrow)$. We have numerically computed and plotted $MI(d,1\uparrow)$ as a function of $t$ in fig.~\ref{fig:MI_imp_1_vs_t_K}.  The inset shows that at low hopping strength, the mutual information for the single channel and the two-channel models saturate to different values. In the single-channel case, the saturation value at $t=0$ is $\log 2$, and the mutual information changes smoothly as \(t\) is turned on. This is similar to the behaviour in the impurity entanglement entropy studied previously. The value of $\log 2$ shows the maximal entanglement between the zeroth site and the impurity, and the perfect screening of the impurity spin. For the two channel problem, we find that the mutual information at \(t=0\) is $MI(d,1_{\uparrow})=0.2401$. The reduction of the value from \(\ln 2\) shows the breakdown of screening. Also note that unlike the single channel case, there is a discontinuity in $MI(d,1_{\uparrow})$ as \(t\) is increased from 0.

\begin{figure}[!htpb]
\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['d','1_up']}
\caption{This figure show the variation of mutual information between the impurity spin and the $1_{\uparrow}$ state against $t$. For more details please refer to the text. The errorbar $\sigma_2$ of the two channel data at low hopping strength $\sigma_2\approx 0.002$.}
\label{fig:MI_imp_1_vs_t_K}
\end{figure}

\par\textit{Case 2:} We have also computed the mutual information $MI(1_{\uparrow},1_{\downarrow})$  between the two electronic states on the zeroth site of the same conduction channel, and plotted them in fig.~\ref{fig:MI_1_2_vs_t_K}. We find that it is a smooth function of $t$ for \(K=1\), and for \(K=2\) there is a discontinuity at $t=0^{+}$. Note that for small values of \(t\), we find  $MI(1_{\uparrow},1_{\downarrow})>MI(d,1_{\uparrow})$ for the \(K=2\) model, showing the presence of strong intra-site correlations.

\begin{figure}[!htpb]
\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['1_up','1_down']}
\caption{Variation of mutual information ($i^2(1_{\uparrow},1_{\downarrow})$) among the two states present on the real-space origin ($1$) of a conduction channel, against $t$. The errorbar $\sigma_2$ for the two channel at low hopping strength is $\sigma_2\approx 0.013$.}
\label{fig:MI_1_2_vs_t_K}
\end{figure}

\par \textit{Case 3:} Next, we measure the mutual information $MI(d,l_{1\uparrow})$ between the impurity site and an electronic state of site that is nearest-neighbour to the real-space origin of one of the conduction channels (see fig.~\ref{fig:schematic_hopping}).  The results are shown in fig.~\ref{fig:MI_d_l1}. Vanishing mutual information for the single channel case shows the perfect screening of the impurity spin. The non-zero value of mutual information at small $t$ values in the \(K=2\) model is again a result of the imperfect screening. As in the previous cases, we find a discontinuity in the mutual information for \(K=2\) as $t \to =0^+$.

\begin{figure}
\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['d','l1_up']}
\caption{Variation of the mutual information $MI(d,l_{1\uparrow})$ between the impurity spin and the $l_{1\uparrow}$ state, against $t$. The errorbar $\sigma_2$ for the two channel case is $\sigma_2\approx 0.001$.}
\label{fig:MI_d_l1}
\end{figure}

\par \textit{Case 4:} A complementary study can be made by calculating the mutual information between the origin of a particular conduction channel and it's nearest neighbour site. They are plotted in fig.~\ref{fig:MI_l_l1}, and we find that at low hopping strength the single channel mutual information vanishes, showing the decoupling of those two states. On the other hand, in the two channel case, there is a non-zero mutual information which indicates the presence of scattering between the local Mott liquid and the local non-Fermi liquid states.

\begin{figure}[!htpb]
\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['1','l1']}
\caption{Variation of the mutual information $MI(1_{\sigma},l_{1\sigma})$ between two nearest neighbor sites against \(t\). The errorbar for the two channel case is $\sigma_2\approx 0.005$.}
\label{fig:MI_l_l1}
\end{figure}

Apart from these, we have also computed an intra-channel tripartite information $I^3(1_{\uparrow},l_{1\uparrow},l_{1\downarrow})$ of the two-channel ground state (blue curve in Fig.~\ref{fig:I3_I2_two_channel}) - it shows that there is a discontinuity in the triparite information at $t=0^+$, and at low hopping strength the tripartite information is independent of $t$ with a value $0.084$. This non-zero value of the tripartie information is consistent with the presence of a non-Fermi liquid effective Hamiltonian having more than just two-particle interactions within it. We have also studied inter-channel mutual informaition $I^2(1_{\uparrow},2_{\uparrow})$ for \(K=2\) (red curve in fig.~\ref{fig:I3_I2_two_channel}). It reveals the correlation and quantum entanglement between these two channels, and demonstrates the all-to-all nature of the local mott liquid.

\begin{figure}[!htpb]
\centering
\includegraphics[width=0.48\textwidth]{plt/I3_I2_A_I.png}
\caption{Red: Mutual information $I^2(1_{\uparrow},2_{\uparrow})$ against \(t\). Blue: Tripartite infrmation $I^3(1_{\uparrow},l_{1\uparrow},l_{1\downarrow})$ against \(t\). The errorbar ($\sigma$) for the $I^3$ and $I^2$ near the low hopping strength are $0.002$ and $0.003$ respectively.}
\label{fig:I3_I2_two_channel}
\end{figure}

\subsubsection{Bures distance and the orthogonality catathrope}
\begin{figure}[!htpb]
\includegraphics[width=0.49\textwidth]{plt/error_Bures_Distance_Ch123_10001}
\caption{Variation of Bures distance between the reduced density matrices of the star graph ground states at $t=0$ and $t\neq 0$, against $t$. The errorbars ($\sigma$) for \(K=2\) and \(K=3\) are $0.14$ and $0.08$ respectively, and near $t\approx 1$ the $\sigma$ are $0.04$ and $0.07$ respectively.}
\label{fig:bures_distance}
\end{figure}
In addition to these entanglement measures, we have also calculated the Bures distance between the states at \(t=0\) and \(t>0\). The Bures distance~\cite{uhlmann1976transition,bures1969extension,hubner1992explicit,hubner1993computation,dittmann1994some,marian2003bures} between two density matrices \(\rho_1,\rho_2\) is defined as 
\begin{equation}
d_{Bures}(\rho_1,\rho_2) = \sqrt{2} \bigg[1- \textrm{Tr}\bigg\{ \bigg(\rho_1^{1/2}  \rho_2 \rho_{1}^{1/2}\bigg)^{1/2} \bigg\}\bigg]
\end{equation}
and is a measure of the distance, in the Hilbert space, between the states forming the density matrices. One can see from the above defination that the maximum and minimum possible distances are $\sqrt{2}$ and $0$ respectively.
\par We get the ground state $|\psi(t)\rangle$ of the problem by solving the Hamiltonian in Eq.~\eqref{eq:excitation_hamiltonian}. This ground state $|\psi(t)\rangle(t)$ and the associated density matrix $\rho(t)= |\psi(t)\rangle \langle \psi(t)|$ are functions of the hopping strength \(t\). We are interested in the reduced density matrix $\rho_{sg}(t)$ of only the sites that form the star graph (impurity site and the zeroth sites of the conduction channels), so we trace out all the nearest neighbor sites from the full density matrix:, $\rho_{sg}(t)=\textrm{Tr}_{n-n}(\rho(t))$. The Bures distance $d_{Bures}(\rho_{sg}(0),\rho_{sg}(t))$ is then calculated between the reduced density matrices at \(t=0\) and \(t > 0\), for \(K=1\), \(K=2\) and \(K=3\).

We have shown the variation of the Bures distance as a function of the hopping strength \(t\) in Fig.~\ref{fig:bures_distance}. Although the Bures distance is \(0\) (by definition) at \(t=0\) for all \(K\), a difference arises as \(t\) is made slightly non-zero: there is a discontinuity in the Bures distance for the two and three channel models, while the single channel Bures distance is continuous. The smooth variation of the Bures distance in the single channel case shows the adiabatic continuity of the reduced star graph density matrix from the $t=0$ case to $t\neq 0$ case. On the other hand, the abrupt jump in the Bures distance for higher-channel cases at $t=0^+$ shows the breakdown of adiabatic continuity between the \(t=0\) and \(t = 0^+\) Hamiltonians and signals an {\it orthogonality catastrophe} between these two ground states. The discontinuity increases as \(K\) is increased, indicating that taking more channels will lead to the maximum Bures distance of $d_{Bures}=\sqrt{2}$ and hence an exact orthogonality.

\section{Dualities of the MCK model}
\label{sec:duality}

We start from a strong coupling \((J \to \infty)\) spin-\(S\) impurity MCK Hamiltonian in the over-screened regime \(\left( K > 2S \right) \),
\begin{equation}\begin{aligned}
	\label{strong_ham}
	H(J) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + J \vec{S_d}\cdot\vec{S}~.
\end{aligned}\end{equation}
Here, \(\vec S\) is the total spin \(\sum_l \sum_{kk^\prime \alpha\beta} \vec \sigma_{\alpha\beta}c^\dagger_{k\alpha,l}c_{k^\prime\beta,l}\) of all the zero modes. At strong coupling, the ground states of the star graph eq.~\ref{star graph} act as a good starting point for a perturbative expansion. As argued previously, there are \(K-2S_d+1\) ground states, labeled by the \(K\) values of the total spin angular momentum \(J^z = S_d^z + S^z = -\frac{K}{2} + S_d, -\frac{K}{2} + S_d + 1, \ldots, \frac{K}{2} - S_d\). Since a general spin-\(s\) object is simply a \(2s+1\) level system, the \(K-\)fold degenerate ground state manifold can be used to define a new impurity spin \(\mathbb{S}_d\) of multiplicity \(2\mathbb{S}_d + 1 = K-2S_d+1\) which implies that we need \(\mathbb{S}_d = \frac{K}{2} - S_d\). That is, the spin-\(S_d\) impurity has a dual described by a spin-\((K-2S_d+1)\) impurity. The states of this new spin are defined by
\begin{gather}
	\hat{\mathbb{S}_d^z} \ket{S^z} = S^z \ket{S^z},\nonumber\\
	\hat{\mathbb{S}_d^\pm} \ket{S^z} = \sqrt{\mathbb{S}_d\left( \mathbb{S}_d + 1 \right) - S^z\left( S^z \pm 1\right)} \ket{S^z \pm 1}
\end{gather}
While the ground state subspace gives rise to the new central spin object, the excited states of the star graph can be used to define bosonic operators that mediate interactions between the central spin and the next-nearest neighbour lattice sites~\cite{kroha_kolf_2007}. In terms of the zero-bandwidth spectrum, the bosonic operators represent scattering between the ground state subspace and the excited subspaces. Through a Schrieffer-Wolff transformation in the small coupling \(\frac{t^2}{J}\), one can then remove this interaction and generate an exchange-coupling between the new impurity \(\vec {\mathbb{S}}_d\) and the new zero modes formed out of the remaining sites in the lattice \cite{kroha_kolf_2007} (by remaining, we mean those real space sites that have not been consumed into forming the new spin). The new Hamiltonian, characterized by the small super-exchange  coupling \(\mathbb{J}\) of the general form \(\gamma t^2/J\), has the form
\begin{equation}\begin{aligned}
	H^\prime(\mathbb{J}) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + \mathbb{J} \vec{\mathbb{S}_d}\cdot\vec{\mathbb{S}}
\end{aligned}\end{equation}
$\vec{\mathbb{S}}$ is the local bath spin formed by the new zero modes. This Hamiltonian is very similar to the one in eq.~\ref{strong_ham}, and that is the essence of the strong-weak duality: One can go from the over-screened strong coupling spin-\(S\) MCK model to another over-screened weak coupling spin-\((K-2S+1)\) MCK model. For the case of \(K=4S\), we have \(\mathbb{S}_d = S_d\), and both \(S_d\) and \(\mathbb{S}_d\) describe the same spin objects (at least formally). The two models are then said to be self-dual. For example, for the case of spin-half MCK model, two-channel model is self-dual.

One important consequence of the duality relationship between the two over-screened models is that the RG equations are also dual; while the strong coupling model has an irrelevant coupling \(\mathcal{J}\) that flows down to the intermediate fixed point \({\mathcal{J}^*}\), the weak coupling model has a relevant coupling \(\mathbb{J}\) that flows up to the same fixed point \({\mathbb{J}}^* = {\mathcal{J}^*}\). From the RG equation for the general spin-\(S\) MCK model, we know that \({\mathbb{J}}^* = \frac{2}{K \rho^\prime}\), where \(\rho^\prime\) is the DOS for the bath of the weak coupling Hamiltonian. This constrains the form of the scaling factor \(\gamma\):
\begin{equation}\begin{aligned}
	{\mathbb{J}}^* = \frac{\gamma 4t^2}{{\mathcal{J}^*}} = \frac{2}{K \rho^\prime} \implies \gamma = \frac{1}{4t^2} {{\mathcal{J}^*}}^2 = \frac{1}{K^2 t^2 \rho \rho^\prime}
\end{aligned}\end{equation}

There exists another set of dual points in the MCK model. This was hinted at when we looked at the degree of compassion in eq.~\ref{gamma}. Since \(\Gamma\) depends only on the magnitude of \(\delta\), both \(\pm \delta\) will give the same degree of compensation, same ground state energy and same ground state degeneracy \(\left(g^{S_d}_K = |\delta|+1\right)\). The definition of \(\delta\) gives the duality transformation as \(K \to 2S_d, S_d \to \frac{K}{2}\). That is, we transform from a \(K-\)channel MCK model with spin-\(S_d\) impurity, to a \(2S_d\)-channel MCK with a spin-\(\frac{K}{2}\) impurity. The exactly-screened model \(K=2S_d\) maps on to itself and is therefore self-dual under this transformation.

For \(K \neq 2S_d\), we transform an over-screened model into an under-screened model and vice versa. This duality relationship allows us to infer the RG scaling behaviour of one of the models if we know that of the other. If we know that for a certain pair of values \(K\) and \(S_d\), the \(K-\)channel MCK model with spin-\(S_d\) impurity has an intermediate fixed point, we can immediately conclude that the \(2S_d\)-channel spin-\(\frac{K}{2}\) model has a strong coupling fixed point.

\section{Quantum Phase transition in the MCK model under channel anisotropy}
\label{anisotropic_rg}

For a channel anisotropic MCK model with \(K\) Kondo couplings \(\mathcal{J}_i\) for each fo the \(K\) conduction channels, the zero bandwidth model is 
\begin{eqnarray}
H_K (\vec{{\mathcal{J}}}) &=& \sum_{i=1}^{K} {\mathcal{J}}_i\vec{S}_d.\vec{S}_i
\label{eq:anisotropy}
\end{eqnarray}
For the special case $\mathcal{J}_i=\mathcal{J}, \forall i$ we get the usual isotropic star graph model. For the case of spin-1/2 impurity, we find that the Hamiltonian with any value of $\mathcal{J}_i>0$ has $K$ fold ground state degeneracy. This shows that the ground state degeneracy of the star graph model is extremely robust against the channel anisotropy; the ground state degeneracy does not change until at least one \(\mathcal{J}_i\) vanishes.
\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{plt/Anisotropy_Channel_3.png}
\caption{\textit{Left:} Variation of the ground state degeneracy against the $J_3$ keeping $J_1=J_2=1$ fixed. \textit{Right:} Variation of ground state degeneracy against $J_1=J_2$ keeping $J_3$ fixed. Both plots show the robustness of the ground state degeneracy against channel anisotropy.}
\label{fig:channel-anisotropy-}
\end{figure}

We have demonstrated this numerically for a three channel anisotropic star graph model.
In Fig.~\ref{fig:channel-anisotropy-}(a), we show that if two couplings are kept fixed to be equal (${\mathcal{J}}_1={\mathcal{J}}_2=1$) and the third coupling ${\mathcal{J}}_3$ is tuned from some finite value to zero, the degeneracy does not change from 3 to 2 until \(\mathcal{J}_3\) becomes zero.
At that point, the model becomes a two channel Kondo problem.
%{\color{red}
We also show in Fig.~\ref{fig:channel-anisotropy-}(b) that we keep the first coupling ${\mathcal{J}}_3$ fixed to $1$ and vary the common coupling ${\mathcal{J}}_1={\mathcal{J}}_2$ from non-zero to zero, this is equivalent to keeping ${\mathcal{J}}_1={\mathcal{J}}_2=1$ fixed and taking ${\mathcal{J}}_1$ to infinity from finite.
In this case we find when the coupling ${\mathcal{J}}_1=\lambda_2=0$ the degeneracy becomes one showing the effective single channel nature.
%}

The above demonstration makes it clear that the ground state degeneracy can change only when at least one of the Kondo couplings vanish. This can be realised under RG flow if one considers the anisotropic MCK model.
\begin{align}
	H = \sum_{k,\alpha,l}\epsilon_{k,l} \hat n_{k\alpha,l} + \sum_{kk^\prime,\atop{\alpha,\beta,l}}{\mathcal{J}}_l \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\beta}c_{k\alpha,l}^\dagger c_{k^\prime\beta, l}~.
\end{align}
We consider the specific case where \(K-1\) channels have the same coupling \({\mathcal{J}}_1 = {\mathcal{J}}_2 = ... = {\mathcal{J}}_{K-1} = {\mathcal{J}}_+\) and the remaining channel has a different coupling \({\mathcal{J}}_K = {\mathcal{J}}_-\). The RG equations for such a model are
\begin{align}
	\frac{\Delta {\mathcal{J}}_\pm}{|\Delta D|} = -\frac{{\mathcal{J}}_\pm^2 \rho}{\mathcal{D}_\pm} + \frac{\rho^2 {\mathcal{J}}_\pm}{2}\left[\frac{(K-1){\mathcal{J}}_+^2}{\mathcal{D}_+} + \frac{{\mathcal{J}}_-^2}{\mathcal{D}_-}\right]~,
\end{align}
where \(\mathcal{D}_\pm = \omega - \frac{D}{2} - \frac{{\mathcal{J}}_\pm}{4}\) are the denominators of the URG equations.
Setting \({\mathcal{J}}_+ = {\mathcal{J}}_-\) leads to the critical fixed point at \({\mathcal{J}}_+^* = {\mathcal{J}}_-^* = {\mathcal{J}}_* = \frac{2}{K \rho}\). We now perturb around this fixed point by defining new variables \(j_\pm = {\mathcal{J}}_\pm - {\mathcal{J}}_*\). We also assume that the bandwidth is large enough so that \(\mathcal{D}_\pm \simeq \omega - \frac{D}{2} - \frac{{\mathcal{J}}_*}{4} = -|\mathcal{D}_*|\). Performing a linear stability analysis about \(j_\pm=0\) then reveals the following two possibilities:

\par\textit{(a)} If \(j_-<0,j_+>0\), the deviation \(j_-\) is relevant and \(\mathcal{J}_-\) flows to zero. The flow of \(j_+\) are constrained such that the remaining couplings \(\mathcal{J}_+\) flow to the stable intermediate fixed point of the \(K-1\) channel MCK model: \(J_{+,*} = \frac{2}{(K-1)\rho}\).
\par\textit{(b)} If \(j_- > 0, j_+<0\), the couplings \(\mathcal{J}_+\) are irrelevant, and this leads to a single channel Kondo model described by the coupling \(\mathcal{J}_-\) which flows to strong coupling.

These conclusions show that the \(K\) channel intermediate fixed point is unstable under channel anisotropy~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000}. If one of the couplings becomes smaller than the rest, then that coupling flows to zero while the other \(K-1\) couplings flow to the \(K-1\) channel fixed point. On the other hand, if \(K-1\) couplings are smaller than a single coupling, then the smaller couplings vanish while the remaining coupling flows to strong-coupling.

\section{Conclusions}
\par
In summary, we have explored the low-energy behaviour of the MCK models using the unitary renormalization group (URG) method and obtained a better understanding of the role of ground state degeneracy and quantum-mechanical frustration in shaping the non-Fermi liquid physics and criticality.
Using the unitary renormalization group technique, we have obtained the zero-temperature phase diagram of the MCK problem and an effective Hamiltonian with a simple zero bandwidth limit - the star graph, and it determines the ground state energy, wavefunction and degeneracy of the MCK models.
This star graph is found to explain much of the physics of overscreening and criticality, including the singularities in the susceptibility and magnetisation, as well as a reduction in the degree to which the impurity spin is compensated.
The overarching message there was that the ground state degeneracy of the star graph (which is unity for single-channel and greater for the overscreened models) was the key ingredient in leading to the qualitative and quantitative differences from the single-channel model
The presence of ground state degeneracy also allows the construction of non-local twist operators and fractional excitations in the ground state manifold.
Integrating out the quantum fluctuations of the impurity leads to an all-to-all effective Hamiltonian for the local bath spins, and the Hamiltonian is foudn to contain inter-channel quantum scattering in terms of electron-hole pairs, theryby creating a local Mott-liquid phase at the origin of the lattice.

\par The low energy effective Hamiltonian (LEH) for the excitations is then obtain by considering fluctuations of the conduction bath on top of the ground state. The LEH for the 2-channel Kondo confirms absence of any Fermi liquid phase due to an exact cancellation across the ground state manifold, and the presence of inter-channel off-diagonal non-Fermi liquid terms. Our analysis reinforces the idea that the ground state degeneracy is crucial to the non-Fermi liquid physics and to the presence of such off-diagonal terms in the LEH.
The existence of a marginal Fermi liquid within the effective Hamiltonian clearly displays the orthogonality catastrophe in the form of singularities that are absent at exact screening.
Studies of various thermodynamic properties (presented in the supplementary material) from this 2-channel Kondo LEH like specific heat and susceptibility show logarithmic dependence at low temperature, in agreement with the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005,emery_kivelson,andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002}.

\par 
The non-diagonal nature of the LEH is further investigated through the several measures of entanglement.
The entanglement entropy, calculated from the minimum \(J^z\) states, between the impurity and the outer spins, as well as between an outer spin and the rest saturate to \(\ln 2\) in the large channel limit saturate. The opposite behaviour happens in the maximum $J^z$ state, where the entanglement entropy decreases with the increase of channel number.
The large values of inter-channel mutual information indicate high inter-channel correlation in the MCK ground state.
The power-law dependence of the multi-partite information among the outer spins of the star graph model is similar to the power-law behavior of the all-to-all local Mott-liquid ground state.
The presence of a discontinuity in the non-Fermi liquid ground state multi-channel entanglement as compared to the smooth behaviour in the single-channel counterpart again points to the orthogonality catastrophe in the low-energy phase of the multi-channel models.
Higher discontinuity for a higher number of channels was observed in the Bures distance study. The URG study of the channel anisotropic MCK shows the critical and unstable nature of the isotropic fixed point; under any anisotropic perturbations, the RG flows go towards either the single-channel model or the symmetric MCK with one less channel coupled to the impurity.
This is complemented by the study of the star graph ground state degeneracy which shows that the degeneracy changes only if one or more couplings vanishes.
When combined, we can conclude that in the presence of channel anisotropy, the degeneracy of the MCK ground state does not change until the RG reaches the stable fixed point.

\par This method serves as a template for the study of other quantum impurity systems.
We have already seen that the degeneracy of the star graph is robust under anisotropy; one can perform similar studies in the presence of a superconducting gap that cuts off the ground state manifold from the excitations, hence providing the degeneracy a topological protection.
The duality transformations then allow us to view the topologically protected ground state as a larger quantum spin which is essentially isolated.
This holds immense potential for applications in quantum information and quantum computation.
More fine-tuned behaviour can be obtained by studying the MCK model with an easy-axis anisotropy term \(\left(J^i\right)^2\) along one of the axes ($i$).
Such a term would, if it is able to survive the RG flows towards low energy, lift the degeneracy of the ground state and make it possible to achieve perfect screening even with \(K > 2S_d\).
One can also study the multi-channel lattice models~\cite{Piguet1997,shaw_1998} to better understand the role played by singlet frustration and ground state degeneracy in the competition between the local moment versus the heavy fermion sea.

\acknowledgments
%\textcolor{red}{
SP and Anirban Mukherjee thanks the CSIR, Govt. of India and IISER Kolkata for funding through a research fellowship. Abhirup Mukherjee thanks IISER Kolkata for funding through a research fellowship. {\color{red}SL thanks $\cdots$}.
%}

\bibliography{mscript_mck_full}
\end{document}

### 2022-04-26 manuscript/supplementary_mck.tex
made final changes after several months

\documentclass[reprint,onecolumn,prb,superscriptaddress]{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,color,ulem,soul,lipsum}
\allowdisplaybreaks
\bibliographystyle{apsrev4-2}
\begin{document}

\title{Supplementary Materials for ``Frustration shapes multi-channel Kondo physics: A star graph perspective"}

\author{Siddhartha Patra}
\email{sp14ip022@iiserkol.ac.in }
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\author{Abhirup Mukherjee}
\email{am18ip014@iiserkol.ac.in }
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\author{Anirban Mukherjee}
\email{mukherjee.anirban.anirban@gmail.com }
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\author{A. Taraphder}
\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
\author{N. S. Vidhyadhiraja}
\email{raja@jncasr.ac.in}
\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
\author{Siddhartha Lal}
\email{slal@iiserkol.ac.in}
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
\date{\today}
\maketitle

\section{Additional Properties of the Star Graph}

\subsection{Energy lowering due to quantum fluctuations}
The star graph Hamiltonian that sits at the heart of the RG fixed point Hamiltonian of the multichannel Kondom model contains a classical Ising term and a quantum fluctuation term:
\begin{equation}\begin{aligned}
	H = {\mathcal{J}}\vec{S_d}\cdot\vec S = \mathcal{J}\left[\underbrace{S_d^z S^z}_\text{Ising term} + \underbrace{\frac{1}{2}\left(S_d^+ S^- + \text{h.c.}\right)}_\text{quantum fluctuation part} \right] = \mathcal{J}\left[\mathcal{H}^C + \mathcal{H}^Q\right] 
	\label{eq:stargraph_hamiltonian}
\end{aligned}\end{equation}
We are interested in studying how the presence of quantum fluctuations in the Hamiltonian of eq.~\ref{eq:stargraph_hamiltonian} stabilises the ground state. This can be understood by looking at the contributions, per channel, of the classical and the quantum parts to the total ground state energy \(E_g\). In the overscreened case \(\left( K > 2S_d \right) \), the contributions are
\begin{gather}
	E_{C} = \frac{1}{K}\langle \psi_g | \mathcal{H}^C | \psi_g \rangle, ~~~~~ E_{Q} = \frac{1}{K}\bra{\psi_g}\mathcal{H}^Q \ket{\psi_g} =\frac{E_g/\mathcal{J} - E_{C}}{K} =  -\frac{1}{2}S_d - \frac{1}{K}\left(S_d + E_{C}\right)
\end{gather}  
where we have defined the contributions \(E_C\) and \(E_Q\) to the ground state energy coming from the Ising and fluctuation parts respectively, and we have substituted the ground state energy \(E_g\) for the overscreened case {\color{blue}from the expression in the main text, just below where the star graph is introduced}. This contribution $E_Q$ is generated by the spin-flip fluctuations between the impurity spin and the outer spins of the star graph. Note that because of the degeneracy of the ground state subspace, there are multiple ground states characterised by different values of \(J^z = S^z + S_d^z\), and different ground states lead to different values of \(E_Q\).

The variation of \(E_Q\) is shown in Fig.\ref{fig:quantum_energy} for the case of $S_d=1/2$, as functions of the number of channels \(K\) as well as the ground state value \(J^z\) in which \(E_Q\) is being calculated. For a particular channel $K$, we find that the maximum \(|E_Q|\) is obtained for the state with smallest magnitude of $J^z$ (\(J^z = 0 \) for odd \(K\) and \(J^z = \pm 1/2\) for even \(K\)), whereas \(|E_Q|\) is minimum in the states with largest \(J^z\) ($J^z=\pm J$). The larger values of \(|E_Q|\) indicate that the quantum fluctuations are largest in the states with minimum \(J^z\), and these states can be thought of as the counterparts to the maximally entangled singlet seen in the single-channel Kondo problem. This behavior persists as \(K \gg 1\): the magnitude \(|Q_Q|\) associated with the $|J^z|= J$ states vanish, showing the classical nature of these states and the lack of quantum fluctuations in that limit. On the other hand, the state $|J^z| = |J^z|_{min}$ has a non-zero \(|E_Q|\) in the large \(K\) limit and hence contains some non-zero quantum fluctuations, showing the true quantum nature of this macroscopic singlet state.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.7\textwidth]{plt/all/Quantum_Energy_per_channel}
\caption{This shows the variation of quantum energy per channel with $1/N$, where $N=N_{ch}+1$ is the total number of spins in the systems including the impurity spins. {\bf REMOVE DELTA IN YLABEL}}
\label{fig:quantum_energy}
\end{figure}

\subsection{Measure of quantum fluctuations}
Here we are interested in calculating the quantum fluctuation present in the  ground state by measuring the expectation value of the spin-flip part of the Hamiltonian: ${\mathcal{Q}}\equiv \langle \psi_g | (J^x)^2+(J^y)^2 |\psi_g\rangle = \langle \psi_g | J^2 - (J^z)^2 |\psi_g\rangle$. For a general spin-$S_d$ impurity, the ground state is characterised by $J=|K/2-S_d|$, which gives $J^2=J(J+1)=(|K/2-S_d|)(|K/2-S_d|+1)$. We define $\Delta=(K/2-S_d)$ to quantify the deviation from exact screening; $\Delta=0$ represents the exactly screened problem, and $\Delta>0$ and $\Delta<0$ represents the overscreened and underscreened problems respectively. Among the degenerate ground state, the maximum quantum fluctuation will occur in the state with minimum \(|J^z|\). Since \(J\) can actually be written as \(J = |\Delta|\), \(J\) will take integer values when \(\Delta\) is integer, and the minimum value of \(|J^z|\) is then zero. Otherwise, when \(\Delta\) is half-integer, \(J\) will also take half-integer values, and the minimum value of \(|J^z|\) is \(1/2\). With these considerations, the minimum value of the quantum fluctuation, {\it per channel}, is
\begin{equation}
q_K = \frac{1}{K}\sqrt{Q_\text{max}} = \frac{1}{K}\sqrt{\langle \psi_g | J^2 - |J^z|_{min}^2 |\psi_g\rangle} = \begin{cases}
	\frac{1}{K}\sqrt{(|K/2-S_d|)(|K/2-S_d|+1)-1/4}, & \text{ where }\Delta\text{ is half-integer}\\
	\frac{1}{K}\sqrt{(|K/2-S_d|)(|K/2-S_d|+1)}, & \text{ where }\Delta\text{ is integer}
\end{cases}
\end{equation}
This expression is symmetric under the transformation \(\Delta \to -\Delta\), and represents a duality between the overscrened and underscreend models. In the limit of large channel number \(K\), \(q_K\) simplifies to $\lim_{K\rightarrow \infty} q_K= \lim_{K \to \infty}\frac{1}{2K}|\Delta(K)|$. Only the over- and under-screened models have non-vanishing (and equal) values of \(q_K\).

\subsection{Staggerred magnetization of the star graph}
 Another probe to study the screening as a function of \(K\) is the staggered magnetization \(\vec{M}_s=\vec{S}-\vec{S}_d\). One can rewrite the Hamiltonian as $\vec{S}_d\cdot\vec{S}= \frac{1}{4}[J^2 - M_s^2]$. Since \(J\) and \(M_s\) commute with each other and hence also with the Hamiltonian, the eigenvalues of $\vec{J}^2$ and \(M_s^2\) act as good quantum numbers for in the ground states of the star graph model. The larger the value of \(\left<M_s^2\right>\), the stronger is the screening in that ground state. For single-channel case with $K=1$, the ground state is a unique 2-spin singlet $|\psi_g\rangle =\frac{1}{\sqrt{2}} (|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle = |J=0,J_z=0\rangle$, and the staggered magnetization per direction is \(M_s^2/3 = 1\), which shows the perfect screening.

Calculating the staggered magnetization for a general multichannel problem with \(K\) channels and a spin-\(S_d\) impurity reveals the breakdown of screening brought about by the presence of multiple channels. We find, in general, that the square of the staggered magnetization per channel is
\begin{equation}
	m_s^2 = \left< \left(\frac{1}{K}M_S\right)^2\right> = \frac{1}{K^2}\langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \frac{1}{K^2}\langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle = \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}
\end{equation}

\begin{figure}
\includegraphics[width=0.7\textwidth]{plt/all/Staggered_mag_50.png}
\caption{This shows how the staggered magnetization changes with the number of channels $N_{ch}$.}
\label{fig:st_mag}
\end{figure}
This shows that as the number of channels increases, the value of \(m_s^2\) decreases from the perfectly-screened value of 3. For \(K \to \infty\) and keeping \(S_d\) finite, \(m_s^2\) approaches a lowered value of \(1/4\).

Due to the $SU(2)$ symmetry of the problem, the staggered magnetisation is the same along each of the three directions, such that the total value \(m_s^2\) is three times the value in any particular direction:
\begin{eqnarray}
\langle(m_s^x)^2\rangle=\langle(m_s^y)^2\rangle=\langle(m_s^z)^2\rangle=\frac{1}{3}m_s^2~,~~   
\end{eqnarray}
As mentioned above, the single channel case displays a value of $\langle (m_s^z)^2 \rangle =1$, showing the perfect screening. If one takes the limit of \(K \to \infty\) keeping \(S_d = K/2\), we get the staggered magnetisation at exact-screening and large \(K\), and the value is $\langle (m_s^z)^2 \rangle =1/4$. This is reduced from the value at \(K=1\). This reduced value however is still greater than the value of \(1/12\) reached as \(K\to \infty\) away from exact-screening by keeping \(S_d\) finite. These conclusions can be easily understood from fig.\ref{fig:st_mag} where we have shown the variation of \(\left<m_s^2 \right>\) as a function of \(K\), keeping \(S_d=1/2\).

\subsection{Thermodynamic quantitites}

\subsubsection{Impurity magnetization in terms of parity operators}
Just like the complete string operator \(\pi^z\), the modified string operator \(\sigma_d^z \pi^z\) is also a Wilson loop operator that wraps around only the outer nodes of the star graph:
\begin{equation}\begin{aligned}
	\pi^z_c \equiv \sigma_d^z \pi^z = \exp\left[i \frac{\pi}{2} \left(\sum_{l=1}^K \sigma^z_l - K\right)\right] 
\end{aligned}\end{equation}
The expectation value of the impurity magnetization along a particular direction and in specific ground states can be related to the 't Hooft operator. We will work in the state comprised of two adjacent eigenstates of \(J^z\):
\begin{equation}\begin{aligned}
	\ket{g^\theta_{J^z}} \equiv \frac{1}{\sqrt 2}\left( \ket{J^z} + e^{i\theta}\ket{J^z+1}\right), && J^z < \frac{1}{2}\left( K-1 \right)
\end{aligned}\end{equation}
The expectation value of the impurity magnetization operator \(\sigma_d^x\) can be expressed as
\begin{equation}\begin{aligned}
	\left<\sigma_d^x\right> \equiv \langle g^\theta_{J^z} \vert \sigma_d^x \vert g^\theta_{J^z}\rangle = - \langle J^z + 1 \vert \pi^x_c \vert -J^z \rangle + \text{h.c.}
\end{aligned}\end{equation}
This expression relates the observable impurity magnetization to the topological 't Hooft operator \cite{Maric2020}. Evaluating the matrix elements gives
\begin{equation}\begin{aligned}
	\label{sigmax}
	\left<\sigma_d^x\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\cos \theta
\end{aligned}\end{equation}
Performing a similar calculation reveals that the impurity magnetizations along \(y\) and \(z\) in the same state are given by
\begin{equation}\begin{aligned}
	\label{sigmayz}
	\left<\sigma_d^y\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\sin \theta, &&\left<\sigma_d^z\right> = - \frac{2J^z + 1}{(1+K)}
\end{aligned}\end{equation}
Combining eqs.~\ref{sigmax} and \ref{sigmayz}, we find
\begin{equation}\begin{aligned}
	\cos^2\theta\left(\left<\sigma^x_d\right>\right)^2 + \sin^2\theta\left(\left<\sigma^y_d\right>\right)^2 + \frac{1}{4}\left(\left<\sigma^z_d\right>\right)^2 = \frac{1}{4}\left(\frac{K}{1+K}\right)^2
\end{aligned}\end{equation}
This relation \textit{constrains the values of the magnetization} along all the directions: the \(x\) and \(y\) magnetization values have already been shown to be related to the `t Hooft operators \(\pi^x\) and \(\pi^y\) and the magnetization along \(z\) is therefore constrained in terms of the `t Hooft operators and the quantized function on the right-hand side (the function is quantized because \(K\) can only take integer values).

\subsubsection{Thermal entropy}
The star graph model can be solved to obtain the partition function, and this then allows the computation of the Helmholtz free energy and hence the thermal entropy:
\begin{equation}
\mathcal{F}= -k_B T\log Z, ~ ~ ~ S = -\frac{\partial \mathcal{F}}{\partial T} = -k_B \log Z -k_B T \frac{1}{Z} \frac{dZ}{dT} = -k_B \log \sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon}  -\frac{1}{\beta} \frac{k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   }{\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon}}
\end{equation}
where \(d(\epsilon)\) is the degeneracy of the state at energy \(\epsilon\). The high and low temperature limits take very simple forms:
\begin{equation}
\lim_{\beta\rightarrow \infty} S = -k_B \log_2 d(\epsilon_{G})~,~~\lim_{\beta\rightarrow 0} S = -k_B \log \sum_\epsilon d(\epsilon)
\end{equation}

In fig.\ref{fig:thermal_entropy}, we plot the thermal entropy (in units of $k_B \log 2$) for a range of temperatures and for different values of \(K\). At large temperatures, \(S\) saturates to integer multiples of \(k_B \log 2\), while at low temperature, that is not always the case. This is because the total Hilbert space dimension \(\sum _\epsilon d(\epsilon)\) is simpy \(2^N\) (\(N\) being the total number of 1-particle states in the Hilbert space), and therefore \(\log \sum _\epsilon d(\epsilon) = N \log 2\) is always an integer multiple of \(N\). On the other hand, the ground state degeneracy \(d(\epsilon_G)\) is \(|K - 2 S_d|\) which is not necessarily of the form \(2^N\) and hence does not always lead to an integer multiple of \(\log 2\).

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{plt/all/ThermalEntanglementVS_LogTemperature_}
\caption{This shows the variation of thermal entropy with the temperature.}
\label{fig:thermal_entropy}
\end{figure}

\section{Additional Topological Features of the Local Mott liquid}

The all-to-all Hamiltonian obtained by resolving the impurity-bath quantum fluctuations is written in terms of the spinor spin operators which are individually made out of two electronic degrees of freedom.
\begin{equation}\begin{aligned}
H_{eff} 
 =\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)   
\label{eq:all-to-all_1}
\end{aligned}\end{equation}
where \(\beta_{\uparrow} ({\mathcal{J}},\omega_{\uparrow})= ({\mathcal{J}}^2 \Gamma_{\uparrow})/2, ~ ~\Gamma_{\uparrow}=(\omega_{\uparrow}-{\mathcal{J}}(S_d^z-1))^{-1}\). This spin operator is defined as $\vec{S}_i=\frac{\hbar}{2} \displaystyle\sum_{\substack{ \alpha,\beta\in \{\uparrow,\downarrow\}}}  c_{0\alpha}^{(i)\dagger} \vec{\sigma}_{\alpha\beta} c_{0\beta}^{(i)}$. In the above eq.\eqref{eq:all-to-all_1} we see the $U(1)$ symmetry of the effective Hamiltonian. Using the spinor repersentation, we obtain the spin creation operation in terms of the electronic degree of freedom:
\begin{equation}
S_i^+ = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{+}_{\alpha\beta} c_{0\beta}^{(i)}
=\frac{\hbar}{2} c_{0\uparrow}^{(i)\dagger} c_{0\downarrow}^{(i)}, ~ ~ ~S_i^z = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{z}_{\alpha\beta} c_{0\beta}^{(i)} =\frac{\hbar}{2} (c_{0\uparrow}^{(i)\dagger} c_{0\uparrow}^{(i)} - c_{0\downarrow}^{(i)\dagger} c_{0\downarrow}^{(i)} )~,
\end{equation}
This spinor is simply the Anderson pseudospin formulation in the spin channel. The spin-creation opertor ($S_i^+$) involves the simultaneous creation of an electron-hole pair at the real space origin of the $i^{th}$ conduction channel. The condensation of such electron-hole pairs has already been shown in ~\cite{anirbanmott1,anirbanmott2}. Thus, for this effective Hamiltonian, one can define twist-translation operations to construct the gauge theory and unveil any hidden degeneracy.

Let's recall the effective Hamiltonian
\begin{eqnarray}
H_{eff} &=& \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{4} \bigg[ \displaystyle\sum_{ij} S_i^+S_j^- ~+ \textrm{h.c.} \bigg]~,
\end{eqnarray}
where $i,j$ are the channel indices. Due to the all-to-all nature of the connectivity, one can draw a total of $K!$ possible unique closed paths ($\mathcal{C}_{\mu}$) such that each node (channel) is touched exactly once. These curves lead to $K!$ translation operators ($\hat{T}_{\mu}$) which keeps the Hamiltonian invariant. Let's define one such translation operator $\hat{T}_{\mu}=e^{i\hat{P}^{cm}_{{\mu}}}$ which gives a periodic shift along the closed path $\mathcal{C}_{\mu}$. The twist operator along the path $\mathcal{C}_{\mu}$ is given by
\begin{eqnarray}
\hat{\mathcal{O}}_{\mu} &=& \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{C}_{\mu}}}^{K} j S_j^z} )~,
\end{eqnarray}
The action of the translation operator on \(S_j^z\) is to translate it by one channel index: $\hat{T}_{\mu} S_j^z \hat T^\dagger_\mu = S_{j+1}^z$ where $j+1$ and $j$ are the nearest neighbor on the closed path $\mathcal{C}_{\mu}$. Then the braiding rule between the twist and translation operators are give as
\begin{equation}
\hat{T}_{\mu}\hat{\mathcal{O}}_{\mu} \hat{T}^{\dagger}_{\mu} \hat{\mathcal{O}}_{\mu}^{\dagger} = \exp\{i[2\pi S_1^z-\frac{2\pi}{K}S^z]\} = \exp\{i[\pm \pi - \frac{2\pi}{K} S^z]\} =\exp(i\frac{2\pi p}{q})
\end{equation}
The availability of the non-trivial braiding statistics between these twist and translation operators is possible if $p\neq 0$ and $q\neq \infty$. Further simplification leads to the condition
\begin{equation}
 \pm\pi -\frac{2\pi}{K} S^z = \frac{2\pi p}{q} \implies  \pm\frac{1}{2}-\frac{S^z}{K} = \frac{p}{q} , ~ ~ ~ \frac{(\pm K-2S^z)}{2K} = \frac{p}{q}~,
\end{equation} 
where $p,q$ are mutual primes. We know that the $S^z$ can take values $(\mp K/2\pm m)$ where $m$ is a integer $0 \leq m \leq K$. Putting this value in the above equation leads to two possible solutions.
\begin{eqnarray}
\frac{(K-m)}{K} &=& \frac{p}{q} ~,~~ \frac{-m}{K}=\frac{p}{q}
\end{eqnarray}
For the first case $K-m=p$ we can see that $m=K$ makes $p$ trivial hus the allowed values are $m=0,\cdots,K-1$, which represents the corresponding $S^z$ eigenvalues 
\begin{eqnarray}
&&-K/2,-K/2+1,\cdots,K/2-2,K/2-1
\end{eqnarray}
Similarly the second case implies, $-m=p$, but $p=0$ is not allowed as this makes the braiding statistics trivial, thus the possible $S^z$ values are 
\begin{eqnarray}
&&\hspace{2.2cm} -K/2+1,-K/2+2,\cdots,K/2-1,K/2
\end{eqnarray}

Thus we get the general braiding statistics between the twist and the translation 
\begin{eqnarray}
\hat{T}_{\mu}\hat{\mathcal{O}_{\mu}} \hat{T}^{\dagger}_{\mu}\hat{\mathcal{O}_{\mu}}^{\dagger} &=& e^{i\frac{2\pi p}{K}}
\end{eqnarray}
where $p$ corresponds to different $S^z$ states, related as $p=\pm K/2-S^z$. Thus we can see that there are $K$ possible $S^z$ plaleau states in the all-to-all model where each plateaux is $K$ fold degenerate. This $p/K$ is similar to the filling factor of the fractional quantum Hall effect. There are possibly $K!$ pairs of twist and translation operator corresponding to different closed paths $\mathcal{C}_{\mu}$ which can probe this degeneracy.

\subsection{Action on the Hamiltonian}
We will now obtain the action of these twist operators on the Hamiltonian in eq.~\ref{eq:all-to-all_1}. Due the all-to-all nature of the effetive Hamiltonian one can find $K!$ possible relative arrangement of those $K$ channels which keeps the Hamiltonian invariant. Here we briefly discuss the choice of the closed loop $\mathcal{C}_{\mu}$ and the insertion of the flux. As shown in the {\color{blue}Fig.\ref{fig:stargraph-to-alltoall}(b)} we have chosen a particular closed path which crosses all the outer spin only once. We embed that closed loop on a plane and put the flux perpendicular to the plane through the closed loop. One can find a different closed loop where the ordering of the outer spins will be different. The action of the translation operator shifts the outer spins along this closed curve by one step.

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.8\textwidth]{./plt/stargraph-to-alltoall.png}
	\caption{(a) Schematic diagram of $8-$channel multichannel Kondo model zero mode in zero bandwidth limit. (b) All-to-all model obtained by disentangling the impurity spin from the bath zero modes. $C_{\mu}$ is a particular closed curve. (c) Translated configuration along the curve $C_{\mu}$ by one unit.}
	\label{fig:stargraph-to-alltoall}
\end{figure}

The action of the twist operator on the $S^x$ is determined in the follwoing calculation
\begin{equation}
\hat{O}_{\mu} S^x \hat{O}^{\dagger}_{\mu} = \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} )S^x \exp({-i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} ) = e^{X} S^x e^{-X}
\end{equation}
For simplicity of thte calculation we define $i\frac{2\pi}{K}=\Omega$, thus $X=\Omega\sum_j jS^z_j$. Thus we get
\begin{equation}
e^X S^x e^{-X}= S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots = \sum_l ( S^x_l \cos \theta_l -  S_l^y \sin \theta_l ) ~,~~~\theta_l=\frac{2\pi l}{K}\\
e^X S^y e^{-X}= \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)
\end{equation}
As already defined, $\theta_l=\frac{2\pi l}{K}=\frac{2\pi (K-n)}{K}$, where $n$ is an integer. We can see that in the large channel limit $\theta_l $ becomes inter multiple of $2\pi$. Thus in the large channel limit
\begin{gather}
 \lim_{K\rightarrow \infty}\hat{\mathcal{O}}_{\mu} H_{eff} \hat{\mathcal{O}}_{\mu}^{\dagger}\nonumber = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[ \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger}  + \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger}  \bigg] = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[  S^{x2}+S^{y2}  \bigg] = H_{eff},\\
 \lim_{K\rightarrow \infty } [\hat{\mathcal{O}},H_{eff}] = 0
\label{eq:hamiltonian_twisted}
\end{gather}

The translation operator $\hat{T}_{\mu}=e^{i\hat{\mathcal{P}}_{\mu}}$ commutes with the Hamiltonian, and hence the generator $\hat{\mathcal{P}}_{\mu}$ also commutes with the Hamiltonian. We can label the $j^{th}$ state with the eigenvalues of this operator $\hat{\mathcal{P}_{\mu}}$ as $|p^{j}_{\mu}\rangle$. The action of these twist and translation operators on these states are
\begin{gather}
\hat{T}_{\mu} |p^j_{\mu} \rangle = e^{i\hat{\mathcal{P}}_{\mu}} |p^j_{\mu} \rangle = e^{ip^j_{\mu}} |p^j_{\mu}\rangle, ~ ~ ~ ~ \hat{T}_{\mu} \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle =  \hat{\mathcal{O}}_{\mu} \hat{T}_{\mu} e^{i\frac{2\pi m}{K}} |p^j_{\mu}\rangle = \hat{\mathcal{O}}_{\mu}   e^{i(\frac{2\pi m}{K}+p_{\mu}^j)} |p^j_{\mu}\rangle~,~~ \frac{2\pi m}{K} \equiv p_{\mu}^{m} \\
\hat{T}_{\mu} \bigg( \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle  \bigg) = e^{i(p_{\mu}^{m}+p_{\mu}^j)} \bigg( \hat{\mathcal{O}}_{\mu}    |p^j_{\mu}\rangle \bigg)    
\end{gather}
where $m$ represents different $S^z$ plateaux. This shows that  $\hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle $ is again an eigenstate of the translation operator, but with an eivenvalue that is different from $|p^j_{\mu} \rangle $, and is thus orthogonal to $\ket{p^j_{\mu}}$. Simiarly one can generally show that $\langle p^j_{\mu} | \hat{\mathcal{O}}^{q}_{\mu} |p^j_{\mu} \rangle=0$, where $q$ is any integer. Also in the large $K$ limit we can see from the eq.\eqref{eq:hamiltonian_twisted} that these differnt twisted states has same energy. Which shows that at each plateau state labeled by the $S^z$ eigenvalue has $K$ fold degenerate eigenstates labeled by the eigenvalue of the translation operators. The complete set of commuting observables is therefore formed by $H,S^z,\hat{T}$, and states can be labeled as  $|E,S^z_j,P^j_{\mu}\rangle$.

\section{Effect of conduction bath excitations on the fixed point theory}
\subsection{Non-Fermi liquid signatures in momentum space for 2-channel Kondo}
Obtaining the effective Hamiltonian involves obtaining the low energy excitations on top of the ground state of the star graph. The large-energy excitations are ones that involve spin flips. This guides the separation of the Hamiltonian into a diagonal and an off-diagonal piece:
\begin{align}
	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_{V + V^\dagger}
\end{align}
We define \(V\) as the interaction term that decreases \(s_\text{tot}^z\) by 1: \(V \ket{s_\text{tot}^z} \to \ket{s_\text{tot}^z - 1}\). Similarly, we define \(V^\dagger \ket{s_\text{tot}^z} \to \ket{s_\text{tot}^z + 1}\). The Schrodinger equation for the ground state can be written as
\begin{widetext}
\begin{align}
	E_\text{gs}\ket{\Psi_\text{gs}} = H \ket{\Psi_\text{gs}} = \left(H_d + V\right)\ket{\Psi_\text{gs}} \implies \left(E_\text{gs} - H_d\right)\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z} = V\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}
\end{align}
\end{widetext}
\(E_\text{gs}\) is the ground state energy, and can be replaced by the star graph ground state energy if we remove the kinetic energy cost via normal ordering: \(E_\text{gs} = -\frac{J}{2}\left(\frac{K}{2}+1\right) \). Since the interaction part \(V\) only changes \(S_d^z \to -S_d^z\) and \(s^z_\text{tot} \to s^z_\text{tot} \pm 1\), we can simplify the equation into individual smaller equations. For the state \((s_\text{tot},s^z_\text{tot}) = (1,0)\), equations are
\begin{align}
	\label{eff_ham_Sdz_10}
	E_\text{gs} \ket{\frac{1}{2}, 1, 0} &= \left(H_d + V \frac{1}{E_\text{gs} - H_d}V^\dagger\right) \ket{\frac{1}{2}, 1, 0}\\
	E_\text{gs} \ket{-\frac{1}{2}, 1, 0} &= \left(H_d + V^\dagger \frac{1}{E_\text{gs} - H_d} V\right) \ket{-\frac{1}{2}, 1, 0}\\
\end{align}
These equations represent the Schrodinger equation for the states \(\ket{S_d^z, 1, 0}\), and the right hand sides therefore give the effective Hamiltonians for those states. If we combine the states into a single subspace \(\ket{1,0}= \left\{\ket{\frac{1}{2}, 1, 0}, \ket{-\frac{1}{2}, 1, 0}\right\}\), the effective Hamiltonian for this composite subspace becomes the sum of the two parts:
\begin{align}
	\label{eff_ham_10}
	H^{1,0}_\text{eff}\ket{1, 0}\bra{1, 0} = \left(H_d + V G_0 V^\dagger + V^\dagger G_0  V\right) \ket{1, 0}
\end{align}
where \(G_0 = \left(E_\text{gs} - H_d\right)^{-1}\). To calculate these effective Hamiltonians, we will expand the denominator in powers of in \(H_0^n/J^{n+1}, n=0,1,2,\ldots\). Expanding up to \(n=2\) and keeping at most two particle interaction terms, 
the effective Hamiltonian is
\begin{widetext}
\begin{align}
	H_\text{eff}^{1, 0} &= H_0 + \frac{J^2}{2\left(E_\text{gs} + \frac{J}{2}\right)}\left[1 + \frac{ H_0 + \left(\frac{1}{2} + S_d^z\right) s^+_\text{tot}X_{1,\text{tot}} - \left(\frac{1}{2} - S_d^z\right) s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 \left(E_\text{gs} + \frac{J}{2}\right)} + \frac{H_0^2}{\left(E_\text{gs} + \frac{J}{2}\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + \frac{J}{2}\right)^3} \right]
\end{align}
\end{widetext}
We employed the definitions 
\begin{equation}\begin{aligned}
X_{n,\text{tot}} \equiv  \sum_l \sum_{k,k^\prime}\left(\epsilon_k - \epsilon_{k^\prime}\right)^n c^\dagger_{k \downarrow}c_{k^\prime \uparrow}, ~ ~ ~ Z_{1,\text{tot}} \equiv \sum_{k,k^\prime,l}\left( \epsilon_k - \epsilon_{k^\prime} \right) \frac{1}{2}\left(c^\dagger_{k \uparrow,l}c_{k^\prime \uparrow,l} - c^\dagger_{k \downarrow,l}c_{k^\prime \downarrow,l}\right)
\end{aligned}\end{equation}
There are several non-Fermi liquid terms of the form \(s^+_\text{tot}X_{1,\text{tot}}, s^-_\text{tot}X^\dagger_{1,\text{tot}},Z_{1,\text{tot}} H_0\). These arise because of the degenerate manifold and the increased availability of states in the Hilbert space for scattering, as compared to the unique singlet ground state of the single-channel Kondo model.

\subsection{Low temperature thermodynamic behaviour}
The non-Fermi liquid (NFL) nature of the effective Hamiltonian can be demonstrated through a calculation of certain thermodyanmic quantities like the impurity specific heat and the magnetic suseptibility. We begin by calculating the self energy of this NFL hamiltonian. In real space one can extract a diagonal piece from the effective Hamiltonian by using the fermionic anticommutation relations.
\begin{eqnarray}
H_{eff}^{off,(2)} |_{diag} &=& -(16t^2/3) [ (S_1^z)^2+ (S_2^z)^2 ] 
\end{eqnarray}
the corresponding momentum space Hamiltonian is obtained from the fouries transform:
\begin{equation}
H_{eff}^{off,(2)} |_{diag}= -\frac{4t^2}{3} \frac{1}{N} \bigg[ \displaystyle\sum_{k,\sigma} n_{k\sigma}(1-\frac{1}{N} \displaystyle\sum_{k_2}  n_{k_2,-\sigma}  ) + \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma} ( 1-\frac{1}{N} \displaystyle\sum_{ k_2} \tilde{n}_{k_2,-\sigma}  ) \bigg]  
\end{equation}
The above relation leads to the self-energy correction to the kinetic energy, which is
\begin{equation}
\bar{\epsilon} _k-\epsilon_k = \Sigma_k = -\frac{4t^2}{3N^2}\bigg(1-\frac{N}{e^{(\epsilon_k-\mu)/k_BT}+1}\bigg)
\label{eq:self-energy-NFL}
\end{equation}
Using the self-energy we calculate the impurity speciftic heat defined as $C_{imp}=C(J^*)-C(0)$ which is defined as
\begin{eqnarray}
C_{imp} &=& \sum_{\Lambda,\sigma} \beta \bigg[ \frac{(\bar{\epsilon}_{\Lambda})^2 e^{\beta \bar{\epsilon}_{\Lambda}}}{( e^{\beta \bar{\epsilon}_{\Lambda}} +1)^2}  -\frac{({\epsilon}_{\Lambda})^2 e^{\beta {\epsilon}_{\Lambda}}}{( e^{\beta {\epsilon}_{\Lambda}} +1)^2} \bigg]
\end{eqnarray}
\begin{figure}[!htb]
\centering
\includegraphics[width=0.7\textwidth]{plt/all/FINAL_fitted_Cv_t_0p1.png}
\caption{This figure shows the variation of the impurity specific heat with the temperature.}
\label{fig:Cv_imp}
\end{figure}
Using the self-energy obtained above, we extract the low-temperature behaviour of the impurity specific heat in the two-channel model for $t=0.1$ and $\mathcal{J}=1$, and it is shown in fig,~\ref{fig:Cv_imp}. We find that at low temperatures, the Sommerfield coefficient \(C_\text{imp}/T\) follows a logarithmic behavior for the two-channel case, which is in agreement with the results known in the literature [CITE].
\begin{eqnarray}
\frac{C_{imp}}{T} \propto \log T
\end{eqnarray}

To calculate the magnetic susceptibilty, we numerically diagonalise the low-energy effective Hamiltonain, and use the following expression:
\begin{eqnarray}
\chi &=& \beta\bigg[\frac{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} \langle \bar{S}^{z2} \rangle}{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} } -\frac{\sum e^{-\beta \epsilon_{\Lambda}} \langle S^{z2 }\rangle }{\sum e^{-\beta \epsilon_{\Lambda}} } \bigg] 
\end{eqnarray}
\begin{figure}[!htb]
\centering
\includegraphics[width=0.7\textwidth]{plt/all/NFL_Chi_log_0p1}
\caption{Suseptibility}
\label{fig:NFL_susecptibility}
\end{figure}
The result is shown in fig.~\ref{fig:NFL_susecptibility}, and we find that at low tempertures, the suseptibility has a logarithmic behavior.
\begin{eqnarray}
\chi(T) &\propto& \log T
\end{eqnarray}

We also calculated the Wilson ratio $C_{imp}/T\chi$, and we find that taking upto three sites on each conduction channel leads to a value of $ W = 8.3$, which is greater than the known value of \(8/3\). We find that taking less number of sites leads to a lower value of \(W\), which shows that taking more number of sites will lead to a value of \(W\) that is lower than \(8.3\) and closer to \(8/3\).

\subsection{Three channel LEH}
Similar to the two channel case, we here calculate the low energy effective Hamiltonain for three channel Kondo problem by introducing the real space hoppting on top of the zero mode three-channel stargraph model. This zero mode three channel stargraph model has three fold degenerate ground states with total $2^4=16$ states in the eigen spectrum. The three degenerate ground states are given as 
\begin{eqnarray}
|\alpha_{-1}\rangle &=& c|1000 \rangle-b (|0100 \rangle + |0010 \rangle+ | 0001 \rangle) \nonumber\\
|\alpha_{+1}\rangle &=& b(|1110 \rangle+ | 1101 \rangle + | 1011 \rangle)-c | 0111 \rangle \nonumber\\
|\alpha_0\rangle &=& -a(|1100 \rangle + |1010\rangle +|1001 \rangle)\nonumber\\
&&~~~~~~~+a(|0110 \rangle+| 0101 \rangle +| 0011\rangle)
\end{eqnarray}
where $a=0.408$, $b=0.289$, $c=0.866$. Here the state is represented by $|n_{d},n_1,n_2,n_3\rangle$, where $n_i=1/0$ represents the spin configuration $S_i^z=\pm 1/2$ respectively. Next we use degenerate perturbation theory to get the LEH which contains diagonal and off-diagonal terms. In this case we get non-zero contribution from all the three ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$. We get the diagonal contribution to the LEH in the second order to be
\begin{eqnarray}
H^{(2)}_{eff, diag} &=& - \frac{7.2 J^2}{\alpha} \hat{I}
\end{eqnarray}
The contribution associater to different ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$ is given respectively as $- \frac{2.4 J^2}{\alpha} \hat{I} + \hat{\mathcal{F}},- \frac{2.4 J^2}{\alpha} \hat{I} ,- \frac{2.4 J^2}{\alpha} \hat{I} - \hat{\mathcal{F} }$,
where $\hat{\mathcal{F}}$ is a function of diagonal number oprators of sites nearest neighbor to the zeroth site of each channels. The off-diagonal terms in the LEH is appearing due to the scattering between pair of degenerate states $(\alpha_0,\alpha_{+1})$ and $(\alpha_0,\alpha_{-1})$, there is no contribution in the second order coming from the scattering between $(\alpha_{-1},\alpha_{+1})$. The effective low energy Hamiltonian in the second ordere is given as

\begin{widetext}
\begin{eqnarray}
H^{(2)}_{eff,off-diag} &=& \sum_{\substack{(ijk)=\\(123),(231),(312)}}\bigg[ c_{i\uparrow}c_{i\downarrow}^{\dagger} \bigg( -2ab \bigg\{ \Sigma_{jk} +c_{j\uparrow}^{\dagger}c_{j\downarrow}c_{k\uparrow}c_{k\downarrow}^{\downarrow} \bigg\} -ac(\Omega_{jk}+\tilde{\Omega}_{jk}) \bigg) + ~~\textrm{h.c.}\bigg] \otimes \hat{\Xi}_l
\end{eqnarray}
\end{widetext}
where different operators are defined as
\begin{gather}
\Sigma_{i,j} = n_{i\uparrow}(1-n_{i\downarrow}) (1-n_{j\uparrow})n_{j\downarrow} + (1-n_{i\uparrow})n_{i\downarrow} n_{j\uparrow} (1 -n_{j\downarrow}), ~ ~\Omega_{i,j} =4S_i^z S_j^z n_{i\uparrow} n_{j\uparrow}, ~ ~ \tilde{\Omega}_{i,j} = 4S_{i}^zS_j^z (1-n_{i\uparrow})(1-n_{j\uparrow}) \nonumber\\
 \hat{\Xi}_l=  ( c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.})
\end{gather}

\section{Hamiltonian RG of spin-\(S\) impurity MCK Model}
\label{appendix_urg}
The Hamiltonian for the channel-isotropic MCK model is:
\begin{gather}
	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\beta= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~,~~
\end{gather}
As mentioned in the same section, the Hamiltonian \(H_{(j-1)}\) of the \((j-1)^\text{th}\) RG step is obtained from the Hamiltonian \(H_{(j)}\) of the preceding RG step by applying a unitary transformation \(U_{(j)}\): \(H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}\). The unitary transformation is obtained in terms of the fermionic operator \(\eta_{(j)}\):
\begin{gather}
	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~, \\
	\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)},~T_{(j)} \equiv \text{Tr}\left(H_{(j)}c_{j}\right)~,\\
	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} T_{(j)}~.
\end{gather}
The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms of the Hamiltonian.

The URG equation for the single-channel Kondo model \cite{kondo_urg} shows a stable strong coupling fixed point. Ferromagnetic interactions are irrelevant. Strictly speaking, that RG equation already encodes, in principle, the multi-channel behaviour, through a modified \(\hat \omega\). To extract this information, we consider the strong coupling fixed-point \(J \gg D\) as a fixed point and analyze its stability from the star graph perspective. For the exactly-screened case, the star graph decouples from the conduction bath, leaving behind a local Fermi liquid interaction on the first site. Similarly, in the under-screened regime, the ground state is composed of states where the impurity spin is only partially screened by the conduction channels. If a particular configuration of the bath-impurity system has the total conduction bath spin down, the impurity will have a residual up spin. This induces a ferromagnetic super-exchange coupling that is irrelevant under RG, so this fixed point is stable as well.

We now come to the over-screened case, where there is a residual spin on the conduction channel site. The neighbouring electrons will now hop in with spins opposite to that of the impurity, so an antiferromagnetic interaction will be induced, and such an interaction is relevant under the RG. This shows that the over-screened regime cannot have a stable strong coupling fixed point, and we need to search for an intermediate coupling fixed point. We therefore need the generator of the unitary transformation that incorporates third order scattering scatterings explicitly. We should take account of all possible processes that render the set of states \(\left\{\ket{\hat n_{q\beta}=1},\ket{\hat n_{q\beta}=0}\right\}\) diagonal. The higher order generator itself has two scattering processes, such that the entire renormalisation term \(c^\dagger_{q\beta} T \eta\) has in total three coherent processes. The complete generator upto third order can be written as
\begin{widetext}
\begin{equation}\begin{aligned}
	\eta = \frac{1}{\hat \omega - H_D}T^\dagger c \simeq \frac{1}{\omega^\prime - H_D}T^\dagger c + \frac{1}{\omega^\prime - H_D}H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X
\end{aligned}\end{equation}
where \(H_X = J \sum_{k,k^\prime < \Lambda_j, \alpha,\alpha^\prime}\vec{S_d}\cdot\vec{s}_{\alpha \alpha^\prime}c^\dagger_{k\alpha}c_{k^\prime\alpha^\prime}\) is scattering between the entangled electrons. There are two third order terms in the above equation corresponding to the two possible sequences in which the processes can occur while keeping the total renormalisation \(c^\dagger_{q\beta}T \eta\) diagonal in \(q\beta\). The second order processes remain unchanged. The total renormalisation takes the form:
\begin{equation}
	\label{full_ren}
	\Delta H_{(j)} = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c  + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(2)}_{(j)}} + \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(3)}_{(j)}}
\end{equation}
\(\Delta H^{(2)}_{(j)}\) and \(\Delta H^{(3)}_{(j)}\) are the renormalisation arising from the the second and third order processes respectively.

It is easier to see the RG flow of the couplings if we write the Hamiltonian in terms of the eigenstates of \(S_d^z\). These eigenstates are defined by \(S_d^z\ket{m_d} = m_d\ket{m_d}, m_d \in \left[-S, S\right]\). In terms of these eigenstates, the Hamiltonian becomes
\begin{equation}\begin{aligned}
	\label{H_spin_S}
	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{m_d=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_{m_d} \ket{m_d}\bra{m_d} c^\dagger_{k \sigma}c_{l \sigma} + \sum_{kl} \sum_{m_d=-S}^{S-1} J^t_{m_d} \left(\ket{m_d+1}\bra{m_d} s^-_{kl}  + \text{h.c.}\right)
\end{aligned}\end{equation}
\end{widetext}
where \(k,l\) sum over the momentum states, \(\sigma\) sums over the spin indices, \(J^\sigma_m = \frac{1}{2} \sigma m J\) in the UV Hamiltonian, and \(J^t_{m} = J\frac{1}{2}\sqrt{S(S+1) - m(m+1)}\) is the coupling that connects \(\ket{m}\) and \(\ket{m+1}\). We first calculate \(\Delta H^{(2)}_{(j)}\). There will be two types of processes - those processes that start from an occupied state (particle sector) and those that start from a vacant state (hole sector). Due to particle hole symmetry of the Hamiltonian, they will be equal to each other and we will only calculate the particle sector contribution.

In the particle sector, we have (\(\hat n_{q\beta}=1\)), so we will work at a negative energy  shell \(\epsilon_q = -D\). The renormalisation can schematically represented as \(H^I_0 \frac{1}{\omega - H^D_{q\beta}} H^I_1\). Both \(H^I_0\) and \(H^I_1\) have all three operators \(S_d^z, S_d^\pm\). We first consider specifically the case of spin-\(\frac{1}{2}\) impurity. Those terms that have identical operators on both sides can be ignored because \({S_d^z}^2 = \text{constant}\) and \({S^\pm}^2 = 0\). All the six terms that \textit{will} renormalise the Hamiltonian have a spin flip operator on at least one side of the Greens function. This means that in the denominator of the Greens function, \(S_d^z\) and \(s^z_{qq}\) have to be anti-parallel in order to produce a non-zero result for that term. This means we can identically replace \(S_d^z s^z_{qq} = -\frac{1}{4}\). Also, in the particle sector, the Greens function always has \(c_{q\beta}\) in front of it, so \(\epsilon_q \tau_{q\beta} = \frac{D}{2}\). The upshot of all this is that the denominator of all scattering processes for the spin-\(\frac{1}{2}\) impurity Hamiltonian will be \(\omega - \frac{D}{2} + \frac{J}{4}\).

We now come to the general case of spin-\(S\) impurity. The various terms that renormalise the Hamiltonian can be described in terms of the bath spin operators that come into them. For example, the term that has \(s^z\) on both sides of the intervening Greens function can be represented as \(z|z\). There are 7 such terms: \(z|z, \pm|\mp, z|\pm, \pm|z\). Each of these terms occur both in the particle and the hole sectors. We will demonstrate the calculation of two of these terms. The \(z|z\) \(+|-\) terms evaluate in the following manner.
\begin{widetext}
\begin{align}
	z|z: & \sum_{kk^\prime,m,\sigma} c^\dagger_{q \sigma} c_{k^\prime \sigma} \ket{m}\bra{m}\frac{{J^\sigma_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}\sigma S_d^z}\ket{m}\bra{m} c^\dagger_{k \sigma}c_{q \sigma} = -\sum_{kk^\prime,m,\sigma}n_{q \sigma}\frac{{J^\sigma_m}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma} \ket{m}\bra{m}}{\omega_{m, \sigma} - \frac{D}{2} + \frac{J}{2}\sigma m}\\
	+|-: & \sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m+1, \uparrow} - \frac{D}{2} + \frac{J}{2}\left( m+1 \right) }
\end{align}
\end{widetext}
We similarly compute the rest of the terms. We again define \(\sum_q \hat n_{q\sigma} = n(D)\). To compare with the spin-\(\frac{1}{2}\) RG equations, we will transform the general spin-\(S\) \(\omega\) to the spin-\(\frac{1}{2}\) \( \omega\), using \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).

The renormalisation in \(J^\sigma_m\) is
\begin{equation}\begin{aligned}
	\Delta J^\sigma_{m} = - n(D) \frac{\left( J^\sigma_m \right) ^2 + \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
\end{aligned}\end{equation}
Here, we have defined \(J^t_m = 0\) for \( |m| > S\). Two relations can be obtained from this RG equation, the RG equations for the sum and difference of the couplings: \(J^\pm_m = \frac{1}{2}\left(J^\uparrow_m \pm J^\downarrow_m\right) \). The RG equation for the sum of the couplings is
\begin{equation}\begin{aligned}
	\Delta J^+_m = -n(D)\frac{\sum_\sigma \left( J^\sigma_m \right) ^2 + \sum_\sigma \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{2\left(\omega - \frac{D}{2} + \frac{J}{4}\right)}\\
	= -n(D)\frac{J^2}{4}\frac{S(S+1)}{\omega - \frac{D}{2} + \frac{J}{4}}
\end{aligned}\end{equation}
This is an \(m-\)independent piece, so it can be summed over to produce an impurity-independent potential scattering term, which we ignore.

The second is the RG equation for the difference of the couplings:
\begin{equation}\begin{aligned}
	\Delta J^-_m = -n(D)\frac{1}{2}\frac{\left( J^t_{m-1} \right) ^2 - \left(J^t_{m}\right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{4}\frac{n(D) m J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
\end{aligned}\end{equation}
The usual \(J\) Kondo coupling is recovered through \(J = 2J^-_m/m\). Substituting this gives 
\begin{equation}\begin{aligned}
	\Delta_\text{p sector} J = -\frac{1}{2}n(D)\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
\end{aligned}\end{equation}

We can also obtain the RG equation for \(J\) from the transverse renormalisation:
\begin{equation}\begin{aligned}
	\Delta J^t_m &= - \frac{n(D)J^t_m \left( J^\downarrow_m + J^\uparrow_{m+1} \right) }{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{2}\frac{n(D)J^t_m J}{\omega - \frac{D}{2} + \frac{J}{4}}
\end{aligned}\end{equation}
Since \(J^t_m \propto J\), we have
\begin{equation}\begin{aligned}
	\Delta J_\text{p sector} &= -\frac{1}{2}\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
\end{aligned}\end{equation}
The total renormalisation from both particle and hole sectors, at this order, is
\begin{equation}\begin{aligned}
	\Delta J^{(2)} &= -\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
\end{aligned}\end{equation}

We now come to the third order renormalisation.
Following eq.~\ref{full_ren}, the next order renormalisation is
\begin{equation}\begin{aligned}
	\label{psector_3rd_ren}
	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c \\
	+ c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X
\end{aligned}\end{equation}
The first term will be of the form
\begin{widetext}
\begin{equation}\begin{aligned}
	\sum_{q,k,l_1} c^\dagger_{q\beta, l_1}c_{k \alpha, l_1}\ket{m_1}\bra{m_2} \frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z} \ket{m_2} c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \bra{m_3}\frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z}\ket{m_3}\bra{m_4}c^\dagger_{k\alpha, l_1}c_{q\beta, l_1}
\end{aligned}\end{equation}
\end{widetext}
We have not bothered to write all the summations and the couplings correctly, because we will only simplify the denominator here. Evaluating the inner products gives
\begin{equation}\begin{aligned}
	\sum_{qk,l_1} \frac{\ket{m_1}\bra{m_4}c^\dagger_{q\beta}c_{k \alpha}c^\dagger_{k_1 \sigma_1, l_2}}{\omega_{m_2,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_2}{4}}  \frac{c_{k_2 \sigma_2,l_2}c^\dagger_{k\alpha}c_{q\beta}}{\omega_{m_3,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_3}{4}}
\end{aligned}\end{equation}
We again use \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).
\begin{equation}\begin{aligned}
	\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}\sum_{qk,l_1} \frac{\hat n_{q\beta}\left(1 - \hat n_{k\alpha}\right)}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2}
\end{aligned}\end{equation}
We define \(\sum_q \hat n_{q\beta} = n(D)\). Performing the sums over \(k\) and \(l_1\) gives
\begin{equation}\begin{aligned}
	-\frac{1}{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}
\end{aligned}\end{equation}
\(\rho\) is the density of states which we have taken to be constant. Reinstating the complete summation and the couplings gives
\begin{equation}\begin{aligned}
	\label{first_group}
	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{2}\lambda_{3}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}
\end{aligned}\end{equation}
There is no sum over \(m_2\) and \(m_3\) because they are constrained by \(m_1\) and \(m_4\) respectively. \(\lambda_i\) represent the couplings present at the three interaction vertices. \(k_{1,2}\) sum over the momenta, \(\sigma_{1,2}\) sum over the spin indices and \(l_2\) sums over the channels.

The second term in eq.~\ref{psector_3rd_ren} can be evaluated in an almost identical fashion. The integral here be negative of the first term, because of an exchange in the scattering processes.
\begin{equation}\begin{aligned}
	\label{second_group}
	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{3}\lambda_{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}
\end{aligned}\end{equation}

The first group of terms (those that appear in \ref{first_group}) in the particle sector can be represented as \(a|b^\prime|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three ceonnected processes. The \(\prime\) on \(b\) indicates that it is the state of the electrons \textit{not being decoupled}. The second group of terms (those that appear in \ref{second_group}) are therefore represented as \(a|b|c^\prime\), because in this group, the interaction \(H_X\) between the electrons that are not being decoupled occur at the very end.
We will only calculate the terms in the particle sector, the ones in hole sector will be equal to these because of particle-hole symmetry. The full list of terms is: 
$z|z^\prime|z\quad$
$z|z|z^\prime\quad$
$-|z^\prime|+\quad$
$-|+|z^\prime\quad$
$+|z^\prime|-\quad$
$+|-|z^\prime\quad$
$ z|+^\prime|z\quad$
$z|-^\prime|z\quad$
$+|+^\prime|-\quad$
$-|+^\prime|+\quad$
$z|z|+^\prime\quad$
$z|z|-^\prime\quad$
$ +|-|+^\prime\quad$
$+|-|-^\prime\quad$
$-|+|+^\prime\quad$
$z|z^\prime|z\quad$
$z|z|z^\prime\quad$
$-|z^\prime|+\quad$
$ -|+|z^\prime\quad$
$+|z^\prime|-\quad$
$+|-|z^\prime\quad$
$z|+^\prime|z\quad$
$z|-^\prime|z\quad$
$+|+^\prime|-\quad$
$-|+^\prime|+\quad$
$z|z|+^\prime\quad$
$z|z|-^\prime\quad$
$+|-|+^\prime\quad$
$+|-|-^\prime\quad$
$-|+|+^\prime\quad$
.

The total renormalisation in  \(J^\sigma_m\) is
\begin{widetext}
\begin{equation}\begin{aligned}
	\Delta J^\sigma_m = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\left[\left( J^t_{m-1} \right)^2 J^\sigma_m + \left( J^t_m \right)^2 J^\sigma_m - \left( J^t_{m-1} \right)^2 J^\sigma_{m-1} - \left(J^t_m\right)^2 J^\sigma_{m+1} \right] = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3 m \sigma
\end{aligned}\end{equation}
Since we had defined \(J^\sigma_m \equiv \frac{1}{2}J m \sigma\), we have \(\Delta J = \frac{2}{m\sigma}\Delta J^\sigma_m\), and we get \(\Delta_\text{p sector} J = \frac{1}{4}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3\).
Combining with the hole sector renormalisation, we get
\begin{equation}\begin{aligned}
	\Delta J^{(3)} = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3
\end{aligned}\end{equation}
The total renormalisation in \(J\) after combining all orders is
\begin{equation}\begin{aligned}
	\Delta J = -\frac{n(D) J^2}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3
\end{aligned}\end{equation}
\end{widetext}

\bibliography{mscript_mck_full}
\end{document}

### 2022-04-26 Manuscript26April2022/mscript_mck_full.tex
corrected typos and changed figure names to remove underscores and some other minor changes made by sir

--- 2022-04-26 manuscript/mscript_mck_full.tex
@@
 \affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-\affiliation{Ames Laboratory, Ames, Iowa 50011, USA}
+%\affiliation{Ames Laboratory, Ames, Iowa 50011, USA}
+\author{N. S. Vidhyadhiraja}
+\email{raja@jncasr.ac.in}
+\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
 \author{A. Taraphder}
+\email{arghya@phy.iitkgp.ernet.in}
 \affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
@@
 tsvelickKondoreview,affleck1993exact,affleck1995conformal}, leading to a spin singlet ground state and local Fermi liquid excitations above that ground state~\cite{nozieres1974fermi,hewsonp}.
-The screening manifests as an {\color{blue}initial increase at temperatures below the Kondo temperature, followed by a saturation} of the resistivity of the metal~\cite{Kondo,Zhang2013}, and in the saturation of the impurity contribution to the magnetic susceptibility at low temperatures~\cite{wilson1975,andreiKondoreview,tsvelickKondoreview}.
+The screening manifests as an initial increase at temperatures below the Kondo temperature, followed by a saturation of the resistivity of the metal~\cite{Kondo,Zhang2013}, and in the saturation of the impurity contribution to the magnetic susceptibility at low temperatures~\cite{wilson1975,andreiKondoreview,tsvelickKondoreview}.
 Generalisations of this model are obtained by taking impurities of higher spin~\cite{hewson1993,Noz_blandin_1980,affleck1993exact}, adding interactions between them~\cite{affleck_1992,affleck_ludwig_jones_1992,georges_1999,zarand_chung_2006,
@@
 One can also construct multi-channel Kondo (MCK) models by allowing \(K\) conduction electron channels \( \left(K > 1\right) \) to interact with a spin-\(\frac{1}{2}\) impurity~($S_{d}$)~\cite{Noz_blandin_1980,zawadowski_1980,cox_zawadowski_1998} via a common exchange coupling \(\mathcal{J}\).
-Using conformal field theory~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005}, bosonization~\cite{emery_kivelson,clarke_giamarchi_1993,zarand_2000,vondelft_prl_1998,schofield_1997}, numerical renormalization group~\cite{bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991}, Bethe ansatz~\cite{andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002} and other methods~\cite{sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}, it has been shown that for the overscreened systems \(\left(K > 2S_d\right)\), the low energy physics is of the non-Fermi liquid type, displaying anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (ensuring that temperature is taken to zero before the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
+Using conformal field theory~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005}, bosonization~\cite{emery_kivelson,clarke_giamarchi_1993,zarand_2000,vondelft_prl_1998,schofield_1997}, numerical renormalization group~\cite{bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991}, Bethe ansatz~\cite{andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002} and other methods~\cite{sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}, it has been shown that for the over-screened systems \(\left(K > 2S_d\right)\), the low energy physics is of the non-Fermi liquid type, displaying anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (ensuring that temperature is taken to zero before the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
 This anomalous divergent behaviour is actually a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: it is susceptible to perturbations that introduce channel isotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}.
-This makes the experimental realisation of such states quite challening.
+This makes the experimental realisation of such states quite challenging.
 Nevertheless, several features of the two-channel Kondo model have been reproduced using structural two-level systems~\cite{zawadowski_1980,vladar_1983} interacting with a conduction bath~\cite{cichorek_2005,ralph_buhrman_1992,ralph_ludwig_1994,Iftikhar2015,Zhu2016}.
@@
 
-The role of ground state degeneracy and quantum-mechanical frustration in the MCK problem has not received sufficient attention, even though they play crucial roles in determining the non-Fermi liquid physics and the quantum criticality of the system.
+The importance of ground state degeneracy and quantum-mechanical frustration in the MCK problem has not received sufficient attention, even though they play crucial roles in determining the non-Fermi liquid physics and the quantum criticality of the system.
 This is, at least partially, due to the lack of an intermediate-coupling effective Hamiltonian that describes the low-energy physics of the MCK (i.e., reveals the nature of the excitations).
@@
 To obtain the RG flow of the MCK model, we have employed the recently developed unitary renormalization group (URG) technique~\cite{anirbanurg1,anirbanurg2}.
-The method has been applied on several fermionic and spin problems like the single-channel Kondo model~\cite{kondo_urg}, the kagome antiferromagnet~\cite{santanukagome}, the 1D~\cite{1dhubjhep} and 2D Hubbard models~\cite{anirbanmott1,anirbanmott2}, the reduced-BCS model~\cite{siddharthacpi} as well as other generalised models of interacing electrons with and without translation invariance~\cite{anirbanurg2}.
+The method has been applied on several fermionic and spin problems like the single-channel Kondo model~\cite{kondo_urg}, the kagome antiferromagnet~\cite{santanukagome}, the 1D~\cite{1dhubjhep} and 2D Hubbard models~\cite{anirbanmott1,anirbanmott2}, the reduced-BCS model~\cite{siddharthacpi} as well as other generalised models of interacting electrons with and without translation invariance~\cite{anirbanurg2}.
 The URG proceeds by decoupling number fluctuations in the high energy electronic states.
@@
 We then proceed to studying the low energy effective Hamiltonian for the non-Fermi liquid excitations lying above the degenerate ground state manifold.
-This enables the computation of a plethora of quantities, such as various thermodynamic measures (e.g., pecific heat and susceptibility), many-particle entanglement and the self-energy of the propagating degrees of freedom.
+This enables the computation of a plethora of quantities, such as various thermodynamic measures (e.g., specific heat and susceptibility), many-particle entanglement and the self-energy of the propagating degrees of freedom.
 We also explore various signatures of criticality, and various duality transformations of the MCK Hamiltonian.
@@
 The magnetisation and susceptibility of the star graph model show critical behaviour in the form a discontinuity and a \(T^{-1}\) divergence respectively.
-We also explore the topological properties of the degenerate groundstate manifold of the star graph model using non-local twist and translation operators.
+We also explore the topological properties of the degenerate ground state manifold of the star graph model using non-local twist and translation operators.
 On decoupling the impurity spin from the conduction spin degrees of freedom within the star graph, we obtain an all-to-all Hamiltonian that represents a local Mott liquid phase.
@@
 
-In section \ref{sec:ent_prop}, we study various entanglement signatures (like the von-Neumann entanglement entropy, mutual information, multipartite information, Bures distance) of the low energy fixed-point ground state of the MCK problem, with and without excitaitons.
+In section \ref{sec:ent_prop}, we study various entanglement signatures (like the von-Neumann entanglement entropy, mutual information, multipartite information, Bures distance) of the low energy fixed-point ground state of the MCK problem, with and without excitations.
 They reveal clear distinctions between the single- and MCK problems in the form of discontinuities.
-In \ref{sec:duality}, we discuss two duality transformations that exist for the MCK model - a strong-weak duality and an overscreened-underscreened duality.
-It is found that the transformations are constrained by the fixed point structure, and they impose relations between the underscreened and overscreened models.
+In \ref{sec:duality}, we discuss two duality transformations that exist for the MCK model - a strong-weak duality and an over-screened-under-screened duality.
+It is found that the transformations are constrained by the fixed point structure, and they impose relations between the under-screened and over-screened models.
 In \ref{anisotropic_rg}, we show the robustness of the ground state degeneracy of the star graph model against the impurity-channel coupling anisotropy, and correlate it with a URG treatment of the channel anisotropic MCK.
 The isotropic fixed point is found to be unstable to asymmetry, leading to impurity phase transitions that lead to dramatic changes in the ground state degeneracy.
-For the sake of brevity, some supporting evidence as well as the details of certain lengthy calculations are presented in Supplementary Materials.
+For the sake of brevity, some supporting evidence and details of certain lengthy calculations are presented in Supplementary Materials~\cite{SM}.
 
@@
 The derivation of the RG equation for the over-screened regime \((2S < K)\) of the spin-\(S\)-impurity \(K\)-channel Kondo problem is shown in detail in the Supplementary Materials (CITE).
-On decoupling circular iso-energetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\text{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
+On decoupling circular isoenergetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\text{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
 \begin{equation}\begin{aligned}
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{plt/rg_flow.pdf}
+	\includegraphics[width=0.45\textwidth]{plt/rgflow.pdf}
 	\caption{The three fixed points of the over-screened RG equation. Only the intermediate one is stable.}
@@
 \begin{equation}\begin{aligned}
-	H^* = \sum_l\left[ \sum^*_{k}\epsilon_{k,l} \hat n_{k\alpha,l} + {\mathcal{J}}\sum_{kk^\prime}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}~.\right]
+	H^* = \sum_l\left[ \sum^*_{k}\epsilon_{k,l} \hat n_{k\alpha,l} + {\mathcal{J}}\sum_{kk^\prime}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\right]~.
 \end{aligned}\end{equation}
@@
 \begin{itemize}
-	\item The ground state is achieved for the maximal value of \(S\), \(S=\frac{K}{2}\), and the corresponding minimal value of \(J\), \(J = |\frac{K}{2} - S_d|\).
-The {\bf ground state energy} is therefore
+	\item The ground state is achieved for the maximal value of \(S\), \(S=\frac{K}{2}\), and the corresponding minimal value of \(J\), \(J = |\frac{K}{2} - S_d|\). The ground state energy is therefore 
 \begin{equation}\begin{aligned}
@@
 = \begin{cases}
-	-\mathcal{J}S_d\left(\frac{K}{2} + 1\right), & \text{ when } K \geq 2S_d\\
-	-\mathcal{J}\frac{K}{2}\left(S_d + 1\right), & \text{ otherwise}
+	-\mathcal{J}S_d\left(\frac{K}{2} + 1\right) & \text{ when } K \geq 2S_d, ~\text{ and}\\
+	-\mathcal{J}\frac{K}{2}\left(S_d + 1\right) & \text{ otherwise}~.
 \end{cases}
@@
 	\label{w_loop}
-	\pi^z = \exp\left[i \frac{\pi}{2} \left(\sigma_d^z + \sum_{l=1}^K \sigma^z_l - K\right)\right] = e^{i \pi \left(J^z - \frac{1}{2}K\right)}
+	\pi^z = \exp\left[i \frac{\pi}{2} \left(\sigma_d^z + \sum_{l=1}^K \sigma^z_l - K\right)\right] = e^{i \pi \left(J^z - \frac{1}{2}K\right)}~.
 \end{aligned}\end{equation}
@@
 	\label{gamma}
-	\Gamma = \frac{1}{4}\left[\left( K_0 + 1 \right) ^2 - \left(|\delta| + 1 \right) ^2\right] 
+	\Gamma = \frac{1}{4}\left[\left( K_0 + 1 \right) ^2 - \left(|\delta| + 1 \right) ^2\right]~.
 \end{aligned}\end{equation}
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{plt/deg_of_comp.pdf}
+	\includegraphics[width=0.45\textwidth]{plt/degofcomp.pdf}
 	\caption{Variation of the degree of compensation as we tune the system from under-screening to over-screening. The maximum spin compensation occurs at exact-screening \(\delta=0\).}
@@
 Z(h) &=&\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\bigg[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \frac{{\mathcal{J}}}{4}}\cosh \beta\sqrt{{\mathcal{J}}^2x^M_m/4 + \alpha^2} \nonumber\\
-&&\hspace{2cm}+ 2e^{-\beta {\mathcal{J}}M/2}\cosh \beta h/2\bigg]
+&&\hspace{2cm}+ 2e^{-\beta {\mathcal{J}}M/2}\cosh \beta h/2\bigg]~.
 \end{eqnarray}
@@
 \begin{align}
-	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z^{\prime\prime}(h)}{Z(h)} - \left(\frac{Z^{\prime}(h)}{Z(h)}\right)^2 \right] 
+	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z^{\prime\prime}(h)}{Z(h)} - \left(\frac{Z^{\prime}(h)}{Z(h)}\right)^2 \right] ~.
 \end{align}
@@
 \begin{align}
-	Z &\to 2 r^K_{M_\text{max}} M_\text{max} e^{\beta \frac{J}{2}(M_\text{max} + 1)}\\
-	Z^{\prime \prime} &\to r^K_{M_\text{max}}\left(\frac{\beta }{2(M_\text{max} + \frac{1}{2})}\right)^2 e^{\beta \frac{J}{2}(M_\text{max} + 1)}\Sigma_{M_\text{max}}\\
-	\chi &\to \frac{\beta\Sigma_\text{max}}{2M_\text{max}\left(2M_\text{max}+1\right)^2} = \frac{\beta(K-1)}{12(K+1)} \sim \frac{1}{T}
+	Z &\to 2 r^K_{M_\text{max}} M_\text{max} e^{\beta \frac{J}{2}(M_\text{max} + 1)}~,\\
+	Z^{\prime \prime} &\to r^K_{M_\text{max}}\left(\frac{\beta }{2(M_\text{max} + \frac{1}{2})}\right)^2 e^{\beta \frac{J}{2}(M_\text{max} + 1)}\Sigma_{M_\text{max}}~,\\
+	\chi &\to \frac{\beta\Sigma_\text{max}}{2M_\text{max}\left(2M_\text{max}+1\right)^2} = \frac{\beta(K-1)}{12(K+1)} \sim \frac{1}{T}~.
 \end{align}
@@
 \begin{equation}\begin{aligned}
-	F(h) = -\frac{1}{\beta}\ln Z(h) = -\frac{1}{\beta}\ln\sum_{E_n}e^{-\beta E_n}
+	F(h) = -\frac{1}{\beta}\ln Z(h) = -\frac{1}{\beta}\ln\sum_{E_n}e^{-\beta E_n}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	E_\text{min} = - \frac{J}{4} - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 + |h|J(K-1)}
+	E_\text{min} = - \frac{J}{4} - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 + |h|J(K-1)}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	F^\prime(h\neq 0, T\to 0) =- \frac{2h + J(K-1)\text{sign}(h)}{4\sqrt{\frac{J^2}{4}(K+1)^2 + h^2 + |h|J(K-1)}}
+	F^\prime(h\neq 0, T\to 0) =- \frac{2h + J(K-1)\text{sign}(h)}{4\sqrt{\frac{J^2}{4}(K+1)^2 + h^2 + |h|J(K-1)}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	m = F^\prime(h \to 0^\pm, T\to 0) = \mp \frac{1}{2}\frac{(K-1)}{(K+1)}
+	m = F^\prime(h \to 0^\pm, T\to 0) = \mp \frac{1}{2}\frac{(K-1)}{(K+1)}~.
 \end{aligned}\end{equation}
@@
 	\centering
-	\includegraphics[width=0.49\textwidth]{plt/disc_mag_imp_gen.pdf}
+	\includegraphics[width=0.49\textwidth]{plt/discmagimpgen.pdf}
 	\caption{Behaviour of the impurity magnetization for three values of \(\left(K, 2S\right) = \left(2, 4\right), \left( 3,3 \right), \left(4, 2\right)  \).
@@
 Indeed, we have checked numerically (see fig.~\ref{mag_crit}) that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S\) is the deviation from exact screening.
-
+Some additional results are presented in the Supplementary Materials~\cite{SM}.
 \subsection{Topological properties of ground state manifold}
@@
 \begin{eqnarray}
-\hat{T} &=& e^{i\frac{2\pi}{K} \hat{\Sigma}} ~,~\hat{O} = e^{i\hat{\phi}}~,~~\hat{\Sigma}=[\hat{J}^z-(K-1)/2]
+\hat{T} &=& e^{i\frac{2\pi}{K} \hat{\Sigma}} ~,~\hat{O} = e^{i\hat{\phi}}~,~~\hat{\Sigma}=[\hat{J}^z-(K-1)/2]~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\hat{\phi}=\tan^{-1}(\hat{J}^y(\hat{J}^x)^{-1})
+\hat{\phi}=\tan^{-1}(\hat{J}^y(\hat{J}^x)^{-1})~.
 \end{eqnarray}
-Then we get $[\hat{\phi},\hat{H}]=0$.
+We then get $[\hat{\phi},\hat{H}]=0$.
 We can label the ground states by the eigenvalues of the translation operator $\hat{T}$.
 We can also use the ground states labeled by the eigenvalues of $J^z$ (say $M$).
-Then the ground states are
+The ground states are now written as
 \begin{eqnarray}
-|M_1\rangle,|M_2\rangle,|M_2\rangle,\cdots ,|M_K\rangle
+|M_1\rangle,|M_2\rangle,|M_2\rangle,\cdots ,|M_K\rangle~.
 \end{eqnarray}
-Then the operations of the translation operators on this states are given by
-\begin{eqnarray}
-\hat{T}|M_i\rangle &=& e^{i\frac{2\pi}{K} [M_i-(K-1)/2]} |M_i\rangle = e^{i2\pi\frac{p_i}{K} } |M_i\rangle~,~p_i\in[K]
-\end{eqnarray}
+The operations of the translation operators on this states are then given by
+\begin{equation}
+\hat{T}|M_i\rangle = e^{i\frac{2\pi}{K} [M_i-(K-1)/2]} |M_i\rangle = e^{i2\pi\frac{p_i}{K} } |M_i\rangle~,~p_i\in[K]~.
+\end{equation}
 The braiding rule between the twist and the translation operators is
 \begin{eqnarray}
-\hat{T}\hat{O}\hat{T}^{\dagger}\hat{O}^{\dagger} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},i\hat{\phi}]}=e^{i\frac{2\pi }{K}} \nonumber\\
-\hat{T}\hat{O}^m\hat{T}^{\dagger}\hat{O}^{\dagger m} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},im\hat{\phi}]}=e^{i2\pi \frac{m}{K}}
+\hat{T}\hat{O}\hat{T}^{\dagger}\hat{O}^{\dagger} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},i\hat{\phi}]}=e^{i\frac{2\pi }{K}} ~,\nonumber\\
+\hat{T}\hat{O}^m\hat{T}^{\dagger}\hat{O}^{\dagger m} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},im\hat{\phi}]}=e^{i2\pi \frac{m}{K}}~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\langle M_i| \hat{O}^{m \dagger}  H \hat{O}^m |M_i\rangle =\langle M_i|  H |M_i\rangle 
+\langle M_i| \hat{O}^{m \dagger}  H \hat{O}^m |M_i\rangle =\langle M_i|  H |M_i\rangle ~.
 \end{eqnarray}
@@
 \begin{gather}
-H = {\mathcal{J}} \vec{S}_d.\displaystyle\sum_i \vec{S}_i ={\mathcal{J}} S_d^zS^z + \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+) \nonumber\\
-H_D = {\mathcal{J}} S^z_d S^z~,~~ H_X = \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+)
+H = {\mathcal{J}} \vec{S}_d.\displaystyle\sum_i \vec{S}_i ={\mathcal{J}} S_d^zS^z + \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+) ~,\nonumber\\
+H_D = {\mathcal{J}} S^z_d S^z~,~~ H_X = \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+)~.
 \end{gather}
@@
 \begin{equation}
-\beta_{\uparrow} ({\mathcal{J}},\omega_{\uparrow}) = ({\mathcal{J}}^2 \Gamma_{\uparrow})/2 ~,~~\Gamma_{\uparrow}=(\omega_{\uparrow}-{\mathcal{J}}(S_d^z-1))^{-1}
+\beta_{\uparrow} ({\mathcal{J}},\omega_{\uparrow}) = ({\mathcal{J}}^2 \Gamma_{\uparrow})/2 ~,~~\Gamma_{\uparrow}=(\omega_{\uparrow}-{\mathcal{J}}(S_d^z-1))^{-1}~.
 \end{equation}
@@
 H_{eff} 
- =\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)   
+ =\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)   ~.
 \end{eqnarray}
 In terms of the electronics degree of freedom, it has the form
-\begin{eqnarray}
-&& \frac{ \beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow}) }{4}   \displaystyle\sum_{\substack{i\neq j \\ \alpha_i,\beta_i\in \{\uparrow,\downarrow\}\\ \alpha_j,\beta_j\in \{\uparrow,\downarrow\}}}\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)}    c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)} +\textrm{h.c.}   \nonumber
+\begin{equation}
+\frac{ \beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow}) }{4}   \displaystyle\sum_{\substack{i\neq j \\ \alpha_i,\beta_i\in \{\uparrow,\downarrow\}\\ \alpha_j,\beta_j\in \{\uparrow,\downarrow\}}}\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)}    c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)} +\textrm{h.c.} ~.
 \label{eq:all-to-all_1}
-\end{eqnarray}
+\end{equation}
 The antiferromagnetic case is for $\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{2} <0$.
@@
 \begin{eqnarray}
-H_{eff}   =-|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})| \times(S^+S^{-}+ S^-S^{+}) /4   
+H_{eff}   =-|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})| \times(S^+S^{-}+ S^-S^{+}) /4   ~.
 \end{eqnarray}
@@
 In the largest $S$ sector there are $K+1$ states.
-Defining the dual operator \(\hat \phi\) with the algbera \([\hat{\phi,S^z}]=i\), we get the twist operator $\hat{Q}=\exp(i\hat{\phi}\Phi/\Phi_0)$.
+Defining the dual operator \(\hat \phi\) with the algebra \([\hat{\phi,S^z}]=i\), we get the twist operator $\hat{Q}=\exp(i\hat{\phi}\Phi/\Phi_0)$.
 Applying this operator, we get the twisted Hamiltonian
-\begin{eqnarray}
-H(\Phi) &=& -\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} S^2   +\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} \bigg(S^{z}-\frac{\Phi}{\Phi_0} \bigg)^2 ~,~~
+\begin{equation}
+H(\Phi) = -\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} S^2   +\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} \bigg(S^{z}-\frac{\Phi}{\Phi_0} \bigg)^2 ~.
 \label{eq:flux_spectral}
-\end{eqnarray}
+\end{equation}
 One can thus explore different $S^z$ ground states via such flux tuning mechanism.
@@
 For a $K$ channel star graph problem the ground state is $K$ fold degenerate associated with different $J^z$ values $\{-(K-1)/2,-(K-3)/2,\cdots  ,(K-1)/2 \}$.
-After removing the quantum fluctuations between the impurity spin and the outer spins, we get an all-to-all model (eq.\eqref{eq:flux_spectral}) as the effective Hamltonian.
+After removing the quantum fluctuations between the impurity spin and the outer spins, we get an all-to-all model (eq.\eqref{eq:flux_spectral}) as the effective Hamiltonian.
 The eigenstates of this all-to-all Hamiltonian can be labeled by the eigenvalues of $S^z$.
@@
 Using the twist operator, we can cycle between the various states.
+Some additional topological features of the Mott liquid are presented in the Supplementary Materials~\cite{SM}.
 
@@
 \begin{eqnarray}
-H^{(2)}&=& {\mathcal{J}} \vec{S}_d.(\vec{S}_1+\vec{S}_2)~~,~~\vec{S}_i =  \frac{1}{2}~ c_{i,\alpha}^{\dagger}~ \vec{\sigma}_{\alpha,\beta}~ c_{i,\beta}~~
+H^{(2)}&=& {\mathcal{J}} \vec{S}_d.(\vec{S}_1+\vec{S}_2)~~,~~\vec{S}_i =  \frac{1}{2}~ c_{i,\alpha}^{\dagger}~ \vec{\sigma}_{\alpha,\beta}~ c_{i,\beta}~.
 \label{eq:channel-2-spin}
@@
 Here, $\vec{S}_i=1,2$ represents the spin degree of freedom present at the origin of the $i^{th}$ channel.
-This zeroth-level Hamiltonian has two degnerate ground states labeled by $\ket{J^z=\pm 1/2}$ with energy $-\mathcal{J}$ and $6$ excited states~\cite{kunj_slal_1999}.
+This zeroth-level Hamiltonian has two degenerate ground states labeled by $\ket{J^z=\pm 1/2}$ with energy $-\mathcal{J}$ and $6$ excited states~\cite{kunj_slal_1999}.
 The perturbation Hamiltonian is the real-space hopping:
@@
 \mathcal{H} &=& \frac{{\mathcal{J}}\hbar}{2}~ \vec{S}_d.
-\displaystyle\sum_{i=\{1,2\}} \displaystyle\sum_{\alpha,\beta\in\{\uparrow,\downarrow\}}c_{i\alpha}^{\dagger} \vec{\sigma}_{\alpha\beta} c_{i\beta} + H_X
+\displaystyle\sum_{i=\{1,2\}} \displaystyle\sum_{\alpha,\beta\in\{\uparrow,\downarrow\}}c_{i\alpha}^{\dagger} \vec{\sigma}_{\alpha\beta} c_{i\beta} + H_X~.
 \label{eq:excitation_hamiltonian}
@@
 \label{gstate-set}
-\left\{ \ket{\alpha_i} \right\} = \left\{ \ket{J^z}\otimes\ket{n_{l_1,\uparrow},n_{l_1,\downarrow},n_{l_2,\uparrow},n_{l_2,\downarrow}} \right\}
+\left\{ \ket{\alpha_i} \right\} = \left\{ \ket{J^z}\otimes\ket{n_{l_1,\uparrow},n_{l_1,\downarrow},n_{l_2,\uparrow},n_{l_2,\downarrow}} \right\}~.
 \end{equation}
@@
 \begin{eqnarray}
-H^{(1)} &=& \sum_{ij} |\alpha_i\rangle \langle \alpha_i  | V| \alpha_j \rangle \langle \alpha_j |~\nonumber\\
+H^{(1)} &=& \sum_{ij} |\alpha_i\rangle \langle \alpha_i  | V| \alpha_j \rangle \langle \alpha_j |~.\nonumber\\
 H^{(2)} &=& \sum_{ij} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j |~.
@@
 The off-diagonal part at first order is also zero.
-At second order we get both diagonal and off-diagonal contribitions to the effective Hamiltonian.
+At second order we get both diagonal and off-diagonal contributions to the effective Hamiltonian.
 
@@
 The total diagonal second-order contribution to the effective Hamiltonian is obtained by adding these two contributions, and the result is a trivial shift: $H^{(2)}_\text{diag} = H^{(2)}_\text{diag}\left(\tilde \alpha_0\right) + H^{(2)}_\text{diag}\left(\tilde \alpha_1\right) = -4t^2 \hat{I}$.
-The fact there is no non-trivial diagonal renormalisation to the low-energy excitations shows the absence of (local) Fermi liquid terms, and this occurs becasuse of the exact cancellation of the field terms \(\pm \Omega_l\).
+The fact there is no non-trivial diagonal renormalisation to the low-energy excitations shows the absence of (local) Fermi liquid terms, and this occurs because of the exact cancellation of the field terms \(\pm \Omega_l\).
 
@@
 &=& -\frac{8t^2}{3} [ (S_1^z)^2 c_{2\uparrow}^{\dagger}c_{2\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) \nonumber\\
-&+& (S_2^z)^2 c_{1\uparrow}^{\dagger}c_{1\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) ] + \textrm{h.c.} ~,~~~~
+&+& (S_2^z)^2 c_{1\uparrow}^{\dagger}c_{1\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) ] + \textrm{h.c.} ~.
 \label{eq:hamiltonian_NFL}
@@
 This effective Hamiltonian is purely of the non-Fermi liquid kind, arising due to the degeneracy of the ground state manifold.
-Using this low energy effective Hamiltonian we have calculated different thermodynamic quatitites like susceptibility, specific heat and the Wilson ratio.
+Using this low energy effective Hamiltonian we have calculated different thermodynamic quantities like susceptibility, specific heat and the Wilson ratio.
 The first two measures show logarithmic behavior at low temperatures, in agreement with known results in the literature.
-These results are shown in the supplementary material.
+These results are shown in the Supplementary Material~\cite{SM}.
 
 Following this method, we have also calculated the effective Hamiltonian for the three channel Kondo model.
-We again find the absence of all Fermi liquid terms upto $2^{nd}$ order, and the presence of non-Fermi liquid terms in the off-diagonal part of the effective Hamiltonian, and these are also shown in the supplementary material.
+We again find the absence of all Fermi liquid terms up to $2^{nd}$ order, and the presence of non-Fermi liquid terms in the off-diagonal part of the effective Hamiltonian, and these are also shown in the Supplementary Material~\cite{SM}.
 
@@
 \begin{equation}\begin{aligned}
-	V_\text{eff} = \frac{2t^2}{J}\sum_{l=1,2}\left(\sum_\sigma \hat n_{0\sigma,l}\right) s^+_{0,\bar l}s^-_{1,\bar l} + \text{h.c.}
+	V_\text{eff} = \frac{2t^2}{J}\sum_{l=1,2}\left(\sum_\sigma \hat n_{0\sigma,l}\right) s^+_{0,\bar l}s^-_{1,\bar l} + \text{h.c.}~,
 \end{aligned}\end{equation}
@@
 	\label{k_space_od}
-	\sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \text{h.c.}
+	\sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \text{h.c.} ~.
 \end{aligned}\end{equation}
@@
 	H_\text{eff,MFL} = \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{2t^2e^{i\left(k_1 - k_2\right)a}}{J} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \text{h.c.}\\
-	= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right)
+	= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right)~.
 \end{aligned}\end{equation}
@@
 	\label{mfl_large}
-	H^*_\text{eff,MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)
+	H^*_\text{eff,MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta R_j =- \frac{R_j^2}{\omega - \epsilon_{j}/2 - R_j/8}
+	\Delta R_j =- \frac{R_j^2}{\omega - \epsilon_{j}/2 - R_j/8}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}
+	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}~.
 \end{aligned}\end{equation}
@@
 	\label{self_energy}
-	\Delta \Sigma(\omega) \sim  \bar \omega \ln \frac{N^* \omega}{\bar \omega}
+	\Delta \Sigma(\omega) \sim  \bar \omega \ln \frac{N^* \omega}{\bar \omega}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	Z(\bar\omega) = \left(2 - \ln \frac{2\bar\omega}{N^* \omega}\right) ^{-1}
+	Z(\bar\omega) = \left(2 - \ln \frac{2\bar\omega}{N^* \omega}\right) ^{-1}~.
 \end{aligned}\end{equation}
@@
 In a 1-channel Kondo model, the ground state is unique and a singlet~\cite{wilson1975renormalization}: \(\ket{J,J_z=0,0} = \frac{1}{\sqrt{2}} \left(\ket{\uparrow_{d},\downarrow_0} - \ket{\downarrow_d, \uparrow_0}\right)\), and the impurity entanglement entropy ($EE_d$) is at the  maximum possible value of $\log 2$.
-We will now calculate the same quantify for the ground states 
+We will now calculate the same quantity for the ground states 
 \begin{equation}\begin{aligned}
@@
 \begin{eqnarray}
-\rho_{d}&=& \textrm{Tr}_{d} \rho=\sum_{S_d^z} \langle S_d^z| \rho | S^z_d\rangle ~,~~EE_d = -\rho_{d} \log \rho_{d}~~~
+\rho_{d}&=& \textrm{Tr}_{d} \rho=\sum_{S_d^z} \langle S_d^z| \rho | S^z_d\rangle ~,~~EE_d = -\rho_{d} \log \rho_{d}~.
 \end{eqnarray}
@@
 \centering
-\includegraphics[width=0.49\textwidth]{plt/EE_multi_channel_ANN.png}
+\includegraphics[width=0.49\textwidth]{plt/EEmultichannelANN.png}
 \caption{Variation of impurity entanglement entropy ($EE_d$) for multiple values of \(K\). The maximum \(EE_d\) at large \(K\) is $\log 2$.}
@@
 On the other hand, the maximum entanglement entropy is attained in the state with minimum \(J^z\).
-This maximum value of the entanglement entopy is always \(\ln 2\) for odd values of \(K\); for even values of \(K\), the value asymptotically reaches $\log 2$ at large \(K\).
+This maximum value of the entanglement entropy is always \(\ln 2\) for odd values of \(K\); for even values of \(K\), the value asymptotically reaches $\log 2$ at large \(K\).
 
-A very similar computation gives the entanglent entropy between one outer spin and the rest of the spins, and it is shown in Fig.~\ref{fig:EE_outer}.
+A very similar computation gives the entanglement entropy between one outer spin and the rest of the spins, and it is shown in Fig.~\ref{fig:EE_outer}.
 We again find that the minimum entanglement entropy is associated with the state $|J^z=J\rangle$ and it falls with increasing \(K\), approaching zero asymptotically; the maximum entanglement entropy is, as before, associated with the state $|\left(J^z\right)_\mathrm{min}\rangle$ and it rises to $\log 2$ in the limit $K\gg 1$.
@@
 \centering
-\includegraphics[width=0.49\textwidth]{plt/outer_EE_multi_channel_ANN.png}
+\includegraphics[width=0.49\textwidth]{plt/outerEEmultichannelANN.png}
 \caption{Variation of the entanglement entropy of an outer spin ($EE_o$) with the rest for different channels $(K)$. The maximum entanglement entropy in the large $K$ limit is $\log 2$.}
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/NEW31Dec_I_2_vs_Nch_[0,1]}
+\includegraphics[width=0.49\textwidth]{plt/NEW31DecI2vsNch[0,1]}
 \caption{Variation of mutual information $I^2(d:o)$ of the impurity with the rest, for different values of $K$. The maximum $I^2(d:o)$ is $0.37$.}
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/NEW31Dec_I_2_vs_Nch_[1,2]}
+\includegraphics[width=0.49\textwidth]{plt/NEW31DecI2vsNch[1,2]}
 \caption{Variation of mutual information $I^2(o:o)$ between 2 outer spins, for multiple $K$. $I^2(o:o)$ vanishes for large $K$.}
@@
 Then, the $N-$partite information that we are interested in is defined as
-\begin{eqnarray}
-I^{N}_{\{\mathcal{A}_N\}} &=& \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.~~~~
+\begin{equation}
+I^{N}_{\{\mathcal{A}_N\}} = \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.
 \label{eq:I_N_definition}
-\end{eqnarray}
+\end{equation}
 \begin{figure}
-\includegraphics[width=0.49\textwidth]{plt/2022_IN_vs_N_K8.png}
+\includegraphics[width=0.49\textwidth]{plt/2022INvsNK8.png}
 \caption{Variation of multipartite information $I^N$ among \(N\) outer spins as a function of $N$, for $K=8$. The inset shows $I^N$ vs $N$ for an all-to-all model. Both show power law behavior.}
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/hopping_fock_states}
+\includegraphics[width=0.49\textwidth]{plt/hoppingfockstates}
 \caption{This is a schematic diagram of (a) single channel and (b) two channel problem. $S_d$ is the impurity spin. For more details refer to the text.}
@@
 \centering
-\includegraphics[width=0.49\textwidth]{plt/A_I1_ch123_['d']}
+\includegraphics[width=0.49\textwidth]{plt/AI1ch123['d']}
 \caption{Variation of impurity entanglement entropy $EE_{imp}$ against $t$, for $K=1,2,3$. }
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['d','1_up']}
+\includegraphics[width=0.49\textwidth]{plt/AI2ch12['d','1up']}
 \caption{This figure show the variation of mutual information between the impurity spin and the $1_{\uparrow}$ state against $t$.
 For more details please refer to the text.
-The errorbar $\sigma_2$ of the two channel data at low hopping strength $\sigma_2\approx 0.002$.}
+The error-bar $\sigma_2$ of the two channel data at low hopping strength $\sigma_2\approx 0.002$.}
 \label{fig:MI_imp_1_vs_t_K}
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['1_up','1_down']}
+\includegraphics[width=0.49\textwidth]{plt/AI2ch12['1up','1down']}
 \caption{Variation of mutual information ($i^2(1_{\uparrow},1_{\downarrow})$) among the two states present on the real-space origin ($1$) of a conduction channel, against $t$.
-The errorbar $\sigma_2$ for the two channel at low hopping strength is $\sigma_2\approx 0.013$.}
+The error-bar $\sigma_2$ for the two channel at low hopping strength is $\sigma_2\approx 0.013$.}
 \label{fig:MI_1_2_vs_t_K}
@@
 \begin{figure}
-\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['d','l1_up']}
+\includegraphics[width=0.49\textwidth]{plt/AI2ch12['d','l1up']}
 \caption{Variation of the mutual information $MI(d,l_{1\uparrow})$ between the impurity spin and the $l_{1\uparrow}$ state, against $t$.
-The errorbar $\sigma_2$ for the two channel case is $\sigma_2\approx 0.001$.}
+The error-bar $\sigma_2$ for the two channel case is $\sigma_2\approx 0.001$.}
 \label{fig:MI_d_l1}
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['1','l1']}
-\caption{Variation of the mutual information $MI(1_{\sigma},l_{1\sigma})$ between two nearest neighbor sites against \(t\). The errorbar for the two channel case is $\sigma_2\approx 0.005$.}
+\includegraphics[width=0.49\textwidth]{plt/AI2ch12['1','l1']}
+\caption{Variation of the mutual information $MI(1_{\sigma},l_{1\sigma})$ between two nearest neighbor sites against \(t\). The error-bar for the two channel case is $\sigma_2\approx 0.005$.}
 \label{fig:MI_l_l1}
@@
 
-Apart from these, we have also computed an intra-channel tripartite information $I^3(1_{\uparrow},l_{1\uparrow},l_{1\downarrow})$ of the two-channel ground state (blue curve in Fig.~\ref{fig:I3_I2_two_channel}) - it shows that there is a discontinuity in the triparite information at $t=0^+$, and at low hopping strength the tripartite information is independent of $t$ with a value $0.084$.
-This non-zero value of the tripartie information is consistent with the presence of a non-Fermi liquid effective Hamiltonian having more than just two-particle interactions within it.
-We have also studied inter-channel mutual informaition $I^2(1_{\uparrow},2_{\uparrow})$ for \(K=2\) (red curve in fig.~\ref{fig:I3_I2_two_channel}).
-It reveals the correlation and quantum entanglement between these two channels, and demonstrates the all-to-all nature of the local mott liquid.
+Apart from these, we have also computed an intra-channel tripartite information $I^3(1_{\uparrow},l_{1\uparrow},l_{1\downarrow})$ of the two-channel ground state (blue curve in Fig.~\ref{fig:I3_I2_two_channel}) - it shows that there is a discontinuity in the tripartite information at $t=0^+$, and at low hopping strength the tripartite information is independent of $t$ with a value $0.084$.
+This non-zero value of the tripartite information is consistent with the presence of a non-Fermi liquid effective Hamiltonian having more than just two-particle interactions within it.
+We have also studied inter-channel mutual information $I^2(1_{\uparrow},2_{\uparrow})$ for \(K=2\) (red curve in fig.~\ref{fig:I3_I2_two_channel}).
+It reveals the correlation and quantum entanglement between these two channels, and demonstrates the all-to-all nature of the local Mott liquid.
 
@@
 \centering
-\includegraphics[width=0.48\textwidth]{plt/I3_I2_A_I.png}
+\includegraphics[width=0.48\textwidth]{plt/I3I2AI.png}
 \caption{Red: Mutual information $I^2(1_{\uparrow},2_{\uparrow})$ against \(t\).
-Blue: Tripartite infrmation $I^3(1_{\uparrow},l_{1\uparrow},l_{1\downarrow})$ against \(t\).
-The errorbar ($\sigma$) for the $I^3$ and $I^2$ near the low hopping strength are $0.002$ and $0.003$ respectively.}
+Blue: Tripartite information $I^3(1_{\uparrow},l_{1\uparrow},l_{1\downarrow})$ against \(t\).
+The error-bar ($\sigma$) for the $I^3$ and $I^2$ near the low hopping strength are $0.002$ and $0.003$ respectively.}
 \label{fig:I3_I2_two_channel}
@@
 
-\subsubsection{Bures distance and the orthogonality catathrope}
+\subsubsection{Bures distance and the orthogonality catastrophe}
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/error_Bures_Distance_Ch123_10001}
+\includegraphics[width=0.49\textwidth]{plt/errorBuresDistanceCh12310001}
 \caption{Variation of Bures distance between the reduced density matrices of the star graph ground states at $t=0$ and $t\neq 0$, against $t$.
-The errorbars ($\sigma$) for \(K=2\) and \(K=3\) are $0.14$ and $0.08$ respectively, and near $t\approx 1$ the $\sigma$ are $0.04$ and $0.07$ respectively.}
+The error-bars ($\sigma$) for \(K=2\) and \(K=3\) are $0.14$ and $0.08$ respectively, and near $t\approx 1$ the $\sigma$ are $0.04$ and $0.07$ respectively.}
 \label{fig:bures_distance}
@@
 \begin{equation}
-d_{Bures}(\rho_1,\rho_2) = \sqrt{2} \bigg[1- \textrm{Tr}\bigg\{ \bigg(\rho_1^{1/2}  \rho_2 \rho_{1}^{1/2}\bigg)^{1/2} \bigg\}\bigg]
+d_{Bures}(\rho_1,\rho_2) = \sqrt{2} \bigg[1- \textrm{Tr}\bigg\{ \bigg(\rho_1^{1/2}  \rho_2 \rho_{1}^{1/2}\bigg)^{1/2} \bigg\}\bigg]~,
 \end{equation}
 and is a measure of the distance, in the Hilbert space, between the states forming the density matrices.
-One can see from the above defination that the maximum and minimum possible distances are $\sqrt{2}$ and $0$ respectively.
+One can see from the above definition that the maximum and minimum possible distances are $\sqrt{2}$ and $0$ respectively.
 \par We get the ground state $|\psi(t)\rangle$ of the problem by solving the Hamiltonian in Eq.~\eqref{eq:excitation_hamiltonian}.
@@
 	\hat{\mathbb{S}_d^z} \ket{S^z} = S^z \ket{S^z},\nonumber\\
-	\hat{\mathbb{S}_d^\pm} \ket{S^z} = \sqrt{\mathbb{S}_d\left( \mathbb{S}_d + 1 \right) - S^z\left( S^z \pm 1\right)} \ket{S^z \pm 1}
+	\hat{\mathbb{S}_d^\pm} \ket{S^z} = \sqrt{\mathbb{S}_d\left( \mathbb{S}_d + 1 \right) - S^z\left( S^z \pm 1\right)} \ket{S^z \pm 1}~.
 \end{gather}
@@
 \begin{equation}\begin{aligned}
-	H^\prime(\mathbb{J}) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + \mathbb{J} \vec{\mathbb{S}_d}\cdot\vec{\mathbb{S}}
+	H^\prime(\mathbb{J}) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + \mathbb{J} \vec{\mathbb{S}_d}\cdot\vec{\mathbb{S}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	{\mathbb{J}}^* = \frac{\gamma 4t^2}{{\mathcal{J}^*}} = \frac{2}{K \rho^\prime} \implies \gamma = \frac{1}{4t^2} {{\mathcal{J}^*}}^2 = \frac{1}{K^2 t^2 \rho \rho^\prime}
+	{\mathbb{J}}^* = \frac{\gamma 4t^2}{{\mathcal{J}^*}} = \frac{2}{K \rho^\prime} \implies \gamma = \frac{1}{4t^2} {{\mathcal{J}^*}}^2 = \frac{1}{K^2 t^2 \rho \rho^\prime}~.
 \end{aligned}\end{equation}
@@
 
-For a channel anisotropic MCK model with \(K\) Kondo couplings \(\mathcal{J}_i\) for each fo the \(K\) conduction channels, the zero bandwidth model is 
+For a channel-anisotropic MCK model with \(K\) Kondo couplings \(\left\{\mathcal{J}_i\right\}\) for each of the \(K\) conduction channels, the zero bandwidth model is 
 \begin{eqnarray}
-H_K (\vec{{\mathcal{J}}}) &=& \sum_{i=1}^{K} {\mathcal{J}}_i\vec{S}_d.\vec{S}_i
+H_K (\vec{{\mathcal{J}}}) &=& \sum_{i=1}^{K} {\mathcal{J}}_i\vec{S}_d.\vec{S}_i~.
 \label{eq:anisotropy}
@@
 \centering
-\includegraphics[width=0.48\textwidth]{plt/Anisotropy_Channel_3.png}
+\includegraphics[width=0.48\textwidth]{plt/AnisotropyChannel3.png}
 \caption{\textit{Left:} Variation of the ground state degeneracy against the $J_3$ keeping $J_1=J_2=1$ fixed.
@@
 Using the unitary renormalization group technique, we have obtained the zero-temperature phase diagram of the MCK problem and an effective Hamiltonian with a simple zero bandwidth limit - the star graph, and it determines the ground state energy, wavefunction and degeneracy of the MCK models.
-This star graph is found to explain much of the physics of overscreening and criticality, including the singularities in the susceptibility and magnetisation, as well as a reduction in the degree to which the impurity spin is compensated.
-The overarching message there was that the ground state degeneracy of the star graph (which is unity for single-channel and greater for the overscreened models) was the key ingredient in leading to the qualitative and quantitative differences from the single-channel model
+This star graph is found to explain much of the physics of over-screening and criticality, including the singularities in the susceptibility and magnetisation, as well as a reduction in the degree to which the impurity spin is compensated.
+The overarching message there was that the ground state degeneracy of the star graph (which is unity for single-channel and greater for the over-screened models) was the key ingredient in leading to the qualitative and quantitative differences from the single-channel model
 The presence of ground state degeneracy also allows the construction of non-local twist operators and fractional excitations in the ground state manifold.
-Integrating out the quantum fluctuations of the impurity leads to an all-to-all effective Hamiltonian for the local bath spins, and the Hamiltonian is foudn to contain inter-channel quantum scattering in terms of electron-hole pairs, theryby creating a local Mott-liquid phase at the origin of the lattice.
+Integrating out the quantum fluctuations of the impurity leads to an all-to-all effective Hamiltonian for the local bath spins, and the Hamiltonian is found to contain inter-channel quantum scattering in terms of electron-hole pairs, thereby creating a local Mott-liquid phase at the origin of the lattice.
 
@@
 The existence of a marginal Fermi liquid within the effective Hamiltonian clearly displays the orthogonality catastrophe in the form of singularities that are absent at exact screening.
-Studies of various thermodynamic properties (presented in the supplementary material) from this 2-channel Kondo LEH like specific heat and susceptibility show logarithmic dependence at low temperature, in agreement with the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005,emery_kivelson,andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002}.
+Studies of various thermodynamic properties (presented in the Supplementary Material~\cite{SM}) from this 2-channel Kondo LEH like specific heat and susceptibility show logarithmic dependence at low temperature, in agreement with the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005,emery_kivelson,andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002}.
 
@@
 \acknowledgments
-%\textcolor{red}{
 SP and Anirban Mukherjee thanks the CSIR, Govt.
@@
 Abhirup Mukherjee thanks IISER Kolkata for funding through a research fellowship.
-{\color{red}SL thanks $\cdots$}.
-%}
+S.
+Lal
+thanks the SERB, Govt. of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
 

### 2022-04-26 Manuscript26April2022/supplementary_mck.tex
corrected typos and changed figure names to remove underscores and some other minor changes made by sir

--- 2022-04-26 manuscript/supplementary_mck.tex
@@
 \affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-\author{A. Taraphder}
-\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
 \author{N. S. Vidhyadhiraja}
@@
 \affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
+\author{A. Taraphder}
+\email{arghya@phy.iitkgp.ernet.in}
+\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
 \author{Siddhartha Lal}
@@
 \subsection{Energy lowering due to quantum fluctuations}
-The star graph Hamiltonian that sits at the heart of the RG fixed point Hamiltonian of the multichannel Kondom model contains a classical Ising term and a quantum fluctuation term:
+The star graph Hamiltonian that sits at the heart of the RG fixed point Hamiltonian of the multichannel Kondo model contains a classical Ising term and a quantum fluctuation term:
 \begin{equation}\begin{aligned}
-	H = {\mathcal{J}}\vec{S_d}\cdot\vec S = \mathcal{J}\left[\underbrace{S_d^z S^z}_\text{Ising term} + \underbrace{\frac{1}{2}\left(S_d^+ S^- + \text{h.c.}\right)}_\text{quantum fluctuation part} \right] = \mathcal{J}\left[\mathcal{H}^C + \mathcal{H}^Q\right]
+	H = {\mathcal{J}}\vec{S_d}\cdot\vec S = \mathcal{J}\left[\underbrace{S_d^z S^z}_\text{Ising term} + \underbrace{\frac{1}{2}\left(S_d^+ S^- + \text{h.c.}\right)}_\text{quantum fluctuation part} \right] = \mathcal{J}\left[\mathcal{H}^C + \mathcal{H}^Q\right] ~.
 	\label{eq:stargraph_hamiltonian}
@@
 This can be understood by looking at the contributions, per channel, of the classical and the quantum parts to the total ground state energy \(E_g\).
-In the overscreened case \(\left( K > 2S_d \right) \), the contributions are
+In the over-screened case \(\left( K > 2S_d \right) \), the contributions are
 \begin{gather}
-	E_{C} = \frac{1}{K}\langle \psi_g | \mathcal{H}^C | \psi_g \rangle, ~~~~~ E_{Q} = \frac{1}{K}\bra{\psi_g}\mathcal{H}^Q \ket{\psi_g} =\frac{E_g/\mathcal{J} - E_{C}}{K} =  -\frac{1}{2}S_d - \frac{1}{K}\left(S_d + E_{C}\right)
+	E_{C} = \frac{1}{K}\langle \psi_g | \mathcal{H}^C | \psi_g \rangle, ~~~~~ E_{Q} = \frac{1}{K}\bra{\psi_g}\mathcal{H}^Q \ket{\psi_g} =\frac{E_g/\mathcal{J} - E_{C}}{K} =  -\frac{1}{2}S_d - \frac{1}{K}\left(S_d + E_{C}\right)~,
 \end{gather}  
-where we have defined the contributions \(E_C\) and \(E_Q\) to the ground state energy coming from the Ising and fluctuation parts respectively, and we have substituted the ground state energy \(E_g\) for the overscreened case {\color{blue}from the expression in the main text, just below where the star graph is introduced}.
+where we have defined the contributions \(E_C\) and \(E_Q\) to the ground state energy coming from the Ising and fluctuation parts respectively, and we have substituted the ground state energy \(E_g\) for the over-screened case from eq.(10) in the main text.
 This contribution $E_Q$ is generated by the spin-flip fluctuations between the impurity spin and the outer spins of the star graph.
@@
 The larger values of \(|E_Q|\) indicate that the quantum fluctuations are largest in the states with minimum \(J^z\), and these states can be thought of as the counterparts to the maximally entangled singlet seen in the single-channel Kondo problem.
-This behavior persists as \(K \gg 1\): the magnitude \(|Q_Q|\) associated with the $|J^z|= J$ states vanish, showing the classical nature of these states and the lack of quantum fluctuations in that limit.
+This behaviour persists as \(K \gg 1\): the magnitude \(|Q_Q|\) associated with the $|J^z|= J$ states vanish, showing the classical nature of these states and the lack of quantum fluctuations in that limit.
 On the other hand, the state $|J^z| = |J^z|_{min}$ has a non-zero \(|E_Q|\) in the large \(K\) limit and hence contains some non-zero quantum fluctuations, showing the true quantum nature of this macroscopic singlet state.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{plt/all/Quantum_Energy_per_channel}
-\caption{This shows the variation of quantum energy per channel with $1/N$, where $N=N_{ch}+1$ is the total number of spins in the systems including the impurity spins. {\bf REMOVE DELTA IN YLABEL}}
+\includegraphics[width=0.7\textwidth]{plt/QuantumEnergyperchannel}
+\caption{This shows the variation of quantum energy per channel with $1/N$, where $N=N_{ch}+1$ is the total number of spins in the systems including the impurity spins.}
 \label{fig:quantum_energy}
@@
 For a general spin-$S_d$ impurity, the ground state is characterised by $J=|K/2-S_d|$, which gives $J^2=J(J+1)=(|K/2-S_d|)(|K/2-S_d|+1)$.
-We define $\Delta=(K/2-S_d)$ to quantify the deviation from exact screening; $\Delta=0$ represents the exactly screened problem, and $\Delta>0$ and $\Delta<0$ represents the overscreened and underscreened problems respectively.
+We define $\Delta=(K/2-S_d)$ to quantify the deviation from exact screening; $\Delta=0$ represents the exactly screened problem, and $\Delta>0$ and $\Delta<0$ represents the over-screened and under-screened problems respectively.
 Among the degenerate ground state, the maximum quantum fluctuation will occur in the state with minimum \(|J^z|\).
@@
 	\frac{1}{K}\sqrt{(|K/2-S_d|)(|K/2-S_d|+1)}, & \text{ where }\Delta\text{ is integer}
-\end{cases}
+\end{cases}~.
 \end{equation}
-This expression is symmetric under the transformation \(\Delta \to -\Delta\), and represents a duality between the overscrened and underscreend models.
+This expression is symmetric under the transformation \(\Delta \to -\Delta\), and represents a duality between the over-screened and under-screened models.
 In the limit of large channel number \(K\), \(q_K\) simplifies to $\lim_{K\rightarrow \infty} q_K= \lim_{K \to \infty}\frac{1}{2K}|\Delta(K)|$.
@@
 
-\subsection{Staggerred magnetization of the star graph}
+\subsection{Staggered magnetization of the star graph}
  Another probe to study the screening as a function of \(K\) is the staggered magnetization \(\vec{M}_s=\vec{S}-\vec{S}_d\).
@@
 \begin{equation}
-	m_s^2 = \left< \left(\frac{1}{K}M_S\right)^2\right> = \frac{1}{K^2}\langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \frac{1}{K^2}\langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle = \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}
+	m_s^2 = \left< \left(\frac{1}{K}M_S\right)^2\right> = \frac{1}{K^2}\langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \frac{1}{K^2}\langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle = \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}~.
 \end{equation}
@@
 \begin{figure}
-\includegraphics[width=0.7\textwidth]{plt/all/Staggered_mag_50.png}
+\includegraphics[width=0.7\textwidth]{plt/Staggeredmag50.png}
 \caption{This shows how the staggered magnetization changes with the number of channels $N_{ch}$.}
@@
 
-\subsection{Thermodynamic quantitites}
+\subsection{Thermodynamic quantities}
 
@@
 \begin{equation}\begin{aligned}
-	\pi^z_c \equiv \sigma_d^z \pi^z = \exp\left[i \frac{\pi}{2} \left(\sum_{l=1}^K \sigma^z_l - K\right)\right] 
+	\pi^z_c \equiv \sigma_d^z \pi^z = \exp\left[i \frac{\pi}{2} \left(\sum_{l=1}^K \sigma^z_l - K\right)\right] ~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\ket{g^\theta_{J^z}} \equiv \frac{1}{\sqrt 2}\left( \ket{J^z} + e^{i\theta}\ket{J^z+1}\right), && J^z < \frac{1}{2}\left( K-1 \right)
+	\ket{g^\theta_{J^z}} \equiv \frac{1}{\sqrt 2}\left( \ket{J^z} + e^{i\theta}\ket{J^z+1}\right), && J^z < \frac{1}{2}\left( K-1 \right)~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left<\sigma_d^x\right> \equiv \langle g^\theta_{J^z} \vert \sigma_d^x \vert g^\theta_{J^z}\rangle = - \langle J^z + 1 \vert \pi^x_c \vert -J^z \rangle + \text{h.c.}
+	\left<\sigma_d^x\right> \equiv \langle g^\theta_{J^z} \vert \sigma_d^x \vert g^\theta_{J^z}\rangle = - \langle J^z + 1 \vert \pi^x_c \vert -J^z \rangle + \text{h.c.}~.
 \end{aligned}\end{equation}
@@
 	\label{sigmax}
-	\left<\sigma_d^x\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\cos \theta
+	\left<\sigma_d^x\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\cos \theta~.
 \end{aligned}\end{equation}
@@
 	\label{sigmayz}
-	\left<\sigma_d^y\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\sin \theta, &&\left<\sigma_d^z\right> = - \frac{2J^z + 1}{(1+K)}
+	\left<\sigma_d^y\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\sin \theta, &&\left<\sigma_d^z\right> = - \frac{2J^z + 1}{(1+K)}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\cos^2\theta\left(\left<\sigma^x_d\right>\right)^2 + \sin^2\theta\left(\left<\sigma^y_d\right>\right)^2 + \frac{1}{4}\left(\left<\sigma^z_d\right>\right)^2 = \frac{1}{4}\left(\frac{K}{1+K}\right)^2
+	\cos^2\theta\left(\left<\sigma^x_d\right>\right)^2 + \sin^2\theta\left(\left<\sigma^y_d\right>\right)^2 + \frac{1}{4}\left(\left<\sigma^z_d\right>\right)^2 = \frac{1}{4}\left(\frac{K}{1+K}\right)^2~.
 \end{aligned}\end{equation}
-This relation \textit{constrains the values of the magnetization} along all the directions: the \(x\) and \(y\) magnetization values have already been shown to be related to the `t Hooft operators \(\pi^x\) and \(\pi^y\) and the magnetization along \(z\) is therefore constrained in terms of the `t Hooft operators and the quantized function on the right-hand side (the function is quantized because \(K\) can only take integer values).
+This relation \textit{constrains the values of the magnetization} in all the directions: the \(x\) and \(y\) magnetization values have already been shown to be related to the `t Hooft operators \(\pi^x\) and \(\pi^y\) and the magnetization along \(z\) is therefore constrained in terms of the `t Hooft operators and the quantized function on the right-hand side (the function is quantized because \(K\) can only take integer values).
 
@@
 \begin{equation}
-\mathcal{F}= -k_B T\log Z, ~ ~ ~ S = -\frac{\partial \mathcal{F}}{\partial T} = -k_B \log Z -k_B T \frac{1}{Z} \frac{dZ}{dT} = -k_B \log \sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon}  -\frac{1}{\beta} \frac{k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   }{\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon}}
+\mathcal{F}= -k_B T\log Z, ~ ~ ~ S = -\frac{\partial \mathcal{F}}{\partial T} = -k_B \log Z -k_B T \frac{1}{Z} \frac{dZ}{dT} = -k_B \log \sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon}  -\frac{1}{\beta} \frac{k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   }{\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon}}~,
 \end{equation}
-where \(d(\epsilon)\) is the degeneracy of the state at energy \(\epsilon\). The high and low temperature limits take very simple forms:
+where \(d(\epsilon)\) is the degeneracy of the state at energy \(\epsilon\). The high and low-temperature limits take very simple forms:
 \begin{equation}
-\lim_{\beta\rightarrow \infty} S = -k_B \log_2 d(\epsilon_{G})~,~~\lim_{\beta\rightarrow 0} S = -k_B \log \sum_\epsilon d(\epsilon)
+\lim_{\beta\rightarrow \infty} S = -k_B \log_2 d(\epsilon_{G})~,~~\lim_{\beta\rightarrow 0} S = -k_B \log \sum_\epsilon d(\epsilon)~.
 \end{equation}
@@
 In fig.\ref{fig:thermal_entropy}, we plot the thermal entropy (in units of $k_B \log 2$) for a range of temperatures and for different values of \(K\).
-At large temperatures, \(S\) saturates to integer multiples of \(k_B \log 2\), while at low temperature, that is not always the case.
-This is because the total Hilbert space dimension \(\sum _\epsilon d(\epsilon)\) is simpy \(2^N\) (\(N\) being the total number of 1-particle states in the Hilbert space), and therefore \(\log \sum _\epsilon d(\epsilon) = N \log 2\) is always an integer multiple of \(N\).
+At large temperatures, \(S\) saturates to integer multiples of \(k_B \log 2\), while at low-temperatures, that is not always the case.
+This is because the total Hilbert space dimension \(\sum _\epsilon d(\epsilon)\) is simply \(2^N\) (\(N\) being the total number of 1-particle states in the Hilbert space), and therefore \(\log \sum _\epsilon d(\epsilon) = N \log 2\) is always an integer multiple of \(N\).
 On the other hand, the ground state degeneracy \(d(\epsilon_G)\) is \(|K - 2 S_d|\) which is not necessarily of the form \(2^N\) and hence does not always lead to an integer multiple of \(\log 2\).
@@
 \centering
-\includegraphics[width=0.7\textwidth]{plt/all/ThermalEntanglementVS_LogTemperature_}
+\includegraphics[width=0.7\textwidth]{plt/ThermalEntanglementVSLogTemperature}
 \caption{This shows the variation of thermal entropy with the temperature.}
@@
 H_{eff} 
- =\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)   
+ =\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)~,
 \label{eq:all-to-all_1}
@@
 In the above eq.\eqref{eq:all-to-all_1} we see the $U(1)$ symmetry of the effective Hamiltonian.
-Using the spinor repersentation, we obtain the spin creation operation in terms of the electronic degree of freedom:
+Using the spinor representation, we obtain the spin creation operation in terms of the electronic degree of freedom:
 \begin{equation}
 S_i^+ = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{+}_{\alpha\beta} c_{0\beta}^{(i)}
-=\frac{\hbar}{2} c_{0\uparrow}^{(i)\dagger} c_{0\downarrow}^{(i)}, ~ ~ ~S_i^z = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{z}_{\alpha\beta} c_{0\beta}^{(i)} =\frac{\hbar}{2} (c_{0\uparrow}^{(i)\dagger} c_{0\uparrow}^{(i)} - c_{0\downarrow}^{(i)\dagger} c_{0\downarrow}^{(i)} )~,
+=\frac{\hbar}{2} c_{0\uparrow}^{(i)\dagger} c_{0\downarrow}^{(i)}, ~ ~ ~S_i^z = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{z}_{\alpha\beta} c_{0\beta}^{(i)} =\frac{\hbar}{2} (c_{0\uparrow}^{(i)\dagger} c_{0\uparrow}^{(i)} - c_{0\downarrow}^{(i)\dagger} c_{0\downarrow}^{(i)} )~.
 \end{equation}
-This spinor is simply the Anderson pseudospin formulation in the spin channel.
-The spin-creation opertor ($S_i^+$) involves the simultaneous creation of an electron-hole pair at the real space origin of the $i^{th}$ conduction channel.
+This spinor is simply the Anderson pseudo-spin formulation in the spin channel.
+The spin-creation operator ($S_i^+$) involves the simultaneous creation of an electron-hole pair at the real space origin of the $i^{th}$ conduction channel.
 The condensation of such electron-hole pairs has already been shown in ~\cite{anirbanmott1,anirbanmott2}.
@@
 \begin{equation}
-\hat{T}_{\mu}\hat{\mathcal{O}}_{\mu} \hat{T}^{\dagger}_{\mu} \hat{\mathcal{O}}_{\mu}^{\dagger} = \exp\{i[2\pi S_1^z-\frac{2\pi}{K}S^z]\} = \exp\{i[\pm \pi - \frac{2\pi}{K} S^z]\} =\exp(i\frac{2\pi p}{q})
+\hat{T}_{\mu}\hat{\mathcal{O}}_{\mu} \hat{T}^{\dagger}_{\mu} \hat{\mathcal{O}}_{\mu}^{\dagger} = \exp\{i[2\pi S_1^z-\frac{2\pi}{K}S^z]\} = \exp\{i[\pm \pi - \frac{2\pi}{K} S^z]\} =\exp(i\frac{2\pi p}{q})~.
 \end{equation}
@@
 \begin{eqnarray}
-\frac{(K-m)}{K} &=& \frac{p}{q} ~,~~ \frac{-m}{K}=\frac{p}{q}
+\frac{(K-m)}{K} &=& \frac{p}{q} ~,~~ \frac{-m}{K}=\frac{p}{q}~.
 \end{eqnarray}
-For the first case $K-m=p$ we can see that $m=K$ makes $p$ trivial hus the allowed values are $m=0,\cdots,K-1$, which represents the corresponding $S^z$ eigenvalues 
+For the first case where $K-m=p$, we can see that $m=K$ makes $p$ trivial, and hence the allowed values are $m=0,\cdots,K-1$, which represents the corresponding $S^z$ eigenvalues 
 \begin{eqnarray}
-&&-K/2,-K/2+1,\cdots,K/2-2,K/2-1
+&&-K/2,-K/2+1,\cdots,K/2-2,K/2-1~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-&&\hspace{2.2cm} -K/2+1,-K/2+2,\cdots,K/2-1,K/2
+&&\hspace{2.2cm} -K/2+1,-K/2+2,\cdots,K/2-1,K/2~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\hat{T}_{\mu}\hat{\mathcal{O}_{\mu}} \hat{T}^{\dagger}_{\mu}\hat{\mathcal{O}_{\mu}}^{\dagger} &=& e^{i\frac{2\pi p}{K}}
+\hat{T}_{\mu}\hat{\mathcal{O}_{\mu}} \hat{T}^{\dagger}_{\mu}\hat{\mathcal{O}_{\mu}}^{\dagger} &=& e^{i\frac{2\pi p}{K}}~,
 \end{eqnarray}
 where $p$ corresponds to different $S^z$ states, related as $p=\pm K/2-S^z$.
-Thus we can see that there are $K$ possible $S^z$ plaleau states in the all-to-all model where each plateaux is $K$ fold degenerate.
+Thus we can see that there are $K$ possible $S^z$ plateau states in the all-to-all model where each plateau is $K$ fold degenerate.
 This $p/K$ is similar to the filling factor of the fractional quantum Hall effect.
-There are possibly $K!$ pairs of twist and translation operator corresponding to different closed paths $\mathcal{C}_{\mu}$ which can probe this degeneracy.
+There are $K!$ pairs of twist and translation operators corresponding to different closed paths $\mathcal{C}_{\mu}$ which can probe this degeneracy.
 
@@
 We will now obtain the action of these twist operators on the Hamiltonian in eq.~\ref{eq:all-to-all_1}.
-Due the all-to-all nature of the effetive Hamiltonian one can find $K!$ possible relative arrangement of those $K$ channels which keeps the Hamiltonian invariant.
-Here we briefly discuss the choice of the closed loop $\mathcal{C}_{\mu}$ and the insertion of the flux.
+Due to the all-to-all nature of the effective Hamiltonian one can find $K!$ possible relative arrangement of those $K$ channels which keeps the Hamiltonian invariant.
+Here we briefly discuss the choice of the closed-loop $\mathcal{C}_{\mu}$ and the insertion of the flux.
 As shown in the {\color{blue}Fig.\ref{fig:stargraph-to-alltoall}(b)} we have chosen a particular closed path which crosses all the outer spin only once.
-We embed that closed loop on a plane and put the flux perpendicular to the plane through the closed loop.
+We embed that closed-loop on a plane and put the flux perpendicular to the plane through the closed loop.
 One can find a different closed loop where the ordering of the outer spins will be different.
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{./plt/stargraph-to-alltoall.png}
+	\includegraphics[width=0.8\textwidth]{plt/stargraph-to-alltoall.png}
 	\caption{(a) Schematic diagram of $8-$channel multichannel Kondo model zero mode in zero bandwidth limit.
@@
 
-The action of the twist operator on the $S^x$ is determined in the follwoing calculation
+The action of the twist operator on the $S^x$ is determined in the following calculation
 \begin{equation}
-\hat{O}_{\mu} S^x \hat{O}^{\dagger}_{\mu} = \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} )S^x \exp({-i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} ) = e^{X} S^x e^{-X}
+\hat{O}_{\mu} S^x \hat{O}^{\dagger}_{\mu} = \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} )S^x \exp({-i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} ) = e^{X} S^x e^{-X}~.
 \end{equation}
-For simplicity of thte calculation we define $i\frac{2\pi}{K}=\Omega$, thus $X=\Omega\sum_j jS^z_j$. Thus we get
+To simplify the calculation, we define $i\frac{2\pi}{K}=\Omega$, thus $X=\Omega\sum_j jS^z_j$. Thus we get
 \begin{equation}
 e^X S^x e^{-X}= S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots = \sum_l ( S^x_l \cos \theta_l -  S_l^y \sin \theta_l ) ~,~~~\theta_l=\frac{2\pi l}{K}\\
-e^X S^y e^{-X}= \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)
+e^X S^y e^{-X}= \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)~.
 \end{equation}
@@
  \lim_{K\rightarrow \infty}\hat{\mathcal{O}}_{\mu} H_{eff} \hat{\mathcal{O}}_{\mu}^{\dagger}\nonumber = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[ \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger}  + \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger}  \bigg] = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[  S^{x2}+S^{y2}  \bigg] = H_{eff},\\
- \lim_{K\rightarrow \infty } [\hat{\mathcal{O}},H_{eff}] = 0
+ \lim_{K\rightarrow \infty } [\hat{\mathcal{O}},H_{eff}] = 0~.
 \label{eq:hamiltonian_twisted}
@@
 
-The translation operator $\hat{T}_{\mu}=e^{i\hat{\mathcal{P}}_{\mu}}$ commutes with the Hamiltonian, and hence the generator $\hat{\mathcal{P}}_{\mu}$ also commutes with the Hamiltonian.
+Since the translation operator $\hat{T}_{\mu}=e^{i\hat{\mathcal{P}}_{\mu}}$ commutes with the Hamiltonian, so does the generator $\hat{\mathcal{P}}_{\mu}$.
 We can label the $j^{th}$ state with the eigenvalues of this operator $\hat{\mathcal{P}_{\mu}}$ as $|p^{j}_{\mu}\rangle$.
@@
 \begin{gather}
-\hat{T}_{\mu} |p^j_{\mu} \rangle = e^{i\hat{\mathcal{P}}_{\mu}} |p^j_{\mu} \rangle = e^{ip^j_{\mu}} |p^j_{\mu}\rangle, ~ ~ ~ ~ \hat{T}_{\mu} \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle =  \hat{\mathcal{O}}_{\mu} \hat{T}_{\mu} e^{i\frac{2\pi m}{K}} |p^j_{\mu}\rangle = \hat{\mathcal{O}}_{\mu}   e^{i(\frac{2\pi m}{K}+p_{\mu}^j)} |p^j_{\mu}\rangle~,~~ \frac{2\pi m}{K} \equiv p_{\mu}^{m} \\
-\hat{T}_{\mu} \bigg( \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle  \bigg) = e^{i(p_{\mu}^{m}+p_{\mu}^j)} \bigg( \hat{\mathcal{O}}_{\mu}    |p^j_{\mu}\rangle \bigg)    
+\hat{T}_{\mu} |p^j_{\mu} \rangle = e^{i\hat{\mathcal{P}}_{\mu}} |p^j_{\mu} \rangle = e^{ip^j_{\mu}} |p^j_{\mu}\rangle, ~ ~ ~ ~ \hat{T}_{\mu} \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle =  \hat{\mathcal{O}}_{\mu} \hat{T}_{\mu} e^{i\frac{2\pi m}{K}} |p^j_{\mu}\rangle = \hat{\mathcal{O}}_{\mu}   e^{i(\frac{2\pi m}{K}+p_{\mu}^j)} |p^j_{\mu}\rangle~,~~ \frac{2\pi m}{K} \equiv p_{\mu}^{m}~, \\
+\hat{T}_{\mu} \bigg( \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle  \bigg) = e^{i(p_{\mu}^{m}+p_{\mu}^j)} \bigg( \hat{\mathcal{O}}_{\mu}    |p^j_{\mu}\rangle \bigg)~,
 \end{gather}
 where $m$ represents different $S^z$ plateaux.
-This shows that  $\hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle $ is again an eigenstate of the translation operator, but with an eivenvalue that is different from $|p^j_{\mu} \rangle $, and is thus orthogonal to $\ket{p^j_{\mu}}$.
-Simiarly one can generally show that $\langle p^j_{\mu} | \hat{\mathcal{O}}^{q}_{\mu} |p^j_{\mu} \rangle=0$, where $q$ is any integer.
-Also in the large $K$ limit we can see from the eq.\eqref{eq:hamiltonian_twisted} that these differnt twisted states has same energy.
+This shows that  $\hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle $ is again an eigenstate of the translation operator, but with an eigenvalue that is different from $|p^j_{\mu} \rangle $, and is thus orthogonal to $\ket{p^j_{\mu}}$.
+Similarly, one can in general show that $\langle p^j_{\mu} | \hat{\mathcal{O}}^{q}_{\mu} |p^j_{\mu} \rangle=0$, where $q$ is any integer.
+Also in the large $K$ limit we can see from the eq.\eqref{eq:hamiltonian_twisted} that these different twisted states has same energy.
 Which shows that at each plateau state labeled by the $S^z$ eigenvalue has $K$ fold degenerate eigenstates labeled by the eigenvalue of the translation operators.
@@
 Obtaining the effective Hamiltonian involves obtaining the low energy excitations on top of the ground state of the star graph.
-The large-energy excitations are ones that involve spin flips.
+The large-energy excitations involve spin flips.
 This guides the separation of the Hamiltonian into a diagonal and an off-diagonal piece:
@@
 The Schrodinger equation for the ground state can be written as
-\begin{widetext}
 \begin{align}
@@
 \end{align}
-\end{widetext}
 \(E_\text{gs}\) is the ground state energy, and can be replaced by the star graph ground state energy if we remove the kinetic energy cost via normal ordering: \(E_\text{gs} = -\frac{J}{2}\left(\frac{K}{2}+1\right) \).
@@
 For the state \((s_\text{tot},s^z_\text{tot}) = (1,0)\), equations are
-\begin{align}
+\begin{equation}
 	\label{eff_ham_Sdz_10}
-	E_\text{gs} \ket{\frac{1}{2}, 1, 0} &= \left(H_d + V \frac{1}{E_\text{gs} - H_d}V^\dagger\right) \ket{\frac{1}{2}, 1, 0}\\
-	E_\text{gs} \ket{-\frac{1}{2}, 1, 0} &= \left(H_d + V^\dagger \frac{1}{E_\text{gs} - H_d} V\right) \ket{-\frac{1}{2}, 1, 0}\\
-\end{align}
-These equations represent the Schrodinger equation for the states \(\ket{S_d^z, 1, 0}\), and the right hand sides therefore give the effective Hamiltonians for those states.
+	E_\text{gs} \ket{\frac{1}{2}, 1, 0} = \left(H_d + V \frac{1}{E_\text{gs} - H_d}V^\dagger\right) \ket{\frac{1}{2}, 1, 0}, ~ ~ ~ ~ ~ E_\text{gs} \ket{-\frac{1}{2}, 1, 0} = \left(H_d + V^\dagger \frac{1}{E_\text{gs} - H_d} V\right) \ket{-\frac{1}{2}, 1, 0}~.\\
+\end{equation}
+These represent the Schrodinger equation for the states \(\ket{S_d^z, 1, 0}\), and the right hand sides therefore give the effective Hamiltonians for those states.
 If we combine the states into a single subspace \(\ket{1,0}= \left\{\ket{\frac{1}{2}, 1, 0}, \ket{-\frac{1}{2}, 1, 0}\right\}\), the effective Hamiltonian for this composite subspace becomes the sum of the two parts:
@@
 	\label{eff_ham_10}
-	H^{1,0}_\text{eff}\ket{1, 0}\bra{1, 0} = \left(H_d + V G_0 V^\dagger + V^\dagger G_0  V\right) \ket{1, 0}
+	H^{1,0}_\text{eff}\ket{1, 0}\bra{1, 0} = \left(H_d + V G_0 V^\dagger + V^\dagger G_0  V\right) \ket{1, 0}~,
 \end{align}
@@
 the effective Hamiltonian is
-\begin{widetext}
 \begin{align}
-	H_\text{eff}^{1, 0} &= H_0 + \frac{J^2}{2\left(E_\text{gs} + \frac{J}{2}\right)}\left[1 + \frac{ H_0 + \left(\frac{1}{2} + S_d^z\right) s^+_\text{tot}X_{1,\text{tot}} - \left(\frac{1}{2} - S_d^z\right) s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 \left(E_\text{gs} + \frac{J}{2}\right)} + \frac{H_0^2}{\left(E_\text{gs} + \frac{J}{2}\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + \frac{J}{2}\right)^3} \right]
+	H_\text{eff}^{1, 0} &= H_0 + \frac{J^2}{2\left(E_\text{gs} + \frac{J}{2}\right)}\left[1 + \frac{ H_0 + \left(\frac{1}{2} + S_d^z\right) s^+_\text{tot}X_{1,\text{tot}} - \left(\frac{1}{2} - S_d^z\right) s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 \left(E_\text{gs} + \frac{J}{2}\right)} + \frac{H_0^2}{\left(E_\text{gs} + \frac{J}{2}\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + \frac{J}{2}\right)^3} \right]~.
 \end{align}
-\end{widetext}
 We employed the definitions 
 \begin{equation}\begin{aligned}
-X_{n,\text{tot}} \equiv  \sum_l \sum_{k,k^\prime}\left(\epsilon_k - \epsilon_{k^\prime}\right)^n c^\dagger_{k \downarrow}c_{k^\prime \uparrow}, ~ ~ ~ Z_{1,\text{tot}} \equiv \sum_{k,k^\prime,l}\left( \epsilon_k - \epsilon_{k^\prime} \right) \frac{1}{2}\left(c^\dagger_{k \uparrow,l}c_{k^\prime \uparrow,l} - c^\dagger_{k \downarrow,l}c_{k^\prime \downarrow,l}\right)
+X_{n,\text{tot}} \equiv  \sum_l \sum_{k,k^\prime}\left(\epsilon_k - \epsilon_{k^\prime}\right)^n c^\dagger_{k \downarrow}c_{k^\prime \uparrow}, ~ ~ ~ Z_{1,\text{tot}} \equiv \sum_{k,k^\prime,l}\left( \epsilon_k - \epsilon_{k^\prime} \right) \frac{1}{2}\left(c^\dagger_{k \uparrow,l}c_{k^\prime \uparrow,l} - c^\dagger_{k \downarrow,l}c_{k^\prime \downarrow,l}\right)~.
 \end{aligned}\end{equation}
@@
 
-\subsection{Low temperature thermodynamic behaviour}
-The non-Fermi liquid (NFL) nature of the effective Hamiltonian can be demonstrated through a calculation of certain thermodyanmic quantities like the impurity specific heat and the magnetic suseptibility.
-We begin by calculating the self energy of this NFL hamiltonian.
-In real space one can extract a diagonal piece from the effective Hamiltonian by using the fermionic anticommutation relations.
+\subsection{Low-temperature thermodynamic behaviour}
+The non-Fermi liquid (NFL) nature of the effective Hamiltonian can be demonstrated through a calculation of certain thermodynamic quantities like the impurity specific heat and the magnetic susceptibility.
+We begin by calculating the self-energy of this NFL hamiltonian.
+In real space, one can extract a diagonal piece from the effective Hamiltonian by using the fermionic anticommutation relations.
 \begin{eqnarray}
-H_{eff}^{off,(2)} |_{diag} &=& -(16t^2/3) [ (S_1^z)^2+ (S_2^z)^2 ] 
+H_{eff}^{off,(2)} |_{diag} &=& -(16t^2/3) [ (S_1^z)^2+ (S_2^z)^2 ] ~,
 \end{eqnarray}
-the corresponding momentum space Hamiltonian is obtained from the fouries transform:
+the corresponding momentum space Hamiltonian is obtained from the Fourier transform:
 \begin{equation}
-H_{eff}^{off,(2)} |_{diag}= -\frac{4t^2}{3} \frac{1}{N} \bigg[ \displaystyle\sum_{k,\sigma} n_{k\sigma}(1-\frac{1}{N} \displaystyle\sum_{k_2}  n_{k_2,-\sigma}  ) + \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma} ( 1-\frac{1}{N} \displaystyle\sum_{ k_2} \tilde{n}_{k_2,-\sigma}  ) \bigg]
+H_{eff}^{off,(2)} |_{diag}= -\frac{4t^2}{3} \frac{1}{N} \bigg[ \displaystyle\sum_{k,\sigma} n_{k\sigma}(1-\frac{1}{N} \displaystyle\sum_{k_2}  n_{k_2,-\sigma}  ) + \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma} ( 1-\frac{1}{N} \displaystyle\sum_{ k_2} \tilde{n}_{k_2,-\sigma}  ) \bigg]~.
 \end{equation}
@@
 \begin{equation}
-\bar{\epsilon} _k-\epsilon_k = \Sigma_k = -\frac{4t^2}{3N^2}\bigg(1-\frac{N}{e^{(\epsilon_k-\mu)/k_BT}+1}\bigg)
+\bar{\epsilon} _k-\epsilon_k = \Sigma_k = -\frac{4t^2}{3N^2}\bigg(1-\frac{N}{e^{(\epsilon_k-\mu)/k_BT}+1}\bigg)~.
 \label{eq:self-energy-NFL}
 \end{equation}
-Using the self-energy we calculate the impurity speciftic heat defined as $C_{imp}=C(J^*)-C(0)$ which is defined as
+Using the self-energy we calculate the impurity specific heat defined as $C_{imp}=C(J^*)-C(0)$ which is defined as
 \begin{eqnarray}
-C_{imp} &=& \sum_{\Lambda,\sigma} \beta \bigg[ \frac{(\bar{\epsilon}_{\Lambda})^2 e^{\beta \bar{\epsilon}_{\Lambda}}}{( e^{\beta \bar{\epsilon}_{\Lambda}} +1)^2}  -\frac{({\epsilon}_{\Lambda})^2 e^{\beta {\epsilon}_{\Lambda}}}{( e^{\beta {\epsilon}_{\Lambda}} +1)^2} \bigg]
+C_{imp} &=& \sum_{\Lambda,\sigma} \beta \bigg[ \frac{(\bar{\epsilon}_{\Lambda})^2 e^{\beta \bar{\epsilon}_{\Lambda}}}{( e^{\beta \bar{\epsilon}_{\Lambda}} +1)^2}  -\frac{({\epsilon}_{\Lambda})^2 e^{\beta {\epsilon}_{\Lambda}}}{( e^{\beta {\epsilon}_{\Lambda}} +1)^2} \bigg]~.
 \end{eqnarray}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{plt/all/FINAL_fitted_Cv_t_0p1.png}
+\includegraphics[width=0.7\textwidth]{plt/FINALfittedCvt0p1.png}
 \caption{This figure shows the variation of the impurity specific heat with the temperature.}
@@
 Using the self-energy obtained above, we extract the low-temperature behaviour of the impurity specific heat in the two-channel model for $t=0.1$ and $\mathcal{J}=1$, and it is shown in fig,~\ref{fig:Cv_imp}.
-We find that at low temperatures, the Sommerfield coefficient \(C_\text{imp}/T\) follows a logarithmic behavior for the two-channel case, which is in agreement with the results known in the literature [CITE].
+We find that at low-temperatures, the Sommerfeld coefficient \(C_\text{imp}/T\) follows a logarithmic behaviour for the two-channel case, which is in agreement with the results known in the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,
+parcollet_olivier_large_N,affleck_2005,emery_kivelson,clarke_giamarchi_1993,zarand_2000,
+vondelft_prl_1998,schofield_1997,bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991,
+andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002,
+sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}.
 \begin{eqnarray}
-\frac{C_{imp}}{T} \propto \log T
+\frac{C_{imp}}{T} \propto \log T~.
 \end{eqnarray}
-
-To calculate the magnetic susceptibilty, we numerically diagonalise the low-energy effective Hamiltonain, and use the following expression:
+To calculate the magnetic susceptibility, we numerically diagonalise the low-energy effective Hamiltonian, and use the following expression:
 \begin{eqnarray}
-\chi &=& \beta\bigg[\frac{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} \langle \bar{S}^{z2} \rangle}{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} } -\frac{\sum e^{-\beta \epsilon_{\Lambda}} \langle S^{z2 }\rangle }{\sum e^{-\beta \epsilon_{\Lambda}} } \bigg]
+\chi &=& \beta\bigg[\frac{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} \langle \bar{S}^{z2} \rangle}{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} } -\frac{\sum e^{-\beta \epsilon_{\Lambda}} \langle S^{z2 }\rangle }{\sum e^{-\beta \epsilon_{\Lambda}} } \bigg] ~.
 \end{eqnarray}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{plt/all/NFL_Chi_log_0p1}
-\caption{Suseptibility}
+\includegraphics[width=0.7\textwidth]{plt/NFLChilog0p1}
+\caption{Susceptibility}
 \label{fig:NFL_susecptibility}
 \end{figure}
-The result is shown in fig.~\ref{fig:NFL_susecptibility}, and we find that at low tempertures, the suseptibility has a logarithmic behavior.
+The result is shown in fig.~\ref{fig:NFL_susecptibility}, and we find that at low temperatures, the susceptibility has a logarithmic behaviour.
 \begin{eqnarray}
@@
 
-We also calculated the Wilson ratio $C_{imp}/T\chi$, and we find that taking upto three sites on each conduction channel leads to a value of $ W = 8.3$, which is greater than the known value of \(8/3\).
+We also calculated the Wilson ratio $C_{imp}/T\chi$, and we find that taking up to three sites on each conduction channel leads to a value of $ W = 8.3$, which is greater than the known value of \(8/3\)~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,
+parcollet_olivier_large_N,affleck_2005,emery_kivelson,clarke_giamarchi_1993,zarand_2000,
+vondelft_prl_1998,schofield_1997,bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991,
+andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002,
+sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}.
 We find that taking less number of sites leads to a lower value of \(W\), which shows that taking more number of sites will lead to a value of \(W\) that is lower than \(8.3\) and closer to \(8/3\).
@@
 \subsection{Three channel LEH}
-Similar to the two channel case, we here calculate the low energy effective Hamiltonain for three channel Kondo problem by introducing the real space hoppting on top of the zero mode three-channel stargraph model.
-This zero mode three channel stargraph model has three fold degenerate ground states with total $2^4=16$ states in the eigen spectrum.
+Similar to the two channel case, we here calculate the low energy effective Hamiltonian for three channel Kondo problem by introducing the real space hopping on top of the zero mode three-channel star graph model.
+This zero mode three channel star graph model has three fold degenerate ground states with total $2^4=16$ states in the eigenspectrum.
 The three degenerate ground states are given as
-\begin{eqnarray}
-|\alpha_{-1}\rangle &=& c|1000 \rangle-b (|0100 \rangle + |0010 \rangle+ | 0001 \rangle) \nonumber\\
-|\alpha_{+1}\rangle &=& b(|1110 \rangle+ | 1101 \rangle + | 1011 \rangle)-c | 0111 \rangle \nonumber\\
-|\alpha_0\rangle &=& -a(|1100 \rangle + |1010\rangle +|1001 \rangle)\nonumber\\
-&&~~~~~~~+a(|0110 \rangle+| 0101 \rangle +| 0011\rangle)
-\end{eqnarray}
+\begin{gather}
+|\alpha_{-1}\rangle = c|1000 \rangle-b (|0100 \rangle + |0010 \rangle+ | 0001 \rangle), ~ ~ |\alpha_{+1}\rangle = b(|1110 \rangle+ | 1101 \rangle + | 1011 \rangle)-c | 0111 \rangle,\\
+|\alpha_0\rangle = -a(|1100 \rangle + |1010\rangle +|1001 \rangle) + a(|0110 \rangle+| 0101 \rangle +| 0011\rangle)~,
+\end{gather}
 where $a=0.408$, $b=0.289$, $c=0.866$.
@@
 \begin{eqnarray}
-H^{(2)}_{eff, diag} &=& - \frac{7.2 J^2}{\alpha} \hat{I}
+H^{(2)}_{eff, diag} &=& - \frac{7.2 J^2}{\alpha} \hat{I}~.
 \end{eqnarray}
-The contribution associater to different ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$ is given respectively as $- \frac{2.4 J^2}{\alpha} \hat{I} + \hat{\mathcal{F}},- \frac{2.4 J^2}{\alpha} \hat{I} ,- \frac{2.4 J^2}{\alpha} \hat{I} - \hat{\mathcal{F} }$,
-where $\hat{\mathcal{F}}$ is a function of diagonal number oprators of sites nearest neighbor to the zeroth site of each channels.
+The contribution associated with different ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$ is given respectively as $- \frac{2.4 J^2}{\alpha} \hat{I} + \hat{\mathcal{F}},- \frac{2.4 J^2}{\alpha} \hat{I} ,- \frac{2.4 J^2}{\alpha} \hat{I} - \hat{\mathcal{F} }$,
+where $\hat{\mathcal{F}}$ is a function of diagonal number operators of sites nearest neighbor to the zeroth site of each channels.
 The off-diagonal terms in the LEH is appearing due to the scattering between pair of degenerate states $(\alpha_0,\alpha_{+1})$ and $(\alpha_0,\alpha_{-1})$, there is no contribution in the second order coming from the scattering between $(\alpha_{-1},\alpha_{+1})$.
-The effective low energy Hamiltonian in the second ordere is given as
-
-\begin{widetext}
+The effective low energy Hamiltonian in the second order is given as
 \begin{eqnarray}
-H^{(2)}_{eff,off-diag} &=& \sum_{\substack{(ijk)=\\(123),(231),(312)}}\bigg[ c_{i\uparrow}c_{i\downarrow}^{\dagger} \bigg( -2ab \bigg\{ \Sigma_{jk} +c_{j\uparrow}^{\dagger}c_{j\downarrow}c_{k\uparrow}c_{k\downarrow}^{\downarrow} \bigg\} -ac(\Omega_{jk}+\tilde{\Omega}_{jk}) \bigg) + ~~\textrm{h.c.}\bigg] \otimes \hat{\Xi}_l
+H^{(2)}_{eff,off-diag} &=& \sum_{\substack{(ijk)=\\(123),(231),(312)}}\bigg[ c_{i\uparrow}c_{i\downarrow}^{\dagger} \bigg( -2ab \bigg\{ \Sigma_{jk} +c_{j\uparrow}^{\dagger}c_{j\downarrow}c_{k\uparrow}c_{k\downarrow}^{\downarrow} \bigg\} -ac(\Omega_{jk}+\tilde{\Omega}_{jk}) \bigg) + ~~\textrm{h.c.}\bigg] \otimes \hat{\Xi}_l~,
 \end{eqnarray}
-\end{widetext}
-where different operators are defined as
+where the different operators have the following definitions:
 \begin{gather}
-\Sigma_{i,j} = n_{i\uparrow}(1-n_{i\downarrow}) (1-n_{j\uparrow})n_{j\downarrow} + (1-n_{i\uparrow})n_{i\downarrow} n_{j\uparrow} (1 -n_{j\downarrow}), ~ ~\Omega_{i,j} =4S_i^z S_j^z n_{i\uparrow} n_{j\uparrow}, ~ ~ \tilde{\Omega}_{i,j} = 4S_{i}^zS_j^z (1-n_{i\uparrow})(1-n_{j\uparrow}) \nonumber\\
- \hat{\Xi}_l=  ( c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.})
+\Sigma_{i,j} = n_{i\uparrow}(1-n_{i\downarrow}) (1-n_{j\uparrow})n_{j\downarrow} + (1-n_{i\uparrow})n_{i\downarrow} n_{j\uparrow} (1 -n_{j\downarrow}), ~ ~\Omega_{i,j} =4S_i^z S_j^z n_{i\uparrow} n_{j\uparrow}, ~ ~ \tilde{\Omega}_{i,j} = 4S_{i}^zS_j^z (1-n_{i\uparrow})(1-n_{j\uparrow}) \nonumber~,\\
+ \hat{\Xi}_l=  ( c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.})~.
 \end{gather}
@@
 \begin{gather}
-	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\beta= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~,~~
+	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\beta= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~.
 \end{gather}
@@
 \begin{gather}
-	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~, \\
-	\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)},~T_{(j)} \equiv \text{Tr}\left(H_{(j)}c_{j}\right)~,\\
-	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} T_{(j)}~.
+	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ ~\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)},~T_{(j)} \equiv \text{Tr}\left(H_{(j)}c_{j}\right)~,~ ~\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} T_{(j)}~.
 \end{gather}
@@
 The higher order generator itself has two scattering processes, such that the entire renormalisation term \(c^\dagger_{q\beta} T \eta\) has in total three coherent processes.
-The complete generator upto third order can be written as
-\begin{widetext}
+The complete generator up to third order can be written as
 \begin{equation}\begin{aligned}
-	\eta = \frac{1}{\hat \omega - H_D}T^\dagger c \simeq \frac{1}{\omega^\prime - H_D}T^\dagger c + \frac{1}{\omega^\prime - H_D}H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X
+	\eta = \frac{1}{\hat \omega - H_D}T^\dagger c \simeq \frac{1}{\omega^\prime - H_D}T^\dagger c + \frac{1}{\omega^\prime - H_D}H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X~,
 \end{aligned}\end{equation}
@@
 	\label{full_ren}
-	\Delta H_{(j)} = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c  + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(2)}_{(j)}} + \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(3)}_{(j)}}
+	\Delta H_{(j)} = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c  + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(2)}_{(j)}} + \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(3)}_{(j)}}~.
 \end{equation}
-\(\Delta H^{(2)}_{(j)}\) and \(\Delta H^{(3)}_{(j)}\) are the renormalisation arising from the the second and third order processes respectively.
+\(\Delta H^{(2)}_{(j)}\) and \(\Delta H^{(3)}_{(j)}\) are the renormalisation arising from the second and third order processes respectively.
 
@@
 	\label{H_spin_S}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{m_d=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_{m_d} \ket{m_d}\bra{m_d} c^\dagger_{k \sigma}c_{l \sigma} + \sum_{kl} \sum_{m_d=-S}^{S-1} J^t_{m_d} \left(\ket{m_d+1}\bra{m_d} s^-_{kl}  + \text{h.c.}\right)
+	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{m_d=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_{m_d} \ket{m_d}\bra{m_d} c^\dagger_{k \sigma}c_{l \sigma} + \sum_{kl} \sum_{m_d=-S}^{S-1} J^t_{m_d} \left(\ket{m_d+1}\bra{m_d} s^-_{kl}  + \text{h.c.}\right)~,
 \end{aligned}\end{equation}
-\end{widetext}
 where \(k,l\) sum over the momentum states, \(\sigma\) sums over the spin indices, \(J^\sigma_m = \frac{1}{2} \sigma m J\) in the UV Hamiltonian, and \(J^t_{m} = J\frac{1}{2}\sqrt{S(S+1) - m(m+1)}\) is the coupling that connects \(\ket{m}\) and \(\ket{m+1}\).
@@
 There are 7 such terms: \(z|z, \pm|\mp, z|\pm, \pm|z\).
-Each of these terms occur both in the particle and the hole sectors.
+Each of these terms occurs both in the particle and the hole sectors.
 We will demonstrate the calculation of two of these terms.
 The \(z|z\) \(+|-\) terms evaluate in the following manner.
-\begin{widetext}
+
 \begin{align}
-	z|z: & \sum_{kk^\prime,m,\sigma} c^\dagger_{q \sigma} c_{k^\prime \sigma} \ket{m}\bra{m}\frac{{J^\sigma_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}\sigma S_d^z}\ket{m}\bra{m} c^\dagger_{k \sigma}c_{q \sigma} = -\sum_{kk^\prime,m,\sigma}n_{q \sigma}\frac{{J^\sigma_m}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma} \ket{m}\bra{m}}{\omega_{m, \sigma} - \frac{D}{2} + \frac{J}{2}\sigma m}\\
-	+|-: & \sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m+1, \uparrow} - \frac{D}{2} + \frac{J}{2}\left( m+1 \right) }
+	z|z: & \sum_{kk^\prime,m,\sigma} c^\dagger_{q \sigma} c_{k^\prime \sigma} \ket{m}\bra{m}\frac{{J^\sigma_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}\sigma S_d^z}\ket{m}\bra{m} c^\dagger_{k \sigma}c_{q \sigma} = -\sum_{kk^\prime,m,\sigma}n_{q \sigma}\frac{{J^\sigma_m}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma} \ket{m}\bra{m}}{\omega_{m, \sigma} - \frac{D}{2} + \frac{J}{2}\sigma m}~,\\
+	+|-: & \sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m+1, \uparrow} - \frac{D}{2} + \frac{J}{2}\left( m+1 \right) }~.
 \end{align}
-\end{widetext}
 We similarly compute the rest of the terms.
@@
 To compare with the spin-\(\frac{1}{2}\) RG equations, we will transform the general spin-\(S\) \(\omega\) to the spin-\(\frac{1}{2}\) \( \omega\), using \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).
-
 The renormalisation in \(J^\sigma_m\) is
@@
 \begin{equation}\begin{aligned}
-	\Delta J^+_m = -n(D)\frac{\sum_\sigma \left( J^\sigma_m \right) ^2 + \sum_\sigma \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{2\left(\omega - \frac{D}{2} + \frac{J}{4}\right)}\\
-	= -n(D)\frac{J^2}{4}\frac{S(S+1)}{\omega - \frac{D}{2} + \frac{J}{4}}
+	\Delta J^+_m = -n(D)\frac{\sum_\sigma \left( J^\sigma_m \right) ^2 + \sum_\sigma \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{2\left(\omega - \frac{D}{2} + \frac{J}{4}\right)} = -n(D)\frac{J^2}{4}\frac{S(S+1)}{\omega - \frac{D}{2} + \frac{J}{4}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J^-_m = -n(D)\frac{1}{2}\frac{\left( J^t_{m-1} \right) ^2 - \left(J^t_{m}\right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{4}\frac{n(D) m J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
+	\Delta J^-_m = -n(D)\frac{1}{2}\frac{\left( J^t_{m-1} \right) ^2 - \left(J^t_{m}\right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{4}\frac{n(D) m J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta_\text{p sector} J = -\frac{1}{2}n(D)\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
+	\Delta_\text{p sector} J = -\frac{1}{2}n(D)\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J^t_m &= - \frac{n(D)J^t_m \left( J^\downarrow_m + J^\uparrow_{m+1} \right) }{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{2}\frac{n(D)J^t_m J}{\omega - \frac{D}{2} + \frac{J}{4}}
+	\Delta J^t_m &= - \frac{n(D)J^t_m \left( J^\downarrow_m + J^\uparrow_{m+1} \right) }{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{2}\frac{n(D)J^t_m J}{\omega - \frac{D}{2} + \frac{J}{4}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J_\text{p sector} &= -\frac{1}{2}\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
+	\Delta J_\text{p sector} &= -\frac{1}{2}\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J^{(2)} &= -\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
+	\Delta J^{(2)} &= -\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
 \end{aligned}\end{equation}
 
-We now come to the third order renormalisation.
+We now come to the third-order renormalisation.
 Following eq.~\ref{full_ren}, the next order renormalisation is
@@
 	\label{psector_3rd_ren}
-	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c \\
-	+ c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X
+	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X~.
 \end{aligned}\end{equation}
 The first term will be of the form
-\begin{widetext}
 \begin{equation}\begin{aligned}
-	\sum_{q,k,l_1} c^\dagger_{q\beta, l_1}c_{k \alpha, l_1}\ket{m_1}\bra{m_2} \frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z} \ket{m_2} c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \bra{m_3}\frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z}\ket{m_3}\bra{m_4}c^\dagger_{k\alpha, l_1}c_{q\beta, l_1}
+	\sum_{q,k,l_1} c^\dagger_{q\beta, l_1}c_{k \alpha, l_1}\ket{m_1}\bra{m_2} \frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z} \ket{m_2} c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \bra{m_3}\frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z}\ket{m_3}\bra{m_4}c^\dagger_{k\alpha, l_1}c_{q\beta, l_1}~.
 \end{aligned}\end{equation}
-\end{widetext}
 We have not bothered to write all the summations and the couplings correctly, because we will only simplify the denominator here. Evaluating the inner products gives
 \begin{equation}\begin{aligned}
-	\sum_{qk,l_1} \frac{\ket{m_1}\bra{m_4}c^\dagger_{q\beta}c_{k \alpha}c^\dagger_{k_1 \sigma_1, l_2}}{\omega_{m_2,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_2}{4}}  \frac{c_{k_2 \sigma_2,l_2}c^\dagger_{k\alpha}c_{q\beta}}{\omega_{m_3,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_3}{4}}
+	\sum_{qk,l_1} \frac{\ket{m_1}\bra{m_4}c^\dagger_{q\beta}c_{k \alpha}c^\dagger_{k_1 \sigma_1, l_2}}{\omega_{m_2,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_2}{4}}  \frac{c_{k_2 \sigma_2,l_2}c^\dagger_{k\alpha}c_{q\beta}}{\omega_{m_3,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_3}{4}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}\sum_{qk,l_1} \frac{\hat n_{q\beta}\left(1 - \hat n_{k\alpha}\right)}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2}
+	\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}\sum_{qk,l_1} \frac{\hat n_{q\beta}\left(1 - \hat n_{k\alpha}\right)}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	-\frac{1}{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}
+	-\frac{1}{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}~.
 \end{aligned}\end{equation}
@@
 	\label{first_group}
-	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{2}\lambda_{3}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}
+	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{2}\lambda_{3}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}~.
 \end{aligned}\end{equation}
@@
 
-The second term in eq.~\ref{psector_3rd_ren} can be evaluated in an almost identical fashion. The integral here be negative of the first term, because of an exchange in the scattering processes.
+The second term in eq.~\ref{psector_3rd_ren} can be evaluated in an almost identical fashion. The integral here will be negative of the first term, because of an exchange in the scattering processes.
 \begin{equation}\begin{aligned}
 	\label{second_group}
-	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{3}\lambda_{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}
+	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{3}\lambda_{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}~.
 \end{aligned}\end{equation}
-
-The first group of terms (those that appear in \ref{first_group}) in the particle sector can be represented as \(a|b^\prime|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three ceonnected processes.
+The first group of terms (those that appear in \ref{first_group}) in the particle sector can be represented as \(a|b^\prime|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three connected processes.
 The \(\prime\) on \(b\) indicates that it is the state of the electrons \textit{not being decoupled}.
@@
 We will only calculate the terms in the particle sector, the ones in hole sector will be equal to these because of particle-hole symmetry. The full list of terms is:
+
 $z|z^\prime|z\quad$
@@
 The total renormalisation in  \(J^\sigma_m\) is
-\begin{widetext}
 \begin{equation}\begin{aligned}
-	\Delta J^\sigma_m = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\left[\left( J^t_{m-1} \right)^2 J^\sigma_m + \left( J^t_m \right)^2 J^\sigma_m - \left( J^t_{m-1} \right)^2 J^\sigma_{m-1} - \left(J^t_m\right)^2 J^\sigma_{m+1} \right] = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3 m \sigma
+	\Delta J^\sigma_m = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\left[\left( J^t_{m-1} \right)^2 J^\sigma_m + \left( J^t_m \right)^2 J^\sigma_m - \left( J^t_{m-1} \right)^2 J^\sigma_{m-1} - \left(J^t_m\right)^2 J^\sigma_{m+1} \right] = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3 m \sigma~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J^{(3)} = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3
+	\Delta J^{(3)} = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J = -\frac{n(D) J^2}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3
+	\Delta J = -\frac{n(D) J^2}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3~.
 \end{aligned}\end{equation}
-\end{widetext}
 

### 2022-04-28 Manuscript27April2022/mscript_mck_full.tex
final version sent to  collaborators

--- 2022-04-26 Manuscript26April2022/mscript_mck_full.tex
@@
 \usepackage[hidelinks]{hyperref}
-\bibliographystyle{apsrev4-1}
+\bibliographystyle{apsrev4-2}
 \begin{document}
 
-\title{Frustration shapes multi-channel Kondo physics: A star graph perspective}
+\title{Frustration shapes multi-channel Kondo physics: a star graph perspective}
 \author{Siddhartha Patra}
@@
 \begin{abstract}
-Our study of the multi-channel Kondo (MCK) model using the recently developed unitary renormalization group (URG) technique shows the importance of ground state degeneracy in explaining various important properties like the breakdown of screening and the presence of local non-Fermi liquids.
-The impurity susceptibility of the zero-bandwidth intermediate coupling fixed point Hamiltonian shows power-law divergence at low temperature, signaling its critical nature.
-Despite the absence of inter-channel coupling in the MCK Hamiltonian, the study of mutual information between two channels shows non-zero correlation among them.
-The presence of non-local twist and translation operators shows the topological nature of the degenerate ground state manifold.
-Upon disentangling the impurity spin, we find the presence of local Mott-liquid made out of inter-channel quantum scatterings.
-We derive the low energy effective Hamiltonian (LEH) upon the addition of excitation to the zero-bandwidth RG fixed point Hamiltonian for the two and three-channel cases, both of which show the absence of local Fermi liquid phase due to exact cancellation coming from different degenerate ground states, and the presence of non-Fermi liquids with inter-channel quantum fluctuations.
-Computation of various thermodynamic quantities like specific heat and susceptibility in the ground state of that non-Fermi liquid shows logarithmic scaling in low temperature, which agrees with the known result in the literature.
-The presence of local marginal Fermi liquid shows the orthogonality catastrophe in the two-channel Kondo model.
-Discontinuity in various entanglement measures as we add the excitations on top of the zero-bandwidth model by tuning the real space nearest-neighbor hopping strength reinforces the presence of orthogonality catastrophe.
-Strong and weak coupling duality also sheds light on the presence of an intermediate coupling fixed point in the MCK problem.
-The study of channel anisotropy under URG reveals series of quantum phase transitions due to the change in ground state degeneracy.
-Our work thus shows a template of studying the zero-bandwidth model followed by the systematic addition of excitations, which can be used to study other impurity problems.
+We study the overscreened multi-channel Kondo (MCK) model using the recently developed unitary renormalization group (URG) technique.
+Our results display the importance of ground state degeneracy in explaining various important properties like the breakdown of screening and the presence of local non-Fermi liquids.
+The impurity susceptibility of the intermediate coupling fixed point Hamiltonian in the zero-bandwidth (or star graph) limit shows a power-law divergence at low temperature, signalling its critical nature.
+Despite the absence of inter-channel coupling in the MCK fixed point Hamiltonian, the study of mutual information between any two channels shows non-zero correlation between them.
+A spectral flow analysis of the star graph reveals that the degenerate ground state manifold possesses topological quantum numbers.
+%The presence of non-local twist and translation operators shows the topological nature of the degenerate ground state manifold. 
+Upon disentangling the impurity spin from its partners in the star graph, we find the presence of a local Mott liquid arising from inter-channel scattering processes.
+The low energy effective Hamiltonian obtained upon adding a finite non-zero conduction bath dispersion to the star graph Hamiltonian for both the two and three-channel cases displays the presence of local non-Fermi liquids arising from inter-channel quantum fluctuations.
+Specifically, we confirm the presence of a local marginal Fermi liquid in the two channel case, whose properties
+%of these non-Fermi liquids Computation of various thermodynamic quantities like specific heat and susceptibility in the ground state of that non-Fermi liquid 
+show logarithmic scaling at low temperature as expected.
+%, which agrees with the known result in the literature. The presence of local marginal Fermi liquid shows the orthogonality catastrophe in the two-channel Kondo model. 
+Discontinuous behaviour is observed in several measures of ground state entanglement, signalling
+the underlying orthogonality catastrophe associated with the degenerate ground state manifold. 
+% as we add the excitations on top of the zero-bandwidth model by tuning the real space nearest-neighbor hopping strength reinforces the presence of orthogonality catastrophe. 
+We extend our results to underscreened and perfectly screened MCK models through duality arguments.
+%a Strong and weak coupling duality also sheds light on the presence of an intermediate coupling fixed point in the MCK problem. 
+A study of channel anisotropy under renormalisation flow reveals a series of quantum phase transitions due to the change in ground state degeneracy.
+Our work thus presents a template for the study of how a degenerate ground state manifold arising from symmetry and duality properties in a multichannel quantum impurity model can lead to novel multicritical phases at intermediate coupling.
+%of studying the zero-bandwidth model followed by the systematic addition of excitations, which can be used to study other impurity problems.
 
@@
 %{\color{blue}
-Local antiferromagnetic exchange interaction between a spin-\(\frac{1}{2}\) impurity and a metal gives rise to the well-understood phenomenon of Kondo effect~\cite{hewson1993}.
+A local antiferromagnetic exchange interaction between a spin-\(\frac{1}{2}\) impurity and its host metal gives rise to the well-understood phenomenon of the Kondo effect (\cite{kondo1964resistance}, see ~\cite{hewson1993} for an extensive discussion).
 Here, the impurity local moment is screened by the conduction electrons at temperatures below a certain scale called the Kondo temperature~\cite{anderson1969exact,anderson1970exact,anderson1970,wilson1975,andreiKondoreview,
 tsvelickKondoreview,affleck1993exact,affleck1995conformal}, leading to a spin singlet ground state and local Fermi liquid excitations above that ground state~\cite{nozieres1974fermi,hewsonp}.
-The screening manifests as an initial increase at temperatures below the Kondo temperature, followed by a saturation of the resistivity of the metal~\cite{Kondo,Zhang2013}, and in the saturation of the impurity contribution to the magnetic susceptibility at low temperatures~\cite{wilson1975,andreiKondoreview,tsvelickKondoreview}.
+The screening manifests as an initial increase at temperatures below the Kondo temperature, followed by a saturation of the resistivity of the metal~\cite{kondo1964resistance,Zhang2013}, and in the saturation of the impurity contribution to the magnetic susceptibility at low temperatures~\cite{wilson1975,andreiKondoreview,tsvelickKondoreview}.
 Generalisations of this model are obtained by taking impurities of higher spin~\cite{hewson1993,Noz_blandin_1980,affleck1993exact}, adding interactions between them~\cite{affleck_1992,affleck_ludwig_jones_1992,georges_1999,zarand_chung_2006,
-mitchell_logan_2011,mitchell_sela_2012,konig_coleman_2021}, by promoting to a Kondo lattice of impurities~\cite{coleman_1987,millis_lee_1987,auerbach_1986,rice_ueda_1986,stewart_1984} or by considering a correlated metal~\cite{granath_1998}.
+mitchell_logan_2011,mitchell_sela_2012,konig_coleman_2021}, by promoting the model to a lattice of Kondo impurities~\cite{coleman_1987,millis_lee_1987,auerbach_1986,rice_ueda_1986,stewart_1984} or by considering the case of a correlated host metal~\cite{granath_1998}.
 One can also construct multi-channel Kondo (MCK) models by allowing \(K\) conduction electron channels \( \left(K > 1\right) \) to interact with a spin-\(\frac{1}{2}\) impurity~($S_{d}$)~\cite{Noz_blandin_1980,zawadowski_1980,cox_zawadowski_1998} via a common exchange coupling \(\mathcal{J}\).
-Using conformal field theory~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005}, bosonization~\cite{emery_kivelson,clarke_giamarchi_1993,zarand_2000,vondelft_prl_1998,schofield_1997}, numerical renormalization group~\cite{bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991}, Bethe ansatz~\cite{andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002} and other methods~\cite{sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}, it has been shown that for the over-screened systems \(\left(K > 2S_d\right)\), the low energy physics is of the non-Fermi liquid type, displaying anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (ensuring that temperature is taken to zero before the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
-This anomalous divergent behaviour is actually a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: it is susceptible to perturbations that introduce channel isotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}.
+Using conformal field theory~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005}, bosonization~\cite{emery_kivelson,clarke_giamarchi_1993,zarand_2000,vondelft_prl_1998,schofield_1997}, numerical renormalization group~\cite{bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991}, Bethe ansatz~\cite{andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002} and other methods~\cite{sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}, it has been shown that for the over-screened systems \(\left(K > 2S_d\right)\), the low energy physics is of the non-Fermi liquid type obtained at an intermediate coupling fixed point of the RG flows~\cite{Noz_blandin_1980}.
+Further, the system displays anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (upon ensuring that temperature is taken to zero before the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
+This anomalous divergent behaviour is a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: the ground state is susceptible to perturbations that introduce channel isotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}.
 This makes the experimental realisation of such states quite challenging.
@@
 
-The importance of ground state degeneracy and quantum-mechanical frustration in the MCK problem has not received sufficient attention, even though they play crucial roles in determining the non-Fermi liquid physics and the quantum criticality of the system.
+The importance of ground state degeneracy and quantum-mechanical frustration in the MCK problem has not received sufficient attention, even though they play crucial roles in determining the quantum criticality and associated non-Fermi liquid physics of the system.
 This is, at least partially, due to the lack of an intermediate-coupling effective Hamiltonian that describes the low-energy physics of the MCK (i.e., reveals the nature of the excitations).
-The term frustration in this context refers to the inability of the impurity spin to bind with the conduction channels and get completely screened by forming a maximally-entangled singlet.
-The absence of such frustration in the single-channel spin-1/2 Kondo model (and more generally, the exact screening variant of the MCK) means that imperfect screening \((K \neq 2S_d)\) should lead to dramatic differences in the multi-channel models.
-Indeed, we demonstrate that there exists an orthogonality catastrophe in the imperfectly screened MCK models leading to the non-Fermi liquid behaviour of its low-energy excitations, and that it is directly related to the existence of a degenerate ground state manifold.
-The effects of these non-Fermi liquid low energy excitations are expected to show up in measures of many-particle entanglement; the lack of an intermediate coupling Hamiltonian has, however, prevented the study of the renormalisation group (RG) evolution of such measures~\cite{alkurtass_affleck_2016,kim_shim_2021}.
-Our approach enables a comparison of, for instance, the inter-channel mutual information along the RG flow and as functions of the excitation energies, providing insight into the nature of the fixed point theory.
+\textit{Frustration} in this context refers to the inability of the impurity spin to bind with the conduction channels, and be screened completely by forming a maximally-entangled singlet ground state.
+The absence of such frustration in the single-channel spin-1/2 Kondo model (and more generally, the exact screening variant of the MCK) means that imperfect screening \((K \neq 2S_d)\) leads to dramatic differences in the multi-channel models.
+Indeed, we demonstrate that there exists an orthogonality catastrophe in the imperfectly screened MCK models that leads to the non-Fermi liquid behaviour of its low-energy excitations, and that this is directly related to the existence of a degenerate ground state manifold.
+The effects of these non-Fermi liquid low energy excitations are expected to appear in measures of many-particle entanglement; the lack of an intermediate coupling Hamiltonian has, however, prevented the study of the renormalisation group (RG) evolution of such measures~\cite{alkurtass_affleck_2016,kim_shim_2021}.
+Importantly, our approach enables a comparison of, for instance, the inter-channel mutual information along the RG flow and as functions of the excitation energies, providing insight into the nature of the fixed point theory.
 %}
 
-To obtain the RG flow of the MCK model, we have employed the recently developed unitary renormalization group (URG) technique~\cite{anirbanurg1,anirbanurg2}.
-The method has been applied on several fermionic and spin problems like the single-channel Kondo model~\cite{kondo_urg}, the kagome antiferromagnet~\cite{santanukagome}, the 1D~\cite{1dhubjhep} and 2D Hubbard models~\cite{anirbanmott1,anirbanmott2}, the reduced-BCS model~\cite{siddharthacpi} as well as other generalised models of interacting electrons with and without translation invariance~\cite{anirbanurg2}.
-The URG proceeds by decoupling number fluctuations in the high energy electronic states.
-Iteratively applying this URG method on the channel-isotropic MCK model leads to a low energy fixed point Hamiltonian at intermediate Kondo coupling.
+To obtain the RG flow of the MCK model, we have employed the unitary renormalization group (URG) technique developed recently by  some of us~\cite{anirbanurg1,anirbanurg2}.
+The method has been applied on several fermionic and spin problems like the single-channel Kondo model~\cite{kondo_urg}, the kagome antiferromagnet~\cite{santanukagome}, the 1D~\cite{1dhubjhep} and 2D Hubbard models~\cite{anirbanmott1,anirbanmott2,mukherjeeMERG2022}, the reduced-BCS model~\cite{siddharthacpi} as well as other generalised models of interacting electrons with and without translation invariance~\cite{anirbanurg2}.
+The URG proceeds by resolving the number fluctuations in the electronic Fock states at high energies by the iterative application of many-particle unitary transformations, leading to their successive decoupling from the states lying at lower energies.
+Applying this URG method to the channel-isotropic MCK model leads to a low-energy fixed point Hamiltonian at the intermediate (Kondo) coupling fixed point of Ref.\cite{Noz_blandin_1980}.
 In further analysing the effective Hamiltonian, we focus initially on the zero bandwidth limit of this Hamiltonian (which corresponds to a frustrated quantum spin model on a star graph).
@@
 On decoupling the impurity spin from the conduction spin degrees of freedom within the star graph, we obtain an all-to-all Hamiltonian that represents a local Mott liquid phase.
-In section ~\ref{sec:excitations}, we obtain the low energy effective Hamiltonian for the low-lying excitations by including a dispersion into the conduction bath.
+In section \ref{sec:excitations}, we obtain the low energy effective Hamiltonian for the low-lying excitations by including a dispersion into the conduction bath.
 Notable features of this effective Hamiltonian include (i) the complete absence of local Fermi liquid terms, and (ii) the emergence of local non-Fermi liquid terms.
@@
 
-In section \ref{sec:ent_prop}, we study various entanglement signatures (like the von-Neumann entanglement entropy, mutual information, multipartite information, Bures distance) of the low energy fixed-point ground state of the MCK problem, with and without excitations.
-They reveal clear distinctions between the single- and MCK problems in the form of discontinuities.
-In \ref{sec:duality}, we discuss two duality transformations that exist for the MCK model - a strong-weak duality and an over-screened-under-screened duality.
-It is found that the transformations are constrained by the fixed point structure, and they impose relations between the under-screened and over-screened models.
+In section \ref{sec:ent_prop}, we study various entanglement signatures (e.g., von-Neumann entanglement entropy, mutual information, multipartite information, Bures distance) of the low energy fixed-point ground state of the MCK problem, with and without dispersion into the bath.
+The discontinuous behaviour observed in these measures for the MCK problem reveal clear distinctions from the single-channel case.
+In \ref{sec:duality}, we discuss two duality transformations that exist for the MCK model - a strong-weak duality, and an over-screened-under-screened duality.
+It is found that the transformations are constrained by the fixed point structure, and impose relations between the under-screened and over-screened models.
 In \ref{anisotropic_rg}, we show the robustness of the ground state degeneracy of the star graph model against the impurity-channel coupling anisotropy, and correlate it with a URG treatment of the channel anisotropic MCK.
 The isotropic fixed point is found to be unstable to asymmetry, leading to impurity phase transitions that lead to dramatic changes in the ground state degeneracy.
-For the sake of brevity, some supporting evidence and details of certain lengthy calculations are presented in Supplementary Materials~\cite{SM}.
+For the sake of brevity, some supporting evidence and details of certain lengthy calculations are presented in Supplementary Materials~\cite{SM}. Finally, we conclude in section \ref{conclusions}.
 
@@
 
-The derivation of the RG equation for the over-screened regime \((2S < K)\) of the spin-\(S\)-impurity \(K\)-channel Kondo problem is shown in detail in the Supplementary Materials (CITE).
+The derivation of the RG equation for the over-screened regime \((2S < K)\) of the spin-\(S\)-impurity \(K\)-channel Kondo problem is shown in detail in the Supplementary Materials~\cite{SM}.
 On decoupling circular isoenergetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\text{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
@@
 By the application of the twist operator $\hat{O}$, one can go from one degenerate ground state to another.
+We note that a similar exploration of the degenerate ground state manifold of spin-1/2 Heisenberg antiferromagnets on geometrically frustrated lattices via twist and translation operators has been conducted in Refs.\cite{pal2019magnetization,pal2020topological}.
 
@@
 \(I^3\) shows behavior similar to the mutual information - the highest \(I^2\) value is associated with the $\left(J^z\right)_\mathrm{min}$ state and it saturates in the limit of $K\gg 1$.
-One can measure $N-$partite information for a collection of subsystems (CSS) $\{\mathcal{A}_N\}\equiv\{A_1,A_2,\cdots,A_N\}$.
-To define the $N-$partite information, we first define the power set of the CSS $\{\mathcal{A}_N\}$ as $\mathcal{P}(\{\mathcal{A}_{N}\})$, and the collection of all subsets of $\mathcal{P}(\{\mathcal{A}_{N}\})$ with $m$ subsystems in it as $\mathcal{B}_m(\{\mathcal{A}_N\})\equiv \{ Q~| ~Q\subset \mathcal{P}(\{\mathcal{A}_{N}\}), |Q|=m \}$.
-We also define the union and intersection of all the subsystems present in $Q$ as ${V}_{\cup}({Q})\equiv \bigcup_{A\in Q} A$ and ${V}_{\cap}({Q})\equiv \bigcap_{A\in Q} A$ respectively.
-Then, the $N-$partite information that we are interested in is defined as
+The $N-$partite information for a collection of subsystems (CSS) $\{\mathcal{A}_N\}\equiv\{A_1,A_2,\cdots,A_N\}$ can also be defined
+as~\cite{siddharthatee} 
 \begin{equation}
@@
 \end{equation}
+where  $\mathcal{B}_m(\{\mathcal{A}_N\})\equiv \{ Q~| ~Q\subset \mathcal{P}(\{\mathcal{A}_{N}\}), |Q|=m \}$, and $\mathcal{P}(\{\mathcal{A}_{N}\})$ is the powerset of $\{\mathcal{A}_N\}$.
+For simplicity, we also define the union and intersection of all the subsystems present in $Q$ as ${V}_{\cup}({Q})\equiv \bigcup_{A\in Q} A$ and ${V}_{\cap}({Q})\equiv \bigcap_{A\in Q} A$ respectively.
+%One can measure $N-$partite information for a collection of subsystems (CSS) $\{\mathcal{A}_N\}\equiv\{A_1,A_2,\cdots,A_N\}$.
+To define the $N-$partite information, we first define the power set of the CSS $\{\mathcal{A}_N\}$ as $\mathcal{P}(\{\mathcal{A}_{N}\})$, and the collection of all subsets of $\mathcal{P}(\{\mathcal{A}_{N}\})$ with $m$ subsystems in it as $\mathcal{B}_m(\{\mathcal{A}_N\})\equiv \{ Q~| ~Q\subset \mathcal{P}(\{\mathcal{A}_{N}\}), |Q|=m \}$.
+We also define the union and intersection of all the subsystems present in $Q$ as ${V}_{\cup}({Q})\equiv \bigcup_{A\in Q} A$ and ${V}_{\cap}({Q})\equiv \bigcap_{A\in Q} A$ respectively.
+Then, the $N-$partite information that we are interested in is defined as
+%\begin{equation}
+%I^{N}_{\{\mathcal{A}_N\}} = \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.
+%\label{eq:I_N_definition}
+%\end{equation}
 \begin{figure}
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{conclusions}
+\par\noindent
+In summary, we have explored the low-energy behaviour of the MCK models using the unitary renormalization group (URG) method, and obtained insight into the role of ground state degeneracy and quantum-mechanical frustration in shaping the non-Fermi liquid physics and criticality.
+We have also obtained the zero-temperature phase diagram of the MCK problem and an effective Hamiltonian with a simple zero bandwidth limit (i.e., the star graph), and shown that it determines the ground state energy, wavefunction and degeneracy of the MCK models.
+The star graph is found to explain much of the physics of over-screening and criticality of the MCK: this includes the singularities in the susceptibility and magnetisation, as well as a reduction in the degree to which the impurity spin is compensated.
+This demonstrates the ground state degeneracy of the star graph (which is unity for single-channel, and greater for the over-screened models) as the key ingredient in leading to the qualitative and quantitative differences of the MCK from the single-channel Kondo model.
+The presence of ground state degeneracy also allows the construction of non-local twist operators and fractional excitations that span the degenerate ground state manifold.
+Integrating out the quantum fluctuations of the impurity leads to an all-to-all effective Hamiltonian for the local conduction bath spins of the star graph.
+This Hamiltonian is found to contain inter-channel quantum scattering in terms of electron-hole pairs, thereby creating a local Mott-liquid phase proximate to the impurity.
 \par 
-In summary, we have explored the low-energy behaviour of the MCK models using the unitary renormalization group (URG) method and obtained a better understanding of the role of ground state degeneracy and quantum-mechanical frustration in shaping the non-Fermi liquid physics and criticality.
-Using the unitary renormalization group technique, we have obtained the zero-temperature phase diagram of the MCK problem and an effective Hamiltonian with a simple zero bandwidth limit - the star graph, and it determines the ground state energy, wavefunction and degeneracy of the MCK models.
-This star graph is found to explain much of the physics of over-screening and criticality, including the singularities in the susceptibility and magnetisation, as well as a reduction in the degree to which the impurity spin is compensated.
-The overarching message there was that the ground state degeneracy of the star graph (which is unity for single-channel and greater for the over-screened models) was the key ingredient in leading to the qualitative and quantitative differences from the single-channel model
-The presence of ground state degeneracy also allows the construction of non-local twist operators and fractional excitations in the ground state manifold.
-Integrating out the quantum fluctuations of the impurity leads to an all-to-all effective Hamiltonian for the local bath spins, and the Hamiltonian is found to contain inter-channel quantum scattering in terms of electron-hole pairs, thereby creating a local Mott-liquid phase at the origin of the lattice.
-
-\par The low energy effective Hamiltonian (LEH) for the excitations is then obtain by considering fluctuations of the conduction bath on top of the ground state.
-The LEH for the 2-channel Kondo confirms absence of any Fermi liquid phase due to an exact cancellation across the ground state manifold, and the presence of inter-channel off-diagonal non-Fermi liquid terms.
-Our analysis reinforces the idea that the ground state degeneracy is crucial to the non-Fermi liquid physics and to the presence of such off-diagonal terms in the LEH.
-The existence of a marginal Fermi liquid within the effective Hamiltonian clearly displays the orthogonality catastrophe in the form of singularities that are absent at exact screening.
-Studies of various thermodynamic properties (presented in the Supplementary Material~\cite{SM}) from this 2-channel Kondo LEH like specific heat and susceptibility show logarithmic dependence at low temperature, in agreement with the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005,emery_kivelson,andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002}.
-
+The low energy effective Hamiltonian (LEH) for the excitations of the MCK problem is then obtained by considering fluctuations of the conduction bath lying above the ground state.
+The LEH for the 2-channel Kondo confirms the absence of any local Fermi liquid physics, as well as the presence of a local marginal Fermi liquid involving from inter-channel off-diagonal scattering processes.
+This reinforces the idea that the ground state degeneracy is crucial to the appearance of non-Fermi liquid physics at the MCK fixed point.
+Further, we also confirm that this arises from an orthogonality catastrophe in the form of singularities that are absent at exact screening.
+Studies of various thermodynamic properties (presented in the Supplementary Material~\cite{SM}) from this 2-channel Kondo LEH (e.g., specific heat and susceptibility) show logarithmic dependence at low temperature, in agreement with the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005,emery_kivelson,andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002}.
 \par 
-The non-diagonal nature of the LEH is further investigated through the several measures of entanglement.
-The entanglement entropy, calculated from the minimum \(J^z\) states, between the impurity and the outer spins, as well as between an outer spin and the rest saturate to \(\ln 2\) in the large channel limit saturate.
-The opposite behaviour happens in the maximum $J^z$ state, where the entanglement entropy decreases with the increase of channel number.
-The large values of inter-channel mutual information indicate high inter-channel correlation in the MCK ground state.
-The power-law dependence of the multi-partite information among the outer spins of the star graph model is similar to the power-law behavior of the all-to-all local Mott-liquid ground state.
-The presence of a discontinuity in the non-Fermi liquid ground state multi-channel entanglement as compared to the smooth behaviour in the single-channel counterpart again points to the orthogonality catastrophe in the low-energy phase of the multi-channel models.
-Higher discontinuity for a higher number of channels was observed in the Bures distance study.
-The URG study of the channel anisotropic MCK shows the critical and unstable nature of the isotropic fixed point; under any anisotropic perturbations, the RG flows go towards either the single-channel model or the symmetric MCK with one less channel coupled to the impurity.
+The non-diagonal nature of the low energy theory is further investigated through several measures of entanglement.
+The entanglement entropy calculated from (i) the minimum \(J^z\) states, (ii)between the impurity and the outer spins as well as (iii) that between an outer spin and the rest, is observed to saturate to \(\ln 2\) in the large channel limit.
+The opposite behaviour is observed in the maximum $J^z$ state, where the entanglement entropy decreases with the increase of channel number.
+Further, the large values of inter-channel mutual information indicate high inter-channel correlation in the MCK ground state.
+Indeed, the power-law dependence of the multi-partite information among the outer spins of the star graph model is similar to the power-law behavior of the all-to-all local Mott-liquid state.
+Importantly, the discontinuous behaviour in the entanglement entropy computed for the MCK ground state in the limit of vanishing bath dispersion, as compared to the smooth behaviour observed in its single-channel counterpart, points to the orthogonality catastrophe in the low-energy phase of the multi-channel models.
+We confirm this by noting a similar discontinuous behaviour in the Bures distance computed between the density matrices computed from the ground states of the star graph (i.e., zero bath dispersion bandwidth) and the MCK (i.e, a non-zero the bath dispersion bandwidth).
+This discontinuity in the Bures distance is observed to grow as the number of channels is increased.
+Finally, the URG study of the channel anisotropic MCK shows the expected critical nature of the channel isotropic fixed point: under any anisotropic perturbations, the RG flows go towards either the single-channel model or the symmetric MCK with one less channel coupled to the impurity.
 This is complemented by the study of the star graph ground state degeneracy which shows that the degeneracy changes only if one or more couplings vanishes.
-When combined, we can conclude that in the presence of channel anisotropy, the degeneracy of the MCK ground state does not change until the RG reaches the stable fixed point.
-
-\par This method serves as a template for the study of other quantum impurity systems.
-We have already seen that the degeneracy of the star graph is robust under anisotropy; one can perform similar studies in the presence of a superconducting gap that cuts off the ground state manifold from the excitations, hence providing the degeneracy a topological protection.
-The duality transformations then allow us to view the topologically protected ground state as a larger quantum spin which is essentially isolated.
-This holds immense potential for applications in quantum information and quantum computation.
-More fine-tuned behaviour can be obtained by studying the MCK model with an easy-axis anisotropy term \(\left(J^i\right)^2\) along one of the axes ($i$).
+Taken together, we conclude that in the presence of channel anisotropy, the degeneracy of the MCK ground state does not change until the RG reaches the stable fixed point with one (or more channels) completely disconnected.
+\par 
+We end by discussing some open directions. 
+%Our approach serves as a template for the study of other quantum impurity systems. 
+Our work presents a template for the study of how a degenerate ground state manifold arising from symmetry and duality properties in a multichannel quantum impurity model can lead to novel multicritical phases at intermediate coupling.
+Employed within an auxiliary model framework (such as dynamical mean-field theory), such quantum impurity models will likely unveil novel quantum critical points (or phases) in bulk lattice models of strongly correlated electrons and spins that arise from the competition of various quantum (or symmetry broken) orders.
+Now, we have already seen that the degeneracy of the star graph is robust under anisotropy.
+%Similar studies can be conducted for the case of superconducting leads, i.e., conduction baths with a superconducting gap. 
+Thus, it appears relevant to study the case of the MCK with superconducting leads, i.e., conduction baths with a superconducting gap.
+Specifically, it will be interesting to see whether the gap can separate the ground state manifold of the star graph from any low-energy excitations, providing thereby a protection for the topological quantum numbers associated with the degenerate ground state manifold.
+The duality transformations then allow us to view the protected ground state as that belonging to an isolated larger quantum spin.
+This holds potential for applications in quantum information and quantum computation (see \cite{lopes2020} for an alternate proposal based on an MCK model).
+Interesting behaviour may also be obtained by studying the MCK model with an easy-axis anisotropy term \(\left(J^i\right)^2\) along one of the axes ($i$).
 Such a term would, if it is able to survive the RG flows towards low energy, lift the degeneracy of the ground state and make it possible to achieve perfect screening even with \(K > 2S_d\).
+Further, understanding the nature of the multicriticality in the MCK model displayed upon introducing channel anisotropy is in itself an important problem (see \cite{zheng2021} for a recent work).
 One can also study the multi-channel lattice models~\cite{Piguet1997,shaw_1998} to better understand the role played by singlet frustration and ground state degeneracy in the competition between the local moment versus the heavy fermion sea.
+Finally, we note that experimental realisations of the star graph have been studied recently with regards to aspects of NMR-based quantum information processing such as algorithmic cooling and information scrambling (see \cite{mahesh2021} for a review).
+It will be interesting to see whether some of the results obtained by us for the spin-1/2 Heisenberg star graph can be tested experimentally in a similar manner.
 
 \acknowledgments
-SP and Anirban Mukherjee thanks the CSIR, Govt.
+S.
+Patra and Anirban Mukherjee thank the CSIR, Govt.
 of India and IISER Kolkata for funding through a research fellowship.
@@
 S.
-Lal
-thanks the SERB, Govt. of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
+Lal thanks the SERB, Govt.
+of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
 

### 2022-06-23 RefereeResponse.tex
completed first referee response

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb}
\usepackage[margin=0.5in]{geometry}
\usepackage{geometry}
\usepackage{color}
\usepackage{xcolor}
\geometry{legalpaper, portrait, margin=1in}
\DeclareUnicodeCharacter{2212}{-}
\DeclareUnicodeCharacter{03B8}{+}
\newcommand{\shat}{\hat{\mathbf{s}}}
\newcommand{\pin}{\par\noindent}
\usepackage{multicol}
% \usepackage{natbib}

\author{Siddhartha Patra, Abhirup Mukherjee, Anirban Mukherjee, N. S. Vidhyadhiraja, A. Taraphder, S Lal}

\title{Referee response to BS14324 Patra}
\begin{document}
\maketitle

We thank the three referees for comments, questions and suggestions. Indeed, these have helped substantially in improving the overall presentation of the manuscript. Below, we present our responses (in blue) to the points raised by the three referees in turn.

\section{First referee}

\paragraph{Point 1.}
In general, the paper is comprehensive and well-organized, though I would encourage the authors to go over the manuscript in the next revision and correct several typos and inconsistencies in notation, few of which I list below.
{\color{blue}\paragraph{Response:} We thank the referee for the comment. We have corrected the typos and inconsistencies in the notation everywhere in the manuscript.}

\paragraph{Point 2.}
Examples of minor issues:
{\color{blue}\paragraph{Response:} We thank the referee for pointing out these typographic errors.} 
\begin{itemize}
	\item Eq.(3), are both the commutator and anticommutator of the $\eta$
operators equal to 1, or just the anticommutator?\\
{\color{blue}{\bf Response:} We thank the referee the referre for pointing out these typographic errors. Indeed, only the anticommutator is unity, while the commutator is actually equal to $2\hat n_j - 1$~\cite{anirbanurg1}. We have updated the manuscript with this correction.}
	\item In several equations, the sum is over $\alpha$ and $\beta,$ but the operators have $\alpha$ and $\alpha^\prime$ indices.\\
{\color{blue}{\bf Response:} We have gone through the entire manuscript and made sure that the notation is now consistent.}
	\item Some notations, like $\theta_M$ above Eq. 16 is introduced and never
	used.\\
{\color{blue}{\bf Response:} We have removed redundant notation here and elsewhere in the manuscript, wherever we could find.}
\end{itemize}

\paragraph{Point 3:}
Can this technique of using the star graph together with effective Hamiltonian for low energy excitations be also used to obtain dynamical properties such as conductance? As this is often one of the most important experimental probes used to study Kondo problems, I would be interested to learn if URG can provide additional insight.

{\color{blue}\paragraph{Response:} We are grateful to the referee for this question. Indeed, we have used the URG method in the past to compute certain dynamic quantities like the impurity Greens function and spectral functions, both at zero and finite temperatures, for the single-channel Kondo model in an earlier work~\cite{kondo_urg}. This was done by working with the fixed point Hamiltonian, without taking the zero bandwidth limit. The spectral function revealed the expected Abrikosov-Suhl resonance at zero frequency, and satisfied the Friedel sum rule. We believe a similar  computation can also be performed to obtain other dynamical quantities like the conductance or the resistance. {\color{red}Should we mention gen-siam-3-peak,etc as an unpublished work here?}}

\paragraph{Point 4.}
In several places, the authors mention performing numerical calculations to verify the obtained results (for example paragraph above Eq 19 about impurity susceptibility). What method was used to perform the calculations? Is it just evaluation of for example Eq 15 for the Heisenberg Hamiltonian of the star graph or is the numerical calculation itself performing the renormalization treatment?

{\color{blue}\paragraph{Response:} In the example cited in the question, we used numerical calculations in the sense of solving the star graph Hamiltonian using exact diagonalisation and then using Eq.(19) to obtain the susceptibility. In order to obtain the contribution to the susceptibility coming from the non-Fermi liquid, however, we did indeed solve the renormalization group equations numerically to obtain the fixed point Hamiltonian.}

\paragraph{Point 5.}
Expanding on the previous point, can unitary renormalization group approach give rise to some new numerical technique akin to numerical renormalization group?

{\color{blue}\paragraph{Response:} While the RG formalism can be put into a numerical setup by abstracting the RG equations, we believe there is greater utility in sticking to the analytical form because it allows applying the method to a wide variety of systems and multiple geomteries, as can be seen in the references mentioned in the work. Moreover, the analytical approach makes it much more easier to obtain fixed point Hamiltonians. For these reasons, we have refrained from taking the numerical route.}

\section{Second referee}

\paragraph{Point 1.}
This block in the Introduction is a bit hard to understand and maybe could be rewritten: "the ground state is susceptible to perturbations that introduce channel isotropy in the exchange couplings [14, 32, 37, 45, 52]. This makes the experimental realisation of such states quite challenging." Do the authors mean channel anisotropy instead of channel isotropy?

{\color{blue}\paragraph{Response:} Indeed, we meant "anisotropy" instead of isotropy. We thank the referee for pointing this out.}

\paragraph{Point 2.} 
After Eq. (7), implicit summation over the spin indices $\alpha,\beta$ should be $\alpha,\alpha^\prime$.

{\color{blue}\paragraph{Response:} We have rectified this in the manuscript.}

\paragraph{Point 3.} 
In Eq. (8) and the text after Eq. (8), why are there two sums in the
k-expansion of S, over $k$ and $k^\prime$, as opposed to only one sum over k? Also, there
is an issue with $\alpha^\prime$ and $\beta$ variables (similar to point 2.)

{\color{blue}\paragraph{Response:} We have rectified the issue with the spin label \(\alpha^\prime\). With regards to the two momentum summations \(k,k^\prime\) in the expressions of \(\vec S\) in and below Eq.(8), both the summations are required. This expression for the spin operator can be found in several textbooks like ~\cite{coleman2015,hewson1993}, and can be obtained by Fourier transforming the perfectly local bath spin operator \(\sum_{\alpha\alpha^\prime}\sigma_{\alpha\beta}c^\dagger_{\alpha}c_{\alpha^\prime}\) formed by the electrons \(c_{\alpha},c_{\alpha^\prime}\) at the origin.}

\paragraph{4.}
In Fig. 3, legend, one of the triangles should be a circle.

{\color{blue}\paragraph{Response:} We have updated the plot with the correct legend. We are grateful to the referee for pointing this out.}

\paragraph{5.}
After Eq. (18), the authors attribute a 1/T contribution to the
susceptibility as a signature of the critical nature of the Hamiltonian. This 1/T (Curie)-behavior is present for the susceptibility of a single magnetic moment in a magnetic field. I don't see critical behavior in this. The log corrections to 1/T would be a signature of criticality.

\paragraph{6.}
Also, in Eq. (8), why does it vanish only for $K=1$, and not when $K=2S_{d}$, in general?

\paragraph{7.}
In Section IV A, the authors classify the terms as Fermi liquid or non-Fermi liquid. Is there a simple way to understand this classification? A possible way is by characterizing the effects of each term, but my question is if there is an immediate way of knowing if the term is FL or NFL.

\bibliographystyle{unsrt}
\bibliography{./Manuscript27April2022/mscript_mck_full.bib}
\end{document}

### 2022-06-24 Ref Response/RefereeResponse.tex
provided all but one response

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,braket}
\usepackage[margin=0.5in]{geometry}
\usepackage{geometry}
\usepackage{color}
\usepackage{xcolor}
\geometry{legalpaper, portrait, margin=1in}
\DeclareUnicodeCharacter{2212}{-}
\DeclareUnicodeCharacter{03B8}{+}
\newcommand{\shat}{\hat{\mathbf{s}}}
\newcommand{\pin}{\par\noindent}
\newcommand{\response}[1]{{\color{blue}\subsection*{Response:}{#1}}}
\renewcommand{\thesubsection}{Point \arabic{subsection}.}
\newcommand{\point}[1]{\subsection{}{#1}}
\usepackage{multicol}
% \usepackage{natbib}

\author{Siddhartha Patra, Abhirup Mukherjee, Anirban Mukherjee, N. S. Vidhyadhiraja,\\ A. Taraphder, S Lal}

\title{Referee response to BS14324 Patra}
\begin{document}
\maketitle

We thank the three referees for comments, questions and suggestions. These have helped substantially in improving the overall presentation of the manuscript. Below, we present our responses (in blue) to the points raised by the three referees in turn.

\section{First referee}

\point{In general, the paper is comprehensive and well-organized, though I would encourage the authors to go over the manuscript in the next revision and correct several typos and inconsistencies in notation, few of which I list below.}
\response{We thank the referee for the comment. We have corrected the typographic errors and notational inconsistencies in the manuscript.}

\point{
Examples of minor issues:
\response{ We thank the referee for pointing out these typographic errors.} 
\begin{itemize}
	\item Eq.(3), are both the commutator and anticommutator of the $\eta$
operators equal to 1, or just the anticommutator?\\
{\color{blue}{\bf Response:} We thank the referee for pointing out these typographic errors. Indeed, only the anticommutator is unity, while the commutator is actually equal to $2\hat n_j - 1$~\cite{anirbanurg1}. We have updated the manuscript with this correction.}
	\item In several equations, the sum is over $\alpha$ and $\beta,$ but the operators have $\alpha$ and $\alpha^\prime$ indices.\\
{\color{blue}{\bf Response:} We have gone through the entire manuscript and made sure that the notation is now consistent.}
	\item Some notations, like $\theta_M$ above Eq. 16 is introduced and never
	used.\\
{\color{blue}{\bf Response:} We have removed redundant notation here and elsewhere in the manuscript, wherever we could find.}
\end{itemize}
}

\point{
Can this technique of using the star graph together with effective Hamiltonian for low energy excitations be also used to obtain dynamical properties such as conductance? As this is often one of the most important experimental probes used to study Kondo problems, I would be interested to learn if URG can provide additional insight.}

\response{ We are grateful to the referee for this question. Indeed, we have used the URG method in the past to compute certain dynamic quantities like the impurity Greens function and spectral functions, both at zero and finite temperatures, for the single-channel Kondo model in an earlier work~\cite{kondo_urg}. This was done by working with the fixed point Hamiltonian, without taking the zero bandwidth limit. The spectral function revealed the expected Abrikosov-Suhl resonance at zero frequency, and satisfied the Friedel sum rule. We believe a similar  computation can also be performed to obtain other dynamical quantities like the conductance or the resistance. {\color{red}Should we mention gen-siam-3-peak,etc as an unpublished work here?}}

\point{
In several places, the authors mention performing numerical calculations to verify the obtained results (for example paragraph above Eq 19 about impurity susceptibility). What method was used to perform the calculations? Is it just evaluation of for example Eq 15 for the Heisenberg Hamiltonian of the star graph or is the numerical calculation itself performing the renormalization treatment?}

\response{ In the example cited in the question, we used numerical calculations in the sense of solving the star graph Hamiltonian using exact diagonalisation and then using Eq.(19) to obtain the susceptibility. In order to obtain the contribution to the susceptibility coming from the non-Fermi liquid, however, we did indeed solve the renormalization group equations numerically to obtain the fixed point Hamiltonian.}

\point{
Expanding on the previous point, can unitary renormalization group approach give rise to some new numerical technique akin to numerical renormalization group?}

\response{While the RG formalism can be put into a numerical setup by abstracting the RG equations, we believe there is greater utility in sticking to the analytical form because it allows applying the method to a wide variety of systems and multiple geomteries, as can be seen in the references mentioned in the work. Moreover, the analytical approach makes it much more easier to obtain fixed point Hamiltonians.}

\section{Second referee}

\point{
My main comments concern Section II-A, in which the authors define the RG procedure. Since the results of the other Sections follow from the results of this Section, I would suggest the authors expand it. Also, some of the results that come later using this technique are familiar to the experts in the field of heavy fermions, but the RG procedure may not be.}

\response{We have now tried to address this in the manuscript by elaborating on the specific questions that the referee has brought up in the two points immediately following this. A more extensive description of the method will take up more space in this already sizable manuscript. We would like to point out that a complete derivation of the formalism and details on the various parts of the method and their implications can be found in Refs.~\cite{anirbanurg1,anirbanurg2} mentioned in the manuscript.}

\point{
It would benefit the reader of this article to get some intuition about the generators, Eqs. (3) and (4). Is there a simple way to understand this choice?}

\response{
	{\it The unitary operator \(U\) mentioned in Eq.(3) can be thought of as a special case of the most general form \(U = e^\mathcal{S}\) of a unitary operator defined by an anti-Hermitian generator \(\mathcal{S}\).} For our case, the generator turns out to be \(\mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger - \eta \right) \), such that the unitary operator is \(U = e^{\frac{\pi}{4}\left(\eta^\dagger - \eta\right) }\). If one then uses the anticommutation and commutation properties of \(\eta,\eta^\dagger\), the exponential can be expanded in its Taylor series and then resummed into the form mentioned in the manuscript.

	{\it With regards to the fermionic operators \(\eta_{(j)},\eta^\dagger_{(j)}\) of Eq.(4), they can be thought of as the many-particle analogue of the single-particle field operators \(c_j,c^\dagger_j\) that change the occupation number of the single-particle Fock space, \(\ket{n_j}\)}. The extra prefactors are required to ensure that the decoupling of the specific fock state happens through a unitary modification of the spectrum of the remnant degrees of freedom. Since the \(j^\text{th}\) degree of freedom is coupled with the others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\), and this is the reason for the \(\text{Tr}\left(H_(j) c_j\right) \) part. The Greens function in front accounts for the dynamical cost of this rotation in terms of the quantum fluctuations \(\hat \omega\) and the kinetic and self energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).

	{\it We have updated the manuscript with these explanations. We are thankful to the referee for these questions.}
}

\point{Other RG proposals come from applying a set of successive unitary transformations (such as the Wegner RG, as discussed in detail in ``The Flow Equation Approach to Many-Particle Systems" by Stefan Kehrein). How does this approach differ from those?}

\response{
There are atleast two specific distinctions between the continuous unitary transformations (CUT) RG as envisaged by Wegner (and others before him) and the URG of the present work.
\begin{itemize}
	\item While most RG methods that apply successive unitary transformations rely on a gradual decrease in the off-diagonal content of the Hamiltonian, the URG proceeds by decoupling each discrete Fock space node at a time. In other words, in the URG, at least one term in the Hamiltonian vanishes at each RG step, while in the CUT RG, there is a gradual decay of the off-diagonal terms in order to make it more band diagonal.
	\item The CUT RG, specifically, has to be applied by choosing a truncation scheme that allows closing the RG equations. The URG, on the other hand, is able to ``resum" the coupling expansion series through the denominator structure and the quantum fluctuation operator.  
\end{itemize}
We have improved the manuscript by adding these comparisons. Comparisons of the URG with other methods like the functional RG or the spectrum bifurcation RG can also be found in Refs.~\cite{anirbanmott1,anirbanurg1}.
}

\point{Also, in Section II, the authors denote by $\ket{j}$ the highest energy electronic state. In this problem, assuming a quadratic dispersion to the electrons in 3 dimensions, the Fermi surface would generally be a sphere. Would $\ket{j}$ be the set of states with $k=k_{F}$?}

\response{We thank the referee for the question. The symbol \(\ket{j}\) is used to label the most energetic state {\it at a particular RG step} of the entire process. In more conventional language, it is simply the collection of states at the running cutoff \(\Lambda\) (bandwidth) of the field theory. As the RG proceeds, this bandwidth shrinks, so \(\ket{j}\) flows to lower and lower energies, until it hits the Fermi surface (assuming the RG has not reached a fixed point by then).
}

\point{
This block in the Introduction is a bit hard to understand and maybe could be rewritten: ``the ground state is susceptible to perturbations that introduce channel isotropy in the exchange couplings [14, 32, 37, 45, 52]. This makes the experimental realisation of such states quite challenging." Do the authors mean channel anisotropy instead of channel isotropy?}

\response{ Indeed, we meant ``anisotropy" instead of isotropy. We thank the referee for pointing this out.}

\point{ 
After Eq. (7), implicit summation over the spin indices $\alpha,\beta$ should be $\alpha,\alpha^\prime$.}

\response{ We have rectified this in the manuscript.}

\point{ 
In Eq. (8) and the text after Eq. (8), why are there two sums in the
k-expansion of S, over $k$ and $k^\prime$, as opposed to only one sum over k? Also, there is an issue with $\alpha^\prime$ and $\beta$ variables (similar to point 2.)}

\response{We have rectified the issue with the spin label \(\alpha^\prime\). With regards to the two momentum summations \(k,k^\prime\) in the expressions of \(\vec S\) in and below Eq.(8), both the summations are required. This expression for the spin operator can be found in several textbooks like ~\cite{coleman2015,hewson1993}, and can be obtained by Fourier transforming the local spin operator \(\sum_{\alpha\alpha^\prime}\vec \sigma_{\alpha\alpha^\prime}c^\dagger_{\alpha}c_{\alpha^\prime}\) formed by the conduction electrons \(c_{\alpha},c_{\alpha^\prime}\) at the origin.}

\point{
In Fig. 3, legend, one of the triangles should be a circle.}

\response{ We have updated the plot with the correct legend. We are grateful to the referee for pointing this out.}

\point{
After Eq. (18), the authors attribute a 1/T contribution to the
susceptibility as a signature of the critical nature of the Hamiltonian. This 1/T (Curie)-behavior is present for the susceptibility of a single magnetic moment in a magnetic field. I don't see critical behavior in this. The log corrections to 1/T would be a signature of criticality.}

\response{We had used the term critical to reflect the fact that the \(1/T\) divergence was a result of the remnant degeneracy of the system at the fixed point. In order to avoid confusion, we have removed the usage of critical in this context from the manuscript.}

\point{
Also, in Eq. (8), why does it vanish only for $K=1$, and not when $K=2S_{d}$, in general?}

\response{We believe the referee is referring to Eq.(18) here, not Eq.(8). The expression in Eq.(18) was derived for the specific case of $S_d = 1/2$ (spin-half impurity), hence it only vanishes at $K=2S_d=1$. The more general case of spin-\(S_d\) impurity was checked numerically, and reported in Fig.(4). We have now included the more general analytical expression for the susceptibility in the manuscript, and this expression does indeed vanish at $K = 2S_d$.}

\point{
In Section IV A, the authors classify the terms as Fermi liquid or non-Fermi liquid. Is there a simple way to understand this classification? A possible way is by characterizing the effects of each term, but my question is if there is an immediate way of knowing if the term is FL or NFL.}

\response{ We thank the referee for allowing us to clarify this. We used the term “non-Fermi liquid” to reflect the fact that, in the RG sense, the low energy $k−$space Hamiltonian was not purely of an $F_{kk^\prime} n_k n_{k^\prime}$ density-density type interaction term.}

\section{Third referee}

\point{
Perhaps the most interesting part is the “star graph” analysis which
are done rigorously as far as I can judge. However, I am not convinced
(especially not by the authors) that the strong coupling teaches
anything useful for the infrared physics. If there is a clear physics
lesson here, it is lost in the myriad of technicalities in the paper.
}

\response{
}

\point{
Regarding computation of the perturbative RG flow, the perturbative
calculation of the beta function doesn’t really need any new
technology (like URD) and it has been done by drawing Feynman diagrams
in all those papers that are cited. Derivation of the effective fixed
point Hamiltonian, cannot be trusted since there is no argument that
subsequent steps are going to make smaller changes (as opposed to
Wilson’s NRG).
}

\response{
The URG is able to ``resum" all orders of couplings through the non-perturbative denominator structure of the RG equation and the quantum fluctuation scale \(\omega\). This ensures that the fixed point Hamiltonians obtained from URG indeed account for the effects of the UV on the IR and are stable in the RG sense.
}

\point{
It’s highly
technical and I believe it does not add anything to what we know and
furthermore, some steps and arguments are, in my opinion, not really
correct.
}

\response{
We believe that the following are new and interesting additions to the knowledge of multichannel Kondo physics that are obtained from our work:
\begin{itemize}
	\item importance of the role of degeneracy and quantum-mechanical frustration in shaping the infrared physics of the MCK, specifically in the non-Fermi liquid behaviour, the thermodynamic properties, the orthogonality catastrophe, the breakdown of screening and in the strong-weak duality,
	\item derivation of a marginal Fermi liquid effective Hamiltonian for the non-Fermi liquid fixed point, hence revealing the microscopic source of the non-Fermi liquid behaviour in the overscreened regime,
	\item the presence of a spin Mott liquid in the effective interactions among the conduction electrons,
	\item demonstration of the orthogonality catastrophe in the ground state through entanglement measures.
\end{itemize}
The observation of the Mott liquid is particularly significant because it highlights a common theme that pervades much of fermionic quantum matter - the role of zero modes in determining the infrared physics. This can be seen in the emergence of a Mott liquid from the 2D Hubbard model as seen from a URG analysis~\cite{anirbanmott1,anirbanmott2,mukherjeeMERG2022}, the emergence of a cooper pair insulator from the reduced BCS Hamiltonian~\cite{siddharthacpi} and the emergence of an effective Heisenberg model in the 1D Hubbard model~\cite{1dhubjhep}.
}

\bibliographystyle{unsrt}
\bibliography{../Manuscript27April2022/mscript_mck_full.bib}
\end{document}

### 2022-06-25 Ref Response/RefereeResponse.tex
added final response

@@
-\documentclass[11pt]{article}
+\documentclass{article}
 \usepackage{amsmath,amssymb,braket}
@@
 \usepackage{multicol}
-% \usepackage{natbib}
 
@@
 
-\response{
+\response{We thank the referee for this question.
+On application of the renormalization group transformations towards the fixed point, there is a reduction in the effective bandwidth of the problem, leading to reduced excitations into the conduction band.
+This enables us to take the zero bandwidth approximation and study the emergent star graph as a "skeletal" problem for the low-energy physics.
+Such a trick reveals, for instance, the ground state of the multichannel problem and the degeneracy.
+Moreover, it allows studying the effects of excitations, as demonstrated by the identification of the non-Fermi liquid component, more specifically a local marginal Fermi liquid.
 }
@@
 \bibliographystyle{unsrt}
-\bibliography{../Manuscript27April2022/mscript_mck_full.bib}
+\bibliography{../manuscript/mscript_mck_full.bib}
 \end{document}

### 2022-06-25 manuscript/mscript_mck_full.tex
added latest manuscript files

@@
 \begin{abstract}
-Our study of the multi-channel Kondo (MCK) model using the recently developed unitary renormalization group (URG) technique shows the importance of ground state degeneracy in explaining various important properties like the breakdown of screening and the presence of local non-Fermi liquids.
-The impurity susceptibility of the zero-bandwidth intermediate coupling fixed point Hamiltonian shows power-law divergence at low temperature, signaling its critical nature.
-Despite the absence of inter-channel coupling in the MCK Hamiltonian, the study of mutual information between two channels shows non-zero correlation among them.
-The presence of non-local twist and translation operators shows the topological nature of the degenerate ground state manifold.
-Upon disentangling the impurity spin, we find the presence of local Mott-liquid made out of inter-channel quantum scatterings.
-We derive the low energy effective Hamiltonian (LEH) upon the addition of excitation to the zero-bandwidth RG fixed point Hamiltonian for the two and three-channel cases, both of which show the absence of local Fermi liquid phase due to exact cancellation coming from different degenerate ground states, and the presence of non-Fermi liquids with inter-channel quantum fluctuations.
-Computation of various thermodynamic quantities like specific heat and susceptibility in the ground state of that non-Fermi liquid shows logarithmic scaling in low temperature, which agrees with the known result in the literature.
-The presence of local marginal Fermi liquid shows the orthogonality catastrophe in the two-channel Kondo model.
-Discontinuity in various entanglement measures as we add the excitations on top of the zero-bandwidth model by tuning the real space nearest-neighbor hopping strength reinforces the presence of orthogonality catastrophe.
-Strong and weak coupling duality also sheds light on the presence of an intermediate coupling fixed point in the MCK problem.
-The study of channel anisotropy under URG reveals series of quantum phase transitions due to the change in ground state degeneracy.
-Our work thus shows a template of studying the zero-bandwidth model followed by the systematic addition of excitations, which can be used to study other impurity problems.
+We study the overscreened multi-channel Kondo (MCK) model using the recently developed unitary renormalization group (URG) technique.
+Our results display the importance of ground state degeneracy in explaining various important properties like the breakdown of screening and the presence of local non-Fermi liquids.
+The impurity susceptibility of the intermediate coupling fixed point Hamiltonian in the zero-bandwidth (or star graph) limit shows a power-law divergence at low temperature, signalling its critical nature.
+Despite the absence of inter-channel coupling in the MCK fixed point Hamiltonian, the study of mutual information between any two channels shows non-zero correlation between them.
+A spectral flow analysis of the star graph reveals that the degenerate ground state manifold possesses topological quantum numbers.
+Upon disentangling the impurity spin from its partners in the star graph, we find the presence of a local Mott liquid arising from inter-channel scattering processes.
+The low energy effective Hamiltonian obtained upon adding a finite non-zero conduction bath dispersion to the star graph Hamiltonian for both the two and three-channel cases displays the presence of local non-Fermi liquids arising from inter-channel quantum fluctuations.
+Specifically, we confirm the presence of a local marginal Fermi liquid in the two channel case, whose properties show logarithmic scaling at low temperature as expected.
+Discontinuous behaviour is observed in several measures of ground state entanglement, signalling
+the underlying orthogonality catastrophe associated with the degenerate ground state manifold. 
+We extend our results to underscreened and perfectly screened MCK models through duality arguments.
+A study of channel anisotropy under renormalisation flow reveals a series of quantum phase transitions due to the change in ground state degeneracy.
+Our work thus presents a template for the study of how a degenerate ground state manifold arising from symmetry and duality properties in a multichannel quantum impurity model can lead to novel multicritical phases at intermediate coupling.
 
@@
 %{\color{blue}
-Local antiferromagnetic exchange interaction between a spin-\(\frac{1}{2}\) impurity and a metal gives rise to the well-understood phenomenon of Kondo effect~\cite{hewson1993}.
+A local antiferromagnetic exchange interaction between a spin-\(\frac{1}{2}\) impurity and its host metal gives rise to the well-understood phenomenon of the Kondo effect (\cite{kondo1964resistance}, see ~\cite{hewson1993} for an extensive discussion).
 Here, the impurity local moment is screened by the conduction electrons at temperatures below a certain scale called the Kondo temperature~\cite{anderson1969exact,anderson1970exact,anderson1970,wilson1975,andreiKondoreview,
 tsvelickKondoreview,affleck1993exact,affleck1995conformal}, leading to a spin singlet ground state and local Fermi liquid excitations above that ground state~\cite{nozieres1974fermi,hewsonp}.
-The screening manifests as an {\color{blue}initial increase at temperatures below the Kondo temperature, followed by a saturation} of the resistivity of the metal~\cite{Kondo,Zhang2013}, and in the saturation of the impurity contribution to the magnetic susceptibility at low temperatures~\cite{wilson1975,andreiKondoreview,tsvelickKondoreview}.
+The screening manifests as an initial increase at temperatures below the Kondo temperature, followed by a saturation of the resistivity of the metal~\cite{kondo1964resistance,Zhang2013}, and in the saturation of the impurity contribution to the magnetic susceptibility at low temperatures~\cite{wilson1975,andreiKondoreview,tsvelickKondoreview}.
 Generalisations of this model are obtained by taking impurities of higher spin~\cite{hewson1993,Noz_blandin_1980,affleck1993exact}, adding interactions between them~\cite{affleck_1992,affleck_ludwig_jones_1992,georges_1999,zarand_chung_2006,
-mitchell_logan_2011,mitchell_sela_2012,konig_coleman_2021}, by promoting to a Kondo lattice of impurities~\cite{coleman_1987,millis_lee_1987,auerbach_1986,rice_ueda_1986,stewart_1984} or by considering a correlated metal~\cite{granath_1998}.
-One can also construct multi-channel Kondo (MCK) models by allowing \(K\) conduction electron channels \( \left(K > 1\right) \) to interact with a spin-\(\frac{1}{2}\) impurity~($S_{d}$)~\cite{Noz_blandin_1980,zawadowski_1980,cox_zawadowski_1998} via a common exchange coupling \(\mathcal{J}\).
-Using conformal field theory~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005}, bosonization~\cite{emery_kivelson,clarke_giamarchi_1993,zarand_2000,vondelft_prl_1998,schofield_1997}, numerical renormalization group~\cite{bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991}, Bethe ansatz~\cite{andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002} and other methods~\cite{sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}, it has been shown that for the overscreened systems \(\left(K > 2S_d\right)\), the low energy physics is of the non-Fermi liquid type, displaying anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (ensuring that temperature is taken to zero before the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
-This anomalous divergent behaviour is actually a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: it is susceptible to perturbations that introduce channel isotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}.
-This makes the experimental realisation of such states quite challening.
+mitchell_logan_2011,mitchell_sela_2012,konig_coleman_2021}, by promoting the model to a lattice of Kondo impurities~\cite{coleman_1987,millis_lee_1987,auerbach_1986,rice_ueda_1986,stewart_1984} or by considering the case of a correlated host metal~\cite{granath_1998}.
+One can also construct multi-channel Kondo (MCK) models by allowing \(K\) conduction electron channels \( \left(K > 1\right) \) to interact with a spin-\(S_{d}\) impurity~\cite{Noz_blandin_1980,zawadowski_1980,cox_zawadowski_1998} via a common exchange coupling \(\mathcal{J}\).
+Using conformal field theory~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005}, bosonization~\cite{emery_kivelson,clarke_giamarchi_1993,zarand_2000,vondelft_prl_1998,schofield_1997}, numerical renormalization group~\cite{bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991}, Bethe ansatz~\cite{andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002} and other methods~\cite{sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}, it has been shown that for the over-screened systems \(\left(K > 2S_d\right)\), the low energy physics is of the non-Fermi liquid type obtained at an intermediate coupling fixed point of the RG flows~\cite{Noz_blandin_1980}.
+Further, the system displays anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (upon ensuring that temperature is taken to zero before the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
+This anomalous divergent behaviour is a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: the ground state is susceptible to perturbations that introduce channel isotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}.
+This makes the experimental realisation of such states quite challenging.
 Nevertheless, several features of the two-channel Kondo model have been reproduced using structural two-level systems~\cite{zawadowski_1980,vladar_1983} interacting with a conduction bath~\cite{cichorek_2005,ralph_buhrman_1992,ralph_ludwig_1994,Iftikhar2015,Zhu2016}.
@@
 
-The role of ground state degeneracy and quantum-mechanical frustration in the MCK problem has not received sufficient attention, even though they play crucial roles in determining the non-Fermi liquid physics and the quantum criticality of the system.
+The importance of ground state degeneracy and quantum-mechanical frustration in the MCK problem has not received sufficient attention, even though they play crucial roles in determining the quantum criticality and associated non-Fermi liquid physics of the system.
 This is, at least partially, due to the lack of an intermediate-coupling effective Hamiltonian that describes the low-energy physics of the MCK (i.e., reveals the nature of the excitations).
-The term frustration in this context refers to the inability of the impurity spin to bind with the conduction channels and get completely screened by forming a maximally-entangled singlet.
-The absence of such frustration in the single-channel spin-1/2 Kondo model (and more generally, the exact screening variant of the MCK) means that imperfect screening \((K \neq 2S_d)\) should lead to dramatic differences in the multi-channel models.
-Indeed, we demonstrate that there exists an orthogonality catastrophe in the imperfectly screened MCK models leading to the non-Fermi liquid behaviour of its low-energy excitations, and that it is directly related to the existence of a degenerate ground state manifold.
-The effects of these non-Fermi liquid low energy excitations are expected to show up in measures of many-particle entanglement; the lack of an intermediate coupling Hamiltonian has, however, prevented the study of the renormalisation group (RG) evolution of such measures~\cite{alkurtass_affleck_2016,kim_shim_2021}.
-Our approach enables a comparison of, for instance, the inter-channel mutual information along the RG flow and as functions of the excitation energies, providing insight into the nature of the fixed point theory.
+\textit{Frustration} in this context refers to the inability of the impurity spin to bind with the conduction channels, and be screened completely by forming a maximally-entangled singlet ground state.
+The absence of such frustration in the single-channel spin-1/2 Kondo model (and more generally, the exact screening variant of the MCK) means that imperfect screening \((K \neq 2S_d)\) leads to dramatic differences in the multi-channel models.
+Indeed, we demonstrate that there exists an orthogonality catastrophe in the imperfectly screened MCK models that leads to the non-Fermi liquid behaviour of its low-energy excitations, and that this is directly related to the existence of a degenerate ground state manifold.
+The effects of these non-Fermi liquid low energy excitations are expected to appear in measures of many-particle entanglement; the lack of an intermediate coupling Hamiltonian has, however, prevented the study of the renormalisation group (RG) evolution of such measures~\cite{alkurtass_affleck_2016,kim_shim_2021}.
+Importantly, our approach enables a comparison of, for instance, the inter-channel mutual information along the RG flow and as functions of the excitation energies, providing insight into the nature of the fixed point theory.
 %}
 
-To obtain the RG flow of the MCK model, we have employed the recently developed unitary renormalization group (URG) technique~\cite{anirbanurg1,anirbanurg2}.
-The method has been applied on several fermionic and spin problems like the single-channel Kondo model~\cite{kondo_urg}, the kagome antiferromagnet~\cite{santanukagome}, the 1D~\cite{1dhubjhep} and 2D Hubbard models~\cite{anirbanmott1,anirbanmott2}, the reduced-BCS model~\cite{siddharthacpi} as well as other generalised models of interacing electrons with and without translation invariance~\cite{anirbanurg2}.
-The URG proceeds by decoupling number fluctuations in the high energy electronic states.
-Iteratively applying this URG method on the channel-isotropic MCK model leads to a low energy fixed point Hamiltonian at intermediate Kondo coupling.
+To obtain the RG flow of the MCK model, we have employed the unitary renormalization group (URG) technique developed recently by  some of us~\cite{anirbanurg1,anirbanurg2}.
+The method has been applied on several fermionic and spin problems like the single-channel Kondo model~\cite{kondo_urg}, the kagome antiferromagnet~\cite{santanukagome}, the 1D~\cite{1dhubjhep} and 2D Hubbard models~\cite{anirbanmott1,anirbanmott2,mukherjeeMERG2022}, the reduced-BCS model~\cite{siddharthacpi} as well as other generalised models of interacting electrons with and without translation invariance~\cite{anirbanurg2}.
+The URG proceeds by resolving the number fluctuations in the electronic Fock states at high energies by the iterative application of many-particle unitary transformations, leading to their successive decoupling from the states lying at lower energies.
+Applying this URG method to the channel-isotropic MCK model leads to a low-energy fixed point Hamiltonian at the intermediate (Kondo) coupling fixed point of Ref.\cite{Noz_blandin_1980}.
 In further analysing the effective Hamiltonian, we focus initially on the zero bandwidth limit of this Hamiltonian (which corresponds to a frustrated quantum spin model on a star graph).
@@
 The magnetisation and susceptibility of the star graph model show critical behaviour in the form a discontinuity and a \(T^{-1}\) divergence respectively.
-We also explore the topological properties of the degenerate groundstate manifold of the star graph model using non-local twist and translation operators.
+We also explore the topological properties of the degenerate ground state manifold of the star graph model using non-local twist and translation operators.
 On decoupling the impurity spin from the conduction spin degrees of freedom within the star graph, we obtain an all-to-all Hamiltonian that represents a local Mott liquid phase.
-In section ~\ref{sec:excitations}, we obtain the low energy effective Hamiltonian for the low-lying excitations by including a dispersion into the conduction bath.
+In section \ref{sec:excitations}, we obtain the low energy effective Hamiltonian for the low-lying excitations by including a dispersion into the conduction bath.
 Notable features of this effective Hamiltonian include (i) the complete absence of local Fermi liquid terms, and (ii) the emergence of local non-Fermi liquid terms.
@@
 
-In section \ref{sec:ent_prop}, we study various entanglement signatures (like the von-Neumann entanglement entropy, mutual information, multipartite information, Bures distance) of the low energy fixed-point ground state of the MCK problem, with and without excitaitons.
-They reveal clear distinctions between the single- and MCK problems in the form of discontinuities.
-In \ref{sec:duality}, we discuss two duality transformations that exist for the MCK model - a strong-weak duality and an overscreened-underscreened duality.
-It is found that the transformations are constrained by the fixed point structure, and they impose relations between the underscreened and overscreened models.
+In section \ref{sec:ent_prop}, we study various entanglement signatures (e.g., von-Neumann entanglement entropy, mutual information, multipartite information, Bures distance) of the low energy fixed-point ground state of the MCK problem, with and without dispersion into the bath.
+The discontinuous behaviour observed in these measures for the MCK problem reveal clear distinctions from the single-channel case.
+In \ref{sec:duality}, we discuss two duality transformations that exist for the MCK model - a strong-weak duality, and an over-screened-under-screened duality.
+It is found that the transformations are constrained by the fixed point structure, and impose relations between the under-screened and over-screened models.
 In \ref{anisotropic_rg}, we show the robustness of the ground state degeneracy of the star graph model against the impurity-channel coupling anisotropy, and correlate it with a URG treatment of the channel anisotropic MCK.
 The isotropic fixed point is found to be unstable to asymmetry, leading to impurity phase transitions that lead to dramatic changes in the ground state degeneracy.
-For the sake of brevity, some supporting evidence as well as the details of certain lengthy calculations are presented in Supplementary Materials.
+For the sake of brevity, some supporting evidence and details of certain lengthy calculations are presented in Supplementary Materials~\cite{SM}. Finally, we conclude in section \ref{conclusions}.
 
@@
 The RG proceeds {by applying unitary transformations in order to block-diagonalize the Hamiltonian by removing number fluctuations of the high energy degrees of freedom}.
-Given the most energetic electronic state at the \(j^\text{th}\) RG step is \(\ket{j}\) and defined by the energy \(D_{(j)}\), the Hamiltonian will in general not conserve the number of particles in this state: \(\left[H_{(j)}, \hat n_{j}\right] \neq 0\).
-The unitary transformation \(U_{(j)}\) will remove this number fluctuation at the next RG step~\cite{anirbanurg1,anirbanurg2}:
+At the $j^{th}$ RG step, we focus on decoupling the highest energy electronic state denoted by $\ket{j}$.
+%Given the most energetic electronic state at the \(j^\text{th}\) RG step is \(\ket{j}\) and defined by the energy \(D_{(j)}\), 
+The Hamiltonian will in general not conserve the number of particles in this state: \(\left[H_{(j)}, \hat n_{j}\right] \neq 0\), and the unitary transformation \(U_{(j)}\) causes this number fluctuation to vanish
+%at the next RG step
+~\cite{anirbanurg1,anirbanurg2}:
 \begin{equation}\begin{aligned}
@@
 \(H^i_{(j)}\) is that part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does not commute with at least one \(\hat n_l\) for \(l < j\).
-The RG flow continues up to energy \(D^*\), where a fixed point is reached from the vanishing of the RG function.
+The RG flow continues till a fixed point is reached at an energy \(D^*\).
+%, where a fixed point is reached from the vanishing of the RG function. 
 %from either the numerator or the denominator.
 
-The derivation of the RG equation for the over-screened regime \((2S < K)\) of the spin-\(S\)-impurity \(K\)-channel Kondo problem is shown in detail in the Supplementary Materials (CITE).
-On decoupling circular iso-energetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\text{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
+The derivation of the RG equation for the over-screened regime \((2S < K)\) of the spin-\(S\)-impurity \(K\)-channel Kondo problem is shown in detail in the Supplementary Materials~\cite{SM}.
+On decoupling circular isoenergetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\text{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
 \begin{equation}\begin{aligned}
@@
 As shown there, this fixed-point goes to \({\mathcal{J}}^* = \infty\) as the bare bandwidth of the conduction electrons is made large.
-The other trivial fixed point is the trivial one at \({\mathcal{J}}^* = 0\).
+The other fixed point is the trivial one at \({\mathcal{J}}^* = 0\).
 The third fixed point is reached when the numerator vanishes: \({\mathcal{J}}^* = \frac{2}{K \rho}\) \cite{Gan_mchannel_1994,Kogan_2018,Kuramoto1998,Noz_blandin_1980}.
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{plt/rg_flow.pdf}
+	\includegraphics[width=0.45\textwidth]{rgflow.pdf}
 	\caption{The three fixed points of the over-screened RG equation. Only the intermediate one is stable.}
@@
 
-We will first study the zero bandwidth limit of the fixed point Hamiltonian, obtained by compressing the sum over the momentum states to a single state at the Fermi surface.
-Upon setting the chemical potential equal to the Fermi energy, the kinetic energy part vanishes and the zero bandwidth model becomes a Heisenberg spin-exchange Hamiltonian.
+We will first study the zero bandwidth limit of the fixed point Hamiltonian, obtained by compressing the sum over the momentum states to a single state at the Fermi surface for each conduction channel (see Fig.\ref{fig:star graph}).
+Upon setting the chemical potential equal to the Fermi energy, the kinetic energy part vanishes and the zero bandwidth model becomes a Heisenberg spin-exchange Hamiltonian
 \begin{equation}\begin{aligned}
@@
 	\centering
-	\includegraphics[width=0.30\textwidth]{plt/stargraph.pdf}
+	\includegraphics[width=0.30\textwidth]{stargraph.pdf}
 	\caption{Zero bandwidth limit of the fixed point Hamiltonian.
@@
 \end{figure}
-The star graph commutes with several operators, including the total spin operator \(J^z = S_d^z + S^z\) along \(z\), the total bath local spin operator \(S^2\) and the string operators 
+The star graph commutes with several operators, including the total spin operator \(J^z = S_d^z + S^z\) along \(z\), the square of the total bath local spin operator (\(S^2\)) and the string operators
 \begin{equation}\begin{aligned}
@@
 There are several reasons for working with the star graph in particular and zero mode Hamiltonians in general.
-In the single-channel Kondo model, the star graph is just the two spin Heisenberg, and it reveals the stabilization of the Kondo model ground state, as well as certain thermodynamic properties (e.g., the impurity contribution to the susceptibility)~\cite{varma_yafet_1976,yosida_1966,wilson1975renormalization,moca_zarand_2021,varma_yafet_1976,kondo_urg}.
-Similarly in the MCK model, the star graph is able to mimic the nature of the RG flows.
+In the single-channel Kondo model, the star graph is just the two spin Heisenberg problem, and it reveals the stabilization of the Kondo model ground state, as well as certain thermodynamic properties (e.g., the impurity contribution to the susceptibility)~\cite{varma_yafet_1976,yosida_1966,wilson1975renormalization,moca_zarand_2021,
+varma_yafet_1976,kondo_urg}.
+Similarly, in the MCK model, the star graph captures accurately the nature of the RG flows.
 At weak coupling \({\mathcal{J}} \to 0^+\), the central spin is weakly coupled to the outer spins and  prone to screening because of the \(S^\pm\) terms in the star graph; at strong coupling \({\mathcal{J}} \to \infty^-\), the outer spin-half objects tightly bind with the central spin-half object to form a single spin object that interacts with the remaining states through an exchange coupling which is RG relevant.
@@
 Moreover, the RG flows of the MCK model have been show to {preserve the degeneracy of the ground state}~\cite{pang_cox_1991,kroha_kolf_2007,zitko_fabrizio_2017}, and the star graph captures this degeneracy in its entirety.
-This is important, because it will be shown in a later section that the lowest excitations of the intermediate fixed point is described a non-Fermi liquid phase, and it can be argued that this non-Fermi liquid physics arises solely from the ground state degeneracy of the underlying zero mode Hamiltonian.
+This is important, because it will be shown in a later section that the lowest excitations of the intermediate fixed point are described by a non-Fermi liquid phase, and it can be argued that this non-Fermi liquid physics arises solely from the ground state degeneracy of the underlying zero mode Hamiltonian.
 As mentioned previously, the ground state degeneracy of the more general star graph with a spin-\({S_d}\) impurity and \(K\) channels is given by \(g^{S_d}_K = |K - 2{S_d}|+1\).
 The cases of \(K=2{S_d}\), \(K<2{S_d}\) and \(K>2{S_d}\) correspond to exactly screened, under-screened and over-screened regimes respectively.
-The latter two cases correspond to a multiply-degenerate manifold \(g^S_K > 1\), and simultaneously have non-Fermi liquid phases~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,Coleman_tsvelik,affleck1993exact,coleman_pepin_2003,roch_nicolas_costi_2009,schiller_avraham_2008,Durganandini_2011}, while the first regime has a unique ground state \(g^S_K = 1\) and is described by a local Fermi liquid (LFL) phase \cite{wilson1975,nozieres1974fermi,Noz_blandin_1980,andreiKondoreview,tsvelickKondoreview}, thereby substantiating the claim that a degeneracy greater than unity is closely tied to non-Fermi liquid physics.
+The latter two cases correspond to a multiply-degenerate manifold with \(g^S_K > 1\), and simultaneously have non-Fermi liquid phases~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,
+Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,
+kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,
+Coleman_tsvelik,affleck1993exact,coleman_pepin_2003,roch_nicolas_costi_2009,schiller_avraham_2008,
+Durganandini_2011}, while the first regime has a unique ground state with \(g^S_K = 1\) and is 
+described by a local Fermi liquid (LFL) phase ~\cite{wilson1975,nozieres1974fermi,Noz_blandin_1980,andreiKondoreview,tsvelickKondoreview}, thereby substantiating the claim that a degeneracy greater than unity is closely tied to non-Fermi liquid physics.
 
@@
 \label{sec:deg_of_comp}
-One can quantify the amount of screening of the local moment at the impurity site by defining a degree of compensation \(\kappa\).
+One can quantify the screening of the local moment at the impurity site by defining a degree of compensation \(\Gamma\).
 Such a quantity also measures the inherent singlet frustration in the problem: the higher the degree of compensation, the better the spin can be screened into a singlet and lower is the frustration.
@@
 The expectation value is calculated in the ground state.
-Since the inner product is simply the ground state energy of a spin-\(S\) impurity \(K-\)channel MCK model in units of the exchange coupling \(J\), we have \(\Gamma = \frac{1}{2} \left[ l_\text{imp}^2 + l_c^2 - g^S_K\left( g^S_K - 1 \right)\right]\), where \(l_\text{imp}^2 = S_d(S_d+1)\) is the length-squared of the impurity spin.
+Since the inner product is simply the ground state energy of a spin-\(S_{d}\) impurity \(K-\)channel MCK model in units of the exchange coupling \(J\), we have \(\Gamma = \frac{1}{2} \left[ l_\text{imp}^2 + l_c^2 - g^S_K\left( g^S_K - 1 \right)\right]\), where \(l_\text{imp}^2 = S_d(S_d+1)\) is the length-squared of the impurity spin.
 Similarly, \(l_c^2 = \frac{K}{2}\left(\frac{K}{2} + 1\right) \) is the length-squared of the total conduction bath spin.
 \(g^S_K = |K - S_d| + 1\) is the ground state degeneracy.
-We will explore the three regimes of screening by defining \(K = K_0 + \delta, S = \frac{K_0}{2} - \delta\).
-\(\delta=0\) represents the exactly-screened case of \(K = 2S = K_0\).
+We will explore the three regimes of screening by defining \(K = K_0 + \delta, S_{d} = \frac{K_0}{2} - \delta\).
+\(\delta=0\) represents the exactly-screened case of \(K = 2S_{d} = K_0\).
 Non-zero \(\delta\) represents either over- or under-screening.
@@
 	\label{gamma}
-	\Gamma = \frac{1}{4}\left[\left( K_0 + 1 \right) ^2 - \left(|\delta| + 1 \right) ^2\right] 
-\end{aligned}\end{equation}
-{For a given \(K_0\), the degree of compensation is maximised for exact screening \(\delta=0\), and is reduced for \(\delta \neq 0\).
+	\Gamma = \frac{1}{4}\left[\left( K_0 + 1 \right) ^2 - \left(|\delta| + 1 \right) ^2\right]~.
+\end{aligned}\end{equation}
+{For a given \(K_0\), the degree of compensation $\Gamma$ is maximised for exact screening \(\delta=0\), and is reduced for \(\delta \neq 0\) (see Fig.\ref{compen}).
 This shows the inability of the system to form a unique singlet ground state and reveals the quantum-mechanical frustration inherent in the zero mode Hamiltonian and therefore in the entire problem.} The degree of compensation is symmetric under the Hamiltonian transformation \(\delta \to -\delta\), and this represents a duality transformation between over-screened and under-screened MCK models.
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{plt/deg_of_comp.pdf}
-	\caption{Variation of the degree of compensation as we tune the system from under-screening to over-screening. The maximum spin compensation occurs at exact-screening \(\delta=0\).}
+	\includegraphics[width=0.45\textwidth]{degofcomp.pdf}
+	\caption{Variation of the degree of compensation $\Gamma$ upon tuning from under-screening to over-screening by varying the deviation from exact screening $\delta=K_{0}/2-S$.
+The maximum spin compensation occurs at exact-screening \(\delta=0\).}
+	\label{compen}
 \end{figure}
@@
 \label{sec:imp_suscept}
-In order to obtain the magnetic susceptibility, We insert a magnetic field that acts only on the impurity and then diagonalize the Hamiltonian.
+In order to obtain the magnetic susceptibility, we insert a magnetic field that acts only on the impurity and then diagonalize the Hamiltonian
 \begin{align}
 	\label{star graph_field_hamiltonian}
-	H(h) = {\mathcal{J}^*} \vec{S_d}\cdot\vec{S} + h S_d^z
+	H(h) = {\mathcal{J}^*} \vec{S_d}\cdot\vec{S} + h S_d^z~.
 \end{align}
@@
 \begin{align}
-	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z^{\prime\prime}(h)}{Z(h)} - \left(\frac{Z^{\prime}(h)}{Z(h)}\right)^2 \right] 
+	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z^{\prime\prime}(h)}{Z(h)} - \left(\frac{Z^{\prime}(h)}{Z(h)}\right)^2 \right] ~,
 \end{align}
@@
 \centering
-\includegraphics[width=0.49\textwidth]{plt/CentralFieldChiPowerlaw.pdf}
+\includegraphics[width=0.49\textwidth]{CentralFieldChiPowerlaw.pdf}
 \caption{Variation of impurity susceptibility against temperature.
@@
 There, the susceptibility becomes constant at low temperatures: \(\chi(T\to 0) = \frac{W}{4 T_K}\), \(T_K\) being the single-channel Kondo temperature and \(W\) the Wilson number \cite{wilson1975renormalization,nozieres1974fermi,bullaNRGreview,kondo_urg}.
-We have checked the case of general spin-\(S\) impurity numerically (fig.~\ref{fig:suseptibility_impurity}), and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
+We have checked the case of general spin-\(S_{d}\) impurity numerically (fig.~\ref{fig:suseptibility_impurity}), and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
 A similar divergence is also seen in the susceptibility of the outer spins, calculated by inserting a magnetic field purely on the outer spins.
@@
 	\centering
-	\includegraphics[width=0.49\textwidth]{plt/disc_mag_imp_gen.pdf}
+	\includegraphics[width=0.49\textwidth]{discmagimpgen.pdf}
 	\caption{Behaviour of the impurity magnetization for three values of \(\left(K, 2S\right) = \left(2, 4\right), \left( 3,3 \right), \left(4, 2\right)  \).
@@
 
-The magnetization is therefore discontinuous as \(h\to 0\); it goes to different values depending on the direction in which we take the limit.
+The magnetization is therefore discontinuous as \(h\to 0\).
 The non-analyticity for \(K>1\) occurs because there is at least one pair of ground state with non-zero parity \(\pi^z\) and magnetic field is able to flip one ground state into the state of opposite parity.
 This available space for scattering is simply the frustration that we discussed earlier.
-Indeed, we have checked numerically (see fig.~\ref{mag_crit}) that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S\) is the deviation from exact screening.
-
+Indeed, we have checked numerically (see fig.~\ref{mag_crit}) that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S_{d}\) is the deviation from exact screening.
+Some additional results are presented in the Supplementary Materials~\cite{SM}.
 \subsection{Topological properties of ground state manifold}
@@
 We now present the non-local twist and translation operators which can be used to explore the degenerate ground state manifold of the star graph model.
-First we define two operators $\hat{T}$ and $\hat{O}$, which we will call the translation and twist operators respectively: 
+We begin by defining two operators $\hat{T}$ and $\hat{O}$, which we will call the translation and twist operators respectively: 
 \begin{eqnarray}
-\hat{T} &=& e^{i\frac{2\pi}{K} \hat{\Sigma}} ~,~\hat{O} = e^{i\hat{\phi}}~,~~\hat{\Sigma}=[\hat{J}^z-(K-1)/2]
+\hat{T} &=& e^{i\frac{2\pi}{K} \hat{\Sigma}} ~,~\hat{O} = e^{i\hat{\phi}}~,~~\hat{\Sigma}=[\hat{J}^z-(K-1)/2]~.
 \end{eqnarray}
-One can see that the generators of these above operators commute with the Hamiltonian: $[H,J^x]=[H,J^z]=[H,J^z]=0$.
-In the large \(K\) limit, we can perform a semi-classical approximation.
-As $J^x$ and $J^y$ both commute with the Hamiltonian $H$, we can write $[H,J^y{(J^{x})}^{-1}]=0$, and any non-singular function of these operators must also commute with the Hamiltonian, which leads us to conclude that
+One can see that the generators of thee above operators commute with the Hamiltonian: $[H,J^x]=[H,J^z]=[H,J^z]=0$. In the large \(K\) limit, we can perform a semi-classical approximation. 
+%As $J^x$ and $J^y$ both commute with the Hamiltonian $H$, we can write $[H,J^y{(J^{x})}^{-1}]=0$, and any non-singular function of these operators must also commute with the Hamiltonian, such that
+Thus, we define
 \begin{eqnarray}
-\hat{\phi}=\tan^{-1}(\hat{J}^y(\hat{J}^x)^{-1})
+%\hat{\phi}=\tan^{-1}(\hat{J}^y(\hat{J}^x)^{-1})~.
+e^{i\hat{\phi}} = \frac{J_{x}}{\sqrt{J^{2} - J_{z}^{2}}} + i\frac{J_{y}}{\sqrt{J^{2} - J_{z}^{2}}}~,
 \end{eqnarray}
-Then we get $[\hat{\phi},\hat{H}]=0$.
+such $[e^{i\hat{\phi}},\hat{H}]=0$.
 We can label the ground states by the eigenvalues of the translation operator $\hat{T}$.
 We can also use the ground states labeled by the eigenvalues of $J^z$ (say $M$).
-Then the ground states are
+The ground states are now written as
 \begin{eqnarray}
-|M_1\rangle,|M_2\rangle,|M_2\rangle,\cdots ,|M_K\rangle
+|M_1\rangle,|M_2\rangle,|M_2\rangle,\cdots ,|M_K\rangle~.
 \end{eqnarray}
-Then the operations of the translation operators on this states are given by
-\begin{eqnarray}
-\hat{T}|M_i\rangle &=& e^{i\frac{2\pi}{K} [M_i-(K-1)/2]} |M_i\rangle = e^{i2\pi\frac{p_i}{K} } |M_i\rangle~,~p_i\in[K]
-\end{eqnarray}
+The operations of the translation operators on these states are then given by
+\begin{equation}
+\hat{T}|M_i\rangle = e^{i\frac{2\pi}{K} [M_i-(K-1)/2]} |M_i\rangle = e^{i2\pi\frac{p_i}{K} } |M_i\rangle~,~p_i\in[K]~.
+\end{equation}
 The braiding rule between the twist and the translation operators is
 \begin{eqnarray}
-\hat{T}\hat{O}\hat{T}^{\dagger}\hat{O}^{\dagger} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},i\hat{\phi}]}=e^{i\frac{2\pi }{K}} \nonumber\\
-\hat{T}\hat{O}^m\hat{T}^{\dagger}\hat{O}^{\dagger m} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},im\hat{\phi}]}=e^{i2\pi \frac{m}{K}}
+\hat{T}\hat{O}\hat{T}^{\dagger}\hat{O}^{\dagger} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},i\hat{\phi}]}=e^{i\frac{2\pi }{K}} ~,\nonumber\\
+\hat{T}\hat{O}^m\hat{T}^{\dagger}\hat{O}^{\dagger m} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},im\hat{\phi}]}=e^{i2\pi \frac{m}{K}}~.
 \end{eqnarray}
-Next, we shown that the states $\hat{O}^m |M_i\rangle$ are orthogonal to each other and with the state $|M_i\rangle$.
+%Next, we shown that the states $\hat{O}^m |M_i\rangle$ are orthogonal to each other and with the state $|M_i\rangle$.
+The states $\hat{O}^m |M_i\rangle$ (with distinct $m$) are labelled by different eigenvalues of the translation operations, and are thus orthogonal to each other
 \begin{gather}
 \hat{T} \hat{O}^m |M_i\rangle = \hat{O}^m \hat{T} e^{i2\pi \frac{m}{K}} |M_i\rangle =\hat{O}^m e^{i \frac{2\pi(m+p_i)}{K} } |M_i\rangle \\
-\hat{T} \bigg(\hat{O}^m |M_i\rangle \bigg) = e^{i \frac{2\pi(m+p_i)}{K} } \bigg( \hat{O}^m |M_i\rangle \bigg)
+\hat{T} \bigg(\hat{O}^m |M_i\rangle \bigg) = e^{i \frac{2\pi(m+p_i)}{K} } \bigg( \hat{O}^m |M_i\rangle \bigg)~.
 \end{gather}
-Different states $\hat{O}^m |M_i\rangle$ for different $m$ are therefore labeled by different eigenvalues of the translation operations, and are thus orthogonal to each other.
+%Different states $\hat{O}^m |M_i\rangle$ for different $m$ are therefore labeled by different eigenvalues of the translation operations, and are thus orthogonal to each other. 
 As the twist operator $\hat{O}$ commutes with the Hamiltonian, we can write
 \begin{eqnarray}
-\langle M_i| \hat{O}^{m \dagger}  H \hat{O}^m |M_i\rangle =\langle M_i|  H |M_i\rangle 
+\langle M_i| \hat{O}^{m \dagger}  H \hat{O}^m |M_i\rangle =\langle M_i|  H |M_i\rangle ~.
 \end{eqnarray}
-Thus the energy eigenvalues of all the orthogonal states are equal, and they form the $K$ fold degenerate ground state subspace.
-By the application of the twist operator $\hat{O}$, one can go from one degenerate ground state to another.
+Thus, the energy eigenvalues of all the orthogonal states are equal, and they form the $K$ fold degenerate ground state subspace.
+By the application of the twist operator $\hat{O}$, we can go from one degenerate ground state to another.
+We note that a similar exploration of the degenerate ground state manifold of spin-1/2 Heisenberg antiferromagnets on geometrically frustrated lattices via twist and translation operators has been conducted in Refs.\cite{pal2019magnetization,pal2020topological}.
 
@@
 \label{sec:loc_mott_liquid}
-By applying the unitary renormalization group method on the zero mode star graph Hamiltonian, we decouple the impurity spin from the zero-modes of the $K$ channels: 
+%By applying the unitary renormalization group method on the zero mode star graph Hamiltonian, we decouple the impurity spin from the zero-modes of the $K$ channels: 
+In order to obtain the effective theory for the K zero modes, we will now use the URG method to decouple the impurity site from the star graph. The starting point is the star graph Hamiltonian
 \begin{gather}
-H = {\mathcal{J}} \vec{S}_d.\displaystyle\sum_i \vec{S}_i ={\mathcal{J}} S_d^zS^z + \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+) \nonumber\\
-H_D = {\mathcal{J}} S^z_d S^z~,~~ H_X = \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+)
+H = {\mathcal{J}} \vec{S}_d.\displaystyle\sum_i \vec{S}_i ={\mathcal{J}} S_d^zS^z + \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+) ~,\nonumber\\
+H_D = {\mathcal{J}} S^z_d S^z~,~~ H_X = \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+)~.
 \end{gather}
@@
 H_{eff} 
- =\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)   
+ =\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)   ~.
 \end{eqnarray}
-In terms of the electronics degree of freedom, it has the form
-\begin{eqnarray}
-&& \frac{ \beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow}) }{4}   \displaystyle\sum_{\substack{i\neq j \\ \alpha_i,\beta_i\in \{\uparrow,\downarrow\}\\ \alpha_j,\beta_j\in \{\uparrow,\downarrow\}}}\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)}    c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)} +\textrm{h.c.}   \nonumber
+In terms of the electronics degree of freedom, this can be written as
+\begin{equation}
+\frac{ \beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow}) }{4}  \left( \displaystyle\sum_{\substack{i\neq j \\ \alpha_i,\beta_i\in \{\uparrow,\downarrow\}\\ \alpha_j,\beta_j\in \{\uparrow,\downarrow\}}}\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)}    c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)} +\textrm{h.c.}\right) ~.
 \label{eq:all-to-all_1}
-\end{eqnarray}
-The antiferromagnetic case is for $\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{2} <0$.
+\end{equation}
+The case $\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{2} <0$ leads to a ferromagnetic effective Hamiltonian.
 In this case, the ground state is realised for $S$ being maximum and $S^z$ being minimum.
@@
 In the ground state, $S$ is maximum, and  therefore $S=K/2$, and $S^z$ can take $2S+1=K+1$ values.
-In the largest $S$ sector there are $K+1$ states.
-Defining the dual operator \(\hat \phi\) with the algbera \([\hat{\phi,S^z}]=i\), we get the twist operator $\hat{Q}=\exp(i\hat{\phi}\Phi/\Phi_0)$.
+Defining the dual operator \(\hat \phi\) with the algebra \([\hat{\phi,S^z}]=i\), we get the twist operator $\hat{Q}=\exp(i\hat{\phi}\Phi/\Phi_0)$.
 Applying this operator, we get the twisted Hamiltonian
-\begin{eqnarray}
-H(\Phi) &=& -\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} S^2   +\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} \bigg(S^{z}-\frac{\Phi}{\Phi_0} \bigg)^2 ~,~~
+\begin{equation}
+H(\Phi) = -\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} S^2   +\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} \bigg(S^{z}-\frac{\Phi}{\Phi_0} \bigg)^2 ~.
 \label{eq:flux_spectral}
-\end{eqnarray}
-One can thus explore different $S^z$ ground states via such flux tuning mechanism.
+\end{equation}
+One can thus explore different $S^z$ ground states via this spectral flow (flux insertion) argument.
 
 For a $K$ channel star graph problem the ground state is $K$ fold degenerate associated with different $J^z$ values $\{-(K-1)/2,-(K-3)/2,\cdots  ,(K-1)/2 \}$.
-After removing the quantum fluctuations between the impurity spin and the outer spins, we get an all-to-all model (eq.\eqref{eq:flux_spectral}) as the effective Hamltonian.
+After removing the quantum fluctuations between the impurity spin and the outer spins, we get an all-to-all model (eq.\eqref{eq:flux_spectral}) as the effective Hamiltonian.
 The eigenstates of this all-to-all Hamiltonian can be labeled by the eigenvalues of $S^z$.
@@
 We will now proceed to extract the nature of the low-energy excitations of the two-channel Kondo problem.
-This will be done by adding real-space hopping to the zero-bandwidth Hamiltonian and treating this hopping as a perturbation above the zero-bandwidth Hamiltonian.
-The zero-bandwidth Hamiltonian obtained from the URG of the two-channel Kondo problem then acts as the zeroth-level Hamiltonian Here:
+This will be done by treating real-space hopping as a perturbation to the zero-bandwidth Hamiltonian, as it accounts for the lowest-energy electronic quantum fluctuations in the conduction bath~\cite{nozieres1974fermi}.
+The zero-bandwidth Hamiltonian obtained from the URG of the two-channel Kondo problem then acts as the zeroth-level Hamiltonian
 \begin{eqnarray}
-H^{(2)}&=& {\mathcal{J}} \vec{S}_d.(\vec{S}_1+\vec{S}_2)~~,~~\vec{S}_i =  \frac{1}{2}~ c_{i,\alpha}^{\dagger}~ \vec{\sigma}_{\alpha,\beta}~ c_{i,\beta}~~
+H^{(0)}_{2CK}&=& {\mathcal{J}} \vec{S}_d.(\vec{S}_1+\vec{S}_2)~~,~~\vec{S}_i =  \frac{1}{2}~ c_{i,\alpha}^{\dagger}~ \vec{\sigma}_{\alpha,\beta}~ c_{i,\beta}~.
 \label{eq:channel-2-spin}
@@
 \end{eqnarray}
-and it will be accounted for using degenerate perturbation theory. Here $l_i$ represents the nearest site to the origin of the $i^{th}$ channel.
+and its effects will now be accounted for using degenerate perturbation theory. Here $l_i$ represents the nearest site to the origin of the $i^{th}$ channel.
 
@@
 The total diagonal second-order contribution to the effective Hamiltonian is obtained by adding these two contributions, and the result is a trivial shift: $H^{(2)}_\text{diag} = H^{(2)}_\text{diag}\left(\tilde \alpha_0\right) + H^{(2)}_\text{diag}\left(\tilde \alpha_1\right) = -4t^2 \hat{I}$.
-The fact there is no non-trivial diagonal renormalisation to the low-energy excitations shows the absence of (local) Fermi liquid terms, and this occurs becasuse of the exact cancellation of the field terms \(\pm \Omega_l\).
+The fact there is no non-trivial diagonal renormalisation to the low-energy excitations shows the absence of (local) Fermi liquid terms.
+%, the exact cancellation of the field terms \(\pm \Omega_l\).
 
@@
 \begin{eqnarray}
-H_{NFL}&=&H^{(2)}_{off} = \sum_{i\neq j} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j | \nonumber\\
+H_{NFL}&=&H^{(2)}_{od} = \sum_{i\neq j} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j | \nonumber\\
 &=& -\frac{8t^2}{3} [ (S_1^z)^2 c_{2\uparrow}^{\dagger}c_{2\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) \nonumber\\
-&+& (S_2^z)^2 c_{1\uparrow}^{\dagger}c_{1\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) ] + \textrm{h.c.} ~,~~~~
+&+& (S_2^z)^2 c_{1\uparrow}^{\dagger}c_{1\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) ] + \textrm{h.c.} ~.
 \label{eq:hamiltonian_NFL}
@@
 This effective Hamiltonian is purely of the non-Fermi liquid kind, arising due to the degeneracy of the ground state manifold.
-Using this low energy effective Hamiltonian we have calculated different thermodynamic quatitites like susceptibility, specific heat and the Wilson ratio.
-The first two measures show logarithmic behavior at low temperatures, in agreement with known results in the literature.
-These results are shown in the supplementary material.
+Using this low energy effective Hamiltonian, we have calculated different thermodynamic quantities like susceptibility, specific heat and the Wilson ratio.
+The first two measures show logarithmic behavior at low temperatures, in agreement with known results in the literature~\cite{Noz_blandin_1980,Gan_Andrei_Coleman_1993,emery_kivelson,Gan_mchannel_1994,
+Tsvelick_Weigmann_mchannel_1984,Tsvelick_weigmann_mchannel_1985,parcollet_olivier_large_N,
+kimura_taro_Su_N_kondo,PhysRevB.73.224445,cox_jarrell_two_channel_rev,affleck_1991_overscreen,
+Coleman_tsvelik,affleck1993exact,coleman_pepin_2003,roch_nicolas_costi_2009,schiller_avraham_2008,
+Durganandini_2011}. These results are shown in the Supplementary Material~\cite{SM}.
 
 Following this method, we have also calculated the effective Hamiltonian for the three channel Kondo model.
-We again find the absence of all Fermi liquid terms upto $2^{nd}$ order, and the presence of non-Fermi liquid terms in the off-diagonal part of the effective Hamiltonian, and these are also shown in the supplementary material.
+We again find the absence of all Fermi liquid terms up to $2^{nd}$ order, and the presence of non-Fermi liquid terms in the off-diagonal part of the effective Hamiltonian, and these are also shown in the Supplementary Material~\cite{SM}.
 
@@
 here, \(\sigma^z_{0,l} = \hat n_{0\uparrow,l} - \hat n_{0\downarrow,l}, s^+ = c^\dagger_{0 \uparrow,l}c_{0 \downarrow,l}\) and \(s^- = \left(s^+\right)^\dagger\).
-The notation \(0\sigma,l\) has the site index \(i=0,1,2,\ldots\) as the first label, the spin index \(\sigma=\uparrow,\downarrow\) as the second label and the channel index \(l=1,2\) as the third index.
+The notation \(0\sigma,l\) has the site index \(i=0,1,2,\ldots\) as the first label, the spin index \(\sigma=\uparrow,\downarrow\) as the second label and the channel index \(l=1,2\) as the third label.
 Such non-Fermi liquid (NFL) terms in the effective Hamiltonian and the absence of any Fermi-liquid term at the same order should be contrasted with the local Fermi liquid excitations induced by the singlet ground state of the single-channel Kondo model~\cite{nozieres1974fermi,wilson1975renormalization,hewson1993}.
@@
 	\label{k_space_od}
-	\sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \text{h.c.}
-\end{aligned}\end{equation}
-This form of the Hamiltonian is very similar to the three-particle interaction term in Appendix B of~\cite{anirbanmott1}.
+	\sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \text{h.c.} ~.
+\end{aligned}\end{equation}
+%This form of the Hamiltonian is very similar to the three-particle interaction term in 
+Such a three particle interaction term was also obtained for the NFL phase of the 2D Hubbard model from a URG treatment (see Appendix B of Ref.\cite{anirbanmott1}).
 The channel indices in Eq.~\ref{k_space_od} can be mapped to the normal directions in~\cite{anirbanmott1}.
@@
 	\label{mfl_large}
-	H^*_\text{eff,MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)
+	H^*_\text{eff,MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)~.
 \end{aligned}\end{equation}
 A non-local version of this effective Hamiltonian was found to describe the normal phase of the Mott insulator of the 2D Hubbard model, as seen from a URG analysis~\cite{anirbanmott1,anirbanmott2}.
-Following~\cite{anirbanmott1}, one can track the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\text{rh}\) RG step, in the form of the URG equation
-\begin{equation}\begin{aligned}
-	\Delta R_j =- \frac{R_j^2}{\omega - \epsilon_{j}/2 - R_j/8}
+Following~\cite{anirbanmott1}, one can track the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\text{th}\) RG step, in the form of the URG equation
+\begin{equation}\begin{aligned}
+	\Delta R_j =- \frac{R_j^2}{\omega - \epsilon_{j}/2 - R_j/8}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}
+	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}~.
 \end{aligned}\end{equation}
 The density of states can be approximated to be \(N^*/R^*\), where \(N^*\) is the total number of states over the interval \(R^*\).
-As suggested by the fixed point value of \(R_j\), we can approximate its behaviour near the fixed point by a linear dependence of the dispersion \(\epsilon_j\).
-The two limits of the integration are the start and end points of the RG.
+As suggested by the fixed point value of \(R_j\), we can approximate its behaviour near the fixed point by a linear dependence on the dispersion \(\epsilon_j\).
+The two limits of the integration are the starting and ending points of the RG.
 We start the RG very close to the Fermi surface and move towards the fixed point \(\epsilon^*\).
-Near the start point, we substitute \(\epsilon = 0\) and \(R = \omega\), following the fixed point condition.
+Near the starting point, we substitute \(\epsilon = 0\) and \(R = \omega\), following the fixed point condition.
 From the fixed point condition, we also substitute \(R^*/8 = \omega - \frac{1}{2}\epsilon^*\).
@@
 \begin{equation}\begin{aligned}
-	Z(\bar\omega) = \left(2 - \ln \frac{2\bar\omega}{N^* \omega}\right) ^{-1}
-\end{aligned}\end{equation}
-As \(\omega \to 0\), the \(Z\) vanishes, implying that the ground state is not adiabatically connected to the Fermi gas in the presence of the NFL terms.
+	Z(\bar\omega) = \left(2 - \ln \frac{2\bar\omega}{N^* \omega}\right) ^{-1}~.
+\end{aligned}\end{equation}
+As \(\omega \to 0\), the \(Z\) vanishes, implying that the ground state is {\it not adiabatically connected} to the Fermi gas in the presence of the NFL terms.
 This is the orthogonality catastrophe~\cite{varma2002singular,anderson_infraredcat,yamada_catastrophe,yamada1979orthogonality} in the two-channel Kondo problem, and it is brought about by the presence of the channel-non diagonal terms in Eq.~\ref{mfl_large}.
@@
 A local NFL term and a similar self-energy was also obtained by Coleman, et al.~\cite{Coleman_tsvelik} in terms of Majorana fermions at the strong-coupling fixed point of the \(\sigma-\tau\) model, which they claimed was equivalent to the intermediate-coupling fixed point of the two-channel Kondo model.
-Along with the work by Schofield~\cite{schofield_1997}, this demonstration shows the universality between the two-channel Kondo and the \(\sigma-\tau\) models.
+Indeed, along with Ref.\cite{schofield_1997}, this demonstration shows the universality between the two-channel Kondo and the \(\sigma-\tau\) models.
 
@@
 \centering
-\includegraphics[width=0.49\textwidth]{plt/EE_multi_channel_ANN.png}
+\includegraphics[width=0.49\textwidth]{EEmultichannelANN.png}
 \caption{Variation of impurity entanglement entropy ($EE_d$) for multiple values of \(K\). The maximum \(EE_d\) at large \(K\) is $\log 2$.}
@@
 On the other hand, the maximum entanglement entropy is attained in the state with minimum \(J^z\).
-This maximum value of the entanglement entopy is always \(\ln 2\) for odd values of \(K\); for even values of \(K\), the value asymptotically reaches $\log 2$ at large \(K\).
-
-A very similar computation gives the entanglent entropy between one outer spin and the rest of the spins, and it is shown in Fig.~\ref{fig:EE_outer}.
+This maximum value of the entanglement entropy is always \(\ln 2\) for odd values of \(K\); for even values of \(K\), the value asymptotically reaches $\log 2$ at large \(K\).
+
+A very similar computation gives the entanglement entropy between one outer spin and the rest of the spins, and it is shown in Fig.~\ref{fig:EE_outer}.
 We again find that the minimum entanglement entropy is associated with the state $|J^z=J\rangle$ and it falls with increasing \(K\), approaching zero asymptotically; the maximum entanglement entropy is, as before, associated with the state $|\left(J^z\right)_\mathrm{min}\rangle$ and it rises to $\log 2$ in the limit $K\gg 1$.
@@
 \centering
-\includegraphics[width=0.49\textwidth]{plt/outer_EE_multi_channel_ANN.png}
+\includegraphics[width=0.49\textwidth]{outerEEmultichannelANN.png}
 \caption{Variation of the entanglement entropy of an outer spin ($EE_o$) with the rest for different channels $(K)$. The maximum entanglement entropy in the large $K$ limit is $\log 2$.}
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/NEW31Dec_I_2_vs_Nch_[0,1]}
+\includegraphics[width=0.49\textwidth]{NEW31DecI2vsNch01}
 \caption{Variation of mutual information $I^2(d:o)$ of the impurity with the rest, for different values of $K$. The maximum $I^2(d:o)$ is $0.37$.}
@@
 \end{eqnarray}
-where $S_{A(B)}$ is the von-Neumann entanglement entropy of the subsystem $A(B)$ with the rest, and \(S_{A\cup B}\) is the von-Neumann entanglement entropy of \(A\) and \(B\) with the rest.
+where $S_{A(B)}$ is the entanglement entropy of the subsystem $A(B)$ with the rest, and \(S_{A\cup B}\) is the entanglement entropy of \(A\) and \(B\) with the rest.
 We are interested in two types of mutual information: firstly, the mutual information $I^2(d:o)$ between the impurity and one of the other spins, and secondly, the mutual information $I^2(o:o)$ between any two of the outer spins.
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/NEW31Dec_I_2_vs_Nch_[1,2]}
+\includegraphics[width=0.49\textwidth]{NEW31DecI2vsNc12}
 \caption{Variation of mutual information $I^2(o:o)$ between 2 outer spins, for multiple $K$. $I^2(o:o)$ vanishes for large $K$.}
@@
 \(I^3\) shows behavior similar to the mutual information - the highest \(I^2\) value is associated with the $\left(J^z\right)_\mathrm{min}$ state and it saturates in the limit of $K\gg 1$.
-One can measure $N-$partite information for a collection of subsystems (CSS) $\{\mathcal{A}_N\}\equiv\{A_1,A_2,\cdots,A_N\}$.
+The $N-$partite information for a collection of subsystems (CSS) $\{\mathcal{A}_N\}\equiv\{A_1,A_2,\cdots,A_N\}$ can also be defined
+as~\cite{siddharthatee} 
+\begin{equation}
+I^{N}_{\{\mathcal{A}_N\}} = \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.
+\label{eq:I_N_definition}
+\end{equation}
+where  $\mathcal{B}_m(\{\mathcal{A}_N\})\equiv \{ Q~| ~Q\subset \mathcal{P}(\{\mathcal{A}_{N}\}), |Q|=m \}$, and $\mathcal{P}(\{\mathcal{A}_{N}\})$ is the powerset of $\{\mathcal{A}_N\}$.
+For simplicity, we also define the union and intersection of all the subsystems present in $Q$ as ${V}_{\cup}({Q})\equiv \bigcup_{A\in Q} A$ and ${V}_{\cap}({Q})\equiv \bigcap_{A\in Q} A$ respectively.
+%One can measure $N-$partite information for a collection of subsystems (CSS) $\{\mathcal{A}_N\}\equiv\{A_1,A_2,\cdots,A_N\}$.
 To define the $N-$partite information, we first define the power set of the CSS $\{\mathcal{A}_N\}$ as $\mathcal{P}(\{\mathcal{A}_{N}\})$, and the collection of all subsets of $\mathcal{P}(\{\mathcal{A}_{N}\})$ with $m$ subsystems in it as $\mathcal{B}_m(\{\mathcal{A}_N\})\equiv \{ Q~| ~Q\subset \mathcal{P}(\{\mathcal{A}_{N}\}), |Q|=m \}$.
@@
 Then, the $N-$partite information that we are interested in is defined as
-\begin{eqnarray}
-I^{N}_{\{\mathcal{A}_N\}} &=& \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.~~~~
-\label{eq:I_N_definition}
-\end{eqnarray}
+%\begin{equation}
+%I^{N}_{\{\mathcal{A}_N\}} = \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.
+%\label{eq:I_N_definition}
+%\end{equation}
 \begin{figure}
-\includegraphics[width=0.49\textwidth]{plt/2022_IN_vs_N_K8.png}
+\includegraphics[width=0.49\textwidth]{2022INvsNK8.png}
 \caption{Variation of multipartite information $I^N$ among \(N\) outer spins as a function of $N$, for $K=8$. The inset shows $I^N$ vs $N$ for an all-to-all model. Both show power law behavior.}
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/hopping_fock_states}
+\includegraphics[width=0.49\textwidth]{hoppingfockstates}
 \caption{This is a schematic diagram of (a) single channel and (b) two channel problem. $S_d$ is the impurity spin. For more details refer to the text.}
@@
 At low hopping strength ($0<t\ll 1$), $EE_{d}$ is independent of $t$ and achieves a constant value.
-This value decreases with increasing \(K\).
 We also find that in this range of \(t\), \(EE_d\) decreases with increasing \(K\).
 This behaviour is reversed at high $t$, and \(EE_d\) is seen to increase with increasing \(K\).
-Though the values of the impurity entanglement entropy for various values of \(K\) are quite similar at low hopping strength, there is a difference in the behaviour as a function of \(t\): the single channel \(EE_d\) varies smoothly at \(t \to 0^+\), whereas the \(EE_d\) for \(K > 1\) show a discontinuity at $t \to 0^+$.
+Though the values of the impurity entanglement entropy for various values of \(K\) are quite similar at low hopping strength,
+%there is a difference in the behaviour as a function of \(t\): 
+as the single channel \(EE_d\) varies smoothly at \(t \to 0^+\), whereas the \(EE_d\) for \(K > 1\) show a discontinuity at $t \to 0^+$.
 
@@
 \centering
-\includegraphics[width=0.49\textwidth]{plt/A_I1_ch123_['d']}
+\includegraphics[width=0.49\textwidth]{AI1ch123d}
 \caption{Variation of impurity entanglement entropy $EE_{imp}$ against $t$, for $K=1,2,3$. }
@@
 \par \textit{Case 1:} We first study the mutual information $MI(d,1\uparrow)$ between the impurity spin $S_d$ and the state $1_\uparrow$ (fig.~\ref{fig:schematic_hopping}), where $1$ represents real-space origin of the $1^\text{st}$ conduction channel.
-For a single channel model, this site is unique because there is just one channel, but in the presence of $K$ channel, there are $K$ possible choices corresponding to each of the channels.
+For a single channel model, this site is unique because there is just one channel, but in the presence of $K$ channels, there are $K$ possible choices corresponding to each of the channels.
 However, because of the symmetry of the Hamiltonian under the exchange of the channel indices, all such choices will show identical mutual information signatures.
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['d','1_up']}
+\includegraphics[width=0.49\textwidth]{AI2ch12d1up}
 \caption{This figure show the variation of mutual information between the impurity spin and the $1_{\uparrow}$ state against $t$.
 For more details please refer to the text.
-The errorbar $\sigma_2$ of the two channel data at low hopping strength $\sigma_2\approx 0.002$.}
+The error-bar $\sigma_2$ of the two channel data at low hopping strength $\sigma_2\approx 0.002$.}
 \label{fig:MI_imp_1_vs_t_K}
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['1_up','1_down']}
+\includegraphics[width=0.49\textwidth]{AI2ch121up1down}
 \caption{Variation of mutual information ($i^2(1_{\uparrow},1_{\downarrow})$) among the two states present on the real-space origin ($1$) of a conduction channel, against $t$.
-The errorbar $\sigma_2$ for the two channel at low hopping strength is $\sigma_2\approx 0.013$.}
+The error-bar $\sigma_2$ for the two channel at low hopping strength is $\sigma_2\approx 0.013$.}
 \label{fig:MI_1_2_vs_t_K}
@@
 
-\par \textit{Case 3:} Next, we measure the mutual information $MI(d,l_{1\uparrow})$ between the impurity site and an electronic state of site that is nearest-neighbour to the real-space origin of one of the conduction channels (see fig.~\ref{fig:schematic_hopping}).
+\par \textit{Case 3:} Next, we measure the mutual information $MI(d,l_{1\uparrow})$ between the impurity site and an electronic state of the site that is nearest-neighbour to the real-space origin of one of the conduction channels (see fig.~\ref{fig:schematic_hopping}).
 The results are shown in fig.~\ref{fig:MI_d_l1}.
 Vanishing mutual information for the single channel case shows the perfect screening of the impurity spin.
-The non-zero value of mutual information at small $t$ values in the \(K=2\) model is again a result of the imperfect screening.
+The non-zero value of mutual information at small values of $t$ in the \(K=2\) model is again a result of the imperfect screening.
 As in the previous cases, we find a discontinuity in the mutual information for \(K=2\) as $t \to =0^+$.
@@
 \begin{figure}
-\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['d','l1_up']}
+\includegraphics[width=0.49\textwidth]{AI2ch12dl1up}
 \caption{Variation of the mutual information $MI(d,l_{1\uparrow})$ between the impurity spin and the $l_{1\uparrow}$ state, against $t$.
-The errorbar $\sigma_2$ for the two channel case is $\sigma_2\approx 0.001$.}
+The error-bar $\sigma_2$ for the two channel case is $\sigma_2\approx 0.001$.}
 \label{fig:MI_d_l1}
@@
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/A_I2_ch12_['1','l1']}
-\caption{Variation of the mutual information $MI(1_{\sigma},l_{1\sigma})$ between two nearest neighbor sites against \(t\). The errorbar for the two channel case is $\sigma_2\approx 0.005$.}
+\includegraphics[width=0.49\textwidth]{AI2ch121l1}
+\caption{Variation of the mutual information $MI(1_{\sigma},l_{1\sigma})$ between two nearest neighbor sites against \(t\). The error-bar for the two channel case is $\sigma_2\approx 0.005$.}
 \label{fig:MI_l_l1}
@@
 \centering
-\includegraphics[width=0.48\textwidth]{plt/I3_I2_A_I.png}
+\includegraphics[width=0.48\textwidth]{I3I2AI.png}
 \caption{Red: Mutual information $I^2(1_{\uparrow},2_{\uparrow})$ against \(t\).
-Blue: Tripartite infrmation $I^3(1_{\uparrow},l_{1\uparrow},l_{1\downarrow})$ against \(t\).
-The errorbar ($\sigma$) for the $I^3$ and $I^2$ near the low hopping strength are $0.002$ and $0.003$ respectively.}
+Blue: Tripartite information $I^3(1_{\uparrow},l_{1\uparrow},l_{1\downarrow})$ against \(t\).
+The error-bar ($\sigma$) for the $I^3$ and $I^2$ near the low hopping strength are $0.002$ and $0.003$ respectively.}
 \label{fig:I3_I2_two_channel}
@@
 
-\subsubsection{Bures distance and the orthogonality catathrope}
+\subsubsection{Bures distance and the orthogonality catastrophe}
 \begin{figure}[!htpb]
-\includegraphics[width=0.49\textwidth]{plt/error_Bures_Distance_Ch123_10001}
+\includegraphics[width=0.49\textwidth]{errorBuresDistanceCh12310001}
 \caption{Variation of Bures distance between the reduced density matrices of the star graph ground states at $t=0$ and $t\neq 0$, against $t$.
-The errorbars ($\sigma$) for \(K=2\) and \(K=3\) are $0.14$ and $0.08$ respectively, and near $t\approx 1$ the $\sigma$ are $0.04$ and $0.07$ respectively.}
+The error-bars ($\sigma$) for \(K=2\) and \(K=3\) are $0.14$ and $0.08$ respectively, and near $t\approx 1$ the $\sigma$ are $0.04$ and $0.07$ respectively.}
 \label{fig:bures_distance}
@@
 On the other hand, the abrupt jump in the Bures distance for higher-channel cases at $t=0^+$ shows the breakdown of adiabatic continuity between the \(t=0\) and \(t = 0^+\) Hamiltonians and signals an {\it orthogonality catastrophe} between these two ground states.
-The discontinuity increases as \(K\) is increased, indicating that taking more channels will lead to the maximum Bures distance of $d_{Bures}=\sqrt{2}$ and hence an exact orthogonality.
+The discontinuity increases as \(K\) is increased, indicating that considering the case of more channels will lead to the maximum Bures distance of $d_{Bures}=\sqrt{2}$ and hence an exact orthogonality.
 
@@
 
-We start from a strong coupling \((J \to \infty)\) spin-\(S\) impurity MCK Hamiltonian in the over-screened regime \(\left( K > 2S \right) \),
+We start from a strong coupling \((J \to \infty)\) spin-\(S_{d}\) impurity MCK Hamiltonian in the over-screened regime \(\left( K > 2S_{d} \right) \),
 \begin{equation}\begin{aligned}
@@
 Here, \(\vec S\) is the total spin \(\sum_l \sum_{kk^\prime \alpha\beta} \vec \sigma_{\alpha\beta}c^\dagger_{k\alpha,l}c_{k^\prime\beta,l}\) of all the zero modes.
-At strong coupling, the ground states of the star graph eq.~\ref{star graph} act as a good starting point for a perturbative expansion.
+At strong coupling, the ground states of the star graph eq.\eqref{star graph} act as a good starting point for a perturbative expansion.
 As argued previously, there are \(K-2S_d+1\) ground states, labeled by the \(K\) values of the total spin angular momentum \(J^z = S_d^z + S^z = -\frac{K}{2} + S_d, -\frac{K}{2} + S_d + 1, \ldots, \frac{K}{2} - S_d\).
 Since a general spin-\(s\) object is simply a \(2s+1\) level system, the \(K-\)fold degenerate ground state manifold can be used to define a new impurity spin \(\mathbb{S}_d\) of multiplicity \(2\mathbb{S}_d + 1 = K-2S_d+1\) which implies that we need \(\mathbb{S}_d = \frac{K}{2} - S_d\).
-That is, the spin-\(S_d\) impurity has a dual described by a spin-\((K-2S_d+1)\) impurity.
+In other words, the spin-\(S_d\) impurity has a dual described by a spin-\((K-2S_d+1)\) impurity.
 The states of this new spin are defined by
@@
 \begin{equation}\begin{aligned}
-	H^\prime(\mathbb{J}) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + \mathbb{J} \vec{\mathbb{S}_d}\cdot\vec{\mathbb{S}}
+	H^\prime(\mathbb{J}) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + \mathbb{J} \vec{\mathbb{S}_d}\cdot\vec{\mathbb{S}}~.
 \end{aligned}\end{equation}
 $\vec{\mathbb{S}}$ is the local bath spin formed by the new zero modes.
-This Hamiltonian is very similar to the one in eq.~\ref{strong_ham}, and that is the essence of the strong-weak duality: One can go from the over-screened strong coupling spin-\(S\) MCK model to another over-screened weak coupling spin-\((K-2S+1)\) MCK model.
-For the case of \(K=4S\), we have \(\mathbb{S}_d = S_d\), and both \(S_d\) and \(\mathbb{S}_d\) describe the same spin objects (at least formally).
-The two models are then said to be self-dual.
-For example, for the case of spin-half MCK model, two-channel model is self-dual.
+This Hamiltonian is very similar to the one in eq.\eqref{strong_ham}, and that is the essence of the strong-weak duality: One can go from the over-screened strong coupling spin-\(S_{d}\) MCK model to another over-screened weak coupling spin-\((K-2S_{d}+1)\) MCK model.
+For the case of \(K=4S_{d}\), we have \(\mathbb{S}_d = S_d\), and both \(S_d\) and \(\mathbb{S}_d\) describe the same objects: the two models are then said to be self-dual.
+For example, for the case of spin-$1/2$ MCK model, two-channel model is self-dual.
 
@@
 \begin{equation}\begin{aligned}
-	{\mathbb{J}}^* = \frac{\gamma 4t^2}{{\mathcal{J}^*}} = \frac{2}{K \rho^\prime} \implies \gamma = \frac{1}{4t^2} {{\mathcal{J}^*}}^2 = \frac{1}{K^2 t^2 \rho \rho^\prime}
-\end{aligned}\end{equation}
-
-There exists another set of dual points in the MCK model.
-This was hinted at when we looked at the degree of compassion in eq.~\ref{gamma}.
+	{\mathbb{J}}^* = \frac{\gamma 4t^2}{{\mathcal{J}^*}} = \frac{2}{K \rho^\prime} \implies \gamma = \frac{1}{4t^2} {{\mathcal{J}^*}}^2 = \frac{1}{K^2 t^2 \rho \rho^\prime}~.
+\end{aligned}\end{equation}
+
+Apart from the strong-weak duality, there exists another set of dual pairs in the MCK model.
+This was hinted at when we looked at the degree of compensation in eq.\eqref{gamma}.
 Since \(\Gamma\) depends only on the magnitude of \(\delta\), both \(\pm \delta\) will give the same degree of compensation, same ground state energy and same ground state degeneracy \(\left(g^{S_d}_K = |\delta|+1\right)\).
-The definition of \(\delta\) gives the duality transformation as \(K \to 2S_d, S_d \to \frac{K}{2}\).
+The definition of \(\delta\) implies the following duality transformation: \(K \to 2S_d, S_d \to \frac{K}{2}\).
 That is, we transform from a \(K-\)channel MCK model with spin-\(S_d\) impurity, to a \(2S_d\)-channel MCK with a spin-\(\frac{K}{2}\) impurity.
@@
 This duality relationship allows us to infer the RG scaling behaviour of one of the models if we know that of the other.
-If we know that for a certain pair of values \(K\) and \(S_d\), the \(K-\)channel MCK model with spin-\(S_d\) impurity has an intermediate fixed point, we can immediately conclude that the \(2S_d\)-channel spin-\(\frac{K}{2}\) model has a strong coupling fixed point.
+Importantly, we see that the existence of an intermediate coupling fixed point in the MCK model for a given \(K\) and \(S_d\) leads to the conclusion that the \(2S_d\)-channel spin-\(\frac{K}{2}\) model has a strong coupling fixed point.
 
@@
 
-For a channel anisotropic MCK model with \(K\) Kondo couplings \(\mathcal{J}_i\) for each fo the \(K\) conduction channels, the zero bandwidth model is 
+For a channel-anisotropic MCK model with \(K\) Kondo couplings \(\left\{\mathcal{J}_i\right\}\) for each of the \(K\) conduction channels, the zero bandwidth model is 
 \begin{eqnarray}
-H_K (\vec{{\mathcal{J}}}) &=& \sum_{i=1}^{K} {\mathcal{J}}_i\vec{S}_d.\vec{S}_i
+H_K (\vec{{\mathcal{J}}}) &=& \sum_{i=1}^{K} {\mathcal{J}}_i\vec{S}_d.\vec{S}_i~.
 \label{eq:anisotropy}
 \end{eqnarray}
-For the special case $\mathcal{J}_i=\mathcal{J}, \forall i$ we get the usual isotropic star graph model.
+For the special case $\mathcal{J}_i=\mathcal{J} \forall i$, we get the usual isotropic star graph model.
 For the case of spin-1/2 impurity, we find that the Hamiltonian with any value of $\mathcal{J}_i>0$ has $K$ fold ground state degeneracy.
@@
 \centering
-\includegraphics[width=0.48\textwidth]{plt/Anisotropy_Channel_3.png}
+\includegraphics[width=0.48\textwidth]{AnisotropyChannel3.png}
 \caption{\textit{Left:} Variation of the ground state degeneracy against the $J_3$ keeping $J_1=J_2=1$ fixed.
@@
 We have demonstrated this numerically for a three channel anisotropic star graph model.
-In Fig.~\ref{fig:channel-anisotropy-}(a), we show that if two couplings are kept fixed to be equal (${\mathcal{J}}_1={\mathcal{J}}_2=1$) and the third coupling ${\mathcal{J}}_3$ is tuned from some finite value to zero, the degeneracy does not change from 3 to 2 until \(\mathcal{J}_3\) becomes zero.
+In Fig.~\ref{fig:channel-anisotropy-}(a), we show that if two couplings are kept constant and equal to one another (${\mathcal{J}}_1={\mathcal{J}}_2=1$) and the third coupling ${\mathcal{J}}_3$ is tuned from some finite value to zero, the degeneracy does not change from 3 to 2 until \(\mathcal{J}_3\) becomes zero.
 At that point, the model becomes a two channel Kondo problem.
 %{\color{red}
-We also show in Fig.~\ref{fig:channel-anisotropy-}(b) that we keep the first coupling ${\mathcal{J}}_3$ fixed to $1$ and vary the common coupling ${\mathcal{J}}_1={\mathcal{J}}_2$ from non-zero to zero, this is equivalent to keeping ${\mathcal{J}}_1={\mathcal{J}}_2=1$ fixed and taking ${\mathcal{J}}_1$ to infinity from finite.
-In this case we find when the coupling ${\mathcal{J}}_1=\lambda_2=0$ the degeneracy becomes one showing the effective single channel nature.
+We also show in Fig.~\ref{fig:channel-anisotropy-}(b) that taking the coupling ${\mathcal{J}}_3$ fixed to $1$ and varying the common coupling ${\mathcal{J}}_1={\mathcal{J}}_2$ from non-zero to zero is equivalent to keeping ${\mathcal{J}}_1={\mathcal{J}}_2=1$ fixed and taking ${\mathcal{J}}_3$ to infinity.
+In this case, when the coupling ${\mathcal{J}}_1={\mathcal{J}}_2=0$, the degeneracy becomes one and reveals the single channel nature of the problem.
 %}
@@
 
-\par\textit{(a)} If \(j_-<0,j_+>0\), the deviation \(j_-\) is relevant and \(\mathcal{J}_-\) flows to zero.
+\par\textit{(a)} If \(j_-<0\) and \(j_+>0\), the deviation \(j_-\) is relevant and \(\mathcal{J}_-\) flows to zero.
 The flow of \(j_+\) are constrained such that the remaining couplings \(\mathcal{J}_+\) flow to the stable intermediate fixed point of the \(K-1\) channel MCK model: \(J_{+,*} = \frac{2}{(K-1)\rho}\).
-\par\textit{(b)} If \(j_- > 0, j_+<0\), the couplings \(\mathcal{J}_+\) are irrelevant, and this leads to a single channel Kondo model described by the coupling \(\mathcal{J}_-\) which flows to strong coupling.
+\par\textit{(b)} If \(j_- > 0\) and \(j_+<0\), the couplings \(\mathcal{J}_+\) are irrelevant, and this leads to a single channel Kondo model described by the coupling \(\mathcal{J}_-\) which flows to strong coupling.
 
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{conclusions}
+\par\noindent
+In summary, we have explored the low-energy behaviour of the MCK models using the unitary renormalization group (URG) method, and obtained insight into the role of ground state degeneracy and quantum-mechanical frustration in shaping the non-Fermi liquid physics and criticality.
+We have also obtained the zero-temperature phase diagram of the MCK problem and an effective Hamiltonian with a simple zero bandwidth limit (i.e., the star graph), and shown that it determines the ground state energy, wavefunction and degeneracy of the MCK models.
+The star graph is found to explain much of the physics of over-screening and criticality of the MCK: this includes the singularities in the susceptibility and magnetisation, as well as a reduction in the degree to which the impurity spin is compensated.
+This demonstrates the ground state degeneracy of the star graph (which is unity for single-channel, and greater than $1$ for the over-screened models) as the key ingredient in leading to the qualitative and quantitative differences of the MCK from the single-channel Kondo model.
+The presence of ground state degeneracy also allows the construction of non-local twist operators and fractional excitations that span the degenerate ground state manifold.
+Integrating out the quantum fluctuations of the impurity leads to an all-to-all effective Hamiltonian for the local conduction bath spins of the star graph.
+This Hamiltonian is found to contain inter-channel quantum fluctuations involving the scattering of electron-hole pairs, thereby creating a local Mott-liquid phase proximate to the impurity.
 \par 
-In summary, we have explored the low-energy behaviour of the MCK models using the unitary renormalization group (URG) method and obtained a better understanding of the role of ground state degeneracy and quantum-mechanical frustration in shaping the non-Fermi liquid physics and criticality.
-Using the unitary renormalization group technique, we have obtained the zero-temperature phase diagram of the MCK problem and an effective Hamiltonian with a simple zero bandwidth limit - the star graph, and it determines the ground state energy, wavefunction and degeneracy of the MCK models.
-This star graph is found to explain much of the physics of overscreening and criticality, including the singularities in the susceptibility and magnetisation, as well as a reduction in the degree to which the impurity spin is compensated.
-The overarching message there was that the ground state degeneracy of the star graph (which is unity for single-channel and greater for the overscreened models) was the key ingredient in leading to the qualitative and quantitative differences from the single-channel model
-The presence of ground state degeneracy also allows the construction of non-local twist operators and fractional excitations in the ground state manifold.
-Integrating out the quantum fluctuations of the impurity leads to an all-to-all effective Hamiltonian for the local bath spins, and the Hamiltonian is foudn to contain inter-channel quantum scattering in terms of electron-hole pairs, theryby creating a local Mott-liquid phase at the origin of the lattice.
-
-\par The low energy effective Hamiltonian (LEH) for the excitations is then obtain by considering fluctuations of the conduction bath on top of the ground state.
-The LEH for the 2-channel Kondo confirms absence of any Fermi liquid phase due to an exact cancellation across the ground state manifold, and the presence of inter-channel off-diagonal non-Fermi liquid terms.
-Our analysis reinforces the idea that the ground state degeneracy is crucial to the non-Fermi liquid physics and to the presence of such off-diagonal terms in the LEH.
-The existence of a marginal Fermi liquid within the effective Hamiltonian clearly displays the orthogonality catastrophe in the form of singularities that are absent at exact screening.
-Studies of various thermodynamic properties (presented in the supplementary material) from this 2-channel Kondo LEH like specific heat and susceptibility show logarithmic dependence at low temperature, in agreement with the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005,emery_kivelson,andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002}.
-
+The low energy effective Hamiltonian (LEH) for the excitations of the MCK problem is then obtained by considering fluctuations of the conduction bath lying above the ground state.
+The LEH for the 2-channel Kondo confirms the absence of any local Fermi liquid physics, as well as the presence of a local marginal Fermi liquid arising from inter-channel off-diagonal scattering processes.
+This reinforces the idea that the ground state degeneracy is crucial to the appearance of non-Fermi liquid physics at the MCK fixed point.
+Further, we confirm that this arises from an orthogonality catastrophe in the form of singularities that are absent at exact screening.
+Studies of various thermodynamic properties (presented in the Supplementary Material~\cite{SM}) from this 2-channel Kondo LEH (e.g., specific heat and susceptibility) show logarithmic dependence at low temperature, in agreement with the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005,emery_kivelson,andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002}.
 \par 
-The non-diagonal nature of the LEH is further investigated through the several measures of entanglement.
-The entanglement entropy, calculated from the minimum \(J^z\) states, between the impurity and the outer spins, as well as between an outer spin and the rest saturate to \(\ln 2\) in the large channel limit saturate.
-The opposite behaviour happens in the maximum $J^z$ state, where the entanglement entropy decreases with the increase of channel number.
-The large values of inter-channel mutual information indicate high inter-channel correlation in the MCK ground state.
-The power-law dependence of the multi-partite information among the outer spins of the star graph model is similar to the power-law behavior of the all-to-all local Mott-liquid ground state.
-The presence of a discontinuity in the non-Fermi liquid ground state multi-channel entanglement as compared to the smooth behaviour in the single-channel counterpart again points to the orthogonality catastrophe in the low-energy phase of the multi-channel models.
-Higher discontinuity for a higher number of channels was observed in the Bures distance study.
-The URG study of the channel anisotropic MCK shows the critical and unstable nature of the isotropic fixed point; under any anisotropic perturbations, the RG flows go towards either the single-channel model or the symmetric MCK with one less channel coupled to the impurity.
+The non-diagonal nature of the low energy theory is further investigated through several measures of entanglement.
+The entanglement entropy calculated from (i) the minimum \(J^z\) states, (ii)between the impurity and the outer spins as well as (iii) that between an outer spin and the rest, is observed to saturate to \(\ln 2\) in the large channel limit.
+The opposite behaviour is observed in the maximum $J^z$ state, where the entanglement entropy decreases with the increase of channel number.
+Moreover, the large values of inter-channel mutual information indicate high inter-channel correlation in the MCK ground state.
+Indeed, the power-law dependence of the multi-partite information among the outer spins of the star graph model is similar to the power-law behavior of the all-to-all local Mott-liquid state.
+Importantly, the discontinuous behaviour in the entanglement entropy computed for the MCK ground state in the limit of vanishing bath dispersion, as compared to the smooth behaviour observed in its single-channel counterpart, points to the orthogonality catastrophe in the low-energy phase of the multi-channel models.
+We confirm this by noting a similar discontinuous behaviour in the Bures distance computed between the density matrices computed from the ground states of the star graph (i.e., zero bath dispersion bandwidth) and the MCK (i.e, a non-zero the bath dispersion bandwidth).
+This discontinuity in the Bures distance is observed to grow as the number of channels is increased.
+Finally, the URG study of the channel anisotropic MCK shows the expected critical nature of the channel isotropic fixed point: under any anisotropic perturbations, the RG flows go towards either the single-channel model or the symmetric MCK with one less channel coupled to the impurity.
 This is complemented by the study of the star graph ground state degeneracy which shows that the degeneracy changes only if one or more couplings vanishes.
-When combined, we can conclude that in the presence of channel anisotropy, the degeneracy of the MCK ground state does not change until the RG reaches the stable fixed point.
-
-\par This method serves as a template for the study of other quantum impurity systems.
-We have already seen that the degeneracy of the star graph is robust under anisotropy; one can perform similar studies in the presence of a superconducting gap that cuts off the ground state manifold from the excitations, hence providing the degeneracy a topological protection.
-The duality transformations then allow us to view the topologically protected ground state as a larger quantum spin which is essentially isolated.
-This holds immense potential for applications in quantum information and quantum computation.
-More fine-tuned behaviour can be obtained by studying the MCK model with an easy-axis anisotropy term \(\left(J^i\right)^2\) along one of the axes ($i$).
+Taken together, we conclude that in the presence of channel anisotropy, the degeneracy of the MCK ground state does not change until the RG reaches the stable fixed point with one (or more channels) completely disconnected.
+\par 
+We end by discussing some open directions. 
+%Our approach serves as a template for the study of other quantum impurity systems. 
+Our work presents a template for the study of how a degenerate ground state manifold arising from symmetry and duality properties in a multichannel quantum impurity model can lead to novel multicritical phases at intermediate coupling.
+Employed within an auxiliary model framework (such as dynamical mean-field theory), such quantum impurity models will likely unveil novel quantum critical points (or phases) in bulk lattice models of strongly correlated electrons and spins that arise from the competition of various quantum (or symmetry broken) orders.
+Since the degeneracy of the star graph is observed to be robust under anisotropy,
+%Similar studies can be conducted for the case of superconducting leads, i.e., conduction baths with a superconducting gap. Thus, 
+it appears relevant to study the case of the MCK with superconducting leads, i.e., conduction baths with a superconducting gap.
+Specifically, it will be interesting to see whether the gap can separate the ground state manifold of the star graph from any low-energy excitations, providing thereby a protection for the topological quantum numbers associated with the degenerate ground state manifold.
+The duality transformations then allow us to view the protected ground state as that belonging to an isolated larger quantum spin.
+This holds potential for applications in quantum information and quantum computation (see \cite{lopes2020} for an alternate proposal based on an MCK model).
+Interesting behaviour may also be obtained by studying the MCK model with an easy-axis anisotropy term \(\left(J^i\right)^2\) along one of the axes ($i$).
 Such a term would, if it is able to survive the RG flows towards low energy, lift the degeneracy of the ground state and make it possible to achieve perfect screening even with \(K > 2S_d\).
+Further, understanding the nature of the multicriticality in the MCK model displayed upon introducing channel anisotropy is in itself an important problem (see \cite{zheng2021} for a recent work).
 One can also study the multi-channel lattice models~\cite{Piguet1997,shaw_1998} to better understand the role played by singlet frustration and ground state degeneracy in the competition between the local moment versus the heavy fermion sea.
+Finally, we note that experimental realisations of the star graph have been studied recently with regards to aspects of NMR-based quantum information processing such as algorithmic cooling and information scrambling (see \cite{mahesh2021} for a review).
+It will be interesting to see whether some of the results obtained by us for the spin-1/2 Heisenberg star graph can be tested experimentally in a similar manner.
+Finally, it is tempting to speculate whether a similar study can be conducted for a MCK system of 1D Tomonaga-Luttinger liquid conduction leads~\cite{lalbosonMCK2010}.
 
 \acknowledgments
-%\textcolor{red}{
-SP and Anirban Mukherjee thanks the CSIR, Govt.
+S.
+Patra and Anirban Mukherjee thank the CSIR, Govt.
 of India and IISER Kolkata for funding through a research fellowship.
 Abhirup Mukherjee thanks IISER Kolkata for funding through a research fellowship.
-{\color{red}SL thanks $\cdots$}.
-%}
+S.
+Lal thanks the SERB, Govt.
+of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
 
 \bibliography{mscript_mck_full}
+
+%\newpage
+%\clearpage
+%\begin{widetext}
+%
+%
+%\section*{Supplementary Materials for ``Frustration shapes multi-channel Kondo physics: a star graph perspective"}
+%
+%%\author{Siddhartha Patra}
+%%\email{sp14ip022@iiserkol.ac.in }
+%%\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
+%%\author{Abhirup Mukherjee}
+%%\email{am18ip014@iiserkol.ac.in }
+%%\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
+%%\author{Anirban Mukherjee}
+%%\email{mukherjee.anirban.anirban@gmail.com }
+%%\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
+%%\author{N. S. Vidhyadhiraja}
+%%\email{raja@jncasr.ac.in}
+%%\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
+%%\author{A. Taraphder}
+%%\email{arghya@phy.iitkgp.ernet.in}
+%%\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
+%%\author{Siddhartha Lal}
+%%\email{slal@iiserkol.ac.in}
+%%\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
+%%\date{\today}
+%%\maketitle
+%
+%\section{Additional Properties of the Star Graph}
+%
+%\subsection{Energy lowering due to quantum fluctuations}
+%The star graph Hamiltonian that sits at the heart of the RG fixed point Hamiltonian of the multichannel Kondo model contains a classical Ising term and a quantum fluctuation term:
+%\begin{equation}\begin{aligned}
+%	H = {\mathcal{J}}\vec{S_d}\cdot\vec S = \mathcal{J}\left[\underbrace{S_d^z S^z}_\text{Ising term} + \underbrace{\frac{1}{2}\left(S_d^+ S^- + \text{h.c.}\right)}_\text{quantum fluctuation part} \right] = \mathcal{J}\left[\mathcal{H}^C + \mathcal{H}^Q\right] ~.
+%	\label{eq:stargraph_hamiltonian}
+%\end{aligned}\end{equation}
+%We are interested in studying how the presence of quantum fluctuations in the Hamiltonian of eq.~\ref{eq:stargraph_hamiltonian} stabilises the ground state.
+This can be understood by looking at the contributions, per channel, of the classical and the quantum parts to the total ground state energy \(E_g\).
+In the over-screened case \(\left( K > 2S_d \right) \), the contributions are
+%\begin{gather}
+%	E_{C} = \frac{1}{K}\langle \psi_g | \mathcal{H}^C | \psi_g \rangle, ~~~~~ E_{Q} = \frac{1}{K}\bra{\psi_g}\mathcal{H}^Q \ket{\psi_g} =\frac{E_g/\mathcal{J} - E_{C}}{K} =  -\frac{1}{2}S_d - \frac{1}{K}\left(S_d + E_{C}\right)~,
+%\end{gather}  
+%where we have defined the contributions \(E_C\) and \(E_Q\) to the ground state energy coming from the Ising and fluctuation parts respectively, and we have substituted the ground state energy \(E_g\) for the over-screened case from eq.(10) in the main text.
+This contribution $E_Q$ is generated by the spin-flip fluctuations between the impurity spin and the outer spins of the star graph.
+Note that because of the degeneracy of the ground state subspace, there are multiple ground states characterised by different values of \(J^z = S^z + S_d^z\), and different ground states lead to different values of \(E_Q\).
+%
+%The variation of \(E_Q\) is shown in Fig.\ref{fig:quantum_energy} for the case of $S_d=1/2$, as functions of the number of channels \(K\) as well as the ground state value \(J^z\) in which \(E_Q\) is being calculated.
+For a particular channel $K$, we find that the maximum \(|E_Q|\) is obtained for the state with smallest magnitude of $J^z$ (\(J^z = 0 \) for odd \(K\) and \(J^z = \pm 1/2\) for even \(K\)), whereas \(|E_Q|\) is minimum in the states with largest \(J^z\) ($J^z=\pm J$).
+The larger values of \(|E_Q|\) indicate that the quantum fluctuations are largest in the states with minimum \(J^z\), and these states can be thought of as the counterparts to the maximally entangled singlet seen in the single-channel Kondo problem.
+This behaviour persists as \(K \gg 1\): the magnitude \(|Q_Q|\) associated with the $|J^z|= J$ states vanish, showing the classical nature of these states and the lack of quantum fluctuations in that limit.
+On the other hand, the state $|J^z| = |J^z|_{min}$ has a non-zero \(|E_Q|\) in the large \(K\) limit and hence contains some non-zero quantum fluctuations, showing the true quantum nature of this macroscopic singlet state.
+%
+%\begin{figure}[!htb]
+%\centering
+%\includegraphics[width=0.7\textwidth]{QuantumEnergyperchannel}
+%\caption{This shows the variation of quantum energy per channel with $1/N$, where $N=N_{ch}+1$ is the total number of spins in the systems including the impurity spins.}
+%\label{fig:quantum_energy}
+%\end{figure}
+%
+%\subsection{Measure of quantum fluctuations}
+%Here we are interested in calculating the quantum fluctuation present in the  ground state by measuring the expectation value of the spin-flip part of the Hamiltonian: ${\mathcal{Q}}\equiv \langle \psi_g | (J^x)^2+(J^y)^2 |\psi_g\rangle = \langle \psi_g | J^2 - (J^z)^2 |\psi_g\rangle$.
+For a general spin-$S_d$ impurity, the ground state is characterised by $J=|K/2-S_d|$, which gives $J^2=J(J+1)=(|K/2-S_d|)(|K/2-S_d|+1)$.
+We define $\Delta=(K/2-S_d)$ to quantify the deviation from exact screening; $\Delta=0$ represents the exactly screened problem, and $\Delta>0$ and $\Delta<0$ represents the over-screened and under-screened problems respectively.
+Among the degenerate ground state, the maximum quantum fluctuation will occur in the state with minimum \(|J^z|\).
+Since \(J\) can actually be written as \(J = |\Delta|\), \(J\) will take integer values when \(\Delta\) is integer, and the minimum value of \(|J^z|\) is then zero.
+Otherwise, when \(\Delta\) is half-integer, \(J\) will also take half-integer values, and the minimum value of \(|J^z|\) is \(1/2\).
+With these considerations, the minimum value of the quantum fluctuation, {\it per channel}, is
+%\begin{equation}
+%q_K = \frac{1}{K}\sqrt{Q_\text{max}} = \frac{1}{K}\sqrt{\langle \psi_g | J^2 - |J^z|_{min}^2 |\psi_g\rangle} = \begin{cases}
+%	\frac{1}{K}\sqrt{(|K/2-S_d|)(|K/2-S_d|+1)-1/4}, & \text{ where }\Delta\text{ is half-integer}\\
+%	\frac{1}{K}\sqrt{(|K/2-S_d|)(|K/2-S_d|+1)}, & \text{ where }\Delta\text{ is integer}
+%\end{cases}~.
+%\end{equation}
+%This expression is symmetric under the transformation \(\Delta \to -\Delta\), and represents a duality between the over-screened and under-screened models.
+In the limit of large channel number \(K\), \(q_K\) simplifies to $\lim_{K\rightarrow \infty} q_K= \lim_{K \to \infty}\frac{1}{2K}|\Delta(K)|$.
+Only the over- and under-screened models have non-vanishing (and equal) values of \(q_K\).
+%
+%
+%\subsection{Staggered magnetization of the star graph}
+% Another probe to study the screening as a function of \(K\) is the staggered magnetization \(\vec{M}_s=\vec{S}-\vec{S}_d\).
+One can rewrite the Hamiltonian as $\vec{S}_d\cdot\vec{S}= \frac{1}{4}[J^2 - M_s^2]$.
+Since \(J\) and \(M_s\) commute with each other and hence also with the Hamiltonian, the eigenvalues of $\vec{J}^2$ and \(M_s^2\) act as good quantum numbers for in the ground states of the star graph model.
+The larger the value of \(\left<M_s^2\right>\), the stronger is the screening in that ground state.
+For single-channel case with $K=1$, the ground state is a unique 2-spin singlet $|\psi_g\rangle =\frac{1}{\sqrt{2}} (|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle = |J=0,J_z=0\rangle$, and the staggered magnetization per direction is \(M_s^2/3 = 1\), which shows the perfect screening.
+%
+%Calculating the staggered magnetization for a general multichannel problem with \(K\) channels and a spin-\(S_d\) impurity reveals the breakdown of screening brought about by the presence of multiple channels.
+We find, in general, that the square of the staggered magnetization per channel is
+%\begin{equation}
+%	m_s^2 = \left< \left(\frac{1}{K}M_S\right)^2\right> = \frac{1}{K^2}\langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \frac{1}{K^2}\langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle = \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}~.
+%\end{equation}
+%
+%\begin{figure}
+%\includegraphics[width=0.7\textwidth]{Staggeredmag50.png}
+%\caption{This shows how the staggered magnetization changes with the number of channels $N_{ch}$.}
+%\label{fig:st_mag}
+%\end{figure}
+%This shows that as the number of channels increases, the value of \(m_s^2\) decreases from the perfectly-screened value of 3.
+For \(K \to \infty\) and keeping \(S_d\) finite, \(m_s^2\) approaches a lowered value of \(1/4\).
+%
+%Due to the $SU(2)$ symmetry of the problem, the staggered magnetisation is the same along each of the three directions, such that the total value \(m_s^2\) is three times the value in any particular direction:
+%\begin{eqnarray}
+%\langle(m_s^x)^2\rangle=\langle(m_s^y)^2\rangle=\langle(m_s^z)^2\rangle=\frac{1}{3}m_s^2~,~~   
+%\end{eqnarray}
+%As mentioned above, the single channel case displays a value of $\langle (m_s^z)^2 \rangle =1$, showing the perfect screening.
+If one takes the limit of \(K \to \infty\) keeping \(S_d = K/2\), we get the staggered magnetisation at exact-screening and large \(K\), and the value is $\langle (m_s^z)^2 \rangle =1/4$.
+This is reduced from the value at \(K=1\).
+This reduced value however is still greater than the value of \(1/12\) reached as \(K\to \infty\) away from exact-screening by keeping \(S_d\) finite.
+These conclusions can be easily understood from fig.\ref{fig:st_mag} where we have shown the variation of \(\left<m_s^2 \right>\) as a function of \(K\), keeping \(S_d=1/2\).
+%
+%
+%\subsection{Thermodynamic quantities}
+%
+%\subsubsection{Impurity magnetization in terms of parity operators}
+%Just like the complete string operator \(\pi^z\), the modified string operator \(\sigma_d^z \pi^z\) is also a Wilson loop operator that wraps around only the outer nodes of the star graph:
+%\begin{equation}\begin{aligned}
+%	\pi^z_c \equiv \sigma_d^z \pi^z = \exp\left[i \frac{\pi}{2} \left(\sum_{l=1}^K \sigma^z_l - K\right)\right] ~.
+%\end{aligned}\end{equation}
+%The expectation value of the impurity magnetization along a particular direction and in specific ground states can be related to the 't Hooft operator.
+We will work in the state comprised of two adjacent eigenstates of \(J^z\):
+%\begin{equation}\begin{aligned}
+%	\ket{g^\theta_{J^z}} \equiv \frac{1}{\sqrt 2}\left( \ket{J^z} + e^{i\theta}\ket{J^z+1}\right), && J^z < \frac{1}{2}\left( K-1 \right)~.
+%\end{aligned}\end{equation}
+%The expectation value of the impurity magnetization operator \(\sigma_d^x\) can be expressed as
+%\begin{equation}\begin{aligned}
+%	\left<\sigma_d^x\right> \equiv \langle g^\theta_{J^z} \vert \sigma_d^x \vert g^\theta_{J^z}\rangle = - \langle J^z + 1 \vert \pi^x_c \vert -J^z \rangle + \text{h.c.}~.
+%\end{aligned}\end{equation}
+%This expression relates the observable impurity magnetization to the topological 't Hooft operator \cite{Maric2020}. Evaluating the matrix elements gives
+%\begin{equation}\begin{aligned}
+%	\label{sigmax}
+%	\left<\sigma_d^x\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\cos \theta~.
+%\end{aligned}\end{equation}
+%Performing a similar calculation reveals that the impurity magnetizations along \(y\) and \(z\) in the same state are given by
+%\begin{equation}\begin{aligned}
+%	\label{sigmayz}
+%	\left<\sigma_d^y\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\sin \theta, &&\left<\sigma_d^z\right> = - \frac{2J^z + 1}{(1+K)}~.
+%\end{aligned}\end{equation}
+%Combining eqs.~\ref{sigmax} and \ref{sigmayz}, we find
+%\begin{equation}\begin{aligned}
+%	\cos^2\theta\left(\left<\sigma^x_d\right>\right)^2 + \sin^2\theta\left(\left<\sigma^y_d\right>\right)^2 + \frac{1}{4}\left(\left<\sigma^z_d\right>\right)^2 = \frac{1}{4}\left(\frac{K}{1+K}\right)^2~.
+%\end{aligned}\end{equation}
+%This relation \textit{constrains the values of the magnetization} in all the directions: the \(x\) and \(y\) magnetization values have already been shown to be related to the `t Hooft operators \(\pi^x\) and \(\pi^y\) and the magnetization along \(z\) is therefore constrained in terms of the `t Hooft operators and the quantized function on the right-hand side (the function is quantized because \(K\) can only take integer values).
+%
+%\subsubsection{Thermal entropy}
+%The star graph model can be solved to obtain the partition function, and this then allows the computation of the Helmholtz free energy and hence the thermal entropy:
+%\begin{equation}
+%\mathcal{F}= -k_B T\log Z, ~ ~ ~ S = -\frac{\partial \mathcal{F}}{\partial T} = -k_B \log Z -k_B T \frac{1}{Z} \frac{dZ}{dT} = -k_B \log \sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon}  -\frac{1}{\beta} \frac{k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   }{\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon}}~,
+%\end{equation}
+%where \(d(\epsilon)\) is the degeneracy of the state at energy \(\epsilon\). The high and low-temperature limits take very simple forms:
+%\begin{equation}
+%\lim_{\beta\rightarrow \infty} S = -k_B \log_2 d(\epsilon_{G})~,~~\lim_{\beta\rightarrow 0} S = -k_B \log \sum_\epsilon d(\epsilon)~.
+%\end{equation}
+%
+%In fig.\ref{fig:thermal_entropy}, we plot the thermal entropy (in units of $k_B \log 2$) for a range of temperatures and for different values of \(K\).
+At large temperatures, \(S\) saturates to integer multiples of \(k_B \log 2\), while at low-temperatures, that is not always the case.
+This is because the total Hilbert space dimension \(\sum _\epsilon d(\epsilon)\) is simply \(2^N\) (\(N\) being the total number of 1-particle states in the Hilbert space), and therefore \(\log \sum _\epsilon d(\epsilon) = N \log 2\) is always an integer multiple of \(N\).
+On the other hand, the ground state degeneracy \(d(\epsilon_G)\) is \(|K - 2 S_d|\) which is not necessarily of the form \(2^N\) and hence does not always lead to an integer multiple of \(\log 2\).
+%
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.7\textwidth]{ThermalEntanglementVSLogTemperature}
+%\caption{This shows the variation of thermal entropy with the temperature.}
+%\label{fig:thermal_entropy}
+%\end{figure}
+%
+%\section{Additional Topological Features of the Local Mott liquid}
+%
+%The all-to-all Hamiltonian obtained by resolving the impurity-bath quantum fluctuations is written in terms of the spinor spin operators which are individually made out of two electronic degrees of freedom.
+%\begin{equation}\begin{aligned}
+%H_{eff} 
+% =\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)~,
+%%\label{eq:all-to-all_1}
+%\end{aligned}\end{equation}
+%where \(\beta_{\uparrow} ({\mathcal{J}},\omega_{\uparrow})= ({\mathcal{J}}^2 \Gamma_{\uparrow})/2, ~ ~\Gamma_{\uparrow}=(\omega_{\uparrow}-{\mathcal{J}}(S_d^z-1))^{-1}\).
+This spin operator is defined as $\vec{S}_i=\frac{\hbar}{2} \displaystyle\sum_{\substack{ \alpha,\beta\in \{\uparrow,\downarrow\}}}  c_{0\alpha}^{(i)\dagger} \vec{\sigma}_{\alpha\beta} c_{0\beta}^{(i)}$.
+In the above eq.\eqref{eq:all-to-all_1} we see the $U(1)$ symmetry of the effective Hamiltonian.
+Using the spinor representation, we obtain the spin creation operation in terms of the electronic degree of freedom:
+%\begin{equation}
+%S_i^+ = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{+}_{\alpha\beta} c_{0\beta}^{(i)}
+%=\frac{\hbar}{2} c_{0\uparrow}^{(i)\dagger} c_{0\downarrow}^{(i)}, ~ ~ ~S_i^z = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{z}_{\alpha\beta} c_{0\beta}^{(i)} =\frac{\hbar}{2} (c_{0\uparrow}^{(i)\dagger} c_{0\uparrow}^{(i)} - c_{0\downarrow}^{(i)\dagger} c_{0\downarrow}^{(i)} )~.
+%\end{equation}
+%This spinor is simply the Anderson pseudo-spin formulation in the spin channel.
+The spin-creation operator ($S_i^+$) involves the simultaneous creation of an electron-hole pair at the real space origin of the $i^{th}$ conduction channel.
+The condensation of such electron-hole pairs has already been shown in ~\cite{anirbanmott1,anirbanmott2}.
+Thus, for this effective Hamiltonian, one can define twist-translation operations to construct the gauge theory and unveil any hidden degeneracy.
+%
+%Let's recall the effective Hamiltonian
+%\begin{eqnarray}
+%H_{eff} &=& \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{4} \bigg[ \displaystyle\sum_{ij} S_i^+S_j^- ~+ \textrm{h.c.} \bigg]~,
+%\end{eqnarray}
+%where $i,j$ are the channel indices.
+Due to the all-to-all nature of the connectivity, one can draw a total of $K!$ possible unique closed paths ($\mathcal{C}_{\mu}$) such that each node (channel) is touched exactly once.
+These curves lead to $K!$ translation operators ($\hat{T}_{\mu}$) which keeps the Hamiltonian invariant.
+Let's define one such translation operator $\hat{T}_{\mu}=e^{i\hat{P}^{cm}_{{\mu}}}$ which gives a periodic shift along the closed path $\mathcal{C}_{\mu}$.
+The twist operator along the path $\mathcal{C}_{\mu}$ is given by
+%\begin{eqnarray}
+%\hat{\mathcal{O}}_{\mu} &=& \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{C}_{\mu}}}^{K} j S_j^z} )~,
+%\end{eqnarray}
+%The action of the translation operator on \(S_j^z\) is to translate it by one channel index: $\hat{T}_{\mu} S_j^z \hat T^\dagger_\mu = S_{j+1}^z$ where $j+1$ and $j$ are the nearest neighbor on the closed path $\mathcal{C}_{\mu}$.
+Then the braiding rule between the twist and translation operators are give as
+%\begin{equation}
+%\hat{T}_{\mu}\hat{\mathcal{O}}_{\mu} \hat{T}^{\dagger}_{\mu} \hat{\mathcal{O}}_{\mu}^{\dagger} = \exp\{i[2\pi S_1^z-\frac{2\pi}{K}S^z]\} = \exp\{i[\pm \pi - \frac{2\pi}{K} S^z]\} =\exp(i\frac{2\pi p}{q})~.
+%\end{equation}
+%The availability of the non-trivial braiding statistics between these twist and translation operators is possible if $p\neq 0$ and $q\neq \infty$. Further simplification leads to the condition
+%\begin{equation}
+% \pm\pi -\frac{2\pi}{K} S^z = \frac{2\pi p}{q} \implies  \pm\frac{1}{2}-\frac{S^z}{K} = \frac{p}{q} , ~ ~ ~ \frac{(\pm K-2S^z)}{2K} = \frac{p}{q}~,
+%\end{equation} 
+%where $p,q$ are mutual primes.
+We know that the $S^z$ can take values $(\mp K/2\pm m)$ where $m$ is a integer $0 \leq m \leq K$.
+Putting this value in the above equation leads to two possible solutions.
+%\begin{eqnarray}
+%\frac{(K-m)}{K} &=& \frac{p}{q} ~,~~ \frac{-m}{K}=\frac{p}{q}~.
+%\end{eqnarray}
+%For the first case where $K-m=p$, we can see that $m=K$ makes $p$ trivial, and hence the allowed values are $m=0,\cdots,K-1$, which represents the corresponding $S^z$ eigenvalues 
+%\begin{eqnarray}
+%&&-K/2,-K/2+1,\cdots,K/2-2,K/2-1~.
+%\end{eqnarray}
+%Similarly the second case implies, $-m=p$, but $p=0$ is not allowed as this makes the braiding statistics trivial, thus the possible $S^z$ values are 
+%\begin{eqnarray}
+%&&\hspace{2.2cm} -K/2+1,-K/2+2,\cdots,K/2-1,K/2~.
+%\end{eqnarray}
+%
+%Thus we get the general braiding statistics between the twist and the translation 
+%\begin{eqnarray}
+%\hat{T}_{\mu}\hat{\mathcal{O}_{\mu}} \hat{T}^{\dagger}_{\mu}\hat{\mathcal{O}_{\mu}}^{\dagger} &=& e^{i\frac{2\pi p}{K}}~,
+%\end{eqnarray}
+%where $p$ corresponds to different $S^z$ states, related as $p=\pm K/2-S^z$.
+Thus we can see that there are $K$ possible $S^z$ plateau states in the all-to-all model where each plateau is $K$ fold degenerate.
+This $p/K$ is similar to the filling factor of the fractional quantum Hall effect.
+There are $K!$ pairs of twist and translation operators corresponding to different closed paths $\mathcal{C}_{\mu}$ which can probe this degeneracy.
+%
+%\subsection{Action on the Hamiltonian}
+%We will now obtain the action of these twist operators on the Hamiltonian in eq.~\ref{eq:all-to-all_1}.
+Due to the all-to-all nature of the effective Hamiltonian one can find $K!$ possible relative arrangement of those $K$ channels which keeps the Hamiltonian invariant.
+Here we briefly discuss the choice of the closed-loop $\mathcal{C}_{\mu}$ and the insertion of the flux.
+As shown in the Fig.\ref{fig:stargraph-to-alltoall}(b) we have chosen a particular closed path which crosses all the outer spin only once.
+We embed that closed-loop on a plane and put the flux perpendicular to the plane through the closed loop.
+One can find a different closed loop where the ordering of the outer spins will be different.
+The action of the translation operator shifts the outer spins along this closed curve by one step.
+%
+%\begin{figure}[htpb]
+%	\centering
+%	\includegraphics[width=0.8\textwidth]{stargraphtoalltoall.png}
+%	\caption{(a) Schematic diagram of $8-$channel multichannel Kondo model zero mode in zero bandwidth limit.
+(b) All-to-all model obtained by disentangling the impurity spin from the bath zero modes.
+$C_{\mu}$ is a particular closed curve.
+(c) Translated configuration along the curve $C_{\mu}$ by one unit.}
+%	\label{fig:stargraph-to-alltoall}
+%\end{figure}
+%
+%The action of the twist operator on the $S^x$ is determined in the following calculation
+%\begin{equation}
+%\hat{O}_{\mu} S^x \hat{O}^{\dagger}_{\mu} = \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} )S^x \exp({-i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} ) = e^{X} S^x e^{-X}~.
+%\end{equation}
+%To simplify the calculation, we define $i\frac{2\pi}{K}=\Omega$, thus $X=\Omega\sum_j jS^z_j$. Thus we get
+%\begin{equation}
+%e^X S^x e^{-X}= S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots = \sum_l ( S^x_l \cos \theta_l -  S_l^y \sin \theta_l ) ~,~~~\theta_l=\frac{2\pi l}{K}\\
+%e^X S^y e^{-X}= \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)~.
+%\end{equation}
+%As already defined, $\theta_l=\frac{2\pi l}{K}=\frac{2\pi (K-n)}{K}$, where $n$ is an integer.
+We can see that in the large channel limit $\theta_l $ becomes inter multiple of $2\pi$.
+Thus in the large channel limit
+%\begin{gather}
+% \lim_{K\rightarrow \infty}\hat{\mathcal{O}}_{\mu} H_{eff} \hat{\mathcal{O}}_{\mu}^{\dagger}\nonumber = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[ \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger}  + \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger}  \bigg] = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[  S^{x2}+S^{y2}  \bigg] = H_{eff},\\
+% \lim_{K\rightarrow \infty } [\hat{\mathcal{O}},H_{eff}] = 0~.
+%\label{eq:hamiltonian_twisted}
+%\end{gather}
+% 
+%Since the translation operator $\hat{T}_{\mu}=e^{i\hat{\mathcal{P}}_{\mu}}$ commutes with the Hamiltonian, so does the generator $\hat{\mathcal{P}}_{\mu}$.
+We can label the $j^{th}$ state with the eigenvalues of this operator $\hat{\mathcal{P}_{\mu}}$ as $|p^{j}_{\mu}\rangle$.
+The action of these twist and translation operators on these states are
+%\begin{gather}
+%\hat{T}_{\mu} |p^j_{\mu} \rangle = e^{i\hat{\mathcal{P}}_{\mu}} |p^j_{\mu} \rangle = e^{ip^j_{\mu}} |p^j_{\mu}\rangle, ~ ~ ~ ~ \hat{T}_{\mu} \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle =  \hat{\mathcal{O}}_{\mu} \hat{T}_{\mu} e^{i\frac{2\pi m}{K}} |p^j_{\mu}\rangle = \hat{\mathcal{O}}_{\mu}   e^{i(\frac{2\pi m}{K}+p_{\mu}^j)} |p^j_{\mu}\rangle~,~~ \frac{2\pi m}{K} \equiv p_{\mu}^{m}~, \\
+%\hat{T}_{\mu} \bigg( \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle  \bigg) = e^{i(p_{\mu}^{m}+p_{\mu}^j)} \bigg( \hat{\mathcal{O}}_{\mu}    |p^j_{\mu}\rangle \bigg)~,
+%\end{gather}
+%where $m$ represents different $S^z$ plateaux.
+This shows that  $\hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle $ is again an eigenstate of the translation operator, but with an eigenvalue that is different from $|p^j_{\mu} \rangle $, and is thus orthogonal to $\ket{p^j_{\mu}}$.
+Similarly, one can in general show that $\langle p^j_{\mu} | \hat{\mathcal{O}}^{q}_{\mu} |p^j_{\mu} \rangle=0$, where $q$ is any integer.
+Also in the large $K$ limit we can see from the eq.\eqref{eq:hamiltonian_twisted} that these different twisted states has same energy.
+Which shows that at each plateau state labeled by the $S^z$ eigenvalue has $K$ fold degenerate eigenstates labeled by the eigenvalue of the translation operators.
+The complete set of commuting observables is therefore formed by $H,S^z,\hat{T}$, and states can be labeled as  $|E,S^z_j,P^j_{\mu}\rangle$.
+%
+%
+%
+%
+%\section{Effect of conduction bath excitations on the fixed point theory}
+%\subsection{Non-Fermi liquid signatures in momentum space for 2-channel Kondo}
+%Obtaining the effective Hamiltonian involves obtaining the low energy excitations on top of the ground state of the star graph.
+The large-energy excitations involve spin flips.
+This guides the separation of the Hamiltonian into a diagonal and an off-diagonal piece:
+%\begin{align}
+%	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_{V + V^\dagger}
+%\end{align}
+%We define \(V\) as the interaction term that decreases \(s_\text{tot}^z\) by 1: \(V \ket{s_\text{tot}^z} \to \ket{s_\text{tot}^z - 1}\).
+Similarly, we define \(V^\dagger \ket{s_\text{tot}^z} \to \ket{s_\text{tot}^z + 1}\).
+The Schrodinger equation for the ground state can be written as
+%\begin{align}
+%	E_\text{gs}\ket{\Psi_\text{gs}} = H \ket{\Psi_\text{gs}} = \left(H_d + V\right)\ket{\Psi_\text{gs}} \implies \left(E_\text{gs} - H_d\right)\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z} = V\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}
+%\end{align}
+%\(E_\text{gs}\) is the ground state energy, and can be replaced by the star graph ground state energy if we remove the kinetic energy cost via normal ordering: \(E_\text{gs} = -\frac{J}{2}\left(\frac{K}{2}+1\right) \).
+Since the interaction part \(V\) only changes \(S_d^z \to -S_d^z\) and \(s^z_\text{tot} \to s^z_\text{tot} \pm 1\), we can simplify the equation into individual smaller equations.
+For the state \((s_\text{tot},s^z_\text{tot}) = (1,0)\), equations are
+%\begin{equation}
+%	\label{eff_ham_Sdz_10}
+%	E_\text{gs} \ket{\frac{1}{2}, 1, 0} = \left(H_d + V \frac{1}{E_\text{gs} - H_d}V^\dagger\right) \ket{\frac{1}{2}, 1, 0}, ~ ~ ~ ~ ~ E_\text{gs} \ket{-\frac{1}{2}, 1, 0} = \left(H_d + V^\dagger \frac{1}{E_\text{gs} - H_d} V\right) \ket{-\frac{1}{2}, 1, 0}~.\\
+%\end{equation}
+%These represent the Schrodinger equation for the states \(\ket{S_d^z, 1, 0}\), and the right hand sides therefore give the effective Hamiltonians for those states.
+If we combine the states into a single subspace \(\ket{1,0}= \left\{\ket{\frac{1}{2}, 1, 0}, \ket{-\frac{1}{2}, 1, 0}\right\}\), the effective Hamiltonian for this composite subspace becomes the sum of the two parts:
+%\begin{align}
+%	\label{eff_ham_10}
+%	H^{1,0}_\text{eff}\ket{1, 0}\bra{1, 0} = \left(H_d + V G_0 V^\dagger + V^\dagger G_0  V\right) \ket{1, 0}~,
+%\end{align}
+%where \(G_0 = \left(E_\text{gs} - H_d\right)^{-1}\).
+To calculate these effective Hamiltonians, we will expand the denominator in powers of in \(H_0^n/J^{n+1}, n=0,1,2,\ldots\).
+Expanding up to \(n=2\) and keeping at most two particle interaction terms,
+%the effective Hamiltonian is
+%\begin{align}
+%	H_\text{eff}^{1, 0} &= H_0 + \frac{J^2}{2\left(E_\text{gs} + \frac{J}{2}\right)}\left[1 + \frac{ H_0 + \left(\frac{1}{2} + S_d^z\right) s^+_\text{tot}X_{1,\text{tot}} - \left(\frac{1}{2} - S_d^z\right) s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 \left(E_\text{gs} + \frac{J}{2}\right)} + \frac{H_0^2}{\left(E_\text{gs} + \frac{J}{2}\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + \frac{J}{2}\right)^3} \right]~.
+%\end{align}
+%We employed the definitions 
+%\begin{equation}\begin{aligned}
+%X_{n,\text{tot}} \equiv  \sum_l \sum_{k,k^\prime}\left(\epsilon_k - \epsilon_{k^\prime}\right)^n c^\dagger_{k \downarrow}c_{k^\prime \uparrow}, ~ ~ ~ Z_{1,\text{tot}} \equiv \sum_{k,k^\prime,l}\left( \epsilon_k - \epsilon_{k^\prime} \right) \frac{1}{2}\left(c^\dagger_{k \uparrow,l}c_{k^\prime \uparrow,l} - c^\dagger_{k \downarrow,l}c_{k^\prime \downarrow,l}\right)~.
+%\end{aligned}\end{equation}
+%There are several non-Fermi liquid terms of the form \(s^+_\text{tot}X_{1,\text{tot}}, s^-_\text{tot}X^\dagger_{1,\text{tot}},Z_{1,\text{tot}} H_0\).
+These arise because of the degenerate manifold and the increased availability of states in the Hilbert space for scattering, as compared to the unique singlet ground state of the single-channel Kondo model.
+%
+%
+%\subsection{Low-temperature thermodynamic behaviour}
+%The non-Fermi liquid (NFL) nature of the effective Hamiltonian can be demonstrated through a calculation of certain thermodynamic quantities like the impurity specific heat and the magnetic susceptibility.
+We begin by calculating the self-energy of this NFL hamiltonian.
+In real space, one can extract a diagonal piece from the effective Hamiltonian by using the fermionic anticommutation relations.
+%\begin{eqnarray}
+%H_{eff}^{off,(2)} |_{diag} &=& -(16t^2/3) [ (S_1^z)^2+ (S_2^z)^2 ] ~,
+%\end{eqnarray}
+%the corresponding momentum space Hamiltonian is obtained from the Fourier transform:
+%\begin{equation}
+%H_{eff}^{off,(2)} |_{diag}= -\frac{4t^2}{3} \frac{1}{N} \bigg[ \displaystyle\sum_{k,\sigma} n_{k\sigma}(1-\frac{1}{N} \displaystyle\sum_{k_2}  n_{k_2,-\sigma}  ) + \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma} ( 1-\frac{1}{N} \displaystyle\sum_{ k_2} \tilde{n}_{k_2,-\sigma}  ) \bigg]~.
+%\end{equation}
+%The above relation leads to the self-energy correction to the kinetic energy, which is
+%\begin{equation}
+%\bar{\epsilon} _k-\epsilon_k = \Sigma_k = -\frac{4t^2}{3N^2}\bigg(1-\frac{N}{e^{(\epsilon_k-\mu)/k_BT}+1}\bigg)~.
+%\label{eq:self-energy-NFL}
+%\end{equation}
+%Using the self-energy we calculate the impurity specific heat defined as $C_{imp}=C(J^*)-C(0)$ which is defined as
+%\begin{eqnarray}
+%C_{imp} &=& \sum_{\Lambda,\sigma} \beta \bigg[ \frac{(\bar{\epsilon}_{\Lambda})^2 e^{\beta \bar{\epsilon}_{\Lambda}}}{( e^{\beta \bar{\epsilon}_{\Lambda}} +1)^2}  -\frac{({\epsilon}_{\Lambda})^2 e^{\beta {\epsilon}_{\Lambda}}}{( e^{\beta {\epsilon}_{\Lambda}} +1)^2} \bigg]~.
+%\end{eqnarray}
+%\begin{figure}[!htb]
+%\centering
+%\includegraphics[width=0.7\textwidth]{FINALfittedCvt0p1.png}
+%\caption{This figure shows the variation of the impurity specific heat with the temperature.}
+%\label{fig:Cv_imp}
+%\end{figure}
+%Using the self-energy obtained above, we extract the low-temperature behaviour of the impurity specific heat in the two-channel model for $t=0.1$ and $\mathcal{J}=1$, and it is shown in fig,~\ref{fig:Cv_imp}.
+We find that at low-temperatures, the Sommerfeld coefficient \(C_\text{imp}/T\) follows a logarithmic behaviour for the two-channel case, which is in agreement with the results known in the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,
+%parcollet_olivier_large_N,affleck_2005,emery_kivelson,clarke_giamarchi_1993,zarand_2000,
+%vondelft_prl_1998,schofield_1997,bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991,
+%andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002,
+%sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}.
+%\begin{eqnarray}
+%\frac{C_{imp}}{T} \propto \log T~.
+%\end{eqnarray}
+%To calculate the magnetic susceptibility, we numerically diagonalise the low-energy effective Hamiltonian, and use the following expression:
+%\begin{eqnarray}
+%\chi &=& \beta\bigg[\frac{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} \langle \bar{S}^{z2} \rangle}{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} } -\frac{\sum e^{-\beta \epsilon_{\Lambda}} \langle S^{z2 }\rangle }{\sum e^{-\beta \epsilon_{\Lambda}} } \bigg] ~.
+%\end{eqnarray}
+%\begin{figure}[!htb]
+%\centering
+%\includegraphics[width=0.7\textwidth]{NFLChilog0p1}
+%\caption{Susceptibility}
+%\label{fig:NFL_susecptibility}
+%\end{figure}
+%The result is shown in fig.~\ref{fig:NFL_susecptibility}, and we find that at low temperatures, the susceptibility has a logarithmic behaviour.
+%\begin{eqnarray}
+%\chi(T) &\propto& \log T
+%\end{eqnarray}
+%
+%We also calculated the Wilson ratio $C_{imp}/T\chi$, and we find that taking up to three sites on each conduction channel leads to a value of $ W = 8.3$, which is greater than the known value of \(8/3\)~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,
+%parcollet_olivier_large_N,affleck_2005,emery_kivelson,clarke_giamarchi_1993,zarand_2000,
+%vondelft_prl_1998,schofield_1997,bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991,
+%andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002,
+%sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}.
+We find that taking less number of sites leads to a lower value of \(W\), which shows that taking more number of sites will lead to a value of \(W\) that is lower than \(8.3\) and closer to \(8/3\).
+%
+%\subsection{Three channel LEH}
+%Similar to the two channel case, we here calculate the low energy effective Hamiltonian for three channel Kondo problem by introducing the real space hopping on top of the zero mode three-channel star graph model.
+This zero mode three channel star graph model has three fold degenerate ground states with total $2^4=16$ states in the eigenspectrum.
+The three degenerate ground states are given as
+%\begin{gather}
+%|\alpha_{-1}\rangle = c|1000 \rangle-b (|0100 \rangle + |0010 \rangle+ | 0001 \rangle), ~ ~ |\alpha_{+1}\rangle = b(|1110 \rangle+ | 1101 \rangle + | 1011 \rangle)-c | 0111 \rangle,\\
+%|\alpha_0\rangle = -a(|1100 \rangle + |1010\rangle +|1001 \rangle) + a(|0110 \rangle+| 0101 \rangle +| 0011\rangle)~,
+%\end{gather}
+%where $a=0.408$, $b=0.289$, $c=0.866$.
+Here the state is represented by $|n_{d},n_1,n_2,n_3\rangle$, where $n_i=1/0$ represents the spin configuration $S_i^z=\pm 1/2$ respectively.
+Next we use degenerate perturbation theory to get the LEH which contains diagonal and off-diagonal terms.
+In this case we get non-zero contribution from all the three ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$.
+We get the diagonal contribution to the LEH in the second order to be
+%\begin{eqnarray}
+%H^{(2)}_{eff, diag} &=& - \frac{7.2 J^2}{\alpha} \hat{I}~.
+%\end{eqnarray}
+%The contribution associated with different ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$ is given respectively as $- \frac{2.4 J^2}{\alpha} \hat{I} + \hat{\mathcal{F}},- \frac{2.4 J^2}{\alpha} \hat{I} ,- \frac{2.4 J^2}{\alpha} \hat{I} - \hat{\mathcal{F} }$,
+%where $\hat{\mathcal{F}}$ is a function of diagonal number operators of sites nearest neighbor to the zeroth site of each channels.
+The off-diagonal terms in the LEH is appearing due to the scattering between pair of degenerate states $(\alpha_0,\alpha_{+1})$ and $(\alpha_0,\alpha_{-1})$, there is no contribution in the second order coming from the scattering between $(\alpha_{-1},\alpha_{+1})$.
+The effective low energy Hamiltonian in the second order is given as
+%\begin{eqnarray}
+%H^{(2)}_{eff,off-diag} &=& \sum_{\substack{(ijk)=\\(123),(231),(312)}}\bigg[ c_{i\uparrow}c_{i\downarrow}^{\dagger} \bigg( -2ab \bigg\{ \Sigma_{jk} +c_{j\uparrow}^{\dagger}c_{j\downarrow}c_{k\uparrow}c_{k\downarrow}^{\downarrow} \bigg\} -ac(\Omega_{jk}+\tilde{\Omega}_{jk}) \bigg) + ~~\textrm{h.c.}\bigg] \otimes \hat{\Xi}_l~,
+%\end{eqnarray}
+%where the different operators have the following definitions:
+%\begin{gather}
+%\Sigma_{i,j} = n_{i\uparrow}(1-n_{i\downarrow}) (1-n_{j\uparrow})n_{j\downarrow} + (1-n_{i\uparrow})n_{i\downarrow} n_{j\uparrow} (1 -n_{j\downarrow}), ~ ~\Omega_{i,j} =4S_i^z S_j^z n_{i\uparrow} n_{j\uparrow}, ~ ~ \tilde{\Omega}_{i,j} = 4S_{i}^zS_j^z (1-n_{i\uparrow})(1-n_{j\uparrow}) \nonumber~,\\
+% \hat{\Xi}_l=  ( c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.})~.
+%\end{gather}
+%
+%\section{Hamiltonian RG of spin-\(S\) impurity MCK Model}
+%\label{appendix_urg}
+%The Hamiltonian for the channel-isotropic MCK model is:
+%\begin{gather}
+%	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\beta= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~.
+%\end{gather}
+%As mentioned in the same section, the Hamiltonian \(H_{(j-1)}\) of the \((j-1)^\text{th}\) RG step is obtained from the Hamiltonian \(H_{(j)}\) of the preceding RG step by applying a unitary transformation \(U_{(j)}\): \(H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}\).
+The unitary transformation is obtained in terms of the fermionic operator \(\eta_{(j)}\):
+%\begin{gather}
+%	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ ~\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)},~T_{(j)} \equiv \text{Tr}\left(H_{(j)}c_{j}\right)~,~ ~\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} T_{(j)}~.
+%\end{gather}
+%The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms of the Hamiltonian.
+%
+%The URG equation for the single-channel Kondo model \cite{kondo_urg} shows a stable strong coupling fixed point.
+Ferromagnetic interactions are irrelevant.
+Strictly speaking, that RG equation already encodes, in principle, the multi-channel behaviour, through a modified \(\hat \omega\).
+To extract this information, we consider the strong coupling fixed-point \(J \gg D\) as a fixed point and analyze its stability from the star graph perspective.
+For the exactly-screened case, the star graph decouples from the conduction bath, leaving behind a local Fermi liquid interaction on the first site.
+Similarly, in the under-screened regime, the ground state is composed of states where the impurity spin is only partially screened by the conduction channels.
+If a particular configuration of the bath-impurity system has the total conduction bath spin down, the impurity will have a residual up spin.
+This induces a ferromagnetic super-exchange coupling that is irrelevant under RG, so this fixed point is stable as well.
+%
+%We now come to the over-screened case, where there is a residual spin on the conduction channel site.
+The neighbouring electrons will now hop in with spins opposite to that of the impurity, so an antiferromagnetic interaction will be induced, and such an interaction is relevant under the RG.
+This shows that the over-screened regime cannot have a stable strong coupling fixed point, and we need to search for an intermediate coupling fixed point.
+We therefore need the generator of the unitary transformation that incorporates third order scattering scatterings explicitly.
+We should take account of all possible processes that render the set of states \(\left\{\ket{\hat n_{q\beta}=1},\ket{\hat n_{q\beta}=0}\right\}\) diagonal.
+The higher order generator itself has two scattering processes, such that the entire renormalisation term \(c^\dagger_{q\beta} T \eta\) has in total three coherent processes.
+The complete generator up to third order can be written as
+%\begin{equation}\begin{aligned}
+%	\eta = \frac{1}{\hat \omega - H_D}T^\dagger c \simeq \frac{1}{\omega^\prime - H_D}T^\dagger c + \frac{1}{\omega^\prime - H_D}H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X~,
+%\end{aligned}\end{equation}
+%where \(H_X = J \sum_{k,k^\prime < \Lambda_j, \alpha,\alpha^\prime}\vec{S_d}\cdot\vec{s}_{\alpha \alpha^\prime}c^\dagger_{k\alpha}c_{k^\prime\alpha^\prime}\) is scattering between the entangled electrons.
+There are two third order terms in the above equation corresponding to the two possible sequences in which the processes can occur while keeping the total renormalisation \(c^\dagger_{q\beta}T \eta\) diagonal in \(q\beta\).
+The second order processes remain unchanged.
+The total renormalisation takes the form:
+%\begin{equation}
+%	\label{full_ren}
+%	\Delta H_{(j)} = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c  + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(2)}_{(j)}} + \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(3)}_{(j)}}~.
+%\end{equation}
+%\(\Delta H^{(2)}_{(j)}\) and \(\Delta H^{(3)}_{(j)}\) are the renormalisation arising from the second and third order processes respectively.
+%
+%It is easier to see the RG flow of the couplings if we write the Hamiltonian in terms of the eigenstates of \(S_d^z\).
+These eigenstates are defined by \(S_d^z\ket{m_d} = m_d\ket{m_d}, m_d \in \left[-S, S\right]\).
+In terms of these eigenstates, the Hamiltonian becomes
+%\begin{equation}\begin{aligned}
+%	\label{H_spin_S}
+%	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{m_d=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_{m_d} \ket{m_d}\bra{m_d} c^\dagger_{k \sigma}c_{l \sigma} + \sum_{kl} \sum_{m_d=-S}^{S-1} J^t_{m_d} \left(\ket{m_d+1}\bra{m_d} s^-_{kl}  + \text{h.c.}\right)~,
+%\end{aligned}\end{equation}
+%where \(k,l\) sum over the momentum states, \(\sigma\) sums over the spin indices, \(J^\sigma_m = \frac{1}{2} \sigma m J\) in the UV Hamiltonian, and \(J^t_{m} = J\frac{1}{2}\sqrt{S(S+1) - m(m+1)}\) is the coupling that connects \(\ket{m}\) and \(\ket{m+1}\).
+We first calculate \(\Delta H^{(2)}_{(j)}\).
+There will be two types of processes - those processes that start from an occupied state (particle sector) and those that start from a vacant state (hole sector).
+Due to particle hole symmetry of the Hamiltonian, they will be equal to each other and we will only calculate the particle sector contribution.
+%
+%In the particle sector, we have (\(\hat n_{q\beta}=1\)), so we will work at a negative energy  shell \(\epsilon_q = -D\).
+The renormalisation can schematically represented as \(H^I_0 \frac{1}{\omega - H^D_{q\beta}} H^I_1\).
+Both \(H^I_0\) and \(H^I_1\) have all three operators \(S_d^z, S_d^\pm\).
+We first consider specifically the case of spin-\(\frac{1}{2}\) impurity.
+Those terms that have identical operators on both sides can be ignored because \({S_d^z}^2 = \text{constant}\) and \({S^\pm}^2 = 0\).
+All the six terms that \textit{will} renormalise the Hamiltonian have a spin flip operator on at least one side of the Greens function.
+This means that in the denominator of the Greens function, \(S_d^z\) and \(s^z_{qq}\) have to be anti-parallel in order to produce a non-zero result for that term.
+This means we can identically replace \(S_d^z s^z_{qq} = -\frac{1}{4}\).
+Also, in the particle sector, the Greens function always has \(c_{q\beta}\) in front of it, so \(\epsilon_q \tau_{q\beta} = \frac{D}{2}\).
+The upshot of all this is that the denominator of all scattering processes for the spin-\(\frac{1}{2}\) impurity Hamiltonian will be \(\omega - \frac{D}{2} + \frac{J}{4}\).
+%
+%We now come to the general case of spin-\(S\) impurity.
+The various terms that renormalise the Hamiltonian can be described in terms of the bath spin operators that come into them.
+For example, the term that has \(s^z\) on both sides of the intervening Greens function can be represented as \(z|z\).
+There are 7 such terms: \(z|z, \pm|\mp, z|\pm, \pm|z\).
+Each of these terms occurs both in the particle and the hole sectors.
+We will demonstrate the calculation of two of these terms.
+The \(z|z\) \(+|-\) terms evaluate in the following manner.
+%
+%\begin{align}
+%	z|z: & \sum_{kk^\prime,m,\sigma} c^\dagger_{q \sigma} c_{k^\prime \sigma} \ket{m}\bra{m}\frac{{J^\sigma_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}\sigma S_d^z}\ket{m}\bra{m} c^\dagger_{k \sigma}c_{q \sigma} = -\sum_{kk^\prime,m,\sigma}n_{q \sigma}\frac{{J^\sigma_m}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma} \ket{m}\bra{m}}{\omega_{m, \sigma} - \frac{D}{2} + \frac{J}{2}\sigma m}~,\\
+%	+|-: & \sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m+1, \uparrow} - \frac{D}{2} + \frac{J}{2}\left( m+1 \right) }~.
+%\end{align}
+%We similarly compute the rest of the terms.
+We again define \(\sum_q \hat n_{q\sigma} = n(D)\).
+To compare with the spin-\(\frac{1}{2}\) RG equations, we will transform the general spin-\(S\) \(\omega\) to the spin-\(\frac{1}{2}\) \( \omega\), using \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).
+%The renormalisation in \(J^\sigma_m\) is
+%\begin{equation}\begin{aligned}
+%	\Delta J^\sigma_{m} = - n(D) \frac{\left( J^\sigma_m \right) ^2 + \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+%\end{aligned}\end{equation}
+%Here, we have defined \(J^t_m = 0\) for \( |m| > S\).
+Two relations can be obtained from this RG equation, the RG equations for the sum and difference of the couplings: \(J^\pm_m = \frac{1}{2}\left(J^\uparrow_m \pm J^\downarrow_m\right) \).
+The RG equation for the sum of the couplings is
+%\begin{equation}\begin{aligned}
+%	\Delta J^+_m = -n(D)\frac{\sum_\sigma \left( J^\sigma_m \right) ^2 + \sum_\sigma \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{2\left(\omega - \frac{D}{2} + \frac{J}{4}\right)} = -n(D)\frac{J^2}{4}\frac{S(S+1)}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+%\end{aligned}\end{equation}
+%This is an \(m-\)independent piece, so it can be summed over to produce an impurity-independent potential scattering term, which we ignore. 
+%
+%The second is the RG equation for the difference of the couplings:
+%\begin{equation}\begin{aligned}
+%	\Delta J^-_m = -n(D)\frac{1}{2}\frac{\left( J^t_{m-1} \right) ^2 - \left(J^t_{m}\right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{4}\frac{n(D) m J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+%\end{aligned}\end{equation}
+%The usual \(J\) Kondo coupling is recovered through \(J = 2J^-_m/m\). Substituting this gives 
+%\begin{equation}\begin{aligned}
+%	\Delta_\text{p sector} J = -\frac{1}{2}n(D)\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+%\end{aligned}\end{equation}
+%
+%We can also obtain the RG equation for \(J\) from the transverse renormalisation:
+%\begin{equation}\begin{aligned}
+%	\Delta J^t_m &= - \frac{n(D)J^t_m \left( J^\downarrow_m + J^\uparrow_{m+1} \right) }{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{2}\frac{n(D)J^t_m J}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+%\end{aligned}\end{equation}
+%Since \(J^t_m \propto J\), we have
+%\begin{equation}\begin{aligned}
+%	\Delta J_\text{p sector} &= -\frac{1}{2}\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+%\end{aligned}\end{equation}
+%The total renormalisation from both particle and hole sectors, at this order, is
+%\begin{equation}\begin{aligned}
+%	\Delta J^{(2)} &= -\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+%\end{aligned}\end{equation}
+%
+%We now come to the third-order renormalisation.
+%Following eq.~\ref{full_ren}, the next order renormalisation is
+%\begin{equation}\begin{aligned}
+%	\label{psector_3rd_ren}
+%	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X~.
+%\end{aligned}\end{equation}
+%The first term will be of the form
+%\begin{equation}\begin{aligned}
+%	\sum_{q,k,l_1} c^\dagger_{q\beta, l_1}c_{k \alpha, l_1}\ket{m_1}\bra{m_2} \frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z} \ket{m_2} c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \bra{m_3}\frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z}\ket{m_3}\bra{m_4}c^\dagger_{k\alpha, l_1}c_{q\beta, l_1}~.
+%\end{aligned}\end{equation}
+%We have not bothered to write all the summations and the couplings correctly, because we will only simplify the denominator here. Evaluating the inner products gives
+%\begin{equation}\begin{aligned}
+%	\sum_{qk,l_1} \frac{\ket{m_1}\bra{m_4}c^\dagger_{q\beta}c_{k \alpha}c^\dagger_{k_1 \sigma_1, l_2}}{\omega_{m_2,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_2}{4}}  \frac{c_{k_2 \sigma_2,l_2}c^\dagger_{k\alpha}c_{q\beta}}{\omega_{m_3,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_3}{4}}~.
+%\end{aligned}\end{equation}
+%We again use \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).
+%\begin{equation}\begin{aligned}
+%	\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}\sum_{qk,l_1} \frac{\hat n_{q\beta}\left(1 - \hat n_{k\alpha}\right)}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2}~.
+%\end{aligned}\end{equation}
+%We define \(\sum_q \hat n_{q\beta} = n(D)\). Performing the sums over \(k\) and \(l_1\) gives
+%\begin{equation}\begin{aligned}
+%	-\frac{1}{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+%\end{aligned}\end{equation}
+%\(\rho\) is the density of states which we have taken to be constant. Reinstating the complete summation and the couplings gives
+%\begin{equation}\begin{aligned}
+%	\label{first_group}
+%	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{2}\lambda_{3}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}~.
+%\end{aligned}\end{equation}
+%There is no sum over \(m_2\) and \(m_3\) because they are constrained by \(m_1\) and \(m_4\) respectively.
+\(\lambda_i\) represent the couplings present at the three interaction vertices.
+\(k_{1,2}\) sum over the momenta, \(\sigma_{1,2}\) sum over the spin indices and \(l_2\) sums over the channels.
+%
+%The second term in eq.~\ref{psector_3rd_ren} can be evaluated in an almost identical fashion. The integral here will be negative of the first term, because of an exchange in the scattering processes.
+%\begin{equation}\begin{aligned}
+%	\label{second_group}
+%	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{3}\lambda_{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}~.
+%\end{aligned}\end{equation}
+%The first group of terms (those that appear in \ref{first_group}) in the particle sector can be represented as \(a|b^\prime|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three connected processes.
+The \(\prime\) on \(b\) indicates that it is the state of the electrons \textit{not being decoupled}.
+The second group of terms (those that appear in \ref{second_group}) are therefore represented as \(a|b|c^\prime\), because in this group, the interaction \(H_X\) between the electrons that are not being decoupled occur at the very end.
+%We will only calculate the terms in the particle sector, the ones in hole sector will be equal to these because of particle-hole symmetry. The full list of terms is: 
+%
+%
+%$z|z^\prime|z\quad$
+%$z|z|z^\prime\quad$
+%$-|z^\prime|+\quad$
+%$-|+|z^\prime\quad$
+%$+|z^\prime|-\quad$
+%$+|-|z^\prime\quad$
+%$ z|+^\prime|z\quad$
+%$z|-^\prime|z\quad$
+%$+|+^\prime|-\quad$
+%$-|+^\prime|+\quad$
+%$z|z|+^\prime\quad$
+%$z|z|-^\prime\quad$
+%$ +|-|+^\prime\quad$
+%$+|-|-^\prime\quad$
+%$-|+|+^\prime\quad$
+%$z|z^\prime|z\quad$
+%$z|z|z^\prime\quad$
+%$-|z^\prime|+\quad$
+%$ -|+|z^\prime\quad$
+%$+|z^\prime|-\quad$
+%$+|-|z^\prime\quad$
+%$z|+^\prime|z\quad$
+%$z|-^\prime|z\quad$
+%$+|+^\prime|-\quad$
+%$-|+^\prime|+\quad$
+%$z|z|+^\prime\quad$
+%$z|z|-^\prime\quad$
+%$+|-|+^\prime\quad$
+%$+|-|-^\prime\quad$
+%$-|+|+^\prime\quad$
+%.
+%
+%The total renormalisation in  \(J^\sigma_m\) is
+%\begin{equation}\begin{aligned}
+%	\Delta J^\sigma_m = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\left[\left( J^t_{m-1} \right)^2 J^\sigma_m + \left( J^t_m \right)^2 J^\sigma_m - \left( J^t_{m-1} \right)^2 J^\sigma_{m-1} - \left(J^t_m\right)^2 J^\sigma_{m+1} \right] = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3 m \sigma~.
+%\end{aligned}\end{equation}
+%Since we had defined \(J^\sigma_m \equiv \frac{1}{2}J m \sigma\), we have \(\Delta J = \frac{2}{m\sigma}\Delta J^\sigma_m\), and we get \(\Delta_\text{p sector} J = \frac{1}{4}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3\).
+%Combining with the hole sector renormalisation, we get
+%\begin{equation}\begin{aligned}
+%	\Delta J^{(3)} = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3~.
+%\end{aligned}\end{equation}
+%The total renormalisation in \(J\) after combining all orders is
+%\begin{equation}\begin{aligned}
+%	\Delta J = -\frac{n(D) J^2}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3~.
+%\end{aligned}\end{equation}
+%
+%\end{widetext}
+%
+%%\bibliography{mscript_mck_supp}
 \end{document}

### 2022-06-25 Ref Response/RefereeResponse.tex
incorporated referee comments in manuscript

@@
 \usepackage{amsmath,amssymb,braket}
-\usepackage[margin=0.5in]{geometry}
-\usepackage{geometry}
 \usepackage{color}
 \usepackage{xcolor}
-\geometry{legalpaper, portrait, margin=1in}
+\usepackage[legalpaper, portrait]{geometry}
 \DeclareUnicodeCharacter{2212}{-}
@@
 \newcommand{\point}[1]{\subsection{}{#1}}
-\usepackage{multicol}
 
@@
 The spectral function revealed the expected Abrikosov-Suhl resonance at zero frequency, and satisfied the Friedel sum rule.
-We believe a similar  computation can also be performed to obtain other dynamical quantities like the conductance or the resistance.
-{\color{red}Should we mention gen-siam-3-peak,etc as an unpublished work here?}}
+We believe a similar  computation can also be performed to obtain other dynamical quantities like the conductance or the resistance.}
 
@@
 \response{ In the example cited in the question, we used numerical calculations in the sense of solving the star graph Hamiltonian using exact diagonalisation and then using Eq.(19) to obtain the susceptibility.
-In order to obtain the contribution to the susceptibility coming from the non-Fermi liquid, however, we did indeed solve the renormalization group equations numerically to obtain the fixed point Hamiltonian.}
+In the Supplementary Material~\cite{SM}, in order to obtain the contribution to the susceptibility coming from the non-Fermi liquid, we numerically diagonalise the Hamiltonian formed of the star graph and the single-particle excitations into the conduction bath.}
 
@@
 
-\response{While the RG formalism can be put into a numerical setup by abstracting the RG equations, we believe there is greater utility in sticking to the analytical form because it allows applying the method to a wide variety of systems and multiple geomteries, as can be seen in the references mentioned in the work.
+\response{
+NEED TO UPADATE THIS
+
+While the RG formalism can be put into a numerical setup by abstracting the RG equations, we believe there is greater utility in sticking to the analytical form because it allows applying the method to a wide variety of systems and multiple geomteries, as can be seen in the references mentioned in the work.
 Moreover, the analytical approach makes it much more easier to obtain fixed point Hamiltonians.}
@@
 The expression in Eq.(18) was derived for the specific case of $S_d = 1/2$ (spin-half impurity), hence it only vanishes at $K=2S_d=1$.
-The more general case of spin-\(S_d\) impurity was checked numerically, and reported in Fig.(4).
-We have now included the more general analytical expression for the susceptibility in the manuscript, and this expression does indeed vanish at $K = 2S_d$.}
+The more general case of spin-\(S_d\) impurity was checked numerically, and reported in Fig.(4).}
 
@@
 \response{ We thank the referee for allowing us to clarify this.
-We used the term “non-Fermi liquid” to reflect the fact that, in the RG sense, the low energy $k−$space Hamiltonian was not purely of an $F_{kk^\prime} n_k n_{k^\prime}$ density-density type interaction term.}
+We used the term “non-Fermi liquid” to reflect the fact that, in the RG sense, the low energy $k−$space Hamiltonian was not purely of an $F_{kk^\prime} n_k n_{k^\prime}$ density-density type interaction term (which is characteristic of a Fermi liquid).}
 
@@
 
+\section{Some additional changes in the manuscript}
+We made the following additional changes in the manuscript, apart from those arising from the suggestions made by the referees (as mentioned above).
+\begin{itemize}
+	\item Updated an arxiv preprint reference to journal
+	\item Modified acknowledgments
+\end{itemize}
+
 \bibliographystyle{unsrt}

### 2022-06-25 manuscript/mscript_mck_full.tex
incorporated referee comments in manuscript

@@
 Our results display the importance of ground state degeneracy in explaining various important properties like the breakdown of screening and the presence of local non-Fermi liquids.
-The impurity susceptibility of the intermediate coupling fixed point Hamiltonian in the zero-bandwidth (or star graph) limit shows a power-law divergence at low temperature, signalling its critical nature.
+The impurity susceptibility of the intermediate coupling fixed point Hamiltonian in the zero-bandwidth (or star graph) limit shows a power-law divergence at low temperature{\color{red}, signalling its critical nature}.
 Despite the absence of inter-channel coupling in the MCK fixed point Hamiltonian, the study of mutual information between any two channels shows non-zero correlation between them.
@@
 Further, the system displays anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (upon ensuring that temperature is taken to zero before the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
-This anomalous divergent behaviour is a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: the ground state is susceptible to perturbations that introduce channel isotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}.
+This anomalous divergent behaviour is a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: the ground state is susceptible to perturbations that introduce channel anisotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}.
 This makes the experimental realisation of such states quite challenging.
@@
 The degree of compensation is simply the average correlation between the impurity spin and the conduction channel local spins; it is found to be maximum at exact screening, and decreases for both over- and under-screening.
-The magnetisation and susceptibility of the star graph model show critical behaviour in the form a discontinuity and a \(T^{-1}\) divergence respectively.
+The magnetisation and susceptibility of the star graph model show {\color{red}critical behaviour in the form} a discontinuity and a \(T^{-1}\) divergence.
 We also explore the topological properties of the degenerate ground state manifold of the star graph model using non-local twist and translation operators.
@@
 	\label{mc_ham}
-	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\beta= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~,~~
+	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\alpha^\prime= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~,~~
 \end{gather}
 where \(\mathcal{J}\) is the Kondo spin-exchange coupling, \(c_{k\alpha,l}\) is the fermionic field operator at momentum \(k\), spin \(\alpha\) and channel \(l\), \(\epsilon_{k,l}\) represents the dispersion of the \(l^\text{th}\) conduction channel, \(\vec \sigma\) is the vector of Pauli matrices and \(\vec S_d = \frac{1}{2}\vec \sigma_d\) is the impurity spin operator.
-Here, \(l\) sums over the \(K\) channels of the conduction bath, \(k,k^\prime\) sum over all the momentum states of the bath and \(\alpha,\beta\) sum over the two spin indices of a single electron.
+Here, \(l\) sums over the \(K\) channels of the conduction bath, \(k,k^\prime\) sum over all the momentum states of the bath and \(\alpha,\alpha^\prime\) sum over the two spin indices of a single electron.
 
@@
 \begin{equation}\begin{aligned}
-	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ \quad\left\{ \eta_{(j)},\eta_{(j)}^\dagger \right\}_\pm = 1~,
-\end{aligned}\end{equation}
-where \(\left\{A,B\right\}_\pm = AB \pm BA\). The generator itself is given by the expression~\cite{anirbanurg1,anirbanurg2}
+	\label{unitary}
+	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ \quad\left\{ \eta_{(j)},\eta_{(j)}^\dagger \right\} = 1~,
+\end{aligned}\end{equation}
+where \(\left\{\cdot\right\}\) is the anticommutator.
+{\color{blue}The unitary operator \(U_{(j)}\) mentioned in Eq.~\eqref{unitary} can be thought of as a special case of the most general form \(U = e^\mathcal{S}\) of a unitary operator defined by an anti-Hermitian generator \(\mathcal{S}\).
+For our case, the generator turns out to be \(\mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right) \), such that the unitary operator is \(U_{(j)} = e^{\frac{\pi}{4}\left(\eta^\dagger_{(j)} - \eta_{(j)}\right) }\).
+If one then uses the anti-commutation and commutation properties of \(\eta_{(j)},\eta^\dagger_{(j)}\)~\cite{anirbanurg1,anirbanurg2}, the exponential can be expanded in its Taylor series and then "resummed" into the form in Eq.~\eqref{unitary}.}
+
+The generator itself is given by the expression~\cite{anirbanurg1,anirbanurg2}
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
+{\color{blue}The operators \(\eta_{(j)},\eta^\dagger_{(j)}\) can be thought of as the many-particle analogue of the single-particle field operators \(c_j,c^\dagger_j\) that change the occupation number of the single-particle Fock space, \(\ket{n_j}\).
+The extra prefactors are required to ensure that the decoupling of the specific Fock state happens through a unitary modification of the spectrum of the remnant degrees of freedom.
+Since the \(j^\text{th}\) degree of freedom is coupled with the others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\), and this is the reason for the \(\text{Tr}\left(H_(j) c_j\right) \) part.}
 The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms in the Hamiltonian:
@@
 The RG flow continues till a fixed point is reached at an energy \(D^*\).
-%, where a fixed point is reached from the vanishing of the RG function. 
-%from either the numerator or the denominator.
+{\color{blue}The Greens function in front accounts for the dynamical cost of this rotation in terms of the quantum fluctuations \(\hat \omega\) and the kinetic and self energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).}
+
+{\color{blue}There exist other renormalisation group schemes that depend on canonical transformations, like the continuous unitary transformations (CUT) RG as envisaged by Wegner (and others before him).
+There are at least two specific distinctions between the CUT RG and the URG of the present work.
+\begin{itemize}
+	\item While most RG methods that apply successive unitary transformations rely on a gradual decrease in the off-diagonal content of the Hamiltonian, the URG proceeds by decoupling each discrete Fock space node at a time.
+In other words, in the URG, at least one term in the Hamiltonian vanishes at each RG step, while in the CUT RG, there is a gradual decay of the off-diagonal terms in order to make it more band diagonal.
+	\item The CUT RG, specifically, has to be applied by choosing a truncation scheme that allows closing the RG equations.
+The URG, on the other hand, is able to ``resum" the coupling expansion series through the denominator structure and the quantum fluctuation operator.
+\end{itemize}
+}
 
@@
 \begin{equation}\begin{aligned}
-	H^* = \sum_l\left[ \sum^*_{k}\epsilon_{k,l} \hat n_{k\alpha,l} + {\mathcal{J}}\sum_{kk^\prime}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\right]~.
+	H^* = \sum_l\left[ \sum^*_{k}\epsilon_{k,l} \hat n_{k\alpha,l} + {\mathcal{J}}\sum_{kk^\prime\atop{\alpha,\alpha^\prime}}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\right]~.
 \end{aligned}\end{equation}
@@
 The \(*\) over the summations indicate that only the momenta inside the window \(D^*\) enter the summation.
-There is an implied summation over the spin indices \(\alpha,\beta\).
 
@@
 	\label{star graph}
-	H^* = {\mathcal{J}}\sum_l\sum_{kk^\prime}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l} = {\mathcal{J}}\vec{S_d}\cdot\vec S~.
-\end{aligned}\end{equation}
-At the last step, we defined the total bath local spin operator \(S = \sum_l \vec{S}_l = \frac{1}{2}\sigma_l = \frac{1}{2}\sum_{kk^\prime}^*\sum_{\alpha\beta}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\).
+	H^* = {\mathcal{J}}\sum_l\sum_{kk^\prime,\atop{\alpha,\alpha^\prime}}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l} = {\mathcal{J}}\vec{S_d}\cdot\vec S~.
+\end{aligned}\end{equation}
+At the last step, we defined the total bath local spin operator \(S = \sum_l \vec{S}_l = \frac{1}{2}\sigma_l = \frac{1}{2}\sum_{kk^\prime}^*\sum_{\alpha\alpha^\prime}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\).
 \begin{figure}[htpb]
@@
 \end{align}
-where the \(\prime\) indicates derivative with respect to \(h\).
-For brevity, we define \(\theta_M = \beta {\mathcal{J}} (M+\frac{1}{2})/2\) and \(\Sigma_M = \sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}(m+\frac{1}{2})^2\).
-At low temperatures, the derivatives are
+where the \(\prime\) indicates derivative with respect to \(h\). At low temperatures, the derivatives are 
 \begin{align}
 	Z &\to 2 r^K_{M_\text{max}} M_\text{max} e^{\beta \frac{J}{2}(M_\text{max} + 1)}~,\\
-	Z^{\prime \prime} &\to r^K_{M_\text{max}}\left(\frac{\beta }{2(M_\text{max} + \frac{1}{2})}\right)^2 e^{\beta \frac{J}{2}(M_\text{max} + 1)}\Sigma_{M_\text{max}}~,\\
-	\chi &\to \frac{\beta\Sigma_\text{max}}{2M_\text{max}\left(2M_\text{max}+1\right)^2} = \frac{\beta(K-1)}{12(K+1)} \sim \frac{1}{T}~.
+	Z^{\prime \prime} &\to r^K_{M_\text{max}}\left(\frac{\beta }{2(M_\text{max} + \frac{1}{2})}\right)^2 e^{\beta \frac{J}{2}(M_\text{max} + 1)}\Sigma_{M_\text{max}}~,
 \end{align}
+such that the susceptibility is
+\begin{equation}
+	\chi \to \frac{\beta\Sigma_\text{max}}{2M_\text{max}\left(2M_\text{max}+1\right)^2} = \frac{\beta(K-1)}{12(K+1)} \sim \frac{1}{T}~.
+\end{equation}
 
@@
 The \(\chi\) is seen to diverge as \(T^{-1}\) at low temperatures.
-Such a non-analyticity in a response function is a signature of the critical nature of the Hamiltonian.
+{\color{red}Such a non-analyticity in a response function is a signature of the critical nature of the Hamiltonian.
 This is in contrast to the behaviour in the non-critical exactly-screened fixed point where the ground state is unique.
-There, the susceptibility becomes constant at low temperatures: \(\chi(T\to 0) = \frac{W}{4 T_K}\), \(T_K\) being the single-channel Kondo temperature and \(W\) the Wilson number \cite{wilson1975renormalization,nozieres1974fermi,bullaNRGreview,kondo_urg}.
-We have checked the case of general spin-\(S_{d}\) impurity numerically (fig.~\ref{fig:suseptibility_impurity}), and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
+There, the susceptibility becomes constant at low temperatures: \(\chi(T\to 0) = \frac{W}{4 T_K}\), \(T_K\) being the single-channel Kondo temperature and \(W\) the Wilson number \cite{wilson1975renormalization,nozieres1974fermi,bullaNRGreview,kondo_urg}.}
+We have checked the case of general spin-\(S_{d}\) impurity (fig.~\ref{fig:suseptibility_impurity}) by {\color{blue}numerically diagonalising the star graph}, and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
 A similar divergence is also seen in the susceptibility of the outer spins, calculated by inserting a magnetic field purely on the outer spins.
@@
 This available space for scattering is simply the frustration that we discussed earlier.
-Indeed, we have checked numerically (see fig.~\ref{mag_crit}) that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S_{d}\) is the deviation from exact screening.
+Indeed, we have checked (see fig.~\ref{mag_crit}) {\color{blue} by diagonalising the star graph numerically} that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S_{d}\) is the deviation from exact screening.
 Some additional results are presented in the Supplementary Materials~\cite{SM}.
@@
 of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
+We thank three anonymous referees for their valuable questions and comments that greatly helped improve the presentation of the work.
 
@@
 
-%\newpage
-%\clearpage
-%\begin{widetext}
-%
-%
-%\section*{Supplementary Materials for ``Frustration shapes multi-channel Kondo physics: a star graph perspective"}
-%
-%%\author{Siddhartha Patra}
-%%\email{sp14ip022@iiserkol.ac.in }
-%%\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-%%\author{Abhirup Mukherjee}
-%%\email{am18ip014@iiserkol.ac.in }
-%%\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-%%\author{Anirban Mukherjee}
-%%\email{mukherjee.anirban.anirban@gmail.com }
-%%\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-%%\author{N. S. Vidhyadhiraja}
-%%\email{raja@jncasr.ac.in}
-%%\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
-%%\author{A. Taraphder}
-%%\email{arghya@phy.iitkgp.ernet.in}
-%%\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
-%%\author{Siddhartha Lal}
-%%\email{slal@iiserkol.ac.in}
-%%\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-%%\date{\today}
-%%\maketitle
-%
-%\section{Additional Properties of the Star Graph}
-%
-%\subsection{Energy lowering due to quantum fluctuations}
-%The star graph Hamiltonian that sits at the heart of the RG fixed point Hamiltonian of the multichannel Kondo model contains a classical Ising term and a quantum fluctuation term:
-%\begin{equation}\begin{aligned}
-%	H = {\mathcal{J}}\vec{S_d}\cdot\vec S = \mathcal{J}\left[\underbrace{S_d^z S^z}_\text{Ising term} + \underbrace{\frac{1}{2}\left(S_d^+ S^- + \text{h.c.}\right)}_\text{quantum fluctuation part} \right] = \mathcal{J}\left[\mathcal{H}^C + \mathcal{H}^Q\right] ~.
-%	\label{eq:stargraph_hamiltonian}
-%\end{aligned}\end{equation}
-%We are interested in studying how the presence of quantum fluctuations in the Hamiltonian of eq.~\ref{eq:stargraph_hamiltonian} stabilises the ground state.
-This can be understood by looking at the contributions, per channel, of the classical and the quantum parts to the total ground state energy \(E_g\).
-In the over-screened case \(\left( K > 2S_d \right) \), the contributions are
-%\begin{gather}
-%	E_{C} = \frac{1}{K}\langle \psi_g | \mathcal{H}^C | \psi_g \rangle, ~~~~~ E_{Q} = \frac{1}{K}\bra{\psi_g}\mathcal{H}^Q \ket{\psi_g} =\frac{E_g/\mathcal{J} - E_{C}}{K} =  -\frac{1}{2}S_d - \frac{1}{K}\left(S_d + E_{C}\right)~,
-%\end{gather}  
-%where we have defined the contributions \(E_C\) and \(E_Q\) to the ground state energy coming from the Ising and fluctuation parts respectively, and we have substituted the ground state energy \(E_g\) for the over-screened case from eq.(10) in the main text.
-This contribution $E_Q$ is generated by the spin-flip fluctuations between the impurity spin and the outer spins of the star graph.
-Note that because of the degeneracy of the ground state subspace, there are multiple ground states characterised by different values of \(J^z = S^z + S_d^z\), and different ground states lead to different values of \(E_Q\).
-%
-%The variation of \(E_Q\) is shown in Fig.\ref{fig:quantum_energy} for the case of $S_d=1/2$, as functions of the number of channels \(K\) as well as the ground state value \(J^z\) in which \(E_Q\) is being calculated.
-For a particular channel $K$, we find that the maximum \(|E_Q|\) is obtained for the state with smallest magnitude of $J^z$ (\(J^z = 0 \) for odd \(K\) and \(J^z = \pm 1/2\) for even \(K\)), whereas \(|E_Q|\) is minimum in the states with largest \(J^z\) ($J^z=\pm J$).
-The larger values of \(|E_Q|\) indicate that the quantum fluctuations are largest in the states with minimum \(J^z\), and these states can be thought of as the counterparts to the maximally entangled singlet seen in the single-channel Kondo problem.
-This behaviour persists as \(K \gg 1\): the magnitude \(|Q_Q|\) associated with the $|J^z|= J$ states vanish, showing the classical nature of these states and the lack of quantum fluctuations in that limit.
-On the other hand, the state $|J^z| = |J^z|_{min}$ has a non-zero \(|E_Q|\) in the large \(K\) limit and hence contains some non-zero quantum fluctuations, showing the true quantum nature of this macroscopic singlet state.
-%
-%\begin{figure}[!htb]
-%\centering
-%\includegraphics[width=0.7\textwidth]{QuantumEnergyperchannel}
-%\caption{This shows the variation of quantum energy per channel with $1/N$, where $N=N_{ch}+1$ is the total number of spins in the systems including the impurity spins.}
-%\label{fig:quantum_energy}
-%\end{figure}
-%
-%\subsection{Measure of quantum fluctuations}
-%Here we are interested in calculating the quantum fluctuation present in the  ground state by measuring the expectation value of the spin-flip part of the Hamiltonian: ${\mathcal{Q}}\equiv \langle \psi_g | (J^x)^2+(J^y)^2 |\psi_g\rangle = \langle \psi_g | J^2 - (J^z)^2 |\psi_g\rangle$.
-For a general spin-$S_d$ impurity, the ground state is characterised by $J=|K/2-S_d|$, which gives $J^2=J(J+1)=(|K/2-S_d|)(|K/2-S_d|+1)$.
-We define $\Delta=(K/2-S_d)$ to quantify the deviation from exact screening; $\Delta=0$ represents the exactly screened problem, and $\Delta>0$ and $\Delta<0$ represents the over-screened and under-screened problems respectively.
-Among the degenerate ground state, the maximum quantum fluctuation will occur in the state with minimum \(|J^z|\).
-Since \(J\) can actually be written as \(J = |\Delta|\), \(J\) will take integer values when \(\Delta\) is integer, and the minimum value of \(|J^z|\) is then zero.
-Otherwise, when \(\Delta\) is half-integer, \(J\) will also take half-integer values, and the minimum value of \(|J^z|\) is \(1/2\).
-With these considerations, the minimum value of the quantum fluctuation, {\it per channel}, is
-%\begin{equation}
-%q_K = \frac{1}{K}\sqrt{Q_\text{max}} = \frac{1}{K}\sqrt{\langle \psi_g | J^2 - |J^z|_{min}^2 |\psi_g\rangle} = \begin{cases}
-%	\frac{1}{K}\sqrt{(|K/2-S_d|)(|K/2-S_d|+1)-1/4}, & \text{ where }\Delta\text{ is half-integer}\\
-%	\frac{1}{K}\sqrt{(|K/2-S_d|)(|K/2-S_d|+1)}, & \text{ where }\Delta\text{ is integer}
-%\end{cases}~.
-%\end{equation}
-%This expression is symmetric under the transformation \(\Delta \to -\Delta\), and represents a duality between the over-screened and under-screened models.
-In the limit of large channel number \(K\), \(q_K\) simplifies to $\lim_{K\rightarrow \infty} q_K= \lim_{K \to \infty}\frac{1}{2K}|\Delta(K)|$.
-Only the over- and under-screened models have non-vanishing (and equal) values of \(q_K\).
-%
-%
-%\subsection{Staggered magnetization of the star graph}
-% Another probe to study the screening as a function of \(K\) is the staggered magnetization \(\vec{M}_s=\vec{S}-\vec{S}_d\).
-One can rewrite the Hamiltonian as $\vec{S}_d\cdot\vec{S}= \frac{1}{4}[J^2 - M_s^2]$.
-Since \(J\) and \(M_s\) commute with each other and hence also with the Hamiltonian, the eigenvalues of $\vec{J}^2$ and \(M_s^2\) act as good quantum numbers for in the ground states of the star graph model.
-The larger the value of \(\left<M_s^2\right>\), the stronger is the screening in that ground state.
-For single-channel case with $K=1$, the ground state is a unique 2-spin singlet $|\psi_g\rangle =\frac{1}{\sqrt{2}} (|\uparrow\downarrow\rangle-|\downarrow\uparrow\rangle = |J=0,J_z=0\rangle$, and the staggered magnetization per direction is \(M_s^2/3 = 1\), which shows the perfect screening.
-%
-%Calculating the staggered magnetization for a general multichannel problem with \(K\) channels and a spin-\(S_d\) impurity reveals the breakdown of screening brought about by the presence of multiple channels.
-We find, in general, that the square of the staggered magnetization per channel is
-%\begin{equation}
-%	m_s^2 = \left< \left(\frac{1}{K}M_S\right)^2\right> = \frac{1}{K^2}\langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \frac{1}{K^2}\langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle = \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}~.
-%\end{equation}
-%
-%\begin{figure}
-%\includegraphics[width=0.7\textwidth]{Staggeredmag50.png}
-%\caption{This shows how the staggered magnetization changes with the number of channels $N_{ch}$.}
-%\label{fig:st_mag}
-%\end{figure}
-%This shows that as the number of channels increases, the value of \(m_s^2\) decreases from the perfectly-screened value of 3.
-For \(K \to \infty\) and keeping \(S_d\) finite, \(m_s^2\) approaches a lowered value of \(1/4\).
-%
-%Due to the $SU(2)$ symmetry of the problem, the staggered magnetisation is the same along each of the three directions, such that the total value \(m_s^2\) is three times the value in any particular direction:
-%\begin{eqnarray}
-%\langle(m_s^x)^2\rangle=\langle(m_s^y)^2\rangle=\langle(m_s^z)^2\rangle=\frac{1}{3}m_s^2~,~~   
-%\end{eqnarray}
-%As mentioned above, the single channel case displays a value of $\langle (m_s^z)^2 \rangle =1$, showing the perfect screening.
-If one takes the limit of \(K \to \infty\) keeping \(S_d = K/2\), we get the staggered magnetisation at exact-screening and large \(K\), and the value is $\langle (m_s^z)^2 \rangle =1/4$.
-This is reduced from the value at \(K=1\).
-This reduced value however is still greater than the value of \(1/12\) reached as \(K\to \infty\) away from exact-screening by keeping \(S_d\) finite.
-These conclusions can be easily understood from fig.\ref{fig:st_mag} where we have shown the variation of \(\left<m_s^2 \right>\) as a function of \(K\), keeping \(S_d=1/2\).
-%
-%
-%\subsection{Thermodynamic quantities}
-%
-%\subsubsection{Impurity magnetization in terms of parity operators}
-%Just like the complete string operator \(\pi^z\), the modified string operator \(\sigma_d^z \pi^z\) is also a Wilson loop operator that wraps around only the outer nodes of the star graph:
-%\begin{equation}\begin{aligned}
-%	\pi^z_c \equiv \sigma_d^z \pi^z = \exp\left[i \frac{\pi}{2} \left(\sum_{l=1}^K \sigma^z_l - K\right)\right] ~.
-%\end{aligned}\end{equation}
-%The expectation value of the impurity magnetization along a particular direction and in specific ground states can be related to the 't Hooft operator.
-We will work in the state comprised of two adjacent eigenstates of \(J^z\):
-%\begin{equation}\begin{aligned}
-%	\ket{g^\theta_{J^z}} \equiv \frac{1}{\sqrt 2}\left( \ket{J^z} + e^{i\theta}\ket{J^z+1}\right), && J^z < \frac{1}{2}\left( K-1 \right)~.
-%\end{aligned}\end{equation}
-%The expectation value of the impurity magnetization operator \(\sigma_d^x\) can be expressed as
-%\begin{equation}\begin{aligned}
-%	\left<\sigma_d^x\right> \equiv \langle g^\theta_{J^z} \vert \sigma_d^x \vert g^\theta_{J^z}\rangle = - \langle J^z + 1 \vert \pi^x_c \vert -J^z \rangle + \text{h.c.}~.
-%\end{aligned}\end{equation}
-%This expression relates the observable impurity magnetization to the topological 't Hooft operator \cite{Maric2020}. Evaluating the matrix elements gives
-%\begin{equation}\begin{aligned}
-%	\label{sigmax}
-%	\left<\sigma_d^x\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\cos \theta~.
-%\end{aligned}\end{equation}
-%Performing a similar calculation reveals that the impurity magnetizations along \(y\) and \(z\) in the same state are given by
-%\begin{equation}\begin{aligned}
-%	\label{sigmayz}
-%	\left<\sigma_d^y\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\sin \theta, &&\left<\sigma_d^z\right> = - \frac{2J^z + 1}{(1+K)}~.
-%\end{aligned}\end{equation}
-%Combining eqs.~\ref{sigmax} and \ref{sigmayz}, we find
-%\begin{equation}\begin{aligned}
-%	\cos^2\theta\left(\left<\sigma^x_d\right>\right)^2 + \sin^2\theta\left(\left<\sigma^y_d\right>\right)^2 + \frac{1}{4}\left(\left<\sigma^z_d\right>\right)^2 = \frac{1}{4}\left(\frac{K}{1+K}\right)^2~.
-%\end{aligned}\end{equation}
-%This relation \textit{constrains the values of the magnetization} in all the directions: the \(x\) and \(y\) magnetization values have already been shown to be related to the `t Hooft operators \(\pi^x\) and \(\pi^y\) and the magnetization along \(z\) is therefore constrained in terms of the `t Hooft operators and the quantized function on the right-hand side (the function is quantized because \(K\) can only take integer values).
-%
-%\subsubsection{Thermal entropy}
-%The star graph model can be solved to obtain the partition function, and this then allows the computation of the Helmholtz free energy and hence the thermal entropy:
-%\begin{equation}
-%\mathcal{F}= -k_B T\log Z, ~ ~ ~ S = -\frac{\partial \mathcal{F}}{\partial T} = -k_B \log Z -k_B T \frac{1}{Z} \frac{dZ}{dT} = -k_B \log \sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon}  -\frac{1}{\beta} \frac{k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   }{\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon}}~,
-%\end{equation}
-%where \(d(\epsilon)\) is the degeneracy of the state at energy \(\epsilon\). The high and low-temperature limits take very simple forms:
-%\begin{equation}
-%\lim_{\beta\rightarrow \infty} S = -k_B \log_2 d(\epsilon_{G})~,~~\lim_{\beta\rightarrow 0} S = -k_B \log \sum_\epsilon d(\epsilon)~.
-%\end{equation}
-%
-%In fig.\ref{fig:thermal_entropy}, we plot the thermal entropy (in units of $k_B \log 2$) for a range of temperatures and for different values of \(K\).
-At large temperatures, \(S\) saturates to integer multiples of \(k_B \log 2\), while at low-temperatures, that is not always the case.
-This is because the total Hilbert space dimension \(\sum _\epsilon d(\epsilon)\) is simply \(2^N\) (\(N\) being the total number of 1-particle states in the Hilbert space), and therefore \(\log \sum _\epsilon d(\epsilon) = N \log 2\) is always an integer multiple of \(N\).
-On the other hand, the ground state degeneracy \(d(\epsilon_G)\) is \(|K - 2 S_d|\) which is not necessarily of the form \(2^N\) and hence does not always lead to an integer multiple of \(\log 2\).
-%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.7\textwidth]{ThermalEntanglementVSLogTemperature}
-%\caption{This shows the variation of thermal entropy with the temperature.}
-%\label{fig:thermal_entropy}
-%\end{figure}
-%
-%\section{Additional Topological Features of the Local Mott liquid}
-%
-%The all-to-all Hamiltonian obtained by resolving the impurity-bath quantum fluctuations is written in terms of the spinor spin operators which are individually made out of two electronic degrees of freedom.
-%\begin{equation}\begin{aligned}
-%H_{eff} 
-% =\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{4} (S^+S^-+S^-S^+)~,
-%%\label{eq:all-to-all_1}
-%\end{aligned}\end{equation}
-%where \(\beta_{\uparrow} ({\mathcal{J}},\omega_{\uparrow})= ({\mathcal{J}}^2 \Gamma_{\uparrow})/2, ~ ~\Gamma_{\uparrow}=(\omega_{\uparrow}-{\mathcal{J}}(S_d^z-1))^{-1}\).
-This spin operator is defined as $\vec{S}_i=\frac{\hbar}{2} \displaystyle\sum_{\substack{ \alpha,\beta\in \{\uparrow,\downarrow\}}}  c_{0\alpha}^{(i)\dagger} \vec{\sigma}_{\alpha\beta} c_{0\beta}^{(i)}$.
-In the above eq.\eqref{eq:all-to-all_1} we see the $U(1)$ symmetry of the effective Hamiltonian.
-Using the spinor representation, we obtain the spin creation operation in terms of the electronic degree of freedom:
-%\begin{equation}
-%S_i^+ = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{+}_{\alpha\beta} c_{0\beta}^{(i)}
-%=\frac{\hbar}{2} c_{0\uparrow}^{(i)\dagger} c_{0\downarrow}^{(i)}, ~ ~ ~S_i^z = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{z}_{\alpha\beta} c_{0\beta}^{(i)} =\frac{\hbar}{2} (c_{0\uparrow}^{(i)\dagger} c_{0\uparrow}^{(i)} - c_{0\downarrow}^{(i)\dagger} c_{0\downarrow}^{(i)} )~.
-%\end{equation}
-%This spinor is simply the Anderson pseudo-spin formulation in the spin channel.
-The spin-creation operator ($S_i^+$) involves the simultaneous creation of an electron-hole pair at the real space origin of the $i^{th}$ conduction channel.
-The condensation of such electron-hole pairs has already been shown in ~\cite{anirbanmott1,anirbanmott2}.
-Thus, for this effective Hamiltonian, one can define twist-translation operations to construct the gauge theory and unveil any hidden degeneracy.
-%
-%Let's recall the effective Hamiltonian
-%\begin{eqnarray}
-%H_{eff} &=& \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{4} \bigg[ \displaystyle\sum_{ij} S_i^+S_j^- ~+ \textrm{h.c.} \bigg]~,
-%\end{eqnarray}
-%where $i,j$ are the channel indices.
-Due to the all-to-all nature of the connectivity, one can draw a total of $K!$ possible unique closed paths ($\mathcal{C}_{\mu}$) such that each node (channel) is touched exactly once.
-These curves lead to $K!$ translation operators ($\hat{T}_{\mu}$) which keeps the Hamiltonian invariant.
-Let's define one such translation operator $\hat{T}_{\mu}=e^{i\hat{P}^{cm}_{{\mu}}}$ which gives a periodic shift along the closed path $\mathcal{C}_{\mu}$.
-The twist operator along the path $\mathcal{C}_{\mu}$ is given by
-%\begin{eqnarray}
-%\hat{\mathcal{O}}_{\mu} &=& \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{C}_{\mu}}}^{K} j S_j^z} )~,
-%\end{eqnarray}
-%The action of the translation operator on \(S_j^z\) is to translate it by one channel index: $\hat{T}_{\mu} S_j^z \hat T^\dagger_\mu = S_{j+1}^z$ where $j+1$ and $j$ are the nearest neighbor on the closed path $\mathcal{C}_{\mu}$.
-Then the braiding rule between the twist and translation operators are give as
-%\begin{equation}
-%\hat{T}_{\mu}\hat{\mathcal{O}}_{\mu} \hat{T}^{\dagger}_{\mu} \hat{\mathcal{O}}_{\mu}^{\dagger} = \exp\{i[2\pi S_1^z-\frac{2\pi}{K}S^z]\} = \exp\{i[\pm \pi - \frac{2\pi}{K} S^z]\} =\exp(i\frac{2\pi p}{q})~.
-%\end{equation}
-%The availability of the non-trivial braiding statistics between these twist and translation operators is possible if $p\neq 0$ and $q\neq \infty$. Further simplification leads to the condition
-%\begin{equation}
-% \pm\pi -\frac{2\pi}{K} S^z = \frac{2\pi p}{q} \implies  \pm\frac{1}{2}-\frac{S^z}{K} = \frac{p}{q} , ~ ~ ~ \frac{(\pm K-2S^z)}{2K} = \frac{p}{q}~,
-%\end{equation} 
-%where $p,q$ are mutual primes.
-We know that the $S^z$ can take values $(\mp K/2\pm m)$ where $m$ is a integer $0 \leq m \leq K$.
-Putting this value in the above equation leads to two possible solutions.
-%\begin{eqnarray}
-%\frac{(K-m)}{K} &=& \frac{p}{q} ~,~~ \frac{-m}{K}=\frac{p}{q}~.
-%\end{eqnarray}
-%For the first case where $K-m=p$, we can see that $m=K$ makes $p$ trivial, and hence the allowed values are $m=0,\cdots,K-1$, which represents the corresponding $S^z$ eigenvalues 
-%\begin{eqnarray}
-%&&-K/2,-K/2+1,\cdots,K/2-2,K/2-1~.
-%\end{eqnarray}
-%Similarly the second case implies, $-m=p$, but $p=0$ is not allowed as this makes the braiding statistics trivial, thus the possible $S^z$ values are 
-%\begin{eqnarray}
-%&&\hspace{2.2cm} -K/2+1,-K/2+2,\cdots,K/2-1,K/2~.
-%\end{eqnarray}
-%
-%Thus we get the general braiding statistics between the twist and the translation 
-%\begin{eqnarray}
-%\hat{T}_{\mu}\hat{\mathcal{O}_{\mu}} \hat{T}^{\dagger}_{\mu}\hat{\mathcal{O}_{\mu}}^{\dagger} &=& e^{i\frac{2\pi p}{K}}~,
-%\end{eqnarray}
-%where $p$ corresponds to different $S^z$ states, related as $p=\pm K/2-S^z$.
-Thus we can see that there are $K$ possible $S^z$ plateau states in the all-to-all model where each plateau is $K$ fold degenerate.
-This $p/K$ is similar to the filling factor of the fractional quantum Hall effect.
-There are $K!$ pairs of twist and translation operators corresponding to different closed paths $\mathcal{C}_{\mu}$ which can probe this degeneracy.
-%
-%\subsection{Action on the Hamiltonian}
-%We will now obtain the action of these twist operators on the Hamiltonian in eq.~\ref{eq:all-to-all_1}.
-Due to the all-to-all nature of the effective Hamiltonian one can find $K!$ possible relative arrangement of those $K$ channels which keeps the Hamiltonian invariant.
-Here we briefly discuss the choice of the closed-loop $\mathcal{C}_{\mu}$ and the insertion of the flux.
-As shown in the Fig.\ref{fig:stargraph-to-alltoall}(b) we have chosen a particular closed path which crosses all the outer spin only once.
-We embed that closed-loop on a plane and put the flux perpendicular to the plane through the closed loop.
-One can find a different closed loop where the ordering of the outer spins will be different.
-The action of the translation operator shifts the outer spins along this closed curve by one step.
-%
-%\begin{figure}[htpb]
-%	\centering
-%	\includegraphics[width=0.8\textwidth]{stargraphtoalltoall.png}
-%	\caption{(a) Schematic diagram of $8-$channel multichannel Kondo model zero mode in zero bandwidth limit.
-(b) All-to-all model obtained by disentangling the impurity spin from the bath zero modes.
-$C_{\mu}$ is a particular closed curve.
-(c) Translated configuration along the curve $C_{\mu}$ by one unit.}
-%	\label{fig:stargraph-to-alltoall}
-%\end{figure}
-%
-%The action of the twist operator on the $S^x$ is determined in the following calculation
-%\begin{equation}
-%\hat{O}_{\mu} S^x \hat{O}^{\dagger}_{\mu} = \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} )S^x \exp({-i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} ) = e^{X} S^x e^{-X}~.
-%\end{equation}
-%To simplify the calculation, we define $i\frac{2\pi}{K}=\Omega$, thus $X=\Omega\sum_j jS^z_j$. Thus we get
-%\begin{equation}
-%e^X S^x e^{-X}= S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots = \sum_l ( S^x_l \cos \theta_l -  S_l^y \sin \theta_l ) ~,~~~\theta_l=\frac{2\pi l}{K}\\
-%e^X S^y e^{-X}= \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)~.
-%\end{equation}
-%As already defined, $\theta_l=\frac{2\pi l}{K}=\frac{2\pi (K-n)}{K}$, where $n$ is an integer.
-We can see that in the large channel limit $\theta_l $ becomes inter multiple of $2\pi$.
-Thus in the large channel limit
-%\begin{gather}
-% \lim_{K\rightarrow \infty}\hat{\mathcal{O}}_{\mu} H_{eff} \hat{\mathcal{O}}_{\mu}^{\dagger}\nonumber = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[ \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger}  + \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger}  \bigg] = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[  S^{x2}+S^{y2}  \bigg] = H_{eff},\\
-% \lim_{K\rightarrow \infty } [\hat{\mathcal{O}},H_{eff}] = 0~.
-%\label{eq:hamiltonian_twisted}
-%\end{gather}
-% 
-%Since the translation operator $\hat{T}_{\mu}=e^{i\hat{\mathcal{P}}_{\mu}}$ commutes with the Hamiltonian, so does the generator $\hat{\mathcal{P}}_{\mu}$.
-We can label the $j^{th}$ state with the eigenvalues of this operator $\hat{\mathcal{P}_{\mu}}$ as $|p^{j}_{\mu}\rangle$.
-The action of these twist and translation operators on these states are
-%\begin{gather}
-%\hat{T}_{\mu} |p^j_{\mu} \rangle = e^{i\hat{\mathcal{P}}_{\mu}} |p^j_{\mu} \rangle = e^{ip^j_{\mu}} |p^j_{\mu}\rangle, ~ ~ ~ ~ \hat{T}_{\mu} \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle =  \hat{\mathcal{O}}_{\mu} \hat{T}_{\mu} e^{i\frac{2\pi m}{K}} |p^j_{\mu}\rangle = \hat{\mathcal{O}}_{\mu}   e^{i(\frac{2\pi m}{K}+p_{\mu}^j)} |p^j_{\mu}\rangle~,~~ \frac{2\pi m}{K} \equiv p_{\mu}^{m}~, \\
-%\hat{T}_{\mu} \bigg( \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle  \bigg) = e^{i(p_{\mu}^{m}+p_{\mu}^j)} \bigg( \hat{\mathcal{O}}_{\mu}    |p^j_{\mu}\rangle \bigg)~,
-%\end{gather}
-%where $m$ represents different $S^z$ plateaux.
-This shows that  $\hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle $ is again an eigenstate of the translation operator, but with an eigenvalue that is different from $|p^j_{\mu} \rangle $, and is thus orthogonal to $\ket{p^j_{\mu}}$.
-Similarly, one can in general show that $\langle p^j_{\mu} | \hat{\mathcal{O}}^{q}_{\mu} |p^j_{\mu} \rangle=0$, where $q$ is any integer.
-Also in the large $K$ limit we can see from the eq.\eqref{eq:hamiltonian_twisted} that these different twisted states has same energy.
-Which shows that at each plateau state labeled by the $S^z$ eigenvalue has $K$ fold degenerate eigenstates labeled by the eigenvalue of the translation operators.
-The complete set of commuting observables is therefore formed by $H,S^z,\hat{T}$, and states can be labeled as  $|E,S^z_j,P^j_{\mu}\rangle$.
-%
-%
-%
-%
-%\section{Effect of conduction bath excitations on the fixed point theory}
-%\subsection{Non-Fermi liquid signatures in momentum space for 2-channel Kondo}
-%Obtaining the effective Hamiltonian involves obtaining the low energy excitations on top of the ground state of the star graph.
-The large-energy excitations involve spin flips.
-This guides the separation of the Hamiltonian into a diagonal and an off-diagonal piece:
-%\begin{align}
-%	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_{V + V^\dagger}
-%\end{align}
-%We define \(V\) as the interaction term that decreases \(s_\text{tot}^z\) by 1: \(V \ket{s_\text{tot}^z} \to \ket{s_\text{tot}^z - 1}\).
-Similarly, we define \(V^\dagger \ket{s_\text{tot}^z} \to \ket{s_\text{tot}^z + 1}\).
-The Schrodinger equation for the ground state can be written as
-%\begin{align}
-%	E_\text{gs}\ket{\Psi_\text{gs}} = H \ket{\Psi_\text{gs}} = \left(H_d + V\right)\ket{\Psi_\text{gs}} \implies \left(E_\text{gs} - H_d\right)\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z} = V\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}
-%\end{align}
-%\(E_\text{gs}\) is the ground state energy, and can be replaced by the star graph ground state energy if we remove the kinetic energy cost via normal ordering: \(E_\text{gs} = -\frac{J}{2}\left(\frac{K}{2}+1\right) \).
-Since the interaction part \(V\) only changes \(S_d^z \to -S_d^z\) and \(s^z_\text{tot} \to s^z_\text{tot} \pm 1\), we can simplify the equation into individual smaller equations.
-For the state \((s_\text{tot},s^z_\text{tot}) = (1,0)\), equations are
-%\begin{equation}
-%	\label{eff_ham_Sdz_10}
-%	E_\text{gs} \ket{\frac{1}{2}, 1, 0} = \left(H_d + V \frac{1}{E_\text{gs} - H_d}V^\dagger\right) \ket{\frac{1}{2}, 1, 0}, ~ ~ ~ ~ ~ E_\text{gs} \ket{-\frac{1}{2}, 1, 0} = \left(H_d + V^\dagger \frac{1}{E_\text{gs} - H_d} V\right) \ket{-\frac{1}{2}, 1, 0}~.\\
-%\end{equation}
-%These represent the Schrodinger equation for the states \(\ket{S_d^z, 1, 0}\), and the right hand sides therefore give the effective Hamiltonians for those states.
-If we combine the states into a single subspace \(\ket{1,0}= \left\{\ket{\frac{1}{2}, 1, 0}, \ket{-\frac{1}{2}, 1, 0}\right\}\), the effective Hamiltonian for this composite subspace becomes the sum of the two parts:
-%\begin{align}
-%	\label{eff_ham_10}
-%	H^{1,0}_\text{eff}\ket{1, 0}\bra{1, 0} = \left(H_d + V G_0 V^\dagger + V^\dagger G_0  V\right) \ket{1, 0}~,
-%\end{align}
-%where \(G_0 = \left(E_\text{gs} - H_d\right)^{-1}\).
-To calculate these effective Hamiltonians, we will expand the denominator in powers of in \(H_0^n/J^{n+1}, n=0,1,2,\ldots\).
-Expanding up to \(n=2\) and keeping at most two particle interaction terms,
-%the effective Hamiltonian is
-%\begin{align}
-%	H_\text{eff}^{1, 0} &= H_0 + \frac{J^2}{2\left(E_\text{gs} + \frac{J}{2}\right)}\left[1 + \frac{ H_0 + \left(\frac{1}{2} + S_d^z\right) s^+_\text{tot}X_{1,\text{tot}} - \left(\frac{1}{2} - S_d^z\right) s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 \left(E_\text{gs} + \frac{J}{2}\right)} + \frac{H_0^2}{\left(E_\text{gs} + \frac{J}{2}\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + \frac{J}{2}\right)^3} \right]~.
-%\end{align}
-%We employed the definitions 
-%\begin{equation}\begin{aligned}
-%X_{n,\text{tot}} \equiv  \sum_l \sum_{k,k^\prime}\left(\epsilon_k - \epsilon_{k^\prime}\right)^n c^\dagger_{k \downarrow}c_{k^\prime \uparrow}, ~ ~ ~ Z_{1,\text{tot}} \equiv \sum_{k,k^\prime,l}\left( \epsilon_k - \epsilon_{k^\prime} \right) \frac{1}{2}\left(c^\dagger_{k \uparrow,l}c_{k^\prime \uparrow,l} - c^\dagger_{k \downarrow,l}c_{k^\prime \downarrow,l}\right)~.
-%\end{aligned}\end{equation}
-%There are several non-Fermi liquid terms of the form \(s^+_\text{tot}X_{1,\text{tot}}, s^-_\text{tot}X^\dagger_{1,\text{tot}},Z_{1,\text{tot}} H_0\).
-These arise because of the degenerate manifold and the increased availability of states in the Hilbert space for scattering, as compared to the unique singlet ground state of the single-channel Kondo model.
-%
-%
-%\subsection{Low-temperature thermodynamic behaviour}
-%The non-Fermi liquid (NFL) nature of the effective Hamiltonian can be demonstrated through a calculation of certain thermodynamic quantities like the impurity specific heat and the magnetic susceptibility.
-We begin by calculating the self-energy of this NFL hamiltonian.
-In real space, one can extract a diagonal piece from the effective Hamiltonian by using the fermionic anticommutation relations.
-%\begin{eqnarray}
-%H_{eff}^{off,(2)} |_{diag} &=& -(16t^2/3) [ (S_1^z)^2+ (S_2^z)^2 ] ~,
-%\end{eqnarray}
-%the corresponding momentum space Hamiltonian is obtained from the Fourier transform:
-%\begin{equation}
-%H_{eff}^{off,(2)} |_{diag}= -\frac{4t^2}{3} \frac{1}{N} \bigg[ \displaystyle\sum_{k,\sigma} n_{k\sigma}(1-\frac{1}{N} \displaystyle\sum_{k_2}  n_{k_2,-\sigma}  ) + \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma} ( 1-\frac{1}{N} \displaystyle\sum_{ k_2} \tilde{n}_{k_2,-\sigma}  ) \bigg]~.
-%\end{equation}
-%The above relation leads to the self-energy correction to the kinetic energy, which is
-%\begin{equation}
-%\bar{\epsilon} _k-\epsilon_k = \Sigma_k = -\frac{4t^2}{3N^2}\bigg(1-\frac{N}{e^{(\epsilon_k-\mu)/k_BT}+1}\bigg)~.
-%\label{eq:self-energy-NFL}
-%\end{equation}
-%Using the self-energy we calculate the impurity specific heat defined as $C_{imp}=C(J^*)-C(0)$ which is defined as
-%\begin{eqnarray}
-%C_{imp} &=& \sum_{\Lambda,\sigma} \beta \bigg[ \frac{(\bar{\epsilon}_{\Lambda})^2 e^{\beta \bar{\epsilon}_{\Lambda}}}{( e^{\beta \bar{\epsilon}_{\Lambda}} +1)^2}  -\frac{({\epsilon}_{\Lambda})^2 e^{\beta {\epsilon}_{\Lambda}}}{( e^{\beta {\epsilon}_{\Lambda}} +1)^2} \bigg]~.
-%\end{eqnarray}
-%\begin{figure}[!htb]
-%\centering
-%\includegraphics[width=0.7\textwidth]{FINALfittedCvt0p1.png}
-%\caption{This figure shows the variation of the impurity specific heat with the temperature.}
-%\label{fig:Cv_imp}
-%\end{figure}
-%Using the self-energy obtained above, we extract the low-temperature behaviour of the impurity specific heat in the two-channel model for $t=0.1$ and $\mathcal{J}=1$, and it is shown in fig,~\ref{fig:Cv_imp}.
-We find that at low-temperatures, the Sommerfeld coefficient \(C_\text{imp}/T\) follows a logarithmic behaviour for the two-channel case, which is in agreement with the results known in the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,
-%parcollet_olivier_large_N,affleck_2005,emery_kivelson,clarke_giamarchi_1993,zarand_2000,
-%vondelft_prl_1998,schofield_1997,bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991,
-%andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002,
-%sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}.
-%\begin{eqnarray}
-%\frac{C_{imp}}{T} \propto \log T~.
-%\end{eqnarray}
-%To calculate the magnetic susceptibility, we numerically diagonalise the low-energy effective Hamiltonian, and use the following expression:
-%\begin{eqnarray}
-%\chi &=& \beta\bigg[\frac{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} \langle \bar{S}^{z2} \rangle}{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} } -\frac{\sum e^{-\beta \epsilon_{\Lambda}} \langle S^{z2 }\rangle }{\sum e^{-\beta \epsilon_{\Lambda}} } \bigg] ~.
-%\end{eqnarray}
-%\begin{figure}[!htb]
-%\centering
-%\includegraphics[width=0.7\textwidth]{NFLChilog0p1}
-%\caption{Susceptibility}
-%\label{fig:NFL_susecptibility}
-%\end{figure}
-%The result is shown in fig.~\ref{fig:NFL_susecptibility}, and we find that at low temperatures, the susceptibility has a logarithmic behaviour.
-%\begin{eqnarray}
-%\chi(T) &\propto& \log T
-%\end{eqnarray}
-%
-%We also calculated the Wilson ratio $C_{imp}/T\chi$, and we find that taking up to three sites on each conduction channel leads to a value of $ W = 8.3$, which is greater than the known value of \(8/3\)~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,
-%parcollet_olivier_large_N,affleck_2005,emery_kivelson,clarke_giamarchi_1993,zarand_2000,
-%vondelft_prl_1998,schofield_1997,bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991,
-%andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002,
-%sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}.
-We find that taking less number of sites leads to a lower value of \(W\), which shows that taking more number of sites will lead to a value of \(W\) that is lower than \(8.3\) and closer to \(8/3\).
-%
-%\subsection{Three channel LEH}
-%Similar to the two channel case, we here calculate the low energy effective Hamiltonian for three channel Kondo problem by introducing the real space hopping on top of the zero mode three-channel star graph model.
-This zero mode three channel star graph model has three fold degenerate ground states with total $2^4=16$ states in the eigenspectrum.
-The three degenerate ground states are given as
-%\begin{gather}
-%|\alpha_{-1}\rangle = c|1000 \rangle-b (|0100 \rangle + |0010 \rangle+ | 0001 \rangle), ~ ~ |\alpha_{+1}\rangle = b(|1110 \rangle+ | 1101 \rangle + | 1011 \rangle)-c | 0111 \rangle,\\
-%|\alpha_0\rangle = -a(|1100 \rangle + |1010\rangle +|1001 \rangle) + a(|0110 \rangle+| 0101 \rangle +| 0011\rangle)~,
-%\end{gather}
-%where $a=0.408$, $b=0.289$, $c=0.866$.
-Here the state is represented by $|n_{d},n_1,n_2,n_3\rangle$, where $n_i=1/0$ represents the spin configuration $S_i^z=\pm 1/2$ respectively.
-Next we use degenerate perturbation theory to get the LEH which contains diagonal and off-diagonal terms.
-In this case we get non-zero contribution from all the three ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$.
-We get the diagonal contribution to the LEH in the second order to be
-%\begin{eqnarray}
-%H^{(2)}_{eff, diag} &=& - \frac{7.2 J^2}{\alpha} \hat{I}~.
-%\end{eqnarray}
-%The contribution associated with different ground states $|J^z=-1\rangle$, $|J^z=0\rangle$ and $|J^z=1\rangle$ is given respectively as $- \frac{2.4 J^2}{\alpha} \hat{I} + \hat{\mathcal{F}},- \frac{2.4 J^2}{\alpha} \hat{I} ,- \frac{2.4 J^2}{\alpha} \hat{I} - \hat{\mathcal{F} }$,
-%where $\hat{\mathcal{F}}$ is a function of diagonal number operators of sites nearest neighbor to the zeroth site of each channels.
-The off-diagonal terms in the LEH is appearing due to the scattering between pair of degenerate states $(\alpha_0,\alpha_{+1})$ and $(\alpha_0,\alpha_{-1})$, there is no contribution in the second order coming from the scattering between $(\alpha_{-1},\alpha_{+1})$.
-The effective low energy Hamiltonian in the second order is given as
-%\begin{eqnarray}
-%H^{(2)}_{eff,off-diag} &=& \sum_{\substack{(ijk)=\\(123),(231),(312)}}\bigg[ c_{i\uparrow}c_{i\downarrow}^{\dagger} \bigg( -2ab \bigg\{ \Sigma_{jk} +c_{j\uparrow}^{\dagger}c_{j\downarrow}c_{k\uparrow}c_{k\downarrow}^{\downarrow} \bigg\} -ac(\Omega_{jk}+\tilde{\Omega}_{jk}) \bigg) + ~~\textrm{h.c.}\bigg] \otimes \hat{\Xi}_l~,
-%\end{eqnarray}
-%where the different operators have the following definitions:
-%\begin{gather}
-%\Sigma_{i,j} = n_{i\uparrow}(1-n_{i\downarrow}) (1-n_{j\uparrow})n_{j\downarrow} + (1-n_{i\uparrow})n_{i\downarrow} n_{j\uparrow} (1 -n_{j\downarrow}), ~ ~\Omega_{i,j} =4S_i^z S_j^z n_{i\uparrow} n_{j\uparrow}, ~ ~ \tilde{\Omega}_{i,j} = 4S_{i}^zS_j^z (1-n_{i\uparrow})(1-n_{j\uparrow}) \nonumber~,\\
-% \hat{\Xi}_l=  ( c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.})~.
-%\end{gather}
-%
-%\section{Hamiltonian RG of spin-\(S\) impurity MCK Model}
-%\label{appendix_urg}
-%The Hamiltonian for the channel-isotropic MCK model is:
-%\begin{gather}
-%	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\beta= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~.
-%\end{gather}
-%As mentioned in the same section, the Hamiltonian \(H_{(j-1)}\) of the \((j-1)^\text{th}\) RG step is obtained from the Hamiltonian \(H_{(j)}\) of the preceding RG step by applying a unitary transformation \(U_{(j)}\): \(H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}\).
-The unitary transformation is obtained in terms of the fermionic operator \(\eta_{(j)}\):
-%\begin{gather}
-%	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ ~\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)},~T_{(j)} \equiv \text{Tr}\left(H_{(j)}c_{j}\right)~,~ ~\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} T_{(j)}~.
-%\end{gather}
-%The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms of the Hamiltonian.
-%
-%The URG equation for the single-channel Kondo model \cite{kondo_urg} shows a stable strong coupling fixed point.
-Ferromagnetic interactions are irrelevant.
-Strictly speaking, that RG equation already encodes, in principle, the multi-channel behaviour, through a modified \(\hat \omega\).
-To extract this information, we consider the strong coupling fixed-point \(J \gg D\) as a fixed point and analyze its stability from the star graph perspective.
-For the exactly-screened case, the star graph decouples from the conduction bath, leaving behind a local Fermi liquid interaction on the first site.
-Similarly, in the under-screened regime, the ground state is composed of states where the impurity spin is only partially screened by the conduction channels.
-If a particular configuration of the bath-impurity system has the total conduction bath spin down, the impurity will have a residual up spin.
-This induces a ferromagnetic super-exchange coupling that is irrelevant under RG, so this fixed point is stable as well.
-%
-%We now come to the over-screened case, where there is a residual spin on the conduction channel site.
-The neighbouring electrons will now hop in with spins opposite to that of the impurity, so an antiferromagnetic interaction will be induced, and such an interaction is relevant under the RG.
-This shows that the over-screened regime cannot have a stable strong coupling fixed point, and we need to search for an intermediate coupling fixed point.
-We therefore need the generator of the unitary transformation that incorporates third order scattering scatterings explicitly.
-We should take account of all possible processes that render the set of states \(\left\{\ket{\hat n_{q\beta}=1},\ket{\hat n_{q\beta}=0}\right\}\) diagonal.
-The higher order generator itself has two scattering processes, such that the entire renormalisation term \(c^\dagger_{q\beta} T \eta\) has in total three coherent processes.
-The complete generator up to third order can be written as
-%\begin{equation}\begin{aligned}
-%	\eta = \frac{1}{\hat \omega - H_D}T^\dagger c \simeq \frac{1}{\omega^\prime - H_D}T^\dagger c + \frac{1}{\omega^\prime - H_D}H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X~,
-%\end{aligned}\end{equation}
-%where \(H_X = J \sum_{k,k^\prime < \Lambda_j, \alpha,\alpha^\prime}\vec{S_d}\cdot\vec{s}_{\alpha \alpha^\prime}c^\dagger_{k\alpha}c_{k^\prime\alpha^\prime}\) is scattering between the entangled electrons.
-There are two third order terms in the above equation corresponding to the two possible sequences in which the processes can occur while keeping the total renormalisation \(c^\dagger_{q\beta}T \eta\) diagonal in \(q\beta\).
-The second order processes remain unchanged.
-The total renormalisation takes the form:
-%\begin{equation}
-%	\label{full_ren}
-%	\Delta H_{(j)} = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c  + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(2)}_{(j)}} + \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(3)}_{(j)}}~.
-%\end{equation}
-%\(\Delta H^{(2)}_{(j)}\) and \(\Delta H^{(3)}_{(j)}\) are the renormalisation arising from the second and third order processes respectively.
-%
-%It is easier to see the RG flow of the couplings if we write the Hamiltonian in terms of the eigenstates of \(S_d^z\).
-These eigenstates are defined by \(S_d^z\ket{m_d} = m_d\ket{m_d}, m_d \in \left[-S, S\right]\).
-In terms of these eigenstates, the Hamiltonian becomes
-%\begin{equation}\begin{aligned}
-%	\label{H_spin_S}
-%	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{m_d=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_{m_d} \ket{m_d}\bra{m_d} c^\dagger_{k \sigma}c_{l \sigma} + \sum_{kl} \sum_{m_d=-S}^{S-1} J^t_{m_d} \left(\ket{m_d+1}\bra{m_d} s^-_{kl}  + \text{h.c.}\right)~,
-%\end{aligned}\end{equation}
-%where \(k,l\) sum over the momentum states, \(\sigma\) sums over the spin indices, \(J^\sigma_m = \frac{1}{2} \sigma m J\) in the UV Hamiltonian, and \(J^t_{m} = J\frac{1}{2}\sqrt{S(S+1) - m(m+1)}\) is the coupling that connects \(\ket{m}\) and \(\ket{m+1}\).
-We first calculate \(\Delta H^{(2)}_{(j)}\).
-There will be two types of processes - those processes that start from an occupied state (particle sector) and those that start from a vacant state (hole sector).
-Due to particle hole symmetry of the Hamiltonian, they will be equal to each other and we will only calculate the particle sector contribution.
-%
-%In the particle sector, we have (\(\hat n_{q\beta}=1\)), so we will work at a negative energy  shell \(\epsilon_q = -D\).
-The renormalisation can schematically represented as \(H^I_0 \frac{1}{\omega - H^D_{q\beta}} H^I_1\).
-Both \(H^I_0\) and \(H^I_1\) have all three operators \(S_d^z, S_d^\pm\).
-We first consider specifically the case of spin-\(\frac{1}{2}\) impurity.
-Those terms that have identical operators on both sides can be ignored because \({S_d^z}^2 = \text{constant}\) and \({S^\pm}^2 = 0\).
-All the six terms that \textit{will} renormalise the Hamiltonian have a spin flip operator on at least one side of the Greens function.
-This means that in the denominator of the Greens function, \(S_d^z\) and \(s^z_{qq}\) have to be anti-parallel in order to produce a non-zero result for that term.
-This means we can identically replace \(S_d^z s^z_{qq} = -\frac{1}{4}\).
-Also, in the particle sector, the Greens function always has \(c_{q\beta}\) in front of it, so \(\epsilon_q \tau_{q\beta} = \frac{D}{2}\).
-The upshot of all this is that the denominator of all scattering processes for the spin-\(\frac{1}{2}\) impurity Hamiltonian will be \(\omega - \frac{D}{2} + \frac{J}{4}\).
-%
-%We now come to the general case of spin-\(S\) impurity.
-The various terms that renormalise the Hamiltonian can be described in terms of the bath spin operators that come into them.
-For example, the term that has \(s^z\) on both sides of the intervening Greens function can be represented as \(z|z\).
-There are 7 such terms: \(z|z, \pm|\mp, z|\pm, \pm|z\).
-Each of these terms occurs both in the particle and the hole sectors.
-We will demonstrate the calculation of two of these terms.
-The \(z|z\) \(+|-\) terms evaluate in the following manner.
-%
-%\begin{align}
-%	z|z: & \sum_{kk^\prime,m,\sigma} c^\dagger_{q \sigma} c_{k^\prime \sigma} \ket{m}\bra{m}\frac{{J^\sigma_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}\sigma S_d^z}\ket{m}\bra{m} c^\dagger_{k \sigma}c_{q \sigma} = -\sum_{kk^\prime,m,\sigma}n_{q \sigma}\frac{{J^\sigma_m}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma} \ket{m}\bra{m}}{\omega_{m, \sigma} - \frac{D}{2} + \frac{J}{2}\sigma m}~,\\
-%	+|-: & \sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m+1, \uparrow} - \frac{D}{2} + \frac{J}{2}\left( m+1 \right) }~.
-%\end{align}
-%We similarly compute the rest of the terms.
-We again define \(\sum_q \hat n_{q\sigma} = n(D)\).
-To compare with the spin-\(\frac{1}{2}\) RG equations, we will transform the general spin-\(S\) \(\omega\) to the spin-\(\frac{1}{2}\) \( \omega\), using \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).
-%The renormalisation in \(J^\sigma_m\) is
-%\begin{equation}\begin{aligned}
-%	\Delta J^\sigma_{m} = - n(D) \frac{\left( J^\sigma_m \right) ^2 + \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-%\end{aligned}\end{equation}
-%Here, we have defined \(J^t_m = 0\) for \( |m| > S\).
-Two relations can be obtained from this RG equation, the RG equations for the sum and difference of the couplings: \(J^\pm_m = \frac{1}{2}\left(J^\uparrow_m \pm J^\downarrow_m\right) \).
-The RG equation for the sum of the couplings is
-%\begin{equation}\begin{aligned}
-%	\Delta J^+_m = -n(D)\frac{\sum_\sigma \left( J^\sigma_m \right) ^2 + \sum_\sigma \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{2\left(\omega - \frac{D}{2} + \frac{J}{4}\right)} = -n(D)\frac{J^2}{4}\frac{S(S+1)}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-%\end{aligned}\end{equation}
-%This is an \(m-\)independent piece, so it can be summed over to produce an impurity-independent potential scattering term, which we ignore. 
-%
-%The second is the RG equation for the difference of the couplings:
-%\begin{equation}\begin{aligned}
-%	\Delta J^-_m = -n(D)\frac{1}{2}\frac{\left( J^t_{m-1} \right) ^2 - \left(J^t_{m}\right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{4}\frac{n(D) m J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-%\end{aligned}\end{equation}
-%The usual \(J\) Kondo coupling is recovered through \(J = 2J^-_m/m\). Substituting this gives 
-%\begin{equation}\begin{aligned}
-%	\Delta_\text{p sector} J = -\frac{1}{2}n(D)\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-%\end{aligned}\end{equation}
-%
-%We can also obtain the RG equation for \(J\) from the transverse renormalisation:
-%\begin{equation}\begin{aligned}
-%	\Delta J^t_m &= - \frac{n(D)J^t_m \left( J^\downarrow_m + J^\uparrow_{m+1} \right) }{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{2}\frac{n(D)J^t_m J}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-%\end{aligned}\end{equation}
-%Since \(J^t_m \propto J\), we have
-%\begin{equation}\begin{aligned}
-%	\Delta J_\text{p sector} &= -\frac{1}{2}\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-%\end{aligned}\end{equation}
-%The total renormalisation from both particle and hole sectors, at this order, is
-%\begin{equation}\begin{aligned}
-%	\Delta J^{(2)} &= -\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-%\end{aligned}\end{equation}
-%
-%We now come to the third-order renormalisation.
-%Following eq.~\ref{full_ren}, the next order renormalisation is
-%\begin{equation}\begin{aligned}
-%	\label{psector_3rd_ren}
-%	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X~.
-%\end{aligned}\end{equation}
-%The first term will be of the form
-%\begin{equation}\begin{aligned}
-%	\sum_{q,k,l_1} c^\dagger_{q\beta, l_1}c_{k \alpha, l_1}\ket{m_1}\bra{m_2} \frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z} \ket{m_2} c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \bra{m_3}\frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z}\ket{m_3}\bra{m_4}c^\dagger_{k\alpha, l_1}c_{q\beta, l_1}~.
-%\end{aligned}\end{equation}
-%We have not bothered to write all the summations and the couplings correctly, because we will only simplify the denominator here. Evaluating the inner products gives
-%\begin{equation}\begin{aligned}
-%	\sum_{qk,l_1} \frac{\ket{m_1}\bra{m_4}c^\dagger_{q\beta}c_{k \alpha}c^\dagger_{k_1 \sigma_1, l_2}}{\omega_{m_2,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_2}{4}}  \frac{c_{k_2 \sigma_2,l_2}c^\dagger_{k\alpha}c_{q\beta}}{\omega_{m_3,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_3}{4}}~.
-%\end{aligned}\end{equation}
-%We again use \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).
-%\begin{equation}\begin{aligned}
-%	\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}\sum_{qk,l_1} \frac{\hat n_{q\beta}\left(1 - \hat n_{k\alpha}\right)}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2}~.
-%\end{aligned}\end{equation}
-%We define \(\sum_q \hat n_{q\beta} = n(D)\). Performing the sums over \(k\) and \(l_1\) gives
-%\begin{equation}\begin{aligned}
-%	-\frac{1}{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-%\end{aligned}\end{equation}
-%\(\rho\) is the density of states which we have taken to be constant. Reinstating the complete summation and the couplings gives
-%\begin{equation}\begin{aligned}
-%	\label{first_group}
-%	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{2}\lambda_{3}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}~.
-%\end{aligned}\end{equation}
-%There is no sum over \(m_2\) and \(m_3\) because they are constrained by \(m_1\) and \(m_4\) respectively.
-\(\lambda_i\) represent the couplings present at the three interaction vertices.
-\(k_{1,2}\) sum over the momenta, \(\sigma_{1,2}\) sum over the spin indices and \(l_2\) sums over the channels.
-%
-%The second term in eq.~\ref{psector_3rd_ren} can be evaluated in an almost identical fashion. The integral here will be negative of the first term, because of an exchange in the scattering processes.
-%\begin{equation}\begin{aligned}
-%	\label{second_group}
-%	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{3}\lambda_{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}~.
-%\end{aligned}\end{equation}
-%The first group of terms (those that appear in \ref{first_group}) in the particle sector can be represented as \(a|b^\prime|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three connected processes.
-The \(\prime\) on \(b\) indicates that it is the state of the electrons \textit{not being decoupled}.
-The second group of terms (those that appear in \ref{second_group}) are therefore represented as \(a|b|c^\prime\), because in this group, the interaction \(H_X\) between the electrons that are not being decoupled occur at the very end.
-%We will only calculate the terms in the particle sector, the ones in hole sector will be equal to these because of particle-hole symmetry. The full list of terms is: 
-%
-%
-%$z|z^\prime|z\quad$
-%$z|z|z^\prime\quad$
-%$-|z^\prime|+\quad$
-%$-|+|z^\prime\quad$
-%$+|z^\prime|-\quad$
-%$+|-|z^\prime\quad$
-%$ z|+^\prime|z\quad$
-%$z|-^\prime|z\quad$
-%$+|+^\prime|-\quad$
-%$-|+^\prime|+\quad$
-%$z|z|+^\prime\quad$
-%$z|z|-^\prime\quad$
-%$ +|-|+^\prime\quad$
-%$+|-|-^\prime\quad$
-%$-|+|+^\prime\quad$
-%$z|z^\prime|z\quad$
-%$z|z|z^\prime\quad$
-%$-|z^\prime|+\quad$
-%$ -|+|z^\prime\quad$
-%$+|z^\prime|-\quad$
-%$+|-|z^\prime\quad$
-%$z|+^\prime|z\quad$
-%$z|-^\prime|z\quad$
-%$+|+^\prime|-\quad$
-%$-|+^\prime|+\quad$
-%$z|z|+^\prime\quad$
-%$z|z|-^\prime\quad$
-%$+|-|+^\prime\quad$
-%$+|-|-^\prime\quad$
-%$-|+|+^\prime\quad$
-%.
-%
-%The total renormalisation in  \(J^\sigma_m\) is
-%\begin{equation}\begin{aligned}
-%	\Delta J^\sigma_m = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\left[\left( J^t_{m-1} \right)^2 J^\sigma_m + \left( J^t_m \right)^2 J^\sigma_m - \left( J^t_{m-1} \right)^2 J^\sigma_{m-1} - \left(J^t_m\right)^2 J^\sigma_{m+1} \right] = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3 m \sigma~.
-%\end{aligned}\end{equation}
-%Since we had defined \(J^\sigma_m \equiv \frac{1}{2}J m \sigma\), we have \(\Delta J = \frac{2}{m\sigma}\Delta J^\sigma_m\), and we get \(\Delta_\text{p sector} J = \frac{1}{4}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3\).
-%Combining with the hole sector renormalisation, we get
-%\begin{equation}\begin{aligned}
-%	\Delta J^{(3)} = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3~.
-%\end{aligned}\end{equation}
-%The total renormalisation in \(J\) after combining all orders is
-%\begin{equation}\begin{aligned}
-%	\Delta J = -\frac{n(D) J^2}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3~.
-%\end{aligned}\end{equation}
-%
-%\end{widetext}
-%
-%%\bibliography{mscript_mck_supp}
 \end{document}

### 2022-06-27 Ref Response/RefereeResponse.tex
updated referee report and manuscript with sir's edits

@@
 \response{ We are grateful to the referee for this question.
-Indeed, we have used the URG method in the past to compute certain dynamic quantities like the impurity Greens function and spectral functions, both at zero and finite temperatures, for the single-channel Kondo model in an earlier work~\cite{kondo_urg}.
-This was done by working with the fixed point Hamiltonian, without taking the zero bandwidth limit.
+Indeed, we have used the URG method in the past to compute certain dynamic quantities for the single-channel Kondo model in an earlier work~\cite{kondo_urg}, e.g., the impurity Greens function and spectral functions at both zero and finite temperatures.
+This was done by working with the fixed point Hamiltonian obtained from the URG flow (and without taking the zero bandwidth limit).
 The spectral function revealed the expected Abrikosov-Suhl resonance at zero frequency, and satisfied the Friedel sum rule.
-We believe a similar  computation can also be performed to obtain other dynamical quantities like the conductance or the resistance.}
+We believe that computations can also be performed using the complete fixed point Hamiltonian (i.e., not just that of the star graph) in order to obtain other Greens functions that yield dynamical quantities like the conductance or the resistance.
+We propose to develop this in a future work.}
 
@@
 \response{ In the example cited in the question, we used numerical calculations in the sense of solving the star graph Hamiltonian using exact diagonalisation and then using Eq.(19) to obtain the susceptibility.
-In the Supplementary Material~\cite{SM}, in order to obtain the contribution to the susceptibility coming from the non-Fermi liquid, we numerically diagonalise the Hamiltonian formed of the star graph and the single-particle excitations into the conduction bath.}
+In the Supplementary Material~\cite{SM}, in order to obtain the contribution to the susceptibility coming from the non-Fermi liquid, we numerically diagonalise the Hamiltonian formed of the star graph and the single-particle excitations into the conduction bath.
+We have now clarified the methods employed below eq.(18) as well as below Fig.5 in the main manuscript and supplementary materials (above eq.(40)).}
 
@@
 
-\response{
-NEED TO UPADATE THIS
-
-While the RG formalism can be put into a numerical setup by abstracting the RG equations, we believe there is greater utility in sticking to the analytical form because it allows applying the method to a wide variety of systems and multiple geomteries, as can be seen in the references mentioned in the work.
-Moreover, the analytical approach makes it much more easier to obtain fixed point Hamiltonians.}
+\response{We thank the referee for this excellent question.
+In the present work (as well as our earlier work on the single channel Kondo effect~\cite{kondo_urg}), we have emphasised obtaining various measurable thermodynamic and dynamical quantities of the quantum impurity model from the numerical diagonalisation of the fixed point effective Hamiltonian of the URG flow.
+In Ref.\cite{kondo_urg}, we found that this gave reasonably good qualitative agreement with the results obtained from the NRG method (in terms of the asymptotic values and the nature of the crossover).
+However, it is also possible to compute various quantities at several points along the URG flow, in the spirit of the NRG procedure.
+Implementing this would, we believe, take us closer to a technique akin to NRG.
+\par\noindent
+Importantly, given that the URG can be (and has already been) applied to a variety of models across dimensions, this would help overcome the major limitation of NRG in being applicable only to quantum impurity models.
+It will be interesting to see the trade-off between an increase in quantitative accuracy versus the complexity of the numerical implementation.
+This challenge we leave to the future.
+However, it is worth pointing out that we have already adopted the philosophy mentioned above in implementing a momentum-space entanglement renormalisation group (MERG) scheme based on the URG method.
+Indeed, we have applied the MERG to the study of several problems of strongly correlated electrons (e.g., the 2D Hubbard model on the square lattice at and away from $1/2$-filling~\cite{mukherjeeMERG2022}, the single channel Kondo problem~\cite{kondo_urg}, the 1D Hubbard model~\cite{1dhubjhep} and the 2D reduced BCS model~\cite{siddharthacpi}).}
 
@@
 
-\response{We have now tried to address this in the manuscript by elaborating on the specific questions that the referee has brought up in the two points immediately following this.
-A more extensive description of the method will take up more space in this already sizable manuscript.
-We would like to point out that a complete derivation of the formalism and details on the various parts of the method and their implications can be found in Refs.~\cite{anirbanurg1,anirbanurg2} mentioned in the manuscript.}
+\response{We thank the referee for raising this point.
+Given the present length of the work, it will be difficult for us to add substantial material devoted to explaining various features of the URG method in the main manuscript.
+Instead, we have improved Sec.4 of the Supplementary Materials (which contains the detailed derivation of the URG flow equations) to cover this.
+In addition, we have addressed within the main manuscript the specific questions that the referee has brought up in the two points immediately following this one (and which are related to the URG method).
+Finally, we have also pointed the readers towards a complete derivation of the URG formalism in Refs.~\cite{anirbanurg1,anirbanurg2}.
+We earnestly request the referee to kindly bear with us on this.}
 
@@
 
-\response{
-	{\it The unitary operator \(U\) mentioned in Eq.(3) can be thought of as a special case of the most general form \(U = e^\mathcal{S}\) of a unitary operator defined by an anti-Hermitian generator \(\mathcal{S}\).} For our case, the generator turns out to be \(\mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger - \eta \right) \), such that the unitary operator is \(U = e^{\frac{\pi}{4}\left(\eta^\dagger - \eta\right) }\).
-If one then uses the anticommutation and commutation properties of \(\eta,\eta^\dagger\), the exponential can be expanded in its Taylor series and then resummed into the form mentioned in the manuscript.
-
-	{\it With regards to the fermionic operators \(\eta_{(j)},\eta^\dagger_{(j)}\) of Eq.(4), they can be thought of as the many-particle analogue of the single-particle field operators \(c_j,c^\dagger_j\) that change the occupation number of the single-particle Fock space, \(\ket{n_j}\)}.
-The extra prefactors are required to ensure that the decoupling of the specific fock state happens through a unitary modification of the spectrum of the remnant degrees of freedom.
-Since the \(j^\text{th}\) degree of freedom is coupled with the others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\), and this is the reason for the \(\text{Tr}\left(H_(j) c_j\right) \) part.
-The Greens function in front accounts for the dynamical cost of this rotation in terms of the quantum fluctuations \(\hat \omega\) and the kinetic and self energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).
-
-	{\it We have updated the manuscript with these explanations. We are thankful to the referee for these questions.}
+\response{The unitary operator \(U\) mentioned in Eq.(3) can be thought of as a special case of the most general form \(U = e^\mathcal{S}\) of a unitary operator defined by an anti-Hermitian generator \(\mathcal{S}\).
+As shown in detail in Ref.\cite{anirbanurg1}, for our case, the generator turns out to be \(\mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger - \eta \right) \), such that the unitary operator is \(U = e^{\frac{\pi}{4}\left(\eta^\dagger - \eta\right) }\).
+If one then uses the anticommutation and commutation properties of \(\eta,\eta^\dagger\), the exponential can be expanded in a Taylor series and then resummed into the form mentioned in the manuscript.
+\par\noindent
+The fermionic operators \(\eta_{(j)},\eta^\dagger_{(j)}\) of Eq.(4) can be thought of as the many-particle analogue of the single-particle field operators \(c_j,c^\dagger_j\) that change the occupation number of the single-particle Fock space \(\ket{n_j}\).
+The presence of the operators in $\eta_{(j)}$ other than $c_j$ are required to ensure that the decoupling of the specific Fock state under consideration is carried out through a unitary modification of the spectrum of the remnant degrees of freedom.
+Since the \(j^\text{th}\) degree of freedom is coupled with many others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\); this is encoded within the \(\text{Tr}\left(H_{(j)} c_j\right) \) term.
+The Greens function in front of $c_j$ accounts for the dynamical cost of this rotation in terms of an operator for quantum fluctuations (\(\hat \omega\)), as well as the kinetic and self-energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).
+\par\noindent
+We have updated the manuscript with these explanations in Sec.IIA, below eqs.(3), (4) and (5). We are thankful to the referee for these questions.
 }
@@
 \response{
-There are atleast two specific distinctions between the continuous unitary transformations (CUT) RG as envisaged by Wegner (and others before him) and the URG of the present work.
+There are atleast two specific distinctions between the continuous unitary transformations (CUT) RG as envisaged by Wegner and the URG of the present work.
 \begin{itemize}
 	\item While most RG methods that apply successive unitary transformations rely on a gradual decrease in the off-diagonal content of the Hamiltonian, the URG proceeds by decoupling each discrete Fock space node at a time.
-In other words, in the URG, at least one term in the Hamiltonian vanishes at each RG step, while in the CUT RG, there is a gradual decay of the off-diagonal terms in order to make it more band diagonal.
-	\item The CUT RG, specifically, has to be applied by choosing a truncation scheme that allows closing the RG equations.
-The URG, on the other hand, is able to ``resum" the coupling expansion series through the denominator structure and the quantum fluctuation operator.
+In other words, the URG achieves a block-diagonalisation of the Hamiltonian at each RG step, while the CUT RG involves a gradual decay of the off-diagonal terms of the Hamiltonian in order to make it more band diagonal.
+	\item The CUT RG involves choosing a truncation scheme that allows closing the RG equations.
+The URG, on the other hand, is able to resum the coupling expansion series through the denominator structure and the quantum fluctuation operator.
 \end{itemize}
@@
 \response{We thank the referee for the question.
-The symbol \(\ket{j}\) is used to label the most energetic state {\it at a particular RG step} of the entire process.
-In more conventional language, it is simply the collection of states at the running cutoff \(\Lambda\) (bandwidth) of the field theory.
-As the RG proceeds, this bandwidth shrinks, so \(\ket{j}\) flows to lower and lower energies, until it hits the Fermi surface (assuming the RG has not reached a fixed point by then).
+At a particular RG step, the symbol \(\ket{j}\) is used to label the collection of the most energetic single particle Fock states of the bath in momentum-space that can be accessed from the ground state by virtual quantum fluctuations (and which are resolved by the decoupling procedure).
+In more conventional language, this collection of states lies at the running cutoff \(\Lambda\) (bandwidth) of the field theory.
+The bandwidth shrinks as the RG proceeds, and \(\ket{j}\) is updated to states at lower energies until it hits the Fermi surface (assuming the RG has not reached a fixed point by then).
 }
@@
 
-\response{ Indeed, we meant ``anisotropy" instead of isotropy. We thank the referee for pointing this out.}
+\response{ Indeed, we meant ``anisotropy" instead of isotropy. We have thus rectified the mistake. We thank the referee for pointing this out.}
 
@@
 
-\response{ We have rectified this in the manuscript.}
+\response{We thank the referee for pointing this out, and have rectified the mistake in the manuscript.}
 
@@
 
-\response{We have rectified the issue with the spin label \(\alpha^\prime\).
-With regards to the two momentum summations \(k,k^\prime\) in the expressions of \(\vec S\) in and below Eq.(8), both the summations are required.
-This expression for the spin operator can be found in several textbooks like ~\cite{coleman2015,hewson1993}, and can be obtained by Fourier transforming the local spin operator \(\sum_{\alpha\alpha^\prime}\vec \sigma_{\alpha\alpha^\prime}c^\dagger_{\alpha}c_{\alpha^\prime}\) formed by the conduction electrons \(c_{\alpha},c_{\alpha^\prime}\) at the origin.}
-
+\response{We have rectified the issue with the spin label \(\alpha^\prime\) label.
+With regards to the two momentum summations \(k,k^\prime\) in the expressions of \(\vec S\) in and below Eq.(8), both the summations are indeed required.
+This is because the expression for the spin operator in eq.(8) can be obtained by Fourier transforming the real-space local spin operator \(\sum_{\alpha\alpha^\prime}\vec \sigma_{\alpha\alpha^\prime}c^\dagger_{\alpha}c_{\alpha^\prime}\) formed by the conduction electrons \(c_{\alpha},c_{\alpha^\prime}\) at the origin.
+The Fourier transformation involves two $k$-space sums (one for each real-space operators).}
 \point{
@@
 
-\response{ We have updated the plot with the correct legend. We are grateful to the referee for pointing this out.}
+\response{We have updated the plot with the correct legend. We are grateful to the referee for pointing this out.}
 
@@
 
-\response{We had used the term critical to reflect the fact that the \(1/T\) divergence was a result of the remnant degeneracy of the system at the fixed point.
-In order to avoid confusion, we have removed the usage of critical in this context from the manuscript.}
+\response{We had (incorrectly) used the term critical to reflect the fact that the \(1/T\) divergence was a result of the remnant degeneracy of the system at the fixed point (reflecting an unscreened moment).
+In order to avoid any confusion on this point, we have removed the usage of the word ``critical" in this context from all places in the manuscript.}
 
@@
 
-\response{We believe the referee is referring to Eq.(18) here, not Eq.(8).
-The expression in Eq.(18) was derived for the specific case of $S_d = 1/2$ (spin-half impurity), hence it only vanishes at $K=2S_d=1$.
-The more general case of spin-\(S_d\) impurity was checked numerically, and reported in Fig.(4).}
+\response{We believe the referee is referring to Eq.(18) here, and not Eq.(8).
+The expression in Eq.(18) was derived for the specific case of $S_d = 1/2$ (spin-half impurity), and hence it only vanishes at $K=2S_d=1$.
+while we do not have an analytic expression of this at present for the case $K=2S_{d}$, we have checked numerically that this is indeed the case.
+This is reported in Fig.(4).}
 
@@
 
-\response{ We thank the referee for allowing us to clarify this.
-We used the term “non-Fermi liquid” to reflect the fact that, in the RG sense, the low energy $k−$space Hamiltonian was not purely of an $F_{kk^\prime} n_k n_{k^\prime}$ density-density type interaction term (which is characteristic of a Fermi liquid).}
+\response{ We thank the referee for seeking a clarification on this point.
+We used the term “non-Fermi liquid” to reflect the fact that, in the RG sense, the low energy $k−$space Hamiltonian was not purely of an $F_{kk^\prime} n_k n_{k^\prime}$ density-density type interaction term (which is characteristic of a Fermi liquid).
+Indeed, the off-diagonal terms in the effective Hamiltonian obtained in eq.(44) is shown to involve a dominant contribution corresponding to an effective Marginal Fermi liquid effective Hamiltonian (eq.(49), involving a $n_{k\sigma} n_{k^{\prime}\uparrow}(1-n_{k^{\prime}\downarrow})$ interaction term, and as shown in an earlier work by us on the 2D Hubbard model~\cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2}).}
 
@@
 \response{We thank the referee for this question.
-On application of the renormalization group transformations towards the fixed point, there is a reduction in the effective bandwidth of the problem, leading to reduced excitations into the conduction band.
-This enables us to take the zero bandwidth approximation and study the emergent star graph as a "skeletal" problem for the low-energy physics.
-Such a trick reveals, for instance, the ground state of the multichannel problem and the degeneracy.
-Moreover, it allows studying the effects of excitations, as demonstrated by the identification of the non-Fermi liquid component, more specifically a local marginal Fermi liquid.
+Upon flowing from the weakly coupled theory to the fixed point under the renormalization group transformations, there is a reduction in the effective bandwidth of the problem (leading to reduced excitations into the conduction band) together with a growth in the effective Kondo coupling.
+This involves a growth in the ratio of the Kondo coupling to the bandwidth of the conduction band, and enables a study of the emergent star graph (obtained from a zero bandwidth approximation) as a ``skeletal" problem for the low-energy physics.
+Such an approach reveals, for instance, the ground state of the multichannel problem and the degeneracy.
+Moreover, it allows studying the effects of excitations (from a calculation in the spirit of Nozieres' calculation for the single channel Kondo problem), as demonstrated by the identification of its local non-Fermi liquid nature.
 }
@@
 \point{
-Regarding computation of the perturbative RG flow, the perturbative
-calculation of the beta function doesn’t really need any new
-technology (like URD) and it has been done by drawing Feynman diagrams
-in all those papers that are cited. Derivation of the effective fixed
+Derivation of the effective fixed
 point Hamiltonian, cannot be trusted since there is no argument that
@@
 \response{
-The URG is able to ``resum" all orders of couplings through the non-perturbative denominator structure of the RG equation and the quantum fluctuation scale \(\omega\).
-This ensures that the fixed point Hamiltonians obtained from URG indeed account for the effects of the UV on the IR and are stable in the RG sense.
+We respectfully disagree with the referee on this point.
+As shown by us in Ref.\cite{anirbanurg1} in detail, the URG involves a resummation to all orders of renormalisations in various couplings.
+This is revealed by the non-perturbative structure of the URG equation.
+This ensures that the fixed point Hamiltonians obtained from URG indeed account for the effects of the UV on the IR, and are stable under renormalised perturbation theory (in the RG sense).
+This has been demonstrated by us in application of the URG to a variety of problems involving correlated electrons (included in the list of references in the main manuscript).
+Furthermore, in a recently published work of ours on the single channel Kondo problem~\cite{kondo_urg}, we have compared the results for several thermodynamic and dynamical measurables obtained from the URG against that obtained from methods such as NRG, and obtained very good agreement.
 }
@@
 \response{
-We believe that the following are new and interesting additions to the knowledge of multichannel Kondo physics that are obtained from our work:
+Again, we respectfully disagree with the referee.
+We believe that the following results are new and interesting additions to the knowledge of multichannel Kondo physics that are obtained from our work:
 \begin{itemize}
@@
 The observation of the Mott liquid is particularly significant because it highlights a common theme that pervades much of fermionic quantum matter - the role of zero modes in determining the infrared physics.
-This can be seen in the emergence of a Mott liquid from the 2D Hubbard model as seen from a URG analysis~\cite{anirbanmott1,anirbanmott2,mukherjeeMERG2022}, the emergence of a cooper pair insulator from the reduced BCS Hamiltonian~\cite{siddharthacpi} and the emergence of an effective Heisenberg model in the 1D Hubbard model~\cite{1dhubjhep}.
+This can be seen, for instance, in the emergence of a Mott liquid from the 2D Hubbard model as seen from a URG analysis~\cite{anirbanmott1,anirbanmott2,mukherjeeMERG2022} and a Cooper pair insulator from the reduced 2D BCS Hamiltonian~\cite{siddharthacpi}.
+Importantly, we have also corroborated several of our analytic and numerical results with those that exist in the literature.
 }

### 2022-06-27 manuscript/mscript_mck_full.tex
updated referee report and manuscript with sir's edits

@@
 The degree of compensation is simply the average correlation between the impurity spin and the conduction channel local spins; it is found to be maximum at exact screening, and decreases for both over- and under-screening.
-The magnetisation and susceptibility of the star graph model show {\color{red}critical behaviour in the form} a discontinuity and a \(T^{-1}\) divergence.
+The magnetisation and susceptibility of the star graph model show {\color{red}critical behaviour in the form} a discontinuity and a \(T^{-1}\) divergence respectively.
 We also explore the topological properties of the degenerate ground state manifold of the star graph model using non-local twist and translation operators.
@@
 where \(\left\{\cdot\right\}\) is the anticommutator.
-{\color{blue}The unitary operator \(U_{(j)}\) mentioned in Eq.~\eqref{unitary} can be thought of as a special case of the most general form \(U = e^\mathcal{S}\) of a unitary operator defined by an anti-Hermitian generator \(\mathcal{S}\).
-For our case, the generator turns out to be \(\mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right) \), such that the unitary operator is \(U_{(j)} = e^{\frac{\pi}{4}\left(\eta^\dagger_{(j)} - \eta_{(j)}\right) }\).
+{\color{blue} Further, $\left[ \eta_{(j)},\eta_{(j)}^\dagger \right] = 2\hat n_{j}-1$.
+The unitary operator \(U_{(j)}\) mentioned in Eq.~\eqref{unitary} can be thought of as a special case of the most general form \(U = e^\mathcal{S}\) of a unitary operator defined by an anti-Hermitian generator \(\mathcal{S}\).
+For our case, the generator turns out to be \(\mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right) \), such that the unitary operator is \(U_{(j)} = e^{\frac{\pi}{4}\left(\eta^\dagger_{(j)} - \eta_{(j)}\right) }\)~\cite{anirbanurg1}.
 If one then uses the anti-commutation and commutation properties of \(\eta_{(j)},\eta^\dagger_{(j)}\)~\cite{anirbanurg1,anirbanurg2}, the exponential can be expanded in its Taylor series and then "resummed" into the form in Eq.~\eqref{unitary}.}
@@
 {\color{blue}The operators \(\eta_{(j)},\eta^\dagger_{(j)}\) can be thought of as the many-particle analogue of the single-particle field operators \(c_j,c^\dagger_j\) that change the occupation number of the single-particle Fock space, \(\ket{n_j}\).
-The extra prefactors are required to ensure that the decoupling of the specific Fock state happens through a unitary modification of the spectrum of the remnant degrees of freedom.
-Since the \(j^\text{th}\) degree of freedom is coupled with the others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\), and this is the reason for the \(\text{Tr}\left(H_(j) c_j\right) \) part.}
+The presence of the operators in $\eta_{(j)}$ other than $c_j$ are required to ensure that the decoupling of the specific Fock state under consideration is carried out through a unitary modification of the spectrum of the remnant degrees of freedom.
+Since the \(j^\text{th}\) degree of freedom is coupled with many others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\); this is encoded within the \(\text{Tr}\left(H_{(j)} c_j\right) \) term.}
 The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms in the Hamiltonian:
@@
 The RG flow continues till a fixed point is reached at an energy \(D^*\).
-{\color{blue}The Greens function in front accounts for the dynamical cost of this rotation in terms of the quantum fluctuations \(\hat \omega\) and the kinetic and self energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).}
-
-{\color{blue}There exist other renormalisation group schemes that depend on canonical transformations, like the continuous unitary transformations (CUT) RG as envisaged by Wegner (and others before him).
-There are at least two specific distinctions between the CUT RG and the URG of the present work.
+{\color{blue} The Greens function in front of $c_j$ accounts for the dynamical cost of this rotation in terms of an operator for quantum fluctuations (\(\hat \omega\)), as well as the kinetic and self-energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).}
+
+{\color{blue}There exist other renormalisation group schemes that depend on canonical transformations, such as Wegner's continuous unitary transformations (CUT) RG (PUT IN REFERENCE) and the similarity RG method by Glaszek and Wilson (PUT IN REFERENCE).
+There are at least two specific distinctions between the CUT RG and the URG method adopted in the present work.
 \begin{itemize}
 	\item While most RG methods that apply successive unitary transformations rely on a gradual decrease in the off-diagonal content of the Hamiltonian, the URG proceeds by decoupling each discrete Fock space node at a time.
-In other words, in the URG, at least one term in the Hamiltonian vanishes at each RG step, while in the CUT RG, there is a gradual decay of the off-diagonal terms in order to make it more band diagonal.
-	\item The CUT RG, specifically, has to be applied by choosing a truncation scheme that allows closing the RG equations.
-The URG, on the other hand, is able to ``resum" the coupling expansion series through the denominator structure and the quantum fluctuation operator.
+In other words, the URG achieves a block-diagonalisation of the Hamiltonian at each RG step, while the CUT RG involves a gradual decay of the off-diagonal terms of the Hamiltonian in order to make it more band diagonal.
+	\item The CUT RG involves choosing a truncation scheme that allows closing the RG equations.
+The URG, on the other hand, is able to resum the coupling expansion series through the denominator structure and the quantum fluctuation operator.
 \end{itemize}
+Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~\cite{anirbanmott1,anirbanurg1}.
 }
@@
 There, the susceptibility becomes constant at low temperatures: \(\chi(T\to 0) = \frac{W}{4 T_K}\), \(T_K\) being the single-channel Kondo temperature and \(W\) the Wilson number \cite{wilson1975renormalization,nozieres1974fermi,bullaNRGreview,kondo_urg}.}
-We have checked the case of general spin-\(S_{d}\) impurity (fig.~\ref{fig:suseptibility_impurity}) by {\color{blue}numerically diagonalising the star graph}, and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
+We have checked the case of general spin-\(S_{d}\) impurity (fig.~\ref{fig:suseptibility_impurity}) by {\color{blue}numerically diagonalising the star graph Hamiltonian}, and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
 A similar divergence is also seen in the susceptibility of the outer spins, calculated by inserting a magnetic field purely on the outer spins.
@@
 This available space for scattering is simply the frustration that we discussed earlier.
-Indeed, we have checked (see fig.~\ref{mag_crit}) {\color{blue} by diagonalising the star graph numerically} that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S_{d}\) is the deviation from exact screening.
+Indeed, we have checked (see fig.~\ref{mag_crit}) {\color{blue} by diagonalising numerically the star graph Hamiltonian} that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S_{d}\) is the deviation from exact screening.
 Some additional results are presented in the Supplementary Materials~\cite{SM}.

### 2022-06-28 manuscript/Supplementary/supplementary_mck.tex
added latest manuscript files
updated supplementary

--- 2022-04-26 Manuscript26April2022/supplementary_mck.tex
@@
 
-\title{Supplementary Materials for ``Frustration shapes multi-channel Kondo physics: A star graph perspective"}
+\title{Supplementary Materials for ``Frustration shapes multi-channel Kondo physics: a star graph perspective"}
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{plt/QuantumEnergyperchannel}
+\includegraphics[width=0.7\textwidth]{QuantumEnergyperchannel}
 \caption{This shows the variation of quantum energy per channel with $1/N$, where $N=N_{ch}+1$ is the total number of spins in the systems including the impurity spins.}
@@
 \begin{figure}
-\includegraphics[width=0.7\textwidth]{plt/Staggeredmag50.png}
+\includegraphics[width=0.7\textwidth]{Staggeredmag50.png}
 \caption{This shows how the staggered magnetization changes with the number of channels $N_{ch}$.}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{plt/ThermalEntanglementVSLogTemperature}
+\includegraphics[width=0.7\textwidth]{ThermalEntanglementVSLogTemperature}
 \caption{This shows the variation of thermal entropy with the temperature.}
@@
 \section{Additional Topological Features of the Local Mott liquid}
+{\color{blue}\subsection{Non-local twist operators and ground state degeneracy}}
 
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{plt/stargraph-to-alltoall.png}
+	\includegraphics[width=0.8\textwidth]{stargraphtoalltoall.png}
 	\caption{(a) Schematic diagram of $8-$channel multichannel Kondo model zero mode in zero bandwidth limit.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{plt/FINALfittedCvt0p1.png}
-\caption{This figure shows the variation of the impurity specific heat with the temperature.}
+\includegraphics[width=0.49\textwidth]{FINALfittedCvt0p1.png}
+\includegraphics[width=0.49\textwidth]{NFLChilog0p1}
+\caption{Anomalous contribution to the impurity specfic heat (left) and the maginetic susceptibility (right) arising from the non-Fermi liquid component}
 \label{fig:Cv_imp}
 \end{figure}
-Using the self-energy obtained above, we extract the low-temperature behaviour of the impurity specific heat in the two-channel model for $t=0.1$ and $\mathcal{J}=1$, and it is shown in fig,~\ref{fig:Cv_imp}.
+Using the self-energy obtained above, we extract the low-temperature behaviour of the impurity specific heat in the two-channel model for $t=0.1$ and $\mathcal{J}=1$, and it is shown in the left panel of fig.~\ref{fig:Cv_imp}.
 We find that at low-temperatures, the Sommerfeld coefficient \(C_\text{imp}/T\) follows a logarithmic behaviour for the two-channel case, which is in agreement with the results known in the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,
@@
 \end{eqnarray}
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.7\textwidth]{plt/NFLChilog0p1}
-\caption{Susceptibility}
-\label{fig:NFL_susecptibility}
-\end{figure}
-The result is shown in fig.~\ref{fig:NFL_susecptibility}, and we find that at low temperatures, the susceptibility has a logarithmic behaviour.
+The result is shown in the right panel of fig.~\ref{fig:Cv_imp}, and we find that at low temperatures, the susceptibility has a logarithmic behaviour.
 \begin{eqnarray}
@@
 \label{appendix_urg}
+{\color{blue}
+\subsection{Details of the URG method}
+
+The non-trivial nature of the impurity problem arises from the fact that the many-particle correlation between the impurity spin and the conduction electron induces a many-particle interaction between the conduction electron states.
+This means that within the conduction band, the states at high and low energies get entangled with each other, leading to what is called UV-IR mixing.
+One of the methods of obtaining the low-energy physics while taking into account the effect of the high energy degrees of freedom is the renormalisation group (RG) approach.
+The specific variant of RG used in this work is the unitary renormalisation group (URG) method developed by some of us in Refs.~\cite{santanukagome,anirbanmott1,anirbanmott2,1dhubjhep,siddharthacpi,mukherjeeMERG2022,kondo_urg}.
+The URG proceeds by applying unitary transformations on the Hamiltonian in order to decouple the high-energy \(k-\)states, leading to a reduction in the effective bandwidth and changes in the couplings for the low-energy degrees of freedom in the process.
+This leads to a sequence of renormalised Hamiltonians, and hence the coupling RG equations.
+While this is similar in spirit to the Poor Man's scaling approach of Anderson as applied to the single channel Kondo model~\cite{anderson1970}, there are several differences between the methods that will be apparent when we describe the method in more detail below.
+
+We start by defining a UV-IR scheme for the single-particle electronic states \(\vec k = (k_F + |\vec k|) \hat k\).
+We label the single-particle \(\vec k-\)states in terms of their normal distance $\Lambda = |\vec k|$ from the Fermi surface (FS) and the orientation of the unit vectors $\hat{s} = \hat k$, where $\hat{s}=\frac{\nabla\epsilon_{\mathbf{k}}}{|\nabla\epsilon_{\mathbf{k}}|}|_{\epsilon_{\mathbf{k}}=E_{F}}$.
+Each \(\hat s\) represents a direction that is normal to the FS.
+Combining these two labels with the spin index \(\sigma=\uparrow,\downarrow\), each single-particle state can be uniquely labelled as $\ket{j,l} = \ket{(k_F + \Lambda_j) \hat s,\sigma}, l\equiv (\hat{s},\sigma)$.
+The $\Lambda$'s are arranged as follows: $\Lambda_{N}>\Lambda_{N-1}>\ldots>0$, such that \(\Lambda_N\) is farthest from the Fermi surface and is hence the most energetic (UV) while \(\Lambda_0\) is closest to the Fermi surface and is least energetic (IR).
+The URG proceeds by disentangling these states \(\Lambda_j\), starting from those near the UV and gradually scaling towards the IR.
+This leads to the Hamiltonian flow equation~\cite{anirbanurg1}
+\begin{equation}
+\centering
+\label{urg_map}
+H_{(j-1)}=U_{(j)}H_{(j)}U^{\dagger}_{(j)}~,
+\end{equation}
+where the unitary operation $U_{(j)}$ is the unitary map at RG step $j$. 
+$U_{(j)}$ disentangles all the electronic states 
+$|\mathbf{k}_{\Lambda_{j}\hat{s}_{m}},\sigma\rangle$
+on the isogeometric curve and has the form~\cite{anirbanmott1,anirbanurg1}
+\begin{equation}
+\centering U_{(j)}=\prod_{l}U_{j,l}, U_{j,l}=\frac{1}{\sqrt{2}}\sum_l [1+\eta_{j,l}-\eta^{\dagger}_{j,l}]~,
+\end{equation}
+where \(l\) sums over the states on the isoenergetic shell at distance \(\Lambda_j\), and $\eta_{j,l}$ are electron-hole transition operators following the algebra
+\begin{equation}
+	\left\{\eta_{j,l},\eta_{j,l}^{\dagger}\right\} = 1~,~\left[\eta_{j,l},\eta_{j,l}^{\dagger}\right] = 2\hat n_{j,l} - 1~.
+\end{equation}
+The transition operator can be expressed in terms of the off-diagonal part of the Hamiltonian, \(H^X_{j,l} = Tr_{j,l}(c^{\dagger}_{j,l}H_{j})c_{j,l} + \text{h.c.}\), and the diagonal part \(H^D_{j,l}\) (kinetic energy and self-energies):
+\begin{eqnarray}
+	\eta_{j,l}&=&Tr_{j,l}(c^{\dagger}_{j,l}H_{j,l})c_{j,l}\frac{1}{\hat{\omega}_{j,l}-Tr_{j,l}(H^{D}_{j,l}\hat{n}_{j,l})\hat{n}_{j,l}}~.~~\label{e-TransOp}
+\end{eqnarray}
+The off-diagonal operator \(Tr_{j,l}(c^{\dagger}_{j,l}H_{j,l})c_{j,l}\) in the numerator of \(\eta_{j,l}\) contains all possible scattering vertices that  change the configuration of the Fock state \(\ket{j,l}\)~\cite{anirbanurg1}.
+The generic forms of $H^{D}_{j,l}$ and $H^{X}_{j,l}$ are as follows
+\begin{equation}\begin{aligned}
+H^{D}_{j,l}=&\sum_{\Lambda\hat{s},\sigma}\epsilon^{j,l}\hat{n}_{\mathbf{k}_{\Lambda\hat{s}},\sigma}+\sum_{\alpha}\Gamma_{\alpha}^{4,(j,l)}\hat{n}_{\mathbf{k}\sigma}\hat{n}_{\mathbf{k}'\sigma'} +\sum_{\beta}\Gamma_{\beta}^{8,(j,l)}\hat{n}_{\mathbf{k}\sigma}\hat{n}_{\mathbf{k}'\sigma'}(1-\hat{n}_{\mathbf{k}''\sigma''})+\ldots~,\\
+H^{X}_{j,l}=&\sum_{\alpha}\Gamma_{\alpha}^{2}c^{\dagger}_{\mathbf{k}\sigma}c_{\mathbf{k}'\sigma'}+\sum_{\beta}\Gamma_{\beta}^{2}c^{\dagger}_{\mathbf{k}\sigma}c^{\dagger}_{\mathbf{k}'\sigma'}c_{\mathbf{k}_{1}'\sigma_{1}'}c_{\mathbf{k}_{1}\sigma_{1}}+\ldots~.
+\end{aligned}\end{equation}
+The indices \(\alpha\) and \(\beta\) are strings that denote the quantum numbers of the incoming and outgoing electronic states at a particular interaction vertex \(\Gamma^n_{\alpha}\) or  \(\Gamma^m_{\beta}\).
+The operator $\hat{\omega}_{j,l}$ accounts for the quantum fluctuations arising from the non-commutation between different parts of the renormalised Hamiltonian and has the following form~\cite{anirbanurg1}
+\begin{eqnarray}
+\hat{\omega}_{j,l}&=&H^{D}_{j,l}+H^{X}_{j,l}-H^{X}_{j,l-1}~.\label{qfOp}
+\end{eqnarray}
+Upon disentangling electronic states $\hat{s},\sigma$ along a isogeometric curve at distance $\Lambda_{j}$, the following effective Hamiltonian $H_{j,l}$ is generated 
+\begin{eqnarray}
+H_{j,l}=\prod_{m=1}^{l}U_{j,m}H_{(j)}[\prod_{m=1}^{l}U_{j,m}]^{\dagger}~.
+\end{eqnarray}
+
+Accounting for only the leading tangential scattering processes, as well as other momentum transfer processes along the normal direction $\hat{s}$, the renormalised Hamiltonian \(H_{(j-1)}\) has the form~\cite{anirbanurg1}
+\begin{equation}
+\hspace*{-0.1cm}Tr_{j,(1,\ldots,2n_{j})}(H_{(j)})+\sum_{l=1}^{2n_{j}}\lbrace c^{\dagger}_{j,l}Tr_{j,l}(H_{(j)}c_{j,l}),\eta_{j,l}\rbrace\tau_{j,l}~.\label{HRG}
+\end{equation}
+The RG fixed point is reached when the denominator in Eq.~\ref{e-TransOp} vanishes, at a certain energy scale \(\Lambda^*\).
+The vanishing of the denominator can be shown to be concomitant with the vanishing of the off-diagonal component \(H^X\)~\cite{anirbanurg1}, and the fixed point value of the quantum fluctuation operator is equal to one of the eigenvalues of the Hamiltonian.
+The fixed point Hamiltonian \(H^*\) consists of the renormalised, still-entangled degrees of freedom \(\Lambda_j\) that lie inside the window \(\Lambda^*\): \(\Lambda_j < \Lambda^*\), as well as the integrals of motion (IOMs) that were decoupled by the URG transformations along the way.
+The IOMs have been stripped of any number fluctuations and are therefore diagonal in the basis of the number operators for each of the decoupled degrees of freedom.
+\begin{equation}\begin{aligned}
+	H^* = \sum_{\Lambda_j < \Lambda^*} H^*(\Lambda_j) + \sum_{\Lambda_j > \Lambda^*}H_\text{IOMs}(\Lambda_j)
+\end{aligned}\end{equation}
+The effective Hamiltonian can be used to construct the corresponding thermal density matrix and hence the partition function at a temperature \(T\):
+\begin{equation}
+Z^* = \mathrm{Tr}\left[ \hat{\rho}^*\right] = \mathrm{Tr}\left[ e^{-\beta \hat{H}^{*}}\right] = \mathrm{Tr}\left[ U^{\dagger} e^{-\beta \hat{H}^{*}} U\right] = \mathrm{Tr}\left[ e^{-\beta \hat{H}}\right] = Z
+\label{partfunc}~,
+\end{equation}
+where \(\beta = 1/k_B T\), \(U = \prod_{1}^{j^{*}}U_{(j)}\), $H$ is the bare Hamiltonian and $j^{*}$ is the RG step at which the IR stable fixed point is reached.
+The unitary transformations preserve the partition function along the RG flow.
+}
+
+\subsection{Derivation of RG equation for the MCK model}
+
 The Hamiltonian for the channel-isotropic MCK model is:
 \begin{gather}
-	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\beta= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~.
+	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\alpha^\prime= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~.
 \end{gather}
-As mentioned in the same section, the Hamiltonian \(H_{(j-1)}\) of the \((j-1)^\text{th}\) RG step is obtained from the Hamiltonian \(H_{(j)}\) of the preceding RG step by applying a unitary transformation \(U_{(j)}\): \(H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}\).
-The unitary transformation is obtained in terms of the fermionic operator \(\eta_{(j)}\):
-\begin{gather}
-	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ ~\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)},~T_{(j)} \equiv \text{Tr}\left(H_{(j)}c_{j}\right)~,~ ~\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} T_{(j)}~.
-\end{gather}
-The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms of the Hamiltonian.
 
@@
 
-\bibliography{mscript_mck_full}
+\bibliography{../mscript_mck_full}
 \end{document}

### 2022-06-29 Ref Response/RefereeResponse.tex
finalised sir's changes

@@
 Given the present length of the work, it will be difficult for us to add substantial material devoted to explaining various features of the URG method in the main manuscript.
-Instead, we have improved Sec.4 of the Supplementary Materials (which contains the detailed derivation of the URG flow equations) to cover this.
+Instead, we have improved Sec.
+4 of the Supplementary Materials (which contains the detailed derivation of the URG flow equations) to cover this: a new subsection (4A) now includes a detailed discussion of the method.
 In addition, we have addressed within the main manuscript the specific questions that the referee has brought up in the two points immediately following this one (and which are related to the URG method).
@@
 This involves a growth in the ratio of the Kondo coupling to the bandwidth of the conduction band, and enables a study of the emergent star graph (obtained from a zero bandwidth approximation) as a ``skeletal" problem for the low-energy physics.
-Such an approach reveals, for instance, the ground state of the multichannel problem and the degeneracy.
-Moreover, it allows studying the effects of excitations (from a calculation in the spirit of Nozieres' calculation for the single channel Kondo problem), as demonstrated by the identification of its local non-Fermi liquid nature.
+Such an approach reveals, for instance, the ground state of the multichannel problem and the degeneracy (Sec.III of the main manuscript).
+Moreover, it allows studying the effects of excitations (from a calculation in the spirit of Nozieres' calculation for the single channel Kondo problem), as demonstrated by the identification of its local non-Fermi liquid nature (Sec.IV and V of the main manuscript and parts of the Supplementary Materials).
 }

### 2022-06-29 manuscript/mscript_mck_full.tex
finalised sir's changes

@@
 
-{\color{blue}There exist other renormalisation group schemes that depend on canonical transformations, such as Wegner's continuous unitary transformations (CUT) RG (PUT IN REFERENCE) and the similarity RG method by Glaszek and Wilson (PUT IN REFERENCE).
+{\color{blue}There exist other renormalisation group schemes that depend on canonical transformations, such as Wegner's continuous unitary transformations (CUT) RG~\cite{wegner1994flow} and the similarity RG method by Glazek and Wilson~\cite{glazek1993renormalization}.
 There are at least two specific distinctions between the CUT RG and the URG method adopted in the present work.
@@
 The \(\chi\) is seen to diverge as \(T^{-1}\) at low temperatures.
-{\color{red}Such a non-analyticity in a response function is a signature of the critical nature of the Hamiltonian.
-This is in contrast to the behaviour in the non-critical exactly-screened fixed point where the ground state is unique.
-There, the susceptibility becomes constant at low temperatures: \(\chi(T\to 0) = \frac{W}{4 T_K}\), \(T_K\) being the single-channel Kondo temperature and \(W\) the Wilson number \cite{wilson1975renormalization,nozieres1974fermi,bullaNRGreview,kondo_urg}.}
+Such a non-analyticity in a response function is {\color{red}a signature of the critical nature of the Hamiltonian.
+This is} in contrast to the behaviour in the {\color{red}non-critical} exactly-screened fixed point where the ground state is unique.
+There, the susceptibility becomes constant at low temperatures: \(\chi(T\to 0) = \frac{W}{4 T_K}\), \(T_K\) being the single-channel Kondo temperature and \(W\) the Wilson number \cite{wilson1975renormalization,nozieres1974fermi,bullaNRGreview,kondo_urg}.
 We have checked the case of general spin-\(S_{d}\) impurity (fig.~\ref{fig:suseptibility_impurity}) by {\color{blue}numerically diagonalising the star graph Hamiltonian}, and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.

### 2022-06-30 Ref Response/RefereeResponse.tex
Spa's changes

@@
 \begin{itemize}
-	\item importance of the role of degeneracy and quantum-mechanical frustration in shaping the infrared physics of the MCK, specifically in the non-Fermi liquid behaviour, the thermodynamic properties, the orthogonality catastrophe, the breakdown of screening and in the strong-weak duality,
+	\item importance of the role of degeneracy and quantum-mechanical frustration in shaping the infrared physics of the MCK, specifically in the absence of any Fermi liquid component and the emergence of non-Fermi liquid behaviour, the thermodynamic properties, the orthogonality catastrophe, the breakdown of screening and in the strong-weak duality,
 	\item derivation of a marginal Fermi liquid effective Hamiltonian for the non-Fermi liquid fixed point, hence revealing the microscopic source of the non-Fermi liquid behaviour in the overscreened regime,
@@
 \begin{itemize}
-	\item Updated an arxiv preprint reference to journal
-	\item Modified acknowledgments
+	\item Included two new references on the CUT and similarity RG methods (Refs.75 and 76 respectively),
+	\item Updated Ref.106 (Ref.104 of the previous manuscript) from the arxiv preprint reference to the published journal reference,
+	\item Modified the acknowledgments to thank all three referees for their helpful comments.
 \end{itemize}

### 2022-06-30 manuscript/Supplementary/supplementary_mck.tex
Spa's changes

@@
 
-The non-trivial nature of the impurity problem arises from the fact that the many-particle correlation between the impurity spin and the conduction electron induces a many-particle interaction between the conduction electron states.
+The non-trivial nature of the impurity problem arises from the fact that the many-particle correlation between the impurity spin and the conduction electrons induces a many-particle interaction among the conduction electron states.
 This means that within the conduction band, the states at high and low energies get entangled with each other, leading to what is called UV-IR mixing.
@@
 \begin{equation}\begin{aligned}
-H^{D}_{j,l}=&\sum_{\Lambda\hat{s},\sigma}\epsilon^{j,l}\hat{n}_{\mathbf{k}_{\Lambda\hat{s}},\sigma}+\sum_{\alpha}\Gamma_{\alpha}^{4,(j,l)}\hat{n}_{\mathbf{k}\sigma}\hat{n}_{\mathbf{k}'\sigma'} +\sum_{\beta}\Gamma_{\beta}^{8,(j,l)}\hat{n}_{\mathbf{k}\sigma}\hat{n}_{\mathbf{k}'\sigma'}(1-\hat{n}_{\mathbf{k}''\sigma''})+\ldots~,\\
-H^{X}_{j,l}=&\sum_{\alpha}\Gamma_{\alpha}^{2}c^{\dagger}_{\mathbf{k}\sigma}c_{\mathbf{k}'\sigma'}+\sum_{\beta}\Gamma_{\beta}^{2}c^{\dagger}_{\mathbf{k}\sigma}c^{\dagger}_{\mathbf{k}'\sigma'}c_{\mathbf{k}_{1}'\sigma_{1}'}c_{\mathbf{k}_{1}\sigma_{1}}+\ldots~.
+H^{D}_{j,l}=&\sum_{\Lambda\hat{s},\sigma}\epsilon^{j,l}\hat{n}_{\mathbf{k}_{\Lambda\hat{s}},\sigma}+\sum_{\alpha}\Gamma_{\alpha}^{4,(j,l)}\hat{n}_{\mathbf{k}\sigma}\hat{n}_{\mathbf{k}'\sigma'} +\sum_{\beta}\Gamma_{\beta}^{6,(j,l)}\hat{n}_{\mathbf{k}\sigma}\hat{n}_{\mathbf{k}'\sigma'}\hat{n}_{\mathbf{k}''\sigma''}+\ldots~,\\
+H^{X}_{j,l}=&\sum_{\alpha}\Gamma_{\alpha}^{2}c^{\dagger}_{\mathbf{k}\sigma}c_{\mathbf{k}'\sigma'}+\sum_{\beta}\Gamma_{\beta}^{4}c^{\dagger}_{\mathbf{k}\sigma}c^{\dagger}_{\mathbf{k}'\sigma'}c_{\mathbf{k}_{1}'\sigma_{1}'}c_{\mathbf{k}_{1}\sigma_{1}}+\ldots~.
 \end{aligned}\end{equation}

### 2022-06-30 manuscript/mscript_mck_full.tex
Spa's changes

@@
 For our case, the generator turns out to be \(\mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right) \), such that the unitary operator is \(U_{(j)} = e^{\frac{\pi}{4}\left(\eta^\dagger_{(j)} - \eta_{(j)}\right) }\)~\cite{anirbanurg1}.
-If one then uses the anti-commutation and commutation properties of \(\eta_{(j)},\eta^\dagger_{(j)}\)~\cite{anirbanurg1,anirbanurg2}, the exponential can be expanded in its Taylor series and then "resummed" into the form in Eq.~\eqref{unitary}.}
+If one then uses the anti-commutation and commutation properties of \(\eta_{(j)},\eta^\dagger_{(j)}\)~\cite{anirbanurg1,anirbanurg2}, the exponential can be expanded in its Taylor series and then resummed into the form in Eq.~\eqref{unitary}.}
 
@@
 \begin{equation}\begin{aligned}
+	\label{eta_dag}
 	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \text{Tr}\left(H_{(j)}c_{j}\right)~.
@@
 The RG flow continues till a fixed point is reached at an energy \(D^*\).
-{\color{blue} The Greens function in front of $c_j$ accounts for the dynamical cost of this rotation in terms of an operator for quantum fluctuations (\(\hat \omega\)), as well as the kinetic and self-energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).}
+{\color{blue} The Greens function in front of $c_j$ (in Eq.~\ref{eta_dag}) accounts for the dynamical cost of this rotation in terms of an operator for quantum fluctuations (\(\hat \omega\)), as well as the kinetic and self-energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).}
 
@@
 There, the susceptibility becomes constant at low temperatures: \(\chi(T\to 0) = \frac{W}{4 T_K}\), \(T_K\) being the single-channel Kondo temperature and \(W\) the Wilson number \cite{wilson1975renormalization,nozieres1974fermi,bullaNRGreview,kondo_urg}.
-We have checked the case of general spin-\(S_{d}\) impurity (fig.~\ref{fig:suseptibility_impurity}) by {\color{blue}numerically diagonalising the star graph Hamiltonian}, and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
+We have checked the case of general spin-\(S_{d}\) impurity (fig.~\ref{fig:suseptibility_impurity}) by {\color{blue}diagonalising the star graph Hamiltonian numerically}, and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
 A similar divergence is also seen in the susceptibility of the outer spins, calculated by inserting a magnetic field purely on the outer spins.

### 2022-08-16 Ref Response 2/RefereeResponse.tex
prepared response to fourth ref.

--- 2022-06-30 Ref Response/RefereeResponse.tex
@@
 \usepackage{amsmath,amssymb,braket}
+\usepackage[hidelinks]{hyperref}
 \usepackage{color}
@@
 
-We thank the three referees for comments, questions and suggestions.
-These have helped substantially in improving the overall presentation of the manuscript.
-Below, we present our responses (in blue) to the points raised by the three referees in turn.
+We thank the referee for their comments and questions. We present our responses below (in blue).
 
-\section{First referee}
+\point{While the work seems carefully done and is quite thorough, what was really achieved in the end is nothing really new or non-trivial.}
 
-\point{In general, the paper is comprehensive and well-organized, though I would encourage the authors to go over the manuscript in the next revision and correct several typos and inconsistencies in notation, few of which I list below.}
-\response{We thank the referee for the comment. We have corrected the typographic errors and notational inconsistencies in the manuscript.}
-
-\point{
-Examples of minor issues:
-\response{ We thank the referee for pointing out these typographic errors.} 
-\begin{itemize}
-	\item Eq.(3), are both the commutator and anticommutator of the $\eta$
-operators equal to 1, or just the anticommutator?\\
-{\color{blue}{\bf Response:} We thank the referee for pointing out these typographic errors.
-Indeed, only the anticommutator is unity, while the commutator is actually equal to $2\hat n_j - 1$~\cite{anirbanurg1}.
-We have updated the manuscript with this correction.}
-	\item In several equations, the sum is over $\alpha$ and $\beta,$ but the operators have $\alpha$ and $\alpha^\prime$ indices.\\
-{\color{blue}{\bf Response:} We have gone through the entire manuscript and made sure that the notation is now consistent.}
-	\item Some notations, like $\theta_M$ above Eq. 16 is introduced and never
-	used.\\
-{\color{blue}{\bf Response:} We have removed redundant notation here and elsewhere in the manuscript, wherever we could find.}
-\end{itemize}
-}
-
-\point{
-Can this technique of using the star graph together with effective Hamiltonian for low energy excitations be also used to obtain dynamical properties such as conductance?
-As this is often one of the most important experimental probes used to study Kondo problems, I would be interested to learn if URG can provide additional insight.}
-
-\response{ We are grateful to the referee for this question.
-Indeed, we have used the URG method in the past to compute certain dynamic quantities for the single-channel Kondo model in an earlier work~\cite{kondo_urg}, e.g., the impurity Greens function and spectral functions at both zero and finite temperatures.
-This was done by working with the fixed point Hamiltonian obtained from the URG flow (and without taking the zero bandwidth limit).
-The spectral function revealed the expected Abrikosov-Suhl resonance at zero frequency, and satisfied the Friedel sum rule.
-We believe that computations can also be performed using the complete fixed point Hamiltonian (i.e., not just that of the star graph) in order to obtain other Greens functions that yield dynamical quantities like the conductance or the resistance.
-We propose to develop this in a future work.}
-
-\point{
-In several places, the authors mention performing numerical calculations to verify the obtained results (for example paragraph above Eq 19 about impurity susceptibility).
-What method was used to perform the calculations?
-Is it just evaluation of for example Eq 15 for the Heisenberg Hamiltonian of the star graph or is the numerical calculation itself performing the renormalization treatment?}
-
-\response{ In the example cited in the question, we used numerical calculations in the sense of solving the star graph Hamiltonian using exact diagonalisation and then using Eq.(19) to obtain the susceptibility.
-In the Supplementary Material~\cite{SM}, in order to obtain the contribution to the susceptibility coming from the non-Fermi liquid, we numerically diagonalise the Hamiltonian formed of the star graph and the single-particle excitations into the conduction bath.
-We have now clarified the methods employed below eq.(18) as well as below Fig.5 in the main manuscript and supplementary materials (above eq.(40)).}
-
-\point{
-Expanding on the previous point, can unitary renormalization group approach give rise to some new numerical technique akin to numerical renormalization group?}
-
-\response{We thank the referee for this excellent question.
-In the present work (as well as our earlier work on the single channel Kondo effect~\cite{kondo_urg}), we have emphasised obtaining various measurable thermodynamic and dynamical quantities of the quantum impurity model from the numerical diagonalisation of the fixed point effective Hamiltonian of the URG flow.
-In Ref.\cite{kondo_urg}, we found that this gave reasonably good qualitative agreement with the results obtained from the NRG method (in terms of the asymptotic values and the nature of the crossover).
-However, it is also possible to compute various quantities at several points along the URG flow, in the spirit of the NRG procedure.
-Implementing this would, we believe, take us closer to a technique akin to NRG.
-\par\noindent
-Importantly, given that the URG can be (and has already been) applied to a variety of models across dimensions, this would help overcome the major limitation of NRG in being applicable only to quantum impurity models.
-It will be interesting to see the trade-off between an increase in quantitative accuracy versus the complexity of the numerical implementation.
-This challenge we leave to the future.
-However, it is worth pointing out that we have already adopted the philosophy mentioned above in implementing a momentum-space entanglement renormalisation group (MERG) scheme based on the URG method.
-Indeed, we have applied the MERG to the study of several problems of strongly correlated electrons (e.g., the 2D Hubbard model on the square lattice at and away from $1/2$-filling~\cite{mukherjeeMERG2022}, the single channel Kondo problem~\cite{kondo_urg}, the 1D Hubbard model~\cite{1dhubjhep} and the 2D reduced BCS model~\cite{siddharthacpi}).}
-
-\section{Second referee}
-
-\point{
-My main comments concern Section II-A, in which the authors define the RG procedure.
-Since the results of the other Sections follow from the results of this Section, I would suggest the authors expand it.
-Also, some of the results that come later using this technique are familiar to the experts in the field of heavy fermions, but the RG procedure may not be.}
-
-\response{We thank the referee for raising this point.
-Given the present length of the work, it will be difficult for us to add substantial material devoted to explaining various features of the URG method in the main manuscript.
-Instead, we have improved Sec.
-4 of the Supplementary Materials (which contains the detailed derivation of the URG flow equations) to cover this: a new subsection (4A) now includes a detailed discussion of the method.
-In addition, we have addressed within the main manuscript the specific questions that the referee has brought up in the two points immediately following this one (and which are related to the URG method).
-Finally, we have also pointed the readers towards a complete derivation of the URG formalism in Refs.~\cite{anirbanurg1,anirbanurg2}.
-We earnestly request the referee to kindly bear with us on this.}
-
-\point{
-It would benefit the reader of this article to get some intuition about the generators, Eqs. (3) and (4). Is there a simple way to understand this choice?}
-
-\response{The unitary operator \(U\) mentioned in Eq.(3) can be thought of as a special case of the most general form \(U = e^\mathcal{S}\) of a unitary operator defined by an anti-Hermitian generator \(\mathcal{S}\).
-As shown in detail in Ref.\cite{anirbanurg1}, for our case, the generator turns out to be \(\mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger - \eta \right) \), such that the unitary operator is \(U = e^{\frac{\pi}{4}\left(\eta^\dagger - \eta\right) }\).
-If one then uses the anticommutation and commutation properties of \(\eta,\eta^\dagger\), the exponential can be expanded in a Taylor series and then resummed into the form mentioned in the manuscript.
-\par\noindent
-The fermionic operators \(\eta_{(j)},\eta^\dagger_{(j)}\) of Eq.(4) can be thought of as the many-particle analogue of the single-particle field operators \(c_j,c^\dagger_j\) that change the occupation number of the single-particle Fock space \(\ket{n_j}\).
-The presence of the operators in $\eta_{(j)}$ other than $c_j$ are required to ensure that the decoupling of the specific Fock state under consideration is carried out through a unitary modification of the spectrum of the remnant degrees of freedom.
-Since the \(j^\text{th}\) degree of freedom is coupled with many others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\); this is encoded within the \(\text{Tr}\left(H_{(j)} c_j\right) \) term.
-The Greens function in front of $c_j$ accounts for the dynamical cost of this rotation in terms of an operator for quantum fluctuations (\(\hat \omega\)), as well as the kinetic and self-energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).
-\par\noindent
-We have updated the manuscript with these explanations in Sec.IIA, below eqs.(3), (4) and (5). We are thankful to the referee for these questions.
-}
-
-\point{Other RG proposals come from applying a set of successive unitary transformations (such as the Wegner RG, as discussed in detail in ``The Flow Equation Approach to Many-Particle Systems" by Stefan Kehrein).
-How does this approach differ from those?}
-
-\response{
-There are atleast two specific distinctions between the continuous unitary transformations (CUT) RG as envisaged by Wegner and the URG of the present work.
-\begin{itemize}
-	\item While most RG methods that apply successive unitary transformations rely on a gradual decrease in the off-diagonal content of the Hamiltonian, the URG proceeds by decoupling each discrete Fock space node at a time.
-In other words, the URG achieves a block-diagonalisation of the Hamiltonian at each RG step, while the CUT RG involves a gradual decay of the off-diagonal terms of the Hamiltonian in order to make it more band diagonal.
-	\item The CUT RG involves choosing a truncation scheme that allows closing the RG equations.
-The URG, on the other hand, is able to resum the coupling expansion series through the denominator structure and the quantum fluctuation operator.
-\end{itemize}
-We have improved the manuscript by adding these comparisons.
-Comparisons of the URG with other methods like the functional RG or the spectrum bifurcation RG can also be found in Refs.~\cite{anirbanmott1,anirbanurg1}.
-}
-
-\point{Also, in Section II, the authors denote by $\ket{j}$ the highest energy electronic state.
-In this problem, assuming a quadratic dispersion to the electrons in 3 dimensions, the Fermi surface would generally be a sphere.
-Would $\ket{j}$ be the set of states with $k=k_{F}$?}
-
-\response{We thank the referee for the question.
-At a particular RG step, the symbol \(\ket{j}\) is used to label the collection of the most energetic single particle Fock states of the bath in momentum-space that can be accessed from the ground state by virtual quantum fluctuations (and which are resolved by the decoupling procedure).
-In more conventional language, this collection of states lies at the running cutoff \(\Lambda\) (bandwidth) of the field theory.
-The bandwidth shrinks as the RG proceeds, and \(\ket{j}\) is updated to states at lower energies until it hits the Fermi surface (assuming the RG has not reached a fixed point by then).
-}
-
-\point{
-This block in the Introduction is a bit hard to understand and maybe could be rewritten: ``the ground state is susceptible to perturbations that introduce channel isotropy in the exchange couplings [14, 32, 37, 45, 52].
-This makes the experimental realisation of such states quite challenging." Do the authors mean channel anisotropy instead of channel isotropy?}
-
-\response{ Indeed, we meant ``anisotropy" instead of isotropy. We have thus rectified the mistake. We thank the referee for pointing this out.}
-
-\point{ 
-After Eq. (7), implicit summation over the spin indices $\alpha,\beta$ should be $\alpha,\alpha^\prime$.}
-
-\response{We thank the referee for pointing this out, and have rectified the mistake in the manuscript.}
-
-\point{ 
-In Eq. (8) and the text after Eq. (8), why are there two sums in the
-k-expansion of S, over $k$ and $k^\prime$, as opposed to only one sum over k? Also, there is an issue with $\alpha^\prime$ and $\beta$ variables (similar to point 2.)}
-
-\response{We have rectified the issue with the spin label \(\alpha^\prime\) label.
-With regards to the two momentum summations \(k,k^\prime\) in the expressions of \(\vec S\) in and below Eq.(8), both the summations are indeed required.
-This is because the expression for the spin operator in eq.(8) can be obtained by Fourier transforming the real-space local spin operator \(\sum_{\alpha\alpha^\prime}\vec \sigma_{\alpha\alpha^\prime}c^\dagger_{\alpha}c_{\alpha^\prime}\) formed by the conduction electrons \(c_{\alpha},c_{\alpha^\prime}\) at the origin.
-The Fourier transformation involves two $k$-space sums (one for each real-space operators).}
-\point{
-In Fig. 3, legend, one of the triangles should be a circle.}
-
-\response{We have updated the plot with the correct legend. We are grateful to the referee for pointing this out.}
-
-\point{
-After Eq. (18), the authors attribute a 1/T contribution to the
-susceptibility as a signature of the critical nature of the Hamiltonian.
-This 1/T (Curie)-behavior is present for the susceptibility of a single magnetic moment in a magnetic field.
-I don't see critical behavior in this.
-The log corrections to 1/T would be a signature of criticality.}
-
-\response{We had (incorrectly) used the term critical to reflect the fact that the \(1/T\) divergence was a result of the remnant degeneracy of the system at the fixed point (reflecting an unscreened moment).
-In order to avoid any confusion on this point, we have removed the usage of the word ``critical" in this context from all places in the manuscript.}
-
-\point{
-Also, in Eq. (8), why does it vanish only for $K=1$, and not when $K=2S_{d}$, in general?}
-
-\response{We believe the referee is referring to Eq.(18) here, and not Eq.(8).
-The expression in Eq.(18) was derived for the specific case of $S_d = 1/2$ (spin-half impurity), and hence it only vanishes at $K=2S_d=1$.
-while we do not have an analytic expression of this at present for the case $K=2S_{d}$, we have checked numerically that this is indeed the case.
-This is reported in Fig.(4).}
-
-\point{
-In Section IV A, the authors classify the terms as Fermi liquid or non-Fermi liquid.
-Is there a simple way to understand this classification?
-A possible way is by characterizing the effects of each term, but my question is if there is an immediate way of knowing if the term is FL or NFL.}
-
-\response{ We thank the referee for seeking a clarification on this point.
-We used the term “non-Fermi liquid” to reflect the fact that, in the RG sense, the low energy $k−$space Hamiltonian was not purely of an $F_{kk^\prime} n_k n_{k^\prime}$ density-density type interaction term (which is characteristic of a Fermi liquid).
-Indeed, the off-diagonal terms in the effective Hamiltonian obtained in eq.(44) is shown to involve a dominant contribution corresponding to an effective Marginal Fermi liquid effective Hamiltonian (eq.(49), involving a $n_{k\sigma} n_{k^{\prime}\uparrow}(1-n_{k^{\prime}\downarrow})$ interaction term, and as shown in an earlier work by us on the 2D Hubbard model~\cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2}).}
-
-\section{Third referee}
-
-\point{
-Perhaps the most interesting part is the “star graph” analysis which
-are done rigorously as far as I can judge. However, I am not convinced
-(especially not by the authors) that the strong coupling teaches
-anything useful for the infrared physics. If there is a clear physics
-lesson here, it is lost in the myriad of technicalities in the paper.
-}
-
-\response{We thank the referee for this question.
-Upon flowing from the weakly coupled theory to the fixed point under the renormalization group transformations, there is a reduction in the effective bandwidth of the problem (leading to reduced excitations into the conduction band) together with a growth in the effective Kondo coupling.
-This involves a growth in the ratio of the Kondo coupling to the bandwidth of the conduction band, and enables a study of the emergent star graph (obtained from a zero bandwidth approximation) as a ``skeletal" problem for the low-energy physics.
-Such an approach reveals, for instance, the ground state of the multichannel problem and the degeneracy (Sec.III of the main manuscript).
-Moreover, it allows studying the effects of excitations (from a calculation in the spirit of Nozieres' calculation for the single channel Kondo problem), as demonstrated by the identification of its local non-Fermi liquid nature (Sec.IV and V of the main manuscript and parts of the Supplementary Materials).
-}
-
-\point{
-Derivation of the effective fixed
-point Hamiltonian, cannot be trusted since there is no argument that
-subsequent steps are going to make smaller changes (as opposed to
-Wilson’s NRG).
-}
-
-\response{
-We respectfully disagree with the referee on this point.
-As shown by us in Ref.\cite{anirbanurg1} in detail, the URG involves a resummation to all orders of renormalisations in various couplings.
-This is revealed by the non-perturbative structure of the URG equation.
-This ensures that the fixed point Hamiltonians obtained from URG indeed account for the effects of the UV on the IR, and are stable under renormalised perturbation theory (in the RG sense).
-This has been demonstrated by us in application of the URG to a variety of problems involving correlated electrons (included in the list of references in the main manuscript).
-Furthermore, in a recently published work of ours on the single channel Kondo problem~\cite{kondo_urg}, we have compared the results for several thermodynamic and dynamical measurables obtained from the URG against that obtained from methods such as NRG, and obtained very good agreement.
-}
-
-\point{
-It’s highly
-technical and I believe it does not add anything to what we know and
-furthermore, some steps and arguments are, in my opinion, not really
-correct.
-}
-
-\response{
-Again, we respectfully disagree with the referee.
-We believe that the following results are new and interesting additions to the knowledge of multichannel Kondo physics that are obtained from our work:
+\response{We believe that the following results are new and interesting additions to the knowledge of multichannel Kondo physics that are obtained from our work:
 \begin{itemize}
@@
 }
+
+\point{Despite the motivation from a complex RG scheme, the authors simply investigate in the end the zero bandwidth 2-channel Kondo model (2CKM),  which is the simple problem of a spin coupled to two fermions.
+This is already contained in the seminal paper of Nozières and Blandin in 1981.
+The authors claim this gives perspectives on the 2CKM fixed point, but on the contrary, the argument of Nozières and Blandin is to show that this zero-bandwidth fixed point is unstable, hence a non-trivial interacting state should arise.
+}
+
+\response{First, we point out that we have studied much more than simply the zero-bandwidth model for the 2CKM.
+We have already stated in response to  Point 1 above the important questions that we have answered for the MCK problem and which are beyond the purview of a zero-bandwidth model.
+
+Second, we comment on the validity of our study of the zero-bandwidth  model at the \textbf{intermediate coupling fixed point (ICFP)} of the MCK  problem.
+Nozieres and Blandin indeed present an argument for why the  zero-bandwidth model at the \textbf{strong coupling fixed point ($J=\infty$)}  is unstable due to the existence of non-trivial RG relevant quantum  fluctuations.
+The resulting RG flow of the Kondo coupling $J$ to  the ICFP resolves these quantum fluctuations.
+The RG stability of the  Kondo coupling $J$ at the ICFP then allows for a renormalised perturbation  theory approach to studying the fixed point Hamiltonian.
+Specifically, the  zero-bandwidth model can be safely extracted (in the RG sense) as the zeroth  approximation of a renormalised perturbation theory in the ratio of  the conduction bath hopping amplitude ($t$) to $J$.
+A study of the  zero-bandwidth model at the ICFP offers, in turn, new perspectives  into the problem, e.g., the ground state degeneracy and it's relation  to the breakdown of exact screening etc.
+In response to the next point, we  comment below on our ability to capture the critical corrections to this zeroth  approximation.
+}
+
+\point{While this study could have some pedagogical value per se, it is  often unnecessarily technical, and some statements are clearly incorrect.
+For instance, the authors failed to see that the 1/T susceptibility is a trivial feature of the zero-bandwidth toy-model, while the true 2CKM fixed point has critical corrections.
+I don't think these can be so easily captured by the expansion they propose.}
+
+\response{As has been shown in considerable detail in Section IV A of the  main manuscript and Section III of the supplementary materials, we have  extracted analytically the effective theory for the low-lying excitations  above the degenerate ground states of the zero-bandwidth model by carrying  out a careful renormalised pertubation theory in $t/J$ for both the 2CK and  3CK problems.
+We have demonstrated the non-Fermi liquid nature of these  excitations, and also confirmed their critical nature by the computation of  some thermodynamic quantities in Section IIIB for the 2CK.
+Indeed, we have  obtained the well-known logarithmic dependence of the specific heat and  susceptibility on temperature from our calculations.
+Again, this further  validates our approach.}
 

### 2022-08-16 Ref Response 2/RefereeResponse.tex
ref response

@@
 \usepackage{xcolor}
-\usepackage[legalpaper, portrait]{geometry}
+\usepackage[legalpaper,portrait,margin=2cm]{geometry}
 \DeclareUnicodeCharacter{2212}{-}
@@
 
-\author{Siddhartha Patra, Abhirup Mukherjee, Anirban Mukherjee, N. S. Vidhyadhiraja,\\ A. Taraphder, S Lal}
+\title{Referee response to BS14324 Patra}
+\author{Siddhartha Patra, Abhirup Mukherjee, Anirban Mukherjee, N. S. Vidhyadhiraja,\\ A. Taraphder, Siddhartha Lal}
 
-\title{Referee response to BS14324 Patra}
 \begin{document}
@@
 
+\section*{Response to the fourth referee}
 \point{While the work seems carefully done and is quite thorough, what was really achieved in the end is nothing really new or non-trivial.}
@@
 	\item importance of the role of degeneracy and quantum-mechanical frustration in shaping the infrared physics of the MCK, specifically in the absence of any Fermi liquid component and the emergence of non-Fermi liquid behaviour, the thermodynamic properties, the orthogonality catastrophe, the breakdown of screening and in the strong-weak duality,
-	\item derivation of a marginal Fermi liquid effective Hamiltonian for the non-Fermi liquid fixed point, hence revealing the microscopic source of the non-Fermi liquid behaviour in the overscreened regime,
+	\item derivation of a marginal Fermi liquid effective Hamiltonian for the non-Fermi liquid fixed point, hence revealing the microscopic source of the non-Fermi liquid behaviour in the overscreened regime; we have confirmed in the supplementary materials that the $\ln T$ behaviour of the impurity specific heat and susceptibility in the 2CKM arises from this effective Hamiltonian
 	\item the presence of a spin Mott liquid in the effective interactions among the conduction electrons,
@@
 This can be seen, for instance, in the emergence of a Mott liquid from the 2D Hubbard model as seen from a URG analysis~\cite{anirbanmott1,anirbanmott2,mukherjeeMERG2022} and a Cooper pair insulator from the reduced 2D BCS Hamiltonian~\cite{siddharthacpi}.
-Importantly, we have also corroborated several of our analytic and numerical results with those that exist in the literature.
+Importantly, we have also corroborated several of our analytic and numerical results for the MCK with those that exist in the literature.
 }
@@
 \response{First, we point out that we have studied much more than simply the zero-bandwidth model for the 2CKM.
-We have already stated in response to  Point 1 above the important questions that we have answered for the MCK problem and which are beyond the purview of a zero-bandwidth model.
-
+We have already stated in response to  Point 1 above the important questions that we have answered for the MCK problem and which are beyond the purview of a zero-bandwidth model.\\
+\par\noindent
 Second, we comment on the validity of our study of the zero-bandwidth  model at the \textbf{intermediate coupling fixed point (ICFP)} of the MCK  problem.
@@
 A study of the zero-bandwidth model at the ICFP offers, in turn, new perspectives  into the problem, e.g., the ground state degeneracy and it's relation  to the breakdown of exact screening etc.
-In response to the next point, we  comment below on our ability to capture the critical corrections to this zeroth  approximation.
+It also informs us on the ground state manifold about which to carry out a systematic treatment of a renormalised perturbative expansion.\\
+\par\noindent
+In response to point 3 below, we  comment on our ability to capture the critical corrections to this zeroth  approximation.
+Finally, we have added a few lines to the manuscript at the end of  Subsection II-B in order to clarify the validity of our zero-bandwidth approximation.
+We believe that, taken together with our summary of main results, this offers adequate clarification of the approach taken and results achieved.
 }
@@
 We have demonstrated the non-Fermi liquid nature of these  excitations, and also confirmed their critical nature by the computation of  some thermodynamic quantities in Section IIIB for the 2CK.
-Indeed, we have  obtained the well-known logarithmic dependence of the specific heat and  susceptibility on temperature from our calculations.
-Again, this further  validates our approach.}
+Indeed, in keeping with the point raised by the referee, we have  obtained the well-known logarithmic dependence of the specific heat and  susceptibility on temperature from our calculations.
+We trust that the referee will find this a satisfactory demonstration.}
 
-\section{Some additional changes in the manuscript}
-We made the following additional changes in the manuscript, apart from those arising from the suggestions made by the referees (as mentioned above).
-\begin{itemize}
-	\item Included two new references on the CUT and similarity RG methods (Refs.75 and 76 respectively),
-	\item Updated Ref.106 (Ref.104 of the previous manuscript) from the arxiv preprint reference to the published journal reference,
-	\item Modified the acknowledgments to thank all three referees for their helpful comments.
-\end{itemize}
+%\section*{Some additional changes in the manuscript}
+%We made the following change in the manuscript:
+%\begin{itemize}
+%	\item In order to clarify the validity of our zero-bandwidth approximation, we have added a few lines to the manuscript at the end of  Subsection II-B.
+%\end{itemize}
 

### 2022-08-16 manuscript/mscript_mck_full.tex
ref response

--- 2022-06-29 manuscript/mscript_mck_full.tex
@@
 Our results display the importance of ground state degeneracy in explaining various important properties like the breakdown of screening and the presence of local non-Fermi liquids.
-The impurity susceptibility of the intermediate coupling fixed point Hamiltonian in the zero-bandwidth (or star graph) limit shows a power-law divergence at low temperature{\color{red}, signalling its critical nature}.
+The impurity susceptibility of the intermediate coupling fixed point Hamiltonian in the zero-bandwidth (or star graph) limit shows a power-law divergence at low temperature.
 Despite the absence of inter-channel coupling in the MCK fixed point Hamiltonian, the study of mutual information between any two channels shows non-zero correlation between them.
@@
 \section{Introduction}
-%{\color{blue}
+
 A local antiferromagnetic exchange interaction between a spin-\(\frac{1}{2}\) impurity and its host metal gives rise to the well-understood phenomenon of the Kondo effect (\cite{kondo1964resistance}, see ~\cite{hewson1993} for an extensive discussion).
@@
 The degree of compensation is simply the average correlation between the impurity spin and the conduction channel local spins; it is found to be maximum at exact screening, and decreases for both over- and under-screening.
-The magnetisation and susceptibility of the star graph model show {\color{red}critical behaviour in the form} a discontinuity and a \(T^{-1}\) divergence respectively.
+The magnetisation and susceptibility of the star graph model show a discontinuity and a \(T^{-1}\) divergence respectively.
 We also explore the topological properties of the degenerate ground state manifold of the star graph model using non-local twist and translation operators.
@@
 where \(\left\{\cdot\right\}\) is the anticommutator.
-{\color{blue} Further, $\left[ \eta_{(j)},\eta_{(j)}^\dagger \right] = 2\hat n_{j}-1$.
+Further, $\left[ \eta_{(j)},\eta_{(j)}^\dagger \right] = 2\hat n_{j}-1$.
 The unitary operator \(U_{(j)}\) mentioned in Eq.~\eqref{unitary} can be thought of as a special case of the most general form \(U = e^\mathcal{S}\) of a unitary operator defined by an anti-Hermitian generator \(\mathcal{S}\).
 For our case, the generator turns out to be \(\mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right) \), such that the unitary operator is \(U_{(j)} = e^{\frac{\pi}{4}\left(\eta^\dagger_{(j)} - \eta_{(j)}\right) }\)~\cite{anirbanurg1}.
-If one then uses the anti-commutation and commutation properties of \(\eta_{(j)},\eta^\dagger_{(j)}\)~\cite{anirbanurg1,anirbanurg2}, the exponential can be expanded in its Taylor series and then "resummed" into the form in Eq.~\eqref{unitary}.}
+If one then uses the anti-commutation and commutation properties of \(\eta_{(j)},\eta^\dagger_{(j)}\)~\cite{anirbanurg1,anirbanurg2}, the exponential can be expanded in its Taylor series and then resummed into the form in Eq.~\eqref{unitary}.
 
@@
 \begin{equation}\begin{aligned}
+	\label{eta_dag}
 	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \text{Tr}\left(H_{(j)}c_{j}\right)~.
 \end{aligned}\end{equation}
-{\color{blue}The operators \(\eta_{(j)},\eta^\dagger_{(j)}\) can be thought of as the many-particle analogue of the single-particle field operators \(c_j,c^\dagger_j\) that change the occupation number of the single-particle Fock space, \(\ket{n_j}\).
+The operators \(\eta_{(j)},\eta^\dagger_{(j)}\) can be thought of as the many-particle analogue of the single-particle field operators \(c_j,c^\dagger_j\) that change the occupation number of the single-particle Fock space, \(\ket{n_j}\).
 The presence of the operators in $\eta_{(j)}$ other than $c_j$ are required to ensure that the decoupling of the specific Fock state under consideration is carried out through a unitary modification of the spectrum of the remnant degrees of freedom.
-Since the \(j^\text{th}\) degree of freedom is coupled with many others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\); this is encoded within the \(\text{Tr}\left(H_{(j)} c_j\right) \) term.}
+Since the \(j^\text{th}\) degree of freedom is coupled with many others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\); this is encoded within the \(\text{Tr}\left(H_{(j)} c_j\right) \) term.
 The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms in the Hamiltonian:
@@
 The RG flow continues till a fixed point is reached at an energy \(D^*\).
-{\color{blue} The Greens function in front of $c_j$ accounts for the dynamical cost of this rotation in terms of an operator for quantum fluctuations (\(\hat \omega\)), as well as the kinetic and self-energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).}
-
-{\color{blue}There exist other renormalisation group schemes that depend on canonical transformations, such as Wegner's continuous unitary transformations (CUT) RG~\cite{wegner1994flow} and the similarity RG method by Glazek and Wilson~\cite{glazek1993renormalization}.
+The Greens function in front of $c_j$ (in Eq.~\ref{eta_dag}) accounts for the dynamical cost of this rotation in terms of an operator for quantum fluctuations (\(\hat \omega\)), as well as the kinetic and self-energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).
+
+There exist other renormalisation group schemes that depend on canonical transformations, such as Wegner's continuous unitary transformations (CUT) RG~\cite{wegner1994flow} and the similarity RG method by Glazek and Wilson~\cite{glazek1993renormalization}.
 There are at least two specific distinctions between the CUT RG and the URG method adopted in the present work.
@@
 Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~\cite{anirbanmott1,anirbanurg1}.
-}
 
@@
 
-In the following sections, we will show how the inherent quantum-mechanical frustration of singlet order that is present in the Hamiltonian leads to the non-trivial physics of the fixed points in terms of non-Fermi liquid phase, diverging thermodynamic quantities, quantum criticality as well as emergent gauge theories.
+{\color{blue}
+We now comment on the validity of our study of the zero-bandwidth  model at the intermediate coupling fixed point (ICFP) of the MCK  problem.
+Nozieres and Blandin indeed present an argument for why the  zero-bandwidth model at the strong coupling fixed point ($J =\infty$)  is unstable due to the existence of non-trivial RG relevant quantum  fluctuations~\cite{Noz_blandin_1980}.
+The resulting RG flow of the Kondo coupling $J$ to  the ICFP resolves these quantum fluctuations.
+The RG stability of the  Kondo coupling $J$ at the ICFP then allows for a renormalised perturbation  theory approach to studying the fixed point Hamiltonian.
+Specifically, the  zero-bandwidth model can be safely extracted (in the RG sense) as the zeroth  approximation of a renormalised perturbation theory in the ratio of  the conduction bath hopping amplitude ($t$) to $J$.
+A study of the  zero-bandwidth model at the ICFP offers, in turn, new perspectives  into the problem, e.g., the ground state degeneracy and it's relation  to the breakdown of exact screening etc., as described in the two preceding paragraphs.
+It also informs us on the ground state manifold about which to carry out a systematic renormalised perturbative expansion to obtain the low-lying excitations (see Sec.\ref{sec:excitations} below, and Sec.III of the supplementary materials).
+Moreover, in} the following sections, we will show how the inherent quantum-mechanical frustration of singlet order that is present in the Hamiltonian leads to the non-trivial physics of the fixed points in terms of non-Fermi liquid phase, diverging thermodynamic quantities, quantum criticality as well as emergent gauge theories.
 \section{Important Properties of the Star Graph}
@@
 The \(\chi\) is seen to diverge as \(T^{-1}\) at low temperatures.
-Such a non-analyticity in a response function is {\color{red}a signature of the critical nature of the Hamiltonian.
-This is} in contrast to the behaviour in the {\color{red}non-critical} exactly-screened fixed point where the ground state is unique.
+Such a non-analyticity in a response function is in contrast to the behaviour in the exactly-screened fixed point where the ground state is unique.
 There, the susceptibility becomes constant at low temperatures: \(\chi(T\to 0) = \frac{W}{4 T_K}\), \(T_K\) being the single-channel Kondo temperature and \(W\) the Wilson number \cite{wilson1975renormalization,nozieres1974fermi,bullaNRGreview,kondo_urg}.
-We have checked the case of general spin-\(S_{d}\) impurity (fig.~\ref{fig:suseptibility_impurity}) by {\color{blue}numerically diagonalising the star graph Hamiltonian}, and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
+In Fig.~\ref{fig:suseptibility_impurity}, we have checked the case of general spin-\(S_{d}\) impurity by diagonalising the star graph Hamiltonian numerically, and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
 A similar divergence is also seen in the susceptibility of the outer spins, calculated by inserting a magnetic field purely on the outer spins.
@@
 This available space for scattering is simply the frustration that we discussed earlier.
-Indeed, we have checked (see fig.~\ref{mag_crit}) {\color{blue} by diagonalising numerically the star graph Hamiltonian} that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S_{d}\) is the deviation from exact screening.
+Indeed, we have checked (see Fig.~\ref{mag_crit}) by diagonalising numerically the star graph Hamiltonian that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S_{d}\) is the deviation from exact screening.
 Some additional results are presented in the Supplementary Materials~\cite{SM}.
@@
 At that point, the model becomes a two channel Kondo problem.
-%{\color{red}
 We also show in Fig.~\ref{fig:channel-anisotropy-}(b) that taking the coupling ${\mathcal{J}}_3$ fixed to $1$ and varying the common coupling ${\mathcal{J}}_1={\mathcal{J}}_2$ from non-zero to zero is equivalent to keeping ${\mathcal{J}}_1={\mathcal{J}}_2=1$ fixed and taking ${\mathcal{J}}_3$ to infinity.
 In this case, when the coupling ${\mathcal{J}}_1={\mathcal{J}}_2=0$, the degeneracy becomes one and reveals the single channel nature of the problem.
-%}
 

### 2022-12-23 MCK-EE/supplementary_mck.tex
impurity fractional EE

\documentclass{revtex4-2}
\usepackage{braket,amsmath,amssymb}
\allowdisplaybreaks
\begin{document}
\title{Impurity entanglement entropy of 2-channel fixed point}
\maketitle
The zero-mode Hamiltonian at the renormalisation group fixed point is a star graph with the impurity as the central node and the zeroth sites of the two conduction channels as the outer nodes: \(H_0 = J^*\vec{S}_d\cdot\sum_{l} \vec{S}_{0,(\alpha)}\), where \(\alpha\) (and Greek letters in genral) denote the channel index. The ground-states of this \(2-\)channel star graph are
\begin{equation}\begin{aligned}
	\ket{\sigma/2} = \frac{\sigma}{\sqrt 6}\left( 2\ket{\sigma \bar\sigma \sigma} - \ket{\bar\sigma \sigma \sigma} - \ket{\sigma \sigma \bar\sigma}\right), \sigma=\pm 1
\end{aligned}\end{equation}
where three confifurations inside the ket are those of the impurity spin, the \(\alpha=1\) channel zeroth site and the \(\alpha=2\) channel zeroth site respectively.
In the full Hamiltonian, there is also the hopping term: \(H_\text{int} = -\frac{t}{N}\sum_{k,\alpha}\left( c^\dagger_{0\sigma,(\alpha)}c_{k\sigma,(\alpha)} + \text{h.c.}\right) \). Introducing the \(k-\)space states into \(H_0\) leads to the following ground-states, classified by \(S_\text{tot}^z = S_d^z + \sum_l S_{0,l}^z + \sum_k \sum_l S_{k,l}^z\) and the filling \(\nu\) of \(k-\)space electrons:
\begin{gather}
	S_\text{tot}^z = 0: \begin{cases}
	\nu=1: \ket{\sigma/2}\ket{h_{\sigma, (\alpha)}},\\
	\nu=3: \ket{\sigma/2}\ket{e_{\bar\sigma, (\alpha)}},\\
	\end{cases} \sigma=\pm 1, \alpha=1,2\\
	S_\text{tot}^z = \frac{\sigma}{2}: \nu=2: \ket{\sigma/2}\ket{\phi}, \sigma=\pm 1\\
	S_\text{tot}^z = \sigma: \begin{cases}
	\nu=3: \ket{\sigma/2}\ket{e_{\sigma, (\alpha)}},\\
	\nu=1: \ket{\sigma/2}\ket{h_{\bar\sigma, (\alpha)}},
	\end{cases}  \sigma=\pm 1, \alpha=1,2
\end{gather}
where \(\ket{\phi}\) is the filled Fermi sea, and \(\ket{e_{\sigma, (\alpha)}}\) and \(\ket{\sigma, (\alpha)}\) are gapless particle and hole excitations: \(\ket{e_{\sigma, (\alpha)}} = \sum_{k \in FS} c^\dagger_{k\sigma,(\alpha)}\ket{\phi}, \ket{h_{\sigma, (\alpha)}} = \sum_{k \in FS} c_{k\sigma,(\alpha)}\ket{\phi}\). The filling \(\nu_1\) and \(\nu_2\) in \(\ket{\phi}\) were set to unity, so that the filling \(\nu\) of the \(\ket{e}\) and \(\ket{h}\) states are 3 and 1 respectively.

In order to obtain the impurity entanglement entropy, we will use the result that the impurity reduced density matrix can be written in terms of the impurity magnetisation (\(m_d^z\)):
\begin{equation}\begin{aligned}
	\rho_\text{imp} = \frac{1}{2}\mathcal{I} + m_d^z \sigma^z 
\end{aligned}\end{equation}
where \(\sigma^z = \begin{pmatrix} 1 & 0 \\ 0 & -1 \end{pmatrix} \) is the Pauli matrix along \(z\). The problem then boils down to calculating the magnetisation \(m_d^z\). For that, we will first obtain the new ground-states in the presence of \(H_\text{int}\). After that, we will insert a global magnetic field into the new ground-state subspace, which will favour the states with the most positive \(S_\text{tot}^z\). The expectation value of \(S_d^z\) in these favoured ground-states, in the presence of a vanishing field, will be the impurity magnetisation. The fact that the subspace with highest \(S_\text{tot}^z\) will be favoured means we only need to solve \(H_\text{int}\) in the subspace of \(S_\text{tot}^z = +1\). This is because the full Hamiltonian and \(H_\text{int}\) conserve \(S_\text{tot}^z\). The pertinent ground-states are
\begin{equation}\begin{aligned}
	S_\text{tot}^z = 1: \begin{cases}
	\nu=3: \begin{cases}
		\nu_{(1)}=2: \ket{1/2}\ket{e_{\uparrow, (1)}}\\
		\nu_{(2)}=2: \ket{1/2}\ket{e_{\uparrow, (2)}}\\
	\end{cases}\\
	\nu=1: \begin{cases}
		\nu_{(1)}=0: \ket{1/2}\ket{h_{\downarrow, (1)}}\\
		\nu_{(2)}=0: \ket{1/2}\ket{h_{\downarrow, (2)}}
	\end{cases}
	\end{cases} 
\end{aligned}\end{equation}
Since \(H_\text{int}\) conserves the filling \(\nu_{(\alpha)}\) of each channel individually, these four states are not mixed by the perturbation \(H_\text{int}\), at any order. The impurity magnetisation then reduces to
\begin{equation}\begin{aligned}
	m_d^z = \braket{1/2 | S_d^z | 1/2 } = \frac{1}{6}\left(4\times\frac{1}{2} - \frac{1}{2} + \frac{1}{2}\right) = \frac{1}{3}
\end{aligned}\end{equation}
The impurity entanglement entropy can then be obtained from \(\rho_\text{imp}\):
\begin{equation}\begin{aligned}
	S_\text{EE}(d) = -\left( \frac{1}{2} + m_d^z \right) \ln\left( \frac{1}{2} + m_d^z \right) - \left( \frac{1}{2} - m_d^z \right) \ln\left( \frac{1}{2} - m_d^z \right) \simeq 0.65\ln 2
\end{aligned}\end{equation}

\end{document}

### 2022-12-23 manuscript/Supplementary/supplementary_mck.tex
impurity fractional EE

@@
 \section{Additional Topological Features of the Local Mott liquid}
-{\color{blue}\subsection{Non-local twist operators and ground state degeneracy}}
+\subsection{Non-local twist operators and ground state degeneracy}
 
@@
 Here we briefly discuss the choice of the closed-loop $\mathcal{C}_{\mu}$ and the insertion of the flux.
-As shown in the {\color{blue}Fig.\ref{fig:stargraph-to-alltoall}(b)} we have chosen a particular closed path which crosses all the outer spin only once.
+As shown in the Fig.\ref{fig:stargraph-to-alltoall}(b) we have chosen a particular closed path which crosses all the outer spin only once.
 We embed that closed-loop on a plane and put the flux perpendicular to the plane through the closed loop.
@@
 \label{appendix_urg}
-{\color{blue}
+
 \subsection{Details of the URG method}
@@
 The unitary transformations preserve the partition function along the RG flow.
-}
 

### 2022-12-23 manuscript/mscript_mck_full.tex
impurity fractional EE

@@
 
-{\color{blue}
 We now comment on the validity of our study of the zero-bandwidth  model at the intermediate coupling fixed point (ICFP) of the MCK  problem.
@@
 It also informs us on the ground state manifold about which to carry out a systematic renormalised perturbative expansion to obtain the low-lying excitations (see Sec.\ref{sec:excitations} below, and Sec.III of the supplementary materials).
-Moreover, in} the following sections, we will show how the inherent quantum-mechanical frustration of singlet order that is present in the Hamiltonian leads to the non-trivial physics of the fixed points in terms of non-Fermi liquid phase, diverging thermodynamic quantities, quantum criticality as well as emergent gauge theories.
+Moreover, in the following sections, we will show how the inherent quantum-mechanical frustration of singlet order that is present in the Hamiltonian leads to the non-trivial physics of the fixed points in terms of non-Fermi liquid phase, diverging thermodynamic quantities, quantum criticality as well as emergent gauge theories.
 \section{Important Properties of the Star Graph}

### 2023-01-04 manuscript/Supplementary/supplementary_mck.tex
--no-message

@@
 \section{Additional Properties of the Star Graph}
+
+\subsection{Partition function of the zero-mode fixed-point Hamiltonian, in the presence of a magnetic field}
+The zero-mode approximation of the fixed-point Hamiltonian is a star graph Hamiltonian:
+\begin{equation}\begin{aligned}
+	H = J^* \vec{S_d}\cdot\vec{s}_\text{tot}
+\end{aligned}\end{equation}
+where \(\vec s_\text{tot} = \sum_l \vec s_l\) is the total spin operator for all the channels.
+We insert a magnetic field that acts only on the impurity and then attempt to diagonalize the Hamiltonian.
+\begin{equation}\begin{aligned}
+	\label{stargraph_field_hamiltonian}
+	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h S_d^z
+\end{aligned}\end{equation}
+The Hamiltonian commutes with \(s_\text{tot}^2\):
+\begin{equation}\begin{aligned}
+\left[s_\text{tot}^2, H(h)\right] = \left[\sum_{i=x,y,z}{s^i_\text{tot}}^2, J^* \sum_{i=x,y,z} S_d^i s^i_\text{tot}\right] = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, \left[s_\text{tot}^i,s_\text{tot}^j\right]\right\} = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, i \epsilon^{ijk}s^k_\text{tot}\right\} = 0
+\end{aligned}\end{equation}
+This means the Hamiltonian is already block-diagonal in the quantum number \(s_\text{tot}\).
+Let us represent the quantum number of \(s_\text{tot}^z\) by \(m\).
+For a particular \(s_\text{tot}\), \(m\) can take values from the set \(\left[-s_\text{tot}, s_\text{tot}\right] \).
+The spin \(S_d^z\) can also take values \(\pm \frac{1}{2}\).
+From now on, we will assume we are in the subspace of a particular \(s_\text{tot} = M\), so we will ignore that quantum number and write the kets simply as \(\ket{S_d^z, m}\).
+So, the notation \(\ket{\uparrow,-1}\) means the state with \(S_d^z = \frac{1}{2}\) and \(m = -1\).
+We will now show that even inside the block of \(2\times s_\text{tot}\) (or \(2\times s_\text{tot} + 1\), depending on where it is odd or even) defined by a particular value of \(s_\text{tot}\), the Hamiltonian actually separates into decoupled \(2\times 2\) blocks.
+To see why, first note that the terminal states \(\ket{\downarrow, -M}\) and \(\ket{\uparrow, M}\) are already eigenstates, because they cannot scatter (the impurity can only flip down, and this would require the bath to flip up, but \(s^z_\text{tot}\) is already at its maximum value \(M\)).
+The other \(2M - 2\) states can be organized into \(2\times 2\) blocks formed by the states \(\ket{\uparrow, m}\) and \(\ket{\downarrow, m+1}\) for \(m \in \left[-M, M-1\right] \).
+The fact that this block does not interact with the other blocks can be observation: if there was some other state which when acted upon by the Hamiltonian gave a non-zero projection on \(\ket{\uparrow, m}\), it would have to come from \(S_d^z = \downarrow\), and this would mean the bath spin would have had to flip down.
+This means the bath spin in that state would have to be \(m+1\), and that is precisely the other state in the block.
+
+Defining \(\epsilon^h_m = \frac{1}{2}\left(Jm + h\right) \) and \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
+\begin{equation}\begin{aligned}
+	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} 
+\end{aligned}\end{equation}
+The eigenvalues are 
+\begin{equation}\begin{aligned}
+	\label{eigenvalue}
+	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}
+\end{aligned}\end{equation}
+where \(\alpha = \epsilon^h_m + J/4\).
+The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\).
+For \(h = 0\), the ground state subspace is \(K-\)fold degenerate and is formed by the negative solutions of eq.~\ref{eigenvalue}.
+This common \(K-\)fold degenerate eigenvalue is \(-J(M+1)/2\).
+The full list of energy eigenvalues at a particular value of \(M\) is
+\begin{equation}\begin{aligned}
+\label{stargraph_spectrum}
+&		JM/2 - h/2, &&\ket{\downarrow, M, -M}, && m = -M\\
+&-J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}, &&\left\{\ket{\uparrow, M, m}, \ket{\downarrow, M, m+1}\right\}, &&m=-M,\ldots,M-1\\
+&JM/2 + h/2, &&\ket{\uparrow, M, M},&& m = M\\
+\end{aligned}\end{equation}
+The eigenstates for each value of \(M,m\) are given by
+\begin{equation}\begin{aligned}
+	\left(\pm\frac{1}{2}\sqrt{J^2 {x_m^M}^2 + 4\alpha^2} - \frac{J}{2}\sqrt{x_m^M}\right)\ket{\uparrow, M, m} + \left(\frac{J}{2}(m+\frac{1}{2}) + \frac{h}{2}\right) \ket{\downarrow, M, m+1}
+\end{aligned}\end{equation}
+
+The partition function is
+\begin{equation}\begin{aligned}
+	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
+	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+\end{aligned}\end{equation}
+where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\).
+This is yet not the complete partition function, because we have not accounted for the possibility that there multiple subspaces of \(M\).
+For example, the \(K=3\) case states can be obtained by adding the third spin-half onto the states \(S=0,1\).
+\(S=0\) gives \(s_\text{tot}=1/2\) and \(S=1\) gives \(s_\text{tot} = 1/2, 3/2\).
+So, \(s_\text{tot} = 1/2\) appears twice.
+These two subspaces are actually orthogonal, because the quantum numbers for the individual channels are different.
+We need to count the number of instances of a particular subspace \(s_\text{tot}=M\).
+It turns out that this number is given by
+\begin{equation}\begin{aligned}
+	r^K_M = {}^{K-1}C_{K/2 - M}
+\end{aligned}\end{equation}
+which means the correct partition function is
+\begin{equation}\begin{aligned}
+	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+\end{aligned}\end{equation}
 
@@
 sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}.
-We find that taking less number of sites leads to a lower value of \(W\), which shows that taking more number of sites will lead to a value of \(W\) that is lower than \(8.3\) and closer to \(8/3\).
+We find that taking less number of sites leads to a {\color{blue} yet higher} value of \(W\), which shows that taking more number of sites will lead to a value of \(W\) that is lower than \(8.3\) and closer to \(8/3\).
 

### 2023-01-04 manuscript/mscript_mck_full.tex
--no-message

@@
 Using conformal field theory~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005}, bosonization~\cite{emery_kivelson,clarke_giamarchi_1993,zarand_2000,vondelft_prl_1998,schofield_1997}, numerical renormalization group~\cite{bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991}, Bethe ansatz~\cite{andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002} and other methods~\cite{sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}, it has been shown that for the over-screened systems \(\left(K > 2S_d\right)\), the low energy physics is of the non-Fermi liquid type obtained at an intermediate coupling fixed point of the RG flows~\cite{Noz_blandin_1980}.
-Further, the system displays anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (upon ensuring that temperature is taken to zero before the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
+Further, the system displays anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (upon ensuring that temperature is taken to zero {\color{blue} after} the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
 This anomalous divergent behaviour is a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: the ground state is susceptible to perturbations that introduce channel anisotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}.

### 2023-01-05 manuscript/Supplementary/supplementary_mck.tex
completed magnetisation and phase shift

@@
 This common \(K-\)fold degenerate eigenvalue is \(-J(M+1)/2\).
-The full list of energy eigenvalues at a particular value of \(M\) is
+The full list of energy eigenvalues at a particular value of \(M\) (characterised by the total spin operator \(J^z = S_d^z + s_\text{tot}^z\)) is
 \begin{equation}\begin{aligned}
 \label{stargraph_spectrum}
-&		JM/2 - h/2, &&\ket{\downarrow, M, -M}, && m = -M\\
-&-J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}, &&\left\{\ket{\uparrow, M, m}, \ket{\downarrow, M, m+1}\right\}, &&m=-M,\ldots,M-1\\
-&JM/2 + h/2, &&\ket{\uparrow, M, M},&& m = M\\
+&		JM/2 - h/2, &&\ket{J=M+\frac{1}{2},J^z=-M-\frac{1}{2},s_\text{tot}=M}, && m = -M\\
+&-J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}, &&\ket{J=M-\frac{1}{2},J^z=m+\frac{1}{2},s_\text{tot}=M}, &&m=-M,\ldots,M-1\\
+&JM/2 + h/2, &&\ket{J=M+\frac{1}{2},J^z=M+\frac{1}{2},s_\text{tot}=M},&& m = M\\
 \end{aligned}\end{equation}
-The eigenstates for each value of \(M,m\) are given by
+The eigenstates for each value of \(M,m\) in the \(J=M-\frac{1}{2}\) sector are given by
 \begin{equation}\begin{aligned}
-	\left(\pm\frac{1}{2}\sqrt{J^2 {x_m^M}^2 + 4\alpha^2} - \frac{J}{2}\sqrt{x_m^M}\right)\ket{\uparrow, M, m} + \left(\frac{J}{2}(m+\frac{1}{2}) + \frac{h}{2}\right) \ket{\downarrow, M, m+1}
+	\ket{M-\frac{1}{2},m+\frac{1}{2},M} =\mathcal{C}_\pm \ket{\uparrow, M, m} \pm \sqrt{1 - \mathcal{C}_\pm^2} \ket{\downarrow, M, m+1}, ~ ~ \mathcal{C}_\pm = \frac{J\sqrt{x_m^M}/2}{\sqrt{J^2 x_m^M/4 + \left(\alpha \mp \sqrt{\alpha^2 + J^2 x_m^M/4}\right)^2 }}
 \end{aligned}\end{equation}
-
-The partition function is
+The partition function is given by
 \begin{equation}\begin{aligned}
-	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
-	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+	Z(h) = \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
 \end{aligned}\end{equation}
@@
 	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+\end{aligned}\end{equation}
+
+\subsection{Features of the polarised ground-states}
+Of particular importance within the ground-state subspace are the zero-field maximally-polarised states, obtained by choosing \(M = \frac{K}{2}, m + \frac{1}{2}= \pm \left( M - \frac{1}{2} \right) =\pm \frac{1}{2}\left(K-1\right)\):
+\begin{equation}\begin{aligned}
+	\ket{J=\frac{K-1}{2},J^z= \frac{\sigma}{2}\left(K-1\right),s_\text{tot}=\frac{K}{2}} = \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma(\frac{K}{2}-1)} - \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma\frac{K}{2}},
+\end{aligned}\end{equation}
+where \(\sigma\) can take values \(\pm 1\) and \(\ket{\sigma}_d\) represents the up and down configurations of the impurity spin.
+The state \(\ket{s_\text{tot}^z=\frac{\sigma K}{2}}\) has all the bath spins pointing in the \(\sigma-\)direction: \(\ket{s_\text{tot}^z=\frac{\sigma K}{2}} = \ket{\sigma,\sigma,\ldots,\sigma} (\sigma=\uparrow \text{ or }\downarrow)\), where the notation is such that a particular symbol (say \(\uparrow\)) at the \(i^\text{th}\) position indicates the configuration of the \(i^\text{th}\) channel.
+The other state \(\ket{s_\text{tot}^z=\sigma(\frac{K}{2} - 1)}\) can be obtained by flipping any one out of the \(K\) spins in the previous state \(\ket{s_\text{tot}^z=\frac{\sigma K}{2}}\), leading to the normalised state \(\ket{s_\text{tot}^z=\sigma(\frac{K}{2} - 1)} = \frac{1}{\sqrt K}\ket{\bar\sigma,\sigma,\ldots,\sigma} + \frac{1}{\sqrt K}\ket{\sigma,\bar\sigma,\ldots,\sigma} + \ldots + \frac{1}{\sqrt K}\ket{\sigma,\sigma\ldots,\bar\sigma}\), a linear combination of all possible states with the spin of one channel in \(\bar\sigma(=-\sigma)\) direction and all other channels remaining in the \(\sigma\) direction.
+With these in mind, the polarised state can be cast in the more explicit form
+\begin{equation}\begin{aligned}
+	\hspace*{-15pt}\ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} \left[\ket{\sigma}_d\otimes\left(\ket{\bar\sigma,\sigma,\ldots,\sigma} + \ket{\sigma,\bar\sigma,\ldots,\sigma} + \ldots + \ket{\sigma,\sigma\ldots,\bar\sigma}\right) - K\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\right].\label{polarised-state}
+\end{aligned}\end{equation}
+
+In order to make the frustration faced by the impurity manifest, we now rewrite these polarised states in the form of superpositions of zero magnetisation singlet states.
+Let us define the singlet state \(\ket{\text{SS}_{d,l}} = \frac{1}{\sqrt 2}\left(\ket{\uparrow}_d\ket{\downarrow}_l - \ket{\downarrow}_d\ket{\uparrow}_l\right),l\in[1,K]\), between the impurity spin and the \(l^\text{th}\) channel, where \(\ket{\cdot}_l\) represents the configuration of the spin in the \(l^\text{th}\) channel.
+The polarised states can then be written as
+\begin{equation}\begin{aligned}
+	\ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} \sum_{l=1}^K\ket{\sigma}_d\otimes\left[\ket{\bar\sigma}_l - \ket{\sigma}_l\right] \otimes\ket{\sigma,\ldots,\sigma}_{l^\prime} = \frac{\sqrt 2}{\sqrt{K(1 + K)}} \sum_{l=1}^K \ket{\text{SS}_{d,l}}\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}.\label{singlet-chain}
+\end{aligned}\end{equation}
+This form of the state shows that the impurity is trying to participate, simultaneously, in forming \(K\) number of singlets.
+Put differently, the presence of \(K\) singlets shows that all \(K\) channels are trying to screen the impurity simultaneously.
+However, the presence of an overall non-zero magnetisation in the states means that the screening is only partial.
+
+From these polarised states, one can now calculate the ``excess charge" supplied by the impurity site to the conduction bath in the form of gapless excitations.
+For this, we first note that the form Eq.~\ref{singlet-chain} of the polarised state shows that all the individual terms in the more explicit form of Eq.~\ref{polarised-state} involve the impurity hybridising with the bath.
+In Eq.~\ref{polarised-state}, each term of the form \(\ket{\sigma}_d\otimes\ket{\bar\sigma}_l\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}\) participates in exactly one singlet \(\ket{\text{SS}_{d,l}}\) and therefore involves hybridisation between the impurity and only the \(l^\text{th}\) channel.
+Each such term therefore contributes an excess charge \(n_\text{exc}^{(l)}\) of unity to the \(l^\text{th}\) conduction channel and none to the other channels: \(n_\text{exc}^{(l)} = 1 = 1 - n_\text{exc}^{(l^\prime)}\).
+The final term \(\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\) in Eq.~\ref{polarised-state} participates in all \(K\) singlets, and therefore involves hybridisation with all the channels.
+This term therefore contributes the entire excess charge of unity across all the channels, which results in an excess charge contribution of \(n_\text{exc}^{(l)}=1/K\) to each channel.
+With these in mind, the total excess charge contributed to each channel from the state in Eq.~\ref{polarised-state} is
+\begin{equation}\begin{aligned}
+	n_\text{exc}^{(l)} = \frac{1}{K(1+K)}\left[1 + K^2 \times \frac{1}{K}\right] = \frac{1}{K}
 \end{aligned}\end{equation}

### 2023-01-05 manuscript/mscript_mck_full.tex
completed magnetisation and phase shift

@@
-\documentclass[reprint,prb,superscriptaddress]{revtex4-2}
+\documentclass[superscriptaddress]{revtex4-2}
 \usepackage{braket,amsmath,amssymb,graphicx,float,color,ulem,soul,lipsum}
@@
 \label{sec:imp_suscept}
-In order to obtain the magnetic susceptibility, we insert a magnetic field that acts only on the impurity and then diagonalize the Hamiltonian
+The impurity magnetic susceptibility can be obtained by diagonalising the zero-mode Hamiltonian \(H(h)\) in the presence of a local magnetic field \(h\) on the impurity:
 \begin{align}
@@
 \end{align}
-The Hamiltonian commutes with \(S\), so it is already block-diagonal in terms of the eigenvalues \(M\) of \(S\).
+The Hamiltonian commutes with \(\vec S\), so it is already block-diagonal in terms of the eigenvalues \(M\) of \(S\).
 \(M\) takes values in the range \(\left[M_\text{min}, M_\text{max}\right]\), where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(\frac{1}{2}\).
+The diagonalisation of the Hamiltonian is shown in the Supplementary Materials~\cite{SM}.
 Defining \(\alpha = \frac{1}{2}\left({\mathcal{J}}m + h\right) + \frac{{\mathcal{J}}}{4}\) and \(x^M_m = M(M+1) - m(m+1)\), the partition function can be written as
@@
 \end{align}
-where the \(\prime\) indicates derivative with respect to \(h\). At low temperatures, the derivatives are 
-\begin{align}
-	Z &\to 2 r^K_{M_\text{max}} M_\text{max} e^{\beta \frac{J}{2}(M_\text{max} + 1)}~,\\
-	Z^{\prime \prime} &\to r^K_{M_\text{max}}\left(\frac{\beta }{2(M_\text{max} + \frac{1}{2})}\right)^2 e^{\beta \frac{J}{2}(M_\text{max} + 1)}\Sigma_{M_\text{max}}~,
-\end{align}
-such that the susceptibility is
+where the \(\prime\) indicates derivative with respect to \(h\). At low temperatures, the susceptibility takes the form
 \begin{equation}
@@
 A similar divergence is also seen in the susceptibility of the outer spins, calculated by inserting a magnetic field purely on the outer spins.
-
-A second non-analyticity arises when we consider the impurity free energy and the magnetization. The thermal free energy is given by
-\begin{equation}\begin{aligned}
-	F(h) = -\frac{1}{\beta}\ln Z(h) = -\frac{1}{\beta}\ln\sum_{E_n}e^{-\beta E_n}~.
-\end{aligned}\end{equation}
-At \(T \to 0\), only the most negative energy \(E_\text{min}\) survives. The minimal energy eigenvalue is
-\begin{equation}\begin{aligned}
-	E_\text{min} = - \frac{J}{4} - \frac{1}{2}\sqrt{J^2(K+1)^2/4 + h^2 + |h|J(K-1)}~.
-\end{aligned}\end{equation}
-The first derivative of the free energy with respect to the field gives
-\begin{equation}\begin{aligned}
-	F^\prime(h\neq 0, T\to 0) =- \frac{2h + J(K-1)\text{sign}(h)}{4\sqrt{\frac{J^2}{4}(K+1)^2 + h^2 + |h|J(K-1)}}~.
-\end{aligned}\end{equation}
-There we used the result that the derivative of \(|x|\) is \(\text{sign}(x)\). If we now take \(h\) to zero from both directions, we get the magnetization of the impurity
-\begin{equation}\begin{aligned}
-	m = F^\prime(h \to 0^\pm, T\to 0) = \mp \frac{1}{2}\frac{(K-1)}{(K+1)}~.
-\end{aligned}\end{equation}
+Some additional results regarding susceptibility are presented in the Supplementary Materials~\cite{SM}.
+
+Departure from single-channel behaviour is most apparent in the presence of the highly polarised states \(\ket{J^z=\pm \frac{K-1}{2}}\) in the ground-state spectrum,
+\begin{equation}\begin{aligned}
+	\ket{J^z=\sigma \frac{K-1}{2}} = \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{S^z=\sigma(\frac{K}{2}-1)} - \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{S^z=\sigma\frac{K}{2}}~, ~ ~ \sigma=\pm 1~,
+\end{aligned}\end{equation}
+where \(\ket{\sigma}_d\) represents the up and down configurations of the impurity spin and \(\ket{S^z}\) represents the configuration of the bath spins.
+These states lead to large unquenched magnetisation at zero temperatures.
+These states lead to singular behaviour of the impurity magnetisation in vanishing field, \(m(h=0^\pm)\).
+In the presence of a field, the ground-state becomes unique: \(\ket{\psi}_\text{gs}(h) = \theta(h)\ket{J^z=\frac{K-1}{2}} + \theta(-h)\ket{J^z=-\frac{K-1}{2}}\), and the impurity magnetisation can be calculated from the state:
+\begin{equation}\begin{aligned}
+	m(h=0^\pm) = \theta(h)\bra{J^z=\frac{K-1}{2}} S_d^z \ket{J^z=\frac{K-1}{2}} + \theta(-h)\bra{J^z=-\frac{K-1}{2}}S_d^z\ket{J^z=-\frac{K-1}{2}} = \pm  \frac{1}{2} \frac{1-K}{1 + K}
+\end{aligned}\end{equation}
+
 \begin{figure}[!htpb]
@@
 
-The magnetization is therefore discontinuous as \(h\to 0\).
-The non-analyticity for \(K>1\) occurs because there is at least one pair of ground state with non-zero parity \(\pi^z\) and magnetic field is able to flip one ground state into the state of opposite parity.
+The magnetization is therefore discontinuous as \(h\to 0\) when \(K>1\).
+The non-analyticity occurs because the magnetic field is able to flip the \(J^z=\pm (K-1)/2\) state into the state of the opposite magnetisation.
 This available space for scattering is simply the frustration that we discussed earlier.
 Indeed, we have checked (see Fig.~\ref{mag_crit}) by diagonalising numerically the star graph Hamiltonian that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S_{d}\) is the deviation from exact screening.
-Some additional results are presented in the Supplementary Materials~\cite{SM}.
+
+These polarised states can also be used to obtain the scattering phase shift suffered by the conduction channels at the Fermi surface.
+As shown in the Supplementary Materials~\cite{SM}, the impurity-bath hybdridisation in the polarised states contribute an excess charge of \(n_\text{exc}^{(l)} = 1/K\) to each conduction channel.
+Following Friedel's sum rule, this leads to a total scattering phase shift of \(\pi/K\) for each channel:
+\begin{equation}\begin{aligned}
+	\delta^{(l)} = \pi n_\text{exc}^{(l)} = \frac{\pi}{K}, ~ ~ l \in \left[1, K\right] 
+\end{aligned}\end{equation}
+In later parts of the work, we will show that this phase shift are linked to the critical non-Fermi liquid exponents of thermodynamic quantities at the fixed point.
+
 \subsection{Topological properties of ground state manifold}

### 2023-01-05 manuscript/mscript_mck_full.tex
add delta and m relation

@@
 \usepackage[hidelinks]{hyperref}
-\bibliographystyle{apsrev4-2}
+\bibliographystyle{apsrev4-1}
 \begin{document}
@@
 \begin{equation}\begin{aligned}
-	m(h=0^\pm) = \theta(h)\bra{J^z=\frac{K-1}{2}} S_d^z \ket{J^z=\frac{K-1}{2}} + \theta(-h)\bra{J^z=-\frac{K-1}{2}}S_d^z\ket{J^z=-\frac{K-1}{2}} = \pm  \frac{1}{2} \frac{1-K}{1 + K}
+	m(h=0^\pm) = \theta(h)\bra{J^z=\frac{K-1}{2}} S_d^z \ket{J^z=\frac{K-1}{2}} + \theta(-h)\bra{J^z=-\frac{K-1}{2}}S_d^z\ket{J^z=-\frac{K-1}{2}} = \pm  \frac{1}{2} \frac{1-K}{1 + K}\label{imp-magnetisation}~.
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-In later parts of the work, we will show that this phase shift are linked to the critical non-Fermi liquid exponents of thermodynamic quantities at the fixed point.
+For \(K > 1\), each channel therefore experiences an unrenormalised phase shift of value between \(0\) and \(\pi\) that, as we will show in a later section, is responsible for the non-Fermi liquid behaviour.
+For example, we will show that this phase shift are linked to the critical non-Fermi liquid exponents of thermodynamic quantities at the fixed point.
+Right now, some evidence of this role of the phase shift can be provided through its relation to the vanishing field impurity magnetisation \(m\) obtained in eq.~\ref{imp-magnetisation}:
+\begin{equation}\begin{aligned}
+	m(h=0^\pm) = \pm \frac{1}{2} \frac{\delta^{(l)} - \pi}{\delta^{(l)} + \pi}~.
+\end{aligned}\end{equation}
+When the phase shift \(\delta^{(l)}\) acquires a fractional value (in units of \(\pi\)), the impurity magnetisation also becomes fractional (in units of \(\frac{1}{2}\)).
+This shows that the unrenormalised phase shift value \(0 < \delta^{(l)} < \pi\) is at the heart of the quantum frustration present in the star graph (and therefore the MCK problem) that neither allows the impurity to be screened, nor allows it to decouple from the conduction channels.
+The decoupling only happens in the limit of extreme screening \((K \to \infty)\), and the impurity spin then becomes a local moment.
 

### 2023-01-05 manuscript/mscript_mck_full.tex
changed layout to JPCM

@@
-\documentclass[superscriptaddress]{revtex4-2}
-\usepackage{braket,amsmath,amssymb,graphicx,float,color,ulem,soul,lipsum}
-\usepackage[hidelinks]{hyperref}
-\bibliographystyle{apsrev4-1}
+\documentclass{iopart}
+\usepackage{iopams}  
+\usepackage{braket,graphicx,amsmath,hyperref}
+\bibliographystyle{unsrt}
 \begin{document}
@@
 \title{Frustration shapes multi-channel Kondo physics: a star graph perspective}
-\author{Siddhartha Patra}
-\email{sp14ip022@iiserkol.ac.in }
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-\author{Abhirup Mukherjee}
-\email{am18ip014@iiserkol.ac.in }
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-\author{Anirban Mukherjee}
-\email{mukherjee.anirban.anirban@gmail.com }
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-%\affiliation{Ames Laboratory, Ames, Iowa 50011, USA}
-\author{N. S. Vidhyadhiraja}
-\email{raja@jncasr.ac.in}
-\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
-\author{A. Taraphder}
-\email{arghya@phy.iitkgp.ernet.in}
-\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
-\author{Siddhartha Lal}
-\email{slal@iiserkol.ac.in}
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
+\author{Siddhartha Patra$^1$, Abhirup Mukherjee$^1$, Anirban Mukherjee$^1$, N. S. Vidhyadhiraja$^4$, A. Taraphder$^5$ and Siddhartha Lal$^1$}
+\eads{\mailto{sp14ip022@iiserkol.ac.in}, \mailto{am18ip014@iiserkol.ac.in}, \mailto{mukherjee.anirban.anirban@gmail.com}, \mailto{raja@jncasr.ac.in}, \mailto{arghya@phy.iitkgp.ernet.in}, \mailto{slal@iiserkol.ac.in}}
+
+\address{$^1$Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
+
+\address{$^4$Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
+
+\address{$^5$Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
+
 \date{\today}
+
 \begin{abstract}
@@
 
-\maketitle
-
-%\tableofcontents
+% \maketitle
+
+\ioptwocol
 
@@
 Using conformal field theory~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,parcollet_olivier_large_N,affleck_2005}, bosonization~\cite{emery_kivelson,clarke_giamarchi_1993,zarand_2000,vondelft_prl_1998,schofield_1997}, numerical renormalization group~\cite{bullaNRGreview,affleck_pang_cox_1992,pang_cox_1991}, Bethe ansatz~\cite{andrei_destri_1984,Tsvelick1984,Tsvelick_1985,andrei_jerez_1995,zarand_costi_2002} and other methods~\cite{sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}, it has been shown that for the over-screened systems \(\left(K > 2S_d\right)\), the low energy physics is of the non-Fermi liquid type obtained at an intermediate coupling fixed point of the RG flows~\cite{Noz_blandin_1980}.
-Further, the system displays anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (upon ensuring that temperature is taken to zero {\color{blue} after} the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
+Further, the system displays anomalous behaviour in thermodynamic properties near \(T=0\) and a fractional zero temperature entropy in the thermodynamic limit (upon ensuring that temperature is taken to zero after the system size is taken to infinity~\cite{rozhkov_1998,vondelft_prl_1998}).
 This anomalous divergent behaviour is a signature of the fact that the MCK system with a single channel-symmetric exchange coupling is quantum critical: the ground state is susceptible to perturbations that introduce channel anisotropy in the exchange couplings~\cite{Noz_blandin_1980,andrei_jerez_1995,affleck_pang_cox_1992,zarand_2000,zheng_2021}.
@@
 
-The importance of ground state degeneracy and quantum-mechanical frustration in the MCK problem has not received sufficient attention, even though they play crucial roles in determining the quantum criticality and associated non-Fermi liquid physics of the system.
+The importance of ground state degeneracy and quantum-mechanical \textit{frustration} in the MCK problem has not received sufficient attention, even though they play crucial roles in determining the quantum criticality and associated non-Fermi liquid physics of the system.
 This is, at least partially, due to the lack of an intermediate-coupling effective Hamiltonian that describes the low-energy physics of the MCK (i.e., reveals the nature of the excitations).
-\textit{Frustration} in this context refers to the inability of the impurity spin to bind with the conduction channels, and be screened completely by forming a maximally-entangled singlet ground state.
+Frustration in this context refers to the inability of the impurity spin to bind with the conduction channels, and be screened completely by forming a maximally-entangled singlet ground state.
 The absence of such frustration in the single-channel spin-1/2 Kondo model (and more generally, the exact screening variant of the MCK) means that imperfect screening \((K \neq 2S_d)\) leads to dramatic differences in the multi-channel models.
@@
 We start with the \(K\)- conduction channel Kondo model Hamiltonian with isotropic couplings \cite{Noz_blandin_1980}:
-\begin{gather}
+\begin{eqnarray}
 	\label{mc_ham}
 	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\alpha^\prime= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~,~~
-\end{gather}
-where \(\mathcal{J}\) is the Kondo spin-exchange coupling, \(c_{k\alpha,l}\) is the fermionic field operator at momentum \(k\), spin \(\alpha\) and channel \(l\), \(\epsilon_{k,l}\) represents the dispersion of the \(l^\text{th}\) conduction channel, \(\vec \sigma\) is the vector of Pauli matrices and \(\vec S_d = \frac{1}{2}\vec \sigma_d\) is the impurity spin operator.
+\end{eqnarray}
+where \(\mathcal{J}\) is the Kondo spin-exchange coupling, \(c_{k\alpha,l}\) is the fermionic field operator at momentum \(k\), spin \(\alpha\) and channel \(l\), \(\epsilon_{k,l}\) represents the dispersion of the \(l^\mathrm{th}\) conduction channel, \(\vec \sigma\) is the vector of Pauli matrices and \(\vec S_d = \frac{1}{2}\vec \sigma_d\) is the impurity spin operator.
 Here, \(l\) sums over the \(K\) channels of the conduction bath, \(k,k^\prime\) sum over all the momentum states of the bath and \(\alpha,\alpha^\prime\) sum over the two spin indices of a single electron.
@@
 At the $j^{th}$ RG step, we focus on decoupling the highest energy electronic state denoted by $\ket{j}$.
-%Given the most energetic electronic state at the \(j^\text{th}\) RG step is \(\ket{j}\) and defined by the energy \(D_{(j)}\), 
+%Given the most energetic electronic state at the \(j^\mathrm{th}\) RG step is \(\ket{j}\) and defined by the energy \(D_{(j)}\), 
 The Hamiltonian will in general not conserve the number of particles in this state: \(\left[H_{(j)}, \hat n_{j}\right] \neq 0\), and the unitary transformation \(U_{(j)}\) causes this number fluctuation to vanish
@@
 ~\cite{anirbanurg1,anirbanurg2}:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}~, ~\left[H_{(j-1)}, \hat n_{j}\right] =0~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 The unitary transformations are given in terms of a fermionic generator \(\eta_{(j)}\)~\cite{anirbanurg1,anirbanurg2}:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{unitary}
 	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ \quad\left\{ \eta_{(j)},\eta_{(j)}^\dagger \right\} = 1~,
-\end{aligned}\end{equation}
+\end{eqnarray}
 where \(\left\{\cdot\right\}\) is the anticommutator.
@@
 
-The generator itself is given by the expression~\cite{anirbanurg1,anirbanurg2}
-\begin{equation}\begin{aligned}
+The generator itself is given by ~\cite{anirbanurg1,anirbanurg2}
+\begin{eqnarray}
 	\label{eta_dag}
-	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \text{Tr}\left(H_{(j)}c_{j}\right)~.
-\end{aligned}\end{equation}
+	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \mathrm{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \mathrm{Tr}\left(H_{(j)}c_{j}\right)~.
+\end{eqnarray}
 The operators \(\eta_{(j)},\eta^\dagger_{(j)}\) can be thought of as the many-particle analogue of the single-particle field operators \(c_j,c^\dagger_j\) that change the occupation number of the single-particle Fock space, \(\ket{n_j}\).
 The presence of the operators in $\eta_{(j)}$ other than $c_j$ are required to ensure that the decoupling of the specific Fock state under consideration is carried out through a unitary modification of the spectrum of the remnant degrees of freedom.
-Since the \(j^\text{th}\) degree of freedom is coupled with many others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\); this is encoded within the \(\text{Tr}\left(H_{(j)} c_j\right) \) term.
+Since the \(j^\mathrm{th}\) degree of freedom is coupled with many others, a rotation of the basis of \(j\) also involves a rotation of the many-particle basis of the remaining degrees of freedom in the Hamiltonian \(H_{(j)}\); this is encoded within the \(\mathrm{Tr}\left(H_{(j)} c_j\right) \) term.
 The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms in the Hamiltonian:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 \(H^i_{(j)}\) is that part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does not commute with at least one \(\hat n_l\) for \(l < j\).
 The RG flow continues till a fixed point is reached at an energy \(D^*\).
-The Greens function in front of $c_j$ (in Eq.~\ref{eta_dag}) accounts for the dynamical cost of this rotation in terms of an operator for quantum fluctuations (\(\hat \omega\)), as well as the kinetic and self-energies \(\text{Tr}\left( H_{(j)}\hat n_j \right) \).
+The Greens function in front of $c_j$ (in Eq.~\ref{eta_dag}) accounts for the dynamical cost of this rotation in terms of an operator for quantum fluctuations (\(\hat \omega\)), as well as the kinetic and self-energies \(\mathrm{Tr}\left( H_{(j)}\hat n_j \right) \).
 
@@
 The derivation of the RG equation for the over-screened regime \((2S < K)\) of the spin-\(S\)-impurity \(K\)-channel Kondo problem is shown in detail in the Supplementary Materials~\cite{SM}.
-On decoupling circular isoenergetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\text{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
-\begin{equation}\begin{aligned}
+On decoupling circular isoenergetic shells at energies \(D_{(j)}\), the change in the Kondo coupling at the \(j^\mathrm{th}\) RG step, \(\Delta {\mathcal{J}}_{(j)}\), is given by
+\begin{eqnarray}
 	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{1}{2}\rho {\mathcal{J}}_{(j)} K \right)~,
-\end{aligned}\end{equation}
+\end{eqnarray}
 where \(\mathcal{N}_{(j)}\) is the number of electronic states at the energy shell \(D_{(j)}\).
@@
 The fixed point Hamiltonian takes the form
-\begin{equation}\begin{aligned}
-	H^* = \sum_l\left[ \sum^*_{k}\epsilon_{k,l} \hat n_{k\alpha,l} + {\mathcal{J}}\sum_{kk^\prime\atop{\alpha,\alpha^\prime}}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\right]~.
-\end{aligned}\end{equation}
+\begin{eqnarray}
+	H^* = \sum_l\left[ \sum^*_{k}\epsilon_{k,l} \hat n_{k\alpha,l} + {\mathcal{J}}\sum_{kk^\prime\atop{\alpha,\alpha^\prime}}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\right].~ ~ ~ ~
+\end{eqnarray}
 We have not explicitly written the decoupled degrees of freedom \(D_{(j)} > D^*\) in the Hamiltonian.
@@
 Upon setting the chemical potential equal to the Fermi energy, the kinetic energy part vanishes and the zero bandwidth model becomes a Heisenberg spin-exchange Hamiltonian
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{star graph}
 	H^* = {\mathcal{J}}\sum_l\sum_{kk^\prime,\atop{\alpha,\alpha^\prime}}^* \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l} = {\mathcal{J}}\vec{S_d}\cdot\vec S~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 At the last step, we defined the total bath local spin operator \(S = \sum_l \vec{S}_l = \frac{1}{2}\sigma_l = \frac{1}{2}\sum_{kk^\prime}^*\sum_{\alpha\alpha^\prime}\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\).
@@
 The star graph commutes with several operators, including the total spin operator \(J^z = S_d^z + S^z\) along \(z\), the square of the total bath local spin operator (\(S^2\)) and the string operators
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 \pi^{x,y,z} = \sigma_d^{x,y,z} \otimes_{l=1}^K \sigma_l^{x,y,z}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 If we define the global spin operator \(\vec J = \vec S + \vec S_d\), the star graph Hamiltonian can be written as \(\frac{1}{2}\mathcal{J}\left[J^2 - S_d^2 - S^2\right] \).
@@
 	\item The ground state is achieved for the maximal value of \(S\), \(S=\frac{K}{2}\), and the corresponding minimal value of \(J\), \(J = |\frac{K}{2} - S_d|\). The ground state energy is therefore 
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 \label{ground-state-energy}
@@
 = \begin{cases}
-	-\mathcal{J}S_d\left(\frac{K}{2} + 1\right) & \text{ when } K \geq 2S_d, ~\text{ and}\\
-	-\mathcal{J}\frac{K}{2}\left(S_d + 1\right) & \text{ otherwise}~.
+	-\mathcal{J}S_d\left(\frac{K}{2} + 1\right) & \mathrm{ when } K \geq 2S_d, ~\mathrm{ and}\\
+	-\mathcal{J}\frac{K}{2}\left(S_d + 1\right) & \mathrm{ otherwise}~.
 \end{cases}
-\end{aligned}\end{equation}
+\end{eqnarray}
 	\item The value of \(J\) corresponds to a multiplicity of \(2J+1 = |K - 2S_d|+1\) in \(J^z\), and since the Hamiltonian does not depend on \(J^z\), these orthogonal states \(\ket{J^z}\) constitute a degeneracy of \(g^{S_d}_K = |K - 2S_d|+1\).
@@
 Interestingly, {the string operator \(\pi^z\) is a Wilson loop operator~\cite{fradkin2013field} that wraps around all the nodes of the star graph}:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{w_loop}
 	\pi^z = \exp\left[i \frac{\pi}{2} \left(\sigma_d^z + \sum_{l=1}^K \sigma^z_l - K\right)\right] = e^{i \pi \left(J^z - \frac{1}{2}K\right)}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 \(\pi^x\) and \(\pi^y\) are 't Hooft operators~\cite{fradkin2013field} and mix states of opposite parity. For example, it can be shown that \(\pi^x \ket{J^z} = -\ket{J^z}\).
@@
 The expectation value is calculated in the ground state.
-Since the inner product is simply the ground state energy of a spin-\(S_{d}\) impurity \(K-\)channel MCK model in units of the exchange coupling \(J\), we have \(\Gamma = \frac{1}{2} \left[ l_\text{imp}^2 + l_c^2 - g^S_K\left( g^S_K - 1 \right)\right]\), where \(l_\text{imp}^2 = S_d(S_d+1)\) is the length-squared of the impurity spin.
+Since the inner product is simply the ground state energy of a spin-\(S_{d}\) impurity \(K-\)channel MCK model in units of the exchange coupling \(J\), we have \(\Gamma = \frac{1}{2} \left[ l_\mathrm{imp}^2 + l_c^2 - g^S_K\left( g^S_K - 1 \right)\right]\), where \(l_\mathrm{imp}^2 = S_d(S_d+1)\) is the length-squared of the impurity spin.
 Similarly, \(l_c^2 = \frac{K}{2}\left(\frac{K}{2} + 1\right) \) is the length-squared of the total conduction bath spin.
@@
 In terms of \(K_0\) and \(\delta\), the degree of compensation becomes
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{gamma}
 	\Gamma = \frac{1}{4}\left[\left( K_0 + 1 \right) ^2 - \left(|\delta| + 1 \right) ^2\right]~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 {For a given \(K_0\), the degree of compensation $\Gamma$ is maximised for exact screening \(\delta=0\), and is reduced for \(\delta \neq 0\) (see Fig.\ref{compen}).
@@
 The impurity magnetic susceptibility can be obtained by diagonalising the zero-mode Hamiltonian \(H(h)\) in the presence of a local magnetic field \(h\) on the impurity:
-\begin{align}
+\begin{eqnarray}
 	\label{star graph_field_hamiltonian}
 	H(h) = {\mathcal{J}^*} \vec{S_d}\cdot\vec{S} + h S_d^z~.
-\end{align}
+\end{eqnarray}
 The Hamiltonian commutes with \(\vec S\), so it is already block-diagonal in terms of the eigenvalues \(M\) of \(S\).
-\(M\) takes values in the range \(\left[M_\text{min}, M_\text{max}\right]\), where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(\frac{1}{2}\).
+\(M\) takes values in the range \(\left[M_\mathrm{min}, M_\mathrm{max}\right]\), where \(M_\mathrm{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\mathrm{min} = 0\)  if \(K\) is even, otherwise \(\frac{1}{2}\).
 The diagonalisation of the Hamiltonian is shown in the Supplementary Materials~\cite{SM}.
@@
 \begin{eqnarray}
-Z(h) &=&\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\bigg[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \frac{{\mathcal{J}}}{4}}\cosh \beta\sqrt{{\mathcal{J}}^2x^M_m/4 + \alpha^2} \nonumber\\
-&&\hspace{2cm}+ 2e^{-\beta {\mathcal{J}}M/2}\cosh \beta h/2\bigg]~.
+	Z(h) =\sum_{M=M_\mathrm{min}}^{M_\mathrm{max}}r^K_M\bigg[&\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \frac{{\mathcal{J}}}{4}}\cosh \beta\sqrt{{\mathcal{J}}^2x^M_m/4 + \alpha^2} \nonumber\\
+& + 2e^{-\beta {\mathcal{J}}M/2}\cosh \beta h/2\bigg]~.
 \end{eqnarray}
@@
 To calculate the impurity magnetic susceptibility, we will use the expression
-\begin{align}
+\begin{eqnarray}
 	\chi = \frac{1}{\beta}\lim_{h \to 0}\left[\frac{Z^{\prime\prime}(h)}{Z(h)} - \left(\frac{Z^{\prime}(h)}{Z(h)}\right)^2 \right] ~,
-\end{align}
+\end{eqnarray}
 where the \(\prime\) indicates derivative with respect to \(h\). At low temperatures, the susceptibility takes the form
 \begin{equation}
-	\chi \to \frac{\beta\Sigma_\text{max}}{2M_\text{max}\left(2M_\text{max}+1\right)^2} = \frac{\beta(K-1)}{12(K+1)} \sim \frac{1}{T}~.
+	\chi \to \frac{\beta\Sigma_\mathrm{max}}{2M_\mathrm{max}\left(2M_\mathrm{max}+1\right)^2} = \frac{\beta(K-1)}{12(K+1)} \sim \frac{1}{T}~.
 \end{equation}
@@
 Departure from single-channel behaviour is most apparent in the presence of the highly polarised states \(\ket{J^z=\pm \frac{K-1}{2}}\) in the ground-state spectrum,
-\begin{equation}\begin{aligned}
-	\ket{J^z=\sigma \frac{K-1}{2}} = \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{S^z=\sigma(\frac{K}{2}-1)} - \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{S^z=\sigma\frac{K}{2}}~, ~ ~ \sigma=\pm 1~,
-\end{aligned}\end{equation}
-where \(\ket{\sigma}_d\) represents the up and down configurations of the impurity spin and \(\ket{S^z}\) represents the configuration of the bath spins.
+\begin{eqnarray}
+	\ket{J^z=\sigma \frac{K-1}{2}} =& \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{S^z=\sigma(\frac{K}{2}-1)} \nonumber\\
+					&- \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{S^z=\sigma\frac{K}{2}},
+\end{eqnarray}
+where \(\sigma=\pm 1\) and \(\ket{\sigma}_d\) represents the up and down configurations of the impurity spin and \(\ket{S^z}\) represents the configuration of the bath spins.
 These states lead to large unquenched magnetisation at zero temperatures.
 These states lead to singular behaviour of the impurity magnetisation in vanishing field, \(m(h=0^\pm)\).
-In the presence of a field, the ground-state becomes unique: \(\ket{\psi}_\text{gs}(h) = \theta(h)\ket{J^z=\frac{K-1}{2}} + \theta(-h)\ket{J^z=-\frac{K-1}{2}}\), and the impurity magnetisation can be calculated from the state:
-\begin{equation}\begin{aligned}
-	m(h=0^\pm) = \theta(h)\bra{J^z=\frac{K-1}{2}} S_d^z \ket{J^z=\frac{K-1}{2}} + \theta(-h)\bra{J^z=-\frac{K-1}{2}}S_d^z\ket{J^z=-\frac{K-1}{2}} = \pm  \frac{1}{2} \frac{1-K}{1 + K}\label{imp-magnetisation}~.
-\end{aligned}\end{equation}
+In the presence of a field, the ground-state becomes unique: \(\ket{\psi}_\mathrm{gs}(h) = \theta(h)\ket{J^z=\frac{K-1}{2}} + \theta(-h)\ket{J^z=-\frac{K-1}{2}}\), and the impurity magnetisation can be calculated from the state:
+\begin{eqnarray}
+	m(h=0^\pm) &= \theta(h)\bra{J^z=\frac{K-1}{2}} S_d^z \ket{J^z=\frac{K-1}{2}} \nonumber\\
+		   &+ \theta(-h)\bra{J^z=-\frac{K-1}{2}}S_d^z\ket{J^z=-\frac{K-1}{2}}\nonumber\\
+	&= \pm  \frac{1}{2} \frac{1-K}{1 + K}\label{imp-magnetisation}~.
+\end{eqnarray}
 
@@
 These polarised states can also be used to obtain the scattering phase shift suffered by the conduction channels at the Fermi surface.
-As shown in the Supplementary Materials~\cite{SM}, the impurity-bath hybdridisation in the polarised states contribute an excess charge of \(n_\text{exc}^{(l)} = 1/K\) to each conduction channel.
+As shown in the Supplementary Materials~\cite{SM}, the impurity-bath hybdridisation in the polarised states contribute an excess charge of \(n_\mathrm{exc}^{(l)} = 1/K\) to each conduction channel.
 Following Friedel's sum rule, this leads to a total scattering phase shift of \(\pi/K\) for each channel:
-\begin{equation}\begin{aligned}
-	\delta^{(l)} = \pi n_\text{exc}^{(l)} = \frac{\pi}{K}, ~ ~ l \in \left[1, K\right] 
-\end{aligned}\end{equation}
+\begin{eqnarray}
+	\delta^{(l)} = \pi n_\mathrm{exc}^{(l)} = \frac{\pi}{K}, ~ ~ l \in \left[1, K\right] 
+\end{eqnarray}
 For \(K > 1\), each channel therefore experiences an unrenormalised phase shift of value between \(0\) and \(\pi\) that, as we will show in a later section, is responsible for the non-Fermi liquid behaviour.
@@
 Right now, some evidence of this role of the phase shift can be provided through its relation to the vanishing field impurity magnetisation \(m\) obtained in eq.~\ref{imp-magnetisation}:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	m(h=0^\pm) = \pm \frac{1}{2} \frac{\delta^{(l)} - \pi}{\delta^{(l)} + \pi}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 When the phase shift \(\delta^{(l)}\) acquires a fractional value (in units of \(\pi\)), the impurity magnetisation also becomes fractional (in units of \(\frac{1}{2}\)).
@@
 The states $\hat{O}^m |M_i\rangle$ (with distinct $m$) are labelled by different eigenvalues of the translation operations, and are thus orthogonal to each other
-\begin{gather}
+\begin{eqnarray}
 \hat{T} \hat{O}^m |M_i\rangle = \hat{O}^m \hat{T} e^{i2\pi \frac{m}{K}} |M_i\rangle =\hat{O}^m e^{i \frac{2\pi(m+p_i)}{K} } |M_i\rangle \\
 \hat{T} \bigg(\hat{O}^m |M_i\rangle \bigg) = e^{i \frac{2\pi(m+p_i)}{K} } \bigg( \hat{O}^m |M_i\rangle \bigg)~.
-\end{gather}
+\end{eqnarray}
 %Different states $\hat{O}^m |M_i\rangle$ for different $m$ are therefore labeled by different eigenvalues of the translation operations, and are thus orthogonal to each other. 
@@
 In order to obtain the effective theory for the K zero modes, we will now use the URG method to decouple the impurity site from the star graph. The starting point is the star graph Hamiltonian
-\begin{gather}
+\begin{eqnarray}
 H = {\mathcal{J}} \vec{S}_d.\displaystyle\sum_i \vec{S}_i ={\mathcal{J}} S_d^zS^z + \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+) ~,\nonumber\\
 H_D = {\mathcal{J}} S^z_d S^z~,~~ H_X = \frac{{\mathcal{J}}}{2} (S_d^+S^-+ S_d^-S^+)~.
-\end{gather}
+\end{eqnarray}
 In order to remove the quantum fluctuations between the impurity spin and the rest, we perform one step of URG:
@@
 \begin{equation}
-\frac{ \beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow}) }{4}  \left( \displaystyle\sum_{\substack{i\neq j \\ \alpha_i,\beta_i\in \{\uparrow,\downarrow\}\\ \alpha_j,\beta_j\in \{\uparrow,\downarrow\}}}\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)}    c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)} +\textrm{h.c.}\right) ~.
+\frac{ \beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow}) }{4}  \sum_{\substack{i\neq j \\ \alpha_i,\beta_i\in \{\uparrow,\downarrow\}\\ \alpha_j,\beta_j\in \{\uparrow,\downarrow\}}}\left(\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)}    c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)} +\textrm{h.c.}\right) ~.
 \label{eq:all-to-all_1}
@@
 \subsubsection{Diagonal renormalisation}
-We first calculate the diagonal renormalisation at second order coming from each of the states \(\ket{\tilde \alpha_0} = \ket{J^z = \frac{1}{2}}\otimes\ket{\psi_\text{rest}}, \ket{\tilde \alpha_1} = \ket{J^z = -\frac{1}{2}}\otimes\ket{\psi_\text{rest}}\), where \(\ket{\psi_\text{rest}}\) refers to the configuration of the remaining sites apart from the two that form the zeroth Hamiltonian.
+We first calculate the diagonal renormalisation at second order coming from each of the states \(\ket{\tilde \alpha_0} = \ket{J^z = \frac{1}{2}}\otimes\ket{\psi_\mathrm{rest}}, \ket{\tilde \alpha_1} = \ket{J^z = -\frac{1}{2}}\otimes\ket{\psi_\mathrm{rest}}\), where \(\ket{\psi_\mathrm{rest}}\) refers to the configuration of the remaining sites apart from the two that form the zeroth Hamiltonian.
 These second order corrections are given by
 \begin{equation}
-H^{(2)}_\text{diag}\left(\tilde \alpha_0\right)  = \frac{2t^2}{E_0} \hat{I} - \Omega_l, ~ ~ H^{(2)}_\text{diag}\left(\tilde \alpha_1\right) = \frac{2t^2}{E_0} \hat{I} + \Omega_l ~,
+H^{(2)}_\mathrm{diag}\left(\tilde \alpha_0\right)  = \frac{2t^2}{E_0} \hat{I} - \Omega_l, ~ ~ H^{(2)}_\mathrm{diag}\left(\tilde \alpha_1\right) = \frac{2t^2}{E_0} \hat{I} + \Omega_l ~,
 \end{equation}
 where $S_{l_i}^z=(n_{l_i\uparrow}-n_{l_i\downarrow})/2$ and $\Omega_l=\frac{2t^2}{3E_0} ( S_{l_1}^z + S_{l_2}^z)$.
-The total diagonal second-order contribution to the effective Hamiltonian is obtained by adding these two contributions, and the result is a trivial shift: $H^{(2)}_\text{diag} = H^{(2)}_\text{diag}\left(\tilde \alpha_0\right) + H^{(2)}_\text{diag}\left(\tilde \alpha_1\right) = -4t^2 \hat{I}$.
+The total diagonal second-order contribution to the effective Hamiltonian is obtained by adding these two contributions, and the result is a trivial shift: $H^{(2)}_\mathrm{diag} = H^{(2)}_\mathrm{diag}\left(\tilde \alpha_0\right) + H^{(2)}_\mathrm{diag}\left(\tilde \alpha_1\right) = -4t^2 \hat{I}$.
 The fact there is no non-trivial diagonal renormalisation to the low-energy excitations shows the absence of (local) Fermi liquid terms.
@@
 The real space local low energy Hamiltonian that takes into account the excitations above the ground state is given by eq.~\ref{eq:hamiltonian_NFL} and can be written as
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{nfl_terms}
-	V_\text{eff} = \frac{2t^2}{{\mathcal{J}^*}}\left[\left(\sigma^z_{0,1}\right)^2 s^+_{0,2} + \left(\sigma^z_{0,2}\right)^2 s^+_{0,1}\right] \left(s^-_{1,1} + s^-_{1,2}\right) + \text{h.c.}~;
-\end{aligned}\end{equation}
+	V_\mathrm{eff} = \frac{2t^2}{{\mathcal{J}^*}}\left[\left(\sigma^z_{0,1}\right)^2 s^+_{0,2} + \left(\sigma^z_{0,2}\right)^2 s^+_{0,1}\right] \left(s^-_{1,1} + s^-_{1,2}\right) + \mathrm{h.c.}~;
+\end{eqnarray}
 here, \(\sigma^z_{0,l} = \hat n_{0\uparrow,l} - \hat n_{0\downarrow,l}, s^+ = c^\dagger_{0 \uparrow,l}c_{0 \downarrow,l}\) and \(s^- = \left(s^+\right)^\dagger\).
@@
 The diagonal part of eq.~\ref{nfl_terms} is
-\begin{equation}\begin{aligned}
-	V_\text{eff} = \frac{2t^2}{J}\sum_{l=1,2}\left(\sum_\sigma \hat n_{0\sigma,l}\right) s^+_{0,\bar l}s^-_{1,\bar l} + \text{h.c.}~,
-\end{aligned}\end{equation}
+\begin{eqnarray}
+	V_\mathrm{eff} = \frac{2t^2}{J}\sum_{l=1,2}\left(\sum_\sigma \hat n_{0\sigma,l}\right) s^+_{0,\bar l}s^-_{1,\bar l} + \mathrm{h.c.}~,
+\end{eqnarray}
 where \(\bar l = 3 - l\) is the channel index complementary to \(l\). We will Fourier transform this effective Hamiltonian into \(k-\)space. The NFL part becomes
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{k_space_od}
-	\sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \text{h.c.} ~.
-\end{aligned}\end{equation}
-%This form of the Hamiltonian is very similar to the three-particle interaction term in 
+	\sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \mathrm{h.c.} ~.\qquad
+\end{eqnarray}
 Such a three particle interaction term was also obtained for the NFL phase of the 2D Hubbard model from a URG treatment (see Appendix B of Ref.\cite{anirbanmott1}).
@@
 The 2 particle-1 hole interaction in Eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
-\begin{equation}\begin{aligned}
-	H_\text{eff,MFL} = \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{2t^2e^{i\left(k_1 - k_2\right)a}}{J} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \text{h.c.}\\
-	= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right)~.
-\end{aligned}\end{equation}
+\begin{eqnarray}
+	H_\mathrm{eff,MFL} &= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{2t^2e^{i\left(k_1 - k_2\right)a}}{J} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \mathrm{h.c.}\nonumber\\
+	&= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right).\qquad 
+\end{eqnarray}
 The most dominant contribution comes from \(k_1 = k_2 = k^\prime\), revealing the non-Fermi liquid metal~\cite{cox_jarrell_two_channel_rev,andrei_jerez_1995}:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{mfl_large}
-	H^*_\text{eff,MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)~.
-\end{aligned}\end{equation}
+	H^*_\mathrm{eff,MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)~.
+\end{eqnarray}
 A non-local version of this effective Hamiltonian was found to describe the normal phase of the Mott insulator of the 2D Hubbard model, as seen from a URG analysis~\cite{anirbanmott1,anirbanmott2}.
-Following~\cite{anirbanmott1}, one can track the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\text{th}\) RG step, in the form of the URG equation
-\begin{equation}\begin{aligned}
+Following~\cite{anirbanmott1}, one can track the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\mathrm{th}\) RG step, in the form of the URG equation
+\begin{eqnarray}
 	\Delta R_j =- \frac{R_j^2}{\omega - \epsilon_{j}/2 - R_j/8}~.
-\end{aligned}\end{equation}
-In the RG equation, \(\epsilon_{j}\) represents the energy of the \(j^\text{th}\) isoenergetic shell. It is seen from 
+\end{eqnarray}
+In the RG equation, \(\epsilon_{j}\) represents the energy of the \(j^\mathrm{th}\) isoenergetic shell. It is seen from 
 the RG equation that \(R\) is relevant in the range of \(\omega < \frac{1}{2}\epsilon_j\) that has been used throughout, leading to a fixed-point at \(R^*/8 = \omega - \frac{1}{2}\epsilon^*)\).
@@
 The renormalisation in \(R\) leads to a renormalisation in the single-particle self-energy~\cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalisation is
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 The density of states can be approximated to be \(N^*/R^*\), where \(N^*\) is the total number of states over the interval \(R^*\).
@@
 On defining \(\bar \omega = N^* \left(\omega - \frac{1}{2}\epsilon^*\right)\), we can write
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{self_energy}
 	\Delta \Sigma(\omega) \sim  \bar \omega \ln \frac{N^* \omega}{\bar \omega}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 The self-energy also provides the quasiparticle residue for each channel\cite{anirbanmott1}:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	Z(\bar\omega) = \left(2 - \ln \frac{2\bar\omega}{N^* \omega}\right) ^{-1}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 As \(\omega \to 0\), the \(Z\) vanishes, implying that the ground state is {\it not adiabatically connected} to the Fermi gas in the presence of the NFL terms.
@@
 We will now calculate the same quantity for the ground states 
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 \ket{J^z} \equiv \ket{S_d=1/2,S=K/2;J=(S-1/2),J^z}
-\end{aligned}\end{equation}
+\end{eqnarray}
 of the $K$ channel model.
@@
 
-\par \textit{Case 1:} We first study the mutual information $MI(d,1\uparrow)$ between the impurity spin $S_d$ and the state $1_\uparrow$ (fig.~\ref{fig:schematic_hopping}), where $1$ represents real-space origin of the $1^\text{st}$ conduction channel.
+\par \textit{Case 1:} We first study the mutual information $MI(d,1\uparrow)$ between the impurity spin $S_d$ and the state $1_\uparrow$ (fig.~\ref{fig:schematic_hopping}), where $1$ represents real-space origin of the $1^\mathrm{st}$ conduction channel.
 For a single channel model, this site is unique because there is just one channel, but in the presence of $K$ channels, there are $K$ possible choices corresponding to each of the channels.
@@
 We start from a strong coupling \((J \to \infty)\) spin-\(S_{d}\) impurity MCK Hamiltonian in the over-screened regime \(\left( K > 2S_{d} \right) \),
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{strong_ham}
 	H(J) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + J \vec{S_d}\cdot\vec{S}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 Here, \(\vec S\) is the total spin \(\sum_l \sum_{kk^\prime \alpha\beta} \vec \sigma_{\alpha\beta}c^\dagger_{k\alpha,l}c_{k^\prime\beta,l}\) of all the zero modes.
@@
 The states of this new spin are defined by
-\begin{gather}
+\begin{eqnarray}
 	\hat{\mathbb{S}_d^z} \ket{S^z} = S^z \ket{S^z},\nonumber\\
 	\hat{\mathbb{S}_d^\pm} \ket{S^z} = \sqrt{\mathbb{S}_d\left( \mathbb{S}_d + 1 \right) - S^z\left( S^z \pm 1\right)} \ket{S^z \pm 1}~.
-\end{gather}
+\end{eqnarray}
 While the ground state subspace gives rise to the new central spin object, the excited states of the star graph can be used to define bosonic operators that mediate interactions between the central spin and the next-nearest neighbour lattice sites~\cite{kroha_kolf_2007}.
@@
 The new Hamiltonian, characterized by the small super-exchange  coupling \(\mathbb{J}\) of the general form \(\gamma t^2/J\), has the form
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	H^\prime(\mathbb{J}) = \sum_{k,\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + \mathbb{J} \vec{\mathbb{S}_d}\cdot\vec{\mathbb{S}}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 $\vec{\mathbb{S}}$ is the local bath spin formed by the new zero modes.
@@
 This constrains the form of the scaling factor \(\gamma\):
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	{\mathbb{J}}^* = \frac{\gamma 4t^2}{{\mathcal{J}^*}} = \frac{2}{K \rho^\prime} \implies \gamma = \frac{1}{4t^2} {{\mathcal{J}^*}}^2 = \frac{1}{K^2 t^2 \rho \rho^\prime}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 
@@
 This can be realised under RG flow if one considers the anisotropic MCK model.
-\begin{align}
+\begin{eqnarray}
 	H = \sum_{k,\alpha,l}\epsilon_{k,l} \hat n_{k\alpha,l} + \sum_{kk^\prime,\atop{\alpha,\beta,l}}{\mathcal{J}}_l \vec{S_d}\cdot\frac{1}{2}\vec{\sigma}_{\alpha\beta}c_{k\alpha,l}^\dagger c_{k^\prime\beta, l}~.
-\end{align}
+\end{eqnarray}
 We consider the specific case where \(K-1\) channels have the same coupling \({\mathcal{J}}_1 = {\mathcal{J}}_2 = ...
@@
 The RG equations for such a model are
-\begin{align}
+\begin{eqnarray}
 	\frac{\Delta {\mathcal{J}}_\pm}{|\Delta D|} = -\frac{{\mathcal{J}}_\pm^2 \rho}{\mathcal{D}_\pm} + \frac{\rho^2 {\mathcal{J}}_\pm}{2}\left[\frac{(K-1){\mathcal{J}}_+^2}{\mathcal{D}_+} + \frac{{\mathcal{J}}_-^2}{\mathcal{D}_-}\right]~,
-\end{align}
+\end{eqnarray}
 where \(\mathcal{D}_\pm = \omega - \frac{D}{2} - \frac{{\mathcal{J}}_\pm}{4}\) are the denominators of the URG equations.
@@
 
-\acknowledgments
+\ack
+
 S.

### 2023-01-07 manuscript/Supplementary/supplementary_mck.tex
further changes to layout

@@
-\documentclass[reprint,onecolumn,prb,superscriptaddress]{revtex4-2}
-\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,color,ulem,soul,lipsum}
-\allowdisplaybreaks
-\bibliographystyle{apsrev4-2}
+\documentclass[10pt]{iopart}
+\usepackage{iopams}  
+\usepackage{braket,graphicx,amsmath}
+\usepackage[hidelinks]{hyperref}
+\usepackage[margin=2cm]{geometry}
+\bibliographystyle{unsrt}
 \begin{document}
@@
 
-\author{Siddhartha Patra}
-\email{sp14ip022@iiserkol.ac.in }
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-\author{Abhirup Mukherjee}
-\email{am18ip014@iiserkol.ac.in }
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-\author{Anirban Mukherjee}
-\email{mukherjee.anirban.anirban@gmail.com }
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
-\author{N. S. Vidhyadhiraja}
-\email{raja@jncasr.ac.in}
-\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
-\author{A. Taraphder}
-\email{arghya@phy.iitkgp.ernet.in}
-\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
-\author{Siddhartha Lal}
-\email{slal@iiserkol.ac.in}
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
+\author{Siddhartha Patra$^1$, Abhirup Mukherjee$^1$, Anirban Mukherjee$^1$, N. S. Vidhyadhiraja$^4$, A. Taraphder$^5$ and Siddhartha Lal$^1$}
+\eads{\mailto{sp14ip022@iiserkol.ac.in}, \mailto{am18ip014@iiserkol.ac.in}, \mailto{mukherjee.anirban.anirban@gmail.com}, \mailto{raja@jncasr.ac.in}, \mailto{arghya@phy.iitkgp.ernet.in}, \mailto{slal@iiserkol.ac.in}}
+
+\address{$^1$Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
+
+\address{$^4$Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
+
+\address{$^5$Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
+
 \date{\today}
-\maketitle
 
@@
 The zero-mode approximation of the fixed-point Hamiltonian is a star graph Hamiltonian:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	H = J^* \vec{S_d}\cdot\vec{s}_\text{tot}
-\end{aligned}\end{equation}
+\end{eqnarray}
 where \(\vec s_\text{tot} = \sum_l \vec s_l\) is the total spin operator for all the channels.
 We insert a magnetic field that acts only on the impurity and then attempt to diagonalize the Hamiltonian.
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{stargraph_field_hamiltonian}
 	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h S_d^z
-\end{aligned}\end{equation}
+\end{eqnarray}
 The Hamiltonian commutes with \(s_\text{tot}^2\):
-\begin{equation}\begin{aligned}
-\left[s_\text{tot}^2, H(h)\right] = \left[\sum_{i=x,y,z}{s^i_\text{tot}}^2, J^* \sum_{i=x,y,z} S_d^i s^i_\text{tot}\right] = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, \left[s_\text{tot}^i,s_\text{tot}^j\right]\right\} = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, i \epsilon^{ijk}s^k_\text{tot}\right\} = 0
-\end{aligned}\end{equation}
+\begin{eqnarray}
+	\hspace*{-20pt}\left[s_\text{tot}^2, H(h)\right] &= \left[\sum_{i=x,y,z}{s^i_\text{tot}}^2, J^* \sum_{i=x,y,z} S_d^i s^i_\text{tot}\right] = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, \left[s_\text{tot}^i,s_\text{tot}^j\right]\right\} = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, i \epsilon^{ijk}s^k_\text{tot}\right\}\nonumber\\
+							 &= 0
+\end{eqnarray}
 This means the Hamiltonian is already block-diagonal in the quantum number \(s_\text{tot}\).
@@
 Defining \(\epsilon^h_m = \frac{1}{2}\left(Jm + h\right) \) and \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} 
-\end{aligned}\end{equation}
+\end{eqnarray}
 The eigenvalues are 
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{eigenvalue}
 	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}
-\end{aligned}\end{equation}
+\end{eqnarray}
 where \(\alpha = \epsilon^h_m + J/4\).
@@
 This common \(K-\)fold degenerate eigenvalue is \(-J(M+1)/2\).
-The full list of energy eigenvalues at a particular value of \(M\) (characterised by the total spin operator \(J^z = S_d^z + s_\text{tot}^z\)) is
-\begin{equation}\begin{aligned}
-\label{stargraph_spectrum}
-&		JM/2 - h/2, &&\ket{J=M+\frac{1}{2},J^z=-M-\frac{1}{2},s_\text{tot}=M}, && m = -M\\
-&-J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}, &&\ket{J=M-\frac{1}{2},J^z=m+\frac{1}{2},s_\text{tot}=M}, &&m=-M,\ldots,M-1\\
-&JM/2 + h/2, &&\ket{J=M+\frac{1}{2},J^z=M+\frac{1}{2},s_\text{tot}=M},&& m = M\\
-\end{aligned}\end{equation}
 The eigenstates for each value of \(M,m\) in the \(J=M-\frac{1}{2}\) sector are given by
-\begin{equation}\begin{aligned}
-	\ket{M-\frac{1}{2},m+\frac{1}{2},M} =\mathcal{C}_\pm \ket{\uparrow, M, m} \pm \sqrt{1 - \mathcal{C}_\pm^2} \ket{\downarrow, M, m+1}, ~ ~ \mathcal{C}_\pm = \frac{J\sqrt{x_m^M}/2}{\sqrt{J^2 x_m^M/4 + \left(\alpha \mp \sqrt{\alpha^2 + J^2 x_m^M/4}\right)^2 }}
-\end{aligned}\end{equation}
+\begin{eqnarray}
+	\fl \ket{M-\frac{1}{2},m+\frac{1}{2},M} =\mathcal{C}_\pm \ket{\uparrow, M, m} \pm \sqrt{1 - \mathcal{C}_\pm^2} \ket{\downarrow, M, m+1}, ~ ~ \mathcal{C}_\pm = \frac{J\sqrt{x_m^M}/2}{\sqrt{J^2 x_m^M/4 + \left(\alpha \mp \sqrt{\alpha^2 + J^2 x_m^M/4}\right)^2 }}
+\end{eqnarray}
 The partition function is given by
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	Z(h) = \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
-\end{aligned}\end{equation}
+\end{eqnarray}
 where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\).
@@
 We need to count the number of instances of a particular subspace \(s_\text{tot}=M\).
-It turns out that this number is given by
-\begin{equation}\begin{aligned}
-	r^K_M = {}^{K-1}C_{K/2 - M}
-\end{aligned}\end{equation}
-which means the correct partition function is
-\begin{equation}\begin{aligned}
+It turns out that this number is given by \(r^K_M = {}^{K-1}C_{K/2 - M}\), which means the correct partition function is
+\begin{eqnarray}
 	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
-\end{aligned}\end{equation}
+\end{eqnarray}
 
@@
 Of particular importance within the ground-state subspace are the zero-field maximally-polarised states, obtained by choosing \(M = \frac{K}{2}, m + \frac{1}{2}= \pm \left( M - \frac{1}{2} \right) =\pm \frac{1}{2}\left(K-1\right)\):
-\begin{equation}\begin{aligned}
-	\ket{J=\frac{K-1}{2},J^z= \frac{\sigma}{2}\left(K-1\right),s_\text{tot}=\frac{K}{2}} = \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma(\frac{K}{2}-1)} - \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma\frac{K}{2}},
-\end{aligned}\end{equation}
+\begin{eqnarray}
+	\fl \ket{J=\frac{K-1}{2},J^z= \frac{\sigma}{2}\left(K-1\right),s_\text{tot}=\frac{K}{2}} = \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma(\frac{K}{2}-1)} - \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma\frac{K}{2}},
+\end{eqnarray}
 where \(\sigma\) can take values \(\pm 1\) and \(\ket{\sigma}_d\) represents the up and down configurations of the impurity spin.
@@
 With these in mind, the polarised state can be cast in the more explicit form
-\begin{equation}\begin{aligned}
-	\hspace*{-15pt}\ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} \left[\ket{\sigma}_d\otimes\left(\ket{\bar\sigma,\sigma,\ldots,\sigma} + \ket{\sigma,\bar\sigma,\ldots,\sigma} + \ldots + \ket{\sigma,\sigma\ldots,\bar\sigma}\right) - K\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\right].\label{polarised-state}
-\end{aligned}\end{equation}
+\begin{eqnarray}
+	\fl \ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} \left[\ket{\sigma}_d\otimes\left(\ket{\bar\sigma,\sigma,\ldots,\sigma} + \ket{\sigma,\bar\sigma,\ldots,\sigma} + \ldots + \ket{\sigma,\sigma\ldots,\bar\sigma}\right) - K\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\right].\label{polarised-state}\qquad
+\end{eqnarray}
 
@@
 The polarised states can then be written as
-\begin{equation}\begin{aligned}
-	\ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} \sum_{l=1}^K\ket{\sigma}_d\otimes\left[\ket{\bar\sigma}_l - \ket{\sigma}_l\right] \otimes\ket{\sigma,\ldots,\sigma}_{l^\prime} = \frac{\sqrt 2}{\sqrt{K(1 + K)}} \sum_{l=1}^K \ket{\text{SS}_{d,l}}\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}.\label{singlet-chain}
-\end{aligned}\end{equation}
+\begin{eqnarray}
+	\fl \ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} \sum_{l=1}^K\ket{\sigma}_d\otimes\left[\ket{\bar\sigma}_l - \ket{\sigma}_l\right] \otimes\ket{\sigma,\ldots,\sigma}_{l^\prime} = \frac{\sqrt 2}{\sqrt{K(1 + K)}} \sum_{l=1}^K \ket{\text{SS}_{d,l}}\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}.\label{singlet-chain}
+\end{eqnarray}
 This form of the state shows that the impurity is trying to participate, simultaneously, in forming \(K\) number of singlets.
@@
 With these in mind, the total excess charge contributed to each channel from the state in Eq.~\ref{polarised-state} is
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	n_\text{exc}^{(l)} = \frac{1}{K(1+K)}\left[1 + K^2 \times \frac{1}{K}\right] = \frac{1}{K}
-\end{aligned}\end{equation}
+\end{eqnarray}
 
@@
 The star graph Hamiltonian that sits at the heart of the RG fixed point Hamiltonian of the multichannel Kondo model contains a classical Ising term and a quantum fluctuation term:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	H = {\mathcal{J}}\vec{S_d}\cdot\vec S = \mathcal{J}\left[\underbrace{S_d^z S^z}_\text{Ising term} + \underbrace{\frac{1}{2}\left(S_d^+ S^- + \text{h.c.}\right)}_\text{quantum fluctuation part} \right] = \mathcal{J}\left[\mathcal{H}^C + \mathcal{H}^Q\right] ~.
 	\label{eq:stargraph_hamiltonian}
-\end{aligned}\end{equation}
+\end{eqnarray}
 We are interested in studying how the presence of quantum fluctuations in the Hamiltonian of eq.~\ref{eq:stargraph_hamiltonian} stabilises the ground state.
@@
 In the over-screened case \(\left( K > 2S_d \right) \), the contributions are
-\begin{gather}
-	E_{C} = \frac{1}{K}\langle \psi_g | \mathcal{H}^C | \psi_g \rangle, ~~~~~ E_{Q} = \frac{1}{K}\bra{\psi_g}\mathcal{H}^Q \ket{\psi_g} =\frac{E_g/\mathcal{J} - E_{C}}{K} =  -\frac{1}{2}S_d - \frac{1}{K}\left(S_d + E_{C}\right)~,
-\end{gather}  
+\begin{eqnarray}
+	E_{C} = \frac{1}{K}\langle \psi_g | \mathcal{H}^C | \psi_g \rangle, \quad E_{Q} = \frac{1}{K}\bra{\psi_g}\mathcal{H}^Q \ket{\psi_g} =\frac{E_g/\mathcal{J} - E_{C}}{K} =  -\frac{1}{2}S_d - \frac{1}{K}\left(S_d + E_{C}\right)~,
+\end{eqnarray}  
 where we have defined the contributions \(E_C\) and \(E_Q\) to the ground state energy coming from the Ising and fluctuation parts respectively, and we have substituted the ground state energy \(E_g\) for the over-screened case from eq.(10) in the main text.
@@
 With these considerations, the minimum value of the quantum fluctuation, {\it per channel}, is
-\begin{equation}
-q_K = \frac{1}{K}\sqrt{Q_\text{max}} = \frac{1}{K}\sqrt{\langle \psi_g | J^2 - |J^z|_{min}^2 |\psi_g\rangle} = \begin{cases}
+\begin{eqnarray}
+\fl q_K = \frac{1}{K}\sqrt{Q_\text{max}} = \frac{1}{K}\sqrt{\langle \psi_g | J^2 - |J^z|_{min}^2 |\psi_g\rangle} = \begin{cases}
 	\frac{1}{K}\sqrt{(|K/2-S_d|)(|K/2-S_d|+1)-1/4}, & \text{ where }\Delta\text{ is half-integer}\\
 	\frac{1}{K}\sqrt{(|K/2-S_d|)(|K/2-S_d|+1)}, & \text{ where }\Delta\text{ is integer}
-\end{cases}~.
-\end{equation}
+\end{cases}~.\quad
+\end{eqnarray}
 This expression is symmetric under the transformation \(\Delta \to -\Delta\), and represents a duality between the over-screened and under-screened models.
@@
 We find, in general, that the square of the staggered magnetization per channel is
-\begin{equation}
-	m_s^2 = \left< \left(\frac{1}{K}M_S\right)^2\right> = \frac{1}{K^2}\langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \frac{1}{K^2}\langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle = \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}~.
-\end{equation}
+\begin{eqnarray}
+	\fl m_s^2 = \left< \left(\frac{1}{K}M_S\right)^2\right> = \frac{1}{K^2}\langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \frac{1}{K^2}\langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle = \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}~.
+\end{eqnarray}
 
@@
 \begin{eqnarray}
-\langle(m_s^x)^2\rangle=\langle(m_s^y)^2\rangle=\langle(m_s^z)^2\rangle=\frac{1}{3}m_s^2~,~~   
+\langle(m_s^x)^2\rangle=\langle(m_s^y)^2\rangle=\langle(m_s^z)^2\rangle=\frac{1}{3}m_s^2~,
 \end{eqnarray}
@@
 Just like the complete string operator \(\pi^z\), the modified string operator \(\sigma_d^z \pi^z\) is also a Wilson loop operator that wraps around only the outer nodes of the star graph:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\pi^z_c \equiv \sigma_d^z \pi^z = \exp\left[i \frac{\pi}{2} \left(\sum_{l=1}^K \sigma^z_l - K\right)\right] ~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 The expectation value of the impurity magnetization along a particular direction and in specific ground states can be related to the 't Hooft operator.
 We will work in the state comprised of two adjacent eigenstates of \(J^z\):
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\ket{g^\theta_{J^z}} \equiv \frac{1}{\sqrt 2}\left( \ket{J^z} + e^{i\theta}\ket{J^z+1}\right), && J^z < \frac{1}{2}\left( K-1 \right)~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 The expectation value of the impurity magnetization operator \(\sigma_d^x\) can be expressed as
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\left<\sigma_d^x\right> \equiv \langle g^\theta_{J^z} \vert \sigma_d^x \vert g^\theta_{J^z}\rangle = - \langle J^z + 1 \vert \pi^x_c \vert -J^z \rangle + \text{h.c.}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 This expression relates the observable impurity magnetization to the topological 't Hooft operator \cite{Maric2020}. Evaluating the matrix elements gives
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{sigmax}
 	\left<\sigma_d^x\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\cos \theta~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 Performing a similar calculation reveals that the impurity magnetizations along \(y\) and \(z\) in the same state are given by
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{sigmayz}
 	\left<\sigma_d^y\right> = - \frac{\sqrt{K^2 - (2J^z + 1)^2}}{2(1+K)}\sin \theta, &&\left<\sigma_d^z\right> = - \frac{2J^z + 1}{(1+K)}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 Combining eqs.~\ref{sigmax} and \ref{sigmayz}, we find
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\cos^2\theta\left(\left<\sigma^x_d\right>\right)^2 + \sin^2\theta\left(\left<\sigma^y_d\right>\right)^2 + \frac{1}{4}\left(\left<\sigma^z_d\right>\right)^2 = \frac{1}{4}\left(\frac{K}{1+K}\right)^2~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 This relation \textit{constrains the values of the magnetization} in all the directions: the \(x\) and \(y\) magnetization values have already been shown to be related to the `t Hooft operators \(\pi^x\) and \(\pi^y\) and the magnetization along \(z\) is therefore constrained in terms of the `t Hooft operators and the quantized function on the right-hand side (the function is quantized because \(K\) can only take integer values).
@@
 The star graph model can be solved to obtain the partition function, and this then allows the computation of the Helmholtz free energy and hence the thermal entropy:
-\begin{equation}
-\mathcal{F}= -k_B T\log Z, ~ ~ ~ S = -\frac{\partial \mathcal{F}}{\partial T} = -k_B \log Z -k_B T \frac{1}{Z} \frac{dZ}{dT} = -k_B \log \sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon}  -\frac{1}{\beta} \frac{k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   }{\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon}}~,
-\end{equation}
+\begin{eqnarray}
+\fl \mathcal{F}= -k_B T\log Z, ~ ~ ~ S = -\frac{\partial \mathcal{F}}{\partial T} = -k_B \log Z -k_B T \frac{1}{Z} \frac{dZ}{dT} = -k_B \log \sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon}  -\frac{1}{\beta} \frac{k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   }{\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon}}~,
+\end{eqnarray}
 where \(d(\epsilon)\) is the degeneracy of the state at energy \(\epsilon\). The high and low-temperature limits take very simple forms:
-\begin{equation}
-\lim_{\beta\rightarrow \infty} S = -k_B \log_2 d(\epsilon_{G})~,~~\lim_{\beta\rightarrow 0} S = -k_B \log \sum_\epsilon d(\epsilon)~.
-\end{equation}
+\begin{eqnarray}
+\lim_{\beta\rightarrow \infty} S = -k_B \log_2 d(\epsilon_{G})~,\quad\lim_{\beta\rightarrow 0} S = -k_B \log \sum_\epsilon d(\epsilon)~.
+\end{eqnarray}
 
@@
 The all-to-all Hamiltonian obtained by resolving the impurity-bath quantum fluctuations is written in terms of the spinor spin operators which are individually made out of two electronic degrees of freedom.
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 H_{eff} 
@@
 \label{eq:all-to-all_1}
-\end{aligned}\end{equation}
+\end{eqnarray}
 where \(\beta_{\uparrow} ({\mathcal{J}},\omega_{\uparrow})= ({\mathcal{J}}^2 \Gamma_{\uparrow})/2, ~ ~\Gamma_{\uparrow}=(\omega_{\uparrow}-{\mathcal{J}}(S_d^z-1))^{-1}\).
@@
 Using the spinor representation, we obtain the spin creation operation in terms of the electronic degree of freedom:
-\begin{equation}
+\begin{eqnarray}
 S_i^+ = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{+}_{\alpha\beta} c_{0\beta}^{(i)}
-=\frac{\hbar}{2} c_{0\uparrow}^{(i)\dagger} c_{0\downarrow}^{(i)}, ~ ~ ~S_i^z = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{z}_{\alpha\beta} c_{0\beta}^{(i)} =\frac{\hbar}{2} (c_{0\uparrow}^{(i)\dagger} c_{0\uparrow}^{(i)} - c_{0\downarrow}^{(i)\dagger} c_{0\downarrow}^{(i)} )~.
-\end{equation}
+=\frac{\hbar}{2} c_{0\uparrow}^{(i)\dagger} c_{0\downarrow}^{(i)}, \quad S_i^z &= \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{z}_{\alpha\beta} c_{0\beta}^{(i)} \nonumber\\
+									       &=\frac{\hbar}{2} (c_{0\uparrow}^{(i)\dagger} c_{0\uparrow}^{(i)} - c_{0\downarrow}^{(i)\dagger} c_{0\downarrow}^{(i)} )~.
+\end{eqnarray}
 This spinor is simply the Anderson pseudo-spin formulation in the spin channel.
@@
 \begin{eqnarray}
-H_{eff} &=& \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{4} \bigg[ \displaystyle\sum_{ij} S_i^+S_j^- ~+ \textrm{h.c.} \bigg]~,
+H_{eff} &=& \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{4} \left[ \displaystyle\sum_{ij} S_i^+S_j^- ~+ \textrm{h.c.} \right]~,
 \end{eqnarray}
@@
 Then the braiding rule between the twist and translation operators are give as
-\begin{equation}
+\begin{eqnarray}
 \hat{T}_{\mu}\hat{\mathcal{O}}_{\mu} \hat{T}^{\dagger}_{\mu} \hat{\mathcal{O}}_{\mu}^{\dagger} = \exp\{i[2\pi S_1^z-\frac{2\pi}{K}S^z]\} = \exp\{i[\pm \pi - \frac{2\pi}{K} S^z]\} =\exp(i\frac{2\pi p}{q})~.
-\end{equation}
+\end{eqnarray}
 The availability of the non-trivial braiding statistics between these twist and translation operators is possible if $p\neq 0$ and $q\neq \infty$. Further simplification leads to the condition
-\begin{equation}
+\begin{eqnarray}
  \pm\pi -\frac{2\pi}{K} S^z = \frac{2\pi p}{q} \implies  \pm\frac{1}{2}-\frac{S^z}{K} = \frac{p}{q} , ~ ~ ~ \frac{(\pm K-2S^z)}{2K} = \frac{p}{q}~,
-\end{equation} 
+\end{eqnarray} 
 where $p,q$ are mutual primes.
@@
 \begin{eqnarray}
-\frac{(K-m)}{K} &=& \frac{p}{q} ~,~~ \frac{-m}{K}=\frac{p}{q}~.
+\frac{(K-m)}{K} &=& \frac{p}{q} ~,\quad \frac{-m}{K}=\frac{p}{q}~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-&&\hspace{2.2cm} -K/2+1,-K/2+2,\cdots,K/2-1,K/2~.
+-K/2+1,-K/2+2,\cdots,K/2-1,K/2~.
 \end{eqnarray}
-
-Thus we get the general braiding statistics between the twist and the translation 
+This gives the general braiding statistics between the twist and the translation,
 \begin{eqnarray}
@@
 The action of the twist operator on the $S^x$ is determined in the following calculation
-\begin{equation}
+\begin{eqnarray}
 \hat{O}_{\mu} S^x \hat{O}^{\dagger}_{\mu} = \exp({i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} )S^x \exp({-i\frac{2\pi}{K} \displaystyle\sum_{\substack{j=1\\ \mathcal{P}_{\mu}}}^{K} j S_j^z} ) = e^{X} S^x e^{-X}~.
-\end{equation}
+\end{eqnarray}
 To simplify the calculation, we define $i\frac{2\pi}{K}=\Omega$, thus $X=\Omega\sum_j jS^z_j$. Thus we get
-\begin{equation}
-e^X S^x e^{-X}= S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots = \sum_l ( S^x_l \cos \theta_l -  S_l^y \sin \theta_l ) ~,~~~\theta_l=\frac{2\pi l}{K}\\
-e^X S^y e^{-X}= \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)~.
-\end{equation}
+\begin{eqnarray}
+e^X S^x e^{-X}= S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots = \sum_l ( S^x_l \cos \theta_l -  S_l^y \sin \theta_l ) ~,\nonumber\\
+e^X S^y e^{-X}= \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)\nonumber\\
+\theta_l=\frac{2\pi l}{K}~.
+\end{eqnarray}
 As already defined, $\theta_l=\frac{2\pi l}{K}=\frac{2\pi (K-n)}{K}$, where $n$ is an integer.
@@
 Thus in the large channel limit
-\begin{gather}
- \lim_{K\rightarrow \infty}\hat{\mathcal{O}}_{\mu} H_{eff} \hat{\mathcal{O}}_{\mu}^{\dagger}\nonumber = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[ \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger}  + \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger}  \bigg] = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \bigg[  S^{x2}+S^{y2}  \bigg] = H_{eff},\\
- \lim_{K\rightarrow \infty } [\hat{\mathcal{O}},H_{eff}] = 0~.
+\begin{eqnarray}
+	\hspace*{-20pt}\lim_{K\rightarrow \infty}\hat{\mathcal{O}}_{\mu} H_{eff} \hat{\mathcal{O}}_{\mu}^{\dagger}\nonumber = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \left[ \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^x \hat{\mathcal{O}}_{\mu}^{\dagger}  + \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger} \hat{\mathcal{O}}_{\mu} S^y \hat{\mathcal{O}}_{\mu}^{\dagger}  \right] = \frac{\beta_{\uparrow}(\alpha,\omega_{\uparrow})}{2} \left[  S^{x2}+S^{y2}  \right] = H_{eff},\\
+\hspace*{-20pt} \lim_{K\rightarrow \infty } [\hat{\mathcal{O}},H_{eff}] = 0~.
 \label{eq:hamiltonian_twisted}
-\end{gather}
+\end{eqnarray}
 
@@
 The action of these twist and translation operators on these states are
-\begin{gather}
-\hat{T}_{\mu} |p^j_{\mu} \rangle = e^{i\hat{\mathcal{P}}_{\mu}} |p^j_{\mu} \rangle = e^{ip^j_{\mu}} |p^j_{\mu}\rangle, ~ ~ ~ ~ \hat{T}_{\mu} \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle =  \hat{\mathcal{O}}_{\mu} \hat{T}_{\mu} e^{i\frac{2\pi m}{K}} |p^j_{\mu}\rangle = \hat{\mathcal{O}}_{\mu}   e^{i(\frac{2\pi m}{K}+p_{\mu}^j)} |p^j_{\mu}\rangle~,~~ \frac{2\pi m}{K} \equiv p_{\mu}^{m}~, \\
-\hat{T}_{\mu} \bigg( \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle  \bigg) = e^{i(p_{\mu}^{m}+p_{\mu}^j)} \bigg( \hat{\mathcal{O}}_{\mu}    |p^j_{\mu}\rangle \bigg)~,
-\end{gather}
+\begin{eqnarray}
+\hspace*{-20pt}\hat{T}_{\mu} |p^j_{\mu} \rangle = e^{i\hat{\mathcal{P}}_{\mu}} |p^j_{\mu} \rangle = e^{ip^j_{\mu}} |p^j_{\mu}\rangle, ~ ~ ~ ~ \hat{T}_{\mu} \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle =  \hat{\mathcal{O}}_{\mu} \hat{T}_{\mu} e^{i\frac{2\pi m}{K}} |p^j_{\mu}\rangle = \hat{\mathcal{O}}_{\mu}   e^{i(\frac{2\pi m}{K}+p_{\mu}^j)} |p^j_{\mu}\rangle~,\quad\frac{2\pi m}{K} \equiv p_{\mu}^{m}~, \nonumber\\
+\hspace*{-20pt}\hat{T}_{\mu} \left( \hat{\mathcal{O}}_{\mu} |p^j_{\mu} \rangle  \right) = e^{i(p_{\mu}^{m}+p_{\mu}^j)} \left( \hat{\mathcal{O}}_{\mu}    |p^j_{\mu}\rangle \right)~,
+\end{eqnarray}
 where $m$ represents different $S^z$ plateaux.
@@
 This guides the separation of the Hamiltonian into a diagonal and an off-diagonal piece:
-\begin{align}
+\begin{eqnarray}
 	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_{V + V^\dagger}
-\end{align}
+\end{eqnarray}
 We define \(V\) as the interaction term that decreases \(s_\text{tot}^z\) by 1: \(V \ket{s_\text{tot}^z} \to \ket{s_\text{tot}^z - 1}\).
@@
 The Schrodinger equation for the ground state can be written as
-\begin{align}
-	E_\text{gs}\ket{\Psi_\text{gs}} = H \ket{\Psi_\text{gs}} = \left(H_d + V\right)\ket{\Psi_\text{gs}} \implies \left(E_\text{gs} - H_d\right)\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z} = V\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}
-\end{align}
+\begin{eqnarray}
+	E_\text{gs}\ket{\Psi_\text{gs}} = H \ket{\Psi_\text{gs}} = \left(H_d + V\right)\ket{\Psi_\text{gs}} \nonumber\\
+	\implies \left(E_\text{gs} - H_d\right)\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z} = V\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}
+\end{eqnarray}
 \(E_\text{gs}\) is the ground state energy, and can be replaced by the star graph ground state energy if we remove the kinetic energy cost via normal ordering: \(E_\text{gs} = -\frac{J}{2}\left(\frac{K}{2}+1\right) \).
@@
 For the state \((s_\text{tot},s^z_\text{tot}) = (1,0)\), equations are
-\begin{equation}
+\begin{eqnarray}
 	\label{eff_ham_Sdz_10}
-	E_\text{gs} \ket{\frac{1}{2}, 1, 0} = \left(H_d + V \frac{1}{E_\text{gs} - H_d}V^\dagger\right) \ket{\frac{1}{2}, 1, 0}, ~ ~ ~ ~ ~ E_\text{gs} \ket{-\frac{1}{2}, 1, 0} = \left(H_d + V^\dagger \frac{1}{E_\text{gs} - H_d} V\right) \ket{-\frac{1}{2}, 1, 0}~.\\
-\end{equation}
+	\hspace*{-30pt}E_\text{gs} \ket{\frac{1}{2}, 1, 0} = \left(H_d + V \frac{1}{E_\text{gs} - H_d}V^\dagger\right) \ket{\frac{1}{2}, 1, 0}, \quad E_\text{gs} \ket{-\frac{1}{2}, 1, 0} = \left(H_d + V^\dagger \frac{1}{E_\text{gs} - H_d} V\right) \ket{-\frac{1}{2}, 1, 0}~.
+\end{eqnarray}
 These represent the Schrodinger equation for the states \(\ket{S_d^z, 1, 0}\), and the right hand sides therefore give the effective Hamiltonians for those states.
 If we combine the states into a single subspace \(\ket{1,0}= \left\{\ket{\frac{1}{2}, 1, 0}, \ket{-\frac{1}{2}, 1, 0}\right\}\), the effective Hamiltonian for this composite subspace becomes the sum of the two parts:
-\begin{align}
+\begin{eqnarray}
 	\label{eff_ham_10}
 	H^{1,0}_\text{eff}\ket{1, 0}\bra{1, 0} = \left(H_d + V G_0 V^\dagger + V^\dagger G_0  V\right) \ket{1, 0}~,
-\end{align}
+\end{eqnarray}
 where \(G_0 = \left(E_\text{gs} - H_d\right)^{-1}\).
@@
 the effective Hamiltonian is
-\begin{align}
-	H_\text{eff}^{1, 0} &= H_0 + \frac{J^2}{2\left(E_\text{gs} + \frac{J}{2}\right)}\left[1 + \frac{ H_0 + \left(\frac{1}{2} + S_d^z\right) s^+_\text{tot}X_{1,\text{tot}} - \left(\frac{1}{2} - S_d^z\right) s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 \left(E_\text{gs} + \frac{J}{2}\right)} + \frac{H_0^2}{\left(E_\text{gs} + \frac{J}{2}\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + \frac{J}{2}\right)^3} \right]~.
-\end{align}
+\begin{eqnarray}
+	H_\text{eff}^{1, 0} = H_0 + \frac{J^2}{2\left(E_\text{gs} + \frac{J}{2}\right)}&\left[1 + \frac{ H_0 + \left(\frac{1}{2} + S_d^z\right) s^+_\text{tot}X_{1,\text{tot}} - \left(\frac{1}{2} - S_d^z\right) s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 \left(E_\text{gs} + \frac{J}{2}\right)} + \frac{H_0^2}{\left(E_\text{gs} + \frac{J}{2}\right)^2} \right.\nonumber\\
+&\left.- \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + \frac{J}{2}\right)^3} \right]~.
+\end{eqnarray}
 We employed the definitions 
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 X_{n,\text{tot}} \equiv  \sum_l \sum_{k,k^\prime}\left(\epsilon_k - \epsilon_{k^\prime}\right)^n c^\dagger_{k \downarrow}c_{k^\prime \uparrow}, ~ ~ ~ Z_{1,\text{tot}} \equiv \sum_{k,k^\prime,l}\left( \epsilon_k - \epsilon_{k^\prime} \right) \frac{1}{2}\left(c^\dagger_{k \uparrow,l}c_{k^\prime \uparrow,l} - c^\dagger_{k \downarrow,l}c_{k^\prime \downarrow,l}\right)~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 There are several non-Fermi liquid terms of the form \(s^+_\text{tot}X_{1,\text{tot}}, s^-_\text{tot}X^\dagger_{1,\text{tot}},Z_{1,\text{tot}} H_0\).
@@
 the corresponding momentum space Hamiltonian is obtained from the Fourier transform:
-\begin{equation}
-H_{eff}^{off,(2)} |_{diag}= -\frac{4t^2}{3} \frac{1}{N} \bigg[ \displaystyle\sum_{k,\sigma} n_{k\sigma}(1-\frac{1}{N} \displaystyle\sum_{k_2}  n_{k_2,-\sigma}  ) + \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma} ( 1-\frac{1}{N} \displaystyle\sum_{ k_2} \tilde{n}_{k_2,-\sigma}  ) \bigg]~.
-\end{equation}
+\begin{eqnarray}
+H_{eff}^{off,(2)} |_{diag}= -\frac{4t^2}{3} \frac{1}{N} \left[ \displaystyle\sum_{k,\sigma} n_{k\sigma}(1-\frac{1}{N} \displaystyle\sum_{k_2}  n_{k_2,-\sigma}  ) + \displaystyle\sum_{k,\sigma} \tilde{n}_{k\sigma} ( 1-\frac{1}{N} \displaystyle\sum_{ k_2} \tilde{n}_{k_2,-\sigma}  ) \right]~.
+\end{eqnarray}
 The above relation leads to the self-energy correction to the kinetic energy, which is
-\begin{equation}
-\bar{\epsilon} _k-\epsilon_k = \Sigma_k = -\frac{4t^2}{3N^2}\bigg(1-\frac{N}{e^{(\epsilon_k-\mu)/k_BT}+1}\bigg)~.
+\begin{eqnarray}
+\bar{\epsilon} _k-\epsilon_k = \Sigma_k = -\frac{4t^2}{3N^2}\left(1-\frac{N}{e^{(\epsilon_k-\mu)/k_BT}+1}\right)~.
 \label{eq:self-energy-NFL}
-\end{equation}
+\end{eqnarray}
 Using the self-energy we calculate the impurity specific heat defined as $C_{imp}=C(J^*)-C(0)$ which is defined as
 \begin{eqnarray}
-C_{imp} &=& \sum_{\Lambda,\sigma} \beta \bigg[ \frac{(\bar{\epsilon}_{\Lambda})^2 e^{\beta \bar{\epsilon}_{\Lambda}}}{( e^{\beta \bar{\epsilon}_{\Lambda}} +1)^2}  -\frac{({\epsilon}_{\Lambda})^2 e^{\beta {\epsilon}_{\Lambda}}}{( e^{\beta {\epsilon}_{\Lambda}} +1)^2} \bigg]~.
+C_{imp} &=& \sum_{\Lambda,\sigma} \beta \left[ \frac{(\bar{\epsilon}_{\Lambda})^2 e^{\beta \bar{\epsilon}_{\Lambda}}}{( e^{\beta \bar{\epsilon}_{\Lambda}} +1)^2}  -\frac{({\epsilon}_{\Lambda})^2 e^{\beta {\epsilon}_{\Lambda}}}{( e^{\beta {\epsilon}_{\Lambda}} +1)^2} \right]~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\chi &=& \beta\bigg[\frac{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} \langle \bar{S}^{z2} \rangle}{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} } -\frac{\sum e^{-\beta \epsilon_{\Lambda}} \langle S^{z2 }\rangle }{\sum e^{-\beta \epsilon_{\Lambda}} } \bigg] ~.
+\chi &=& \beta\left[\frac{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} \langle \bar{S}^{z2} \rangle}{\sum e^{-\beta \bar{\epsilon}_{\Lambda}} } -\frac{\sum e^{-\beta \epsilon_{\Lambda}} \langle S^{z2 }\rangle }{\sum e^{-\beta \epsilon_{\Lambda}} } \right] ~.
 \end{eqnarray}
@@
 sengupta_1994,fabrizio_nozieres_1995,Coleman_tsvelik,fabrizio_gogolin_1995}.
-We find that taking less number of sites leads to a {\color{blue} yet higher} value of \(W\), which shows that taking more number of sites will lead to a value of \(W\) that is lower than \(8.3\) and closer to \(8/3\).
+We find that taking less number of sites leads to a yet higher value of \(W\), which shows that taking more number of sites will lead to a value of \(W\) that is lower than \(8.3\) and closer to \(8/3\).
+
+\subsection{Orthogonality catastrophe in the gapless excitations}
 
@@
 The three degenerate ground states are given as
-\begin{gather}
-|\alpha_{-1}\rangle = c|1000 \rangle-b (|0100 \rangle + |0010 \rangle+ | 0001 \rangle), ~ ~ |\alpha_{+1}\rangle = b(|1110 \rangle+ | 1101 \rangle + | 1011 \rangle)-c | 0111 \rangle,\\
+\begin{eqnarray}
+|\alpha_{-1}\rangle = c|1000 \rangle-b (|0100 \rangle + |0010 \rangle+ | 0001 \rangle), ~ ~ |\alpha_{+1}\rangle = b(|1110 \rangle+ | 1101 \rangle + | 1011 \rangle)-c | 0111 \rangle,\nonumber\\
 |\alpha_0\rangle = -a(|1100 \rangle + |1010\rangle +|1001 \rangle) + a(|0110 \rangle+| 0101 \rangle +| 0011\rangle)~,
-\end{gather}
+\end{eqnarray}
 where $a=0.408$, $b=0.289$, $c=0.866$.
@@
 \begin{eqnarray}
-H^{(2)}_{eff,off-diag} &=& \sum_{\substack{(ijk)=\\(123),(231),(312)}}\bigg[ c_{i\uparrow}c_{i\downarrow}^{\dagger} \bigg( -2ab \bigg\{ \Sigma_{jk} +c_{j\uparrow}^{\dagger}c_{j\downarrow}c_{k\uparrow}c_{k\downarrow}^{\downarrow} \bigg\} -ac(\Omega_{jk}+\tilde{\Omega}_{jk}) \bigg) + ~~\textrm{h.c.}\bigg] \otimes \hat{\Xi}_l~,
+	H^{(2)}_{eff,off-diag} = \sum_{\substack{(ijk)=\\(123),(231),(312)}}&\left[ c_{i\uparrow}c_{i\downarrow}^{\dagger} \left( -2ab \left\{ \Sigma_{jk} +c_{j\uparrow}^{\dagger}c_{j\downarrow}c_{k\uparrow}c_{k\downarrow}^{\downarrow} \right\} -ac(\Omega_{jk}+\tilde{\Omega}_{jk}) \right) \right.\nonumber\\
+										  &\left. + \textrm{h.c.}\right] \otimes \hat{\Xi}_l~,
 \end{eqnarray}
 where the different operators have the following definitions:
-\begin{gather}
-\Sigma_{i,j} = n_{i\uparrow}(1-n_{i\downarrow}) (1-n_{j\uparrow})n_{j\downarrow} + (1-n_{i\uparrow})n_{i\downarrow} n_{j\uparrow} (1 -n_{j\downarrow}), ~ ~\Omega_{i,j} =4S_i^z S_j^z n_{i\uparrow} n_{j\uparrow}, ~ ~ \tilde{\Omega}_{i,j} = 4S_{i}^zS_j^z (1-n_{i\uparrow})(1-n_{j\uparrow}) \nonumber~,\\
- \hat{\Xi}_l=  ( c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.})~.
-\end{gather}
+\begin{eqnarray}
+\fl \Sigma_{i,j} = n_{i\uparrow}(1-n_{i\downarrow}) (1-n_{j\uparrow})n_{j\downarrow} + (1-n_{i\uparrow})n_{i\downarrow} n_{j\uparrow} (1 -n_{j\downarrow}), ~ ~\Omega_{i,j} =4S_i^z S_j^z n_{i\uparrow} n_{j\uparrow}, ~ ~ \tilde{\Omega}_{i,j} = 4S_{i}^zS_j^z (1-n_{i\uparrow})(1-n_{j\uparrow}) \nonumber~,\\
+\fl \hat{\Xi}_l=  ( c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.})~.
+\end{eqnarray}
 
@@
 This leads to the Hamiltonian flow equation~\cite{anirbanurg1}
-\begin{equation}
+\begin{eqnarray}
 \centering
@@
 H_{(j-1)}=U_{(j)}H_{(j)}U^{\dagger}_{(j)}~,
-\end{equation}
+\end{eqnarray}
 where the unitary operation $U_{(j)}$ is the unitary map at RG step $j$. 
@@
 on the isogeometric curve and has the form~\cite{anirbanmott1,anirbanurg1}
-\begin{equation}
+\begin{eqnarray}
 \centering U_{(j)}=\prod_{l}U_{j,l}, U_{j,l}=\frac{1}{\sqrt{2}}\sum_l [1+\eta_{j,l}-\eta^{\dagger}_{j,l}]~,
-\end{equation}
+\end{eqnarray}
 where \(l\) sums over the states on the isoenergetic shell at distance \(\Lambda_j\), and $\eta_{j,l}$ are electron-hole transition operators following the algebra
-\begin{equation}
+\begin{eqnarray}
 	\left\{\eta_{j,l},\eta_{j,l}^{\dagger}\right\} = 1~,~\left[\eta_{j,l},\eta_{j,l}^{\dagger}\right] = 2\hat n_{j,l} - 1~.
-\end{equation}
+\end{eqnarray}
 The transition operator can be expressed in terms of the off-diagonal part of the Hamiltonian, \(H^X_{j,l} = Tr_{j,l}(c^{\dagger}_{j,l}H_{j})c_{j,l} + \text{h.c.}\), and the diagonal part \(H^D_{j,l}\) (kinetic energy and self-energies):
 \begin{eqnarray}
-	\eta_{j,l}&=&Tr_{j,l}(c^{\dagger}_{j,l}H_{j,l})c_{j,l}\frac{1}{\hat{\omega}_{j,l}-Tr_{j,l}(H^{D}_{j,l}\hat{n}_{j,l})\hat{n}_{j,l}}~.~~\label{e-TransOp}
+	\eta_{j,l}&=&Tr_{j,l}(c^{\dagger}_{j,l}H_{j,l})c_{j,l}\frac{1}{\hat{\omega}_{j,l}-Tr_{j,l}(H^{D}_{j,l}\hat{n}_{j,l})\hat{n}_{j,l}}~.\label{e-TransOp}
 \end{eqnarray}
@@
 The generic forms of $H^{D}_{j,l}$ and $H^{X}_{j,l}$ are as follows
-\begin{equation}\begin{aligned}
-H^{D}_{j,l}=&\sum_{\Lambda\hat{s},\sigma}\epsilon^{j,l}\hat{n}_{\mathbf{k}_{\Lambda\hat{s}},\sigma}+\sum_{\alpha}\Gamma_{\alpha}^{4,(j,l)}\hat{n}_{\mathbf{k}\sigma}\hat{n}_{\mathbf{k}'\sigma'} +\sum_{\beta}\Gamma_{\beta}^{6,(j,l)}\hat{n}_{\mathbf{k}\sigma}\hat{n}_{\mathbf{k}'\sigma'}\hat{n}_{\mathbf{k}''\sigma''}+\ldots~,\\
+\begin{eqnarray}
+H^{D}_{j,l}=&\sum_{\Lambda\hat{s},\sigma}\epsilon^{j,l}\hat{n}_{\mathbf{k}_{\Lambda\hat{s}},\sigma}+\sum_{\alpha}\Gamma_{\alpha}^{4,(j,l)}\hat{n}_{\mathbf{k}\sigma}\hat{n}_{\mathbf{k}'\sigma'} +\sum_{\beta}\Gamma_{\beta}^{6,(j,l)}\hat{n}_{\mathbf{k}\sigma}\hat{n}_{\mathbf{k}'\sigma'}\hat{n}_{\mathbf{k}''\sigma''}+\ldots~,\nonumber\\
 H^{X}_{j,l}=&\sum_{\alpha}\Gamma_{\alpha}^{2}c^{\dagger}_{\mathbf{k}\sigma}c_{\mathbf{k}'\sigma'}+\sum_{\beta}\Gamma_{\beta}^{4}c^{\dagger}_{\mathbf{k}\sigma}c^{\dagger}_{\mathbf{k}'\sigma'}c_{\mathbf{k}_{1}'\sigma_{1}'}c_{\mathbf{k}_{1}\sigma_{1}}+\ldots~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 The indices \(\alpha\) and \(\beta\) are strings that denote the quantum numbers of the incoming and outgoing electronic states at a particular interaction vertex \(\Gamma^n_{\alpha}\) or  \(\Gamma^m_{\beta}\).
@@
 Accounting for only the leading tangential scattering processes, as well as other momentum transfer processes along the normal direction $\hat{s}$, the renormalised Hamiltonian \(H_{(j-1)}\) has the form~\cite{anirbanurg1}
-\begin{equation}
+\begin{eqnarray}
 \hspace*{-0.1cm}Tr_{j,(1,\ldots,2n_{j})}(H_{(j)})+\sum_{l=1}^{2n_{j}}\lbrace c^{\dagger}_{j,l}Tr_{j,l}(H_{(j)}c_{j,l}),\eta_{j,l}\rbrace\tau_{j,l}~.\label{HRG}
-\end{equation}
+\end{eqnarray}
 The RG fixed point is reached when the denominator in Eq.~\ref{e-TransOp} vanishes, at a certain energy scale \(\Lambda^*\).
@@
 The IOMs have been stripped of any number fluctuations and are therefore diagonal in the basis of the number operators for each of the decoupled degrees of freedom.
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	H^* = \sum_{\Lambda_j < \Lambda^*} H^*(\Lambda_j) + \sum_{\Lambda_j > \Lambda^*}H_\text{IOMs}(\Lambda_j)
-\end{aligned}\end{equation}
+\end{eqnarray}
 The effective Hamiltonian can be used to construct the corresponding thermal density matrix and hence the partition function at a temperature \(T\):
-\begin{equation}
+\begin{eqnarray}
 Z^* = \mathrm{Tr}\left[ \hat{\rho}^*\right] = \mathrm{Tr}\left[ e^{-\beta \hat{H}^{*}}\right] = \mathrm{Tr}\left[ U^{\dagger} e^{-\beta \hat{H}^{*}} U\right] = \mathrm{Tr}\left[ e^{-\beta \hat{H}}\right] = Z
 \label{partfunc}~,
-\end{equation}
+\end{eqnarray}
 where \(\beta = 1/k_B T\), \(U = \prod_{1}^{j^{*}}U_{(j)}\), $H$ is the bare Hamiltonian and $j^{*}$ is the RG step at which the IR stable fixed point is reached.
@@
 The Hamiltonian for the channel-isotropic MCK model is:
-\begin{gather}
-	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\alpha^\prime= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~.
-\end{gather}
+\begin{eqnarray}
+	H = \sum_l\left[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\alpha^\prime= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\right]~.
+\end{eqnarray}
 
@@
 The complete generator up to third order can be written as
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\eta = \frac{1}{\hat \omega - H_D}T^\dagger c \simeq \frac{1}{\omega^\prime - H_D}T^\dagger c + \frac{1}{\omega^\prime - H_D}H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X~,
-\end{aligned}\end{equation}
+\end{eqnarray}
 where \(H_X = J \sum_{k,k^\prime < \Lambda_j, \alpha,\alpha^\prime}\vec{S_d}\cdot\vec{s}_{\alpha \alpha^\prime}c^\dagger_{k\alpha}c_{k^\prime\alpha^\prime}\) is scattering between the entangled electrons.
@@
 The total renormalisation takes the form:
-\begin{equation}
+\begin{eqnarray}
 	\label{full_ren}
-	\Delta H_{(j)} = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c  + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(2)}_{(j)}} + \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(3)}_{(j)}}~.
-\end{equation}
+	\fl \Delta H_{(j)} = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c  + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(2)}_{(j)}} + \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(3)}_{(j)}}.\qquad
+\end{eqnarray}
 \(\Delta H^{(2)}_{(j)}\) and \(\Delta H^{(3)}_{(j)}\) are the renormalisation arising from the second and third order processes respectively.
@@
 In terms of these eigenstates, the Hamiltonian becomes
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{H_spin_S}
 	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{m_d=-S}^S \sum_{kl,\atop{\sigma=\uparrow,\downarrow}} J^\sigma_{m_d} \ket{m_d}\bra{m_d} c^\dagger_{k \sigma}c_{l \sigma} + \sum_{kl} \sum_{m_d=-S}^{S-1} J^t_{m_d} \left(\ket{m_d+1}\bra{m_d} s^-_{kl}  + \text{h.c.}\right)~,
-\end{aligned}\end{equation}
+\end{eqnarray}
 where \(k,l\) sum over the momentum states, \(\sigma\) sums over the spin indices, \(J^\sigma_m = \frac{1}{2} \sigma m J\) in the UV Hamiltonian, and \(J^t_{m} = J\frac{1}{2}\sqrt{S(S+1) - m(m+1)}\) is the coupling that connects \(\ket{m}\) and \(\ket{m+1}\).
@@
 
-\begin{align}
-	z|z: & \sum_{kk^\prime,m,\sigma} c^\dagger_{q \sigma} c_{k^\prime \sigma} \ket{m}\bra{m}\frac{{J^\sigma_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}\sigma S_d^z}\ket{m}\bra{m} c^\dagger_{k \sigma}c_{q \sigma} = -\sum_{kk^\prime,m,\sigma}n_{q \sigma}\frac{{J^\sigma_m}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma} \ket{m}\bra{m}}{\omega_{m, \sigma} - \frac{D}{2} + \frac{J}{2}\sigma m}~,\\
-	+|-: & \sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m+1, \uparrow} - \frac{D}{2} + \frac{J}{2}\left( m+1 \right) }~.
-\end{align}
+\begin{eqnarray}
+	\hspace*{-40pt}z|z: & \sum_{kk^\prime,m,\sigma} c^\dagger_{q \sigma} c_{k^\prime \sigma} \ket{m}\bra{m}\frac{{J^\sigma_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}\sigma S_d^z}\ket{m}\bra{m} c^\dagger_{k \sigma}c_{q \sigma} = -\sum_{kk^\prime,m,\sigma}n_{q \sigma}\frac{{J^\sigma_m}^2 c^\dagger_{k \sigma}c_{k^\prime\sigma} \ket{m}\bra{m}}{\omega_{m, \sigma} - \frac{D}{2} + \frac{J}{2}\sigma m}~,\nonumber\\
+	\hspace*{-40pt}+|-: & \sum_{kk^\prime,m} c^\dagger_{q \uparrow} c_{k^\prime \downarrow} \ket{m}\bra{m+1}\frac{{J^t_m}^2}{\omega - \frac{D}{2} + \frac{J}{2}S_d^z}\ket{m+1}\bra{m} c^\dagger_{k \downarrow}c_{q \uparrow} = -n_{q \uparrow}\sum_{kk^\prime,m}\frac{{J^t_m}^2 c^\dagger_{k \downarrow}c_{k^\prime\downarrow} \ket{m}\bra{m}}{\omega_{m+1, \uparrow} - \frac{D}{2} + \frac{J}{2}\left( m+1 \right) }~.
+\end{eqnarray}
 We similarly compute the rest of the terms.
@@
 The renormalisation in \(J^\sigma_m\) is
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\Delta J^\sigma_{m} = - n(D) \frac{\left( J^\sigma_m \right) ^2 + \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 Here, we have defined \(J^t_m = 0\) for \( |m| > S\).
@@
 The RG equation for the sum of the couplings is
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\Delta J^+_m = -n(D)\frac{\sum_\sigma \left( J^\sigma_m \right) ^2 + \sum_\sigma \left( J^t_{m-\frac{1+\sigma}{2}} \right) ^2}{2\left(\omega - \frac{D}{2} + \frac{J}{4}\right)} = -n(D)\frac{J^2}{4}\frac{S(S+1)}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 This is an \(m-\)independent piece, so it can be summed over to produce an impurity-independent potential scattering term, which we ignore.
@@
 The second is the RG equation for the difference of the couplings:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\Delta J^-_m = -n(D)\frac{1}{2}\frac{\left( J^t_{m-1} \right) ^2 - \left(J^t_{m}\right) ^2}{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{4}\frac{n(D) m J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 The usual \(J\) Kondo coupling is recovered through \(J = 2J^-_m/m\). Substituting this gives 
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\Delta_\text{p sector} J = -\frac{1}{2}n(D)\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 
 We can also obtain the RG equation for \(J\) from the transverse renormalisation:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\Delta J^t_m &= - \frac{n(D)J^t_m \left( J^\downarrow_m + J^\uparrow_{m+1} \right) }{\omega - \frac{D}{2} + \frac{J}{4}} = -\frac{1}{2}\frac{n(D)J^t_m J}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 Since \(J^t_m \propto J\), we have
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\Delta J_\text{p sector} &= -\frac{1}{2}\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 The total renormalisation from both particle and hole sectors, at this order, is
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\Delta J^{(2)} &= -\frac{n(D)J^2}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 
@@
 Following eq.~\ref{full_ren}, the next order renormalisation is
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{psector_3rd_ren}
 	\Delta H^{(3)}_j = c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 The first term will be of the form
-\begin{equation}\begin{aligned}
-	\sum_{q,k,l_1} c^\dagger_{q\beta, l_1}c_{k \alpha, l_1}\ket{m_1}\bra{m_2} \frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z} \ket{m_2} c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \bra{m_3}\frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z}\ket{m_3}\bra{m_4}c^\dagger_{k\alpha, l_1}c_{q\beta, l_1}~.
-\end{aligned}\end{equation}
+\begin{eqnarray}
+\fl\sum_{q,k,l_1} c^\dagger_{q\beta, l_1}c_{k \alpha, l_1}\ket{m_1}\bra{m_2} \frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z} \ket{m_2} c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \bra{m_3}\frac{1}{\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J}{4}S_d^z}\ket{m_3}\bra{m_4}c^\dagger_{k\alpha, l_1}c_{q\beta, l_1}.\qquad
+\end{eqnarray}
 We have not bothered to write all the summations and the couplings correctly, because we will only simplify the denominator here. Evaluating the inner products gives
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\sum_{qk,l_1} \frac{\ket{m_1}\bra{m_4}c^\dagger_{q\beta}c_{k \alpha}c^\dagger_{k_1 \sigma_1, l_2}}{\omega_{m_2,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_2}{4}}  \frac{c_{k_2 \sigma_2,l_2}c^\dagger_{k\alpha}c_{q\beta}}{\omega_{m_3,\beta} - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{\beta J m_3}{4}}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 We again use \(\omega_{m,\sigma} \to \omega - \frac{J}{2}\left(m\sigma - \frac{1}{2}\right)\).
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}\sum_{qk,l_1} \frac{\hat n_{q\beta}\left(1 - \hat n_{k\alpha}\right)}{\left(\omega - \frac{D}{2} - \frac{\epsilon_k}{2} + \frac{J}{4}\right)^2}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 We define \(\sum_q \hat n_{q\beta} = n(D)\). Performing the sums over \(k\) and \(l_1\) gives
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	-\frac{1}{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2} \frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 \(\rho\) is the density of states which we have taken to be constant. Reinstating the complete summation and the couplings gives
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{first_group}
 	-\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{2}\lambda_{3}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 There is no sum over \(m_2\) and \(m_3\) because they are constrained by \(m_1\) and \(m_4\) respectively.
@@
 The second term in eq.~\ref{psector_3rd_ren} can be evaluated in an almost identical fashion. The integral here will be negative of the first term, because of an exchange in the scattering processes.
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\label{second_group}
 	\frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\sum_{m_1,m_4,k_1,k_2,\atop{l_2,\sigma_1\sigma_2}}\lambda_{1}\lambda_{3}\lambda_{2}\ket{m_1}\bra{m_4}c^\dagger_{k_1 \sigma_1, l_2}c_{k_2 \sigma_2,l_2}~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 The first group of terms (those that appear in \ref{first_group}) in the particle sector can be represented as \(a|b^\prime|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three connected processes.
@@
 The total renormalisation in  \(J^\sigma_m\) is
-\begin{equation}\begin{aligned}
-	\Delta J^\sigma_m = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\left[\left( J^t_{m-1} \right)^2 J^\sigma_m + \left( J^t_m \right)^2 J^\sigma_m - \left( J^t_{m-1} \right)^2 J^\sigma_{m-1} - \left(J^t_m\right)^2 J^\sigma_{m+1} \right] = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3 m \sigma~.
-\end{aligned}\end{equation}
+\begin{eqnarray}
+	\hspace*{-20pt}\Delta J^\sigma_m = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}\left[\left( J^t_{m-1} \right)^2 J^\sigma_m + \left( J^t_m \right)^2 J^\sigma_m - \left( J^t_{m-1} \right)^2 J^\sigma_{m-1} - \left(J^t_m\right)^2 J^\sigma_{m+1} \right] = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3 m \sigma~.\qquad
+\end{eqnarray}
 Since we had defined \(J^\sigma_m \equiv \frac{1}{2}J m \sigma\), we have \(\Delta J = \frac{2}{m\sigma}\Delta J^\sigma_m\), and we get \(\Delta_\text{p sector} J = \frac{1}{4}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3\).
 Combining with the hole sector renormalisation, we get
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\Delta J^{(3)} = \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 The total renormalisation in \(J\) after combining all orders is
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\Delta J = -\frac{n(D) J^2}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{2}\frac{\rho n(D) K}{\omega - \frac{D}{2} + \frac{J}{4}}J^3~.
-\end{aligned}\end{equation}
+\end{eqnarray}
+
+\section*{References}
 

### 2023-01-07 manuscript/mscript_mck_full.tex
further changes to layout

@@
 \usepackage{iopams}  
-\usepackage{braket,graphicx,amsmath,hyperref}
+\usepackage{braket,graphicx,amsmath}
+\usepackage[hidelinks]{hyperref}
 \bibliographystyle{unsrt}
@@
 
-% \maketitle
-
 \ioptwocol
@@
 Importantly, our approach enables a comparison of, for instance, the inter-channel mutual information along the RG flow and as functions of the excitation energies, providing insight into the nature of the fixed point theory.
-%}
 
@@
 	\label{mc_ham}
-	H = \sum_l\bigg[\sum_{\substack{k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{kk^\prime\\\alpha,\alpha^\prime= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}\bigg]~,~~
+	\hspace*{-5pt}H = \sum_{\substack{l,k\\\alpha=\uparrow,\downarrow}}\epsilon_{k,l} \hat n_{k\alpha,l} + \frac{\mathcal{J}}{2}\sum_{\substack{l,kk^\prime\\\alpha,\alpha^\prime= \uparrow,\downarrow}} \vec{S_d}\cdot\vec{\sigma}_{\alpha\alpha^\prime}c_{k\alpha,l}^\dagger c_{k^\prime\alpha^\prime, l}~,
 \end{eqnarray}
@@
 At the $j^{th}$ RG step, we focus on decoupling the highest energy electronic state denoted by $\ket{j}$.
-%Given the most energetic electronic state at the \(j^\mathrm{th}\) RG step is \(\ket{j}\) and defined by the energy \(D_{(j)}\), 
 The Hamiltonian will in general not conserve the number of particles in this state: \(\left[H_{(j)}, \hat n_{j}\right] \neq 0\), and the unitary transformation \(U_{(j)}\) causes this number fluctuation to vanish
-%at the next RG step
 ~\cite{anirbanurg1,anirbanurg2}:
@@
 	\centering
-	\includegraphics[width=0.30\textwidth]{stargraph.pdf}
+	\includegraphics[width=0.35\textwidth]{stargraph.pdf}
 	\caption{Zero bandwidth limit of the fixed point Hamiltonian.
@@
 Moreover, in the following sections, we will show how the inherent quantum-mechanical frustration of singlet order that is present in the Hamiltonian leads to the non-trivial physics of the fixed points in terms of non-Fermi liquid phase, diverging thermodynamic quantities, quantum criticality as well as emergent gauge theories.
-\section{Important Properties of the Star Graph}
+\section{Important properties of the star graph}
 \label{sec:props_star}
@@
 where the \(\prime\) indicates derivative with respect to \(h\). At low temperatures, the susceptibility takes the form
-\begin{equation}
+\begin{eqnarray}
 	\chi \to \frac{\beta\Sigma_\mathrm{max}}{2M_\mathrm{max}\left(2M_\mathrm{max}+1\right)^2} = \frac{\beta(K-1)}{12(K+1)} \sim \frac{1}{T}~.
-\end{equation}
+\end{eqnarray}
 
@@
 
-The magnetization is therefore discontinuous as \(h\to 0\) when \(K>1\).
+The magnetization is therefore discontinuous as \(h\to 0\) for \(K>1\).
 The non-analyticity occurs because the magnetic field is able to flip the \(J^z=\pm (K-1)/2\) state into the state of the opposite magnetisation.
@@
 \begin{eqnarray}
-\hat{T} &=& e^{i\frac{2\pi}{K} \hat{\Sigma}} ~,~\hat{O} = e^{i\hat{\phi}}~,~~\hat{\Sigma}=[\hat{J}^z-(K-1)/2]~.
+\hat{T} = e^{i\frac{2\pi}{K} \hat{\Sigma}} ~,~\hat{O} = e^{i\hat{\phi}}~,~~\hat{\Sigma}=[\hat{J}^z-(K-1)/2]~.
 \end{eqnarray}
 One can see that the generators of thee above operators commute with the Hamiltonian: $[H,J^x]=[H,J^z]=[H,J^z]=0$. In the large \(K\) limit, we can perform a semi-classical approximation. 
-%As $J^x$ and $J^y$ both commute with the Hamiltonian $H$, we can write $[H,J^y{(J^{x})}^{-1}]=0$, and any non-singular function of these operators must also commute with the Hamiltonian, such that
 Thus, we define
 \begin{eqnarray}
-%\hat{\phi}=\tan^{-1}(\hat{J}^y(\hat{J}^x)^{-1})~.
 e^{i\hat{\phi}} = \frac{J_{x}}{\sqrt{J^{2} - J_{z}^{2}}} + i\frac{J_{y}}{\sqrt{J^{2} - J_{z}^{2}}}~,
@@
 The operations of the translation operators on these states are then given by
-\begin{equation}
+\begin{eqnarray}
 \hat{T}|M_i\rangle = e^{i\frac{2\pi}{K} [M_i-(K-1)/2]} |M_i\rangle = e^{i2\pi\frac{p_i}{K} } |M_i\rangle~,~p_i\in[K]~.
-\end{equation}
+\end{eqnarray}
 The braiding rule between the twist and the translation operators is
 \begin{eqnarray}
-\hat{T}\hat{O}\hat{T}^{\dagger}\hat{O}^{\dagger} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},i\hat{\phi}]}=e^{i\frac{2\pi }{K}} ~,\nonumber\\
-\hat{T}\hat{O}^m\hat{T}^{\dagger}\hat{O}^{\dagger m} &=& e^{\frac{2\pi }{K}[i\hat{\Sigma},im\hat{\phi}]}=e^{i2\pi \frac{m}{K}}~.
-\end{eqnarray}
-%Next, we shown that the states $\hat{O}^m |M_i\rangle$ are orthogonal to each other and with the state $|M_i\rangle$.
+\hat{T}\hat{O}\hat{T}^{\dagger}\hat{O}^{\dagger} = e^{\frac{2\pi }{K}[i\hat{\Sigma},i\hat{\phi}]}=e^{i\frac{2\pi }{K}} ~,\nonumber\\
+\hat{T}\hat{O}^m\hat{T}^{\dagger}\hat{O}^{\dagger m} = e^{\frac{2\pi }{K}[i\hat{\Sigma},im\hat{\phi}]}=e^{i2\pi \frac{m}{K}}~.
+\end{eqnarray}
 The states $\hat{O}^m |M_i\rangle$ (with distinct $m$) are labelled by different eigenvalues of the translation operations, and are thus orthogonal to each other
@@
 \end{eqnarray}
-%Different states $\hat{O}^m |M_i\rangle$ for different $m$ are therefore labeled by different eigenvalues of the translation operations, and are thus orthogonal to each other. 
 As the twist operator $\hat{O}$ commutes with the Hamiltonian, we can write
@@
 \label{sec:loc_mott_liquid}
-%By applying the unitary renormalization group method on the zero mode star graph Hamiltonian, we decouple the impurity spin from the zero-modes of the $K$ channels: 
 In order to obtain the effective theory for the K zero modes, we will now use the URG method to decouple the impurity site from the star graph. The starting point is the star graph Hamiltonian
@@
 \begin{eqnarray}
-\Delta H &=& H_X ({\hat{\omega}-H_D})^{-1} H_X 
+\Delta H = H_X ({\hat{\omega}-H_D})^{-1} H_X 
 \end{eqnarray}
@@
 We use this expectation value to replace the denominator of the above RG equation.
-\begin{equation}
+\begin{eqnarray}
 \beta_{\uparrow} ({\mathcal{J}},\omega_{\uparrow}) = ({\mathcal{J}}^2 \Gamma_{\uparrow})/2 ~,~~\Gamma_{\uparrow}=(\omega_{\uparrow}-{\mathcal{J}}(S_d^z-1))^{-1}~.
-\end{equation}
+\end{eqnarray}
 The effective Hamiltonian is therefore
@@
 In terms of the electronics degree of freedom, this can be written as
-\begin{equation}
-\frac{ \beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow}) }{4}  \sum_{\substack{i\neq j \\ \alpha_i,\beta_i\in \{\uparrow,\downarrow\}\\ \alpha_j,\beta_j\in \{\uparrow,\downarrow\}}}\left(\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)}    c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)} +\textrm{h.c.}\right) ~.
+\begin{eqnarray}
+	\frac{ \beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow}) }{4}  \sum_{i\neq j}\sum_{\alpha_i,\beta_i}\sum_{\alpha_j,\beta_j}&\left(\vec{\sigma}_{\alpha_i\beta_i}\vec{\sigma}_{\alpha_j\beta_j}  c_{0\alpha_i}^{(i)\dagger}  c_{0\beta_i}^{(i)} c_{0\alpha_j}^{(j)\dagger}  c_{0\beta_j}^{(j)} \right.\nonumber\\
+																   &\left. +\textrm{h.c.}\right) ~.
 \label{eq:all-to-all_1}
-\end{equation}
+\end{eqnarray}
 The case $\frac{\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})}{2} <0$ leads to a ferromagnetic effective Hamiltonian.
@@
 Applying this operator, we get the twisted Hamiltonian
-\begin{equation}
-H(\Phi) = -\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} S^2   +\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} \bigg(S^{z}-\frac{\Phi}{\Phi_0} \bigg)^2 ~.
+\begin{eqnarray}
+	H(\Phi) = -\frac{|\beta_{\uparrow}({\mathcal{J}},\omega_{\uparrow})|}{2} \left[S^2 - \left(S^{z}-\frac{\Phi}{\Phi_0} \right)^2\right] ~.
 \label{eq:flux_spectral}
-\end{equation}
+\end{eqnarray}
 One can thus explore different $S^z$ ground states via this spectral flow (flux insertion) argument.
@@
 \begin{eqnarray}
-H^{(0)}_{2CK}&=& {\mathcal{J}} \vec{S}_d.(\vec{S}_1+\vec{S}_2)~~,~~\vec{S}_i =  \frac{1}{2}~ c_{i,\alpha}^{\dagger}~ \vec{\sigma}_{\alpha,\beta}~ c_{i,\beta}~.
+H^{(0)}_{2CK}= {\mathcal{J}} \vec{S}_d.(\vec{S}_1+\vec{S}_2)~~,~~\vec{S}_i =  \frac{1}{2}~ c_{i,\alpha}^{\dagger}~ \vec{\sigma}_{\alpha,\beta}~ c_{i,\beta}~.
 \label{eq:channel-2-spin}
@@
 \begin{eqnarray}
-H_{X} &=& -t \displaystyle\sum_{\substack{<1,l_1> \\ <2,l_2>}} (c^{\dagger}_{1,\sigma}c_{l_1,\sigma}+c^{\dagger}_{2,\sigma}c_{l_2,\sigma}+ ~\textrm{h.c.})~,
+H_{X} = -t \displaystyle\sum_{<1,l_1>}\sum_{<2,l_2>} (c^{\dagger}_{1,\sigma}c_{l_1,\sigma}+c^{\dagger}_{2,\sigma}c_{l_2,\sigma}+ ~\textrm{h.c.}),
 \end{eqnarray}
@@
 \begin{eqnarray}
-\mathcal{H} &=& \frac{{\mathcal{J}}\hbar}{2}~ \vec{S}_d.
+\mathcal{H} = \frac{{\mathcal{J}}\hbar}{2}~ \vec{S}_d.
 \displaystyle\sum_{i=\{1,2\}} \displaystyle\sum_{\alpha,\beta\in\{\uparrow,\downarrow\}}c_{i\alpha}^{\dagger} \vec{\sigma}_{\alpha\beta} c_{i\beta} + H_X~.
@@
 In this expanded basis, there are $32$ degenerate ground states:
-\begin{equation}
+\begin{eqnarray}
 \label{gstate-set}
 \left\{ \ket{\alpha_i} \right\} = \left\{ \ket{J^z}\otimes\ket{n_{l_1,\uparrow},n_{l_1,\downarrow},n_{l_2,\uparrow},n_{l_2,\downarrow}} \right\}~.
-\end{equation}
+\end{eqnarray}
 The \(32-\)fold degeneracy arises from the two-fold degeneracy of \(J^z\) (\(J^z = \pm 1/2\)) multiplying the \(16-\)fold degeneracy of the rest of the sites \(n_{l_i,\sigma}\) (each of the four \(n_{l_i,\sigma}\) can be 0 or 1, leading to a \(2^4\)-fold degeneracy).
@@
 \begin{eqnarray}
-H^{(1)} &=& \sum_{ij} |\alpha_i\rangle \langle \alpha_i  | V| \alpha_j \rangle \langle \alpha_j |~.\nonumber\\
-H^{(2)} &=& \sum_{ij} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j |~.
+H^{(1)} = \sum_{ij} |\alpha_i\rangle \langle \alpha_i  | V| \alpha_j \rangle \langle \alpha_j |~.\nonumber\\
+H^{(2)} = \sum_{ij} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j |~.
 \end{eqnarray}
@@
 These second order corrections are given by
-\begin{equation}
+\begin{eqnarray}
 H^{(2)}_\mathrm{diag}\left(\tilde \alpha_0\right)  = \frac{2t^2}{E_0} \hat{I} - \Omega_l, ~ ~ H^{(2)}_\mathrm{diag}\left(\tilde \alpha_1\right) = \frac{2t^2}{E_0} \hat{I} + \Omega_l ~,
-\end{equation}
+\end{eqnarray}
 where $S_{l_i}^z=(n_{l_i\uparrow}-n_{l_i\downarrow})/2$ and $\Omega_l=\frac{2t^2}{3E_0} ( S_{l_1}^z + S_{l_2}^z)$.
@@
 The fact there is no non-trivial diagonal renormalisation to the low-energy excitations shows the absence of (local) Fermi liquid terms.
-%, the exact cancellation of the field terms \(\pm \Omega_l\).
 
 \subsubsection{Off-diagonal renormalisation}
-The off-diagonal contribution to the second order effective Hamiltonian is 
-\begin{eqnarray}
-H_{NFL}&=&H^{(2)}_{od} = \sum_{i\neq j} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j | \nonumber\\
-&=& -\frac{8t^2}{3} [ (S_1^z)^2 c_{2\uparrow}^{\dagger}c_{2\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) \nonumber\\
-&+& (S_2^z)^2 c_{1\uparrow}^{\dagger}c_{1\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) ] + \textrm{h.c.} ~.
+The off-diagonal contribution to the second order effective Hamiltonian is obtained purely from \(H^{(2)}_{od}\):
+\begin{eqnarray}
+	H_{NFL} &= \sum_{i\neq j} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j | \nonumber\\
+			       &= -\frac{8t^2}{3} [ (S_1^z)^2 c_{2\uparrow}^{\dagger}c_{2\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) \nonumber\\
+&+ (S_2^z)^2 c_{1\uparrow}^{\dagger}c_{1\downarrow}  (  c_{l_1\uparrow}c_{l_1\downarrow}^{\dagger} +  c_{l_2\uparrow}c_{l_2\downarrow}^{\dagger}  ) ] + \textrm{h.c.} ~.
 \label{eq:hamiltonian_NFL}
@@
 	\label{nfl_terms}
-	V_\mathrm{eff} = \frac{2t^2}{{\mathcal{J}^*}}\left[\left(\sigma^z_{0,1}\right)^2 s^+_{0,2} + \left(\sigma^z_{0,2}\right)^2 s^+_{0,1}\right] \left(s^-_{1,1} + s^-_{1,2}\right) + \mathrm{h.c.}~;
+	\hspace*{-5pt}V_\mathrm{eff} = \frac{2t^2}{{\mathcal{J}^*}}\left[\left(\sigma^z_{0,1}\right)^2 s^+_{0,2} + \left(\sigma^z_{0,2}\right)^2 s^+_{0,1}\right] \left(s^-_{1,1} + s^-_{1,2}\right) + \mathrm{h.c.};\nonumber\\
 \end{eqnarray}
@@
 	\label{k_space_od}
-	\sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \mathrm{h.c.} ~.\qquad
+	\frac{2t^2}{J}\sum_{\left\{k_i,k_i^\prime\right\}}\sum_{\sigma, l} &\left(e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l}\right.\nonumber\\
+									   &\left. + \mathrm{h.c.}\right) ~.\qquad
 \end{eqnarray}
@@
 \begin{eqnarray}
-	H_\mathrm{eff,MFL} &= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{2t^2e^{i\left(k_1 - k_2\right)a}}{J} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \mathrm{h.c.}\nonumber\\
+	H_\mathrm{MFL} &= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{2t^2e^{i\left(k_1 - k_2\right)a}}{J} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \mathrm{h.c.}\nonumber\\
 	&= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right).\qquad 
@@
 	\label{mfl_large}
-	H^*_\mathrm{eff,MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)~.
+	H^*_\mathrm{MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\rho_{d}&=& \textrm{Tr}_{d} \rho=\sum_{S_d^z} \langle S_d^z| \rho | S^z_d\rangle ~,~~EE_d = -\rho_{d} \log \rho_{d}~.
+\rho_{d}= \textrm{Tr}_{d} \rho=\sum_{S_d^z} \langle S_d^z| \rho | S^z_d\rangle ~,~~EE_d = -\rho_{d} \log \rho_{d}~.
 \end{eqnarray}
@@
 as~\cite{siddharthatee} 
-\begin{equation}
+\begin{eqnarray}
 I^{N}_{\{\mathcal{A}_N\}} = \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.
 \label{eq:I_N_definition}
-\end{equation}
+\end{eqnarray}
 where  $\mathcal{B}_m(\{\mathcal{A}_N\})\equiv \{ Q~| ~Q\subset \mathcal{P}(\{\mathcal{A}_{N}\}), |Q|=m \}$, and $\mathcal{P}(\{\mathcal{A}_{N}\})$ is the powerset of $\{\mathcal{A}_N\}$.
 For simplicity, we also define the union and intersection of all the subsystems present in $Q$ as ${V}_{\cup}({Q})\equiv \bigcup_{A\in Q} A$ and ${V}_{\cap}({Q})\equiv \bigcap_{A\in Q} A$ respectively.
-%One can measure $N-$partite information for a collection of subsystems (CSS) $\{\mathcal{A}_N\}\equiv\{A_1,A_2,\cdots,A_N\}$.
-To define the $N-$partite information, we first define the power set of the CSS $\{\mathcal{A}_N\}$ as $\mathcal{P}(\{\mathcal{A}_{N}\})$, and the collection of all subsets of $\mathcal{P}(\{\mathcal{A}_{N}\})$ with $m$ subsystems in it as $\mathcal{B}_m(\{\mathcal{A}_N\})\equiv \{ Q~| ~Q\subset \mathcal{P}(\{\mathcal{A}_{N}\}), |Q|=m \}$.
-We also define the union and intersection of all the subsystems present in $Q$ as ${V}_{\cup}({Q})\equiv \bigcup_{A\in Q} A$ and ${V}_{\cap}({Q})\equiv \bigcap_{A\in Q} A$ respectively.
-Then, the $N-$partite information that we are interested in is defined as
-%\begin{equation}
-%I^{N}_{\{\mathcal{A}_N\}} = \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.
-%\label{eq:I_N_definition}
-%\end{equation}
 \begin{figure}
@@
 Though the values of the impurity entanglement entropy for various values of \(K\) are quite similar at low hopping strength,
-%there is a difference in the behaviour as a function of \(t\): 
 as the single channel \(EE_d\) varies smoothly at \(t \to 0^+\), whereas the \(EE_d\) for \(K > 1\) show a discontinuity at $t \to 0^+$.
@@
 The Bures distance~\cite{uhlmann1976transition,bures1969extension,hubner1992explicit,hubner1993computation,dittmann1994some,marian2003bures} between two density matrices \(\rho_1,\rho_2\) is defined as
-\begin{equation}
+\begin{eqnarray}
 d_{Bures}(\rho_1,\rho_2) = \sqrt{2} \bigg[1- \textrm{Tr}\bigg\{ \bigg(\rho_1^{1/2}  \rho_2 \rho_{1}^{1/2}\bigg)^{1/2} \bigg\}\bigg]~,
-\end{equation}
+\end{eqnarray}
 and is a measure of the distance, in the Hilbert space, between the states forming the density matrices.
@@
 
-\section{Dualities of the MCK model}
+\section{Duality properties of the MCK model}
 \label{sec:duality}
@@
 \begin{eqnarray}
-H_K (\vec{{\mathcal{J}}}) &=& \sum_{i=1}^{K} {\mathcal{J}}_i\vec{S}_d.\vec{S}_i~.
+H_K (\vec{{\mathcal{J}}}) = \sum_{i=1}^{K} {\mathcal{J}}_i\vec{S}_d.\vec{S}_i~.
 \label{eq:anisotropy}
@@
 Performing a linear stability analysis about \(j_\pm=0\) then reveals the following two possibilities:
-
-\par\textit{(a)} If \(j_-<0\) and \(j_+>0\), the deviation \(j_-\) is relevant and \(\mathcal{J}_-\) flows to zero.
+\begin{itemize}
+	\item[(a)] If \(j_-<0\) and \(j_+>0\), the deviation \(j_-\) is relevant and \(\mathcal{J}_-\) flows to zero.
 The flow of \(j_+\) are constrained such that the remaining couplings \(\mathcal{J}_+\) flow to the stable intermediate fixed point of the \(K-1\) channel MCK model: \(J_{+,*} = \frac{2}{(K-1)\rho}\).
-\par\textit{(b)} If \(j_- > 0\) and \(j_+<0\), the couplings \(\mathcal{J}_+\) are irrelevant, and this leads to a single channel Kondo model described by the coupling \(\mathcal{J}_-\) which flows to strong coupling.
+	\item[(b)] If \(j_- > 0\) and \(j_+<0\), the couplings \(\mathcal{J}_+\) are irrelevant, and this leads to a single channel Kondo model described by the coupling \(\mathcal{J}_-\) which flows to strong coupling.
+\end{itemize}
 
@@
 We end by discussing some open directions. 
-%Our approach serves as a template for the study of other quantum impurity systems. 
 Our work presents a template for the study of how a degenerate ground state manifold arising from symmetry and duality properties in a multichannel quantum impurity model can lead to novel multicritical phases at intermediate coupling.
@@
 Since the degeneracy of the star graph is observed to be robust under anisotropy,
-%Similar studies can be conducted for the case of superconducting leads, i.e., conduction baths with a superconducting gap. Thus, 
 it appears relevant to study the case of the MCK with superconducting leads, i.e., conduction baths with a superconducting gap.
@@
 of India and IISER Kolkata for funding through a research fellowship.
-Abhirup Mukherjee thanks IISER Kolkata for funding through a research fellowship.
+Abhirup Mukherjee thanks IISER Kolkata for funding through a junior and a senior research fellowship.
 S.
@@
 
+\section*{References}
+
 \bibliography{mscript_mck_full}

### 2023-01-09 manuscript/MCK-manuscript.tex
added orth cat.

--- 2023-01-07 manuscript/mscript_mck_full.tex
@@
 \usepackage{iopams}  
-\usepackage{braket,graphicx,amsmath}
+\usepackage{braket,graphicx,amsmath,color}
 \usepackage[hidelinks]{hyperref}
@@
 When the phase shift \(\delta^{(l)}\) acquires a fractional value (in units of \(\pi\)), the impurity magnetisation also becomes fractional (in units of \(\frac{1}{2}\)).
-This shows that the unrenormalised phase shift value \(0 < \delta^{(l)} < \pi\) is at the heart of the quantum frustration present in the star graph (and therefore the MCK problem) that neither allows the impurity to be screened, nor allows it to decouple from the conduction channels.
-The decoupling only happens in the limit of extreme screening \((K \to \infty)\), and the impurity spin then becomes a local moment.
+This shows that the "unrenormalised" phase shift value \(0 < \delta^{(l)} < \pi\)~\cite{anderson_1990} is at the heart of the quantum frustration present in the MCK problem, and leads, as we will see later, to a dramatic change in the ground-state wavefunction of the remaining degrees of freedom as the impurity is introduced, producing the well-known orthogonality catastrophe~\cite{anderson1967infrared,varma2002singular}.
 
@@
 Indeed, along with Ref.\cite{schofield_1997}, this demonstration shows the universality between the two-channel Kondo and the \(\sigma-\tau\) models.
+
+{\color{blue}We show in the Supplementary Materials~\cite{SM} that this orthogonality catastrophe can also be understood as a drastic change in the wavefunction and its quantum numbers.
+Upon taking account of the hopping between the star graph and the \(k-\)states of the conduction bath, the full ground-state \(\ket{\psi_-^{(l)}}\) and low-lying excited states \(\ket{\psi_+^{(l)}}\), in the \(l^\text{th}\) channel, take the form:
+\begin{equation}\begin{aligned}
+\ket{\psi_\pm^{(l)}} = \frac{1}{\sqrt 2}\left(\ket{\chi_{\frac{-1}{2}}}\otimes\ket{e_\uparrow^{(l)}} \pm \ket{\chi_{\frac{1}{2}}}\otimes\ket{e_\downarrow^{(l)}}\right)~,
+\end{aligned}\end{equation}
+where \(\ket{\chi_{\frac{\sigma}{2}}} = \frac{1}{\sqrt 6}\left( \ket{\sigma,\sigma,\bar\sigma} + \ket{\sigma,\bar\sigma,\sigma} -2\ket{\bar\sigma,\sigma,\sigma} \right),~ \sigma=\pm 1\) are the ground-states of the two-channel star graph, and \(\ket{e_\sigma^{(l)}} \equiv e^\dagger_{\sigma,(l)}\ket{\phi} = \sum_{k\in\text{FS}}c^\dagger_{k\sigma,(l)}\ket{\phi}\) are gapless excitations close to the Fermi surface (FS) \(\ket{\phi}\).
+We can now calculate the residue for scattering processes of the form \(e^\dagger_{\sigma,(l)} e_{\bar\sigma,(l)}\), in the new ground-state and excited state, and they are found to vanish:
+\begin{equation}
+	Z = |\braket{\psi_+^{(l)}| e^\dagger_{\uparrow,(l)} e_{\downarrow,(l)} | \psi_-^{(l)}}|^2 = \left|\bra{\psi_+^{(l)}}\left(\ket{\chi_{\frac{1}{2}}}\ket{e_\uparrow^{(l)}}\right)\right|^2 = 0
+\end{equation}
+This shows that the single-particle excitations are no longer long-lived, signaling the orthogonality catastrophe.}
 
@@
 
-\bibliography{mscript_mck_full}
+\bibliography{MCK-manuscript}
 

### 2023-01-09 manuscript/Supplementary/MCK-supplementary.tex
added orth cat.

--- 2023-01-07 manuscript/Supplementary/supplementary_mck.tex
@@
-\documentclass[10pt]{iopart}
+\documentclass[12pt]{iopart}
 \usepackage{iopams}  
@@
 
-\subsection{Orthogonality catastrophe in the gapless excitations}
+\subsection{Orthogonality catastrophe in the gapless excitations of the 2CK}
+By combining the ground-states of the star graph and the effect of hopping into the remaining lattice, it is possible to demonstrate an orthogonality catastrophe~\cite{anderson1967infrared,varma2002singular} in the new modified ground-state.
+The full Hilbert space consists of the star graph (formed by the impurity site and the zeroth sites of all channels) and the {\it reduced} conduction bath (formed by sites 1 and beyond in all channels).
+All terms in the Hamiltonian conserve the total spin \(S_\text{tot}^z = S_d^z + S_0^z + s^z\) composed of the impurity spin \(S_d^z\), the zeroth site spin \(S_0^z = \sum_l S_{0,(l)}^z\) and the spin of the reduced bath \(s^z\).
+We will work in the \(S_\text{tot}^z = 0\) sector.
+To construct the non-magnetic ground-states, we will assume the presence of gapless excitations vanishingly close to the Fermi surface in the reduced conduction bath.
+If \(\ket{\phi}\) represents the filled Fermi volume configuration of all the channels, these excitations can be written as \(\ket{e_\sigma^{(l)}} \equiv e^\dagger_{\sigma,(l)} \ket{\phi} = \sum_{k \in \text{FS}}c^\dagger_{k\sigma,(l)} \ket{\phi}\), where \(l \in \left\{1,2\right\} \) is the channel index.
+Apart from these states, we have the star graph ground-states at \(S_\text{sg}^z \equiv S_d^z + S_0^z = \pm \frac{1}{2}\): \(\ket{S_\text{sg}^z = \frac{\sigma}{2}} = \frac{1}{\sqrt 6}\left( \ket{\sigma,\sigma,\bar\sigma} + \ket{\sigma,\bar\sigma,\sigma} -2\ket{\bar\sigma,\sigma,\sigma} \right),~ \sigma=\pm 1 \).
+Within each ket, the three symbols indicate the configuration of the impurity spin, the zeroth site of the first channel and that of the second channel respectively.
+In the absence of any hopping between the star graph and the reduced conduction bath, the full non-magnetic ground states are then of the form:
+\begin{equation}\begin{aligned}
+	\ket{l,\sigma} = \ket{S^z_\text{sg}=\frac{-\sigma}{2}}\otimes\ket{e_{\sigma}^{(l)}},~l\in\left\{ 1,2 \right\},~\sigma=\pm 1~.
+\end{aligned}\end{equation}
+We now introduce the hopping \(H_\text{int}\) between the star graph and the reduced conduction bath,
+\begin{equation}\begin{aligned}
+	H_\text{int} = -t\frac{1}{\sqrt N}\sum_{k,\sigma,l}\left( c^\dagger_{k\sigma,(l)}c_{0\sigma,(l)} + \text{h.c.} \right)~,
+\end{aligned}\end{equation}
+and treat it under degenerate perturbation theory.
+Since all terms in the Hamiltonian conserve the number of particles in each channel, the states with different \(l\) do not mix.
+For each value of \(l\), the \(2\times 2\) matrix of \(H_\text{int}\) takes the form
+\begin{equation}\begin{aligned}
+	H_\text{int} = \frac{4t^2}{J^*}\begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix} ~.
+\end{aligned}\end{equation}
+The non-zero off-diagonal terms arise because of second-order scattering processes.
+Diagonalising this gives the modified new ground-states:
+\begin{equation}\begin{aligned}
+	\ket{\psi_\pm^{(l)}} = \frac{1}{\sqrt 2}\left(\ket{l,\uparrow} \pm \ket{l,\downarrow}\right), E_\pm = -4t^2/J^*~.
+\end{aligned}\end{equation}
+We can now calculate the residue for scattering processes of the kind \(e^\dagger_{\sigma,(l)} e_{\bar\sigma,(l)}\), in the new ground-state and excited state, and they are found to vanish:
+\begin{equation}\begin{aligned}
+	Z = |\braket{\psi_+^{(l)}| e^\dagger_{\uparrow,(l)} e_{\downarrow,(l)} | \psi_-^{(l)}}|^2 = \left|\bra{\psi_+^{(l)}}\left(\ket{S_\text{sg}^z=\frac{1}{2}}\ket{e_\uparrow^{(l)}}\right)\right|^2 = 0
+\end{aligned}\end{equation}
+This shows that the single-particle excitations are no longer long-lived, signaling the orthogonality catastrophe.
 
@@
 \begin{eqnarray}
-|\alpha_{-1}\rangle = c|1000 \rangle-b (|0100 \rangle + |0010 \rangle+ | 0001 \rangle), ~ ~ |\alpha_{+1}\rangle = b(|1110 \rangle+ | 1101 \rangle + | 1011 \rangle)-c | 0111 \rangle,\nonumber\\
-|\alpha_0\rangle = -a(|1100 \rangle + |1010\rangle +|1001 \rangle) + a(|0110 \rangle+| 0101 \rangle +| 0011\rangle)~,
+\fl |\alpha_{-1}\rangle = c|1000 \rangle-b (|0100 \rangle + |0010 \rangle+ | 0001 \rangle), ~ ~ |\alpha_{+1}\rangle = b(|1110 \rangle+ | 1101 \rangle + | 1011 \rangle)-c | 0111 \rangle,\nonumber\\
+\fl |\alpha_0\rangle = -a(|1100 \rangle + |1010\rangle +|1001 \rangle) + a(|0110 \rangle+| 0101 \rangle +| 0011\rangle)~,
 \end{eqnarray}
@@
 
-\bibliography{../mscript_mck_full}
+\bibliography{../MCK-manuscript}
 \end{document}

### 2023-01-09 manuscript/MCK-manuscript.tex
added phase shift and exponents

@@
 Following Friedel's sum rule, this leads to a total scattering phase shift of \(\pi/K\) for each channel:
-\begin{eqnarray}
+\begin{eqnarray}\label{phase-stargraph}
 	\delta^{(l)} = \pi n_\mathrm{exc}^{(l)} = \frac{\pi}{K}, ~ ~ l \in \left[1, K\right] 
@@
 Right now, some evidence of this role of the phase shift can be provided through its relation to the vanishing field impurity magnetisation \(m\) obtained in eq.~\ref{imp-magnetisation}:
-\begin{eqnarray}
+\begin{eqnarray}\label{magnetisation-phase}
 	m(h=0^\pm) = \pm \frac{1}{2} \frac{\delta^{(l)} - \pi}{\delta^{(l)} + \pi}~.
@@
 \end{equation}
-This shows that the single-particle excitations are no longer long-lived, signaling the orthogonality catastrophe.}
+This shows that the single-particle excitations are no longer long-lived, signaling the orthogonality catastrophe.
+
+The orthogonality catastrophe in the infrared wavefunction points towards an ``unrenormalised" scattering phase shift in the conduction electrons at the fixed point.
+We have already seen from the zero mode approximation of the fixed point Hamiltonian that each channel suffers a phase shift of \(\delta^{(l)} = \pi/K\) (eq.~\ref{phase-stargraph}), which is non-zero but less than the unitarity limit.
+In this section, we will see how the phase shift guides the renormalisation group flow of the Kondo coupling \(J\).
+Following refs.~\cite{si_kotliar_1993,giamarchi_varma_1993,giamarchi_book}, the URG equation for \(J\) can be cast in the form
+\begin{equation}\begin{aligned}
+	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{\rho {\mathcal{J}}_{(j)}}{2\delta^{(l)}/\pi} \right)~,
+\end{aligned}\end{equation}
+The Kondo coupling continues to flow until the phase shift acquires the appropriate value: \(2\delta^{(l)}/\pi = \rho \mathcal{J}^* = 2/K\).
+Following eq.~\ref{magnetisation-phase}, this also leads to the fractional value of \(1/4\) for the impurity magnetisation \(m(0^+)\) in the spin-half two-channel Kondo model.
+The incommensurate values of both \(\delta^{(l)}\) and \(m(0^+)\) point to the frustrated nature of the problem and the absence of complete screening.
+These phase shifts also affect thermodynamic properties in the form of critical exponents in power-law behaviour.
+The impurity contributions to the specific heat linear coefficient \(\gamma = C_v/T\), the magnetic susceptibility \(\chi\) and the thermal entropy \(S\) take the forms~\cite{andrei_destri_1984,Tsvelick_Weigmann_mchannel_1984,affleck1993exact}
+\begin{eqnarray}
+	\gamma,\chi \sim \left( T/T_K \right)^\frac{1 - 2\delta^{(l)}/\pi}{1 + 2\delta^{(l)}/\pi}, ~ S \sim \ln \left[2\cos \frac{\delta^{(l)}}{1 + 2\delta^{(l)}/\pi}\right] 
+\end{eqnarray}
+}
 

### 2023-01-13 MCK-manuscript/MCK-manuscript.tex
sir's changes

--- 2023-01-07 manuscript/mscript_mck_full.tex
@@
 \begin{eqnarray}
-	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{1}{2}\rho {\mathcal{J}}_{(j)} K \right)~,
+	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{1}{2}\rho {\mathcal{J}}_{(j)} K \right)~, \label{mckRG}
 \end{eqnarray}
@@
 where \(\sigma=\pm 1\) and \(\ket{\sigma}_d\) represents the up and down configurations of the impurity spin and \(\ket{S^z}\) represents the configuration of the bath spins.
-These states lead to large unquenched magnetisation at zero temperatures.
-These states lead to singular behaviour of the impurity magnetisation in vanishing field, \(m(h=0^\pm)\).
+These states lead to large unquenched magnetisation (\(m(h=0^\pm)\)) at zero temperatures
+%. These states lead to singular behaviour of the impurity magnetisation 
+that displays discontinuous behaviour in the limit of a vanishing field $h\to 0\pm$.
+This can be seen as follows.
 In the presence of a field, the ground-state becomes unique: \(\ket{\psi}_\mathrm{gs}(h) = \theta(h)\ket{J^z=\frac{K-1}{2}} + \theta(-h)\ket{J^z=-\frac{K-1}{2}}\), and the impurity magnetisation can be calculated from the state:
@@
 
-The magnetization is therefore discontinuous as \(h\to 0\) for \(K>1\).
-The non-analyticity occurs because the magnetic field is able to flip the \(J^z=\pm (K-1)/2\) state into the state of the opposite magnetisation.
-This available space for scattering is simply the frustration that we discussed earlier.
+The magnetization is therefore discontinuous as \(h\to 0\pm\) for \(K>1\).
+The non-analyticity occurs because the magnetic field is able to flip the states with \(J^z= (K-1)/2\) into the state of the opposite magnetisation and vice versa.
+The available space for scattering is simply the frustration that we discussed earlier.
 Indeed, we have checked (see Fig.~\ref{mag_crit}) by diagonalising numerically the star graph Hamiltonian that the non-analyticity exists for all \(\delta \neq 0\), where \(\delta = \frac{K}{2} - S_{d}\) is the deviation from exact screening.
@@
 Following Friedel's sum rule, this leads to a total scattering phase shift of \(\pi/K\) for each channel:
-\begin{eqnarray}
+\begin{eqnarray}\label{phase-stargraph}
 	\delta^{(l)} = \pi n_\mathrm{exc}^{(l)} = \frac{\pi}{K}, ~ ~ l \in \left[1, K\right] 
 \end{eqnarray}
-For \(K > 1\), each channel therefore experiences an unrenormalised phase shift of value between \(0\) and \(\pi\) that, as we will show in a later section, is responsible for the non-Fermi liquid behaviour.
-For example, we will show that this phase shift are linked to the critical non-Fermi liquid exponents of thermodynamic quantities at the fixed point.
-Right now, some evidence of this role of the phase shift can be provided through its relation to the vanishing field impurity magnetisation \(m\) obtained in eq.~\ref{imp-magnetisation}:
-\begin{eqnarray}
+For \(K > 1\), each channel therefore experiences an unrenormalised phase shift of value between \(0\) and \(\pi\) that, as we will show in a later section, is responsible for the non-Fermi liquid behaviour observed at the ICFP.
+For example, we will show that these phase shifts are linked to the critical non-Fermi liquid exponents of various thermodynamic quantities at the fixed point.
+That this phase shift is tied to the frustration that leads to incomplete Kondo screening at the ICFP can be evidenced
+%of this role of the phase shift can be provided 
+through its relation to the impurity magnetisation \(m (h=0\pm)\) obtained in eq.~\ref{imp-magnetisation}:
+\begin{eqnarray}\label{magnetisation-phase}
 	m(h=0^\pm) = \pm \frac{1}{2} \frac{\delta^{(l)} - \pi}{\delta^{(l)} + \pi}~.
 \end{eqnarray}
-When the phase shift \(\delta^{(l)}\) acquires a fractional value (in units of \(\pi\)), the impurity magnetisation also becomes fractional (in units of \(\frac{1}{2}\)).
-This shows that the unrenormalised phase shift value \(0 < \delta^{(l)} < \pi\) is at the heart of the quantum frustration present in the star graph (and therefore the MCK problem) that neither allows the impurity to be screened, nor allows it to decouple from the conduction channels.
-The decoupling only happens in the limit of extreme screening \((K \to \infty)\), and the impurity spin then becomes a local moment.
+When the phase shift \(\delta^{(l)}\) acquires a fractional value (in units of \(\pi\)) at the ICFP, the impurity magnetisation also becomes fractional (in units of \(\frac{1}{2}\)).
+We will see shortly that this unrenormalised phase shift value of \(0 < \delta^{(l)} < \pi\)~\cite{anderson_1990} is also at the heart of
+%the quantum frustration present in the MCK problem, and leads, as we will see shortly, to 
+an orthogonality catastrophe, i.e., a dramatic change in the ground-state wavefunction of the conduction bath degrees of freedom as the impurity is introduced among them~\cite{anderson1967infrared,varma2002singular}.
 
@@
 Indeed, along with Ref.\cite{schofield_1997}, this demonstration shows the universality between the two-channel Kondo and the \(\sigma-\tau\) models.
+
+Further, we argue below that the orthogonality catastrophe for the 2-channel problem can also be understood as a drastic change in the ground state and lowest-lying excited state wavefunctions and related quantum numbers.
+The detailed calculation has been shown in the Supplementary Materials~\cite{SM}.
+Upon taking account of the hopping between the star graph and the \(k-\)states of the conduction bath, the full ground-state \(\ket{\psi_-^{(l)}}\) and low-lying excited states \(\ket{\psi_+^{(l)}}\)  in the \(l^\text{th}\) channel  take the form:
+\begin{equation}\begin{aligned}
+\ket{\psi_\pm^{(l)}} = \frac{1}{\sqrt 2}\left(\ket{\chi_{-\frac{1}{2}}}\otimes\ket{e_\uparrow^{(l)}} \pm \ket{\chi_{\frac{1}{2}}}\otimes\ket{e_\downarrow^{(l)}}\right)~,
+\end{aligned}\end{equation}
+where \(\ket{\chi_{\frac{\sigma}{2}}} = \frac{1}{\sqrt 6}\left( \ket{\sigma,\sigma,\bar\sigma} + \ket{\sigma,\bar\sigma,\sigma} -2\ket{\bar\sigma,\sigma,\sigma} \right),~ \sigma=\pm 1\) are the ground-states of the two-channel star graph, and \(\ket{e_\sigma^{(l)}} \equiv e^\dagger_{\sigma,(l)}\ket{\phi} = \sum_{k\in\text{FS}}c^\dagger_{k\sigma,(l)}\ket{\phi}\) are gapless excitations close to the Fermi surface (FS) \(\ket{\phi}\).
+The residue for scattering processes of the form \(e^\dagger_{\sigma,(l)} e_{\bar\sigma,(l)}\) between the new ground and excited states is then found to vanish:
+\begin{equation}
+	Z = |\braket{\psi_+^{(l)}| e^\dagger_{\uparrow,(l)} e_{\downarrow,(l)} | \psi_-^{(l)}}|^2 = \left|\bra{\psi_+^{(l)}}\left(\ket{\chi_{\frac{1}{2}}}\ket{e_\uparrow^{(l)}}\right)\right|^2 = 0~.
+\end{equation}
+This shows that single-particle excitations (a signature of the local Fermi liquid associated with the single channel Kondo fixed point) are no longer long-lived, signalling the orthogonality catastrophe.
+
+The orthogonality catastrophe in the infrared wavefunction arises from an unrenormalised scattering phase shift in the conduction electrons at the fixed point.
+We have already seen from the zero mode approximation of the fixed point Hamiltonian that each channel suffers a phase shift of \(\delta^{(l)} = \pi/K\) (eq.~\ref{phase-stargraph}), which is non-zero but less than the limit of unitarity.
+We will now see that this phase shift guides the renormalisation group flow of the Kondo coupling \(J\).
+Following refs.~\cite{si_kotliar_1993,giamarchi_varma_1993,giamarchi_book}, the URG equation for \(J\) (eq.\ref{mckRG}) can be recast in the form
+\begin{equation}\begin{aligned}
+	\Delta {\mathcal{J}}_{(j)} = -\frac{{\mathcal{J}}_{(j)}^2 \mathcal{N}_{(j)}}{\omega_{(j)} - \frac{D_{(j)}}{2} + \frac{{\mathcal{J}}_{(j)}}{4}}\left( 1 - \frac{\rho {\mathcal{J}}_{(j)}}{2\delta^{(l)}/\pi} \right)~.
+\end{aligned}\label{scattphaseRG}\end{equation}
+The Kondo coupling $J$ continues to flow under RG until it obtains a value dictated by the phase shift of the star graph: \(\rho \mathcal{J}^* = 2\delta^{(l)}/\pi = 2/K\).
+Following eq.~\ref{magnetisation-phase}, this also leads to the fractional value of \(1/4\) for the impurity magnetisation \(m(0^+)\) in the spin-half two-channel Kondo model.
+Indeed, the values of both \(\delta^{(l)}\) and \(m(0^+)\) point to the frustrated nature of the MCK problem and the absence of complete screening of the impurity moment at the ICFP.
+Importantly, the phase shifts \(\delta^{(l)}\) also affect the critical exponents of well-known algebraic behaviour of several thermodynamic properties at the ICFP.
+The impurity contributions to the specific heat linear coefficient \(\gamma = C_v/T\), the magnetic susceptibility \(\chi\) and the thermal entropy \(S\) take the forms~\cite{andrei_destri_1984,Tsvelick_Weigmann_mchannel_1984,affleck1993exact}
+\begin{eqnarray}
+	\gamma &\sim & \left( T/T_K \right)^\frac{1 - 2\delta^{(l)}/\pi}{1 + 2\delta^{(l)}/\pi} = \left( T/T_K \right)^\frac{K-2}{K+2}\sim \chi~,\nonumber\\ 
+	S &\sim & \ln \left[2|\cos \left(\frac{\delta^{(l)}}{1 + 2\delta^{(l)}/\pi}\right)|\right]
+	 = \ln \left[2|\cos \left(\frac{\pi}{K + 2}\right)|\right]~. \label{powerlawquants}
+\end{eqnarray}
 

### 2023-01-13 MCK-manuscript/Supplementary/MCK-supplementary.tex
sir's changes

--- 2023-01-09 manuscript/Supplementary/MCK-supplementary.tex
@@
 From these polarised states, one can now calculate the ``excess charge" supplied by the impurity site to the conduction bath in the form of gapless excitations.
-For this, we first note that the form Eq.~\ref{singlet-chain} of the polarised state shows that all the individual terms in the more explicit form of Eq.~\ref{polarised-state} involve the impurity hybridising with the bath.
-In Eq.~\ref{polarised-state}, each term of the form \(\ket{\sigma}_d\otimes\ket{\bar\sigma}_l\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}\) participates in exactly one singlet \(\ket{\text{SS}_{d,l}}\) and therefore involves hybridisation between the impurity and only the \(l^\text{th}\) channel.
+For this, we first note that the form Eq.~\ref{singlet-chain} of the polarised state shows that all the individual terms in the more explicit form of eq.~\ref{polarised-state} involve the impurity hybridising with the bath.
+In eq.~\ref{polarised-state}, each term of the form \(\ket{\sigma}_d\otimes\ket{\bar\sigma}_l\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}\) participates in exactly one singlet \(\ket{\text{SS}_{d,l}}\) and therefore involves hybridisation between the impurity and only the \(l^\text{th}\) channel.
 Each such term therefore contributes an excess charge \(n_\text{exc}^{(l)}\) of unity to the \(l^\text{th}\) conduction channel and none to the other channels: \(n_\text{exc}^{(l)} = 1 = 1 - n_\text{exc}^{(l^\prime)}\).
@@
 \end{eqnarray}
+This result then connects to the Friedel scattering phase shift (eq.(20) of the main manuscript) and the magnetisation of the impurity (eq.(21) of the main manuscript).
+In this way, the excess charge $n_\text{exc}^{(l)}$ of the star graph is also observed to guide the RG flow of the MCK problem to the intermediate coupling fixed point (eq.(55) of the main manuscript), and lead to the power-law behaviour of various thermodynamic quantities at the fixed point (eq.(56) of the main manuscript).
 
@@
 \subsection{Orthogonality catastrophe in the gapless excitations of the 2CK}
-By combining the ground-states of the star graph and the effect of hopping into the remaining lattice, it is possible to demonstrate an orthogonality catastrophe~\cite{anderson1967infrared,varma2002singular} in the new modified ground-state.
+By combining the ground-states of the star graph and the effect of hopping into the remaining lattice, it is possible to demonstrate an orthogonality catastrophe~\cite{anderson1967infrared,varma2002singular} in the modified ground-state (see also subsection 5.2.3 of the main manuscript for an entanglement based perspective).
 The full Hilbert space consists of the star graph (formed by the impurity site and the zeroth sites of all channels) and the {\it reduced} conduction bath (formed by sites 1 and beyond in all channels).
-All terms in the Hamiltonian conserve the total spin \(S_\text{tot}^z = S_d^z + S_0^z + s^z\) composed of the impurity spin \(S_d^z\), the zeroth site spin \(S_0^z = \sum_l S_{0,(l)}^z\) and the spin of the reduced bath \(s^z\).
+All terms in the Hamiltonian conserve the total spin \(S_\text{tot}^z = S_d^z + S_0^z + s^z\) composed of the impurity spin \(S_d^z\), the total zeroth site spin \(S_0^z = \sum_l S_{0,(l)}^z\) and the spin of the reduced bath \(s^z\).
 We will work in the \(S_\text{tot}^z = 0\) sector.
@@
 \end{aligned}\end{equation}
-We now introduce the hopping \(H_\text{int}\) between the star graph and the reduced conduction bath,
+Using degenerate perturbation theory, we now treat the effects of hopping \(H_\text{int}\) between the star graph and the reduced conduction bath
 \begin{equation}\begin{aligned}
-	H_\text{int} = -t\frac{1}{\sqrt N}\sum_{k,\sigma,l}\left( c^\dagger_{k\sigma,(l)}c_{0\sigma,(l)} + \text{h.c.} \right)~,
+	H_\text{int} = -t\frac{1}{\sqrt N}\sum_{k,\sigma,l}\left( c^\dagger_{k\sigma,(l)}c_{0\sigma,(l)} + \text{h.c.} \right)~.
 \end{aligned}\end{equation}
-and treat it under degenerate perturbation theory.
 Since all terms in the Hamiltonian conserve the number of particles in each channel, the states with different \(l\) do not mix.
@@
 \begin{equation}\begin{aligned}
-	H_\text{int} = \frac{4t^2}{J^*}\begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix} ~.
+	H_\text{int} = \frac{4t^2}{J^*}\begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix} ~,
 \end{aligned}\end{equation}
-The non-zero off-diagonal terms arise because of second-order scattering processes.
-Diagonalising this gives the modified new ground-states:
+where the non-zero off-diagonal terms arise because of second-order scattering processes. Diagonalising this gives the modified new ground-states:
 \begin{equation}\begin{aligned}
-	\ket{\psi_\pm^{(l)}} = \frac{1}{\sqrt 2}\left(\ket{l,\uparrow} \pm \ket{l,\downarrow}\right), E_\pm = -4t^2/J^*~.
+	\ket{\psi_\pm^{(l)}} = \frac{1}{\sqrt 2}\left(\ket{l,\uparrow} \pm \ket{l,\downarrow}\right)~,~ E_\pm = -4t^2/J^*~.
 \end{aligned}\end{equation}
-We can now calculate the residue for scattering processes of the kind \(e^\dagger_{\sigma,(l)} e_{\bar\sigma,(l)}\), in the new ground-state and excited state, and they are found to vanish:
+We can now compute the residue for scattering processes of the kind \(e^\dagger_{\sigma,(l)} e_{\bar\sigma,(l)}\) between the new ground-state and excited state, and display that they vanish identically:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-This shows that the single-particle excitations are no longer long-lived, signaling the orthogonality catastrophe.
+This shows that the single-particle excitations are no longer long-lived, signalling the orthogonality catastrophe inherent in the intermediate coupling fixed point theory of the MCK.
 

### 2023-01-13 MCK-manuscript/Supplementary/MCK-supplementary.tex
fixed punctuation and equation in main ans supp

@@
-\documentclass[12pt]{iopart}
+\documentclass{iopart}
 \usepackage{iopams}  
-\usepackage{braket,graphicx,amsmath}
-\usepackage[hidelinks]{hyperref}
+\usepackage{braket,graphicx,cite,amsmath}
+\usepackage[colorlinks,linkcolor={blue},citecolor={blue}]{hyperref}
 \usepackage[margin=2cm]{geometry}
@@
 \begin{eqnarray}
-	H = J^* \vec{S_d}\cdot\vec{s}_\text{tot}
+	H = J^* \vec{S_d}\cdot\vec{s}_\text{tot}~,
 \end{eqnarray}
@@
 	\label{stargraph_field_hamiltonian}
-	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h S_d^z
+	H(h) = J^* \vec{S_d}\cdot\vec{s}_\text{tot} + h S_d^z~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\hspace*{-20pt}\left[s_\text{tot}^2, H(h)\right] &= \left[\sum_{i=x,y,z}{s^i_\text{tot}}^2, J^* \sum_{i=x,y,z} S_d^i s^i_\text{tot}\right] = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, \left[s_\text{tot}^i,s_\text{tot}^j\right]\right\} = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, i \epsilon^{ijk}s^k_\text{tot}\right\}\nonumber\\
-							 &= 0
+	\left[s_\text{tot}^2, H(h)\right] &= \left[\sum_{i=x,y,z}{s^i_\text{tot}}^2, J^* \sum_{i=x,y,z} S_d^i s^i_\text{tot}\right] = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, \left[s_\text{tot}^i,s_\text{tot}^j\right]\right\}\nonumber\\
+							 & = \sum_{i,j}J^* S_d^i \left\{s_\text{tot}^i, i \epsilon^{ijk}s^k_\text{tot}\right\} = 0~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} 
+	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} ~.
 \end{eqnarray}
@@
 	\label{eigenvalue}
-	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}
+	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}~,
 \end{eqnarray}
@@
 The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\).
-For \(h = 0\), the ground state subspace is \(K-\)fold degenerate and is formed by the negative solutions of eq.~\ref{eigenvalue}.
+For \(h = 0\), the ground state subspace is \(K-\)fold degenerate and is formed by the negative solutions of eq.~\eqref{eigenvalue}.
 This common \(K-\)fold degenerate eigenvalue is \(-J(M+1)/2\).
@@
 \begin{eqnarray}
-	\fl \ket{M-\frac{1}{2},m+\frac{1}{2},M} =\mathcal{C}_\pm \ket{\uparrow, M, m} \pm \sqrt{1 - \mathcal{C}_\pm^2} \ket{\downarrow, M, m+1}, ~ ~ \mathcal{C}_\pm = \frac{J\sqrt{x_m^M}/2}{\sqrt{J^2 x_m^M/4 + \left(\alpha \mp \sqrt{\alpha^2 + J^2 x_m^M/4}\right)^2 }}
+	\ket{M-\frac{1}{2},m+\frac{1}{2},M} =\mathcal{C}_\pm \ket{\uparrow, M, m} \pm \sqrt{1 - \mathcal{C}_\pm^2} \ket{\downarrow, M, m+1}, \\
+	\mathcal{C}_\pm = \frac{J\sqrt{x_m^M}/2}{\sqrt{J^2 x_m^M/4 + \left(\alpha \mp \sqrt{\alpha^2 + J^2 x_m^M/4}\right)^2 }}~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-	Z(h) = \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+	Z(h) = \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]~,
 \end{eqnarray}
@@
 \begin{eqnarray}
-	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
+	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\fl \ket{J=\frac{K-1}{2},J^z= \frac{\sigma}{2}\left(K-1\right),s_\text{tot}=\frac{K}{2}} = \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma(\frac{K}{2}-1)} - \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma\frac{K}{2}},
+	\ket{J=\frac{K-1}{2},J^z= \frac{\sigma}{2}\left(K-1\right),s_\text{tot}=\frac{K}{2}} \nonumber\\
+	= \frac{1}{\sqrt{1 + K}} \ket{\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma(\frac{K}{2}-1)} - \frac{\sqrt K}{\sqrt{1 + K}}\ket{\bar\sigma}_d\otimes\ket{s_\text{tot}^z=\sigma\frac{K}{2}},
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\fl \ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} \left[\ket{\sigma}_d\otimes\left(\ket{\bar\sigma,\sigma,\ldots,\sigma} + \ket{\sigma,\bar\sigma,\ldots,\sigma} + \ldots + \ket{\sigma,\sigma\ldots,\bar\sigma}\right) - K\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\right].\label{polarised-state}\qquad
+	\ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} &\left[\ket{\sigma}_d\otimes\left(\ket{\bar\sigma,\sigma,\ldots,\sigma} + \ket{\sigma,\bar\sigma,\ldots,\sigma} + \ldots + \ket{\sigma,\sigma\ldots,\bar\sigma}\right) \right.\nonumber\\
+										&\left.- K\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\right].\label{polarised-state}\qquad
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\fl \ket{J^z= \frac{\sigma}{2}\left(K-1\right)} = \frac{1}{\sqrt{K(1 + K)}} \sum_{l=1}^K\ket{\sigma}_d\otimes\left[\ket{\bar\sigma}_l - \ket{\sigma}_l\right] \otimes\ket{\sigma,\ldots,\sigma}_{l^\prime} = \frac{\sqrt 2}{\sqrt{K(1 + K)}} \sum_{l=1}^K \ket{\text{SS}_{d,l}}\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}.\label{singlet-chain}
+	\ket{J^z= \frac{\sigma}{2}\left(K-1\right)} &= \frac{1}{\sqrt{K(1 + K)}} \sum_{l=1}^K\ket{\sigma}_d\otimes\left[\ket{\bar\sigma}_l - \ket{\sigma}_l\right] \otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}\nonumber \\
+						    &= \frac{\sqrt 2}{\sqrt{K(1 + K)}} \sum_{l=1}^K \ket{\text{SS}_{d,l}}\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}.\label{singlet-chain}
 \end{eqnarray}
@@
 From these polarised states, one can now calculate the ``excess charge" supplied by the impurity site to the conduction bath in the form of gapless excitations.
-For this, we first note that the form Eq.~\ref{singlet-chain} of the polarised state shows that all the individual terms in the more explicit form of eq.~\ref{polarised-state} involve the impurity hybridising with the bath.
-In eq.~\ref{polarised-state}, each term of the form \(\ket{\sigma}_d\otimes\ket{\bar\sigma}_l\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}\) participates in exactly one singlet \(\ket{\text{SS}_{d,l}}\) and therefore involves hybridisation between the impurity and only the \(l^\text{th}\) channel.
+For this, we first note that the form eq.~\eqref{singlet-chain} of the polarised state shows that all the individual terms in the more explicit form of eq.~\eqref{polarised-state} involve the impurity hybridising with the bath.
+In eq.~\eqref{polarised-state}, each term of the form \(\ket{\sigma}_d\otimes\ket{\bar\sigma}_l\otimes\ket{\sigma,\ldots,\sigma}_{l^\prime}\) participates in exactly one singlet \(\ket{\text{SS}_{d,l}}\) and therefore involves hybridisation between the impurity and only the \(l^\text{th}\) channel.
 Each such term therefore contributes an excess charge \(n_\text{exc}^{(l)}\) of unity to the \(l^\text{th}\) conduction channel and none to the other channels: \(n_\text{exc}^{(l)} = 1 = 1 - n_\text{exc}^{(l^\prime)}\).
-The final term \(\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\) in Eq.~\ref{polarised-state} participates in all \(K\) singlets, and therefore involves hybridisation with all the channels.
+The final term \(\ket{\bar\sigma}_d\otimes \ket{\sigma,\sigma,\ldots,\sigma}\) in eq.~\eqref{polarised-state} participates in all \(K\) singlets, and therefore involves hybridisation with all the channels.
 This term therefore contributes the entire excess charge of unity across all the channels, which results in an excess charge contribution of \(n_\text{exc}^{(l)}=1/K\) to each channel.
-With these in mind, the total excess charge contributed to each channel from the state in Eq.~\ref{polarised-state} is
+With these in mind, the total excess charge contributed to each channel from the state in eq.~\eqref{polarised-state} is
 \begin{eqnarray}
-	n_\text{exc}^{(l)} = \frac{1}{K(1+K)}\left[1 + K^2 \times \frac{1}{K}\right] = \frac{1}{K}
+	n_\text{exc}^{(l)} = \frac{1}{K(1+K)}\left[1 + K^2 \times \frac{1}{K}\right] = \frac{1}{K}~.
 \end{eqnarray}
@@
 \end{eqnarray}
-We are interested in studying how the presence of quantum fluctuations in the Hamiltonian of eq.~\ref{eq:stargraph_hamiltonian} stabilises the ground state.
+We are interested in studying how the presence of quantum fluctuations in the Hamiltonian of eq.~\eqref{eq:stargraph_hamiltonian} stabilises the ground state.
 This can be understood by looking at the contributions, per channel, of the classical and the quantum parts to the total ground state energy \(E_g\).
@@
 
-The variation of \(E_Q\) is shown in Fig.\ref{fig:quantum_energy} for the case of $S_d=1/2$, as functions of the number of channels \(K\) as well as the ground state value \(J^z\) in which \(E_Q\) is being calculated.
+The variation of \(E_Q\) is shown in Fig.\eqref{fig:quantum_energy} for the case of $S_d=1/2$, as functions of the number of channels \(K\) as well as the ground state value \(J^z\) in which \(E_Q\) is being calculated.
 For a particular channel $K$, we find that the maximum \(|E_Q|\) is obtained for the state with smallest magnitude of $J^z$ (\(J^z = 0 \) for odd \(K\) and \(J^z = \pm 1/2\) for even \(K\)), whereas \(|E_Q|\) is minimum in the states with largest \(J^z\) ($J^z=\pm J$).
@@
 \begin{eqnarray}
-\fl q_K = \frac{1}{K}\sqrt{Q_\text{max}} = \frac{1}{K}\sqrt{\langle \psi_g | J^2 - |J^z|_{min}^2 |\psi_g\rangle} = \begin{cases}
+	q_K &= \frac{1}{K}\sqrt{Q_\text{max}} = \frac{1}{K}\sqrt{\langle \psi_g | J^2 - |J^z|_{min}^2 |\psi_g\rangle}\nonumber\\
+					     &= \begin{cases}
 	\frac{1}{K}\sqrt{(|K/2-S_d|)(|K/2-S_d|+1)-1/4}, & \text{ where }\Delta\text{ is half-integer}\\
@@
 \begin{eqnarray}
-	\fl m_s^2 = \left< \left(\frac{1}{K}M_S\right)^2\right> = \frac{1}{K^2}\langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \frac{1}{K^2}\langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle = \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}~.
+	m_s^2 &= \left< \left(\frac{1}{K}M_S\right)^2\right> = \frac{1}{K^2}\langle \psi_g | (\vec{S}_d - \vec{S})^2 |\psi_g\rangle = \frac{1}{K^2}\langle \psi_g | 2(\vec{S}_d^2 + \vec{S}^2)-\vec{J}^2 |\psi_g\rangle \nonumber\\
+	      &= \frac{2S_d(S_d+1)}{K^2}+\frac{1}{4}+\frac{1}{K}+\frac{1}{4K^2}~.
 \end{eqnarray}
@@
 This reduced value however is still greater than the value of \(1/12\) reached as \(K\to \infty\) away from exact-screening by keeping \(S_d\) finite.
-These conclusions can be easily understood from fig.\ref{fig:st_mag} where we have shown the variation of \(\left<m_s^2 \right>\) as a function of \(K\), keeping \(S_d=1/2\).
+These conclusions can be easily understood from fig.\eqref{fig:st_mag} where we have shown the variation of \(\left<m_s^2 \right>\) as a function of \(K\), keeping \(S_d=1/2\).
 
@@
 \end{eqnarray}
-Combining eqs.~\ref{sigmax} and \ref{sigmayz}, we find
+Combining eqs.~\eqref{sigmax} and \eqref{sigmayz}, we find
 \begin{eqnarray}
@@
 \begin{eqnarray}
-\fl \mathcal{F}= -k_B T\log Z, ~ ~ ~ S = -\frac{\partial \mathcal{F}}{\partial T} = -k_B \log Z -k_B T \frac{1}{Z} \frac{dZ}{dT} = -k_B \log \sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon}  -\frac{1}{\beta} \frac{k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   }{\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon}}~,
+\mathcal{F}= -k_B T\log Z, \nonumber\\
+S = -\frac{\partial \mathcal{F}}{\partial T} = -k_B \log Z -k_B T \frac{1}{Z} \frac{dZ}{dT} = -k_B \log \sum_{\epsilon} d(\epsilon) e^{-\beta \epsilon}  -\frac{1}{\beta} \frac{k_B\sum_\epsilon \epsilon d(\epsilon) e^{-\beta \epsilon} \beta^2   }{\sum_\epsilon  d(\epsilon)e^{-\beta \epsilon}}~,
 \end{eqnarray}
@@
 
-In fig.\ref{fig:thermal_entropy}, we plot the thermal entropy (in units of $k_B \log 2$) for a range of temperatures and for different values of \(K\).
+In fig.\eqref{fig:thermal_entropy}, we plot the thermal entropy (in units of $k_B \log 2$) for a range of temperatures and for different values of \(K\).
 At large temperatures, \(S\) saturates to integer multiples of \(k_B \log 2\), while at low-temperatures, that is not always the case.
@@
 S_i^+ = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{+}_{\alpha\beta} c_{0\beta}^{(i)}
-=\frac{\hbar}{2} c_{0\uparrow}^{(i)\dagger} c_{0\downarrow}^{(i)}, \quad S_i^z &= \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{z}_{\alpha\beta} c_{0\beta}^{(i)} \nonumber\\
-									       &=\frac{\hbar}{2} (c_{0\uparrow}^{(i)\dagger} c_{0\uparrow}^{(i)} - c_{0\downarrow}^{(i)\dagger} c_{0\downarrow}^{(i)} )~.
+=\frac{\hbar}{2} c_{0\uparrow}^{(i)\dagger} c_{0\downarrow}^{(i)}, \quad S_i^z = \frac{\hbar}{2} \displaystyle\sum_{\alpha,\beta\in \{\uparrow\downarrow\}} c_{0\alpha}^{(i)\dagger} {\sigma}^{z}_{\alpha\beta} c_{0\beta}^{(i)} = \frac{\hbar}{2} (c_{0\uparrow}^{(i)\dagger} c_{0\uparrow}^{(i)} - c_{0\downarrow}^{(i)\dagger} c_{0\downarrow}^{(i)} )~.\qquad
 \end{eqnarray}
@@
 \subsection{Action on the Hamiltonian}
-We will now obtain the action of these twist operators on the Hamiltonian in eq.~\ref{eq:all-to-all_1}.
+We will now obtain the action of these twist operators on the Hamiltonian in eq.~\eqref{eq:all-to-all_1}.
 Due to the all-to-all nature of the effective Hamiltonian one can find $K!$ possible relative arrangement of those $K$ channels which keeps the Hamiltonian invariant.
 Here we briefly discuss the choice of the closed-loop $\mathcal{C}_{\mu}$ and the insertion of the flux.
-As shown in the Fig.\ref{fig:stargraph-to-alltoall}(b) we have chosen a particular closed path which crosses all the outer spin only once.
+As shown in the Fig.\eqref{fig:stargraph-to-alltoall}(b) we have chosen a particular closed path which crosses all the outer spin only once.
 We embed that closed-loop on a plane and put the flux perpendicular to the plane through the closed loop.
@@
 e^X S^x e^{-X}= S^x+[X,S^x] + \frac{1}{2!}[X,[X,S^x]] +\cdots = \sum_l ( S^x_l \cos \theta_l -  S_l^y \sin \theta_l ) ~,\nonumber\\
-e^X S^y e^{-X}= \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)\nonumber\\
+e^X S^y e^{-X}= \sum_l  (S^y_l \cos\theta_l  + S^x_l \sin\theta_l)\nonumber~,\\
 \theta_l=\frac{2\pi l}{K}~.
@@
 \begin{eqnarray}
-	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_{V + V^\dagger}
+	H = H_d + V = \underbrace{H_0 + J S_d^z s_\text{tot}^z}_{H_d} + \underbrace{\frac{J}{2}S_d^+ s_\text{tot}^- + \text{h.c.}}_{V + V^\dagger}~.
 \end{eqnarray}
@@
 	E_\text{gs}\ket{\Psi_\text{gs}} = H \ket{\Psi_\text{gs}} = \left(H_d + V\right)\ket{\Psi_\text{gs}} \nonumber\\
-	\implies \left(E_\text{gs} - H_d\right)\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z} = V\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}
+	\implies \left(E_\text{gs} - H_d\right)\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z} = V\sum C_{S_d^z, s_\text{tot},s_\text{tot}^z}\ket{S_d^z, s_\text{tot}, s_\text{tot}^z}~.
 \end{eqnarray}
@@
 \end{figure}
-Using the self-energy obtained above, we extract the low-temperature behaviour of the impurity specific heat in the two-channel model for $t=0.1$ and $\mathcal{J}=1$, and it is shown in the left panel of fig.~\ref{fig:Cv_imp}.
+Using the self-energy obtained above, we extract the low-temperature behaviour of the impurity specific heat in the two-channel model for $t=0.1$ and $\mathcal{J}=1$, and it is shown in the left panel of fig.~\eqref{fig:Cv_imp}.
 We find that at low-temperatures, the Sommerfeld coefficient \(C_\text{imp}/T\) follows a logarithmic behaviour for the two-channel case, which is in agreement with the results known in the literature~\cite{affleck_1991_overscreen,affleck_ludwig_1991,affleck_pang_cox_1992,affleck1993exact,
@@
 \end{eqnarray}
-The result is shown in the right panel of fig.~\ref{fig:Cv_imp}, and we find that at low temperatures, the susceptibility has a logarithmic behaviour.
+The result is shown in the right panel of fig.~\eqref{fig:Cv_imp}, and we find that at low temperatures, the susceptibility has a logarithmic behaviour.
 \begin{eqnarray}
-\chi(T) &\propto& \log T
+\chi(T) &\propto& \log T~.
 \end{eqnarray}
@@
 In the absence of any hopping between the star graph and the reduced conduction bath, the full non-magnetic ground states are then of the form:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\ket{l,\sigma} = \ket{S^z_\text{sg}=\frac{-\sigma}{2}}\otimes\ket{e_{\sigma}^{(l)}},~l\in\left\{ 1,2 \right\},~\sigma=\pm 1~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 Using degenerate perturbation theory, we now treat the effects of hopping \(H_\text{int}\) between the star graph and the reduced conduction bath
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	H_\text{int} = -t\frac{1}{\sqrt N}\sum_{k,\sigma,l}\left( c^\dagger_{k\sigma,(l)}c_{0\sigma,(l)} + \text{h.c.} \right)~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 Since all terms in the Hamiltonian conserve the number of particles in each channel, the states with different \(l\) do not mix.
 For each value of \(l\), the \(2\times 2\) matrix of \(H_\text{int}\) takes the form
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	H_\text{int} = \frac{4t^2}{J^*}\begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix} ~,
-\end{aligned}\end{equation}
+\end{eqnarray}
 where the non-zero off-diagonal terms arise because of second-order scattering processes. Diagonalising this gives the modified new ground-states:
-\begin{equation}\begin{aligned}
+\begin{eqnarray}
 	\ket{\psi_\pm^{(l)}} = \frac{1}{\sqrt 2}\left(\ket{l,\uparrow} \pm \ket{l,\downarrow}\right)~,~ E_\pm = -4t^2/J^*~.
-\end{aligned}\end{equation}
+\end{eqnarray}
 We can now compute the residue for scattering processes of the kind \(e^\dagger_{\sigma,(l)} e_{\bar\sigma,(l)}\) between the new ground-state and excited state, and display that they vanish identically:
-\begin{equation}\begin{aligned}
-	Z = |\braket{\psi_+^{(l)}| e^\dagger_{\uparrow,(l)} e_{\downarrow,(l)} | \psi_-^{(l)}}|^2 = \left|\bra{\psi_+^{(l)}}\left(\ket{S_\text{sg}^z=\frac{1}{2}}\ket{e_\uparrow^{(l)}}\right)\right|^2 = 0
-\end{aligned}\end{equation}
+\begin{eqnarray}
+	Z = |\braket{\psi_+^{(l)}| e^\dagger_{\uparrow,(l)} e_{\downarrow,(l)} | \psi_-^{(l)}}|^2 = \left|\bra{\psi_+^{(l)}}\left(\ket{S_\text{sg}^z=\frac{1}{2}}\ket{e_\uparrow^{(l)}}\right)\right|^2 = 0~.
+\end{eqnarray}
 This shows that the single-particle excitations are no longer long-lived, signalling the orthogonality catastrophe inherent in the intermediate coupling fixed point theory of the MCK.
@@
 \begin{eqnarray}
-\fl |\alpha_{-1}\rangle = c|1000 \rangle-b (|0100 \rangle + |0010 \rangle+ | 0001 \rangle), ~ ~ |\alpha_{+1}\rangle = b(|1110 \rangle+ | 1101 \rangle + | 1011 \rangle)-c | 0111 \rangle,\nonumber\\
-\fl |\alpha_0\rangle = -a(|1100 \rangle + |1010\rangle +|1001 \rangle) + a(|0110 \rangle+| 0101 \rangle +| 0011\rangle)~,
+|\alpha_{-1}\rangle = c|1000 \rangle-b (|0100 \rangle + |0010 \rangle+ | 0001 \rangle), ~ ~ |\alpha_{+1}\rangle = b(|1110 \rangle+ | 1101 \rangle + | 1011 \rangle)-c | 0111 \rangle,\nonumber\\
+|\alpha_0\rangle = -a(|1100 \rangle + |1010\rangle +|1001 \rangle) + a(|0110 \rangle+| 0101 \rangle +| 0011\rangle)~,
 \end{eqnarray}
@@
 \begin{eqnarray}
-	H^{(2)}_{eff,off-diag} = \sum_{\substack{(ijk)=\\(123),(231),(312)}}&\left[ c_{i\uparrow}c_{i\downarrow}^{\dagger} \left( -2ab \left\{ \Sigma_{jk} +c_{j\uparrow}^{\dagger}c_{j\downarrow}c_{k\uparrow}c_{k\downarrow}^{\downarrow} \right\} -ac(\Omega_{jk}+\tilde{\Omega}_{jk}) \right) \right.\nonumber\\
-										  &\left. + \textrm{h.c.}\right] \otimes \hat{\Xi}_l~,
+	H^{(2)}_{eff,off-diag} = \sum_{\substack{(ijk)=\\(123),(231),(312)}}&\left[ c_{i\uparrow}c_{i\downarrow}^{\dagger} \left( -2ab \left\{ \Sigma_{jk} +c_{j\uparrow}^{\dagger}c_{j\downarrow}c_{k\uparrow}c_{k\downarrow}^{\downarrow} \right\} -ac(\Omega_{jk}+\tilde{\Omega}_{jk}) \right) + \textrm{h.c.}\right] \otimes \hat{\Xi}_l~,\qquad
 \end{eqnarray}
@@
 \begin{eqnarray}
-\fl \Sigma_{i,j} = n_{i\uparrow}(1-n_{i\downarrow}) (1-n_{j\uparrow})n_{j\downarrow} + (1-n_{i\uparrow})n_{i\downarrow} n_{j\uparrow} (1 -n_{j\downarrow}), ~ ~\Omega_{i,j} =4S_i^z S_j^z n_{i\uparrow} n_{j\uparrow}, ~ ~ \tilde{\Omega}_{i,j} = 4S_{i}^zS_j^z (1-n_{i\uparrow})(1-n_{j\uparrow}) \nonumber~,\\
-\fl \hat{\Xi}_l=  ( c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.})~.
+\Sigma_{i,j} = n_{i\uparrow}(1-n_{i\downarrow}) (1-n_{j\uparrow})n_{j\downarrow} + (1-n_{i\uparrow})n_{i\downarrow} n_{j\uparrow} (1 -n_{j\downarrow}), \quad \Omega_{i,j} = 4S_i^z S_j^z n_{i\uparrow} n_{j\uparrow}\nonumber~,\\
+\tilde{\Omega}_{i,j} = 4S_{i}^zS_j^z (1-n_{i\uparrow})(1-n_{j\uparrow}), \quad\hat{\Xi}_l=  ( c_{l_1\uparrow}^{\dagger} c_{l_1\downarrow} +c_{l_2\uparrow}^{\dagger} c_{l_2\downarrow} + c_{l_3\uparrow}^{\dagger} c_{l_3\downarrow} + \textrm{h.c.})~.
 \end{eqnarray}
@@
 \end{eqnarray}
-The RG fixed point is reached when the denominator in Eq.~\ref{e-TransOp} vanishes, at a certain energy scale \(\Lambda^*\).
+The RG fixed point is reached when the denominator in eq.~\eqref{e-TransOp} vanishes, at a certain energy scale \(\Lambda^*\).
 The vanishing of the denominator can be shown to be concomitant with the vanishing of the off-diagonal component \(H^X\)~\cite{anirbanurg1}, and the fixed point value of the quantum fluctuation operator is equal to one of the eigenvalues of the Hamiltonian.
@@
 \begin{eqnarray}
-	H^* = \sum_{\Lambda_j < \Lambda^*} H^*(\Lambda_j) + \sum_{\Lambda_j > \Lambda^*}H_\text{IOMs}(\Lambda_j)
+	H^* = \sum_{\Lambda_j < \Lambda^*} H^*(\Lambda_j) + \sum_{\Lambda_j > \Lambda^*}H_\text{IOMs}(\Lambda_j)~.
 \end{eqnarray}
@@
 	\label{full_ren}
-	\fl \Delta H_{(j)} = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c  + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(2)}_{(j)}} + \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(3)}_{(j)}}.\qquad
+	\Delta H_{(j)} = &\underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c  + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(2)}_{(j)}} \nonumber\\
+			 &+ \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c + c^\dagger T \frac{1}{\omega^\prime - H_D} T^\dagger c \frac{1}{\omega^\prime - H_D} H_X + \left(c^\dagger \leftrightarrow c\right)}_{\Delta H^{(3)}_{(j)}}.\qquad
 \end{eqnarray}
@@
 \end{eqnarray}
-
 We can also obtain the RG equation for \(J\) from the transverse renormalisation:
@@
 We now come to the third-order renormalisation.
-Following eq.~\ref{full_ren}, the next order renormalisation is
+Following eq.~\eqref{full_ren}, the next order renormalisation is
 \begin{eqnarray}
@@
 
-The second term in eq.~\ref{psector_3rd_ren} can be evaluated in an almost identical fashion. The integral here will be negative of the first term, because of an exchange in the scattering processes.
+The second term in eq.~\eqref{psector_3rd_ren} can be evaluated in an almost identical fashion.
+The integral here will be negative of the first term, because of an exchange in the scattering processes.
 \begin{eqnarray}
@@
 \end{eqnarray}
-The first group of terms (those that appear in \ref{first_group}) in the particle sector can be represented as \(a|b^\prime|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three connected processes.
+The first group of terms (those that appear in \eqref{first_group}) in the particle sector can be represented as \(a|b^\prime|c\), where \(a,b,c \in \left\{z,+,-\right\} \) and represent the operator for the conduction electrons in the three connected processes.
 The \(\prime\) on \(b\) indicates that it is the state of the electrons \textit{not being decoupled}.
-The second group of terms (those that appear in \ref{second_group}) are therefore represented as \(a|b|c^\prime\), because in this group, the interaction \(H_X\) between the electrons that are not being decoupled occur at the very end.
+The second group of terms (those that appear in \eqref{second_group}) are therefore represented as \(a|b|c^\prime\), because in this group, the interaction \(H_X\) between the electrons that are not being decoupled occur at the very end.
 We will only calculate the terms in the particle sector, the ones in hole sector will be equal to these because of particle-hole symmetry. The full list of terms is:

### 2023-04-17 MCK-manuscript/MCK-manuscript.tex
fixed punctuation and equation in main ans supp
rewrote the summary of main results

@@
 \usepackage{iopams}  
-\usepackage{braket,graphicx,amsmath,color}
-\usepackage[hidelinks]{hyperref}
+\usepackage{braket,graphicx,amsmath,cite}
+\usepackage[colorlinks,linkcolor={blue},citecolor={blue}]{hyperref}
 \bibliographystyle{unsrt}
@@
 
-\subsection*{Summary of Main Results}
-We start in section \ref{rg_section} by describing the URG flows for the MCK, the intermediate coupling URG fixed point Hamiltonian and the features of the zero bandwidth (star graph) limit of the effective Hamiltonian.
-In section \ref{sec:props_star}, we explore some properties of the zero bandwidth model: namely, the degree of compensation, impurity magnetisation and impurity susceptibility.
-The degree of compensation is simply the average correlation between the impurity spin and the conduction channel local spins; it is found to be maximum at exact screening, and decreases for both over- and under-screening.
-The magnetisation and susceptibility of the star graph model show a discontinuity and a \(T^{-1}\) divergence respectively.
-We also explore the topological properties of the degenerate ground state manifold of the star graph model using non-local twist and translation operators.
-On decoupling the impurity spin from the conduction spin degrees of freedom within the star graph, we obtain an all-to-all Hamiltonian that represents a local Mott liquid phase.
-In section \ref{sec:excitations}, we obtain the low energy effective Hamiltonian for the low-lying excitations by including a dispersion into the conduction bath.
-Notable features of this effective Hamiltonian include (i) the complete absence of local Fermi liquid terms, and (ii) the emergence of local non-Fermi liquid terms.
-Both are shown to result from the ground state degeneracy of the underlying star graph model.
-The excitations of the two-channel Kondo problem are found to pertain to a local marginal Fermi liquid, signalling an orthogonality catastrophe.
-
-In section \ref{sec:ent_prop}, we study various entanglement signatures (e.g., von-Neumann entanglement entropy, mutual information, multipartite information, Bures distance) of the low energy fixed-point ground state of the MCK problem, with and without dispersion into the bath.
-The discontinuous behaviour observed in these measures for the MCK problem reveal clear distinctions from the single-channel case.
-In \ref{sec:duality}, we discuss two duality transformations that exist for the MCK model - a strong-weak duality, and an over-screened-under-screened duality.
-It is found that the transformations are constrained by the fixed point structure, and impose relations between the under-screened and over-screened models.
-In \ref{anisotropic_rg}, we show the robustness of the ground state degeneracy of the star graph model against the impurity-channel coupling anisotropy, and correlate it with a URG treatment of the channel anisotropic MCK.
-The isotropic fixed point is found to be unstable to asymmetry, leading to impurity phase transitions that lead to dramatic changes in the ground state degeneracy.
-For the sake of brevity, some supporting evidence and details of certain lengthy calculations are presented in Supplementary Materials~\cite{SM}. Finally, we conclude in section \ref{conclusions}.
+{\color{blue}The work is split into seven major sections.
+In Sections 2 and 3, we describe the URG method mentioned above, apply it to obtain the renormalisation group (RG) flows of the multichannel Kondo model, and explore some properties of the zero bandwidth limit of the RG fixed point Hamiltonian.
+In Sections 4 and 5, we study the gapless excitations on top of the zero bandwidth limit.
+In Section 6, we discuss some duality transformation properties of the MCK model.
+In Section 7, we look into the effects of channel anisotropy.
+We finally conclude with some discussions of the results in Section 8.}
+
+\subsection*{Summary of main results}
+\begin{itemize}
+	\item We elucidate, within the the context of the multichannel Kondo problem, the importance of the zero bandwidth limit of the RG fixed point Hamiltonian.
+We show that this zero bandwidth Hamiltonian directly leads to several properties of the MCK problem, like the ground-state magnetisation, scattering phase shift, Wilson loop and 't Hooft operators and degree of compensation.
+	\item The ground-state degeneracy of the zero bandwidth Hamiltonian is found to be topological in nature: the orthogonal states can be explored by the application of twist operators.
+Integrating out the impurity from the conduction bath states leads to the emergence of a topologically degenerate local Mott liquid.
+	\item We also demonstrate that the effective Hamiltonian for the gapless excitations of the fixed point Hamiltonian is of the non-Fermi liquid kind, involving scattering process that connect multiple conduction channels and leading to an orthogonality catastrophe in the ground-state.
+In momentum space, the self-energy resembles that of a marginal Fermi liquid localised near the impurity spin.
+	\item We link the non-Fermi liquid behaviour and orthogonality catastrophe with an ``unrenormalised" scattering phase shift; we show that this phase shift also leads to the well-known anomalous behaviour of quantities like the specific heat, magnetic susceptibility and thermal entropy.
+	\item By combining the strong-weak duality of the MCK Hamiltonian with that of the RG equations, we show that the strong-coupling theory is constrained to be of a simple form.
+We also discuss an additional duality transformation that ``exchanges" the number of channels and impurity spin.
+This property allows us to infer the RG scaling behaviour of one of the models if we know that of the other.
+\end{itemize}
 
@@
 	\label{w_loop}
-	\pi^z = \exp\left[i \frac{\pi}{2} \left(\sigma_d^z + \sum_{l=1}^K \sigma^z_l - K\right)\right] = e^{i \pi \left(J^z - \frac{1}{2}K\right)}~.
+	\pi^z = \exp\left[i \frac{\pi}{2} \left(\sigma_d^z + \sum_{l=1}^K \sigma^z_l - K\right)\right] = e^{i \pi \left(J^z - \frac{1}{2}K\right)}~.\qquad
 \end{eqnarray}
@@
 \begin{eqnarray}\label{phase-stargraph}
-	\delta^{(l)} = \pi n_\mathrm{exc}^{(l)} = \frac{\pi}{K}, ~ ~ l \in \left[1, K\right] 
+	\delta^{(l)} = \pi n_\mathrm{exc}^{(l)} = \frac{\pi}{K}, ~ ~ l \in \left[1, K\right] ~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\Delta H = H_X ({\hat{\omega}-H_D})^{-1} H_X 
+\Delta H = H_X ({\hat{\omega}-H_D})^{-1} H_X ~.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\beta_{\uparrow} ({\mathcal{J}},\omega_{\uparrow}) = ({\mathcal{J}}^2 \Gamma_{\uparrow})/2 ~,~~\Gamma_{\uparrow}=(\omega_{\uparrow}-{\mathcal{J}}(S_d^z-1))^{-1}~.
+\beta_{\uparrow} ({\mathcal{J}},\omega_{\uparrow}) = ({\mathcal{J}}^2 \Gamma_{\uparrow})/2 ~,~~\Gamma_{\uparrow}=(\omega_{\uparrow}-{\mathcal{J}}(S_d^z-1))^{-1}~.\qquad
 \end{eqnarray}
@@
 \begin{eqnarray}
-H^{(1)} = \sum_{ij} |\alpha_i\rangle \langle \alpha_i  | V| \alpha_j \rangle \langle \alpha_j |~.\nonumber\\
+H^{(1)} = \sum_{ij} |\alpha_i\rangle \langle \alpha_i  | V| \alpha_j \rangle \langle \alpha_j |~,\nonumber\\
 H^{(2)} = \sum_{ij} \sum_l |\alpha_i\rangle \frac{\langle \alpha_i  | V| \mu_l \rangle \langle \mu_l  | V| \alpha_j \rangle}{E_0-E_{l}}\langle \alpha_j |~.
@@
 	\label{nfl_terms}
-	\hspace*{-5pt}V_\mathrm{eff} = \frac{2t^2}{{\mathcal{J}^*}}\left[\left(\sigma^z_{0,1}\right)^2 s^+_{0,2} + \left(\sigma^z_{0,2}\right)^2 s^+_{0,1}\right] \left(s^-_{1,1} + s^-_{1,2}\right) + \mathrm{h.c.};\nonumber\\
+	V_\mathrm{eff} =& \frac{2t^2}{{\mathcal{J}^*}}\left[\left(\sigma^z_{0,1}\right)^2 s^+_{0,2} + \left(\sigma^z_{0,2}\right)^2 s^+_{0,1}\right] \left(s^-_{1,1} + s^-_{1,2}\right) \nonumber\\
+			&+ \mathrm{h.c.};
 \end{eqnarray}
@@
 \begin{eqnarray}
-	\gamma &\sim & \left( T/T_K \right)^\frac{1 - 2\delta^{(l)}/\pi}{1 + 2\delta^{(l)}/\pi} = \left( T/T_K \right)^\frac{K-2}{K+2}\sim \chi~,\nonumber\\ 
-	S &\sim & \ln \left[2|\cos \left(\frac{\delta^{(l)}}{1 + 2\delta^{(l)}/\pi}\right)|\right]
-	 = \ln \left[2|\cos \left(\frac{\pi}{K + 2}\right)|\right]~. \label{powerlawquants}
+	\gamma &\sim  \left( T/T_K \right)^\frac{1 - 2\delta^{(l)}/\pi}{1 + 2\delta^{(l)}/\pi} = \left( T/T_K \right)^\frac{K-2}{K+2}\sim \chi~,\nonumber\\ 
+	S &\sim  \ln \left[2|\cos \left(\frac{\delta^{(l)}}{1 + 2\delta^{(l)}/\pi}\right)|\right] \nonumber \\
+	  &= \ln \left[2|\cos \left(\frac{\pi}{K + 2}\right)|\right]~. \label{powerlawquants}
 \end{eqnarray}
@@
 \begin{eqnarray}
-\ket{J^z} \equiv \ket{S_d=1/2,S=K/2;J=(S-1/2),J^z}
+\ket{J^z} \equiv \ket{S_d=1/2,S=K/2;J=(S-1/2),J^z}~,
 \end{eqnarray}
@@
 \begin{eqnarray}
-I^{N}_{\{\mathcal{A}_N\}} = \bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg]- S_{V_{\cap}(\mathcal{A}_N)}~.
+	I^{N}_{\{\mathcal{A}_N\}} = &\bigg[\displaystyle\sum_{m=1}^{N} (-1)^{m-1} \displaystyle\sum_{Q \in \mathcal{B}_m(\{\mathcal{A}\})} S_{V_{\cup}({Q})} \bigg] \nonumber\\
+				    &- S_{V_{\cap}(\mathcal{A}_N)}~.
 \label{eq:I_N_definition}

### 2023-04-18 MCK-manuscript/MCK-manuscript.tex
some corrections

@@
 
-{\color{blue}The work is split into seven major sections.
+The work is split into seven major sections.
 In Sections 2 and 3, we describe the URG method mentioned above, apply it to obtain the renormalisation group (RG) flows of the multichannel Kondo model, and explore some properties of the zero bandwidth limit of the RG fixed point Hamiltonian.
@@
 In Section 7, we look into the effects of channel anisotropy.
-We finally conclude with some discussions of the results in Section 8.}
+We finally conclude with some discussions of the results in Section 8.
 
@@
 In momentum space, the self-energy resembles that of a marginal Fermi liquid localised near the impurity spin.
-	\item We link the non-Fermi liquid behaviour and orthogonality catastrophe with an ``unrenormalised" scattering phase shift; we show that this phase shift also leads to the well-known anomalous behaviour of quantities like the specific heat, magnetic susceptibility and thermal entropy.
+	\item We link the non-Fermi liquid behaviour and orthogonality catastrophe with an ``unrenormalised" scattering phase shift {\color{blue}that can be obtained from the zero bandwidth problem}; we show that this phase shift also leads to the well-known anomalous behaviour of quantities like the specific heat, magnetic susceptibility and thermal entropy.
+	\item {\color{blue}Various entanglement measures like the impurity entanglement entropy and the impurity-bath mutual information for the overscreened cases show a discontinuity as the rest of the conduction bath (beyond the initial site) is introduced back into the problem.
+This discontinuity does not exist in the single-channel problem, and it points to the orthogonality catastrophe present in the overscreened ground-state.}
 	\item By combining the strong-weak duality of the MCK Hamiltonian with that of the RG equations, we show that the strong-coupling theory is constrained to be of a simple form.
-We also discuss an additional duality transformation that ``exchanges" the number of channels and impurity spin.
-This property allows us to infer the RG scaling behaviour of one of the models if we know that of the other.
+We also discuss an additional duality transformation that connects underscreened and overscreened models, that involves exchanging the number of channels and impurity spin.
+This transformation allows us to infer the infrared scaling behaviour of one of the models if we know that of the other.
 \end{itemize}

### 2023-04-19 MCK-manuscript/MCK-manuscript.tex
finalised all changes to manuscript

--- 2023-04-17 MCK-manuscript/MCK-manuscript.tex
@@
 In momentum space, the self-energy resembles that of a marginal Fermi liquid localised near the impurity spin.
-	\item We link the non-Fermi liquid behaviour and orthogonality catastrophe with an ``unrenormalised" scattering phase shift; we show that this phase shift also leads to the well-known anomalous behaviour of quantities like the specific heat, magnetic susceptibility and thermal entropy.
-	\item By combining the strong-weak duality of the MCK Hamiltonian with that of the RG equations, we show that the strong-coupling theory is constrained to be of a simple form.
-We also discuss an additional duality transformation that ``exchanges" the number of channels and impurity spin.
-This property allows us to infer the RG scaling behaviour of one of the models if we know that of the other.
+	\item We link the non-Fermi liquid behaviour and orthogonality catastrophe with an ``unrenormalised" scattering phase shift that can be obtained from the zero bandwidth problem; we show that this phase shift also leads to the well-known anomalous behaviour of quantities like the specific heat, magnetic susceptibility and thermal entropy.
+	\item Various entanglement measures, e.g., impurity entanglement entropy and impurity-bath mutual information, for the overscreened case show discontinuous behaviour as the conduction bath states beyond the zero-bandwidth problem are re-introduced via single-electron hopping.
+These discontinuities do not exist in the single-channel problem, and arise from the orthogonality catastrophe present in the overscreened ground-state.
+	\item By combining the strong-weak duality of the MCK Hamiltonian with that of the RG equations, we show that the strong-coupling theory is constrained to take a simple form.
+We also discuss an additional duality transformation connecting underscreened and overscreened models that involves exchanging the number of channels and impurity spin: this allows us to infer the infrared scaling behaviour of one  class of models from a knowledge of the other.
 \end{itemize}

### 2023-04-19 MCK-manuscript/Supplementary/MCK-supplementary.tex
finalised all changes to manuscript

@@
 
+\subsection{Stability of strong coupling fixed point in the overscreened and underscreened models}
+We recall briefly the contrasting stability of the strong coupling fixed point in the overscreened and underscreened multichannel Kondo problems.
+As pointed out in Ref.\cite{Noz_blandin_1980}, adding electronic tunnelling from the conduction bath to the zero-bandwidth model reveals an effective Heisenberg exchange interaction between the effective spin ($\vec{S}^{*}$) of the zero-bandwidth model and the bath electrons (of the various channels $l=1,\ldots,K$) proximate to it: $H_{\mathrm{eff}} \sim J_{\mathrm{eff}}\sum_{l=1}^{K} \vec{S}^{*}\cdot\vec{S}^{(1)}_{l}$, where $J_{\mathrm{eff}}\sim \mathrm{sgn}(K-2S) t^{2}/J$ and $S^{*}=|K-2S|$.
+For the underscreened case $K<2S$, $J_{\mathrm{eff}}<0$ is ferromagnetic in nature; on the other hand, for the overscreened case $K>2S$, $J_{\mathrm{eff}}>0$ is antiferromagnetic.
+The opposite nature of the effective interaction arises from the fact that the Pauli exclusion principle favours electronic hopping from the conduction bath into the zero-bandwidth model for $\vec{S}^{*}$ being aligned (antialigned) with the incoming bath electrons for $K<2S$ ($K>2S$).
+Accordingly, $J_{\mathrm{eff}}$ is found to be RG irrelevant for the underscreened case, and leads to the strong coupling fixed point for the Kondo coupling $J$ being stable.
+On the other hand, $J_{\mathrm{eff}}$ is found to be RG relevant for the overscreened case and leads to a stable fixed point at intermediate coupling.
+Together with the duality relation between overscreened and underscreened multichannel Kondo problems discussed in Sec.
+6 of the main manuscript, this allows us to infer the scaling behaviour of one class of models from a knowledge of the other.
+
 \section*{References}

### 2023-04-19 Ref Response JCPM/RefereeResponse.tex
created referee response and tracked pdf

\documentclass{article}
\usepackage{amsmath,amssymb,braket}
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\usepackage{xcolor}
\usepackage[legalpaper,portrait,margin=2cm]{geometry}
\DeclareUnicodeCharacter{2212}{-}
\DeclareUnicodeCharacter{03B8}{+}
\newcommand{\shat}{\hat{\mathbf{s}}}
\newcommand{\pin}{\par\noindent}
\newcommand{\response}[1]{{\color{blue}\subsection*{Response:}{#1}}}
\renewcommand{\thesubsection}{Feedback from the referee:}
\newcommand{\point}[1]{\subsection{}{#1}}

\title{Referee response to JPCM-121631}
\author{Siddhartha Patra, Abhirup Mukherjee, Anirban Mukherjee, N. S. Vidhyadhiraja,\\ A. Taraphder, Siddhartha Lal}

\begin{document}
\maketitle

\flushleft
We present our responses below (in blue).

\section*{Response to the first referee}
{\color{blue}We thank the referee for their comments and feedback.}

\section*{Response to the second referee}
\point{
However, it is to be noted that this system has been studied in great details in many earlier works. So it would be nice if the authors can provide a list of results that they obtain from their analysis which has not been obtained earlier. To me, this was not clear from their introduction.}

\response{We thank the referee for their comments and suggestion. To address this, we have improved the `{\bf Summary of results}' subsection in the introduction and stated very precisely what new results have been obtained by us.
For the convenience of the referee, we are providing a copy of the same:

{\it \flushleft Summary of main results}
	\begin{itemize}
	\item We elucidate, within the the context of the multichannel Kondo problem, the importance of the zero bandwidth limit of the RG fixed point Hamiltonian. We show that this zero bandwidth Hamiltonian directly leads to several properties of the MCK problem, like the ground-state magnetisation, scattering phase shift, Wilson loop and 't Hooft operators and degree of compensation.
	\item The ground-state degeneracy of the zero bandwidth Hamiltonian is found to be topological in nature: the orthogonal states can be explored by the application of twist operators. Integrating out the impurity from the conduction bath states leads to the emergence of a topologically degenerate local Mott liquid.
	\item We also demonstrate that the effective Hamiltonian for the gapless excitations of the fixed point Hamiltonian is of the non-Fermi liquid kind, involving scattering process that connect multiple conduction channels and leading to an orthogonality catastrophe in the ground-state. In momentum space, the self-energy resembles that of a marginal Fermi liquid localised near the impurity spin. 
	\item We link the non-Fermi liquid behaviour and orthogonality catastrophe with an ``unrenormalised" scattering phase shift that can be obtained from the zero bandwidth problem; we show that this phase shift also leads to the well-known anomalous behaviour of quantities like the specific heat, magnetic susceptibility and thermal entropy.
	\item Various entanglement measures, e.g., impurity entanglement entropy and impurity-bath mutual information, for the overscreened case show discontinuous behaviour as the conduction bath states beyond the zero-bandwidth problem are re-introduced via single-electron hopping. These discontinuities do not exist in the single-channel problem, and arise from the orthogonality catastrophe present in the overscreened ground-state.
	\item By combining the strong-weak duality of the MCK Hamiltonian with that of the RG equations, we show that the strong-coupling theory is constrained to take a simple form. We also discuss an additional duality transformation connecting underscreened and overscreened models that involves exchanging the number of channels and impurity spin: this allows us to infer the infrared scaling behaviour of one  class of models from a knowledge of the other.
	\end{itemize}
}

\section*{Some additional changes in the manuscript}
We made the following change(s) in the manuscript:
\begin{itemize}
	\item We have added a paragraph just above the `Summary of main results' subsection in the introduction, describing the layout of the work.
	\item For the sake of completion, we have also added a subsection at the end of the Supplementary Materials recalling the argument of Nozieres and Blandin regarding the contrasting stability of the strong-coupling fixed point in the case of overscreened and underscreened MCK models.
\end{itemize}

Both these changes, as well as the improved {\bf Summary of results} subsection, have been {\it marked in blue colour} in the tracked pdf that is titled 'Complete Document for Review (PDF Only)'.

\bibliographystyle{unsrt}
\bibliography{../manuscript/mscript_mck_full.bib}
\end{document}
